### 2020-05-23 paper/tci.tex
First commit

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

\documentclass[journal]{IEEEtran}

\bibliographystyle{IEEEtran}
\usepackage{lineno,hyperref}
\usepackage{amsmath,graphicx, amssymb,tabularx,booktabs}
\usepackage{subcaption}
\usepackage[font=small,skip=2pt]{caption}
\usepackage{boxedminipage}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xcolor}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Eliminating prior-bias from sparse-projection tomographic reconstructions}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Preeti Gopal,
  Sharat Chandran,
  Imants Svalbe,
        and~Ajit Rajwade
\thanks{Preeti Gopal is with IITB-Monash Research Academy}
\thanks{Sharat Chandran and Ajit Rajwade are with the Department of Computer Science and Engineering, IIT Bombay}
\thanks{Imants Svalbe is with the School of Physics and Astronomy, Monash University}}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Tomographic reconstruction from undersampled measurements is a necessity when the measurement process is potentially harmful, needs to be rapid, or is resource-expensive. In such cases, information from previously existing longitudinal scans of the same object (forming the `object-prior'), helps in the reconstruction of the current object (`test') while requiring significantly fewer updating measurements. In this work, we improve the state of the art by proposing the context under which priors can be effectively used based on the final goal of the application at hand.

Our work is based on longitudinal data acquisition scenarios where we wish to study new changes that evolve within an object over time, such as in repeated scanning for disease monitoring, or in tomography-guided surgical procedures. While this is easily feasible when measurements are acquired from a large number of projection angles (referred to as `views' henceforth), it is challenging when the number of views is limited. If the goal is to track the changes while simultaneously reducing sub-sampling artefacts, we propose (1) acquiring measurements from a \emph{small} number of views and using a global \emph{`unselective'} prior based reconstruction. If the goal is to observe \emph{details} of new changes, we propose (2) acquiring measurements from a \emph{moderate} number of views and using a more involved reconstruction routine. We show that in the latter case, a `selective' technique is necessary in order to prevent the prior from adversely affecting the reconstruction of new structures that are absent in any of the earlier scans. The reconstruction of new regions is safeguarded from the bias of the prior by computing regional weights that moderate the local influence of the priors. We are thus able to effectively reconstruct both the old and the new structures in the test. We have tested the efficacy of our method on synthetic as well as real volume data. The results demonstrate the use of both unselective and selective priors in different scenarios. Our methods significantly improve the overall quality of the reconstructed data while minimizing the number of measurements needed for imaging in longitudinal studies.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Limited-view tomographic reconstruction, compressed sensing, priors, longitudinal studies.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
\label{sec:intro}
Computed Tomography (CT) deals with the recovery of an entire object from a limited set of projection data which are acquired by passing X-rays at different orientations (`views') through the object. In order to minimize the radiation exposed to the subject, current research seeks to either significantly reduce the radiation intensity required to reconstruct with adequate fidelity~\cite{gopal2019low} or significantly reduce the number of measurements required to reconstruct with adequate fidelity. In this regard, there are two lines of pursuit. One is to intelligently choose those sets of projection views that capture most information~\cite{King2018,Anthony2018,barkan17,fischer16,andrei14}, and the other is to improve the reconstruction algorithms to get the most accurate recovery of the underlying slice, given the measurements from any limited set of views~\cite{yang2018,geyer2015,kilic2011}. This paper deals with the latter scenario.

In this context, measurements in conventional data acquisition techniques are acquired by sampling the physical object uniformly above the Nyquist rate. However, in the last decade, reconstruction from sub-Nyquist sampled data has been made possible due to methods such as the widely used Compressed Sensing (CS) technique~\cite{Donoho,introCS}, which assumes the data to exhibit properties such as sparsity of the underlying image under certain mathematical transforms such as the Discrete Cosine Transform (DCT) or wavelet transforms. Fig.~\ref{fig:diff_methods} shows that although CS removes the artefacts created due to sub-sampling, its reconstruction is blurred. When prior information about the data is used along with CS, the reconstruction improves significantly. The algorithm presented in~\cite{Essam2015} drew inspiration from CS and solved for the reconstruction from limited views using alternating direction method of multipliers. In other techniques like in~\cite{Polak2017}, reconstruction is performed by estimating sparse gradients in the data. In~\cite{Li2015}, the required number of views is reduced by minimizing the total variation in the data. The measurements and an initial estimate of the data guide the iterative routines.

\begin{figure}[!h]
\centering
\fcolorbox{red}{white}{\begin{subfigure}[b]{0.155\linewidth}
        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template1.png}
        \caption{}
     \end{subfigure}
\begin{subfigure}[b]{0.155\linewidth}
        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template2.png}
        \caption{}
     \end{subfigure}
\begin{subfigure}[b]{0.155\linewidth}
        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template3.png}
        \caption{}
     \end{subfigure}
\begin{subfigure}[b]{0.155\linewidth}
        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template4.png}
        \caption{}
     \end{subfigure}
\begin{subfigure}[b]{0.155\linewidth}
        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template5.png}
        \caption{}
     \end{subfigure}
\begin{subfigure}[b]{0.155\linewidth}
        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template6.png}
        \caption{}
     \end{subfigure}}\\
\begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/humerus/global_local/groundTruth.png}}
        \caption{Test}
\end{subfigure}
\quad
    \begin{subfigure}[b]{0.23\linewidth}
        \includegraphics[width=\textwidth]{../images/humerus/fbp_humerus.png}
        \caption{FBP}
     \end{subfigure}
    \begin{subfigure}[b]{0.23\linewidth}
        \includegraphics[width=\textwidth]{../images/humerus/global_local/reconNoPrior.png}
        \caption{CS}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\linewidth}
        \includegraphics[width=\textwidth]{../images/humerus/global_local/global.png}
        \caption{This paper}
     \end{subfigure}
    \caption{\textit{Knowing more about the data helps.} Reconstructions of (g) a test slice  of size $(200,200)$ from the Humerus CT dataset~\cite{humerus} are performed using object-prior [(a)-(f)] and from measurements obtained from only 10 views. (h) Filtered backprojection (FBP) shows streaky sub-sampling artefacts (i) CS reduces the artefacts significantly while slightly blurring details (j) Prior information coupled with CS greatly improves the reconstruction.}
\label{fig:diff_methods}
\end{figure}

In addition, when some extra information about the object's structure is known~\cite{PICCS,cardiacPICCS,lubner2011,pirple,mota2017}, it is beneficial in further reducing the number of measurements.  These prior-based techniques use information from previously scanned data (`object-prior') of the same object or a similar one, and utilize it to reconstruct new volumes from very few sets of additional measurements. However, the above methods have the following two limitations: (1) the prior information may potentially overwhelm the essential details that appear in the test, (2) there is the key issue of choice of \textit{a} particular previously scanned object among the many previously acquired scans. A large part of this paper is dedicated to alleviating the former limitation, which is an important issue that has so far been overlooked in the literature on tomography. The latter limitation was relaxed in~\cite{liu2016,Xu2012} by building dictionary-based priors from multiple previously scanned objects. However, as reported in~\cite{my_dicta_paper}, dictionary priors are not as accurate and fast as global eigenspace priors.  Global eigenspace priors are better able to exploit the similarity of a test volume to object-prior, by assuming that the new test volume lies within the space spanned by the eigenvectors of the multiple representative previously scanned objects. Fig.~\ref{fig:diff_methods} shows the advantage of combining the global prior with CS.
\subsection{Contributions}
\label{sec:contributions}
In this work (Fig.~\ref{fig:prior_overview}), we focus on further reducing the number of measurements, with  particular emphasis on longitudinal studies. For example, we consider medical datasets which consist of multiple CT scans being taken during a radio-frequency ablation procedure~\cite{Dong2015}. The process consists of inserting a needle probe into a patient's body. When the needle reaches the tumor site, an electric current is passed to burn the tumor. Repeated CT scans of the patient need to be acquired in order to visualize the movement of the needle and to ensure that it is reaching the appropriate target. A few initial densely-sampled scans are used as object-prior to help the physician know the position of the needle. The later scans are used to reveal the exact changes during and after burning of the tumor (ablation).  In this context, we demonstrate the combined use of CS with the global prior, in two flavors: the vanilla (unselective) and selective global prior-based reconstruction. The choice of the number of measurement views and the type of reconstruction- unselective or selective, is driven by the goal of the procedure.

\begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{../images/prior_cmb.png}
        \caption{Overview of our work. The choice of the number of measurement views and the type of reconstruction is driven by the goal in the application under consideration.  When our goal is relatively simple, such as tracking the location of new changes while simultaneously reducing sub-sampling artefacts, we propose (a) acquiring measurements from a small number of views (`few-view' imaging) and using unselective prior based reconstruction. When our goal becomes more ambitious, such as observing details of the new changes while simultaneously reducing sub-sampling artefacts, we propose (b) acquiring measurements from a slightly higher number of views (`moderate-view' imaging) and using selective prior-based reconstruction. In either case, the number of views is lower than what is conventionally used.}
 \label{fig:prior_overview}
\end{figure}

\begin{enumerate}
\item Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using unselective prior based reconstruction. 
\item Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts. In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a selective prior-based reconstruction. The selective technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
\end{enumerate}

After the results of the above study are presented, the remainder of this paper discusses each of the above two approaches in detail. Specifically, we discuss how the global prior can impose an inflexible constant weight (and hence a bias) when reconstructing the data. If we want to observe details, this bias can be removed by moderating the control of the prior by imposing spatially varying weights to the prior.

This paper is organized as follows: Section~\ref{sec:tmh} demonstrates the utility of both the unselective and selective methods on a longitudinal medical dataset. Section~\ref{sec:unselective_global_prior} describes the construction of the unselective global eigenspace prior. In addition, we recap the advantages of global prior over dictionary priors. Section~\ref{sec:selective_prior} describes how the unselective prior needs to be modified when accurate details of new changes are to be observed. A selective technique offers a solution. Results validated on both synthetic and real 3D biological datasets are shown. Finally, we conclude with key inferences that can be drawn from our work in Section~\ref{sec:conclusions}.

%--------------------------------THM section-------------------------

\section{Application: Reconstruction for CT-guided radio-ablation study}
\label{sec:tmh}
Before diving into the details of the unselective and the selective global prior methods, we first show how both the techniques can be applied to our advantage in a real-life medical longitudinal study. Our data~\footnote{Source: Tata Memorial Centre~\cite{tmh}, Parel, Mumbai.  This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of CT scans from a longitudinal study. This involves successive scans of the liver taken during a radio-frequency ablation procedure described in the previous section. In such a procedure, the physician inserts a thin needle-like probe into the organ~\cite{rfa}. Once the needle hits the tumor, a high-frequency current is passed through the tip of the probe and this burns the malignant tumor. Throughout this process, multiple CT scans help the physician to track the position of the needle and check the changes within. In this context, we classify the goal of any of our reconstruction techniques into two categories:

%--------------------------Results on TMH data--------------------------
%------------------RFA 2 data
\begin{figure}[h!]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 2}
    \end{subfigure}
     \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 3}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 4}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 5}
    \end{subfigure}
              \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 6}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 7}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 8}
    \end{subfigure}     
     \caption{Radio-frequency ablation dataset: One of the slices (512 x 512) from each of the 8 scan volumes of a longitudinal study dataset of the liver. Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor. (h) the organ after the ablation: this slice is displayed on a separate intensity scale to enable proper viewing of the region marked in green that shows the after-effects of ablating the tumor.} 
\label{fig:RFA2_test_object-prior}
\end{figure}

%--------------------RFA 2 few views
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/very_few_views/colorTestIm.png}}}\hfill
\subcaptionbox{Backprojection}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
\subcaptionbox{CS}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
\subcaptionbox{Proposed\\ method: unselective prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) Filtered backprojection and no prior resulting in streaks, SSIM $= 0.48$ (c) CS and no prior resulting in blurred bone structures, SSIM $=0.35$ and (d) unselective global prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$. The region enclosed in red rectangle is our RoI as it contains both the new position of the needle and some background. All SSIM values are computed for this RoI.}}
\label{fig:RFA2_very_few_views}
\end{figure}

%-------RFA2 moderate views

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
\subcaptionbox{Backprojection}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
\subcaptionbox{CS}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
\subcaptionbox{Proposed\\ method: unselective\\ prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
\subcaptionbox{Proposed\\ method: selective prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
\subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) CS with SSIM $=0.46$ and (d) unselective global prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) selective prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}). The region enclosed in green rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background. The SSIM is computed in this RoI. (f) shows the computed weights map (defined later in the paper) used for reconstruction. Darker intensities indicate lower weights to prior as these are the regions of new changes.}
\label{fig:RFA2_few_views}
\end{figure}

\begin{enumerate}
\item To track the position of the needle in a relatively well reconstructed background.
\item To accurately observe the new changes amidst a relatively well reconstructed background after the needle touches the tumor.
\end{enumerate}

The needle has a very high attenuation coefficient when compared to that of the organs. Hence, the needle can be tracked by acquiring measurements from a very small number of views. We use the unselective global prior reconstruction here to reduce the artefacts due to sub-sampling. The unselective method is fast and sufficient to track the position of the needle.  Once the needle reaches the site of the tumor, we propose changing the imaging protocol to acquire measurements from a moderate number of views. This will enable us to get more information about the new changes. In addition, we then deploy the selective prior method in order to locate the regions of new changes and penalize any dominance of the prior in these regions.  Regardless of the imaging protocol we use (`few' or `moderate'), the number of views is smaller (atleast one-fifth) than the conventional number of views used in a standard hospital setting.

The dataset from this longitudinal medical study consists of 8 scans taken during the ablation procedure. We demonstrate our method for 2D reconstruction by choosing a single slice from each of the 8 volumes as our dataset. Note that all these 8 slices are located at the \emph{same} index~\footnote{The notion of~\textit{same index} (slice number corresponding to the same depth) makes sense in the context, because in such problems, the different scans are aligned with each other.} within each of the respective volumes. Fig.~\ref{fig:RFA2_test_object-prior} shows the chosen set of 2D slices (each of size $512 \times 512$) from the different volumes. Observe that the needle is seen in all of the first 7 slices  and the effect of ablation is seen in the 8th slice. \\

\textbf{Tracking the needle:} We first choose slices 1-6 as our object-prior, and reconstruct slice 7 with the specific goal of tracking the needle and simultaneously reduce artefacts. Fig.~\ref{fig:RFA2_very_few_views} shows the reconstruction of slice 7 from its measurements from only 90 views. The reconstructions are quantitatively compared using the Structural Similarity Index Metric (SSIM).\\

\textbf{Observing details of the ablation:} Next, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e. a somewhat higher number of views this time. Fig.~\ref{fig:RFA2_few_views} shows the reconstructions of slice 8 by different methods. We see that the selective prior reconstruction brings in the advantage of the prior without it adversely affecting the new regions.

%---------------------------------Unselective section---------------------
\section{Methods}
\label{sec:methods}
Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a global (unselective) prior-based reconstruction in Sec.~\ref{sec:unselective_global_prior}. This is followed by details of our technique in Sec.~\ref{sec:selective_prior}. Our method estimates the location and magnitude of new changes, and eventually prevents the prior from adversely affecting the reconstruction of new regions in the test. This, we refer to as a \textit{selective} global prior-based reconstruction routine.
\subsection{\textbf{Summary of unselective global prior-based reconstruction}}
\label{sec:unselective_global_prior}

Principal Component Analysis (PCA) has been traditionally used to find the significant modes of (Gaussian corrupted) data. In this regard, it has been widely applied in the context of data compression. However, PCA can also be seen as a tool to provide an orthogonal basis to represent the space in which the test data could lie. This space is constructed from the available set of previously scanned objects which must cover a realistically representative range of structures. We first present the eigenspace-cum-CS prior-based reconstruction, which was shown~\cite{my_dicta_paper} to be better when compared to dictionary-based priors. %A preliminary version of this particular method was earlier presented in \cite{my_dicta_paper}.

To begin with, when an object is scanned multiple times, a set of high quality reconstructions (i.e. reconstructions from a dense set of projection views) may be chosen as object-prior for the reconstruction of future scan volumes, which in turn, may be scanned using far fewer measurements. The eigenspace $E_{\text{high}}$ of the $L$ previously scanned objects $Q_1,Q_2,...,Q_L$ is pre-computed. Here, it is assumed that the test volume can be expressed as a sparse linear combination of the principal components (eigenvectors of the covariance matrix) obtained from a group of structurally similar volumes. Hence, the object-prior is represented by means of PCA. For the eigenspace to encompass a range of possible structures in the test slice, the object-prior must represent a wide structural range. Moreover, if these volumes are not aligned, then they must be first registered before computing the prior. The prior is built by computing the covariance matrix from the template set $\{Q_i\}_{i=1}^L$. \emph{The space spanned by the eigenvectors $\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance matrix is the global prior and is assumed to contain any test slice that is similar, but not necessarily identical to the object-prior.}  We use all of the $L-1$ orthogonal eigenvectors as a basis to represent the unknown test volume. Let $\boldsymbol{x} = \boldsymbol{\Upsilon\theta}$ denote the reconstructed volume, $\boldsymbol{y} = \boldsymbol{\mathcal{R} x}$ its measured tomographic projections, $\boldsymbol{\mathcal{R}}$ the tomographic projection operator, $\boldsymbol{\theta}$ the sparse coefficients of $\boldsymbol{x}$, $\boldsymbol{\Upsilon}$ the basis in which $\boldsymbol{x}$ is assumed to be sparse, $\boldsymbol{\mu}$ the mean of the previously scanned objects, and $\boldsymbol{\alpha}$ the vector of eigen-coefficients of the test scan, of which $\alpha_k$ is the $k^{\textrm{th}}$ element. Then, once the eigenspace is pre-computed, the test is reconstructed by minimizing the following cost function:
\vspace{4mm}
 \begin{equation}
   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
J_1(\boldsymbol{\theta,\alpha}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1+\lambda_2\lVert\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k)\rVert_2^2.
\label{Eq:main_prior}
\end{equation}
Here, $\lambda_1$, $\lambda_2$ are tunable weights given to the sparsity and prior terms respectively. The unknowns $\boldsymbol{\theta}$ and $\boldsymbol{\alpha}$
are solved by alternately minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{\theta})$ using a fixed $\boldsymbol{\alpha}$, and $J_{\boldsymbol\theta}(\boldsymbol{\alpha})$ using the resultant $\boldsymbol{\theta}$, where 
\begin{align}
J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) &\triangleq \lVert\boldsymbol{\mathcal{R} x- y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1+\lambda_2\lVert\boldsymbol{x} - (\boldsymbol{\mu + V\alpha})\rVert_2^2, \\
J_{\boldsymbol\theta}(\boldsymbol{\alpha}) &\triangleq \lVert\boldsymbol{\Upsilon\theta} - (\boldsymbol{\mu + V\alpha})\rVert_2^2.
\end{align}
Note that $\boldsymbol{\theta}$ is solved for using the basis pursuit CS solver~\cite{l1ls}. Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
\begin{equation}
\boldsymbol{\boldsymbol{\alpha}} = \boldsymbol{V}^T(\boldsymbol{\Upsilon \theta} -\boldsymbol{\mu}).
\end{equation}
 Optimal values of $\lambda_1, \lambda_2$ must be empirically chosen \textit{a priori}, based on the reconstructions of one of the template volumes (see also Sec.~\ref{sec:discussion}). The cost function described in Eq.~\ref{Eq:main_prior} is biconvex and the convergence of this optimization is guaranteed by the monotone convergence theorem.
 %---------------------------------------------------------
 \vspace{2mm}
\subsubsection{\textbf{Patch-based techniques}}
\label{sec:patch_based}
Next we present a comparison~\cite{my_dicta_paper} of the performance of the aforementioned PCA-based global prior with a prior that is based on construction of patch-wise dictionaries. In both cases, the reconstruction routine is based on typical CS techniques. The well-known K-SVD algorithm \cite{Aharon2006} was chosen for construction of patch-based dictionaries. For this, patches were extracted from each of the template volumes, from which an overcomplete dictionary was obtained. The basic aim of the K-SVD algorithm (or any overcomplete dictionary learning technique) is the compact linear representation of all these patches using the dictionary columns. Let $\boldsymbol{D}$ denote the dictionary learned, $N_p$ the total number of patches, and $\boldsymbol{H_i}$ the operator to extract the $i^{\textrm{th}}$ patch from the intermediate reconstructed slice/volume. Then, once $\boldsymbol{D}$ is computed in an earlier `training phase', each new test slice (or test volume) can be reconstructed by optimizing a cost function such as the one below:
\begin{multline}
J_2(\boldsymbol{\theta},\{\boldsymbol{\alpha_i}\}_{i=1}^{N_p}) = \lVert\boldsymbol{\mathcal{R}\Upsilon\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \\ \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\lVert \boldsymbol{H_i\Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2 +\frac{\lambda_3}{ N_p}\sum_{i=1}^{N_p}\lVert\boldsymbol{\alpha_i}\rVert_1.
\label{Eq:main_patchBased}
\end{multline}
The reconstruction proceeds in an alternating manner, first by minimization of Eq.~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}. For both these, the solver in~\cite{l1ls} is used. For the former case, the cost function reduces to:
\begin{equation}
J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = \lVert \boldsymbol{\mathcal{R} \Upsilon \theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\rVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2.
\label{Eq:primaryObj_patchBased}
\end{equation}
For each $i \in \{1,...,N_p\}$, the cost function reduces to:
\begin{equation}
J_{\boldsymbol{\theta}}(\boldsymbol{\alpha}_i) =  \lVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D\alpha_i}\rVert_2^2  + \frac{\lambda_3}{\lambda_2}\lVert\boldsymbol{\alpha_i}\rVert_1.
\label{Eq:alpha_patchBased}
\end{equation}
This summarizes the comparison with patch-based methods.
%----------------------------------------------------

\subsection{\textbf{Selective prior-based reconstruction}}
\label{sec:selective_prior}
\vspace{1mm}
\noindent \begin{boxedminipage}{0.5\textwidth} 
{\bf Schematic 1}: Motivation behind our algorithm. (The plus $\oplus$ and the
minus $\ominus$ operators are placeholders; precise details available
in Section~\ref{sec:thealgo}). 
%\vspace{0.2cm}

{\small
 Let \textcolor{blue}{prior $Q:=$ old regions ($O$)}\\
 Let \textcolor{blue}{test volume $\boldsymbol{x}:=$ old regions ($O$) $\oplus$ new regions ($N$)}\\
% \textbf{Steps:}     
    \begin{enumerate}
\item  Compute pilot reconstruction of $\boldsymbol{x}$. Let this be called $X$.\\ \textcolor{blue}{$X = O \oplus N \oplus Ar(O) \oplus Ar(N)$}, where \\ \textcolor{blue}{$Ar(O)$} denote the reconstruction artefacts that depend on the old regions, the imaging geometry and the reconstruction method, and\\
 \textcolor{blue}{$Ar(N)$} denote the reconstruction artefacts that depend on the new regions, imaging geometry and the reconstruction method.
\item  Note that \textcolor{blue}{$Q \ominus X = N \oplus Ar(O) \oplus Ar(N)$} gives the new regions, but along with lots of artefacts due to the imaging geometry (sparse views). To eliminate these unwanted artefacts, compute \textcolor{blue}{$Y = Q \oplus Ar(O)$} by simulating projections from $Q$ using the same imaging geometry used to scan $\boldsymbol{x}$, and then reconstructing a lower quality prior volume $Y$. 
    \item Note that \textcolor{blue}{$Y \ominus X = N \oplus Ar(N)$} contains the artefacts due to the new regions only. These are different for different reconstruction methods. To eliminate these method dependent artefacts, compute $Y$ and $X$ using different reconstruction methods. Let these be denoted by $Y^j$ and $X^j$ respectively.
    \item Compute
\vspace{-0.2cm}
           \textcolor{blue}{\begin{equation*}
            Y^1 \ominus X^1 = N \oplus Ar^1(N)
           \end{equation*}
\vspace{-0.5cm}
           \begin{equation*}
            Y^2 \ominus X^2 = N \oplus Ar^2(N)
           \end{equation*}}
\vspace{-0.4cm}
   \item  New regions are obtained by computing
\vspace{-0.2cm}
          \textcolor{blue}{\begin{equation*}
          (Y^1 \ominus X^1)\cap(Y^2 \ominus X^2)= N
          \end{equation*}}   
\vspace{-0.5cm}
    \item Finally, assign space-varying weights $\boldsymbol{W}$ based on step $5$.
    \end{enumerate}
\label{algo:newRegionDetection}
}
\end{boxedminipage}
%--------------------------------------------------
\\

Although the unselective global prior can be very useful in some circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a major limitation when we want accurate details of the new changes. While the unselective prior compensates very well for the possible artefacts due to sparse measurements, it dominates the regions with new changes masking the signal, as seen in Fig.~\ref{fig:RFA2_few_views}-d. Ideally, we will want to impose the prior only in the regions that are common between the test and object-prior.  Our selective prior based reconstruction overcomes this limitation by minimizing the following cost function:
\begin{equation}
%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
\label{eq:selective_prior}
\end{equation}
The key to our method is the discovery of a diagonal weights
 matrix $\boldsymbol{W}$, where $W_{ii}$ contains the (non-negative) weight assigned to the $i^{\textrm{th}}$ voxel of the prior. $\boldsymbol{W}$ is first constructed using some preliminary reconstruction methods (to be described in the following section), following which Eq.~\ref{eq:selective_prior} is used to obtain the final reconstruction. In regions of change in test data, we want lower weights for the prior when compared to regions that are similar to the prior.  
\vspace{2mm}
 \subsubsection{\textbf{Computation of weights matrix $\boldsymbol{W}$}}
Since the test volume (referred to as $\boldsymbol{x}$) is unknown to begin with, it is not possible to decipher the precise regions in $\boldsymbol{x}$ that are different from all the previously scanned objects (`object-prior'). We refer the reader to Schematic 1 that describes the evolution of the procedure used to detect the new regions in the unknown volume. We start with $X^{\text{fdk}}$, the initial backprojection reconstruction of the test volume using the Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} in an attempt to discover the difference between the object-prior and the test volume. Let $\boldsymbol{V_{\text{high}}}$ be the eigenspace constructed from high-quality object-prior. However, the difference between $X^{\text{fdk}}$ and its projection onto the eigenspace $\boldsymbol{V_{\text{high}}}$ will detect the new regions along with  many false positives (false new regions). This is because, $X^{\text{fdk}}$ will contain many geometric-specific artefacts arising from sparse measurements (angle undersampling), which are absent in the high quality object-prior used to construct the eigenspace $\boldsymbol{V_{\text{high}}}$. To discover unwanted artefacts of the imaging geometry, in a counter-intuitive way, we generate \emph{low quality} reconstruction of the object-prior as described below.
\vspace{2mm}
\subsubsection{\textbf{Algorithm to compute weights-map $\boldsymbol{W}$}}
\label{sec:thealgo}
\begin{enumerate}

\item Perform a pilot reconstruction $X^{\text{fdk}}$ of the
  test volume $\boldsymbol{x}$ using FDK.

\item Compute low quality template volumes $Y^\text{fdk}$. 
In Schematic 1, for ease of exposition, we assumed a single
template. In the sequel, we assume $L$ previously scanned objects from which we build
an eigenspace. 
\vspace{-0.1cm}

  \begin{enumerate}
  \item Generate simulated measurements $\boldsymbol{y_{Q_i}}$ for every template $Q_i$, using the exact same projections views and imaging geometry with which the measurements $\boldsymbol{y}$ of the test volume $\boldsymbol{x}$ were acquired, and 
\item Perform $L$  preliminary FDK reconstructions of each of the $L$ object-prior from $\boldsymbol{y_{Q_i}}$.  Let this be denoted by $\{Y^{\text{fdk}}_i\}_{i=1}^L$.
  \end{enumerate}
\item Build eigenspace $\boldsymbol{V_{\text{low}}}$ from $\{Y^{\text{fdk}}_i\}_{i=1}^L$.  Let $P^{\text{fdk}}$ denote projection of $X^{\text{fdk}}$ onto $\boldsymbol{V_{\text{low}}}$. The difference between $P^{\text{fdk}}$ and $X^{\text{fdk}}$ will not contain false positives due to imaging geometry, but will have false positives due to artefacts that are specific to the reconstruction method used. To resolve this, perform steps $4$ and $5$.
%\vspace{-0.3cm}
\item Project with multiple methods.
%\vspace{-0.1cm}
  \begin{enumerate}
  \item Perform pilot reconstructions of the test using $M$ different
    reconstruction algorithms\footnote{CS~\cite{lasso}, Algebraic Reconstruction Technique (ART)~\cite{art},
     Simultaneous Algebraic Reconstruction Technique (SART)~\cite{sart} and  Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt}}. Let this set be denoted
    as $X \triangleq \{X^j\}_{j=1}^M$ where $j$ is an index for the
    reconstruction method, and $X^1 = X^{\text{fdk}}$.

  \item From $\boldsymbol{y_{Q_i}}$, perform reconstructions of the template $Q_i$ using the $M$ different algorithms, for each of the $L$ previously scanned objects. Let this set be denoted by $Y \triangleq \{\{Y_{i}^j\}_{j=1}^M\}_{i=1}^L$ where $Y^{1}_i = Y^{\text{fdk}}_i$, $\forall i \in \{1,..,,L\}$.

  \item For each of the $M$ algorithms (indexed by $j$), build an eigenspace $\boldsymbol{V_\text{low}^j}$ from $\{Y_1^j,Y_2^j, \ldots, Y_{L}^j\}$. %($j=1..M$).

  \item Next, for each $j$,  project $X^j$  onto $\boldsymbol{V_\text{low}^j}$. Let this projection be denoted by $P^j$. To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e. are similar to the template reconstructions). The rest, i.e. new changes and their reconstruction method-dependent-artefacts, are not captured by this projection and need to be eliminated.
  \end{enumerate}
%\vspace{-0.1cm}
\item To remove all reconstruction method dependent false positives, we compute $\min_{j}(|X^j(x,y,z) - P^j(x,y,z)|)$. (The intuition for using the `min' is provided in the paragraph immediately following step 6 of this procedure.)
\item Finally, the weight to prior for each voxel coordinate $(x,y,z)$ is given by
  \begin{equation} 
    \boldsymbol{W_v}(x,y,z) = (1+k(\min_{j}|X^j(x,y,z) - P^j(x,y,z)|))^{-1}.
  \end{equation}
\label{eq:weightsEq}
\end{enumerate}
\vspace{0.01mm}
Note that here $\boldsymbol{W_v}(x,y,z)$ represents the weight to the prior in the $(x,y,z)^{th}$ voxel. $\boldsymbol{W_v}(x,y,z)$ must be
low whenever the preliminary test reconstruction $X^j(x,y,z)$ is different from its projection $P^j(x,y,z)$ onto the prior eigenspace, for \emph{every} method $j \in \{1,...,M\}$. This is
because it is unlikely that \emph{every} algorithm would produce a significant artefact at a voxel, and hence we hypothesize that the large difference has arisen due to genuine structural changes. The parameter $k$ decides the sensitivity of the weights to the difference $|X^j(x,y,z) - P^j(x,y,z)|$ and hence it depends on the size of the new regions we want to detect.  
%It must be chosen empirically based on the reconstruction of one of the template
%volumes. 
We found that our final reconstruction results obtained by
solving Eqn.~\ref{eq:selective_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
%-------------------------------------------
\subsubsection{Motivation for the use of multiple types of eigenspaces for the computation of weights}

%-----------------------------potato data
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
\captionsetup{labelformat=empty}
        \caption{}
\label{fig:potato_test}
     \end{subfigure}
      \caption{Potato dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A1}
\end{figure}

%-----------------------------potato 2D weights
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_fbp30.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_dct30.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_wavelet30.png}
        \caption{CS-Haar}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_art30.png}
        \caption{ART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sart30.png}
        \caption{SART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sirt30.png}
        \caption{SIRT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_all_methods30.png}
        \caption{combined}
     \end{subfigure}
      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $V_{low}$) constructed using different reconstruction methods, as specified in Eq.~\ref{eq:weights}. The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}. }
\label{fig:weights_map_2Dpotato}
\end{figure}
%-----------------------------potato 2D weights
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/cs_wavelet.png}
        \caption{CS-Haar}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/art.png}
        \caption{ART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/sart.png}
        \caption{SART}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/sirt.png}
        \caption{SIRT}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/2D/weighted_pca_all_methods30.png}
        \caption{combined}
     \end{subfigure}
      \caption{(a)-(f):Different reconstructions of~\ref{fig:potato_test}. The magnitude and sharpness of the artefacts is different for each method. (g) Selective-prior method that combines weights-map information from all other methods.} 
\label{fig:reconstructions_diff_methods}
\end{figure}

The changes and new structures present in the test data will generate different artifacts for different reconstruction techniques. These artifacts would not be captured by reconstructions of the object-prior since the underlying new changes and structures may be absent in all of the previously scanned objects. We aim to let the weights be independent of the type of artifact. Hence, we use a combination of different reconstruction techniques to generate different types of eigenspaces and combine information from all of them to compute weights. To illustrate the benefit of this method, we first performed 2D reconstruction of a test slice from the potato dataset (please refer Sec.~\ref{Sec:potato} for details of the dataset) Fig.~\ref{fig:object-prior_test_potato_A1} shows the test and template slices. Fig.~\ref{fig:weights_map_2Dpotato}  shows the weights-maps generated using Eq.~\ref{eq:weightsEq} by various reconstruction methods. It can be seen that the weights are low in the region of the new change in test data. Because all the iterative methods are computationally expensive, we chose only FBP and CS-DCT for computing weights-maps for all 3D reconstructions.

%----------------------------------------Results-----------------------
\section{Results}
\label{sec:results}

The proposed methods have been validated on 2D and 3D synthetic and real tomographic data of biological and medical specimens. The results below demonstrate the advantage of the selective global prior method over the unselective method.

%\subsection{\textbf{Evaluation of selective prior-reconstruction in real 3D data}}

%-----------------------results of potato dataset

The proposed method has been validated on new\footnote {These and our code will be made available to the community.} scans of biological specimens in a longitudinal setting. These datasets in the form of \emph{raw cone-beam projection measurements} were acquired from a lab at the Australian National University (ANU). We emphasize that in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections \emph{simulated} from 3D volumes. This is because most CT scanners do not reveal the raw projections, and instead output only the full reconstructed volumes. Moreover, the process of conversion from the projections to the full volumes is proprietary. \emph{Departing from this, we demonstrate reconstruction results from raw projection data.} In all figures in this section, `unselective prior' refers to optimizing Eqn.~\ref{eq:selective_prior} with $\boldsymbol{W}(x,y,z)=1$.
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
      \caption{Potato 3D dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A}
\end{figure}

%--------potato reconstruction--------------------------------------------------
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.185\columnwidth]{../images/potato/testIm_color.png}}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
\subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm.png}}\hfill
\subcaptionbox{Unselective \\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
\caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts. The reconstructed volumes can be viewed in~\cite{supp_paper}.}
\label{fig:potato_3D_results_A}
\end{figure}
%----------------------------------------------------------
%-----------------------results of potato dataset

\subsubsection{\textbf{Potato dataset}}
\label{Sec:potato}
The first (Potato) dataset consisted of four scans of the humble potato, chosen for its simplicity (Fig.~\ref{fig:object-prior_test_potato_A}). Measurements from each scan consisted of real cone-beam projections from 900 views, each of size $150\times150$. The corresponding size of the reconstructed volume is $150\times150\times100$. While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.  Projections were obtained using circular cone beam geometry. The specimen was kept in the same position throughout the acquisitions. In cases where such an alignment is not present, all the template volumes must be pre-aligned before computing the eigenspace. The test must be registered to the object-prior after its preliminary pilot reconstruction. %Further, this alignment can be refined following every update of the reconstructed test volume.
 The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views. The test volume was reconstructed using measurements from 45 projection views, i.e. $5\%$ of the projection views from which ground truth was reconstructed.  The selected 3D
ground truth of template volumes, test volume, as well as the 3D reconstructions are shown in~\cite{supp_paper}. Fig.~\ref{fig:potato_3D_results_A} shows a slice from the reconstructed 3D volume. We observe that our method reconstructs new structures while simultaneously reducing streak artefacts.\\ %The new regions detected by different reconstruction methods are shown in Fig.~\ref{fig:weights_map_2Dpotato}. The lower intensities denote new regions which were assigned lower weights. This ensures that the new regions are reconstructed using projection measurements alone, avoiding erroneous influence of the prior.
%---------------------------------------
\begin{table}[!h]
\caption{SSIM of 3D reconstructed potato volumes from various methods. Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects. In this dataset alone, the new changes are in a homogeneous background. Hence, the FDK performs the best when the RoI alone is considered. However, it fails when the entire volume is considered due to the prominent streaky artefacts.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{CS} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + CS\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + CS\end{tabular}} \\ \hline
\textbf{red RoI}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.850       & 0.712                                                               & 0.852                                                            \\ \hline
\textbf{full volume} & 1 (ideal)                     & 0.744        & 0.817       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}
%-------------------------------------------------
\subsubsection{\textbf{Okra dataset}}
\label{Sec:okra}
In order to test on data with intricate structures, a second (Okra) dataset consisting of five scans of an okra specimen was acquired (Fig.~\ref{fig:object-prior_test_okra}). The measurements consisted of real cone-beam projections from 450 views, each of size $336\times156$. The corresponding size of the reconstructed volume is $338\times338\times123$. Prior to the first scan, two holes were drilled on the surface of the specimen. This was followed by four scans, each after introducing one new cut. The ground truth consists of FDK reconstructed volumes from the the full set of 450 view projections. The test volume was reconstructed from a partial set of 45 projections, i.e. $10\%$ of the projection views from which ground truth was reconstructed. The selected 3D ground truth of template volumes, the test volume as well as the 3D reconstructions can be seen in~\cite{supp_paper}. One of the slices of the reconstructed volumes is shown in Fig.~\ref{fig:okra_3D_results}. The red and green 3D RoI in the video and images show the regions where new changes are present. Based on the potato and the okra experiments, we see that our method is able to \emph{discover both} the presence of a new structure, as well as the absence of a structure.

%--------------------------------okra data-------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.176\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/testCropped.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:object-prior_test_okra}
\end{figure}
%----------------------------------------------------

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.185\columnwidth]{../images/okra/testCropped.png}}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
\subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
\subcaptionbox{Unselective \\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/prior_weighted_cropped.png}}
\caption{3D reconstruction of the okra from $10\%$ projection
  views (b) has strong streak artefacts, (c) blurred, (d) no new
  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
  corresponding to red and green regions) while simultaneously
  reducing streak artefacts. The reconstructed volumes can be viewed in ~\cite{supp_paper}.}
\label{fig:okra_3D_results}
\end{figure}

%--------------------------------------zoomed okra

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/input_cropped.png}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/FDK_cropped.png}}\hfill
\subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Unselective \\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/weighted_prior_cropped.png}}
\caption{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
 ).}
\label{fig:okra_zoomed_3D_results}
\end{figure}

%---------------------------------------
\begin{table}[!h]
  \caption{SSIM of 3D RoI of reconstructed okra volumes from various methods. Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{CS} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + CS\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + CS\end{tabular}} \\ \hline
\textbf{red RoI}   & 1 (ideal)                     & 0.737        & 0.836       & 0.858                                                               & \textcolor{red}{0.883}                                                                  \\ \hline
\textbf{green RoI} & 1 (ideal)                     & 0.798        & \textcolor{red}{0.861}       & 0.800                                                               & \textcolor{red}{0.861}                                                                  \\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

%-------------------------sprouts data

\begin{figure}[!h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
\captionsetup{labelformat=empty}
        \caption{}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}\\
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
        right).}
\label{fig:object-prior_test_sprouts}
\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
\subsubsection{\textbf{Sprouts dataset}}
\label{Sec:sprouts}
The third dataset consists of six scans of an in vivo
sprout specimen imaged at its various stages of growth
(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size $130\times130\times130$. In contrast to the scientific
experiment performed for the case of the okra and the potato where we
introduced man-made defects, the changes here are purely the work of
nature. %-----------------------------sprouts 3D results
\begin{figure}[!h]
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
%\captionsetup{labelformat=empty}
        \caption{CS}
     \end{subfigure}\\
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Unselective Prior}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Selective prior}
     \end{subfigure}
     \caption{3D reconstruction of sprouts from $2.5\%$ projection views
   (b, c) have poor details (d) no new information detected (the
   prior dominates as can be seen in the blue and red regions) and
   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed in ~\cite{supp_paper}.} 
\label{fig:sprouts_3D_results}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
%-------------------------------------------------------------
\begin{table}[]
\caption{SSIM of 3D RoI of reconstructed sprouts volumes from various methods. The RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{CS} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + CS\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + CS\end{tabular}} \\ \hline
\textbf{red RoI}   & 1 (ideal)                     & 0.852        & 0.843       & 0.834                                                               & \textcolor{red}{0.881}                                                                  \\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}
The ground truth consists of FDK reconstructed volumes from a set of
1800 view projections. The test volume was reconstructed from partial
set of 45 projections, i.e. $2.5\%$ of the projection views from which
ground truth was reconstructed. The selected 3D ground truth of
template volumes, test volume, as well as the 3D reconstructions are
shown in~\cite{supp_paper}. One of the slices of the
reconstructed volumes is shown in
Fig.~\ref{fig:sprouts_3D_results}. For the sake of exposition, the red region of interest (RoI) has been culled out from 7
consecutive slices in the 3D volume to indicate new structures; other
changes can be viewed in the video. Tables~\ref{table:potato_ssim},~\ref{table:okra_ssim} and \ref{table:sprouts_ssim} shows the improvement in the Structure
Similarity Index (SSIM) of the reconstructed new regions as compared
to other methods.

\subsection{\textbf{More results on CT-guided radio-frequency ablation data}}

%-------------------- RFA 2 new protocol
\begin{figure}[!h]
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
\captionsetup{labelformat=empty}       
 \caption{image-1}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_1.png}
\captionsetup{labelformat=empty}       
 \caption{image-1 recon}
    \end{subfigure}
 \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
\captionsetup{labelformat=empty}       
 \caption{image-2}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_2.png}
\captionsetup{labelformat=empty}       
 \caption{image-2 recon}
    \end{subfigure}
 \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
\captionsetup{labelformat=empty}       
 \caption{image-3}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_3.png}
\captionsetup{labelformat=empty}       
 \caption{image-3 recon}
    \end{subfigure}
 \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
\captionsetup{labelformat=empty}       
 \caption{image-4}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_4.png}
\captionsetup{labelformat=empty}       
 \caption{image-4 recon}
    \end{subfigure}
 \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
\captionsetup{labelformat=empty}       
 \caption{image-5}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_5.png}
\captionsetup{labelformat=empty}       
 \caption{image-5 recon}
    \end{subfigure}
 \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6.png}
\captionsetup{labelformat=empty}       
 \caption{image-6}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_6.png}
\captionsetup{labelformat=empty}       
 \caption{image-6 recon}
    \end{subfigure}
 \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
\captionsetup{labelformat=empty}       
 \caption{image-7}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_7.png}
\captionsetup{labelformat=empty}       
 \caption{image-7 recon}
    \end{subfigure}
 \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/testIm.png}
\captionsetup{labelformat=empty}       
 \caption{image-8}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/weighted_pca_all_methods_kk_0_01.png}
\captionsetup{labelformat=empty}       
 \caption{image-8 recon}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/weightsIm_all_methods_kk_0_01.png}
\captionsetup{labelformat=empty}       
 \caption{weights map}
    \end{subfigure}
       \caption{Reconstructions (referred as `recon') of all slices of  of Fig.~\ref{fig:RFA2_test_object-prior} using the suggested protocol in Table.~\ref{tab:realistic_imaging_protocol}. The last image is the weights map corresponding to the reconstruction of image-8. The new changes in the tumor site is picked up by the weights map. }
\label{fig:RFA2_new_protocol}
\end{figure}

Earlier in Sec.~\ref{sec:tmh}, we discussed that the imaging protocols fell under two categories depending on the final goal (tracking or observing details): very few-view imaging and moderate view imaging. \textbf{Ideally, we may prefer to gradually increase from few-view to moderate views as the probe gradually approaches the tumor site.} For the reconstruction of $n^{\textrm{th}}$ slice i.e. slice imaged at time $t=n$, the few-view reconstructions of the previously acquired slices can be used as object-prior. However, the first scan must always be taken with large number of views because it acts as a reference template to start with. Table.~\ref{tab:realistic_imaging_protocol} summarizes this protocol for the dataset of Fig~\ref{fig:RFA2_test_object-prior}, and Fig.~\ref{fig:RFA2_new_protocol} shows the reconstructions when this realistic protocol is used.

\begin{table}[!h]
  \caption{Suggested multi-step imaging protocol for the CT-guided radio-frequency ablation dataset of Fig~\ref{fig:RFA2_test_object-prior}. The number of views is gradually increased as the probe approaches the tumor site. Only the first scan is taken with large number of views to act as a reference template. The few-view reconstructions of a slice acts as the object-prior for the reconstruction of slice being imaged at next time instant.}
  \vspace{2mm}
\centering\small\setlength\tabcolsep{2pt}
\hspace*{-1cm}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{\begin{tabular}[c]{@{}c@{}}Slice being\\ imaged at\\ time t\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Probe distance from\\ tumor or \\ ablation stage\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ imaging\\ views\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Reconstruction\\ protocol: type \\ of global prior\end{tabular}} \\ \hline
Slice t=1 & Very far from tumor & 360 & CS, no prior \\ \hline
Slice t=2 & Sufficiently far from tumor & 40 & Unselective \\ \hline
Slice t=3 & Far from tumor & 50 & Unselective \\ \hline
Slice t=4 & Near tumor & 60 & Unselective \\ \hline
Slice t=5 & Sufficiently near tumor & 70 & Unselective \\ \hline
Slice t=6 & Very near tumor & 80 & Unselective \\ \hline
Slice t=7 & Very near tumor & 90 & Unselective \\ \hline
Slice t=8 & During, after ablation & 120 & Selective \\ \hline
\end{tabular}\hspace*{-1cm}
\label{tab:realistic_imaging_protocol}
\end{table}

%--------------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}
The presented unselective prior-based algorithm is suited to applications where we wish to detect the location of new changes in an object over time, and the presented selective prior-based algorithm is suited to applications where we wish to observe the intricate details of those new changes. This distinction in the techniques used has not been studied earlier in literature~\cite{geyer2015,Ali2018,Tan2017,PICCS} to the best of our knowledge. Eventhough methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored. We have presented a principled method of tackling this particular issue via our weights map. We not only estimate the location of new changes, but also compute their intensities. This information is then used to modulate the strength of the prior during the reconstruction of the test. Our results consist of 3D reconstructions from real cone-beam projections of two datasets, and both 3D and 2D reconstructions from cone-beam and parallel beam projections respectively. In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions. An in-dept analysis of each of the results in presented in Sec.~\ref{sec:results}. We now discuss the need for registration between object-prior and the test, and the effect of hyper-parameters on our reconstructions.

\subsection{Issue of misalignment between test and templates}
As with any global prior-based method, there is a need for the test volume to be registered with the object-prior. In all our longitudinal study experiments, the volumes were already aligned during imaging. However, if this were not the case, then the prior must be aligned to the test based on an initial pilot reconstruction of the test.

\subsection{Effect of hyper-parameters}
\label{subsec:k}
The parameters $\lambda_1$ and $\lambda_2$ must be chosen empirically or by cross-validation by treating one of the previously scanned objects as test. In our experiments, we had fixed $\lambda_1$ to be 1 and found that this value is nearly data-independent. The value of $\lambda_2$ largely depends on the amount of artefacts we aim to remove by using prior at the cost of their dominance in the new regions. This value was chosen to lie between $0-1$ for our datasets. Finally, the hyper-parameter $k$ defines the sensitivity of the weights map to the difference between the test image and the prior (projection of test onto the space of object-prior). When $k=0$, our method converges to the unselective prior method. As $k$ increases, the weights map starts capturing the new changes in the test, at the cost of detecting a few false positives i.e. false new changes. In other words, as the weights map becomes more sensitive to the difference between the test and object-prior, it becomes more noisy. In order to visualize the effect of the hyper-parameter $k$, we performed 2D reconstructions of okra dataset for different values of $k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map obtained for each of the $k$ values. We estimate an approximate choice for the optimal value of $k$ by treating one of the object-prior as test and reconstructing it. We also note that although the weights map is heavily influenced by $k$, the final reconstructions are stable for large variations in $k$, as seen in Fig.~\ref{fig:reconstructions_as_k_varies}. Alternatively, in cases where one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using a learning based method described in~\cite{supp_paper}.

%--------------effect of the value of $k$ on Okra dataset

\begin{figure}[h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_10normalized.png}
        \caption{k=10}
     \end{subfigure}     
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_50normalized.png}
        \caption{k=50}
     \end{subfigure} 
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_90normalized.png}
        \caption{k=90}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_130normalized.png}
        \caption{k=130}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_170normalized.png}
        \caption{k=170}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_210normalized.png}
        \caption{k=210}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_250normalized.png}
        \caption{k=250}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_290normalized.png}
        \caption{k=290}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_330normalized.png}
        \caption{k=330}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_370normalized.png}
        \caption{k=370}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_410normalized.png}
        \caption{k=410}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=1.15\textwidth]{../images/okra/2D_okra/weightsIm_450normalized_colorbar.png}
        \caption{k=450}
     \end{subfigure}
    \caption{Different weights-maps for okra reconstruction. Low intensity denotes regions of new changes in test.}
\label{fig:few_view_okra_2D_weights}
\end{figure}
\begin{figure}[h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca10_colorIm.png}
        \caption{k=10,\\ SSIM = 0.944}
     \end{subfigure}     
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca50.png}
        \caption{k=50,\\ SSIM = 0.959}
     \end{subfigure} 
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca90.png}
        \caption{k=90,\\ SSIM = 0.955}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca130.png}
        \caption{k=130,\\ SSIM = 0.948}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca170.png}
        \caption{k=170,\\ SSIM = 0.942}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca210.png}
        \caption{k=210,\\ SSIM = 0.936}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca250.png}
        \caption{k=250,\\ SSIM = 0.931}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca290.png}
        \caption{k=290,\\ SSIM = 0.926}
     \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca330.png}
        \caption{k=330,\\ SSIM = 0.922}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca370.png}
        \caption{k=370,\\ SSIM = 0.918}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca410.png}
        \caption{k=410,\\ SSIM = 0.915}
     \end{subfigure}
   \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca450.png}
        \caption{k=450,\\ SSIM = 0.911}
     \end{subfigure}
    \caption{2D reconstructions showing stable reconstructions for large variations in $k$. The SSIM values for all images are computed within the red RoI (shown in (a)), the region where the test is different from all of the previously scanned objects.}
\label{fig:reconstructions_as_k_varies}
\end{figure}

%--------------------------Conclusion-----------------------
\section{Conclusions}
\label{sec:conclusions}
This work deals with the effective use of priors for tomographic reconstruction in longitudinal studies. We show that we can either use the unselective global prior method or the selective prior method to our advantage, depending on our goal. We establish the context under which these methods can be used, as shown in Schematic~1. When we wish to approximately know the location of new changes, we apply an unselective prior because it is fast and sufficient for the task at hand. We also choose a smaller number of views in order to reduce radiation. In addition, we show that when our goal shifts to observing the details of the new changes accurately, we acquire projections from a moderate number of views in order to capture more information. We further combine this with the somewhat slower but more accurate technique of reconstruction-- the selective prior-based method. This method ensures that the reconstruction of localized new information in the data is not affected by the priors. We have thus improved the state of the art by detecting these regions of change and assigning low prior weights wherever necessary. The probability of presence of a `new region' is enhanced considerably by a novel combination of different reconstruction techniques.  We have validated our technique on medical 2D and real, biological 3D datasets for longitudinal studies. The method is also largely robust to the number of previously scanned objects used. We urge the reader to see the videos of reconstructed volumes in~\cite{supp_paper}. 
%Our method has been shown to make the best use of prior
%only when needed, thus detecting new changes of the test
%data.

\section{Acknowledgement}
We are grateful to Dr. Andrew Kingston for facilitating data collection at the  Australian National University. AR gratefully acknowledges IITB Seed-grant 14IRCCSG012, as well as NVIDIA Corporation for the generous donation of a Titan-X GPU card, which was essential for computing 3D reconstructions for the research reported here. We also thank Dr. Akshay Baheti for providing us with medical data from Tata Memorial Hospital, Mumbai. 
{%\footnotesize
\bibliography{tci_ref}}
\end{document}

### 2020-05-23 paper/tci_Mar19.tex
First commit

--- 2020-05-23 paper/tci.tex
@@
 
-\textbf{Observing details of the ablation:} Next, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e.
-a somewhat higher number of views this time.
+\textbf{Observing details of the ablation:} Next, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e., a somewhat higher number of views this time.
 Fig.~\ref{fig:RFA2_few_views} shows the reconstructions of slice 8 by different methods.
@@
 
-To begin with, when an object is scanned multiple times, a set of high quality reconstructions (i.e.
-reconstructions from a dense set of projection views) may be chosen as object-prior for the reconstruction of future scan volumes, which in turn, may be scanned using far fewer measurements.
+To begin with, when an object is scanned multiple times, a set of high quality reconstructions (i.e., reconstructions from a dense set of projection views) may be chosen as object-prior for the reconstruction of future scan volumes, which in turn, may be scanned using far fewer measurements.
 The eigenspace $E_{\text{high}}$ of the $L$ previously scanned objects $Q_1,Q_2,...,Q_L$ is pre-computed.
@@
 \end{multline}
-The reconstruction proceeds in an alternating manner, first by minimization of Eq.~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}.
+The reconstruction proceeds in an alternating manner, first by minimization of Eq~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}.
 For both these, the solver in~\cite{l1ls} is used.
@@
 Let this projection be denoted by $P^j$.
-To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e.
-are similar to the template reconstructions).
+To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e., are similar to the template reconstructions).
 The rest, i.e.
@@
   \end{equation}
-\label{eq:weightsEq}
+\label{eq:weights}
 \end{enumerate}
@@
      \end{subfigure}
-      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $V_{low}$) constructed using different reconstruction methods, as specified in Eq.~\ref{eq:weights}.
-The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
+      \caption{Weight maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $V_{low}$) constructed using different reconstruction methods, as specified in Eq.~\ref{eq:weights}.
+The weight maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
 }
@@
      \end{subfigure}
-      \caption{(a)-(f):Different reconstructions of~\ref{fig:potato_test}.
+      \caption{(a)-(g):Different reconstructions of~\ref{fig:potato_test}.
 The magnitude and sharpness of the artefacts is different for each method.
-(g) Selective-prior method that combines weights-map information from all other methods.}
+(h) Selective-prior method that combines weights-map information from all other methods.}
 \label{fig:reconstructions_diff_methods}
@@
 To illustrate the benefit of this method, we first performed 2D reconstruction of a test slice from the potato dataset (please refer Sec.~\ref{Sec:potato} for details of the dataset) Fig.~\ref{fig:object-prior_test_potato_A1} shows the test and template slices.
-Fig.~\ref{fig:weights_map_2Dpotato}  shows the weights-maps generated using Eq.~\ref{eq:weightsEq} by various reconstruction methods.
+Fig.~\ref{fig:weights_map_2Dpotato}  shows the weight maps generated using Eq~\ref{eq:weights} by various reconstruction methods.
 It can be seen that the weights are low in the region of the new change in test data.
-Because all the iterative methods are computationally expensive, we chose only FBP and CS-DCT for computing weights-maps for all 3D reconstructions.
+Because all the iterative methods are computationally expensive, we chose only FBP and CS-DCT for computing weight maps for all 3D reconstructions.
 
@@
 \label{Sec:potato}
-The first (Potato) dataset consisted of four scans of the humble potato, chosen for its simplicity (Fig.~\ref{fig:object-prior_test_potato_A}).
+The first (Potato) dataset consisted of four scans of the humble potato, chosen for its simplicity (Figs.~\ref{fig:object-prior_test_potato_A}).
 Measurements from each scan consisted of real cone-beam projections from 900 views, each of size $150\times150$.
@@
  The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views.
-The test volume was reconstructed using measurements from 45 projection views, i.e.
-$5\%$ of the projection views from which ground truth was reconstructed.
+The test volume was reconstructed using measurements from 45 projection views, i.e, $5\%$ of the projection views from which ground truth was reconstructed.
 The selected 3D
@@
 \label{Sec:okra}
-In order to test on data with intricate structures, a second (Okra) dataset consisting of five scans of an okra specimen was acquired (Fig.~\ref{fig:object-prior_test_okra}).
+In order to test on data with intricate structures, a \textbf{second (Okra) dataset} consisting of five scans of an okra specimen was acquired (Fig.~\ref{fig:object-prior_test_okra}).
 The measurements consisted of real cone-beam projections from 450 views, each of size $336\times156$.
@@
 The ground truth consists of FDK reconstructed volumes from the the full set of 450 view projections.
-The test volume was reconstructed from a partial set of 45 projections, i.e.
-$10\%$ of the projection views from which ground truth was reconstructed.
+The test volume was reconstructed from a partial set of 45 projections, i.e, $10\%$ of the projection views from which ground truth was reconstructed.
 The selected 3D ground truth of template volumes, the test volume as well as the 3D reconstructions can be seen in~\cite{supp_paper}.
@@
         \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
-%\captionsetup{labelformat=empty}
+\captionsetup{labelformat=empty}
         \caption{Test}
@@
         \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
-%\captionsetup{labelformat=empty}
+\captionsetup{labelformat=empty}
         \caption{FDK}
@@
         \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
-%\captionsetup{labelformat=empty}
+\captionsetup{labelformat=empty}
         \caption{CS}
@@
         \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
-%\captionsetup{labelformat=empty}
+\captionsetup{labelformat=empty}
         \caption{Unselective Prior}
@@
         \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
-%\captionsetup{labelformat=empty}
+\captionsetup{labelformat=empty}
         \caption{Selective prior}
@@
 1800 view projections. The test volume was reconstructed from partial
-set of 45 projections, i.e. $2.5\%$ of the projection views from which
+set of 45 projections, i.e, $2.5\%$ of the projection views from which
 ground truth was reconstructed. The selected 3D ground truth of
@@
        \caption{Reconstructions (referred as `recon') of all slices of  of Fig.~\ref{fig:RFA2_test_object-prior} using the suggested protocol in Table.~\ref{tab:realistic_imaging_protocol}.
-The last image is the weights map corresponding to the reconstruction of image-8.
+The last image is the weights map corresponding to the reconstruction of slice-8.
 The new changes in the tumor site is picked up by the weights map.
@@
 Earlier in Sec.~\ref{sec:tmh}, we discussed that the imaging protocols fell under two categories depending on the final goal (tracking or observing details): very few-view imaging and moderate view imaging.
-\textbf{Ideally, we may prefer to gradually increase from few-view to moderate views as the probe gradually approaches the tumor site.} For the reconstruction of $n^{\textrm{th}}$ slice i.e.
-slice imaged at time $t=n$, the few-view reconstructions of the previously acquired slices can be used as object-prior.
+\textbf{Ideally, we may prefer to gradually increase from few-view to moderate views as the probe gradually approaches the tumor site.} For the reconstruction of $n^{\textrm{th}}$ slice i.e., slice imaged at time $t=n$, the few-view reconstructions of the previously acquired slices can be used as object-prior.
 However, the first scan must always be taken with large number of views because it acts as a reference template to start with.
@@
 Our results consist of 3D reconstructions from real cone-beam projections of two datasets, and both 3D and 2D reconstructions from cone-beam and parallel beam projections respectively.
-In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
+In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009}(FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
 An in-dept analysis of each of the results in presented in Sec.~\ref{sec:results}.
@@
 When $k=0$, our method converges to the unselective prior method.
-As $k$ increases, the weights map starts capturing the new changes in the test, at the cost of detecting a few false positives i.e.
-false new changes.
+As $k$ increases, the weights map starts capturing the new changes in the test, at the cost of detecting a few false positives i.e., false new changes.
 In other words, as the weights map becomes more sensitive to the difference between the test and object-prior, it becomes more noisy.
@@
      \end{subfigure}
-    \caption{Different weights-maps for okra reconstruction. Low intensity denotes regions of new changes in test.}
+    \caption{Different weight maps for okra reconstruction. Low intensity denotes regions of new changes in test.}
 \label{fig:few_view_okra_2D_weights}
@@
 \section{Acknowledgement}
-We are grateful to Dr.
-Andrew Kingston for facilitating data collection at the  Australian National University.
+We are grateful to Dr.Andrew Kingston for facilitating data collection at the  Australian National University.
 AR gratefully acknowledges IITB Seed-grant 14IRCCSG012, as well as NVIDIA Corporation for the generous donation of a Titan-X GPU card, which was essential for computing 3D reconstructions for the research reported here.

### 2020-05-25 paper/tci.tex
Corrected typos pointed by R2

@@
 Fig.~\ref{fig:diff_methods} shows the advantage of combining the global prior with CS.
-\subsection{Contributions}
+\subsection{\textbf{Contributions}}
 \label{sec:contributions}
@@
 In this context, we demonstrate the combined use of CS with the global prior, in two flavors: the vanilla (unselective) and selective global prior-based reconstruction.
-The choice of the number of measurement views and the type of reconstruction- unselective or selective, is driven by the goal of the procedure.
+The choice of the number of measurement views and the type of reconstruction - unselective or selective, is driven by the goal of the procedure.
 
@@
 We found that our final reconstruction results obtained by
-solving Eqn.~\ref{eq:selective_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
+solving Eq.~\ref{eq:selective_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
 %-------------------------------------------
-\subsubsection{Motivation for the use of multiple types of eigenspaces for the computation of weights}
+\subsubsection{\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights}}
 
@@
      \end{subfigure}
-      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $V_{low}$) constructed using different reconstruction methods, as specified in Eq.~\ref{eq:weights}.
+      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $V_{low}$) constructed using different reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}.
 The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
@@
 
-The proposed methods have been validated on 2D and 3D synthetic and real tomographic data of biological and medical specimens.
+The proposed method has been validated on 2D and 3D synthetic and real tomographic data of biological and medical specimens.
 The results below demonstrate the advantage of the selective global prior method over the unselective method.
@@
 Moreover, the process of conversion from the projections to the full volumes is proprietary.
-\emph{Departing from this, we demonstrate reconstruction results from raw projection data.} In all figures in this section, `unselective prior' refers to optimizing Eqn.~\ref{eq:selective_prior} with $\boldsymbol{W}(x,y,z)=1$.
+\emph{Departing from this, we demonstrate reconstruction results from raw projection data.} In all figures in this section, `unselective prior' refers to optimizing Eq.~\ref{eq:selective_prior} with $\boldsymbol{W}(x,y,z)=1$.
 \begin{figure}[!h]
@@
 \subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm.png}}\hfill
-\subcaptionbox{Unselective \\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
+\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
 \subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
@@
 \subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
-\subcaptionbox{Unselective \\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
 \subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/prior_weighted_cropped.png}}
@@
 \subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Unselective \\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
 \subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/weighted_prior_cropped.png}}
@@
 consecutive slices in the 3D volume to indicate new structures; other
-changes can be viewed in the video. Tables~\ref{table:potato_ssim},~\ref{table:okra_ssim} and \ref{table:sprouts_ssim} shows the improvement in the Structure
+changes can be viewed in the video. Tables~\ref{table:potato_ssim},~\ref{table:okra_ssim} and \ref{table:sprouts_ssim} show the improvement in the Structure
 Similarity Index (SSIM) of the reconstructed new regions as compared
@@
 The presented unselective prior-based algorithm is suited to applications where we wish to detect the location of new changes in an object over time, and the presented selective prior-based algorithm is suited to applications where we wish to observe the intricate details of those new changes.
-This distinction in the techniques used has not been studied earlier in literature~\cite{geyer2015,Ali2018,Tan2017,PICCS} to the best of our knowledge.
+This distinction in the techniques used has not been studied earlier in literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our knowledge.
 Eventhough methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
@@
 In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
-An in-dept analysis of each of the results in presented in Sec.~\ref{sec:results}.
+An in-depth analysis of each of the results is presented in Sec.~\ref{sec:results}.
 We now discuss the need for registration between object-prior and the test, and the effect of hyper-parameters on our reconstructions.

### 2020-05-25 paper/tci.tex
Completed round-1 of changes pointed by R1

@@
 Before diving into the details of the unselective and the selective global prior methods, we first show how both the techniques can be applied to our advantage in a real-life medical longitudinal study.
-Our data~\footnote{Source: Tata Memorial Centre~\cite{tmh}, Parel, Mumbai.
-This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of CT scans from a longitudinal study.
+Longitudinal studies, in general, refer to the process of taking multiple CT scans of an object over specific intervals of time in order to study the evolution of the changes taking place in its interior.
+Here, our data~\footnote{Source: Tata Memorial Centre~\cite{tmh}, Parel, Mumbai.
+This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of CT scans from one such medical procedure.
 This involves successive scans of the liver taken during a radio-frequency ablation procedure described in the previous section.
@@
 {\bf Schematic 1}: Motivation behind our algorithm. (The plus $\oplus$ and the
-minus $\ominus$ operators are placeholders; precise details available
+minus $\ominus$ operators denote set-union and set-difference respectively; precise details available
 in Section~\ref{sec:thealgo}). 
@@
 \item  Compute pilot reconstruction of $\boldsymbol{x}$.
-Let this be called $X$.\\ \textcolor{blue}{$X = O \oplus N \oplus Ar(O) \oplus Ar(N)$}, where \\ \textcolor{blue}{$Ar(O)$} denote the reconstruction artefacts that depend on the old regions, the imaging geometry and the reconstruction method, and\\
- \textcolor{blue}{$Ar(N)$} denote the reconstruction artefacts that depend on the new regions, imaging geometry and the reconstruction method.
+Let this be called $X$.\\ \textcolor{blue}{$X = O \oplus N \oplus Ar(O) \oplus Ar(N)$}, where \\ \textcolor{blue}{$Ar(O)$} denote the reconstruction artefacts that depend on the \textit{old} regions, the imaging geometry and the reconstruction method, and\\
+ \textcolor{blue}{$Ar(N)$} denote the reconstruction artefacts that depend on the \textit{new} regions, imaging geometry and the reconstruction method.
 \item  Note that \textcolor{blue}{$Q \ominus X = N \oplus Ar(O) \oplus Ar(N)$} gives the new regions, but along with lots of artefacts due to the imaging geometry (sparse views).
@@
 \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
-\subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm.png}}\hfill
+\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm.png}}\hfill
 \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
@@
 \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
-\subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
+\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
 \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
@@
 \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/FDK_cropped.png}}\hfill
-\subcaptionbox{CS, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/CS_cropped.png}}\hfill
 \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
@@
 \end{figure}
-%-------------------------------------------------------------
+
+%--------------------------------------zoomed sprouts
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_cropped.png}}\hfill
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_cropped.png}}\hfill
+\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_cropped.png}}\hfill
+\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_cropped.png}}
+\caption{Zoomed-in portion $(16 \times 21)$ corresponding to the red RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods (b) unclear, (c) unclear, (d) only two strong structures seen and (e) there is a hint of a third structure too (as seen in the test RoI).}
+\label{fig:sprouts_zoomed_3D_results}
+\end{figure}
+
+%--------------------------------------------------------------
 \begin{table}[]
@@
 shown in~\cite{supp_paper}. One of the slices of the
-reconstructed volumes is shown in
-Fig.~\ref{fig:sprouts_3D_results}. For the sake of exposition, the red region of interest (RoI) has been culled out from 7
+reconstructed volumes and its zoomed-in RoI are shown in
+Figs.~\ref{fig:sprouts_3D_results} and ~\ref{fig:sprouts_zoomed_3D_results} respectively. For the sake of exposition, the red region of interest (RoI) has been culled out from 7
 consecutive slices in the 3D volume to indicate new structures; other
@@
 \textbf{\begin{tabular}[c]{@{}c@{}}Slice being\\ imaged at\\ time t\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Probe distance from\\ tumor or \\ ablation stage\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ imaging\\ views\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Reconstruction\\ protocol: type \\ of global prior\end{tabular}} \\ \hline
-Slice t=1 & Very far from tumor & 360 & CS, no prior \\ \hline
+Slice t=1 & Very far from tumor & 360 & CS \\ \hline
 Slice t=2 & Sufficiently far from tumor & 40 & Unselective \\ \hline

### 2020-05-29 paper/supplementary.tex
Added supplementary material and images, moved patch-based techniques to supplementary, removed schematic 1.

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Supplemental material for `Eliminating prior-bias from sparse-projection
tomographic reconstructions'}
\begin{document}
\maketitle
This supplementary material consists of details of the optimization routine used in our method, links to view our 3D reconstructions and results of 2D reconstructions for different projection views.

\tableofcontents
\newpage
\section{\textbf{Patch-based techniques}}
\label{sec:patch_based}
Here we present a comparison~\cite{my_dicta_paper} of the performance of the aforementioned PCA-based global prior with a prior that is based on construction of patch-wise dictionaries. In both cases, the reconstruction routine is based on typical CS techniques. The well-known K-SVD algorithm \cite{Aharon2006} was chosen for construction of patch-based dictionaries. For this, patches were extracted from each of the template volumes, from which an overcomplete dictionary was obtained. The basic aim of the K-SVD algorithm (or any overcomplete dictionary learning technique) is the compact linear representation of all these patches using the dictionary columns. Let $\boldsymbol{D}$ denote the dictionary learned, $N_p$ the total number of patches, and $\boldsymbol{H_i}$ the operator to extract the $i^{\textrm{th}}$ patch from the intermediate reconstructed slice/volume. Then, once $\boldsymbol{D}$ is computed in an earlier `training phase', each new test slice (or test volume) can be reconstructed by optimizing a cost function such as the one below:
\begin{multline}
J_2(\boldsymbol{\theta},\{\boldsymbol{\alpha_i}\}_{i=1}^{N_p}) = \lVert\boldsymbol{\mathcal{R}\Upsilon\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \\ \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\lVert \boldsymbol{H_i\Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2 +\frac{\lambda_3}{ N_p}\sum_{i=1}^{N_p}\lVert\boldsymbol{\alpha_i}\rVert_1.
\label{Eq:main_patchBased}
\end{multline}
The reconstruction proceeds in an alternating manner, first by minimization of Eq.~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}. For both these, the solver in~\cite{l1ls} is used. For the former case, the cost function reduces to:
\begin{equation}
J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = \lVert \boldsymbol{\mathcal{R} \Upsilon \theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\rVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2.
\label{Eq:primaryObj_patchBased}
\end{equation}
For each $i \in \{1,...,N_p\}$, the cost function reduces to:
\begin{equation}
J_{\boldsymbol{\theta}}(\boldsymbol{\alpha}_i) =  \lVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D\alpha_i}\rVert_2^2  + \frac{\lambda_3}{\lambda_2}\lVert\boldsymbol{\alpha_i}\rVert_1.
\label{Eq:alpha_patchBased}
\end{equation}
This summarizes the comparison with patch-based methods.
%--------------------------------------------------------------------------
\section{An alternate method to compute weights-map}
The problem of recovering the unknown data $\boldsymbol{x}$ from its measurements falls under the broad category of inverse problems. In almost all such cases, the measurement model is known. However, a direct analytical inverse solution does not exist in most cases because of the enormous size of the matrix modelling the measurement process. The complexity is further increased when insufficient number of measurements are taken leading to an ill-posed problem. In such circumstances, iterative schemes are used to solve for $\boldsymbol{x}$ by minimizing a cost function.

A simple cost function $E_\text{model}$ would minimise any difference between the measurements of the data and the imaging model:

\begin{equation}
E_\text{model} = \lVert\boldsymbol{\Phi x- y}\rVert_2^2.
\end{equation}
where $\boldsymbol{y}$ denotes the acquired measurements of $\boldsymbol{x}$ under an imaging model $\boldsymbol{\Phi}$. In our 3D reconstructions, $\boldsymbol{\Phi}$ denotes cone-beam projection model. In the case of sparse measurements (measurements from significantly few projection views), some known information of the underlying unknown data is imposed in order to get its better estimate. The Compressive Sensing is one such method that exploits the fact that most naturally occurring data are sparse under some mathematical transform. The cost function is now given by

\begin{equation}
E_\text{CS} = \lVert\boldsymbol{\Phi x- y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
\end{equation}
Here $\boldsymbol{\theta}$ are the unknown sparse coefficients of $\boldsymbol{x}$. In order to further improve the reconstruction, we can use information available from the scans of similar volumes in the past. Such methods are known as `\emph{prior}-based methods'.

For our reconstruction, the cost function $E$ includes a third term enforcing weighted similarity between the reconstructed volume and pre-computed prior.

\begin{equation}
  E(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\Phi x- y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{i}\boldsymbol{V_i}\alpha_i))\rVert_2^2
\label{eq:weighted_prior}
\end{equation}
\newpage

\textbf{Building the prior:}\\

We now describe the method used to build the prior. We begin with, it is assumed that the test volume can be expressed as a compact linear combination of the principal components extracted from a set of similar volumes (called here as `object-prior'). Hence, the prior is built using Principal Component Analysis (PCA), which has been a widely used technique to represent data in terms of its significant modes or directions of variation. \\

First, a set of representative 3D volumes is chosen as object-prior. These volumes must represent a wide range in anatomy, in order to contribute to an eigenspace that can encompass a range of possible test slice anatomy. If these volumes are not aligned, then they must be first registered before computing the prior. The prior is built by computing the covariance matrix $C$ from the template set $\{Q_i\}$, as shown in Eq.~\ref{eq:PCA}, The space spanned by the eigenvectors $\boldsymbol{\{V_i\}}$ (eigenspace) of the covariance matrix is the global prior and is assumed to contain any test slice that is similar, but not necessarily identical to the object-prior. The covariance matrix is given by:
 \begin{equation}
\begin{split}
  C  & = \frac{1}{N-1}\sum_{i=1}^N(Q_i - \mu)(Q_i - \mu)^{T}\\
\end{split}
\label{eq:PCA}
\end{equation}
where $\mu$ denotes the mean of all previously scanned volumes $\{Q_i\}$ and $L$ denotes the number of previously scanned volumes chosen. The eigenvalue decomposition of $C$ will give $L$ orthogonal eigen vectors. We use all of the $L$ eigenvectors as a basis to represent the unknown test volume.  \\

\textbf{Minimizing the Cost function}\\

We minimize the cost specified in Eqn.~\ref{eq:weighted_prior} by alternately solving for $\boldsymbol{\alpha}$ and $\boldsymbol{\theta}$

\begin{equation}
E_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = ||\Phi\Psi\boldsymbol{\theta}- y||_2^2  + \lambda_1||\boldsymbol{\theta}||_1+\lambda_2||\Psi\boldsymbol{\theta} - (\mu + \sum_{i}V_i\alpha_i)||_2^2
\label{Eq:primaryObj}
\end{equation}
\begin{equation}
E_{\boldsymbol\theta}(\boldsymbol{\alpha}) = ||\Psi\boldsymbol{\theta} - (\mu + \sum_{i}V_i\alpha_i)||_2^2
\label{Eq:alpha1}
\end{equation}
Eq.~\ref{Eq:alpha1} leads to the following closed form update for $\alpha$:
\begin{equation}
\boldsymbol{\alpha} = \boldsymbol{V}^T(\Psi\boldsymbol{\theta} - \mu)
\label{Eq:alpha}
\end{equation}
An optimal value of $\lambda_2$ is empirically chosen \textit{a priori}, based on the reconstructions of one of the template slices.

%--------------------------------Links to videos-------------------------------------------------
\newpage
\section{Links to view our 3D reconstructions}

Please refer to the following videos to view the 3D datasets and reconstruction results referred in our paper:

\begin{itemize}
\item \textbf{Okra groundtruth:} \\ \url{https://www.dropbox.com/s/gn3fk3ev7s7tup0/GroundTruth.mp4?dl=0}\\
	The first four images correspond to the four template volumes and the last (right-most) image corresponds to the test volume.
\item \textbf{Okra 3D reconstruction results:} \\ \url{https://www.dropbox.com/s/o7vga1kjzcayjmt/Reconstruction.mp4?dl=0}\\
       The order of images from left to right correspond to the test volume, FDK reconstruction, CS reconstruction, unselective prior + CS reconstruction, and our reconstruction. 
\item \textbf{Potato groundtruth:} \\ \url{https://www.dropbox.com/s/whwu3th4ozr96k1/GroundTruth.mp4?dl=0}\\
	The first three images correspond to the three template volumes and the last (right-most) image corresponds to the test volume.
\item \textbf{Potato 3D reconstruction results:}\\  \url{https://www.dropbox.com/s/k41qg1kwrry9rwp/Reconstruction.mp4?dl=0}\\
       The order of images from left to right correspond to the test volume, FDK reconstruction, CS reconstruction, unselective prior + CS reconstruction, and our reconstruction.
\item \textbf{Sprouts groundtruth:} \\ \url{https://www.dropbox.com/s/0d7jbojscbx4ciz/GroundTruth.mp4?dl=0}\\
	The first five images correspond to the five template volumes and the last (right-most) image corresponds to the test volume.
\item \textbf{Sprouts 3D reconstruction results:}\\  \url{https://www.dropbox.com/s/o3jmsa4dwtd8a6l/Reconstruction.mp4?dl=0}\\
       The order of images from left to right correspond to the test volume, FDK reconstruction, CS reconstruction, unselective prior + CS reconstruction, and our reconstruction.

\end{itemize}

\newpage
\section{2D reconstruction results on colon CT dataset}

\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/template1.png}
        \caption{template 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/template2.png}
        \caption{template 2}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/template3.png}
        \caption{template 3}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/template4.png}
        \caption{template 4}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/template5.png}
        \caption{template 5}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/testIm.png}
        \caption{test image}
     \end{subfigure}
      \caption{2D object-prior (referred to as `templates' here)  and test slice of colon CT dataset. The region in red shows the synthetic new region added to the test slice.}
\label{fig:joint}
\end{figure}

%--------------------------------2D Colon results----------------------------

\newpage
\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/testIm.png}
        \caption{Test image}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/plain_pca.png}
        \caption{unselective prior+cs}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/weighted_pca5.png}
       \caption{our method}
     \end{subfigure}
      \caption{Reconstruction of colon CT: (b) has many streak artefacts (c) slightly blurred (d) Inaccurate reconstruction of new region (corresponding to the red RoI) (d) new region accurately detected while simultaneously removing streak artefacts.}
\label{fig:joint}
\end{figure}

%-----------------------------Sprouts : data--------------------------
\newpage
\section{2D reconstruction for different projection views}

\textbf{2D Sprouts dataset}

\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template1.png}
        \caption{template 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template2.png}
        \caption{template 2}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template3.png}
        \caption{template 3}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template4.png}
        \caption{template 4}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template5.png}
        \caption{template 5}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
        \caption{test image}
     \end{subfigure}
      \caption{Sprouts data: CT of different stages of sprouts growing in a jar. The templates refer to previously scanned volumes that form the `object-prior'.}
\label{fig:joint}
\end{figure}

%-----------------------------Sprouts (19 angles)--------------------------
\newpage
\subsection{Reconstruction from 19 projection views}
\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
        \caption{Test image}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/cs_wavelet.png}
        \caption{CS-wavelet}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/plain_pca.png}
        \caption{unselective prior+cs}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/weighted_pca5.png}
       \caption{our method}
     \end{subfigure}
      \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $10\%$ sampling (19 projection views).}
\label{fig:joint}
\end{figure}

%-----------------------------Sprouts (66 angles)--------------------------
\newpage
\subsection{Reconstruction from 66 projection views}
\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
        \caption{Test image}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/cs_wavelet.png}
        \caption{CS-wavelet}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/plain_pca.png}
        \caption{unselective prior+cs}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/weighted_pca5.png}
        \caption{our method}
     \end{subfigure}
     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $30\%$ sampling (55 projection views).} 
\label{fig:joint}
\end{figure}

%-----------------------------Sprouts (110 angles)--------------------------
\newpage
\subsection{Reconstruction from 110 projection views}
\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
        \caption{Test image}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/cs_wavelet.png}
        \caption{CS-wavelet}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/plain_pca.png}
        \caption{unselective prior}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/weighted_pca5.png}
        \caption{our method}
     \end{subfigure}
     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $50\%$ sampling (92 projection views).} 
\label{fig:joint}
\end{figure}

%-----------------------------Sprouts (154 angles)--------------------------
\newpage
\subsection{Reconstruction from 154 projection views}
\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
        \caption{Test image}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_wavelet.png}
        \caption{CS-wavelet}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/plain_pca.png}
        \caption{prior unselective+cs}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/weighted_pca5.png}
        \caption{our method}
     \end{subfigure}
     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $83\%$ sampling (154 projection views).} 
\label{fig:joint}
\end{figure}
----------------------------------------------------------------------------------------------------------------------------------
\bibliography{tci_ref}
\end{document}

### 2020-05-29 paper/tci.tex
converted from dos to unix format
Added a small change ("--")
Added supplementary material and images, moved patch-based techniques to supplementary, removed schematic 1.

@@
  \vspace{2mm}
-\subsubsection{\textbf{Patch-based techniques}}
-\label{sec:patch_based}
-Next we present a comparison~\cite{my_dicta_paper} of the performance of the aforementioned PCA-based global prior with a prior that is based on construction of patch-wise dictionaries.
-In both cases, the reconstruction routine is based on typical CS techniques.
-The well-known K-SVD algorithm \cite{Aharon2006} was chosen for construction of patch-based dictionaries.
-For this, patches were extracted from each of the template volumes, from which an overcomplete dictionary was obtained.
-The basic aim of the K-SVD algorithm (or any overcomplete dictionary learning technique) is the compact linear representation of all these patches using the dictionary columns.
-Let $\boldsymbol{D}$ denote the dictionary learned, $N_p$ the total number of patches, and $\boldsymbol{H_i}$ the operator to extract the $i^{\textrm{th}}$ patch from the intermediate reconstructed slice/volume.
-Then, once $\boldsymbol{D}$ is computed in an earlier `training phase', each new test slice (or test volume) can be reconstructed by optimizing a cost function such as the one below:
-\begin{multline}
-J_2(\boldsymbol{\theta},\{\boldsymbol{\alpha_i}\}_{i=1}^{N_p}) = \lVert\boldsymbol{\mathcal{R}\Upsilon\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \\ \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\lVert \boldsymbol{H_i\Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2 +\frac{\lambda_3}{ N_p}\sum_{i=1}^{N_p}\lVert\boldsymbol{\alpha_i}\rVert_1.
-\label{Eq:main_patchBased}
-\end{multline}
-The reconstruction proceeds in an alternating manner, first by minimization of Eq.~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}.
-For both these, the solver in~\cite{l1ls} is used.
-For the former case, the cost function reduces to:
-\begin{equation}
-J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = \lVert \boldsymbol{\mathcal{R} \Upsilon \theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\rVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2.
-\label{Eq:primaryObj_patchBased}
-\end{equation}
-For each $i \in \{1,...,N_p\}$, the cost function reduces to:
-\begin{equation}
-J_{\boldsymbol{\theta}}(\boldsymbol{\alpha}_i) =  \lVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D\alpha_i}\rVert_2^2  + \frac{\lambda_3}{\lambda_2}\lVert\boldsymbol{\alpha_i}\rVert_1.
-\label{Eq:alpha_patchBased}
-\end{equation}
-This summarizes the comparison with patch-based methods.
-%----------------------------------------------------
 
@@
 \label{sec:selective_prior}
-\vspace{1mm}
-\noindent \begin{boxedminipage}{0.5\textwidth} 
-{\bf Schematic 1}: Motivation behind our algorithm. (The plus $\oplus$ and the
-minus $\ominus$ operators denote set-union and set-difference respectively; precise details available
-in Section~\ref{sec:thealgo}). 
-%\vspace{0.2cm}
-
-{\small
- Let \textcolor{blue}{prior $Q:=$ old regions ($O$)}\\
- Let \textcolor{blue}{test volume $\boldsymbol{x}:=$ old regions ($O$) $\oplus$ new regions ($N$)}\\
-% \textbf{Steps:}     
-    \begin{enumerate}
-\item  Compute pilot reconstruction of $\boldsymbol{x}$.
-Let this be called $X$.\\ \textcolor{blue}{$X = O \oplus N \oplus Ar(O) \oplus Ar(N)$}, where \\ \textcolor{blue}{$Ar(O)$} denote the reconstruction artefacts that depend on the \textit{old} regions, the imaging geometry and the reconstruction method, and\\
- \textcolor{blue}{$Ar(N)$} denote the reconstruction artefacts that depend on the \textit{new} regions, imaging geometry and the reconstruction method.
-\item  Note that \textcolor{blue}{$Q \ominus X = N \oplus Ar(O) \oplus Ar(N)$} gives the new regions, but along with lots of artefacts due to the imaging geometry (sparse views).
-To eliminate these unwanted artefacts, compute \textcolor{blue}{$Y = Q \oplus Ar(O)$} by simulating projections from $Q$ using the same imaging geometry used to scan $\boldsymbol{x}$, and then reconstructing a lower quality prior volume $Y$.
-    \item Note that \textcolor{blue}{$Y \ominus X = N \oplus Ar(N)$} contains the artefacts due to the new regions only.
-These are different for different reconstruction methods.
-To eliminate these method dependent artefacts, compute $Y$ and $X$ using different reconstruction methods.
-Let these be denoted by $Y^j$ and $X^j$ respectively.
-    \item Compute
-\vspace{-0.2cm}
-           \textcolor{blue}{\begin{equation*}
-            Y^1 \ominus X^1 = N \oplus Ar^1(N)
-           \end{equation*}
-\vspace{-0.5cm}
-           \begin{equation*}
-            Y^2 \ominus X^2 = N \oplus Ar^2(N)
-           \end{equation*}}
-\vspace{-0.4cm}
-   \item  New regions are obtained by computing
-\vspace{-0.2cm}
-          \textcolor{blue}{\begin{equation*}
-          (Y^1 \ominus X^1)\cap(Y^2 \ominus X^2)= N
-          \end{equation*}}   
-\vspace{-0.5cm}
-    \item Finally, assign space-varying weights $\boldsymbol{W}$ based on step $5$.
-    \end{enumerate}
-\label{algo:newRegionDetection}
-}
-\end{boxedminipage}
-%--------------------------------------------------
-\\
 
@@
 Since the test volume (referred to as $\boldsymbol{x}$) is unknown to begin with, it is not possible to decipher the precise regions in $\boldsymbol{x}$ that are different from all the previously scanned objects (`object-prior').
-We refer the reader to Schematic 1 that describes the evolution of the procedure used to detect the new regions in the unknown volume.
 We start with $X^{\text{fdk}}$, the initial backprojection reconstruction of the test volume using the Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} in an attempt to discover the difference between the object-prior and the test volume.
@@
 \item Compute low quality template volumes $Y^\text{fdk}$. 
-In Schematic 1, for ease of exposition, we assumed a single
-template. In the sequel, we assume $L$ previously scanned objects from which we build
+We assume $L$ previously scanned objects from which we build
 an eigenspace. 
@@
 We show that we can either use the unselective global prior method or the selective prior method to our advantage, depending on our goal.
-We establish the context under which these methods can be used, as shown in Schematic~1.
+We establish the context under which these methods can be used, as outlined in Fig.~\ref{fig:prior_overview}.
 When we wish to approximately know the location of new changes, we apply an unselective prior because it is fast and sufficient for the task at hand.

### 2020-06-02 paper/tci.tex
added SSIM table for Fig.8 (2D reconstruction of potato)

@@
 In this context, we demonstrate the combined use of CS with the global prior, in two flavors: the vanilla (unselective) and selective global prior-based reconstruction.
-The choice of the number of measurement views and the type of reconstruction - unselective or selective, is driven by the goal of the procedure.
+The choice of the number of measurement views and the type of reconstruction -- unselective or selective, is driven by the goal of the procedure.
 
@@
 The magnitude and sharpness of the artefacts is different for each method.
-(g) Selective-prior method that combines weights-map information from all other methods.}
+(g) Selective-prior method that combines weights-map information from all other methods.
+The SSIM of these reconstructions is shown in Table.~\ref{table:potato_2D_ssim}.}
 \label{fig:reconstructions_diff_methods}
@@
 Because all the iterative methods are computationally expensive, we chose only FBP and CS-DCT for computing weights-maps for all 3D reconstructions.
+%---------------------------------------
+\begin{table}[!h]
+\caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g).
+The SSIM of the ground-truth (ideal reconstruction) is 1, and these are computed within the red RoI of the test image shown in Fig.~\ref{fig:potato_test}.}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\hline
+ Fig.~\ref{fig:reconstructions_diff_methods}  & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} \\\hline
+\textbf{red RoI}  & 0.502 & 0.597  & 0.453 & 0.474 & 0.565 & 0.523 & \textcolor{red}{0.759} \\ \hline
+\end{tabular}
+\label{table:potato_2D_ssim}
+\end{table}
+%-------------------------------------------------
 

### 2020-06-03 paper/tci.tex
edited definition of longitudinal studies + minor typo

@@
 These prior-based techniques use information from previously scanned data (`object-prior') of the same object or a similar one, and utilize it to reconstruct new volumes from very few sets of additional measurements.
-However, the above methods have the following two limitations: (1) the prior information may potentially overwhelm the essential details that appear in the test, (2) there is the key issue of choice of \textit{a} particular previously scanned object among the many previously acquired scans.
+However, the above methods have the following two limitations: (1) the prior information may potentially overwhelm the essential details that appear in the test, (2) there is the key issue of choice of \textit{a particular} previously scanned object among the many previously acquired scans.
 A large part of this paper is dedicated to alleviating the former limitation, which is an important issue that has so far been overlooked in the literature on tomography.
@@
 Before diving into the details of the unselective and the selective global prior methods, we first show how both the techniques can be applied to our advantage in a real-life medical longitudinal study.
-Longitudinal studies, in general, refer to the process of taking multiple CT scans of an object over specific intervals of time in order to study the evolution of the changes taking place in its interior.
+Longitudinal studies here refers to the acquisition of sequential CT scans of the same subject to track time-evolving changes within the subject's interior.
 Here, our data~\footnote{Source: Tata Memorial Centre~\cite{tmh}, Parel, Mumbai.
-This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of CT scans from one such medical procedure.
-This involves successive scans of the liver taken during a radio-frequency ablation procedure described in the previous section.
+This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of successive scans of the liver taken during a radio-frequency ablation procedure described in the previous section.
 In such a procedure, the physician inserts a thin needle-like probe into the organ~\cite{rfa}.

### 2020-06-05 paper/tci.tex
retracted statement on CS; replaced "cs" by "l1-ls" in most places.

@@
 \usepackage{boxedminipage}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
+%\usepackage{algpseudocode}
+%\usepackage{algorithm}
 \usepackage{xcolor}
@@
 However, in the last decade, reconstruction from sub-Nyquist sampled data has been made possible due to methods such as the widely used Compressed Sensing (CS) technique~\cite{Donoho,introCS}, which assumes the data to exhibit properties such as sparsity of the underlying image under certain mathematical transforms such as the Discrete Cosine Transform (DCT) or wavelet transforms.
-Fig.~\ref{fig:diff_methods} shows that although CS removes the artefacts created due to sub-sampling, its reconstruction is blurred.
-When prior information about the data is used along with CS, the reconstruction improves significantly.
+Among the many optimizers used in CS, we used the l1-regularized least squares (l1-ls) form and observed that although this optimizer removes most of the artefacts created due to sub-sampling, its reconstruction is blurred when the number of views is very limited, as shown in Fig.~\ref{fig:diff_methods}.
+Specifically, the reconstruction in Fig.~\ref{fig:humerus_cs} is obtained by minimizing the following cost using the solver in~\cite{l1ls}:
+ \begin{equation}
+J_{CS}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
+\label{Eq:simple_cs}
+\end{equation}
+Here, $\boldsymbol{x} = \boldsymbol{\Upsilon\theta}$ denotes the reconstructed volume, $\boldsymbol{y}$ its measured tomographic projections, $\boldsymbol{\mathcal{R}}$ the tomographic projection operator such that ideally $\boldsymbol{y} = \boldsymbol{\mathcal{R} x}$, and $\boldsymbol{\theta}$ the sparse coefficients of $\boldsymbol{x}$.
+$\boldsymbol{\Upsilon}$ is the basis in which $\boldsymbol{x}$ is assumed to be sparse, and is chosen to be DCT here.
+In addition to this sparsity prior, when object specific prior information is  used as well, the reconstruction improves significantly.
 The algorithm presented in~\cite{Essam2015} drew inspiration from CS and solved for the reconstruction from limited views using alternating direction method of multipliers.
@@
         \includegraphics[width=\textwidth]{../images/humerus/global_local/reconNoPrior.png}
-        \caption{CS}
+        \caption{l1-ls}
+        \label{fig:humerus_cs}
     \end{subfigure}
@@
     \caption{\textit{Knowing more about the data helps.} Reconstructions of (g) a test slice  of size $(200,200)$ from the Humerus CT dataset~\cite{humerus} are performed using object-prior [(a)-(f)] and from measurements obtained from only 10 views.
-(h) Filtered backprojection (FBP) shows streaky sub-sampling artefacts (i) CS reduces the artefacts significantly while slightly blurring details (j) Prior information coupled with CS greatly improves the reconstruction.}
+(h) Filtered backprojection (FBP) shows streaky sub-sampling artefacts (i) l1-ls reduces the artefacts significantly while slightly blurring details (j) Prior information coupled with l1-ls (CS) greatly improves the reconstruction.}
 \label{fig:diff_methods}
@@
 Global eigenspace priors are better able to exploit the similarity of a test volume to object-prior, by assuming that the new test volume lies within the space spanned by the eigenvectors of the multiple representative previously scanned objects.
-Fig.~\ref{fig:diff_methods} shows the advantage of combining the global prior with CS.
+Fig.~\ref{fig:diff_methods} shows the advantage of combining the global prior with the l1-ls form of CS.
 \subsection{\textbf{Contributions}}
@@
 The later scans are used to reveal the exact changes during and after burning of the tumor (ablation).
-In this context, we demonstrate the combined use of CS with the global prior, in two flavors: the vanilla (unselective) and selective global prior-based reconstruction.
+In this context, we demonstrate the combined use of l1-ls (CS) with the global prior, in two flavors: the vanilla (unselective) and selective global prior-based reconstruction.
 The choice of the number of measurement views and the type of reconstruction -- unselective or selective, is driven by the goal of the procedure.
@@
 \subcaptionbox{Backprojection}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
-\subcaptionbox{CS}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
 \subcaptionbox{Proposed\\ method: unselective prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
-\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) Filtered backprojection and no prior resulting in streaks, SSIM $= 0.48$ (c) CS and no prior resulting in blurred bone structures, SSIM $=0.35$ and (d) unselective global prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
+\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) Filtered backprojection and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures, SSIM $=0.35$ and (d) unselective global prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
 The region enclosed in red rectangle is our RoI as it contains both the new position of the needle and some background.
@@
 \subcaptionbox{Backprojection}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
-\subcaptionbox{CS}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
 \subcaptionbox{Proposed\\ method: unselective\\ prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
@@
 \subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
-\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) CS with SSIM $=0.46$ and (d) unselective global prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) selective prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
+\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) l1-ls with SSIM $=0.46$ and (d) unselective global prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) selective prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
 The region enclosed in green rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
@@
 \emph{The space spanned by the eigenvectors $\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance matrix is the global prior and is assumed to contain any test slice that is similar, but not necessarily identical to the object-prior.}  We use all of the $L-1$ orthogonal eigenvectors as a basis to represent the unknown test volume.
-Let $\boldsymbol{x} = \boldsymbol{\Upsilon\theta}$ denote the reconstructed volume, $\boldsymbol{y} = \boldsymbol{\mathcal{R} x}$ its measured tomographic projections, $\boldsymbol{\mathcal{R}}$ the tomographic projection operator, $\boldsymbol{\theta}$ the sparse coefficients of $\boldsymbol{x}$, $\boldsymbol{\Upsilon}$ the basis in which $\boldsymbol{x}$ is assumed to be sparse, $\boldsymbol{\mu}$ the mean of the previously scanned objects, and $\boldsymbol{\alpha}$ the vector of eigen-coefficients of the test scan, of which $\alpha_k$ is the $k^{\textrm{th}}$ element.
+Let $\boldsymbol{\mu}$ denote the mean of the previously scanned objects, and $\boldsymbol{\alpha}$ the vector of eigen-coefficients of the test scan, of which $\alpha_k$ is the $k^{\textrm{th}}$ element.
 Then, once the eigenspace is pre-computed, the test is reconstructed by minimizing the following cost function:
@@
         \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_dct30.png}
-        \caption{CS-DCT}
+        \caption{(l1-ls)-DCT}
      \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_wavelet30.png}
-        \caption{CS-Haar}
+        \caption{(l1-ls)-Haar}
      \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../images/potato/2D/cs_dct.png}
-        \caption{CS-DCT}
+        \caption{(l1-ls)-DCT}
      \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../images/potato/2D/cs_wavelet.png}
-        \caption{CS-Haar}
+        \caption{(l1-ls)-Haar}
      \end{subfigure}
@@
 It can be seen that the weights are low in the region of the new change in test data.
-Because all the iterative methods are computationally expensive, we chose only FBP and CS-DCT for computing weights-maps for all 3D reconstructions.
+Because all the iterative methods are computationally expensive, we chose only FBP and (l1-ls)-DCT for computing weights-maps for all 3D reconstructions.
 %---------------------------------------
@@
 \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
-\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm.png}}\hfill
 \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
@@
 \hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{CS} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + CS\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + CS\end{tabular}} \\ \hline
+                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
 \textbf{red RoI}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.850       & 0.712                                                               & 0.852                                                            \\ \hline
@@
 \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
-\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
 \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
@@
 \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/FDK_cropped.png}}\hfill
-\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/CS_cropped.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/CS_cropped.png}}\hfill
 \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
@@
 \hline
-                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{CS} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + CS\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + CS\end{tabular}} \\ \hline
+                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
 \textbf{red RoI}   & 1 (ideal)                     & 0.737        & 0.836       & 0.858                                                               & \textcolor{red}{0.883}                                                                  \\ \hline
@@
 %\captionsetup{labelformat=empty}
-        \caption{CS}
+        \caption{l1-ls}
      \end{subfigure}\\
@@
 \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_cropped.png}}\hfill
-\subcaptionbox{CS}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_cropped.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_cropped.png}}\hfill
 \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_cropped.png}}\hfill
@@
 \hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{CS} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + CS\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + CS\end{tabular}} \\ \hline
+                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
 \textbf{red RoI}   & 1 (ideal)                     & 0.852        & 0.843       & 0.834                                                               & \textcolor{red}{0.881}                                                                  \\ \hline
@@
 \textbf{\begin{tabular}[c]{@{}c@{}}Slice being\\ imaged at\\ time t\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Probe distance from\\ tumor or \\ ablation stage\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ imaging\\ views\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Reconstruction\\ protocol: type \\ of global prior\end{tabular}} \\ \hline
-Slice t=1 & Very far from tumor & 360 & CS \\ \hline
+Slice t=1 & Very far from tumor & 360 & l1-ls \\ \hline
 Slice t=2 & Sufficiently far from tumor & 40 & Unselective \\ \hline

### 2020-06-08 paper/tci.tex
included newly marked zoomed RoI of sprouts

@@
 \centering
-\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_cropped.png}}\hfill
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_cropped.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_cropped.png}}\hfill
-\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_cropped.png}}
-\caption{Zoomed-in portion $(16 \times 21)$ corresponding to the red RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods (b) unclear, (c) unclear, (d) only two strong structures seen and (e) there is a hint of a third structure too (as seen in the test RoI).}
+\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_marked.png}}\hfill
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_marked.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_marked.png}}\hfill
+\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_marked.png}}\hfill
+\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_marked.png}}
+\caption{Zoomed-in portion $(41 \times 36)$ containing the RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods (a) the test showing 3 distinct structures (in red here) (b) 3 structures recovered with poor contrast, (c) structures indistinguishable, (d) only two strong structures seen and (e) there is a hint of a third structure too with better contrast.}
 \label{fig:sprouts_zoomed_3D_results}

### 2020-06-11 paper/tci.tex
Modified Fig.16. (zoomed sprouts)

@@
     \boldsymbol{W_v}(x,y,z) = (1+k(\min_{j}|X^j(x,y,z) - P^j(x,y,z)|))^{-1}.
+    \label{eq:weightsEq}
   \end{equation}
-\label{eq:weightsEq}
 \end{enumerate}
@@
   \centering
+  \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_croppedBig.png}}\hfill
+    \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_croppedBig.png}}\hfill
+      \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_croppedBig.png}}\hfill
+        \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_croppedBig.png}}\hfill
+        \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_croppedBig.png}}\hfill
           \subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_marked.png}}\hfill
@@
 \subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_marked.png}}
-\caption{Zoomed-in portion $(41 \times 36)$ containing the RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods (a) the test showing 3 distinct structures (in red here) (b) 3 structures recovered with poor contrast, (c) structures indistinguishable, (d) only two strong structures seen and (e) there is a hint of a third structure too with better contrast.}
+\caption{Zoomed-in portion $(41 \times 36)$ containing the RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods.
+The images of the bottom row are the same as repective images of the top row, with regions marked additionally.
+(a) the test showing 3 distinct structures (in red here) (b) 3 structures recovered with poor contrast, (c) structures indistinguishable, (d) only two strong structures seen and (e) there is a hint of a third structure too with better contrast.}
 \label{fig:sprouts_zoomed_3D_results}

### 2020-06-22 paper/tci.tex
Added bigger RoI info and new CS potato image

@@
 \emph{Departing from this, we demonstrate reconstruction results from raw projection data.} In all figures in this section, `unselective prior' refers to optimizing Eq.~\ref{eq:selective_prior} with $\boldsymbol{W}(x,y,z)=1$.
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-      \caption{Potato 3D dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
-        volume (extreme right). Notice the appearance of the fourth
-        hole in the test slice. }
-\label{fig:object-prior_test_potato_A}
-\end{figure}
-
-%--------potato reconstruction--------------------------------------------------
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.185\columnwidth]{../images/potato/testIm_color.png}}}\hfill
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm.png}}\hfill
-\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
-\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
-\caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts.
-The reconstructed volumes can be viewed in~\cite{supp_paper}.}
-\label{fig:potato_3D_results_A}
-\end{figure}
 %----------------------------------------------------------
-%-----------------------results of potato dataset
-
-\subsubsection{\textbf{Potato dataset}}
-\label{Sec:potato}
-The first (Potato) dataset consisted of four scans of the humble potato, chosen for its simplicity (Fig.~\ref{fig:object-prior_test_potato_A}).
-Measurements from each scan consisted of real cone-beam projections from 900 views, each of size $150\times150$.
-The corresponding size of the reconstructed volume is $150\times150\times100$.
-While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
-Projections were obtained using circular cone beam geometry.
-The specimen was kept in the same position throughout the acquisitions.
-In cases where such an alignment is not present, all the template volumes must be pre-aligned before computing the eigenspace.
-The test must be registered to the object-prior after its preliminary pilot reconstruction.
-%Further, this alignment can be refined following every update of the reconstructed test volume.
- The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views.
-The test volume was reconstructed using measurements from 45 projection views, i.e.
-$5\%$ of the projection views from which ground truth was reconstructed.
-The selected 3D
-ground truth of template volumes, test volume, as well as the 3D reconstructions are shown in~\cite{supp_paper}.
-Fig.~\ref{fig:potato_3D_results_A} shows a slice from the reconstructed 3D volume.
-We observe that our method reconstructs new structures while simultaneously reducing streak artefacts.\\ %The new regions detected by different reconstruction methods are shown in Fig.~\ref{fig:weights_map_2Dpotato}.
-The lower intensities denote new regions which were assigned lower weights.
-This ensures that the new regions are reconstructed using projection measurements alone, avoiding erroneous influence of the prior.
-%---------------------------------------
-\begin{table}[!h]
-\caption{SSIM of 3D reconstructed potato volumes from various methods.
-Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.
-In this dataset alone, the new changes are in a homogeneous background.
-Hence, the FDK performs the best when the RoI alone is considered.
-However, it fails when the entire volume is considered due to the prominent streaky artefacts.}
-\begin{tabular}{|l|c|c|c|c|c|}
-\hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{red RoI}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.850       & 0.712                                                               & 0.852                                                            \\ \hline
-\textbf{full volume} & 1 (ideal)                     & 0.744        & 0.817       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
-\end{tabular}
-\label{table:potato_ssim}
-\end{table}
 %-------------------------------------------------
@@
 \label{Sec:okra}
-In order to test on data with intricate structures, a second (Okra) dataset consisting of five scans of an okra specimen was acquired (Fig.~\ref{fig:object-prior_test_okra}).
+Our first dataset is that of an Okra specimen consisting of its five scans (Fig.~\ref{fig:object-prior_test_okra}).
 The measurements consisted of real cone-beam projections from 450 views, each of size $336\times156$.
@@
 This was followed by four scans, each after introducing one new cut.
+The specimen was kept in the same position throughout the acquisitions.
+In cases where such an alignment is not present, all the template volumes must be pre-aligned before computing the eigenspace.
+The test must be registered to the object-prior after its preliminary pilot reconstruction.
 The ground truth consists of FDK reconstructed volumes from the the full set of 450 view projections.
@@
 \label{Sec:sprouts}
-The third dataset consists of six scans of an in vivo
+The second dataset consists of six scans of an in vivo
 sprout specimen imaged at its various stages of growth
@@
 consecutive slices in the 3D volume to indicate new structures; other
-changes can be viewed in the video. Tables~\ref{table:potato_ssim},~\ref{table:okra_ssim} and \ref{table:sprouts_ssim} show the improvement in the Structure
+changes can be viewed in the video. Tables~\ref{table:okra_ssim} and \ref{table:sprouts_ssim} show the improvement in the Structure
 Similarity Index (SSIM) of the reconstructed new regions as compared
@@
 %--------------------------------------------------------------------------
+
+\subsection{\textbf{Challenging dataset}}
+\label{Sec:potato}
+While the design of the weights map in the proposed algorithm aims to combine the best of information from both the current measurements and the prior, we found FDK to be preferable when the test object has a simple, homogeneous structure without intricate details.
+One such dataset is the Potato dataset, the results on which are detailed here.\\
+This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
+Measurements from each scan consisted of real cone-beam projections from 900 views, each of size $150\times150$.
+The corresponding size of the reconstructed volume is $150\times150\times100$.
+While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
+Projections were obtained using circular cone beam geometry.
+%Further, this alignment can be refined following every update of the reconstructed test volume.
+The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views.
+The test volume was reconstructed using measurements from 45 projection views, i.e.
+$5\%$ of the projection views from which ground truth was reconstructed.
+The selected 3D
+ground truth of template volumes, test volume, as well as the 3D reconstructions are shown in~\cite{supp_paper}.
+Fig.~\ref{fig:potato_3D_results_A} shows a slice from the reconstructed 3D volume.
+We observe that our method reconstructs new structures while simultaneously reducing streak artefacts.\\ %The new regions detected by different reconstruction methods are shown in Fig.~\ref{fig:weights_map_2Dpotato}.
+The lower intensities denote new regions which were assigned lower weights.
+This ensures that the new regions are reconstructed using projection measurements alone, avoiding erroneous influence of the prior.
+Table~\ref{table:potato_ssim} shows the Structure Similarity Index (SSIM) of the reconstructed new regions using various methods.
+We observe that the FDK performs very well for smaller RoI; as the RoIs get bigger, the FDK reconstructions have poor SSIM due to strong subsampling artefacts.
+In contrast, the results from l1-ls and our method progressively improve when compared to FDK as the RoIs get bigger.
+Hence, in practice, one may choose FDK for the case of simple, homogeneous dataset with smaller RoI,  and prefer selective prior-based reconstruction when the dataset is complex and RoIs are larger.
+%---------------------------------------
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.235\linewidth}
+        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_green.png}}
+\captionsetup{labelformat=empty}
+\caption{}
+\label{fig:potato3D_test}
+     \end{subfigure}
+      \caption{Potato 3D dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
+        volume (extreme right). Notice the appearance of the fourth
+        hole in the test slice. }
+\label{fig:object-prior_test_potato_A}
+\end{figure}
+
+%--------potato reconstruction--------------------------------------------------
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.185\columnwidth]{../images/potato/testIm_green.png}}}\hfill
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm_new.png}}\hfill
+\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
+\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
+\caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts.
+The reconstructed volumes can be viewed in~\cite{supp_paper}.}
+\label{fig:potato_3D_results_A}
+\end{figure}
+%------------------------------------------------------------------------
+\begin{table}[!h]
+\caption{SSIM of 3D reconstructed potato volumes from various methods.
+Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.
+In this dataset alone, the new changes are in a homogeneous background.
+Hence, the FDK performs the best when the RoI alone is considered.
+However, it fails when the entire volume is considered due to the prominent streaky artefacts.}
+\begin{tabular}{|l|c|c|c|c|c|}
+\hline
+                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior\\+ l1-ls\end{tabular}} \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.807      & 0.712                                                               & 0.852                                                            \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.918}        & 0.870      & 0.871                                                               & 0.880                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.878       & \textcolor{red}{0.928}    & 0.922                                                            & 0.895                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.744        & 0.874       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}red RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.945}        & 0.804       & 0.721                                                               & 0.858                                                            \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}green RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.920}        & 0.872       & 0.886                                                               & 0.901                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}cyan RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & 0.879        & \textcolor{red}{0.928}       & 0.926                                                               & 0.903                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}full \\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & 0.746        & \textcolor{red}{0.903}       & 0.866                                                               & 0.868                                                                  \\ \hline
+\end{tabular}
+\label{table:potato_ssim}
+\end{table}
+
 \section{Discussion}
@@
 We now discuss the need for registration between object-prior and the test, and the effect of hyper-parameters on our reconstructions.
+
+\begin{table}[!h]
+  \centering
+\caption{Computation time for reconstruction of volumes using various methods}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\hline
+   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\\hline
+\textbf{Potato}  &  &   &  &  \\ \hline
+\textbf{Okra}  &  &   &  &  \\ \hline
+\textbf{Sprouts}  &  &   &  &  \\ \hline
+\end{tabular}
+\label{table:Computation_time_3D}
+\end{table}
 

### 2020-06-22 paper/tci.tex
removed SSIM of slice- potato

@@
 \textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.744        & 0.874       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}red RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.945}        & 0.804       & 0.721                                                               & 0.858                                                            \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}green RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.920}        & 0.872       & 0.886                                                               & 0.901                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}cyan RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & 0.879        & \textcolor{red}{0.928}       & 0.926                                                               & 0.903                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}full \\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & 0.746        & \textcolor{red}{0.903}       & 0.866                                                               & 0.868                                                                  \\ \hline
 \end{tabular}

### 2020-06-23 paper/tci.tex
added new CS 3D potato image, updated SSIM potato table, added computation time for potato

@@
                    & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior\\+ l1-ls\end{tabular}} \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.807      & 0.712                                                               & 0.852                                                            \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.918}        & 0.870      & 0.871                                                               & 0.880                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.878       & \textcolor{red}{0.928}    & 0.922                                                            & 0.895                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.744        & 0.874       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.877      & 0.712                                                               & 0.852                                                            \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.918}        & 0.911      & 0.871                                                               & 0.880                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.878       & \textcolor{red}{0.939}    & 0.922                                                            & 0.895                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.744        & 0.813       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
 \end{tabular}
@@
   \centering
-\caption{Computation time for reconstruction of volumes using various methods}
+\caption{Computation time for reconstruction of volumes using various methods.
+The configuration of the system used was x86\_64 architecture, 62GB RAM, 12-core AMD 3.8GHz processor, with Nvidia GeForce RTX 2080 Ti GPU.}
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|}
@@
    & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\\hline
-\textbf{Potato}  &  &   &  &  \\ \hline
+\textbf{Potato, 45 views}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
 \textbf{Okra}  &  &   &  &  \\ \hline

### 2020-06-23 paper/tci.tex
All SSIM values now have 2 significant digits only

@@
 \begin{table}[!h]
+  \centering
 \caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g).
@@
  Fig.~\ref{fig:reconstructions_diff_methods}  & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} \\\hline
-\textbf{red RoI}  & 0.502 & 0.597  & 0.453 & 0.474 & 0.565 & 0.523 & \textcolor{red}{0.759} \\ \hline
+\textbf{red RoI}  & 0.50 & 0.60  & 0.45 & 0.47 & 0.56 & 0.52 & \textcolor{red}{0.76} \\ \hline
 \end{tabular}
@@
                    &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{red RoI}   & 1 (ideal)                     & 0.737        & 0.836       & 0.858                                                               & \textcolor{red}{0.883}                                                                  \\ \hline
-\textbf{green RoI} & 1 (ideal)                     & 0.798        & \textcolor{red}{0.861}       & 0.800                                                               & \textcolor{red}{0.861}                                                                  \\ \hline
+\textbf{red RoI}   & 1 (ideal)                     & 0.74        & 0.84       & 0.86                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
+\textbf{green RoI} & 1 (ideal)                     & 0.80        & \textcolor{red}{0.86}       & 0.80                                                               & \textcolor{red}{0.86}                                                                  \\ \hline
 \end{tabular}
@@
                    & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{red RoI}   & 1 (ideal)                     & 0.852        & 0.843       & 0.834                                                               & \textcolor{red}{0.881}                                                                  \\ \hline
+\textbf{red RoI}   & 1 (ideal)                     & 0.85        & 0.84       & 0.83                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
 \end{tabular}
@@
                    & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior\\+ l1-ls\end{tabular}} \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.877      & 0.712                                                               & 0.852                                                            \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.918}        & 0.911      & 0.871                                                               & 0.880                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.878       & \textcolor{red}{0.939}    & 0.922                                                            & 0.895                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.744        & 0.813       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.94}        & 0.88      & 0.71                                                               & 0.85                                                            \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.92}        & 0.91      & 0.87                                                               & 0.88                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.88       & \textcolor{red}{0.94}    & 0.92                                                            & 0.89                                                                  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.74        & 0.81       & \textcolor{red}{0.86}                                                               & \textcolor{red}{0.86}                                                                  \\ \hline
 \end{tabular}

### 2020-06-25 paper/tci.tex
Inserted recon. on homogeneous data in "Discussion"

@@
 
-\subsection{\textbf{Challenging dataset}}
+\section{Discussion}
+\label{sec:discussion}
+The presented unselective prior-based algorithm is suited to applications where we wish to detect the location of new changes in an object over time, and the presented selective prior-based algorithm is suited to applications where we wish to observe the intricate details of those new changes.
+This distinction in the techniques used has not been studied earlier in literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our knowledge.
+Eventhough methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
+We have presented a principled method of tackling this particular issue via our weights map.
+We not only estimate the location of new changes, but also compute their intensities.
+This information is then used to modulate the strength of the prior during the reconstruction of the test.
+Our results consist of 3D reconstructions from real cone-beam projections of two datasets, and both 3D and 2D reconstructions from cone-beam and parallel beam projections respectively.
+In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
+An in-depth analysis of each of the results is presented in Sec.~\ref{sec:results}.
+We now discuss the need for registration between object-prior and the test, the method that suits best when the data is homogeneous, and the effect of hyper-parameters on our reconstructions.
+
+\begin{table}[!h]
+  \centering
+\caption{Computation time for reconstruction of volumes using various methods.
+The configuration of the system used was x86\_64 architecture, 62GB RAM, 12-core AMD 3.8GHz processor, with Nvidia GeForce RTX 2080 Ti GPU.}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\hline
+   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\\hline
+\textbf{Potato, 45 views}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
+\textbf{Okra}  &  &   &  &  \\ \hline
+\textbf{Sprouts}  &  &   &  &  \\ \hline
+\end{tabular}
+\label{table:Computation_time_3D}
+\end{table}
+
+\subsection{Issue of misalignment between test and templates}
+As with any global prior-based method, there is a need for the test volume to be registered with the object-prior.
+In all our longitudinal study experiments, the volumes were already aligned during imaging.
+However, if this were not the case, then the prior must be aligned to the test based on an initial pilot reconstruction of the test.
+
+\subsection{Reconstruction of homogeneous data}
 \label{Sec:potato}
@@
 
-\section{Discussion}
-\label{sec:discussion}
-The presented unselective prior-based algorithm is suited to applications where we wish to detect the location of new changes in an object over time, and the presented selective prior-based algorithm is suited to applications where we wish to observe the intricate details of those new changes.
-This distinction in the techniques used has not been studied earlier in literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our knowledge.
-Eventhough methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
-We have presented a principled method of tackling this particular issue via our weights map.
-We not only estimate the location of new changes, but also compute their intensities.
-This information is then used to modulate the strength of the prior during the reconstruction of the test.
-Our results consist of 3D reconstructions from real cone-beam projections of two datasets, and both 3D and 2D reconstructions from cone-beam and parallel beam projections respectively.
-In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
-An in-depth analysis of each of the results is presented in Sec.~\ref{sec:results}.
-We now discuss the need for registration between object-prior and the test, and the effect of hyper-parameters on our reconstructions.
-
-\begin{table}[!h]
-  \centering
-\caption{Computation time for reconstruction of volumes using various methods.
-The configuration of the system used was x86\_64 architecture, 62GB RAM, 12-core AMD 3.8GHz processor, with Nvidia GeForce RTX 2080 Ti GPU.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-\hline
-   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\\hline
-\textbf{Potato, 45 views}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
-\textbf{Okra}  &  &   &  &  \\ \hline
-\textbf{Sprouts}  &  &   &  &  \\ \hline
-\end{tabular}
-\label{table:Computation_time_3D}
-\end{table}
-
-\subsection{Issue of misalignment between test and templates}
-As with any global prior-based method, there is a need for the test volume to be registered with the object-prior.
-In all our longitudinal study experiments, the volumes were already aligned during imaging.
-However, if this were not the case, then the prior must be aligned to the test based on an initial pilot reconstruction of the test.
-
 \subsection{Effect of hyper-parameters}

### 2020-06-25 paper/tci.tex
rearranged

@@
 
-\subsection{\textbf{Selective prior-based reconstruction}}
+ \section{Resuls: Reconstruction by unselective prior}
+ %--------------------------------okra data-------------------------------
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.176\linewidth}
+        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/test.png}}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
+       first four from the left), and one from the test volume
+       (extreme right). In the regions marked in red and green, while
+       all slices have deformities, the test
+       has none.}
+\label{fig:object-prior_test_okra}
+\end{figure}
+%----------------------------------------------------
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.185\columnwidth]{../images/okra/test.png}}}\hfill
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
+\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\caption{3D reconstruction of the okra from $10\%$ projection
+  views (b) has strong streak artefacts, (c) blurred, (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in ~\cite{supp_paper}.}
+\label{fig:okra_3D_results_unselective}
+\end{figure}
+
+%---------------------------------------
+\begin{table}[!h]
+  \centering
+  \caption{SSIM of the full reconstructed okra volume by various methods.}
+\begin{tabular}{|l|c|c|c|c|}
+\hline
+                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} \\ \hline
+\textbf{full Volume} & 1 (ideal)                     & 0.87        &  0.92       & \textcolor{red}{0.95}                                                                                   \\ \hline
+\end{tabular}
+\label{table:okra_ssim_full_volume}
+\end{table}
+
+%-------------------------sprouts data
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+    \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}\\
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.29\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
+        right).}
+\label{fig:object-prior_test_sprouts}
+\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+ %-----------------------------sprouts 3D results
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.29\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{FDK}
+    \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{l1-ls}
+     \end{subfigure}\\
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{Unselective Prior}
+     \end{subfigure}
+     \caption{3D reconstruction of sprouts from $2.5\%$ projection views
+   (b, c) have poor details (d) no new information detected (the
+   prior dominates as can be seen in the blue and red regions) and
+   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed in ~\cite{supp_paper}.} 
+\label{fig:sprouts_3D_results}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\begin{table}
+  \centering
+  \caption{SSIM of the full reconstructed sprouts volume by various methods.}
+\begin{tabular}{|l|c|c|c|c|}
+\hline
+                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} \\ \hline
+\textbf{Full volume}   & 1 (ideal)                    & 0.82        & 0.71       & \textcolor{red}{0.92}                                                                                                                       \\ \hline
+\end{tabular}
+\label{table:sprouts_ssim}
+\end{table}
+%----------------------------------------------------------------------
+\section{Method:Selective prior-based reconstruction}
 \label{sec:selective_prior}
@@
 
-%--------------------------------okra data-------------------------------
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.176\linewidth}
-        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/testCropped.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
-       first four from the left), and one from the test volume
-       (extreme right). In the regions marked in red and green, while
-       all slices have deformities, the test
-       has none.}
-\label{fig:object-prior_test_okra}
-\end{figure}
 %----------------------------------------------------
@@
 
-%-------------------------sprouts data
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-    \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}\\
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.29\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
-        right).}
-\label{fig:object-prior_test_sprouts}
-\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
 \subsubsection{\textbf{Sprouts dataset}}

### 2020-06-26 paper/tci.tex
rearrangement

@@
 %---------------------------------Unselective section---------------------
-\section{Methods}
-\label{sec:methods}
+\section{Method: unselective global prior-based reconstruction}
+\label{sec:unselective_global_prior}
 Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a global (unselective) prior-based reconstruction in Sec.~\ref{sec:unselective_global_prior}.
@@
 This, we refer to as a \textit{selective} global prior-based reconstruction routine.
-\subsection{\textbf{Summary of unselective global prior-based reconstruction}}
-\label{sec:unselective_global_prior}
 
@@
  \section{Resuls: Reconstruction by unselective prior}
+
+ The proposed method has been validated on new\footnote {These and our code will be made available to the community.} scans of biological specimens in a longitudinal setting.
+These datasets in the form of \emph{raw cone-beam projection measurements} were acquired from a lab at the Australian National University (ANU).
+%We emphasize that in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections \emph{simulated} from 3D volumes.
+This is because most CT scanners do not reveal the raw projections, and instead output only the full reconstructed volumes.
+Moreover, the process of conversion from the projections to the full volumes is proprietary.
+\emph{Departing from this, we demonstrate reconstruction results from raw projection data.}
+In all figures in this section, `unselective prior' refers to optimizing Eq.~\ref{eq:selective_prior} with $\boldsymbol{W}(x,y,z)=1$.
+%----------------------------------------------------------
+%-------------------------------------------------
+\subsubsection{\textbf{Okra dataset}}
+\label{Sec:okra_unselective}
+Our first dataset is that of an Okra specimen consisting of its five scans (Fig.~\ref{fig:object-prior_test_okra}).
+The measurements consisted of real cone-beam projections from 450 views, each of size $336\times156$.
+The corresponding size of the reconstructed volume is $338\times338\times123$.
+Prior to the first scan, two holes were drilled on the surface of the specimen.
+This was followed by four scans, each after introducing one new cut.
+The specimen was kept in the same position throughout the acquisitions.
+In cases where such an alignment is not present, all the template volumes must be pre-aligned before computing the eigenspace.
+The test must be registered to the object-prior after its preliminary pilot reconstruction.
+The ground truth consists of FDK reconstructed volumes from the the full set of 450 view projections.
+The test volume was reconstructed from a partial set of 45 projections, i.e.
+$10\%$ of the projection views from which ground truth was reconstructed.
+The selected 3D ground truth of template volumes, the test volume as well as the 3D reconstructions can be seen in~\cite{supp_paper}.
+One of the slices of the reconstructed volumes is shown in Fig.~\ref{fig:okra_3D_results}.
+The red and green 3D RoI in the video and images show the regions where new changes are present.
+Based on the potato and the okra experiments, we see that our method is able to \emph{discover both} the presence of a new structure, as well as the absence of a structure.
+
  %--------------------------------okra data-------------------------------
@@
 \end{table}
-
+\subsubsection{\textbf{Sprouts dataset}}
+\label{Sec:sprouts}
+The second dataset consists of six scans of an in vivo
+sprout specimen imaged at its various stages of growth
+(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size $130\times130\times130$. In contrast to the scientific
+experiment performed for the case of the okra and the potato where we
+introduced man-made defects, the changes here are purely the work of
+nature.
 %-------------------------sprouts data
@@
 %----------------------------------------Results-----------------------
-\section{Results}
+\section{Results: Reconstruction by selective prior}
 \label{sec:results}
@@
 The results below demonstrate the advantage of the selective global prior method over the unselective method.
-
-%\subsection{\textbf{Evaluation of selective prior-reconstruction in real 3D data}}
-
-%-----------------------results of potato dataset
-
-The proposed method has been validated on new\footnote {These and our code will be made available to the community.} scans of biological specimens in a longitudinal setting.
-These datasets in the form of \emph{raw cone-beam projection measurements} were acquired from a lab at the Australian National University (ANU).
-We emphasize that in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections \emph{simulated} from 3D volumes.
-This is because most CT scanners do not reveal the raw projections, and instead output only the full reconstructed volumes.
-Moreover, the process of conversion from the projections to the full volumes is proprietary.
-\emph{Departing from this, we demonstrate reconstruction results from raw projection data.} In all figures in this section, `unselective prior' refers to optimizing Eq.~\ref{eq:selective_prior} with $\boldsymbol{W}(x,y,z)=1$.
-%----------------------------------------------------------
-%-------------------------------------------------
-\subsubsection{\textbf{Okra dataset}}
-\label{Sec:okra}
-Our first dataset is that of an Okra specimen consisting of its five scans (Fig.~\ref{fig:object-prior_test_okra}).
-The measurements consisted of real cone-beam projections from 450 views, each of size $336\times156$.
-The corresponding size of the reconstructed volume is $338\times338\times123$.
-Prior to the first scan, two holes were drilled on the surface of the specimen.
-This was followed by four scans, each after introducing one new cut.
-The specimen was kept in the same position throughout the acquisitions.
-In cases where such an alignment is not present, all the template volumes must be pre-aligned before computing the eigenspace.
-The test must be registered to the object-prior after its preliminary pilot reconstruction.
-The ground truth consists of FDK reconstructed volumes from the the full set of 450 view projections.
-The test volume was reconstructed from a partial set of 45 projections, i.e.
-$10\%$ of the projection views from which ground truth was reconstructed.
-The selected 3D ground truth of template volumes, the test volume as well as the 3D reconstructions can be seen in~\cite{supp_paper}.
-One of the slices of the reconstructed volumes is shown in Fig.~\ref{fig:okra_3D_results}.
-The red and green 3D RoI in the video and images show the regions where new changes are present.
-Based on the potato and the okra experiments, we see that our method is able to \emph{discover both} the presence of a new structure, as well as the absence of a structure.
 
@@
 \label{Sec:sprouts}
-The second dataset consists of six scans of an in vivo
-sprout specimen imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size $130\times130\times130$. In contrast to the scientific
-experiment performed for the case of the okra and the potato where we
-introduced man-made defects, the changes here are purely the work of
-nature. %-----------------------------sprouts 3D results
+ %-----------------------------sprouts 3D results
 \begin{figure}[!h]

### 2020-06-30 paper/tci.tex
Included new story Fig.1

@@
 While this is easily feasible when measurements are acquired from a large number of projection angles (referred to as `views' henceforth), it is challenging when the number of views is limited.
-If the goal is to track the changes while simultaneously reducing sub-sampling artefacts, we propose (1) acquiring measurements from a \emph{small} number of views and using a global \emph{`unselective'} prior based reconstruction.
+If the goal is to track the changes while simultaneously reducing sub-sampling artefacts, we propose (1) acquiring measurements from a \emph{small} number of views and using a global \emph{`uniform'} prior based reconstruction.
 If the goal is to observe \emph{details} of new changes, we propose (2) acquiring measurements from a \emph{moderate} number of views and using a more involved reconstruction routine.
-We show that in the latter case, a `selective' technique is necessary in order to prevent the prior from adversely affecting the reconstruction of new structures that are absent in any of the earlier scans.
+We show that in the latter case, a `spatially-varying' technique is necessary in order to prevent the prior from adversely affecting the reconstruction of new structures that are absent in any of the earlier scans.
 The reconstruction of new regions is safeguarded from the bias of the prior by computing regional weights that moderate the local influence of the priors.
@@
 We have tested the efficacy of our method on synthetic as well as real volume data.
-The results demonstrate the use of both unselective and selective priors in different scenarios.
+The results demonstrate the use of both uniform and spatially-varying priors in different scenarios.
 Our methods significantly improve the overall quality of the reconstructed data while minimizing the number of measurements needed for imaging in longitudinal studies.
@@
 In this context, measurements in conventional data acquisition techniques are acquired by sampling the physical object uniformly above the Nyquist rate.
+In such a case when there are sufficient measurements, reconstruction using the conventional filtered backprojection (FBP) suffices, as seen in Fig.~\ref{fig:story1}.
 However, in the last decade, reconstruction from sub-Nyquist sampled data has been made possible due to methods such as the widely used Compressed Sensing (CS) technique~\cite{Donoho,introCS}, which assumes the data to exhibit properties such as sparsity of the underlying image under certain mathematical transforms such as the Discrete Cosine Transform (DCT) or wavelet transforms.
-Among the many optimizers used in CS, we used the l1-regularized least squares (l1-ls) form and observed that although this optimizer removes most of the artefacts created due to sub-sampling, its reconstruction is blurred when the number of views is very limited, as shown in Fig.~\ref{fig:diff_methods}.
-Specifically, the reconstruction in Fig.~\ref{fig:humerus_cs} is obtained by minimizing the following cost using the solver in~\cite{l1ls}:
+Fig.~\ref{fig:story2} shows how reconstruction using CS routine is better than FBP for sub-Nyquist number of views.
+Here, among the many optimizers used in CS, we have used the l1-regularized least squares (l1-ls) form and observed that although this optimizer removes most of the artefacts created due to sub-sampling, its reconstruction is blurred when the number of views is very limited, as shown in Fig.~\ref{fig:story2}.
+Specifically, the reconstruction in Fig.~\ref{fig:story2-CS} and~\ref{fig:story3-CS} is obtained by minimizing the following cost using the solver in~\cite{l1ls}:
  \begin{equation}
@@
 \centering
-\fcolorbox{red}{white}{\begin{subfigure}[b]{0.155\linewidth}
-        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template1.png}
-        \caption{}
-     \end{subfigure}
-\begin{subfigure}[b]{0.155\linewidth}
-        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template2.png}
-        \caption{}
-     \end{subfigure}
-\begin{subfigure}[b]{0.155\linewidth}
-        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template3.png}
-        \caption{}
-     \end{subfigure}
-\begin{subfigure}[b]{0.155\linewidth}
-        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template4.png}
-        \caption{}
-     \end{subfigure}
-\begin{subfigure}[b]{0.155\linewidth}
-        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template5.png}
-        \caption{}
-     \end{subfigure}
-\begin{subfigure}[b]{0.155\linewidth}
-        \includegraphics[width=1\textwidth]{../images/humerus/humerus_template6.png}
-        \caption{}
-     \end{subfigure}}\\
-\begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/humerus/global_local/groundTruth.png}}
+    \begin{subfigure}[b]{0.23\linewidth}
+        \includegraphics[width=\textwidth]{../images/story/testIm.png}
         \caption{Test}
+        \label{fig:story1-test}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.23\linewidth}
+        \includegraphics[width=\textwidth]{../images/story/600_views/fbp.png}
+        \caption{FBP, no prior}
+        \label{fig:1000_views_fbp}
+    \end{subfigure}
+    %\begin{subfigure}[b]{0.23\linewidth}
+     %   \includegraphics[width=\textwidth]{../images/story/600_views/CS_lambda0_0.00.png}
+     %   \caption{Least squares}
+     %\end{subfigure}
+    \caption{Reconstruction from large number of views (600 views); (a) 2D test slice of size [260, 260] (b) FBP reconstruction (SSIM = 0.92).}% (c) Least squares reconstruction (SSIM = 0.99).}
+\label{fig:story1}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+    %\begin{subfigure}[b]{0.23\linewidth}
+     %   \includegraphics[width=\textwidth]{../images/story/testIm.png}
+      %  \caption{Test}
+     %\end{subfigure}
+    \begin{subfigure}[b]{0.23\linewidth}
+        \includegraphics[width=\textwidth]{../images/story/100_views/fbp.png}
+        \caption{FBP, no prior}
+        \label{fig:1000_views_fbp}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/humerus/fbp_humerus.png}
-        \caption{FBP}
-     \end{subfigure}
+        \includegraphics[width=\textwidth]{../images/story/100_views/CS_lambda0_2.00.png}
+        \caption{sparsity prior}
+        \label{fig:story2-CS}
+     \end{subfigure}
+    \caption{Reconstruction of Fig.~\ref{fig:story1-test} from sub-Nyquist number of views (100 views); (a) FBP reconstruction (SSIM = 0.83) (b) l1-ls reconstruction (SSIM = 0.90).}
+\label{fig:story2}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+    %\begin{subfigure}[b]{0.23\linewidth}
+     %   \includegraphics[width=\textwidth]{../images/story/testIm.png}
+      %  \caption{Test}
+     %\end{subfigure}
     \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/humerus/global_local/reconNoPrior.png}
-        \caption{l1-ls}
-        \label{fig:humerus_cs}
-    \end{subfigure}
+        \includegraphics[width=\textwidth]{../images/story/40_views/fbp.png}
+        \caption{FBP,\\ no prior}
+        \label{fig:1000_views_fbp}
+    \end{subfigure}
+    \quad
     \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/humerus/global_local/global.png}
-        \caption{This paper}
-     \end{subfigure}
-    \caption{\textit{Knowing more about the data helps.} Reconstructions of (g) a test slice  of size $(200,200)$ from the Humerus CT dataset~\cite{humerus} are performed using object-prior [(a)-(f)] and from measurements obtained from only 10 views.
-(h) Filtered backprojection (FBP) shows streaky sub-sampling artefacts (i) l1-ls reduces the artefacts significantly while slightly blurring details (j) Prior information coupled with l1-ls (CS) greatly improves the reconstruction.}
-\label{fig:diff_methods}
+        \includegraphics[width=\textwidth]{../images/story/40_views/CS_lambda0_3.00.png}
+        \caption{sparsity \\prior}
+        \label{fig:story3-CS}
+    \end{subfigure}
+    \quad
+        \begin{subfigure}[b]{0.23\linewidth}
+        \includegraphics[width=\textwidth]{../images/story/40_views/plain_pca.png}
+        \caption{sparsity \\+ object prior}
+     \end{subfigure}
+    \caption{Reconstruction of Fig.~\ref{fig:story1-test} from sub-sub-Nyquist number of views (40 views); (a) FBP reconstruction (SSIM = 0.74) (b) l1-ls reconstruction (SSIM = 0.84) (c) prior-based reconstruction (SSIM = 0.85).}
+\label{fig:story3}
 \end{figure}
@@
 In addition, when some extra information about the object's structure is known~\cite{PICCS,cardiacPICCS,lubner2011,pirple,mota2017}, it is beneficial in further reducing the number of measurements.
-These prior-based techniques use information from previously scanned data (`object-prior') of the same object or a similar one, and utilize it to reconstruct new volumes from very few sets of additional measurements.
+As seen in Fig.~\ref{fig:story3}, the use of object prior further improves the reconstruction when the number of views is far below the Nyquist criterion.
+The prior-based techniques use information from previously scanned data (`object-prior') of the same object or a similar one, and utilize it to reconstruct new volumes from very few sets of additional measurements.
 However, the above methods have the following two limitations: (1) the prior information may potentially overwhelm the essential details that appear in the test, (2) there is the key issue of choice of \textit{a particular} previously scanned object among the many previously acquired scans.
@@
 Global eigenspace priors are better able to exploit the similarity of a test volume to object-prior, by assuming that the new test volume lies within the space spanned by the eigenvectors of the multiple representative previously scanned objects.
-Fig.~\ref{fig:diff_methods} shows the advantage of combining the global prior with the l1-ls form of CS.
+%Fig.~\ref{fig:diff_methods} shows the advantage of combining the global prior with the l1-ls form of CS.
 \subsection{\textbf{Contributions}}
@@
 The later scans are used to reveal the exact changes during and after burning of the tumor (ablation).
-In this context, we demonstrate the combined use of l1-ls (CS) with the global prior, in two flavors: the vanilla (unselective) and selective global prior-based reconstruction.
-The choice of the number of measurement views and the type of reconstruction -- unselective or selective, is driven by the goal of the procedure.
+In this context, we demonstrate the combined use of l1-ls (CS) with the global prior, in two flavors: the vanilla (uniform) and spatially-varying global prior-based reconstruction.
+The choice of the number of measurement views and the type of reconstruction -- uniform or spatially-varying, is driven by the goal of the procedure.
 
@@
 The choice of the number of measurement views and the type of reconstruction is driven by the goal in the application under consideration.
-When our goal is relatively simple, such as tracking the location of new changes while simultaneously reducing sub-sampling artefacts, we propose (a) acquiring measurements from a small number of views (`few-view' imaging) and using unselective prior based reconstruction.
-When our goal becomes more ambitious, such as observing details of the new changes while simultaneously reducing sub-sampling artefacts, we propose (b) acquiring measurements from a slightly higher number of views (`moderate-view' imaging) and using selective prior-based reconstruction.
+When our goal is relatively simple, such as tracking the location of new changes while simultaneously reducing sub-sampling artefacts, we propose (a) acquiring measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
+When our goal becomes more ambitious, such as observing details of the new changes while simultaneously reducing sub-sampling artefacts, we propose (b) acquiring measurements from a slightly higher number of views (`moderate-view' imaging) and using spatially-varying prior-based reconstruction.
 In either case, the number of views is lower than what is conventionally used.}
@@
 \begin{enumerate}
-\item Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using unselective prior based reconstruction.
+\item Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
 \item Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
-In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a selective prior-based reconstruction.
-The selective technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
+In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a spatially-varying prior-based reconstruction.
+The spatially-varying technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
 \end{enumerate}
@@
 
-This paper is organized as follows: Section~\ref{sec:tmh} demonstrates the utility of both the unselective and selective methods on a longitudinal medical dataset.
-Section~\ref{sec:unselective_global_prior} describes the construction of the unselective global eigenspace prior.
+This paper is organized as follows: Section~\ref{sec:tmh} demonstrates the utility of both the uniform and spatially-varying methods on a longitudinal medical dataset.
+Section~\ref{sec:uniform_global_prior} describes the construction of the uniform global eigenspace prior.
 In addition, we recap the advantages of global prior over dictionary priors.
-Section~\ref{sec:selective_prior} describes how the unselective prior needs to be modified when accurate details of new changes are to be observed.
-A selective technique offers a solution.
+Section~\ref{sec:spatially-varying_prior} describes how the uniform prior needs to be modified when accurate details of new changes are to be observed.
+A spatially-varying technique offers a solution.
 Results validated on both synthetic and real 3D biological datasets are shown.
@@
 \label{sec:tmh}
-Before diving into the details of the unselective and the selective global prior methods, we first show how both the techniques can be applied to our advantage in a real-life medical longitudinal study.
+Before diving into the details of the uniform and the spatially-varying global prior methods, we first show how both the techniques can be applied to our advantage in a real-life medical longitudinal study.
 Longitudinal studies here refers to the acquisition of sequential CT scans of the same subject to track time-evolving changes within the subject's interior.
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
-\subcaptionbox{Proposed\\ method: unselective prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
-\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) Filtered backprojection and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures, SSIM $=0.35$ and (d) unselective global prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
+\subcaptionbox{Proposed\\ method: uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
+\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) Filtered backprojection and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures, SSIM $=0.35$ and (d) uniform global prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
 The region enclosed in red rectangle is our RoI as it contains both the new position of the needle and some background.
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
-\subcaptionbox{Proposed\\ method: unselective\\ prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
-\subcaptionbox{Proposed\\ method: selective prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
+\subcaptionbox{Proposed\\ method: uniform\\ prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
+\subcaptionbox{Proposed\\ method: spatially-varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
 \subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
-\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) l1-ls with SSIM $=0.46$ and (d) unselective global prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) selective prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
+\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) l1-ls with SSIM $=0.46$ and (d) uniform global prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) spatially-varying prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
 The region enclosed in green rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
@@
 Hence, the needle can be tracked by acquiring measurements from a very small number of views.
-We use the unselective global prior reconstruction here to reduce the artefacts due to sub-sampling.
-The unselective method is fast and sufficient to track the position of the needle.
+We use the uniform global prior reconstruction here to reduce the artefacts due to sub-sampling.
+The uniform method is fast and sufficient to track the position of the needle.
 Once the needle reaches the site of the tumor, we propose changing the imaging protocol to acquire measurements from a moderate number of views.
 This will enable us to get more information about the new changes.
-In addition, we then deploy the selective prior method in order to locate the regions of new changes and penalize any dominance of the prior in these regions.
+In addition, we then deploy the spatially-varying prior method in order to locate the regions of new changes and penalize any dominance of the prior in these regions.
 Regardless of the imaging protocol we use (`few' or `moderate'), the number of views is smaller (atleast one-fifth) than the conventional number of views used in a standard hospital setting.
@@
 Fig.~\ref{fig:RFA2_few_views} shows the reconstructions of slice 8 by different methods.
-We see that the selective prior reconstruction brings in the advantage of the prior without it adversely affecting the new regions.
-
-%---------------------------------Unselective section---------------------
-\section{Method: unselective global prior-based reconstruction}
-\label{sec:unselective_global_prior}
-Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a global (unselective) prior-based reconstruction in Sec.~\ref{sec:unselective_global_prior}.
-This is followed by details of our technique in Sec.~\ref{sec:selective_prior}.
+We see that the spatially-varying prior reconstruction brings in the advantage of the prior without it adversely affecting the new regions.
+
+%---------------------------------Uniform section---------------------
+\section{Method: uniform prior-based reconstruction}
+\label{sec:uniform_global_prior}
+Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a global (uniform) prior-based reconstruction in Sec.~\ref{sec:uniform_global_prior}.
+This is followed by details of our technique in Sec.~\ref{sec:spatially-varying_prior}.
 Our method estimates the location and magnitude of new changes, and eventually prevents the prior from adversely affecting the reconstruction of new regions in the test.
-This, we refer to as a \textit{selective} global prior-based reconstruction routine.
+This, we refer to as a \textit{spatially-varying} global prior-based reconstruction routine.
 
@@
 
- \section{Resuls: Reconstruction by unselective prior}
+ \section{Results: Reconstruction by uniform prior}
 
@@
 \emph{Departing from this, we demonstrate reconstruction results from raw projection data.}
-In all figures in this section, `unselective prior' refers to optimizing Eq.~\ref{eq:selective_prior} with $\boldsymbol{W}(x,y,z)=1$.
+In all figures in this section, `uniform prior' refers to optimizing Eq.~\ref{eq:spatially-varying_prior} with $\boldsymbol{W}(x,y,z)=1$.
 %----------------------------------------------------------
@@
 \subsubsection{\textbf{Okra dataset}}
-\label{Sec:okra_unselective}
+\label{Sec:okra_uniform}
 Our first dataset is that of an Okra specimen consisting of its five scans (Fig.~\ref{fig:object-prior_test_okra}).
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
-\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
 \caption{3D reconstruction of the okra from $10\%$ projection
   views (b) has strong streak artefacts, (c) blurred, (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in ~\cite{supp_paper}.}
-\label{fig:okra_3D_results_unselective}
+\label{fig:okra_3D_results_uniform}
 \end{figure}
@@
 \hline
-                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} \\ \hline
+                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
 \textbf{full Volume} & 1 (ideal)                     & 0.87        &  0.92       & \textcolor{red}{0.95}                                                                                   \\ \hline
@@
 %\captionsetup{labelformat=empty}
-        \caption{Unselective Prior}
+        \caption{Uniform Prior}
      \end{subfigure}
@@
 \hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} \\ \hline
+                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
 \textbf{Full volume}   & 1 (ideal)                    & 0.82        & 0.71       & \textcolor{red}{0.92}                                                                                                                       \\ \hline
@@
 %----------------------------------------------------------------------
-\section{Method:Selective prior-based reconstruction}
-\label{sec:selective_prior}
-
-Although the unselective global prior can be very useful in some circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a major limitation when we want accurate details of the new changes.
-While the unselective prior compensates very well for the possible artefacts due to sparse measurements, it dominates the regions with new changes masking the signal, as seen in Fig.~\ref{fig:RFA2_few_views}-d.
+\section{Method: Spatially-Varying prior-based reconstruction}
+\label{sec:spatially-varying_prior}
+
+Although the uniform global prior can be very useful in some circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a major limitation when we want accurate details of the new changes.
+While the uniform prior compensates very well for the possible artefacts due to sparse measurements, it dominates the regions with new changes masking the signal, as seen in Fig.~\ref{fig:RFA2_few_views}-d.
 Ideally, we will want to impose the prior only in the regions that are common between the test and object-prior.
-Our selective prior based reconstruction overcomes this limitation by minimizing the following cost function:
+Our spatially-varying prior based reconstruction overcomes this limitation by minimizing the following cost function:
 \begin{equation}
@@
 J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
-\label{eq:selective_prior}
+\label{eq:spatially-varying_prior}
 \end{equation}
@@
  matrix $\boldsymbol{W}$, where $W_{ii}$ contains the (non-negative) weight assigned to the $i^{\textrm{th}}$ voxel of the prior.
-$\boldsymbol{W}$ is first constructed using some preliminary reconstruction methods (to be described in the following section), following which Eq.~\ref{eq:selective_prior} is used to obtain the final reconstruction.
+$\boldsymbol{W}$ is first constructed using some preliminary reconstruction methods (to be described in the following section), following which Eq.~\ref{eq:spatially-varying_prior} is used to obtain the final reconstruction.
 In regions of change in test data, we want lower weights for the prior when compared to regions that are similar to the prior.
@@
 We found that our final reconstruction results obtained by
-solving Eq.~\ref{eq:selective_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
+solving Eq.~\ref{eq:spatially-varying_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
 %-------------------------------------------
@@
 The magnitude and sharpness of the artefacts is different for each method.
-(g) Selective-prior method that combines weights-map information from all other methods.
+(g) Spatially-Varying-prior method that combines weights-map information from all other methods.
 The SSIM of these reconstructions is shown in Table.~\ref{table:potato_2D_ssim}.}
@@
 %----------------------------------------Results-----------------------
-\section{Results: Reconstruction by selective prior}
+\section{Results: Reconstruction by spatially-varying prior}
 \label{sec:results}
@@
 The proposed method has been validated on 2D and 3D synthetic and real tomographic data of biological and medical specimens.
-The results below demonstrate the advantage of the selective global prior method over the unselective method.
+The results below demonstrate the advantage of the spatially-varying global prior method over the uniform method.
 
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
-\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/prior_weighted_cropped.png}}
+\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/prior_weighted_cropped.png}}
 \caption{3D reconstruction of the okra from $10\%$ projection
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/CS_cropped.png}}\hfill
-\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/weighted_prior_cropped.png}}
+\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/weighted_prior_cropped.png}}
 \caption{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
@@
 \hline
-                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
+                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior + l1-ls\end{tabular}} \\ \hline
 \textbf{red RoI}   & 1 (ideal)                     & 0.74        & 0.84       & 0.86                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
@@
 %\captionsetup{labelformat=empty}
-        \caption{Unselective Prior}
+        \caption{Uniform\\ Prior}
      \end{subfigure}
@@
 %\captionsetup{labelformat=empty}
-        \caption{Selective prior}
-     \end{subfigure}
+        \caption{Spatially-Varying\\ prior}
+    \end{subfigure}
+    %\quad
      \caption{3D reconstruction of sprouts from $2.5\%$ projection views
@@
               \subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_marked.png}}\hfill
-                \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_marked.png}}\hfill
-\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_marked.png}}
+                \subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_marked.png}}\hfill
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_marked.png}}
 \caption{Zoomed-in portion $(41 \times 36)$ containing the RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods.
-The images of the bottom row are the same as repective images of the top row, with regions marked additionally.
+The images of the bottom row are the same as respective images of the top row, with regions marked additionally.
 (a) the test showing 3 distinct structures (in red here) (b) 3 structures recovered with poor contrast, (c) structures indistinguishable, (d) only two strong structures seen and (e) there is a hint of a third structure too with better contrast.}
@@
 \hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\ \hline
+                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior + l1-ls\end{tabular}} \\ \hline
 \textbf{red RoI}   & 1 (ideal)                     & 0.85        & 0.84       & 0.83                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
@@
 Slice t=1 & Very far from tumor & 360 & l1-ls \\ \hline
-Slice t=2 & Sufficiently far from tumor & 40 & Unselective \\ \hline
-Slice t=3 & Far from tumor & 50 & Unselective \\ \hline
-Slice t=4 & Near tumor & 60 & Unselective \\ \hline
-Slice t=5 & Sufficiently near tumor & 70 & Unselective \\ \hline
-Slice t=6 & Very near tumor & 80 & Unselective \\ \hline
-Slice t=7 & Very near tumor & 90 & Unselective \\ \hline
-Slice t=8 & During, after ablation & 120 & Selective \\ \hline
+Slice t=2 & Sufficiently far from tumor & 40 & Uniform \\ \hline
+Slice t=3 & Far from tumor & 50 & Uniform \\ \hline
+Slice t=4 & Near tumor & 60 & Uniform \\ \hline
+Slice t=5 & Sufficiently near tumor & 70 & Uniform \\ \hline
+Slice t=6 & Very near tumor & 80 & Uniform \\ \hline
+Slice t=7 & Very near tumor & 90 & Uniform \\ \hline
+Slice t=8 & During, after ablation & 120 & Spatially-Varying \\ \hline
 \end{tabular}\hspace*{-1cm}
@@
 \label{sec:discussion}
-The presented unselective prior-based algorithm is suited to applications where we wish to detect the location of new changes in an object over time, and the presented selective prior-based algorithm is suited to applications where we wish to observe the intricate details of those new changes.
+The presented uniform prior-based algorithm is suited to applications where we wish to detect the location of new changes in an object over time, and the presented spatially-varying prior-based algorithm is suited to applications where we wish to observe the intricate details of those new changes.
 This distinction in the techniques used has not been studied earlier in literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our knowledge.
@@
 \hline
-   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior + l1-ls\end{tabular}} \\\hline
-\textbf{Potato, 45 views}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
-\textbf{Okra}  &  &   &  &  \\ \hline
-\textbf{Sprouts}  &  &   &  &  \\ \hline
+   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Spatially-Varying\\prior + l1-ls\end{tabular}} \\\hline
+%\textbf{\begin{tabular}[c]{@{}c@{}}Potato\\size:(150,150,100)\\45 views\end{tabular}}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338,338,123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 27 min. \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130,130,130)\\xx views\end{tabular}}  &  &   &  &  \\ \hline
 \end{tabular}
@@
 In contrast, the results from l1-ls and our method progressively improve when compared to FDK as the RoIs get bigger.
-Hence, in practice, one may choose FDK for the case of simple, homogeneous dataset with smaller RoI,  and prefer selective prior-based reconstruction when the dataset is complex and RoIs are larger.
+Hence, in practice, one may choose FDK for the case of simple, homogeneous dataset with smaller RoI,  and prefer spatially-varying prior-based reconstruction when the dataset is complex and RoIs are larger.
 %---------------------------------------
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm_new.png}}\hfill
-\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
-\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
+\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
 \caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts.
@@
 \hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior\\+ l1-ls\end{tabular}} \\ \hline
+                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Spatially-Varying\\prior\\+ l1-ls\end{tabular}} \\ \hline
 \textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.94}        & 0.88      & 0.71                                                               & 0.85                                                            \\ \hline
@@
 Finally, the hyper-parameter $k$ defines the sensitivity of the weights map to the difference between the test image and the prior (projection of test onto the space of object-prior).
-When $k=0$, our method converges to the unselective prior method.
+When $k=0$, our method converges to the uniform prior method.
 As $k$ increases, the weights map starts capturing the new changes in the test, at the cost of detecting a few false positives i.e.
@@
 This work deals with the effective use of priors for tomographic reconstruction in longitudinal studies.
-We show that we can either use the unselective global prior method or the selective prior method to our advantage, depending on our goal.
+We show that we can either use the uniform global prior method or the spatially-varying prior method to our advantage, depending on our goal.
 We establish the context under which these methods can be used, as outlined in Fig.~\ref{fig:prior_overview}.
-When we wish to approximately know the location of new changes, we apply an unselective prior because it is fast and sufficient for the task at hand.
+When we wish to approximately know the location of new changes, we apply an uniform prior because it is fast and sufficient for the task at hand.
 We also choose a smaller number of views in order to reduce radiation.
 In addition, we show that when our goal shifts to observing the details of the new changes accurately, we acquire projections from a moderate number of views in order to capture more information.
-We further combine this with the somewhat slower but more accurate technique of reconstruction-- the selective prior-based method.
+We further combine this with the somewhat slower but more accurate technique of reconstruction-- the spatially-varying prior-based method.
 This method ensures that the reconstruction of localized new information in the data is not affected by the priors.

### 2020-07-03 paper/tci.tex
Introduction, Related work rewritten

@@
 \usepackage{xcolor}
+\usepackage[sort&compress]{natbib}
 
@@
 We are thus able to effectively reconstruct both the old and the new structures in the test.
-We have tested the efficacy of our method on synthetic as well as real volume data.
+We have tested the efficacy of our method on synthetic as well as real projection data.
 The results demonstrate the use of both uniform and spatially-varying priors in different scenarios.
@@
 Computed Tomography (CT) deals with the recovery of an entire object from a limited set of projection data which are acquired by passing X-rays at different orientations (`views') through the object.
-In order to minimize the radiation exposed to the subject, current research seeks to either significantly reduce the radiation intensity required to reconstruct with adequate fidelity~\cite{gopal2019low} or significantly reduce the number of measurements required to reconstruct with adequate fidelity.
-In this regard, there are two lines of pursuit.
-One is to intelligently choose those sets of projection views that capture most information~\cite{King2018,Anthony2018,barkan17,fischer16,andrei14}, and the other is to improve the reconstruction algorithms to get the most accurate recovery of the underlying slice, given the measurements from any limited set of views~\cite{yang2018,geyer2015,kilic2011}.
-This paper deals with the latter scenario.
-
-In this context, measurements in conventional data acquisition techniques are acquired by sampling the physical object uniformly above the Nyquist rate.
-In such a case when there are sufficient measurements, reconstruction using the conventional filtered backprojection (FBP) suffices, as seen in Fig.~\ref{fig:story1}.
-However, in the last decade, reconstruction from sub-Nyquist sampled data has been made possible due to methods such as the widely used Compressed Sensing (CS) technique~\cite{Donoho,introCS}, which assumes the data to exhibit properties such as sparsity of the underlying image under certain mathematical transforms such as the Discrete Cosine Transform (DCT) or wavelet transforms.
-Fig.~\ref{fig:story2} shows how reconstruction using CS routine is better than FBP for sub-Nyquist number of views.
-Here, among the many optimizers used in CS, we have used the l1-regularized least squares (l1-ls) form and observed that although this optimizer removes most of the artefacts created due to sub-sampling, its reconstruction is blurred when the number of views is very limited, as shown in Fig.~\ref{fig:story2}.
-Specifically, the reconstruction in Fig.~\ref{fig:story2-CS} and~\ref{fig:story3-CS} is obtained by minimizing the following cost using the solver in~\cite{l1ls}:
+It is preferable to minimize the radiation exposed to the object, in order to prevent any potential damage to it and in order to fasten the acquisition time.
+Therefore, current research seeks to either significantly reduce the radiation intensity required to reconstruct with adequate fidelity~\cite{yang2018,Lin2016,Xie2017,gopal2019low} or significantly reduce the number of measurements required to reconstruct with adequate fidelity.
+For the latter case, there are two lines of pursuit.
+One is to intelligently choose those sets of projection views that capture most information~\cite{King2018,Anthony2018,barkan17,fischer16,andrei14}, and the other, which is the focus of this paper, is to design the reconstruction algorithm in order to achieve the most accurate recovery of the underlying slice, given the measurements from any limited set of views~\cite{yang2018,geyer2015,kilic2011}.
+
+In conventional data acquisition techniques, the tomographic measurements $\boldsymbol{y}$ are acquired by sampling the physical object $\boldsymbol{x}$ uniformly above the Nyquist rate.
+In such a case when there are sufficient measurements, reconstruction using the conventional filtered backprojection (FBP) suffices, as seen in Fig.~\ref{fig:story} (600 views case).
+However, in the last decade, reconstruction from limited sampled data has been made possible by assuming the data to exhibit sparsity under certain mathematical transforms $\boldsymbol{\Upsilon}$ such as the Discrete Cosine Transform (DCT) or wavelet transforms.
+This is known as sparsity prior and is the fundamental principle in the widely used Compressed Sensing (CS) technique~\cite{Donoho,introCS}.
+Fig.~\ref{fig:story} demonstrates the benefit of using sparsity prior when the number of projection views is limited (100 views in Fig.~\ref{fig:story}).
+
+There are multiple ways to incorporate the sparsity prior using CS.
+We use the LASSO (least absolute shrinkage and selection operator) which iteratively solves for the solution by penalizing a combination of least squares error and l1-norm of the sparse coefficients $\boldsymbol{\theta}$ of the object $\boldsymbol{x}$.
+If $\boldsymbol{\mathcal{R}}$ represents the acquisition model, then the LASSO solution is described by one that minimizes:
+
  \begin{equation}
-J_{CS}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
+J_{CS}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1.
 \label{Eq:simple_cs}
  \end{equation}
-Here, $\boldsymbol{x} = \boldsymbol{\Upsilon\theta}$ denotes the reconstructed volume, $\boldsymbol{y}$ its measured tomographic projections, $\boldsymbol{\mathcal{R}}$ the tomographic projection operator such that ideally $\boldsymbol{y} = \boldsymbol{\mathcal{R} x}$, and $\boldsymbol{\theta}$ the sparse coefficients of $\boldsymbol{x}$.
-$\boldsymbol{\Upsilon}$ is the basis in which $\boldsymbol{x}$ is assumed to be sparse, and is chosen to be DCT here.
-In addition to this sparsity prior, when object specific prior information is  used as well, the reconstruction improves significantly.
-The algorithm presented in~\cite{Essam2015} drew inspiration from CS and solved for the reconstruction from limited views using alternating direction method of multipliers.
-In other techniques like in~\cite{Polak2017}, reconstruction is performed by estimating sparse gradients in the data.
-In~\cite{Li2015}, the required number of views is reduced by minimizing the total variation in the data.
-The measurements and an initial estimate of the data guide the iterative routines.
-
-\begin{figure}[!h]
+
+ We solve this cost function using the popular l1-regularized least squares (l1-ls) package available in~\cite{l1ls}.
+We also choose DCT as our sparsity basis $\boldsymbol{\Upsilon}$.
+We observed that there was no significant benefit in choosing wavelets over DCT.
+ \begin{figure}[h]
 \centering
-    \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/story/testIm.png}
-        \caption{Test}
-        \label{fig:story1-test}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/story/600_views/fbp.png}
-        \caption{FBP, no prior}
-        \label{fig:1000_views_fbp}
-    \end{subfigure}
-    %\begin{subfigure}[b]{0.23\linewidth}
-     %   \includegraphics[width=\textwidth]{../images/story/600_views/CS_lambda0_0.00.png}
-     %   \caption{Least squares}
-     %\end{subfigure}
-    \caption{Reconstruction from large number of views (600 views); (a) 2D test slice of size [260, 260] (b) FBP reconstruction (SSIM = 0.92).}% (c) Least squares reconstruction (SSIM = 0.99).}
-\label{fig:story1}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-    %\begin{subfigure}[b]{0.23\linewidth}
-     %   \includegraphics[width=\textwidth]{../images/story/testIm.png}
-      %  \caption{Test}
-     %\end{subfigure}
-    \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/story/100_views/fbp.png}
-        \caption{FBP, no prior}
-        \label{fig:1000_views_fbp}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/story/100_views/CS_lambda0_2.00.png}
-        \caption{sparsity prior}
-        \label{fig:story2-CS}
-     \end{subfigure}
-    \caption{Reconstruction of Fig.~\ref{fig:story1-test} from sub-Nyquist number of views (100 views); (a) FBP reconstruction (SSIM = 0.83) (b) l1-ls reconstruction (SSIM = 0.90).}
-\label{fig:story2}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-    %\begin{subfigure}[b]{0.23\linewidth}
-     %   \includegraphics[width=\textwidth]{../images/story/testIm.png}
-      %  \caption{Test}
-     %\end{subfigure}
-    \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/story/40_views/fbp.png}
-        \caption{FBP,\\ no prior}
-        \label{fig:1000_views_fbp}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/story/40_views/CS_lambda0_3.00.png}
-        \caption{sparsity \\prior}
-        \label{fig:story3-CS}
-    \end{subfigure}
-    \quad
-        \begin{subfigure}[b]{0.23\linewidth}
-        \includegraphics[width=\textwidth]{../images/story/40_views/plain_pca.png}
-        \caption{sparsity \\+ object prior}
-     \end{subfigure}
-    \caption{Reconstruction of Fig.~\ref{fig:story1-test} from sub-sub-Nyquist number of views (40 views); (a) FBP reconstruction (SSIM = 0.74) (b) l1-ls reconstruction (SSIM = 0.84) (c) prior-based reconstruction (SSIM = 0.85).}
-\label{fig:story3}
-\end{figure}
-
-In addition, when some extra information about the object's structure is known~\cite{PICCS,cardiacPICCS,lubner2011,pirple,mota2017}, it is beneficial in further reducing the number of measurements.
-As seen in Fig.~\ref{fig:story3}, the use of object prior further improves the reconstruction when the number of views is far below the Nyquist criterion.
-The prior-based techniques use information from previously scanned data (`object-prior') of the same object or a similar one, and utilize it to reconstruct new volumes from very few sets of additional measurements.
-However, the above methods have the following two limitations: (1) the prior information may potentially overwhelm the essential details that appear in the test, (2) there is the key issue of choice of \textit{a particular} previously scanned object among the many previously acquired scans.
-A large part of this paper is dedicated to alleviating the former limitation, which is an important issue that has so far been overlooked in the literature on tomography.
-The latter limitation was relaxed in~\cite{liu2016,Xu2012} by building dictionary-based priors from multiple previously scanned objects.
+	\includegraphics[width=0.4\textwidth]{../images/story/story.png}
+        \caption{Illustration of the use of various priors as the number of views reduces.
+For large number of views (600 views), the FBP reconstruction is of good quality (SSIM = 0.92.
+As the number of views become limited (100 views), the reconstruction using sparsity prior (SSIM = 0.90) is better than FBP reconstruction (SSIM = 0.83).
+If the number of views is further reduced (40 views), the presence of both sparsity prior and object improves the reconstruction (SSIM = 0.85) when compared to presence of only sparsity prior (SSIM = 0.84) or no prior (SSIM = 0.74).}
+ \label{fig:story}
+ \end{figure} 
+ When the number of views is significantly less, the sparsity prior alone is not sufficient, as seen in Fig.~\ref{fig:story} for the case of 40 views.
+In such cases, any additional information, specifc to the object being scanned (i.e., object prior) is useful in further improving the reconstruction.
+Such techniques may also use information from previously scanned data of the same object or a similar one.
+However, with the use of such an object prior, a new challenge emerges:  the prior information may potentially overwhelm the essential new details that appear in the test.
+It is in this context that the work in this paper fits in: the design of an algorithm that estimates the location and magnitude of new changes in the (unknown) test object.
+This eventually prevents the prior from adversely affecting the reconstruction of new regions in the test.
+We refer to this as a \textit{spatially-varying} uniform prior-based reconstruction routine.
+We present results on real and simulated 3D data for different longitudinal studies.
+These are studies wherein sequential CT scans of the same object are acquired to track time-evolving changes within its interior.
+
+  %although this optimizer removes most of the artefacts created due to sub-sampling, its reconstruction is blurred when the number of views is very limited, as shown in Fig.~\ref{fig:story2}. 
+%(2) there is the key issue of the choice of \textit{a particular} previously scanned object as template among the many previously acquired scans
+ \section{Related Work}
+ Most of the related work for object-prior based reconstruction has been in the areas of dynamic CT and 4D-CT.
+In dynamic CT, the object being scanned undergoes changes between successive projection views and hence is not stationary even within a single complete scan.
+In 4D-CT, the object undergoes changes between successive scans.
+In both these cases, it may be possible to use very specific object-properties for reconstruction.
+For example, in~\cite{Van2015}, the knowledge of attenuation coefficient of the fluid was used as a prior for reconstructing its flow through gravel.
+In~\cite{Koen2020}, the changes across the sucessive scan volumes is assumed to be continuous, thus enabling the use of optical flow to model the motion between corresponding voxels of different scan volumes.
+In another study~\cite{vincent2017}, changes between successive scans were modelled by affine deformation whose parameters were computed for motion-correction.
+Such a correction enables acquisition from fewer views than would have otherwise not been possible for reconstruction with adequate fidelity.
+In~\cite{daniil2015}, all the scan volumes are reconstructed together using spatio-temporal regularization.
+Unlike these methods, if however, the object-prior were not available in the first place, then other techniques presented in~\cite{Essam2015,Polak2017} and~\cite{Li2015} could be used for the reconstruction of a single volume from few projection views.
+
+ In contrast to the prior-based studies mentioned above, we reconstruct the current test object without any assumption of continuity of changes or some knowledge of the attenuation coefficients of the structures.
+We use the current measurements from few-views and previous high-quality scans of the same object.
+We utilize the uniform global eigenspace prior presented in~\cite{my_dicta_paper} which assume that the new test volume lies within the space spanned by the eigenvectors of the multiple representative previously scanned objects.
+We then demonstrate how the global prior can impose an inflexible constant weight (and hence a bias) when reconstructing the data.
+As a solution, we present a method to moderate the control of the prior by estimating and imposing spatially-varying weights to the prior in order to reconstruct new structures accurately.
+This spatially-varying prior tunes the effect of the templates in different regions of the reconstruction.
+
+ %Various forms of object priors have been used for reconstruction from limited views (`few-views').
+In ~\cite{Van2014}, the time-varying region within an object is computed by modelling it as a B-spline.
+% \cite{PICCS} uses only a single template and enforces a uniform similarity between the current object's reconstruction and the single template. 
+%In addition, when some extra information about the object's structure is known~\cite{PICCS,cardiacPICCS,lubner2011,pirple,mota2017},   %The latter limitation was relaxed in~\cite{liu2016,Xu2012} by building dictionary-based priors from multiple previously scanned objects.
 However, as reported in~\cite{my_dicta_paper}, dictionary priors are not as accurate and fast as global eigenspace priors.
-Global eigenspace priors are better able to exploit the similarity of a test volume to object-prior, by assuming that the new test volume lies within the space spanned by the eigenvectors of the multiple representative previously scanned objects.
-%Fig.~\ref{fig:diff_methods} shows the advantage of combining the global prior with the l1-ls form of CS.
-\subsection{\textbf{Contributions}}
-\label{sec:contributions}
-In this work (Fig.~\ref{fig:prior_overview}), we focus on further reducing the number of measurements, with  particular emphasis on longitudinal studies.
-For example, we consider medical datasets which consist of multiple CT scans being taken during a radio-frequency ablation procedure~\cite{Dong2015}.
-The process consists of inserting a needle probe into a patient's body.
-When the needle reaches the tumor site, an electric current is passed to burn the tumor.
-Repeated CT scans of the patient need to be acquired in order to visualize the movement of the needle and to ensure that it is reaching the appropriate target.
-A few initial densely-sampled scans are used as object-prior to help the physician know the position of the needle.
-The later scans are used to reveal the exact changes during and after burning of the tumor (ablation).
-In this context, we demonstrate the combined use of l1-ls (CS) with the global prior, in two flavors: the vanilla (uniform) and spatially-varying global prior-based reconstruction.
-The choice of the number of measurement views and the type of reconstruction -- uniform or spatially-varying, is driven by the goal of the procedure.
 
@@
 
-\begin{enumerate}
-\item Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
-\item Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
-In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a spatially-varying prior-based reconstruction.
-The spatially-varying technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
-\end{enumerate}
-
-After the results of the above study are presented, the remainder of this paper discusses each of the above two approaches in detail.
-Specifically, we discuss how the global prior can impose an inflexible constant weight (and hence a bias) when reconstructing the data.
-If we want to observe details, this bias can be removed by moderating the control of the prior by imposing spatially varying weights to the prior.
-
 This paper is organized as follows: Section~\ref{sec:tmh} demonstrates the utility of both the uniform and spatially-varying methods on a longitudinal medical dataset.
-Section~\ref{sec:uniform_global_prior} describes the construction of the uniform global eigenspace prior.
-In addition, we recap the advantages of global prior over dictionary priors.
-Section~\ref{sec:spatially-varying_prior} describes how the uniform prior needs to be modified when accurate details of new changes are to be observed.
+Section~\ref{sec:method_uniform_prior} describes the construction of the uniform eigenspace prior, followed by the corresponding results in real and synthetic 3D biological datasets in Section~\ref{sec:results_uniform_prior}.
+Section~\ref{sec:method_spatially_varying_prior} describes how the uniform prior needs to be modified when accurate details of new changes are to be observed.
 A spatially-varying technique offers a solution.
-Results validated on both synthetic and real 3D biological datasets are shown.
+The results are presented in Section~\ref{sec:results_spatially_varying_prior}.
+Section\ref{sec:discussion} discusses tuning of the hyperparameters involved, and a special case of reconstruction.
 Finally, we conclude  with key inferences that can be drawn from our work in Section~\ref{sec:conclusions}.
@@
 Before diving into the details of the uniform and the spatially-varying global prior methods, we first show how both the techniques can be applied to our advantage in a real-life medical longitudinal study.
-Longitudinal studies here refers to the acquisition of sequential CT scans of the same subject to track time-evolving changes within the subject's interior.
 Here, our data~\footnote{Source: Tata Memorial Centre~\cite{tmh}, Parel, Mumbai.
-This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of successive scans of the liver taken during a radio-frequency ablation procedure described in the previous section.
-In such a procedure, the physician inserts a thin needle-like probe into the organ~\cite{rfa}.
-Once the needle hits the tumor, a high-frequency current is passed through the tip of the probe and this burns the malignant tumor.
-Throughout this process, multiple CT scans help the physician to track the position of the needle and check the changes within.
+This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of successive scans of the liver taken during a radio-frequency ablation procedure.
+In such a procedure~\cite{Dong2015}, the physician inserts a thin needle-like probe into the organ.
+Repeated CT scans of the patient need to be acquired in order to track the movement of the needle and to ensure that it is reaching the appropriate target tumor.
+Once the needle hits the tumor, a high-frequency electric current is passed through the tip of the probe and this burns the malignant tumor (ablation).
+The scan at this ablation stage must also reveal accurate details of the changes within.
 In this context, we classify the goal of any of our reconstruction techniques into two categories:
@@
 \begin{enumerate}
-\item To track the position of the needle in a relatively well reconstructed background.
-\item To accurately observe the new changes amidst a relatively well reconstructed background after the needle touches the tumor.
+\item To track the position of the needle in a relatively well-reconstructed background.%Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
+\item To accurately observe the new changes amidst a relatively well reconstructed background after the needle touches the tumor.%Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
+In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a spatially-varying prior-based reconstruction.
+The spatially-varying technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
 \end{enumerate} 
-
-The needle has a very high attenuation coefficient when compared to that of the organs.
-Hence, the needle can be tracked by acquiring measurements from a very small number of views.
+Here, we demonstrate the combined use of l1-ls (CS) with the global prior, in two flavors: the vanilla (uniform) and spatially-varying global prior-based reconstruction.
+The choice of the number of measurement views and the type of reconstruction -- uniform or spatially-varying, is driven by the goal of the procedure.
+First, in order to track the needle, a very small number of views is sufficient because the needle has a very high attenuation coefficient when compared to that of the organs.
 We use the uniform global prior reconstruction here to reduce the artefacts due to sub-sampling.
@@
 \section{Method: uniform prior-based reconstruction}
-\label{sec:uniform_global_prior}
-Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a global (uniform) prior-based reconstruction in Sec.~\ref{sec:uniform_global_prior}.
-This is followed by details of our technique in Sec.~\ref{sec:spatially-varying_prior}.
-Our method estimates the location and magnitude of new changes, and eventually prevents the prior from adversely affecting the reconstruction of new regions in the test.
-This, we refer to as a \textit{spatially-varying} global prior-based reconstruction routine.
-
+\label{sec:method_uniform_prior}
+Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform (global) prior-based reconstruction.
 Principal Component Analysis (PCA) has been traditionally used to find the significant modes of (Gaussian corrupted) data.
@@
  \section{Results: Reconstruction by uniform prior}
+ \label{sec:results_uniform_prior}
 
@@
 \section{Method: Spatially-Varying prior-based reconstruction}
-\label{sec:spatially-varying_prior}
+\label{sec:method_spatially_varying_prior}
 
@@
 \section{Results: Reconstruction by spatially-varying prior}
-\label{sec:results}
+\label{sec:results_spatially_varying_prior}
 

### 2020-07-08 paper/tci.tex
Different Fig.1

@@
 As the number of views become limited (100 views), the reconstruction using sparsity prior (SSIM = 0.90) is better than FBP reconstruction (SSIM = 0.83).
-If the number of views is further reduced (40 views), the presence of both sparsity prior and object improves the reconstruction (SSIM = 0.85) when compared to presence of only sparsity prior (SSIM = 0.84) or no prior (SSIM = 0.74).}
+If the number of views is further reduced (30 views), the presence of both sparsity prior and object improves the reconstruction (SSIM = 0.85) when compared to presence of only sparsity prior (SSIM = 0.82) or no prior (SSIM = 0.69).}
  \label{fig:story}
  \end{figure} 
- When the number of views is significantly less, the sparsity prior alone is not sufficient, as seen in Fig.~\ref{fig:story} for the case of 40 views.
+ When the number of views is significantly less, the sparsity prior alone is not sufficient, as seen in Fig.~\ref{fig:story} for the case of 30 views.
 In such cases, any additional information, specifc to the object being scanned (i.e., object prior) is useful in further improving the reconstruction.
@@
 
-This paper is organized as follows: Section~\ref{sec:tmh} demonstrates the utility of both the uniform and spatially-varying methods on a longitudinal medical dataset.
+This paper is organized as follows: Section~\ref{sec:contributions} lays down the key contributions of this work.
+Section~\ref{sec:tmh} demonstrates the utility of both the uniform and spatially-varying methods on a longitudinal medical dataset.
 Section~\ref{sec:method_uniform_prior} describes the construction of the uniform eigenspace prior, followed by the corresponding results in real and synthetic 3D biological datasets in Section~\ref{sec:results_uniform_prior}.
 Section~\ref{sec:method_spatially_varying_prior} describes how the uniform prior needs to be modified when accurate details of new changes are to be observed.
-A spatially-varying technique offers a solution.
-The results are presented in Section~\ref{sec:results_spatially_varying_prior}.
-Section\ref{sec:discussion} discusses tuning of the hyperparameters involved, and a special case of reconstruction.
+A spatially-varying technique offers a solution, the results of which are presented in Section~\ref{sec:results_spatially_varying_prior}.
+Section\ref{sec:discussion} discusses tuning of the hyperparameters involved, and limitations of our method.
 Finally, we conclude  with key inferences that can be drawn from our work in Section~\ref{sec:conclusions}.
+\section{Contributions}
+\label{sec:contributions}
+This paper focusses on few-views reconstruction for longitudinal studies, and has the following key contributions:
+\begin{itemize}
+\item The scenarios where a uniform object prior is sufficient for the application at hand, and the scenarios for which it will fail, are demonstrated.
+\item A weights map is designed to depict the location and strength of new changes at every voxel.
+A novel algorithm is presented to build this map from sub-sampled measurements of the test and a set of high quality templates.
+Once the weights map is built, it is used for accurate reconstruction of those changes in the test that are absent in all of the templates.
+\item Finally, the methods are validated  on real and syntheric 3D tomographic data of biological datasets from various longitudinal studies, and quatitative accuracies are presented using the Structural Similarity Index Metric (SSIM).
+ \end{itemize}
 
@@
 Fig.~\ref{fig:RFA2_very_few_views} shows the reconstruction of slice 7 from its measurements from only 90 views.
-The reconstructions are quantitatively compared using the Structural Similarity Index Metric (SSIM).\\
+The reconstructions are quantitatively compared using SSIM.\\
 

### 2020-07-09 paper/tci.tex
updated the intro, flow

@@
 \usepackage{xcolor}
-\usepackage[sort&compress]{natbib}
+%\usepackage[sort&compress]{natbib}
 
@@
 \begin{abstract}
-Tomographic reconstruction from undersampled measurements is a necessity when the measurement process is potentially harmful, needs to be rapid, or is resource-expensive.
-In such cases, information from previously existing longitudinal scans of the same object (forming the `object-prior'), helps in the reconstruction of the current object (`test') while requiring significantly fewer updating measurements.
-In this work, we improve the state of the art by proposing the context under which priors can be effectively used based on the final goal of the application at hand.
-
-Our work is based on longitudinal data acquisition scenarios where we wish to study new changes that evolve within an object over time, such as in repeated scanning for disease monitoring, or in tomography-guided surgical procedures.
-While this is easily feasible when measurements are acquired from a large number of projection angles (referred to as `views' henceforth), it is challenging when the number of views is limited.
-If the goal is to track the changes while simultaneously reducing sub-sampling artefacts, we propose (1) acquiring measurements from a \emph{small} number of views and using a global \emph{`uniform'} prior based reconstruction.
-If the goal is to observe \emph{details} of new changes, we propose (2) acquiring measurements from a \emph{moderate} number of views and using a more involved reconstruction routine.
-We show that in the latter case, a `spatially-varying' technique is necessary in order to prevent the prior from adversely affecting the reconstruction of new structures that are absent in any of the earlier scans.
-The reconstruction of new regions is safeguarded from the bias of the prior by computing regional weights that moderate the local influence of the priors.
-We are thus able to effectively reconstruct both the old and the new structures in the test.
-We have tested the efficacy of our method on synthetic as well as real projection data.
-The results demonstrate the use of both uniform and spatially-varying priors in different scenarios.
-Our methods significantly improve the overall quality of the reconstructed data while minimizing the number of measurements needed for imaging in longitudinal studies.
+  Tomographic reconstruction from undersampled measurements is a
+  necessity when the measurement process is potentially harmful, needs
+  to be rapid, or is resource-expensive. In such cases, information
+  from previously existing longitudinal scans of the same object
+  (`object-prior'), helps in the reconstruction from the current
+  measurements of that object (`test'), while requiring significantly
+  fewer updating measurements. In this work, we improve the state of
+  the art by proposing the context under which priors can be
+  effectively used based on the final goal of the application at hand.
+
+  Our work is based on longitudinal data acquisition scenarios where
+  we wish to study new changes that evolve within an object over time,
+  such as in repeated scanning for disease monitoring, or in
+  tomography-guided surgical procedures. While this is easily feasible
+  when measurements are acquired from a large number of projection
+  angles (`views'), it is challenging when the number of views is
+  limited.
+
+  If the goal is to track the changes while simultaneously reducing
+  sub-sampling artefacts, we propose (1) acquiring measurements from
+  an \emph{extremely small} number of views and using a global
+  \emph{`uniform'} prior-based reconstruction. If the goal is to
+  observe \textbf{details} of new changes, we propose (2) acquiring
+  measurements from a \emph{moderate} number of views (albeit, still
+  sub-Nyquist), and using a more involved reconstruction routine. We
+  show that in the latter case, a `spatially-varying' technique is
+  appropriate in order to prevent the prior from adversely affecting the
+  reconstruction of new structures that are absent in any of the
+  earlier scans. The reconstruction of new regions is safeguarded from
+  the bias of the prior by computing regional weights that moderate
+  the local influence of the priors. We are thus able to effectively
+  reconstruct both the old and the new structures in the test. We have
+  tested the efficacy of our method on synthetic as well as real
+  projection data. The results demonstrate the use of both uniform and
+  spatially-varying priors in different scenarios. Our methods
+  significantly improve the overall quality of the reconstructed data
+  while minimizing the number of measurements needed for imaging in
+  longitudinal studies.
 \end{abstract}
@@
 \label{sec:intro}
-Computed Tomography (CT) deals with the recovery of an entire object from a limited set of projection data which are acquired by passing X-rays at different orientations (`views') through the object.
-It is preferable to minimize the radiation exposed to the object, in order to prevent any potential damage to it and in order to fasten the acquisition time.
-Therefore, current research seeks to either significantly reduce the radiation intensity required to reconstruct with adequate fidelity~\cite{yang2018,Lin2016,Xie2017,gopal2019low} or significantly reduce the number of measurements required to reconstruct with adequate fidelity.
-For the latter case, there are two lines of pursuit.
-One is to intelligently choose those sets of projection views that capture most information~\cite{King2018,Anthony2018,barkan17,fischer16,andrei14}, and the other, which is the focus of this paper, is to design the reconstruction algorithm in order to achieve the most accurate recovery of the underlying slice, given the measurements from any limited set of views~\cite{yang2018,geyer2015,kilic2011}.
-
-In conventional data acquisition techniques, the tomographic measurements $\boldsymbol{y}$ are acquired by sampling the physical object $\boldsymbol{x}$ uniformly above the Nyquist rate.
-In such a case when there are sufficient measurements, reconstruction using the conventional filtered backprojection (FBP) suffices, as seen in Fig.~\ref{fig:story} (600 views case).
-However, in the last decade, reconstruction from limited sampled data has been made possible by assuming the data to exhibit sparsity under certain mathematical transforms $\boldsymbol{\Upsilon}$ such as the Discrete Cosine Transform (DCT) or wavelet transforms.
-This is known as sparsity prior and is the fundamental principle in the widely used Compressed Sensing (CS) technique~\cite{Donoho,introCS}.
-Fig.~\ref{fig:story} demonstrates the benefit of using sparsity prior when the number of projection views is limited (100 views in Fig.~\ref{fig:story}).
-
+Computed Tomography (CT) deals with the recovery of an entire object
+from a limited set of projection data which are acquired by passing
+X-rays at different orientations (`views'). It is preferable to
+minimize the radiation exposed in order to prevent any potential
+damage to it and in order to reduce the acquisition time. Therefore,
+current research seeks to either significantly reduce the radiation
+intensity required to reconstruct with adequate
+fidelity~\cite{yang2018,Lin2016,Xie2017,gopal2019low} or significantly
+reduce the number of measurements required to reconstruct with
+adequate fidelity. For the latter case, there are two lines of
+pursuit. One is to intelligently choose those sets of projection views
+that capture most
+information~\cite{King2018,Anthony2018,barkan17,fischer16,andrei14},
+and the other, which is the focus of this paper, is to design the
+reconstruction algorithm in order to achieve the most accurate
+recovery of the underlying slice, given the measurements from any
+limited set of views~\cite{yang2018,geyer2015,kilic2011}.
+
+In conventional data acquisition techniques, the tomographic
+measurements $\boldsymbol{y}$ are acquired by sampling the physical
+object $\boldsymbol{x}$ uniformly with a substantial number of views,
+ideally above the Nyquist rate. In such a case when there are
+sufficient measurements, reconstruction using the conventional
+filtered backprojection (FBP) suffices, as seen in
+Fig.~\ref{fig:story} (first column, 600 views). The figure shows the
+ground truth image (260x260) of naturally growing sprouts at the top
+left (the details of the dataset is postponed to
+Section~\ref{sec:results_uniform_prior}).
+
+However, in the last decade, reconstruction from reduced views has
+been made possible by assuming the data to exhibit sparsity under
+certain mathematical transforms $\boldsymbol{\Upsilon}$ such as the
+wavelet transforms, or the Discrete Cosine Transform (DCT). This is
+known as sparsity prior and is the fundamental principle in the widely
+used Compressed Sensing (CS) technique~\cite{Donoho,introCS}.
 There are multiple ways to incorporate the sparsity prior using CS.
-We use the LASSO (least absolute shrinkage and selection operator) which iteratively solves for the solution by penalizing a combination of least squares error and l1-norm of the sparse coefficients $\boldsymbol{\theta}$ of the object $\boldsymbol{x}$.
-If $\boldsymbol{\mathcal{R}}$ represents the acquisition model, then the LASSO solution is described by one that minimizes:
-
+We use the LASSO (least absolute shrinkage and selection operator) which iteratively solves for the solution by penalizing a combination of least squares error and $L_1$-norm of the sparse coefficients $\boldsymbol{\theta}$ of the object $\boldsymbol{x}$.
+If $\boldsymbol{\mathcal{R}}$ represents the acquisition model, then the LASSO solution is described by one that minimizes
  \begin{equation}
-J_{CS}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1.
+J_{\text{CS}}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
 \label{Eq:simple_cs}
  \end{equation}
-
- We solve this cost function using the popular l1-regularized least squares (l1-ls) package available in~\cite{l1ls}.
-We also choose DCT as our sparsity basis $\boldsymbol{\Upsilon}$.
-We observed that there was no significant benefit in choosing wavelets over DCT.
- \begin{figure}[h]
+ Fig.~\ref{fig:story} (second column) demonstrates the benefit of
+ using sparsity prior when the number of projection views is limited
+ (100 views).  We solve this cost function using the popular
+ l1-regularized least squares (l1-ls) package available
+ in~\cite{l1ls}, and  choose DCT as our sparsity basis
+ $\boldsymbol{\Upsilon}$.
+
+ %%% Postpone later We observed that there was no significant benefit
+ %%% in choosing wavelets over DCT.  }
+
+ \begin{figure}[t]
 \centering
 	\includegraphics[width=0.4\textwidth]{../images/story/story.png}
-        \caption{Illustration of the use of various priors as the number of views reduces.
-For large number of views (600 views), the FBP reconstruction is of good quality (SSIM = 0.92.
-As the number of views become limited (100 views), the reconstruction using sparsity prior (SSIM = 0.90) is better than FBP reconstruction (SSIM = 0.83).
-If the number of views is further reduced (30 views), the presence of both sparsity prior and object improves the reconstruction (SSIM = 0.85) when compared to presence of only sparsity prior (SSIM = 0.82) or no prior (SSIM = 0.69).}
+        \caption{Illustration of the use of various priors as the
+          number of views reduces. For extremely large number of views
+          (600 views), the FBP reconstruction (first column) is of
+          very good quality (Structural Similarity Index Metric,
+          SSIM=0.92). As the number of views become limited (100
+          views), the reconstruction using sparsity prior (middle
+          column) is better both visually and quantitatively than FBP
+          (SSIM of 0.90 vs 0.83). If the number of views is
+          drastically reduced (30 views), the presence of both
+          sparsity prior and object prior improves the reconstruction
+          (SSIM = 0.85) when compared to presence of only sparsity
+          prior (SSIM = 0.82) or no prior (SSIM = 0.69). In all cases,
+          the ground truth (260x260) appears in the top left.}
  \label{fig:story}
  \end{figure}
- When the number of views is significantly less, the sparsity prior alone is not sufficient, as seen in Fig.~\ref{fig:story} for the case of 30 views.
-In such cases, any additional information, specifc to the object being scanned (i.e., object prior) is useful in further improving the reconstruction.
-Such techniques may also use information from previously scanned data of the same object or a similar one.
-However, with the use of such an object prior, a new challenge emerges:  the prior information may potentially overwhelm the essential new details that appear in the test.
-It is in this context that the work in this paper fits in: the design of an algorithm that estimates the location and magnitude of new changes in the (unknown) test object.
-This eventually prevents the prior from adversely affecting the reconstruction of new regions in the test.
-We refer to this as a \textit{spatially-varying} uniform prior-based reconstruction routine.
-We present results on real and simulated 3D data for different longitudinal studies.
-These are studies wherein sequential CT scans of the same object are acquired to track time-evolving changes within its interior.
+
+ When the number of views is significantly reduced, the sparsity prior
+ alone is not sufficient.  In such cases additional information
+ specific to the object being scanned (i.e., object prior) is useful
+ in further improving the reconstruction.  While this has been done in
+ the context of dynamic CT-scans (as discussed in
+ Section~\ref{sec:related}), in this paper we use a set $S$ of
+ previous scans of the same object that is more appropriate in a
+ longitudinal context. As seen in Fig.~\ref{fig:story} (last column,
+ 30 views) our method uses the prior scans \emph{uniformly} by
+ creating an eigenspace representation
+ (Section~\ref{sec:method_uniform_prior}).
+
+ However, with the use of such an object prior, a new challenge
+ emerges. The prior set S may potentially overwhelm the necessary
+ details, or since several prior scans are available, finding the
+ right prior may be an issue. We therefore seek an algorithm that
+ estimates the location and magnitude of new changes in the (unknown)
+ test. As we show in Section~\ref{sec:method_spatially_varying_prior},
+ this eventually prevents the prior from adversely affecting the
+ reconstruction of new regions in the test. We refer to this method as
+ a \textit{spatially-varying} global prior-based reconstruction
+ routine, that still uses all the previous scans in the set $S$.
+
+ This paper is organized as follows. After discussing related work in
+ Section~\ref{sec:related}, Section~\ref{sec:contributions} lays down
+ the key contributions of this work. Section~\ref{sec:tmh}
+ demonstrates the utility of both the uniform and spatially-varying
+ methods on a longitudinal medical dataset. We now move to the
+ details. Section~\ref{sec:method_uniform_prior} describes the
+ construction of the uniform eigenspace prior, followed by the
+ corresponding results in real and synthetic 3D biological datasets in
+ Section~\ref{sec:results_uniform_prior}. Section~\ref{sec:method_spatially_varying_prior}
+ describes how the uniform prior needs to be modified when accurate
+ details of new changes are to be observed. A spatially-varying
+ technique offers a solution, the results of which are presented in
+ Section~\ref{sec:results_spatially_varying_prior}. Section\ref{sec:discussion}
+ discusses tuning of the hyperparameters involved, and limitations of
+ our method. Finally, we conclude with key inferences that can be
+ drawn from our work in Section~\ref{sec:conclusions}.
+
+% We present results on real and simulated 3D
+%  data for different longitudinal studies.  These are studies wherein
+%  sequential CT scans of the same object are acquired to track
+%  time-evolving changes within its interior.
 
@@
 %(2) there is the key issue of the choice of \textit{a particular} previously scanned object as template among the many previously acquired scans
+
  \section{Related Work}
- Most of the related work for object-prior based reconstruction has been in the areas of dynamic CT and 4D-CT.
-In dynamic CT, the object being scanned undergoes changes between successive projection views and hence is not stationary even within a single complete scan.
-In 4D-CT, the object undergoes changes between successive scans.
-In both these cases, it may be possible to use very specific object-properties for reconstruction.
-For example, in~\cite{Van2015}, the knowledge of attenuation coefficient of the fluid was used as a prior for reconstructing its flow through gravel.
-In~\cite{Koen2020}, the changes across the sucessive scan volumes is assumed to be continuous, thus enabling the use of optical flow to model the motion between corresponding voxels of different scan volumes.
-In another study~\cite{vincent2017}, changes between successive scans were modelled by affine deformation whose parameters were computed for motion-correction.
-Such a correction enables acquisition from fewer views than would have otherwise not been possible for reconstruction with adequate fidelity.
-In~\cite{daniil2015}, all the scan volumes are reconstructed together using spatio-temporal regularization.
-Unlike these methods, if however, the object-prior were not available in the first place, then other techniques presented in~\cite{Essam2015,Polak2017} and~\cite{Li2015} could be used for the reconstruction of a single volume from few projection views.
-
- In contrast to the prior-based studies mentioned above, we reconstruct the current test object without any assumption of continuity of changes or some knowledge of the attenuation coefficients of the structures.
-We use the current measurements from few-views and previous high-quality scans of the same object.
-We utilize the uniform global eigenspace prior presented in~\cite{my_dicta_paper} which assume that the new test volume lies within the space spanned by the eigenvectors of the multiple representative previously scanned objects.
-We then demonstrate how the global prior can impose an inflexible constant weight (and hence a bias) when reconstructing the data.
-As a solution, we present a method to moderate the control of the prior by estimating and imposing spatially-varying weights to the prior in order to reconstruct new structures accurately.
-This spatially-varying prior tunes the effect of the templates in different regions of the reconstruction.
+\label{sec:related}
+Few view projection has been explored in~\cite{Essam2015,Polak2017}
+and~\cite{Li2015}. However
+{\color{red} add here!!  Why is this bad and how does it compare with
+ours? }
+
+Most object-prior based reconstruction has been in the areas of
+dynamic CT and 4D-CT. In dynamic CT, the object being scanned
+undergoes changes between successive projection views and hence is not
+stationary even within a single complete scan. In contrast, in 4D-CT,
+a set of 3D CT scans over short intervals of time are taken as the
+object undergoes changes between successive scans. In both these
+cases, it may be possible to use very specific object-properties for
+reconstruction. For example, in~\cite{Van2015}, the knowledge of the
+attenuation coefficient of the fluid is used as a prior for
+reconstructing its flow through gravel. In~\cite{Koen2020}, the
+changes across the sucessive scan volumes is assumed to be continuous,
+thus enabling the use of optical flow to model the motion between
+corresponding voxels of different scan volumes. In another
+study~\cite{vincent2017}, changes between successive scans were
+modelled by affine deformation whose parameters were computed for
+motion-correction. Such a correction enables acquisition from fewer
+views than would have otherwise not been possible for reconstruction
+with adequate fidelity. In~\cite{daniil2015}, all the scan volumes are
+reconstructed together using spatio-temporal regularization.
+
+\section{Contributions}
+\label{sec:contributions}
+This paper focusses on few-views reconstruction with an emphasis on
+longitudinal studies.  Fig.~\ref{fig:prior_overview} provides an
+overview. In contrast to the object prior-based studies
+mentioned above, we reconstruct the current test object without any
+assumption of continuity of changes or some knowledge of the
+attenuation coefficients of the structures. We do not make any
+temporal assumption in terms of time intervals such as in 4D CT
+scans. We use the current measurements from few-views and previous
+scans of the same object. A key idea in our work is the starting point
+-- the new test volume is close to the space spanned by the
+eigenvectors of the multiple representative previously scanned
+objects.
+
+% We utilize the uniform global eigenspace prior presented
+% in~\cite{my_dicta_paper} which assume
+
+We also demonstrate how the global prior can impose an inflexible
+constant weight (and hence an unnecessary bias) when reconstructing
+the data. As a solution, we present a method to moderate the control
+of the prior by estimating and imposing spatially-varying weights to
+the prior in order to reconstruct new structures accurately. This
+spatially-varying prior tunes the effect of the templates in different
+regions of the reconstruction.
 
@@
 	\includegraphics[width=0.5\textwidth]{../images/prior_cmb.png}
-        \caption{Overview of our work.
-The choice of the number of measurement views and the type of reconstruction is driven by the goal in the application under consideration.
-When our goal is relatively simple, such as tracking the location of new changes while simultaneously reducing sub-sampling artefacts, we propose (a) acquiring measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
-When our goal becomes more ambitious, such as observing details of the new changes while simultaneously reducing sub-sampling artefacts, we propose (b) acquiring measurements from a slightly higher number of views (`moderate-view' imaging) and using spatially-varying prior-based reconstruction.
-In either case, the number of views is lower than what is conventionally used.}
+        \caption{Overview of our work. The choice of the number of
+          measurement views and the type of reconstruction is driven
+          by the goal in the application under consideration.  (a) When
+          our goal is relatively simple, such as tracking the location
+          of new changes while simultaneously reducing sub-sampling
+          artefacts, we propose acquiring measurements from an
+          extremely small number of views (`few-view' imaging) and
+          using uniform prior based reconstruction. (b) When our goal
+          becomes more ambitious, such as observing details of the new
+          changes while simultaneously reducing sub-sampling
+          artefacts, we propose acquiring measurements from a
+          slightly higher number of views (`moderate-view' imaging)
+          and using spatially-varying prior-based reconstruction. In
+          either case, the number of views is lower than what is
+          conventionally used.}
  \label{fig:prior_overview}
@@
 
-This paper is organized as follows: Section~\ref{sec:contributions} lays down the key contributions of this work.
-Section~\ref{sec:tmh} demonstrates the utility of both the uniform and spatially-varying methods on a longitudinal medical dataset.
-Section~\ref{sec:method_uniform_prior} describes the construction of the uniform eigenspace prior, followed by the corresponding results in real and synthetic 3D biological datasets in Section~\ref{sec:results_uniform_prior}.
-Section~\ref{sec:method_spatially_varying_prior} describes how the uniform prior needs to be modified when accurate details of new changes are to be observed.
-A spatially-varying technique offers a solution, the results of which are presented in Section~\ref{sec:results_spatially_varying_prior}.
-Section\ref{sec:discussion} discusses tuning of the hyperparameters involved, and limitations of our method.
-Finally, we conclude  with key inferences that can be drawn from our work in Section~\ref{sec:conclusions}.
-\section{Contributions}
-\label{sec:contributions}
-This paper focusses on few-views reconstruction for longitudinal studies, and has the following key contributions:
+In summary, the key contributions are
 \begin{itemize}
-\item The scenarios where a uniform object prior is sufficient for the application at hand, and the scenarios for which it will fail, are demonstrated.
-\item A weights map is designed to depict the location and strength of new changes at every voxel.
-A novel algorithm is presented to build this map from sub-sampled measurements of the test and a set of high quality templates.
-Once the weights map is built, it is used for accurate reconstruction of those changes in the test that are absent in all of the templates.
-\item Finally, the methods are validated  on real and syntheric 3D tomographic data of biological datasets from various longitudinal studies, and quatitative accuracies are presented using the Structural Similarity Index Metric (SSIM).
+\item We create and present new 3D biological datasets, and as seen in
+  Fig.~\ref{fig:story} demonstrate the use of object priors when very
+  few views are used. More results appear in
+  Section~\ref{sec:results_uniform_prior} and in the supplementary
+  material.  Our results consist of 3D reconstructions from real
+  cone-beam projections.
+  \item The scenarios where a uniform object prior is sufficient for
+    the application at hand, and the scenarios for which it will fail,
+    are demonstrated. This leads to the idea of a weights map
+    designed to depict the location and strength of new changes at
+    every voxel. A novel algorithm is presented to build this map from
+    sub-sampled measurements of the test and a set of high quality
+    templates. Once the weights map is built, it is used for accurate
+    reconstruction of those changes in the test that are absent in all
+    of the templates. Results appear in
+    Section~\ref{sec:results_spatially_varying_prior}.
+  \item We show the efficacy of our results in a real-life medical
+    longitudinal studies with data obtained in a clinical setting from
+    a live teaching and
+    research hospital 
  \end{itemize}
@@
 \label{sec:tmh}
-Before diving into the details of the uniform and the spatially-varying global prior methods, we first show how both the techniques can be applied to our advantage in a real-life medical longitudinal study.
-Here, our data~\footnote{Source: Tata Memorial Centre~\cite{tmh}, Parel, Mumbai.
-This is the national comprehensive centre for the prevention, treatment, education and research in cancer, and is recognized as one of the leading cancer centres in India.} consists of successive scans of the liver taken during a radio-frequency ablation procedure.
-In such a procedure~\cite{Dong2015}, the physician inserts a thin needle-like probe into the organ.
-Repeated CT scans of the patient need to be acquired in order to track the movement of the needle and to ensure that it is reaching the appropriate target tumor.
-Once the needle hits the tumor, a high-frequency electric current is passed through the tip of the probe and this burns the malignant tumor (ablation).
-The scan at this ablation stage must also reveal accurate details of the changes within.
-In this context, we classify the goal of any of our reconstruction techniques into two categories:
+Before diving into the details of the uniform and the
+spatially-varying global prior methods, we first show how both the
+techniques can be applied to our advantage in a real-life medical
+longitudinal study. Here, our data~\footnote{Source: Tata Memorial
+  Centre~\cite{tmh}, Parel, Mumbai.  This is the national
+  comprehensive centre for the prevention, treatment, education and
+  research in cancer, and is recognized as one of the leading cancer
+  centres in India.} consists of successive scans of the liver taken
+during a radio-frequency ablation procedure. In such a
+procedure~\cite{Dong2015}, the physician inserts a thin needle-like
+probe into the organ. Repeated CT scans of the patient need to be
+acquired in order to track the movement of the needle and to ensure
+that it is reaching the appropriate target tumor. Once the needle hits
+the tumor, a high-frequency electric current is passed through the tip
+of the probe and this burns the malignant tumor (ablation). The scan
+at this ablation stage must also reveal accurate details of the
+changes within. In this context, we classify the goal of any of our
+reconstruction techniques into two categories: 
+\begin{enumerate}
+\item To track the position of the needle in a relatively well-reconstructed background.%Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
+\item To accurately observe the new changes amidst a relatively well reconstructed background after the needle touches the tumor.%Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
+In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a spatially-varying prior-based reconstruction.
+The spatially-varying technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
+\end{enumerate}
 
@@
 
-\begin{enumerate}
-\item To track the position of the needle in a relatively well-reconstructed background.%Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
-\item To accurately observe the new changes amidst a relatively well reconstructed background after the needle touches the tumor.%Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
-In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a spatially-varying prior-based reconstruction.
-The spatially-varying technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
-\end{enumerate} 
 Here, we demonstrate the combined use of l1-ls (CS) with the global prior, in two flavors: the vanilla (uniform) and spatially-varying global prior-based reconstruction.
@@
 \label{sec:discussion}
-The presented uniform prior-based algorithm is suited to applications where we wish to detect the location of new changes in an object over time, and the presented spatially-varying prior-based algorithm is suited to applications where we wish to observe the intricate details of those new changes.
-This distinction in the techniques used has not been studied earlier in literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our knowledge.
-Eventhough methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
+The presented uniform prior-based algorithm is suited to applications
+where we wish to detect the location of new changes in an object over
+time, and the presented spatially-varying prior-based algorithm is
+suited to applications where we wish to observe the intricate details
+of those new changes. This distinction in the techniques used has not
+been studied earlier in
+literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our
+knowledge.
+Even though methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
 We have presented a principled method of tackling this particular issue via our weights map.

### 2020-07-09 paper/tci.tex
minor changes

@@
  \end{equation}
- Fig.~\ref{fig:story} (second column) demonstrates the benefit of
- using sparsity prior when the number of projection views is limited
- (100 views).  We solve this cost function using the popular
- l1-regularized least squares (l1-ls) package available
- in~\cite{l1ls}, and  choose DCT as our sparsity basis
- $\boldsymbol{\Upsilon}$.
+ We solve this cost function using the popular l1-regularized least
+ squares (l1-ls) package available in~\cite{l1ls}, and choose DCT as
+ our sparsity basis $\boldsymbol{\Upsilon}$.  Fig.~\ref{fig:story}
+ (second column) demonstrates the benefit of using sparsity prior when
+ the number of projection views is limited (100 views).
 

### 2020-07-10 paper/tci.tex
Changes in Fig.1, related work, Intro.

@@
 known as sparsity prior and is the fundamental principle in the widely
-used Compressed Sensing (CS) technique~\cite{Donoho,introCS}.
-There are multiple ways to incorporate the sparsity prior using CS.
-We use the LASSO (least absolute shrinkage and selection operator) which iteratively solves for the solution by penalizing a combination of least squares error and $L_1$-norm of the sparse coefficients $\boldsymbol{\theta}$ of the object $\boldsymbol{x}$.
-If $\boldsymbol{\mathcal{R}}$ represents the acquisition model, then the LASSO solution is described by one that minimizes
+used Compressed Sensing (CS) technique~\cite{Donoho,introCS}.  There
+are multiple ways to incorporate the sparsity prior using CS. We use
+the LASSO (least absolute shrinkage and selection operator) which
+iteratively solves for the solution by penalizing a combination of
+least squares error and $L_1$-norm of the sparse coefficients
+$\boldsymbol{\theta}$ of the object $\boldsymbol{x}$. If $\boldsymbol{\Psi}$
+represents the sparsity basis i.e. if $\boldsymbol{x} = \boldsymbol{\Psi\theta}$, and 
+$\boldsymbol{\mathcal{R}}$ represents the acquisition model, then the
+LASSO solution is described by one that minimizes
  \begin{equation}
@@
 \label{sec:related}
-Few view projection has been explored in~\cite{Essam2015,Polak2017}
-and~\cite{Li2015}. However
-{\color{red} add here!!  Why is this bad and how does it compare with
-ours? }
+There exist techniques that aim to reconstruct from few-views in
+specialized applications. For example, in~\cite{Essam2015},
+sparsity-constrained optimization is presented for angiography. Here,
+the regions of interest are the vessels alone and they are highlighted
+by physically inserting a contrast agent, and therefore there is a
+inherent sharper contrast between the vessels and the
+background. In many other general application scenarios like the ones presented in this paper,
+any information about the regions of interest is not known.
+In other applications where the spatial-gradient of the underlying volume is known to be sparse, the `total variation' method, as used in~\cite{Li2015,Polak2017} can be applied.
+As we will later see in Figs.\ref{fig:object-prior_test_okra} and~\ref{fig:object-prior_test_sprouts}, the spatial-gradient of many datasets is not sparse.
 
@@
 stationary even within a single complete scan. In contrast, in 4D-CT,
-a set of 3D CT scans over short intervals of time are taken as the
-object undergoes changes between successive scans. In both these
-cases, it may be possible to use very specific object-properties for
+a set of 3D CT scans are taken over short intervals of time and all the 3D volumes are reconstructed together.
+Here, the object undergoes changes between successive scans.
+~\cite{PICCS} is one of the earliest work to establish the use of object-prior along with sparsity prior in dynamic CT.
+Its limitation was the unchecked over-emphasis of the prior on the reconstruction of the test at hand.
+This limitation was later dealt with by applying very specific object-properties for
 reconstruction. For example, in~\cite{Van2015}, the knowledge of the
@@
 
-Here, we demonstrate the combined use of l1-ls (CS) with the global prior, in two flavors: the vanilla (uniform) and spatially-varying global prior-based reconstruction.
-The choice of the number of measurement views and the type of reconstruction -- uniform or spatially-varying, is driven by the goal of the procedure.
-First, in order to track the needle, a very small number of views is sufficient because the needle has a very high attenuation coefficient when compared to that of the organs.
-We use the uniform global prior reconstruction here to reduce the artefacts due to sub-sampling.
-The uniform method is fast and sufficient to track the position of the needle.
-Once the needle reaches the site of the tumor, we propose changing the imaging protocol to acquire measurements from a moderate number of views.
-This will enable us to get more information about the new changes.
-In addition, we then deploy the spatially-varying prior method in order to locate the regions of new changes and penalize any dominance of the prior in these regions.
-Regardless of the imaging protocol we use (`few' or `moderate'), the number of views is smaller (atleast one-fifth) than the conventional number of views used in a standard hospital setting.
-
-The dataset from this longitudinal medical study consists of 8 scans taken during the ablation procedure.
-We demonstrate our method for 2D reconstruction by choosing a single slice from each of the 8 volumes as our dataset.
-Note that all these 8 slices are located at the \emph{same} index~\footnote{The notion of~\textit{same index} (slice number corresponding to the same depth) makes sense in the context, because in such problems, the different scans are aligned with each other.} within each of the respective volumes.
-Fig.~\ref{fig:RFA2_test_object-prior} shows the chosen set of 2D slices (each of size $512 \times 512$) from the different volumes.
-Observe that the needle is seen in all of the first 7 slices  and the effect of ablation is seen in the 8th slice.
-\\
-
-\textbf{Tracking the needle:} We first choose slices 1-6 as our object-prior, and reconstruct slice 7 with the specific goal of tracking the needle and simultaneously reduce artefacts.
-Fig.~\ref{fig:RFA2_very_few_views} shows the reconstruction of slice 7 from its measurements from only 90 views.
-The reconstructions are quantitatively compared using SSIM.\\
+Here, we demonstrate the combined use of l1-ls (CS) with the global
+prior, in two flavors: the vanilla (uniform) and spatially-varying
+global prior-based reconstruction. The choice of the number of
+measurement views and the type of reconstruction -- uniform or
+spatially-varying, is driven by the goal of the procedure. First, in
+order to track the needle, a very small number of views is sufficient
+because the needle has a very high attenuation coefficient when
+compared to that of the organs. We use the uniform global prior
+reconstruction here to reduce the artefacts due to sub-sampling. The
+uniform method is fast and sufficient to track the position of the
+needle.  Once the needle reaches the site of the tumor, we propose
+changing the imaging protocol to acquire measurements from a moderate
+number of views. This will enable us to get more information about the
+new changes. In addition, we then deploy the spatially-varying prior
+method in order to locate the regions of new changes and penalize any
+dominance of the prior in these regions.  Regardless of the imaging
+protocol we use (`few' or `moderate'), the number of views is smaller
+(atleast one-fifth) than the conventional number of views used in a
+standard hospital setting.
+
+The dataset from this longitudinal medical study consists of 8 scans
+taken during the ablation procedure. We demonstrate our method for 2D
+reconstruction by choosing a single slice from each of the 8 volumes
+as our dataset. Note that all these 8 slices are located at the
+\emph{same} index~\footnote{The notion of~\textit{same index} (slice
+  number corresponding to the same depth) makes sense in the context,
+  because in such problems, the different scans are aligned with each
+  other.} within each of the respective
+volumes. Fig.~\ref{fig:RFA2_test_object-prior} shows the chosen set of
+2D slices (each of size $512 \times 512$) from the different
+volumes. Observe that the needle is seen in all of the first 7 slices
+and the effect of ablation is seen in the 8th slice. \\
+
+\textbf{Tracking the needle:} We first choose slices 1-6 as our
+object-prior, and reconstruct slice 7 with the specific goal of
+tracking the needle and simultaneously reduce
+artefacts. Fig.~\ref{fig:RFA2_very_few_views} shows the reconstruction
+of slice 7 from its measurements from only 90 views. The
+reconstructions are quantitatively compared using SSIM.\\
 
@@
 
- The proposed method has been validated on new\footnote {These and our code will be made available to the community.} scans of biological specimens in a longitudinal setting.
-These datasets in the form of \emph{raw cone-beam projection measurements} were acquired from a lab at the Australian National University (ANU).
-%We emphasize that in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections \emph{simulated} from 3D volumes.
-This is because most CT scanners do not reveal the raw projections, and instead output only the full reconstructed volumes.
-Moreover, the process of conversion from the projections to the full volumes is proprietary.
-\emph{Departing from this, we demonstrate reconstruction results from raw projection data.}
+ The proposed method has been validated on new\footnote {These and our
+   code will be made available to the community.} scans of biological
+ specimens in a longitudinal setting. These datasets in the form of
+ \emph{raw cone-beam projection measurements} were acquired from a lab
+ at the Australian National University (ANU). %We emphasize that in
+ most of the literature on tomographic reconstruction, the results are
+ shown on reconstruction from projections \emph{simulated} from 3D
+ volumes. This is because most CT scanners do not reveal the raw
+ projections, and instead output only the full reconstructed
+ volumes. Moreover, the process of conversion from the projections to
+ the full volumes is proprietary. \emph{Departing from this, we
+   demonstrate reconstruction results from raw projection data.}
 In all figures in this section, `uniform prior' refers to optimizing Eq.~\ref{eq:spatially-varying_prior} with $\boldsymbol{W}(x,y,z)=1$.
@@
 \label{Sec:okra_uniform}
-Our first dataset is that of an Okra specimen consisting of its five scans (Fig.~\ref{fig:object-prior_test_okra}).
-The measurements consisted of real cone-beam projections from 450 views, each of size $336\times156$.
-The corresponding size of the reconstructed volume is $338\times338\times123$.
-Prior to the first scan, two holes were drilled on the surface of the specimen.
-This was followed by four scans, each after introducing one new cut.
-The specimen was kept in the same position throughout the acquisitions.
-In cases where such an alignment is not present, all the template volumes must be pre-aligned before computing the eigenspace.
-The test must be registered to the object-prior after its preliminary pilot reconstruction.
-The ground truth consists of FDK reconstructed volumes from the the full set of 450 view projections.
-The test volume was reconstructed from a partial set of 45 projections, i.e.
-$10\%$ of the projection views from which ground truth was reconstructed.
-The selected 3D ground truth of template volumes, the test volume as well as the 3D reconstructions can be seen in~\cite{supp_paper}.
-One of the slices of the reconstructed volumes is shown in Fig.~\ref{fig:okra_3D_results}.
-The red and green 3D RoI in the video and images show the regions where new changes are present.
-Based on the potato and the okra experiments, we see that our method is able to \emph{discover both} the presence of a new structure, as well as the absence of a structure.
+Our first dataset is that of an Okra specimen consisting of its five
+scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
+consisted of real cone-beam projections from 450 views, each of size
+$336\times156$. The corresponding size of the reconstructed volume is
+$338\times338\times123$. Prior to the first scan, two holes were
+drilled on the surface of the specimen. This was followed by four
+scans, each after introducing one new cut. The specimen was kept in
+the same position throughout the acquisitions. In cases where such an
+alignment is not present, all the template volumes must be pre-aligned
+before computing the eigenspace. The test must be registered to the
+object-prior after its preliminary pilot reconstruction. The ground
+truth consists of FDK reconstructed volumes from the the full set of
+450 view projections. The test volume was reconstructed from a partial
+set of 45 projections, i.e. $10\%$ of the projection views from which
+ground truth was reconstructed. The selected 3D ground truth of
+template volumes, the test volume as well as the 3D reconstructions
+can be seen in~\cite{supp_paper}. One of the slices of the
+reconstructed volumes is shown in Fig.~\ref{fig:okra_3D_results}. The
+red and green 3D RoI in the video and images show the regions where
+new changes are present. Based on the potato and the okra experiments,
+we see that our method is able to \emph{discover both} the presence of
+a new structure, as well as the absence of a structure.
 
@@
      \end{subfigure}
-     \caption{3D reconstruction of sprouts from $2.5\%$ projection views
-   (b, c) have poor details (d) no new information detected (the
-   prior dominates as can be seen in the blue and red regions) and
-   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed in ~\cite{supp_paper}.} 
+     \caption{3D reconstruction of sprouts from $2.5\%$ projection
+       views (b, c) have poor details (d) no new information detected
+       (the prior dominates as can be seen in the blue and red
+       regions) and (e) new information detected in the regions of
+       interest. The reconstructed volumes can be viewed in
+       ~\cite{supp_paper}.} 
 \label{fig:sprouts_3D_results}
@@
 
-Although the uniform global prior can be very useful in some circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a major limitation when we want accurate details of the new changes.
-While the uniform prior compensates very well for the possible artefacts due to sparse measurements, it dominates the regions with new changes masking the signal, as seen in Fig.~\ref{fig:RFA2_few_views}-d.
-Ideally, we will want to impose the prior only in the regions that are common between the test and object-prior.
-Our spatially-varying prior based reconstruction overcomes this limitation by minimizing the following cost function:
+Although the uniform global prior can be very useful in some
+circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a major
+limitation when we want accurate details of the new changes. While the
+uniform prior compensates very well for the possible artefacts due to
+sparse measurements, it dominates the regions with new changes masking
+the signal, as seen in Fig.~\ref{fig:RFA2_few_views}-d. Ideally, we
+will want to impose the prior only in the regions that are common
+between the test and object-prior.  Our spatially-varying prior based
+reconstruction overcomes this limitation by minimizing the following
+cost function:
 \begin{equation}
@@
  \subsubsection{\textbf{Computation of weights matrix $\boldsymbol{W}$}}
-Since the test volume (referred to as $\boldsymbol{x}$) is unknown to begin with, it is not possible to decipher the precise regions in $\boldsymbol{x}$ that are different from all the previously scanned objects (`object-prior').
-We start with $X^{\text{fdk}}$, the initial backprojection reconstruction of the test volume using the Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} in an attempt to discover the difference between the object-prior and the test volume.
-Let $\boldsymbol{V_{\text{high}}}$ be the eigenspace constructed from high-quality object-prior.
-However, the difference between $X^{\text{fdk}}$ and its projection onto the eigenspace $\boldsymbol{V_{\text{high}}}$ will detect the new regions along with  many false positives (false new regions).
-This is because, $X^{\text{fdk}}$ will contain many geometric-specific artefacts arising from sparse measurements (angle undersampling), which are absent in the high quality object-prior used to construct the eigenspace $\boldsymbol{V_{\text{high}}}$.
-To discover unwanted artefacts of the imaging geometry, in a counter-intuitive way, we generate \emph{low quality} reconstruction of the object-prior as described below.
+Since the test volume (referred to as $\boldsymbol{x}$) is unknown to
+begin with, it is not possible to decipher the precise regions in
+$\boldsymbol{x}$ that are different from all the previously scanned
+objects (`object-prior'). We start with $X^{\text{fdk}}$, the initial
+backprojection reconstruction of the test volume using the
+Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} in an attempt to
+discover the difference between the object-prior and the test
+volume. Let $\boldsymbol{V_{\text{high}}}$ be the eigenspace
+constructed from high-quality object-prior. However, the difference
+between $X^{\text{fdk}}$ and its projection onto the eigenspace
+$\boldsymbol{V_{\text{high}}}$ will detect the new regions along with
+many false positives (false new regions). This is because,
+$X^{\text{fdk}}$ will contain many geometric-specific artefacts
+arising from sparse measurements (angle undersampling), which are
+absent in the high quality object-prior used to construct the
+eigenspace $\boldsymbol{V_{\text{high}}}$. To discover unwanted
+artefacts of the imaging geometry, in a counter-intuitive way, we
+generate \emph{low quality} reconstruction of the object-prior as
+described below.
 \vspace{2mm}
@@
 \begin{enumerate}
-  \item Generate simulated measurements $\boldsymbol{y_{Q_i}}$ for every template $Q_i$, using the exact same projections views and imaging geometry with which the measurements $\boldsymbol{y}$ of the test volume $\boldsymbol{x}$ were acquired, and
-\item Perform $L$  preliminary FDK reconstructions of each of the $L$ object-prior from $\boldsymbol{y_{Q_i}}$.  Let this be denoted by $\{Y^{\text{fdk}}_i\}_{i=1}^L$.
+  \item Generate simulated measurements $\boldsymbol{y_{Q_i}}$ for
+    every template $Q_i$, using the exact same projections views and
+    imaging geometry with which the measurements $\boldsymbol{y}$ of
+    the test volume $\boldsymbol{x}$ were acquired, and
+\item Perform $L$ preliminary FDK reconstructions of each of the $L$
+  object-prior from $\boldsymbol{y_{Q_i}}$.  Let this be denoted by
+  $\{Y^{\text{fdk}}_i\}_{i=1}^L$.
   \end{enumerate}
-\item Build eigenspace $\boldsymbol{V_{\text{low}}}$ from $\{Y^{\text{fdk}}_i\}_{i=1}^L$.
-Let $P^{\text{fdk}}$ denote projection of $X^{\text{fdk}}$ onto $\boldsymbol{V_{\text{low}}}$.
-The difference between $P^{\text{fdk}}$ and $X^{\text{fdk}}$ will not contain false positives due to imaging geometry, but will have false positives due to artefacts that are specific to the reconstruction method used.
-To resolve this, perform steps $4$ and $5$.
+\item Build eigenspace $\boldsymbol{V_{\text{low}}}$ from
+  $\{Y^{\text{fdk}}_i\}_{i=1}^L$.  Let $P^{\text{fdk}}$ denote
+  projection of $X^{\text{fdk}}$ onto
+  $\boldsymbol{V_{\text{low}}}$. The difference between
+  $P^{\text{fdk}}$ and $X^{\text{fdk}}$ will not contain false
+  positives due to imaging geometry, but will have false positives due
+  to artefacts that are specific to the reconstruction method used. To
+  resolve this, perform steps $4$ and $5$.
 %\vspace{-0.3cm}
@@
 
-The changes and new structures present in the test data will generate different artifacts for different reconstruction techniques.
-These artifacts would not be captured by reconstructions of the object-prior since the underlying new changes and structures may be absent in all of the previously scanned objects.
-We aim to let the weights be independent of the type of artifact.
-Hence, we use a combination of different reconstruction techniques to generate different types of eigenspaces and combine information from all of them to compute weights.
-To illustrate the benefit of this method, we first performed 2D reconstruction of a test slice from the potato dataset (please refer Sec.~\ref{Sec:potato} for details of the dataset) Fig.~\ref{fig:object-prior_test_potato_A1} shows the test and template slices.
-Fig.~\ref{fig:weights_map_2Dpotato}  shows the weights-maps generated using Eq.~\ref{eq:weightsEq} by various reconstruction methods.
-It can be seen that the weights are low in the region of the new change in test data.
-Because all the iterative methods are computationally expensive, we chose only FBP and (l1-ls)-DCT for computing weights-maps for all 3D reconstructions.
+The changes and new structures present in the test data will generate
+different artifacts for different reconstruction techniques. These
+artifacts would not be captured by reconstructions of the object-prior
+since the underlying new changes and structures may be absent in all
+of the previously scanned objects. We aim to let the weights be
+independent of the type of artifact. Hence, we use a combination of
+different reconstruction techniques to generate different types of
+eigenspaces and combine information from all of them to compute
+weights. To illustrate the benefit of this method, we first performed
+2D reconstruction of a test slice from the potato dataset (please
+refer Sec.~\ref{Sec:potato} for details of the dataset)
+Fig.~\ref{fig:object-prior_test_potato_A1} shows the test and template
+slices. Fig.~\ref{fig:weights_map_2Dpotato} shows the weights-maps
+generated using Eq.~\ref{eq:weightsEq} by various reconstruction
+methods. It can be seen that the weights are low in the region of the
+new change in test data. Because all the iterative methods are
+computationally expensive, we chose only FBP and (l1-ls)-DCT for
+computing weights-maps for all 3D reconstructions.
 %---------------------------------------
@@
 
-The proposed method has been validated on 2D and 3D synthetic and real tomographic data of biological and medical specimens.
-The results below demonstrate the advantage of the spatially-varying global prior method over the uniform method.
+The proposed method has been validated on 2D and 3D synthetic and real
+tomographic data of biological and medical specimens. The results
+below demonstrate the advantage of the spatially-varying global prior
+method over the uniform method.
 
@@
 \begin{table}[!h]
-  \caption{SSIM of 3D RoI of reconstructed okra volumes from various methods. Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.}
+  \caption{SSIM of 3D RoI of reconstructed okra volumes from various
+    methods. Each RoI spans 7 consecutive slices where the test is
+    different from all of the previously scanned objects.}
 \begin{tabular}{|l|c|c|c|c|c|}
-\hline
-                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{red RoI}   & 1 (ideal)                     & 0.74        & 0.84       & 0.86                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
-\textbf{green RoI} & 1 (ideal)                     & 0.80        & \textcolor{red}{0.86}       & 0.80                                                               & \textcolor{red}{0.86}                                                                  \\ \hline
+\hline &
+\textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} &
+\textbf{FDK} & \textbf{l1-ls} &
+\textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior +
+    l1-ls\end{tabular}} &
+\textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior +
+    l1-ls\end{tabular}} \\ \hline \textbf{red RoI} & 1 (ideal) & 0.74
+& 0.84 & 0.86 & \textcolor{red}{0.88} \\ \hline \textbf{green RoI} & 1
+(ideal) & 0.80 & \textcolor{red}{0.86} & 0.80 & \textcolor{red}{0.86}
+\\ \hline
 \end{tabular}
@@
 template volumes, test volume, as well as the 3D reconstructions are
-shown in~\cite{supp_paper}. One of the slices of the
-reconstructed volumes and its zoomed-in RoI are shown in
-Figs.~\ref{fig:sprouts_3D_results} and ~\ref{fig:sprouts_zoomed_3D_results} respectively. For the sake of exposition, the red region of interest (RoI) has been culled out from 7
-consecutive slices in the 3D volume to indicate new structures; other
-changes can be viewed in the video. Tables~\ref{table:okra_ssim} and \ref{table:sprouts_ssim} show the improvement in the Structure
+shown in~\cite{supp_paper}. One of the slices of the reconstructed
+volumes and its zoomed-in RoI are shown in
+Figs.~\ref{fig:sprouts_3D_results} and
+~\ref{fig:sprouts_zoomed_3D_results} respectively. For the sake of
+exposition, the red region of interest (RoI) has been culled out from
+7 consecutive slices in the 3D volume to indicate new structures;
+other changes can be viewed in the video. Tables~\ref{table:okra_ssim}
+and \ref{table:sprouts_ssim} show the improvement in the Structure
 Similarity Index (SSIM) of the reconstructed new regions as compared
@@
 %\textbf{\begin{tabular}[c]{@{}c@{}}Potato\\size:(150,150,100)\\45 views\end{tabular}}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338,338,123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 27 min. \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338,338,123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
 \textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130,130,130)\\xx views\end{tabular}}  &  &   &  &  \\ \hline
@@
 \begin{table}[!h]
-\caption{SSIM of 3D reconstructed potato volumes from various methods.
-Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.
-In this dataset alone, the new changes are in a homogeneous background.
-Hence, the FDK performs the best when the RoI alone is considered.
-However, it fails when the entire volume is considered due to the prominent streaky artefacts.}
+\caption{SSIM of 3D reconstructed potato volumes from various
+  methods. Each RoI spans 7 consecutive slices where the test is
+  different from all of the previously scanned objects. In this
+  dataset alone, the new changes are in a homogeneous
+  background. Hence, the FDK performs the best when the RoI alone is
+  considered. However, it fails when the entire volume is considered
+  due to the prominent streaky artefacts.}
 \begin{tabular}{|l|c|c|c|c|c|}
-\hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Spatially-Varying\\prior\\+ l1-ls\end{tabular}} \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.94}        & 0.88      & 0.71                                                               & 0.85                                                            \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.92}        & 0.91      & 0.87                                                               & 0.88                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.88       & \textcolor{red}{0.94}    & 0.92                                                            & 0.89                                                                  \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.74        & 0.81       & \textcolor{red}{0.86}                                                               & \textcolor{red}{0.86}                                                                  \\ \hline
+\hline &
+\textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} &
+\textbf{FDK} & \textbf{l1-ls} &
+\textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior\\+
+    l1-ls\end{tabular}} &
+\textbf{\begin{tabular}[c]{@{}c@{}}Spatially-Varying\\prior\\+
+    l1-ls\end{tabular}} \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}} & 1
+(ideal) & \textcolor{red}{0.94} & 0.88 & 0.71 & 0.85 \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1
+(ideal) & \textcolor{red}{0.92} & 0.91 & 0.87 & 0.88 \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}cyan RoI\\volume\end{tabular}} & 1
+(ideal) & 0.88 & \textcolor{red}{0.94} & 0.92 & 0.89 \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1
+(ideal) & 0.74 & 0.81 & \textcolor{red}{0.86} & \textcolor{red}{0.86}
+\\ \hline
 \end{tabular}
@@
 \label{subsec:k}
-The parameters $\lambda_1$ and $\lambda_2$ must be chosen empirically or by cross-validation by treating one of the previously scanned objects as test.
-In our experiments, we had fixed $\lambda_1$ to be 1 and found that this value is nearly data-independent.
-The value of $\lambda_2$ largely depends on the amount of artefacts we aim to remove by using prior at the cost of their dominance in the new regions.
-This value was chosen to lie between $0-1$ for our datasets.
-Finally, the hyper-parameter $k$ defines the sensitivity of the weights map to the difference between the test image and the prior (projection of test onto the space of object-prior).
-When $k=0$, our method converges to the uniform prior method.
-As $k$ increases, the weights map starts capturing the new changes in the test, at the cost of detecting a few false positives i.e.
-false new changes.
-In other words, as the weights map becomes more sensitive to the difference between the test and object-prior, it becomes more noisy.
-In order to visualize the effect of the hyper-parameter $k$, we performed 2D reconstructions of okra dataset for different values of $k$.
-Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map obtained for each of the $k$ values.
-We estimate an approximate choice for the optimal value of $k$ by treating one of the object-prior as test and reconstructing it.
-We also note that although the weights map is heavily influenced by $k$, the final reconstructions are stable for large variations in $k$, as seen in Fig.~\ref{fig:reconstructions_as_k_varies}.
-Alternatively, in cases where one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using a learning based method described in~\cite{supp_paper}.
+The parameters $\lambda_1$ and $\lambda_2$ must be chosen empirically
+or by cross-validation by treating one of the previously scanned
+objects as test. In our experiments, we had fixed $\lambda_1$ to be 1
+and found that this value is nearly data-independent. The value of
+$\lambda_2$ largely depends on the amount of artefacts we aim to
+remove by using prior at the cost of their dominance in the new
+regions. This value was chosen to lie between $0-1$ for our
+datasets. Finally, the hyper-parameter $k$ defines the sensitivity of
+the weights map to the difference between the test image and the prior
+(projection of test onto the space of object-prior). When $k=0$, our
+method converges to the uniform prior method. As $k$ increases, the
+weights map starts capturing the new changes in the test, at the cost
+of detecting a few false positives i.e. false new changes. In other
+words, as the weights map becomes more sensitive to the difference
+between the test and object-prior, it becomes more noisy. In order to
+visualize the effect of the hyper-parameter $k$, we performed 2D
+reconstructions of okra dataset for different values of
+$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
+obtained for each of the $k$ values. We estimate an approximate choice
+for the optimal value of $k$ by treating one of the object-prior as
+test and reconstructing it. We also note that although the weights map
+is heavily influenced by $k$, the final reconstructions are stable for
+large variations in $k$, as seen in
+Fig.~\ref{fig:reconstructions_as_k_varies}. Alternatively, in cases
+where one wishes to completely avoid the use of this hyper-parameter,
+one can construct a binary weights-map using a learning based method
+described in~\cite{supp_paper}.
 
@@
 \label{sec:conclusions}
-This work deals with the effective use of priors for tomographic reconstruction in longitudinal studies.
-We show that we can either use the uniform global prior method or the spatially-varying prior method to our advantage, depending on our goal.
-We establish the context under which these methods can be used, as outlined in Fig.~\ref{fig:prior_overview}.
-When we wish to approximately know the location of new changes, we apply an uniform prior because it is fast and sufficient for the task at hand.
-We also choose a smaller number of views in order to reduce radiation.
-In addition, we show that when our goal shifts to observing the details of the new changes accurately, we acquire projections from a moderate number of views in order to capture more information.
-We further combine this with the somewhat slower but more accurate technique of reconstruction-- the spatially-varying prior-based method.
-This method ensures that the reconstruction of localized new information in the data is not affected by the priors.
-We have thus improved the state of the art by detecting these regions of change and assigning low prior weights wherever necessary.
-The probability of presence of a `new region' is enhanced considerably by a novel combination of different reconstruction techniques.
-We have validated our technique on medical 2D and real, biological 3D datasets for longitudinal studies.
-The method is also largely robust to the number of previously scanned objects used.
-We urge the reader to see the videos of reconstructed volumes in~\cite{supp_paper}.
+This work deals with the effective use of priors for tomographic
+reconstruction in longitudinal studies. We show that we can either use
+the uniform global prior method or the spatially-varying prior method
+to our advantage, depending on our goal. We establish the context
+under which these methods can be used, as outlined in
+Fig.~\ref{fig:prior_overview}. When we wish to approximately know the
+location of new changes, we apply an uniform prior because it is fast
+and sufficient for the task at hand. We also choose a smaller number
+of views in order to reduce radiation. In addition, we show that when
+our goal shifts to observing the details of the new changes
+accurately, we acquire projections from a moderate number of views in
+order to capture more information. We further combine this with the
+somewhat slower but more accurate technique of reconstruction-- the
+spatially-varying prior-based method. This method ensures that the
+reconstruction of localized new information in the data is not
+affected by the priors. We have thus improved the state of the art by
+detecting these regions of change and assigning low prior weights
+wherever necessary. The probability of presence of a `new region' is
+enhanced considerably by a novel combination of different
+reconstruction techniques.  We have validated our technique on medical
+2D and real, biological 3D datasets for longitudinal studies. The
+method is also largely robust to the number of previously scanned
+objects used. We urge the reader to see the videos of reconstructed
+volumes in~\cite{supp_paper}.
 %Our method has been shown to make the best use of prior
@@
 \section{Acknowledgement}
-We are grateful to Dr.
-Andrew Kingston for facilitating data collection at the  Australian National University.
-AR gratefully acknowledges IITB Seed-grant 14IRCCSG012, as well as NVIDIA Corporation for the generous donation of a Titan-X GPU card, which was essential for computing 3D reconstructions for the research reported here.
-We also thank Dr.
-Akshay Baheti for providing us with medical data from Tata Memorial Hospital, Mumbai.
+We are grateful to Dr. Andrew Kingston for facilitating data
+collection at the Australian National University. AR gratefully
+acknowledges IITB Seed-grant 14IRCCSG012, as well as NVIDIA
+Corporation for the generous donation of a Titan-X GPU card, which was
+essential for computing 3D reconstructions for the research reported
+here. We also thank Dr. Akshay Baheti for providing us with medical
+data from Tata Memorial Hospital, Mumbai.
 {%\footnotesize

### 2020-07-10 paper/tci.tex
minor changes to eq 1 and related work section

@@
 $\boldsymbol{\theta}$ of the object $\boldsymbol{x}$. If $\boldsymbol{\Psi}$
-represents the sparsity basis i.e. if $\boldsymbol{x} = \boldsymbol{\Psi\theta}$, and 
+represents the sparsity basis, i.e., if $\boldsymbol{x} = \boldsymbol{\Psi\theta}$, and 
 $\boldsymbol{\mathcal{R}}$ represents the acquisition model, then the
@@
  \begin{equation}
-J_{\text{CS}}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
+J_{\text{CS}}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} \Psi\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
 \label{Eq:simple_cs}
@@
  technique offers a solution, the results of which are presented in
- Section~\ref{sec:results_spatially_varying_prior}. Section\ref{sec:discussion}
+ Section~\ref{sec:results_spatially_varying_prior}. Section~\ref{sec:discussion}
  discusses tuning of the hyperparameters involved, and limitations of
@@
 \label{sec:related}
-There exist techniques that aim to reconstruct from few-views in
+The idea of using a reduced number of views is most pronounced in
 specialized applications. For example, in~\cite{Essam2015},
@@
 by physically inserting a contrast agent, and therefore there is a
-inherent sharper contrast between the vessels and the
-background. In many other general application scenarios like the ones presented in this paper,
-any information about the regions of interest is not known.
-In other applications where the spatial-gradient of the underlying volume is known to be sparse, the `total variation' method, as used in~\cite{Li2015,Polak2017} can be applied.
-As we will later see in Figs.\ref{fig:object-prior_test_okra} and~\ref{fig:object-prior_test_sprouts}, the spatial-gradient of many datasets is not sparse.
+inherent sharper contrast between the vessels and the background.  In
+other applications where the spatial-gradient of the underlying volume
+is known to be sparse, the `total variation' method, as used
+in~\cite{Li2015,Polak2017} can be applied.  In a more generalized
+application scenario, like the ones addressed in this paper, any
+information about the regions of interest is not known, and such
+techniques have limited applicability.
+
+%  As can be seen
+% in the situatiowe will
+% later see in Figs.\ref{fig:object-prior_test_okra}
+% and~\ref{fig:object-prior_test_sprouts}, the spatial-gradient of many
+% datasets is not sparse.
 
@@
 stationary even within a single complete scan. In contrast, in 4D-CT,
-a set of 3D CT scans are taken over short intervals of time and all the 3D volumes are reconstructed together.
-Here, the object undergoes changes between successive scans.
-~\cite{PICCS} is one of the earliest work to establish the use of object-prior along with sparsity prior in dynamic CT.
-Its limitation was the unchecked over-emphasis of the prior on the reconstruction of the test at hand.
-This limitation was later dealt with by applying very specific object-properties for
-reconstruction. For example, in~\cite{Van2015}, the knowledge of the
-attenuation coefficient of the fluid is used as a prior for
-reconstructing its flow through gravel. In~\cite{Koen2020}, the
-changes across the sucessive scan volumes is assumed to be continuous,
-thus enabling the use of optical flow to model the motion between
-corresponding voxels of different scan volumes. In another
-study~\cite{vincent2017}, changes between successive scans were
-modelled by affine deformation whose parameters were computed for
-motion-correction. Such a correction enables acquisition from fewer
-views than would have otherwise not been possible for reconstruction
-with adequate fidelity. In~\cite{daniil2015}, all the scan volumes are
-reconstructed together using spatio-temporal regularization.
+a set of 3D CT scans are taken over short intervals of time, and the
+object undergoes changes between successive scans.  The reconstruction
+is then performed over the entire set generating several 3D
+volumes. ~\cite{PICCS} is one of the earliest work to establish the
+use of object-prior along with sparsity prior in dynamic CT, in an
+attempt to reduce the number of views. The limitation is the
+unchecked over-emphasis of the prior on the reconstruction of the test
+at hand. This limitation was later dealt with by applying very
+specific object-properties for reconstruction. For example,
+in~\cite{Van2015}, the knowledge of the attenuation coefficient of the
+fluid is used as a prior for reconstructing its flow through
+gravel. In~\cite{Koen2020}, the changes across the sucessive scan
+volumes is assumed to be continuous, thus enabling the use of optical
+flow to model the motion between corresponding voxels of different
+scan volumes. In another study~\cite{vincent2017}, changes between
+successive scans were modelled by affine deformation whose parameters
+were computed for motion-correction. Such a correction enables
+acquisition from fewer views than would have otherwise not been
+possible for reconstruction with adequate
+fidelity. In~\cite{daniil2015}, all the scan volumes are reconstructed
+together using spatio-temporal regularization.
 
@@
 This paper focusses on few-views reconstruction with an emphasis on
-longitudinal studies.  Fig.~\ref{fig:prior_overview} provides an
-overview. In contrast to the object prior-based studies
-mentioned above, we reconstruct the current test object without any
-assumption of continuity of changes or some knowledge of the
-attenuation coefficients of the structures. We do not make any
-temporal assumption in terms of time intervals such as in 4D CT
-scans. We use the current measurements from few-views and previous
-scans of the same object. A key idea in our work is the starting point
--- the new test volume is close to the space spanned by the
-eigenvectors of the multiple representative previously scanned
-objects.
+longitudinal studies. In contrast to the object prior-based studies mentioned
+above, we reconstruct the current test object without any assumption
+of continuity of changes or some knowledge of the attenuation
+coefficients of the structures. We do not make any temporal assumption
+in terms of time intervals -- prior scans could be months apart. We
+use the current measurements from few-views and previous scans of the
+same object. A key idea in our work is the starting point -- the new
+test volume is close to the space spanned by the eigenvectors of the
+multiple representative previously scanned objects.
 
@@
 regions of the reconstruction.
+
+Fig.~\ref{fig:prior_overview} provides an overview.
 

### 2020-07-11 paper/tci.tex
very minor edits

@@
 gravel. In~\cite{Koen2020}, the changes across the sucessive scan
-volumes is assumed to be continuous, thus enabling the use of optical
+volumes are assumed to be continuous, thus enabling the use of optical
 flow to model the motion between corresponding voxels of different
@@
 In this regard, it has been widely applied in the context of data compression.
-However, PCA can also be seen as a tool to provide an orthogonal basis to represent the space in which the test data could lie.
+However, PCA can also be seen as a tool to provide an orthogonal basis to represent the space in which most of the test data could lie (except the new changes).
 This space is constructed from the available set of previously scanned objects which must cover a realistically representative range of structures.
-We first present the eigenspace-cum-CS prior-based reconstruction, which was shown~\cite{my_dicta_paper} to be better when compared to dictionary-based priors.
+%, which was shown~\cite{my_dicta_paper} to be better when compared to dictionary-based priors.
 %A preliminary version of this particular method was earlier presented in \cite{my_dicta_paper}.
 
+We first present the eigenspace-cum-CS prior-based reconstruction.
 To begin with, when an object is scanned multiple times, a set of high quality reconstructions (i.e.
@@
  \emph{raw cone-beam projection measurements} were acquired from a lab
- at the Australian National University (ANU). %We emphasize that in
- most of the literature on tomographic reconstruction, the results are
- shown on reconstruction from projections \emph{simulated} from 3D
- volumes. This is because most CT scanners do not reveal the raw
- projections, and instead output only the full reconstructed
- volumes. Moreover, the process of conversion from the projections to
- the full volumes is proprietary. \emph{Departing from this, we
+ at the Australian National University (ANU). Data from commercially
+ available CT machines is not suitable because most CT scanners do
+ not reveal the raw measurements, and instead output only the full
+ reconstructed volumes. Moreover, the process of conversion from the
+ projections to the full volumes is proprietary.
+ %We emphasize that in
+% most of the literature on tomographic reconstruction, the results are
+ %shown on reconstruction from projections \emph{simulated} from 3D
+ %volumes. This is because most CT scanners do not reveal the raw
+ %projections, and instead output only the full reconstructed
+ %volumes. Moreover, the process of conversion from the projections to
+ %the full volumes is proprietary.
+ \emph{Departing from this, we
    demonstrate reconstruction results from raw projection data.}
@@
 In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
-An in-depth analysis of each of the results is presented in Sec.~\ref{sec:results}.
+An in-depth analysis of each of the results is presented in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior}.
 We now discuss the need for registration between object-prior and the test, the method that suits best when the data is homogeneous, and the effect of hyper-parameters on our reconstructions.
@@
 \textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338,338,123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130,130,130)\\xx views\end{tabular}}  &  &   &  &  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130,130,130)\\xx views\end{tabular}}  & 6 sec. & 3 hrs. & 60 min. &  \\ \hline
 \end{tabular}

### 2020-07-17 paper/tci.tex
Made a few changes suggested by Prof.Sharat

@@
 %\usepackage[sort&compress]{natbib}
+\usepackage{footnote}
+\makesavenoteenv{tabular}
 
@@
   sub-sampling artefacts, we propose (1) acquiring measurements from
-  an \emph{extremely small} number of views and using a global
+  an \emph{extremely small} number of views and using a
   \emph{`uniform'} prior-based reconstruction. If the goal is to
@@
 \label{sec:intro}
-Computed Tomography (CT) deals with the recovery of an entire object
+Computed Tomography (CT) deals with the recovery of details of an
+object's interior
 from a limited set of projection data which are acquired by passing
@@
 Fig.~\ref{fig:story} (first column, 600 views). The figure shows the
-ground truth image (260x260) of naturally growing sprouts at the top
+ground truth image (260$\times$260) of naturally growing sprouts at the top
 left (the details of the dataset is postponed to
@@
 \centering
-	\includegraphics[width=0.4\textwidth]{../images/story/story.png}
+	\includegraphics[width=0.45\textwidth]{../images/story/story.png}
         \caption{Illustration of the use of various priors as the
@@
  previous scans of the same object that is more appropriate in a
- longitudinal context. As seen in Fig.~\ref{fig:story} (last column,
- 30 views) our method uses the prior scans \emph{uniformly} by
- creating an eigenspace representation
+ longitudinal context. Specifically, longitudinal studies here refers
+ to the acquisition of sequential CT scans of the same subject to
+ track time-evolving changes within the subject's interior. As seen in
+ Fig.~\ref{fig:story} (last column, 30 views) our method uses the
+ prior scans \emph{uniformly} by creating an eigenspace representation
  (Section~\ref{sec:method_uniform_prior}).
@@
  reconstruction of new regions in the test. We refer to this method as
- a \textit{spatially-varying} global prior-based reconstruction
- routine, that still uses all the previous scans in the set $S$.
+ a \textit{spatially-varying} prior-based reconstruction
+ routine, that still uses \textit{all} the previous scans in the set $S$.
 
@@
 This paper focusses on few-views reconstruction with an emphasis on
-longitudinal studies. In contrast to the object prior-based studies mentioned
-above, we reconstruct the current test object without any assumption
-of continuity of changes or some knowledge of the attenuation
+longitudinal studies. In contrast to
+the object prior-based studies mentioned above, we
+reconstruct the current test object without any assumption of
+continuity of changes or some knowledge of the attenuation
 coefficients of the structures. We do not make any temporal assumption
@@
 
-We also demonstrate how the global prior can impose an inflexible
+We also demonstrate how the uniform prior can impose an inflexible
 constant weight (and hence an unnecessary bias) when reconstructing
@@
 Before diving into the details of the uniform and the
-spatially-varying global prior methods, we first show how both the
+spatially-varying prior methods, we first show how both the
 techniques can be applied to our advantage in a real-life medical
@@
     \end{subfigure}     
-     \caption{Radio-frequency ablation dataset: One of the slices (512 x 512) from each of the 8 scan volumes of a longitudinal study dataset of the liver.
+     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver.
 Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.
@@
 \subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/very_few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{Backprojection}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
 \subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
 \subcaptionbox{Proposed\\ method: uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
-\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) Filtered backprojection and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures, SSIM $=0.35$ and (d) uniform global prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
+\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) FBP and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures, SSIM $=0.35$ and (d) uniform prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
 The region enclosed in red rectangle is our RoI as it contains both the new position of the needle and some background.
@@
 \subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{Backprojection}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
 \subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
@@
 \subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
-\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) l1-ls with SSIM $=0.46$ and (d) uniform global prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) spatially-varying prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
+\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) l1-ls with SSIM $=0.46$ and (d) uniform prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) spatially-varying prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
 The region enclosed in green rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
@@
 
-Here, we demonstrate the combined use of l1-ls (CS) with the global
-prior, in two flavors: the vanilla (uniform) and spatially-varying
-global prior-based reconstruction. The choice of the number of
+%Here, we demonstrate the combined use of l1-ls (CS) with the object
+%prior, in two flavors: the vanilla (uniform) and spatially-varying
+%prior-based reconstruction.
+The choice of the number of
 measurement views and the type of reconstruction -- uniform or
@@
 because the needle has a very high attenuation coefficient when
-compared to that of the organs. We use the uniform global prior
+compared to that of the organs. We use the uniform prior
 reconstruction here to reduce the artefacts due to sub-sampling. The
@@
 volumes. Fig.~\ref{fig:RFA2_test_object-prior} shows the chosen set of
-2D slices (each of size $512 \times 512$) from the different
+2D slices (each of size 512$\times$512) from the different
 volumes. Observe that the needle is seen in all of the first 7 slices
@@
 
-\textbf{Observing details of the ablation:} Next, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e.
-a somewhat higher number of views this time.
+\textbf{Observing details of the ablation:} Next, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e., a somewhat higher number of views this time.
 Fig.~\ref{fig:RFA2_few_views} shows the reconstructions of slice 8 by different methods.
-We see that the spatially-varying prior reconstruction brings in the advantage of the prior without it adversely affecting the new regions.
+We see that the spatially-varying prior reconstruction brings in the advantage of the prior without adversely affecting the reconstruction of new regions.
 
 %---------------------------------Uniform section---------------------
-\section{Method: uniform prior-based reconstruction}
+\section{Uniform prior-based reconstruction}
 \label{sec:method_uniform_prior}
-Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform (global) prior-based reconstruction.
+Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform  prior-based reconstruction.
 Principal Component Analysis (PCA) has been traditionally used to find the significant modes of (Gaussian corrupted) data.
@@
 We first present the eigenspace-cum-CS prior-based reconstruction.
-To begin with, when an object is scanned multiple times, a set of high quality reconstructions (i.e.
-reconstructions from a dense set of projection views) may be chosen as object-prior for the reconstruction of future scan volumes, which in turn, may be scanned using far fewer measurements.
+To begin with, when an object is scanned multiple times, a set of high quality reconstructions (i.e., reconstructions from a dense set of projection views) may be chosen as object-prior for the reconstruction of future scan volumes, which in turn, may be scanned using far fewer measurements.
 The eigenspace $E_{\text{high}}$ of the $L$ previously scanned objects $Q_1,Q_2,...,Q_L$ is pre-computed.
-Here, it is assumed that the test volume can be expressed as a sparse linear combination of the principal components (eigenvectors of the covariance matrix) obtained from a group of structurally similar volumes.
+Here, it is assumed that the test volume, barring the new changes, can be expressed as a sparse linear combination of the principal components (eigenvectors of the covariance matrix) obtained from a group of structurally similar volumes.
 Hence, the object-prior is represented by means of PCA.
@@
 The prior is built by computing the covariance matrix from the template set $\{Q_i\}_{i=1}^L$.
-\emph{The space spanned by the eigenvectors $\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance matrix is the global prior and is assumed to contain any test slice that is similar, but not necessarily identical to the object-prior.}  We use all of the $L-1$ orthogonal eigenvectors as a basis to represent the unknown test volume.
+The space spanned by the eigenvectors $\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance matrix is the object prior and is assumed to contain most of the test slice that is similar, but not necessarily identical to the object-prior.
+We use all of the $L-1$ orthogonal eigenvectors as a basis to represent the unknown test volume.
 Let $\boldsymbol{\mu}$ denote the mean of the previously scanned objects, and $\boldsymbol{\alpha}$ the vector of eigen-coefficients of the test scan, of which $\alpha_k$ is the $k^{\textrm{th}}$ element.
@@
  Optimal values of $\lambda_1, \lambda_2$ must be empirically chosen \textit{a priori}, based on the reconstructions of one of the template volumes (see also Sec.~\ref{sec:discussion}).
-The cost function described in Eq.~\ref{Eq:main_prior} is biconvex and the convergence of this optimization is guaranteed by the monotone convergence theorem.
+The cost function described in Eq.~\ref{Eq:main_prior} is biconvex and the convergence of this optimization is guaranteed by the monotone convergence theorem~\cite{monotone}.
  %---------------------------------------------------------
@@
    demonstrate reconstruction results from raw projection data.}
-In all figures in this section, `uniform prior' refers to optimizing Eq.~\ref{eq:spatially-varying_prior} with $\boldsymbol{W}(x,y,z)=1$.
+%In all figures in this section, `uniform prior' refers to optimizing Eq.~\ref{eq:spatially-varying_prior} with $\boldsymbol{W}(x,y,z)=1$.
 %----------------------------------------------------------
@@
 consisted of real cone-beam projections from 450 views, each of size
-$336\times156$. The corresponding size of the reconstructed volume is
-$338\times338\times123$. Prior to the first scan, two holes were
+336$\times$156. The corresponding size of the reconstructed volume is
+338$\times$338$\times$123. Prior to the first scan, two holes were
 drilled on the surface of the specimen. This was followed by four
@@
 object-prior after its preliminary pilot reconstruction. The ground
-truth consists of FDK reconstructed volumes from the the full set of
-450 view projections. The test volume was reconstructed from a partial
-set of 45 projections, i.e. $10\%$ of the projection views from which
-ground truth was reconstructed. The selected 3D ground truth of
-template volumes, the test volume as well as the 3D reconstructions
-can be seen in~\cite{supp_paper}. One of the slices of the
-reconstructed volumes is shown in Fig.~\ref{fig:okra_3D_results}. The
-red and green 3D RoI in the video and images show the regions where
-new changes are present. Based on the potato and the okra experiments,
-we see that our method is able to \emph{discover both} the presence of
-a new structure, as well as the absence of a structure.
+truth consists of volumes reconstructed using the Feldkamp-Davis-Kress
+(FDK) algorithm~\cite{FDK} from the full set of 450 view
+projections. The test volume was reconstructed from a partial set of
+45 projections, i.e., $10\%$ of the projection views from which ground
+truth was reconstructed. The selected 3D ground truth of template
+volumes, the test volume as well as the 3D reconstructions can be seen
+in the supplementary material~\cite{supp_paper}. One of the slices of
+the reconstructed volumes is shown in
+Fig.~\ref{fig:okra_3D_results}. The red and green 3D RoI in the video
+and images show the regions where new changes are present. Based on
+the potato and the okra experiments, we see that our method is able to
+\emph{discover both} the presence of a new structure, as well as the
+absence of a structure.
 
@@
 \caption{3D reconstruction of the okra from $10\%$ projection
-  views (b) has strong streak artefacts, (c) blurred, (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in ~\cite{supp_paper}.}
+  views (b) has strong streak artefacts, (c) blurred, (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
 \label{fig:okra_3D_results_uniform}
@@
                    &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{full Volume} & 1 (ideal)                     & 0.87        &  0.92       & \textcolor{red}{0.95}                                                                                   \\ \hline
+\textbf{full Volume} & 1 (ideal)                     & 0.83        &  0.87       & \textcolor{red}{0.89}                                                                                   \\ \hline
 \end{tabular}
@@
 sprout specimen imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size $130\times130\times130$. In contrast to the scientific
-experiment performed for the case of the okra and the potato where we
+(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size 130$\times$130$\times$130. In contrast to the scientific
+experiment performed for the case of the okra where we
 introduced man-made defects, the changes here are purely the work of
@@
        regions) and (e) new information detected in the regions of
-       interest. The reconstructed volumes can be viewed in
+       interest. The reconstructed volumes can be viewed in the supplementary material
        ~\cite{supp_paper}.} 
@@
                    & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{Full volume}   & 1 (ideal)                    & 0.82        & 0.71       & \textcolor{red}{0.92}                                                                                                                       \\ \hline
+\textbf{Full volume}   & 1 (ideal)                    & 0.91        & 0.82       & \textcolor{red}{0.95}                                                                                                                       \\ \hline
 \end{tabular}
@@
 %----------------------------------------------------------------------
-\section{Method: Spatially-Varying prior-based reconstruction}
+\section{Spatially-Varying prior-based reconstruction}
 \label{sec:method_spatially_varying_prior}
 
-Although the uniform global prior can be very useful in some
+Although the uniform prior can be very useful in some
 circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a major
@@
 sparse measurements, it dominates the regions with new changes masking
-the signal, as seen in Fig.~\ref{fig:RFA2_few_views}-d. Ideally, we
+the signal, as was seen earlier in Fig.~\ref{fig:RFA2_few_views}-d. Ideally, we
 will want to impose the prior only in the regions that are common
@@
 In regions of change in test data, we want lower weights for the prior when compared to regions that are similar to the prior.
-\vspace{2mm}
- \subsubsection{\textbf{Computation of weights matrix $\boldsymbol{W}$}}
+ \\
+
+\textbf{Computation of weights matrix $\boldsymbol{W}$:}
 Since the test volume (referred to as $\boldsymbol{x}$) is unknown to
@@
 objects (`object-prior'). We start with $X^{\text{fdk}}$, the initial
-backprojection reconstruction of the test volume using the
-Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} in an attempt to
+backprojection reconstruction of the test volume using FDK in an attempt to
 discover the difference between the object-prior and the test
@@
 described below.
-\vspace{2mm}
-\subsubsection{\textbf{Algorithm to compute weights-map $\boldsymbol{W}$}}
+\\
+
+\textbf{Algorithm to compute weights-map $\boldsymbol{W}$:}
 \label{sec:thealgo}
@@
 Let this projection be denoted by $P^j$.
-To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e.
-are similar to the template reconstructions).
-The rest, i.e.
-new changes and their reconstruction method-dependent-artefacts, are not captured by this projection and need to be eliminated.
+To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e., are similar to the template reconstructions).
+The rest, i.e., new changes and their reconstruction method-dependent-artefacts, are not captured by this projection and need to be eliminated.
   \end{enumerate}
@@
 We found that our final reconstruction results obtained by
-solving Eq.~\ref{eq:spatially-varying_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
+solving Eq.~\ref{eq:spatially-varying_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.\\
 %-------------------------------------------
-\subsubsection{\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights}}
-
+
+\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights:}
 %-----------------------------potato data
@@
      \end{subfigure}
-      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $V_{low}$) constructed using different reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}.
+      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $\boldsymbol{V_\text{low}}$) constructed using different reconstruction methods individually (a-f) and collectively (g) by fusing information from all reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}.
 The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
@@
      \end{subfigure}
-      \caption{(a)-(f):Different reconstructions of~\ref{fig:potato_test}.
+      \caption{(a)-(f):Different reconstructions of~\ref{fig:object-prior_test_potato_A1}(d).
 The magnitude and sharpness of the artefacts is different for each method.
@@
 tomographic data of biological and medical specimens. The results
-below demonstrate the advantage of the spatially-varying global prior
+below demonstrate the advantage of the spatially-varying prior
 method over the uniform method.
@@
   corresponding to red and green regions) while simultaneously
-  reducing streak artefacts. The reconstructed volumes can be viewed in ~\cite{supp_paper}.}
+  reducing streak artefacts. The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
 \label{fig:okra_3D_results}
@@
     l1-ls\end{tabular}} \\ \hline \textbf{red RoI} & 1 (ideal) & 0.74
-& 0.84 & 0.86 & \textcolor{red}{0.88} \\ \hline \textbf{green RoI} & 1
-(ideal) & 0.80 & \textcolor{red}{0.86} & 0.80 & \textcolor{red}{0.86}
+& 0.84 & 0.85 & \textcolor{red}{0.88} \\ \hline \textbf{green RoI} & 1
+(ideal) & 0.81 & 0.82 & 0.77 & \textcolor{red}{0.83}
 \\ \hline
@@
    prior dominates as can be seen in the blue and red regions) and
-   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed in ~\cite{supp_paper}.} 
+   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.} 
 \label{fig:sprouts_3D_results}
@@
                    & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{red RoI}   & 1 (ideal)                     & 0.85        & 0.84       & 0.83                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
+\textbf{red RoI}   & 1 (ideal)                     & 0.85        & 0.86       & 0.83                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
 \end{tabular}
@@
 1800 view projections. The test volume was reconstructed from partial
-set of 45 projections, i.e. $2.5\%$ of the projection views from which
+set of 45 projections, i.e., $2.5\%$ of the projection views from which
 ground truth was reconstructed. The selected 3D ground truth of
 template volumes, test volume, as well as the 3D reconstructions are
-shown in~\cite{supp_paper}. One of the slices of the reconstructed
+shown in the supplementary material~\cite{supp_paper}. One of the slices of the reconstructed
 volumes and its zoomed-in RoI are shown in
@@
 \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Slice being\\ imaged at\\ time t\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Probe distance from\\ tumor or \\ ablation stage\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ imaging\\ views\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Reconstruction\\ protocol: type \\ of global prior\end{tabular}} \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Slice being\\ imaged at\\ time t\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Probe distance from\\ tumor or \\ ablation stage\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ imaging\\ views\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Reconstruction\\ protocol: type \\ of prior\end{tabular}} \\ \hline
 Slice t=1 & Very far from tumor & 360 & l1-ls \\ \hline
@@
 An in-depth analysis of each of the results is presented in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior}.
-We now discuss the need for registration between object-prior and the test, the method that suits best when the data is homogeneous, and the effect of hyper-parameters on our reconstructions.
+We now discuss computation times, the method that suits best when the data is homogeneous, and the effect of hyper-parameters on our reconstructions.
 
@@
 \hline
-   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Spatially-Varying\\prior + l1-ls\end{tabular}} \\\hline
+   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}c@{}}Spatially-\\Varying\\ prior \\+ l1-ls\end{tabular}} \\\hline
 %\textbf{\begin{tabular}[c]{@{}c@{}}Potato\\size:(150,150,100)\\45 views\end{tabular}}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338,338,123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130,130,130)\\xx views\end{tabular}}  & 6 sec. & 3 hrs. & 60 min. &  \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338$\times$338$\times$123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130$\times$130$\times$130)\\xx views\end{tabular}}  & 6 sec. & 3 hrs. & 60 min. &  17 hrs.\\ \hline
 \end{tabular}
@@
 \end{table}
-
-\subsection{Issue of misalignment between test and templates}
-As with any global prior-based method, there is a need for the test volume to be registered with the object-prior.
-In all our longitudinal study experiments, the volumes were already aligned during imaging.
-However, if this were not the case, then the prior must be aligned to the test based on an initial pilot reconstruction of the test.
+\subsection{Computation time}
+The computation time for each of the methods is presented in Table~\ref{table:Computation_time_3D}.
+For spatially-varying prior, most of the computation time is used in the generation of low-quality eigen-space by reconstructing  each of the templates using CS and FDK.
+This process cannot be performed offline as it involves applying the same imaging geometry used for scanning the test.
+We had performed these reconstructions sequentially.
+Ideally, these reconstructions must be performed parallely on different machines to significantly reduce the computation time.
 
@@
 This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
-Measurements from each scan consisted of real cone-beam projections from 900 views, each of size $150\times150$.
-The corresponding size of the reconstructed volume is $150\times150\times100$.
+Measurements from each scan consisted of real cone-beam projections from 900 views, each of size 150$\times$150.
+The corresponding size of the reconstructed volume is 150$\times$150$\times$100.
 While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
@@
 The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views.
-The test volume was reconstructed using measurements from 45 projection views, i.e.
-$5\%$ of the projection views from which ground truth was reconstructed.
+The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed.
 The selected 3D
-ground truth of template volumes, test volume, as well as the 3D reconstructions are shown in~\cite{supp_paper}.
+ground truth of template volumes, test volume, as well as the 3D reconstructions are shown in the supplementary material~\cite{supp_paper}.
 Fig.~\ref{fig:potato_3D_results_A} shows a slice from the reconstructed 3D volume.
@@
 \caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts.
-The reconstructed volumes can be viewed in~\cite{supp_paper}.}
+The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
 \label{fig:potato_3D_results_A}
@@
 weights map starts capturing the new changes in the test, at the cost
-of detecting a few false positives i.e. false new changes. In other
+of detecting a few false positives i.e., false new changes. In other
 words, as the weights map becomes more sensitive to the difference
@@
 one can construct a binary weights-map using a learning based method
-described in~\cite{supp_paper}.
+described in the supplementary material~\cite{supp_paper}.
 
@@
 reconstruction in longitudinal studies. We show that we can either use
-the uniform global prior method or the spatially-varying prior method
+the uniform prior method or the spatially-varying prior method
 to our advantage, depending on our goal. We establish the context
@@
 objects used. We urge the reader to see the videos of reconstructed
-volumes in~\cite{supp_paper}.
+volumes in the supplementary material~\cite{supp_paper}.
 %Our method has been shown to make the best use of prior

### 2020-07-18 paper/tci.tex
Minor changes in the intro

@@
 ground truth image (260$\times$260) of naturally growing sprouts at the top
-left (the details of the dataset is postponed to
+left (the details of this dataset is postponed to
 Section~\ref{sec:results_uniform_prior}).
@@
 	\includegraphics[width=0.45\textwidth]{../images/story/story.png}
-        \caption{Illustration of the use of various priors as the
-          number of views reduces. For extremely large number of views
-          (600 views), the FBP reconstruction (first column) is of
-          very good quality (Structural Similarity Index Metric,
-          SSIM=0.92). As the number of views become limited (100
-          views), the reconstruction using sparsity prior (middle
-          column) is better both visually and quantitatively than FBP
-          (SSIM of 0.90 vs 0.83). If the number of views is
-          drastically reduced (30 views), the presence of both
-          sparsity prior and object prior improves the reconstruction
-          (SSIM = 0.85) when compared to presence of only sparsity
-          prior (SSIM = 0.82) or no prior (SSIM = 0.69). In all cases,
-          the ground truth (260x260) appears in the top left.}
+        \caption{Illustration of the use of various priors in the
+          reconstruction as the number of views reduces. In all cases,
+          the ground truth (260$\times$260) appears in the top left.
+          For extremely large number of views (600 views), the FBP
+          reconstruction (first column) is of very good quality
+          (Structural Similarity Index Metric, SSIM=0.92). As the
+          number of views become limited (100 views), the
+          reconstruction using sparsity prior (middle column) is
+          better both visually and quantitatively than FBP (SSIM of
+          0.90 vs 0.83). If the number of views is drastically reduced
+          (30 views), the presence of both sparsity prior and object
+          prior improves the reconstruction (SSIM=0.85) when compared
+          to presence of only sparsity prior (SSIM=0.82) or no prior
+          (SSIM=0.69).}
  \label{fig:story}
@@
 
- When the number of views is significantly reduced, the sparsity prior
- alone is not sufficient.  In such cases additional information
- specific to the object being scanned (i.e., object prior) is useful
- in further improving the reconstruction.  While this has been done in
- the context of dynamic CT-scans (as discussed in
+ When the number of views is significantly reduced (this paper), the
+ sparsity prior alone is not sufficient.  In such cases additional
+ information specific to the object being scanned (i.e., object prior)
+ is useful in further improving the reconstruction.  While this has
+ been done in the context of dynamic CT-scans (as discussed in
  Section~\ref{sec:related}), in this paper we use a set $S$ of
- previous scans of the same object that is more appropriate in a
- longitudinal context. Specifically, longitudinal studies here refers
- to the acquisition of sequential CT scans of the same subject to
- track time-evolving changes within the subject's interior. As seen in
- Fig.~\ref{fig:story} (last column, 30 views) our method uses the
- prior scans \emph{uniformly} by creating an eigenspace representation
- (Section~\ref{sec:method_uniform_prior}).
+ previous scans of the same object. This is relevant in a longitudinal
+ context: the acquisition of sequential CT scans of the same subject
+ in order to track time-evolving changes within the subject's
+ interior. As seen in Fig.~\ref{fig:story} (last column, 30 views) our
+ method uses the prior scans \emph{uniformly} by creating an
+ eigenspace representation (Section~\ref{sec:method_uniform_prior}).
 
  However, with the use of such an object prior, a new challenge
- emerges. The prior set S may potentially overwhelm the necessary
- details, or since several prior scans are available, finding the
- right prior may be an issue. We therefore seek an algorithm that
- estimates the location and magnitude of new changes in the (unknown)
- test. As we show in Section~\ref{sec:method_spatially_varying_prior},
- this eventually prevents the prior from adversely affecting the
+ emerges. The prior set $S$ may potentially overwhelm the necessary
+ details; when several prior scans are available, finding the right
+ prior is an issue. We therefore seek an algorithm that estimates the
+ location and magnitude of new changes in the (unknown) test. As we
+ show in Section~\ref{sec:method_spatially_varying_prior}, this
+ eventually prevents the prior from adversely affecting the
  reconstruction of new regions in the test. We refer to this method as
- a \textit{spatially-varying} prior-based reconstruction
- routine, that still uses \textit{all} the previous scans in the set $S$.
+ a \textit{spatially-varying} prior-based reconstruction routine, that
+ still uses \textit{all} the previous scans in the set $S$, without
+ using simply the prior scan, or endeavoring to find the ``right'' prior.
 

### 2020-07-18 paper/tci.tex
added "Datasets" and other changes

--- 2020-07-17 paper/tci.tex
@@
 \label{sec:related}
-The idea of using a reduced number of views is most pronounced in
-specialized applications. For example, in~\cite{Essam2015},
-sparsity-constrained optimization is presented for angiography. Here,
-the regions of interest are the vessels alone and they are highlighted
-by physically inserting a contrast agent, and therefore there is a
-inherent sharper contrast between the vessels and the background.  In
-other applications where the spatial-gradient of the underlying volume
-is known to be sparse, the `total variation' method, as used
-in~\cite{Li2015,Polak2017} can be applied.  In a more generalized
-application scenario, like the ones addressed in this paper, any
-information about the regions of interest is not known, and such
-techniques have limited applicability.
-
-%  As can be seen
-% in the situatiowe will
-% later see in Figs.\ref{fig:object-prior_test_okra}
-% and~\ref{fig:object-prior_test_sprouts}, the spatial-gradient of many
-% datasets is not sparse.
-
-Most object-prior based reconstruction has been in the areas of
-dynamic CT and 4D-CT. In dynamic CT, the object being scanned
-undergoes changes between successive projection views and hence is not
-stationary even within a single complete scan. In contrast, in 4D-CT,
-a set of 3D CT scans are taken over short intervals of time, and the
-object undergoes changes between successive scans.  The reconstruction
-is then performed over the entire set generating several 3D
-volumes. ~\cite{PICCS} is one of the earliest work to establish the
-use of object-prior along with sparsity prior in dynamic CT, in an
-attempt to reduce the number of views. The limitation is the
-unchecked over-emphasis of the prior on the reconstruction of the test
-at hand. This limitation was later dealt with by applying very
-specific object-properties for reconstruction. For example,
-in~\cite{Van2015}, the knowledge of the attenuation coefficient of the
-fluid is used as a prior for reconstructing its flow through
-gravel. In~\cite{Koen2020}, the changes across the sucessive scan
-volumes are assumed to be continuous, thus enabling the use of optical
-flow to model the motion between corresponding voxels of different
-scan volumes. In another study~\cite{vincent2017}, changes between
-successive scans were modelled by affine deformation whose parameters
-were computed for motion-correction. Such a correction enables
-acquisition from fewer views than would have otherwise not been
-possible for reconstruction with adequate
-fidelity. In~\cite{daniil2015}, all the scan volumes are reconstructed
-together using spatio-temporal regularization.
+In this section, we survey the existing literature on tomographic reconstruction from undersampled measurements using object priors.
+In most cases, the object prior consists of an object reconstructed to high quality from a large number of projection angles.
+One of the earliest pieces of work in this area is the well-cited PICCS method~\cite{PICCS}, which enforces a robust-norm based similarity between the object to be reconstructed (called the `test' henceforth) and the object prior, in addition to a sparsity prior on the test.
+However in such a technique, there is no inherent mechanism to prevent the prior from overwhelming the current reconstruction, and choice of relative weights between the object and sparsity priors is difficult.
+A closely related method called PIRPLE was proposed in~\cite{pirple}, with additional steps to register the object prior and the test and a somewhat more flexible combination of data fidelity terms, sparsity prior and object prior.
+However, this method too has similar limitations as PICCS.
+In some pieces of work, the object prior is projected in the same angles as the current set of test measurements, and a set of projection differences is computed.
+These projection differences are essentially tomographic projections of the difference between the unknown test and the known object prior.
+Hence, a variety of reconstruction algorithms can be used to estimate such a difference image which can then be added to the object prior to yield the final estimate of the test.
+Such methods have been proposed in~\cite{Pourmorteza2015,Lee2012}.
+However, the reconstruction of the difference image will inherently contain artifacts due to a sparse set of projections, and these artifacts will appear in the final reconstruction as there is no mechanism to mitigate them (unlike the method that we propose).
+In some recent techniques such as~\cite{Marjolein2016}, additional knowledge regarding regions of most likely change between the test and object prior is assumed, and lower weights are assigned to the prior in those regions.
+However, this is not done in a data driven manner and relies on additional expert domain knowledge which may not be available or which may be infeasible to acquire.
+There exists a fairly large-sized body of literature for reconstruction of structurally changing objects.
+In such cases, it may be infeasible to gather a large number of projections at every time instant.
+Moreover, there is additional temporal redundancy available which can reduce the required sample complexity for good reconstruction, and at the same time, tracking structural changes across time is of paramount importance.
+Many interesting approaches for this have been proposed in~\cite{daniil2015,koen2020, Van2015,HaoGao,Van2014}.
+These approaches variously use 4D sparsifying transforms for exploiting spatio-temporal redundancy~\cite{daniil2015}, robust principal components analysis assuming that the object consists of a large static part (background) and a sparse moving part (foreground)~\cite{HaoGao}, optical flow computations between projections (at different time instances) of the dynamic nonrigid object~\cite{koen2020} with additional key-frame and residual modelling in~\cite{Guangming2019}, spline-based models for tracking the regions of change in an SIRT framework~\cite{Van2014}, or knowledge of fluid models (piecewise constant shapes of attenuation curves in the dynamic region) in an SIRT framework~\cite{HaoGao}.
+However all these techniques ~\cite{daniil2015,koen2020,Van2015,HaoGao,Van2014} essentially reconstruct all the different stages of the object simultaneously, and use the extra redundancy across time simultaneously.
+However, in the scenario of a longitudinal study (where projection measurements are acquired at instants that are several weeks apart) which we consider in this paper, such approaches are not feasible.
+A longitudinal study will necessarily require reconstruction results after acquisition of each set of measurements.
+In this paper, we present a technique that makes use of multiple object priors, corresponding to high quality reconstructions of similar objects across time.
+We use these priors to improve the reconstruction of the test from largely undersampled measurements.
+In particular, we define the regions of change between the test and the eigenspace spanned by the previous high quality object priors in a purely data driven manner.
+Very importantly, our technique clearly differentiates between genuine structural changes and ``changes'' that appear due to undersampling artefacts.
+Since we use a statistical model with multiple object priors, we avoid the problem of selecting an appropriate single object prior unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and also make use of the additional information available in the multiple priors.
 
@@
 \begin{itemize}
-\item We create and present new 3D biological datasets, and as seen in
-  Fig.~\ref{fig:story} demonstrate the use of object priors when very
-  few views are used. More results appear in
-  Section~\ref{sec:results_uniform_prior} and in the supplementary
-  material.  Our results consist of 3D reconstructions from real
-  cone-beam projections.
-  \item The scenarios where a uniform object prior is sufficient for
-    the application at hand, and the scenarios for which it will fail,
-    are demonstrated. This leads to the idea of a weights map
+\item We create new 3D biological datasets (Section~\ref{sec:datasets}) and
+  present results on real cone-beam projections. Our datasets and code
+  will be made available to the community.
+  \item As seen in Fig.~\ref{fig:story}, we demonstrate the use of
+    uniform priors when very few views are used. More results appear
+    in Section~\ref{sec:results_uniform_prior} and in the
+    supplementary material.
+  \item We discuss the scenarios where a uniform object prior is
+    sufficient for the application at hand, and the scenarios for
+    which it will fail . This leads to the idea of a weights map
     designed to depict the location and strength of new changes at
@@
 
+%-------------------------------Dataset----------------------------
+\section{Datasets}
+\label{sec:datasets}
+In this sections, we lay the details of all the datasets used in this work.
+\subsection{Real measurements of scanned volumes}
+These datasets in the form of raw cone-beam projection measurements were acquired from a lab
+ at the Australian National University (ANU). Data from commercially
+ available CT machines is not suitable because most CT scanners do
+ not reveal the raw measurements, and instead output only the full
+ reconstructed volumes. Moreover, the process of conversion from the
+ projections to the full volumes is proprietary. Departing from this, we
+ demonstrate reconstruction results (in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior} from the following raw projection data.\\
+
+\textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
+scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
+consisted of real circular cone-beam projections from 450 views, each of size
+336$\times$156. The corresponding size of the reconstructed volume is
+338$\times$338$\times$123. Prior to the first scan, two holes were
+drilled on the surface of the specimen. This was followed by four
+scans, each after introducing one new cut. The specimen was kept in
+the same position throughout the acquisitions. In cases where such an
+alignment is not present, all the template volumes must be pre-aligned
+before computing the eigenspace. The test must be registered to the
+object-prior after its preliminary pilot reconstruction. The ground
+truth consists of volumes reconstructed using the Feldkamp-Davis-Kress
+(FDK) algorithm~\cite{FDK} from the full set of 450 view
+projections. The test volume was reconstructed from a partial set of
+45 projections, i.e., $10\%$ of the projection views from which ground
+truth was reconstructed.\\
+
+\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
+Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150.
+The corresponding size of the reconstructed volume is 150$\times$150$\times$100.
+While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
+Projections were obtained using circular cone beam geometry.
+%Further, this alignment can be refined following every update of the reconstructed test volume.
+The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views.
+The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed.
+\subsection{Simulated measurements from real-life reconstructed volumes}
+\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU, consists of six reconstructed
+volumes corresponding to six scans of an in-vivo sprout specimen
+imaged at its various stages of growth
+(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated
+from the given volume of size 130$\times$130$\times$130. The ground
+truth consists of FDK reconstructed volumes from a set of 1800 view
+projections. The test volume was reconstructed from partial set of 45
+projections, i.e., $2.5\%$ of the projection views from which ground
+truth was reconstructed.\\
+
+\textbf{Radio-frequency ablation:} We have used this dataset to
+illustrate an application where \textit{both} uniform and spatially-varying priors are
+useful. The data~\footnote{Source: Tata Memorial
+  Centre~\cite{tmh}, Parel, Mumbai.  This is the national
+  comprehensive centre for the prevention, treatment, education and
+  research in cancer, and is recognized as one of the leading cancer
+  centres in India.} consists of simulated parallel beam measurements of 2D slices
+of the organ (liver) at different stages of the scan. The details of this study are presented in the next section.
+
 %--------------------------------THM section-------------------------
@@
 techniques can be applied to our advantage in a real-life medical
-longitudinal study. Here, our data~\footnote{Source: Tata Memorial
-  Centre~\cite{tmh}, Parel, Mumbai.  This is the national
-  comprehensive centre for the prevention, treatment, education and
-  research in cancer, and is recognized as one of the leading cancer
-  centres in India.} consists of successive scans of the liver taken
+longitudinal study. Here, our data consists of successive scans of the liver taken
 during a radio-frequency ablation procedure. In such a
@@
 
- The proposed method has been validated on new\footnote {These and our
-   code will be made available to the community.} scans of biological
- specimens in a longitudinal setting. These datasets in the form of
- \emph{raw cone-beam projection measurements} were acquired from a lab
- at the Australian National University (ANU). Data from commercially
- available CT machines is not suitable because most CT scanners do
- not reveal the raw measurements, and instead output only the full
- reconstructed volumes. Moreover, the process of conversion from the
- projections to the full volumes is proprietary.
+ The proposed method has been validated on new scans of biological
+ specimens in a longitudinal setting. 
  %We emphasize that in
@@
  %the full volumes is proprietary.
- \emph{Departing from this, we
-   demonstrate reconstruction results from raw projection data.}
+
 %In all figures in this section, `uniform prior' refers to optimizing Eq.~\ref{eq:spatially-varying_prior} with $\boldsymbol{W}(x,y,z)=1$.
@@
 \label{Sec:okra_uniform}
-Our first dataset is that of an Okra specimen consisting of its five
-scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
-consisted of real cone-beam projections from 450 views, each of size
-336$\times$156. The corresponding size of the reconstructed volume is
-338$\times$338$\times$123. Prior to the first scan, two holes were
-drilled on the surface of the specimen. This was followed by four
-scans, each after introducing one new cut. The specimen was kept in
-the same position throughout the acquisitions. In cases where such an
-alignment is not present, all the template volumes must be pre-aligned
-before computing the eigenspace. The test must be registered to the
-object-prior after its preliminary pilot reconstruction. The ground
-truth consists of volumes reconstructed using the Feldkamp-Davis-Kress
-(FDK) algorithm~\cite{FDK} from the full set of 450 view
-projections. The test volume was reconstructed from a partial set of
-45 projections, i.e., $10\%$ of the projection views from which ground
-truth was reconstructed. The selected 3D ground truth of template
-volumes, the test volume as well as the 3D reconstructions can be seen
-in the supplementary material~\cite{supp_paper}. One of the slices of
-the reconstructed volumes is shown in
-Fig.~\ref{fig:okra_3D_results}. The red and green 3D RoI in the video
-and images show the regions where new changes are present. Based on
-the potato and the okra experiments, we see that our method is able to
-\emph{discover both} the presence of a new structure, as well as the
-absence of a structure.
+ One of the slices of the reconstructed volumes is shown in
+ Fig.~\ref{fig:okra_3D_results_uniform}. The SSIM values presented in
+ Table~\ref{table:okra_ssim_full_volume} show that the presence of a
+ unifrom object prior significantly improves the overall
+ reconstruction in comparison with the usage of sparsity prior alone.
+ The selected 3D ground truth of template volumes, the test volume as
+ well as the 3D reconstructions can be seen in the supplementary
+ material~\cite{supp_paper}.
 
@@
 \end{table}
+%----------------------------------------------------
 \subsubsection{\textbf{Sprouts dataset}}
 \label{Sec:sprouts}
-The second dataset consists of six scans of an in vivo
-sprout specimen imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size 130$\times$130$\times$130. In contrast to the scientific
-experiment performed for the case of the okra where we
-introduced man-made defects, the changes here are purely the work of
-nature.
+ In contrast to the scientific experiment performed for the case of
+ the okra where we introduced man-made defects, the changes here are
+ purely the work of nature. One of the slices of the reconstructed
+ volumes is shown in
+ Fig.~\ref{fig:sprouts_3D_results_uniform}. Table~\ref{table:sprouts_ssim_full_volume}
+ shows the SSIM of the full reconstructed volumes.  Here again, the
+ presence of a unifrom object prior significantly improves the overall
+ reconstruction in comparison with the usage of sparsity prior alone.
+ The selected 3D ground truth of template volumes, the test volume as
+ well as the 3D reconstructions can be seen in the supplementary
+ material~\cite{supp_paper}.
 %-------------------------sprouts data
@@
        ~\cite{supp_paper}.} 
-\label{fig:sprouts_3D_results}
+\label{fig:sprouts_3D_results_uniform}
 %\addtolength{\textfloatsep}{-0.8cm}
@@
 \end{tabular}
-\label{table:sprouts_ssim}
+\label{table:sprouts_ssim_full_volume}
 \end{table}
@@
 
+\subsubsection{\textbf{Okra dataset}}
+\label{Sec:okra_spatially_varying}
+The red and green 3D RoI in the video
+and images show the regions where new changes are present.
+
 %----------------------------------------------------
@@
 \subsubsection{\textbf{Sprouts dataset}}
-\label{Sec:sprouts}
+\label{Sec:sprouts_spatially_varying}
  %-----------------------------sprouts 3D results
@@
 \end{table}
-The ground truth consists of FDK reconstructed volumes from a set of
-1800 view projections. The test volume was reconstructed from partial
-set of 45 projections, i.e., $2.5\%$ of the projection views from which
-ground truth was reconstructed. The selected 3D ground truth of
+ The selected 3D ground truth of
 template volumes, test volume, as well as the 3D reconstructions are
@@
 While the design of the weights map in the proposed algorithm aims to combine the best of information from both the current measurements and the prior, we found FDK to be preferable when the test object has a simple, homogeneous structure without intricate details.
-One such dataset is the Potato dataset, the results on which are detailed here.\\
-This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
-Measurements from each scan consisted of real cone-beam projections from 900 views, each of size 150$\times$150.
-The corresponding size of the reconstructed volume is 150$\times$150$\times$100.
-While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
-Projections were obtained using circular cone beam geometry.
-%Further, this alignment can be refined following every update of the reconstructed test volume.
-The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views.
-The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed.
+One such dataset is the Potato dataset.\\
  The selected 3D
@@
 reconstruction in longitudinal studies. We show that we can either use
-the uniform prior method or the spatially-varying prior method
-to our advantage, depending on our goal. We establish the context
-under which these methods can be used, as outlined in
+the uniform prior method or the spatially-varying prior method to our
+advantage, depending on our goal. We establish the context under which
+these methods can be used, as outlined in
 Fig.~\ref{fig:prior_overview}. When we wish to approximately know the
@@
 reconstruction of localized new information in the data is not
-affected by the priors. We have thus improved the state of the art by
-detecting these regions of change and assigning low prior weights
-wherever necessary. The probability of presence of a `new region' is
-enhanced considerably by a novel combination of different
-reconstruction techniques.  We have validated our technique on medical
-2D and real, biological 3D datasets for longitudinal studies. The
-method is also largely robust to the number of previously scanned
-objects used. We urge the reader to see the videos of reconstructed
-volumes in the supplementary material~\cite{supp_paper}.
+affected by the priors. Based on the potato and the okra experiments,
+we see that our method is able to \emph{discover both} the presence of
+a new structure, as well as the absence of a structure. We have thus
+improved the state of the art by detecting these regions of change and
+assigning low prior weights wherever necessary. The probability of
+presence of a `new region' is enhanced considerably by a novel
+combination of different reconstruction techniques.  We have validated
+our technique on medical 2D and real, biological 3D datasets for
+longitudinal studies. The method is also largely robust to the number
+of previously scanned objects used. We urge the reader to see the
+videos of reconstructed volumes in the supplementary
+material~\cite{supp_paper}.
 %Our method has been shown to make the best use of prior

### 2020-07-18 paper/tci.tex
Rearranged dataset figures

@@
 truth was reconstructed.\\
+ %--------------------------------okra data-------------------------------
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.176\linewidth}
+        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/testCropped.png}}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
+       first four from the left), and one from the test volume
+       (extreme right). In the regions marked in red and green, while
+       all slices have deformities, the test
+       has none.}
+\label{fig:object-prior_test_okra}
+\end{figure}
+%----------------------------------------------------
 
@@
 The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed.
+%---------------------------------------
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.235\linewidth}
+        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_green.png}}
+\captionsetup{labelformat=empty}
+\caption{}
+\label{fig:potato3D_test}
+     \end{subfigure}
+      \caption{Potato 3D dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
+        volume (extreme right). Notice the appearance of the fourth
+        hole in the test slice. }
+\label{fig:object-prior_test_potato_A}
+\end{figure}
+
 \subsection{Simulated measurements from real-life reconstructed volumes}
@@
 truth was reconstructed.\\
+%-------------------------sprouts data
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+    \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}\\
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.29\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
+        right).}
+\label{fig:object-prior_test_sprouts}
+\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
 
@@
 of the organ (liver) at different stages of the scan. The details of this study are presented in the next section.
+%--------------------------Results on TMH data--------------------------
+%------------------RFA 2 data
+\begin{figure}[h!]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 2}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 3}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 4}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 5}
+    \end{subfigure}
+              \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 6}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 7}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 8}
+    \end{subfigure}     
+     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver.
+Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.
+(h) the organ after the ablation: this slice is displayed on a separate intensity scale to enable proper viewing of the region marked in green that shows the after-effects of ablating the tumor.}
+\label{fig:RFA2_test_object-prior}
+\end{figure}
 
@@
 \end{enumerate}
-
-%--------------------------Results on TMH data--------------------------
-%------------------RFA 2 data
-\begin{figure}[h!]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 1}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 2}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 3}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 4}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 5}
-    \end{subfigure}
-              \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 6}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 7}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 8}
-    \end{subfigure}     
-     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver.
-Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.
-(h) the organ after the ablation: this slice is displayed on a separate intensity scale to enable proper viewing of the region marked in green that shows the after-effects of ablating the tumor.}
-\label{fig:RFA2_test_object-prior}
-\end{figure}
 
@@
 
- %--------------------------------okra data-------------------------------
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.176\linewidth}
-        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/test.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
-       first four from the left), and one from the test volume
-       (extreme right). In the regions marked in red and green, while
-       all slices have deformities, the test
-       has none.}
-\label{fig:object-prior_test_okra}
-\end{figure}
-%----------------------------------------------------
-
 \begin{figure}[!h]
@@
  material~\cite{supp_paper}.
-%-------------------------sprouts data
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-    \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}\\
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.29\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
-        right).}
-\label{fig:object-prior_test_sprouts}
-\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
+
  %-----------------------------sprouts 3D results
@@
 \textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights:}
+
 %-----------------------------potato data
@@
 \end{figure}
-
 %-----------------------------potato 2D weights
@@
 Hence, in practice, one may choose FDK for the case of simple, homogeneous dataset with smaller RoI,  and prefer spatially-varying prior-based reconstruction when the dataset is complex and RoIs are larger.
-%---------------------------------------
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_green.png}}
-\captionsetup{labelformat=empty}
-\caption{}
-\label{fig:potato3D_test}
-     \end{subfigure}
-      \caption{Potato 3D dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
-        volume (extreme right). Notice the appearance of the fourth
-        hole in the test slice. }
-\label{fig:object-prior_test_potato_A}
-\end{figure}
 

### 2020-07-18 paper/tci.tex
Sec"datasets" completed.

@@
  \textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
-scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
+scans (Figure~\ref{fig:object-prior_test_okra}). The measurements
 consisted of real circular cone-beam projections from 450 views, each of size
@@
 
-\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
+\textbf{Potato:} This dataset consisted of four scans of the humble potato (Figure~\ref{fig:object-prior_test_potato_A}).
 Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150.
@@
 imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated
+(Figure~\ref{fig:object-prior_test_sprouts}). Projections were generated
 from the given volume of size 130$\times$130$\times$130. The ground
@@
 
-\textbf{Radio-frequency ablation:} We have used this dataset to
+\textbf{Radio-frequency ablation:} We have used this dataset (Figure~\ref{fig:RFA2_test_object-prior} to
 illustrate an application where \textit{both} uniform and spatially-varying priors are
@@
 
-The proposed method has been validated on 2D and 3D synthetic and real
-tomographic data of biological and medical specimens. The results
-below demonstrate the advantage of the spatially-varying prior
-method over the uniform method.
+%The proposed method has been validated on 2D and 3D synthetic and real
+%tomographic data of biological and medical specimens.
+The results below show the advantage of spatially-varying prior over uniform prior while reconstructing details of the new changes within the object.
 
@@
 \label{Sec:okra_spatially_varying}
-The red and green 3D RoI in the video
-and images show the regions where new changes are present.
+One of the slices from the reconstructed volumes 
+is shown in Figure.~\ref{fig:okra_3D_results}. The red and green 3D
+RoI in the video and images show the regions where new changes are
+present. The zoomed-in images around the major region of change (red
+RoI) is shown in Figure~\ref{fig:okra_zoomed_3D_results}. As in the
+test, the reconstruction by spatially-varying method shows the absence
+of the deformity and better removal of sub-sampling artefacts when
+compared to FDK and l1-ls. This is also seen in the SSIM values in
+Table~\ref{table:okra_ssim}.
 
@@
 other changes can be viewed in the video. Tables~\ref{table:okra_ssim}
-and \ref{table:sprouts_ssim} show the improvement in the Structure
-Similarity Index (SSIM) of the reconstructed new regions as compared
+and \ref{table:sprouts_ssim} show the improvement in SSIM of the reconstructed new regions as compared
 to other methods.
 
-\subsection{\textbf{More results on CT-guided radio-frequency ablation data}}
+%--------------------------------------------------------------------------
+
+\section{Discussion}
+\label{sec:discussion}
+The presented uniform prior-based algorithm is suited to applications
+where we wish to detect the location of new changes in an object over
+time, and the presented spatially-varying prior-based algorithm is
+suited to applications where we wish to observe the intricate details
+of those new changes. This distinction in the techniques used has not
+been studied earlier in
+literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our
+knowledge.
+Even though methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
+We have presented a principled method of tackling this particular issue via our weights map.
+We not only estimate the location of new changes, but also compute their intensities.
+This information is then used to modulate the strength of the prior during the reconstruction of the test.
+Our results consist of 3D reconstructions from real cone-beam projections of two datasets, and both 3D and 2D reconstructions from cone-beam and parallel beam projections respectively.
+In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
+An in-depth analysis of each of the results is presented in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior}.
+We now discuss computation times, the method that suits best when the data is homogeneous, and the effect of hyper-parameters on our reconstructions.
+
+\subsection{\textbf{Realistic imaging protocol}}
 
@@
 \end{table}
-
-%--------------------------------------------------------------------------
-
-\section{Discussion}
-\label{sec:discussion}
-The presented uniform prior-based algorithm is suited to applications
-where we wish to detect the location of new changes in an object over
-time, and the presented spatially-varying prior-based algorithm is
-suited to applications where we wish to observe the intricate details
-of those new changes. This distinction in the techniques used has not
-been studied earlier in
-literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our
-knowledge.
-Even though methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
-We have presented a principled method of tackling this particular issue via our weights map.
-We not only estimate the location of new changes, but also compute their intensities.
-This information is then used to modulate the strength of the prior during the reconstruction of the test.
-Our results consist of 3D reconstructions from real cone-beam projections of two datasets, and both 3D and 2D reconstructions from cone-beam and parallel beam projections respectively.
-In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
-An in-depth analysis of each of the results is presented in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior}.
-We now discuss computation times, the method that suits best when the data is homogeneous, and the effect of hyper-parameters on our reconstructions.
-
+%-----------------------------------------
 \begin{table}[!h]

### 2020-07-20 paper/supplementary.tex
edited figures,supplemetary material

@@
 \end{figure}
-----------------------------------------------------------------------------------------------------------------------------------
+\newpage
+%--------------------------BIG images: TMH results
+\section{Bigger images for reconstruction results shown in main paper}
+\subsection{Liver}
+%-------RFA2 moderate views
+\textbf{Goal: Observe details of new changes}
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
+\subcaptionbox{Spatially-varying prior}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
+\caption[Representative results-2]{Reconstruction of Liver corresponding to Figure 8 of the main paper.}
+\label{fig:RFA2_few_views_biggerIm}
+\end{figure}
+\newpage
+
+\textbf{Test image Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+\centering
+\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}
+\captionsetup{labelformat=empty}
+\caption[Representative results-2]{\large{Test slice}}
+\label{fig:RFA2_few_views_bigger}
+\end{figure}
+\newpage
+\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+\centering
+\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}
+\captionsetup{labelformat=empty}
+\caption[Representative results-2]{\large{FBP}}
+\label{fig:RFA2_few_views_bigger}
+\end{figure}
+\newpage
+\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+\centering
+\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}
+\captionsetup{labelformat=empty}
+\caption[Representative results-2]{\large{l1-ls}}
+\label{fig:RFA2_few_views_bigger}
+\end{figure}
+\newpage
+\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm} is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+\centering
+\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}
+\captionsetup{labelformat=empty}
+\caption[Representative results-2]{\large{Spatially-varying prior method}}
+\label{fig:RFA2_few_views_bigger}
+\end{figure}
+\newpage
+
+%------------------------------------Bigger images for Sprouts------------------
+\textbf{Sprouts:}
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.4\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{FDK}
+    \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{l1-ls}
+     \end{subfigure}\\
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{Uniform\\ Prior}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{Spatially-Varying\\ prior}
+    \end{subfigure}
+    %\quad
+    %\captionsetup{labelformat=empty}
+     \caption{Reconstruction of sprouts corresponding to Figure 16 of the main paper.} 
+\label{fig:sprouts_3D_results_biggerIm}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\newpage
+\textbf{Test image of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+    \begin{subfigure}[b]{\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+\captionsetup{labelformat=empty}
+        \caption{\large{Test}}
+     \end{subfigure}
+\end{figure}
+\newpage
+\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+    \begin{subfigure}[b]{\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}}
+\captionsetup{labelformat=empty}
+        \caption{\large{FDK}}
+     \end{subfigure}
+\end{figure}
+\newpage
+\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+    \begin{subfigure}[b]{\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/csIm.png}}
+\captionsetup{labelformat=empty}
+        \caption{\large{l1-ls}}
+     \end{subfigure}
+\end{figure}
+\newpage
+\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+    \begin{subfigure}[b]{\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}}
+\captionsetup{labelformat=empty}
+        \caption{\large{Uniform Prior}}
+     \end{subfigure}
+\end{figure}
+\newpage
+\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\begin{figure}[!h]
+    \begin{subfigure}[b]{\linewidth}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}}
+\captionsetup{labelformat=empty}
+        \caption{\large{Spatially-Varying Prior}}
+     \end{subfigure}
+\end{figure}
+\newpage
+
+%--------------------------------Bigger results for Okra------------------------
+\textbf{Okra:}
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.2\columnwidth]{../images/okra/testCropped.png}}}\hfill
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.2\columnwidth]{../images/okra/cs_cropped.png}}\hfill
+\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/prior_weighted_cropped.png}}
+\caption{Reconstruction of okra corresponding to Figure 14 of the main paper.}
+\label{fig:okra_3D_results_biggerIm}
+\end{figure}
+\newpage
+\textbf{Test image of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=0.5\columnwidth]{../images/okra/testCropped.png}
+\captionsetup{labelformat=empty}
+        \caption{\large{Test}}
+\end{figure}
+\newpage
+
+\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=0.5\columnwidth]{../images/okra/fdk_cropped.png}
+\captionsetup{labelformat=empty}
+        \caption{\large{FDK}}
+\end{figure}
+\newpage
+
+\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=0.5\columnwidth]{../images/okra/cs_cropped.png}
+\captionsetup{labelformat=empty}
+        \caption{\large{l1-ls}}
+\end{figure}
+\newpage
+
+\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=0.5\columnwidth]{../images/okra/pca_cropped.png}
+\captionsetup{labelformat=empty}
+        \caption{\large{Uniform Prior}}
+\end{figure}
+\newpage
+
+\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=0.5\columnwidth]{../images/okra/prior_weighted_cropped.png}
+\captionsetup{labelformat=empty}
+        \caption{\large{Spatially-Varying prior}}
+\end{figure}
+\newpage
+
+%----------------------------------Comparison with Literature------------------------
+\section{Detecting new changes directly in the measurements}
+Sec.2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature.
+Here we present a 2D reconstruction  result (of the test shown in Figure.~\ref{fig:comparisonLit_dataset}) to compare our method with~\cite{Lee2012}, in which the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
+This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
+However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image.
+This is shown in Figure~\ref{fig:comparisonLit_results}.
+A quantitative comparison over the region of interest is shown in Table~\ref{tab:comparisonLit}.
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+%\captionsetup{labelformat=empty}
+        \caption{Template}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/testIm_color.png}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Template and test from the Potato dataset for the reconstructions shown in Figure.~\ref{fig:comparisonLit_results}} 
+\label{fig:comparisonLit_dataset}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+\newpage
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/result_new_changes.png}
+%\captionsetup{labelformat=empty}
+        \caption{~\cite{Lee2012}:new-changes}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/result_literature_test.png}
+%\captionsetup{labelformat=empty}
+        \caption{~\cite{Lee2012}:Reconstruction}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/weightsIm_all_methods30.png}
+%\captionsetup{labelformat=empty}
+        \caption{Our weights-map}
+    \end{subfigure}
+   \quad
+        \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/weighted_pca_all_methods30.png}
+%\captionsetup{labelformat=empty}
+        \caption{Our Reconstruction}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Reconstruction of the test in Figure~\ref{fig:comparisonLit_dataset}.
+Reconstructions were performed from 12 views.
+Gaussian noise of 0 mean and SD = $1\%$ of mean of measurements, was added to the measurements.}
+\label{fig:comparisonLit_results}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\begin{table}[!h]
+  \centering
+      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}}
+  \begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
+\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
+\textbf{\begin{tabular}[c]{@{}l@{}}Spatially-varying \\prior\end{tabular}} & 0.89 & 0.92 \\ \hline
+  \end{tabular}
+  \label{tab:comparisonLit}
+\end{table}
+
 \bibliography{tci_ref}

### 2020-07-20 paper/tci.tex
minor edit
edited figures,supplemetary material

@@
  sparsity prior alone is not sufficient.  In such cases additional
- information specific to the object being scanned (i.e., object prior)
- is useful in further improving the reconstruction.  While this has
- been done in the context of dynamic CT-scans (as discussed in
+ information (called the `object-prior') specific to the current
+ object being scanned (called the `test' henceforth) is useful in
+ further improving the reconstruction.  While this has been done in
+ the context of dynamic CT-scans (as discussed in
  Section~\ref{sec:related}), in this paper we use a set $S$ of
@@
  emerges. The prior set $S$ may potentially overwhelm the necessary
- details; when several prior scans are available, finding the right
- prior is an issue. We therefore seek an algorithm that estimates the
- location and magnitude of new changes in the (unknown) test. As we
- show in Section~\ref{sec:method_spatially_varying_prior}, this
- eventually prevents the prior from adversely affecting the
- reconstruction of new regions in the test. We refer to this method as
- a \textit{spatially-varying} prior-based reconstruction routine, that
+ details, and when several prior scans are available, finding the
+ right prior is an issue. We therefore seek an algorithm that
+ estimates the location and magnitude of new changes in the
+ (unknown) test. As we show in
+ Section~\ref{sec:method_spatially_varying_prior}, this eventually
+ prevents the prior from adversely affecting the reconstruction of new
+ regions in the test. We refer to this method as a
+ \textit{spatially-varying} prior-based reconstruction routine, that
  still uses \textit{all} the previous scans in the set $S$, without
- using simply the prior scan, or endeavoring to find the ``right'' prior.
+ using simply the prior scan, or endeavoring to find the ``right''
+ prior.
 
@@
 In most cases, the object prior consists of an object reconstructed to high quality from a large number of projection angles.
-One of the earliest pieces of work in this area is the well-cited PICCS method~\cite{PICCS}, which enforces a robust-norm based similarity between the object to be reconstructed (called the `test' henceforth) and the object prior, in addition to a sparsity prior on the test.
+One of the earliest pieces of work in this area is the well-cited PICCS method~\cite{PICCS}, which enforces a robust-norm based similarity between the test and the object prior, in addition to a sparsity prior on the test.
 However in such a technique, there is no inherent mechanism to prevent the prior from overwhelming the current reconstruction, and choice of relative weights between the object and sparsity priors is difficult.
@@
 However, the reconstruction of the difference image will inherently contain artifacts due to a sparse set of projections, and these artifacts will appear in the final reconstruction as there is no mechanism to mitigate them (unlike the method that we propose).
+This can be seen in Sec.7 of our supplementary material~\cite{supp_paper}, where we have compared our method with~\cite{Lee2012}.
 In some recent techniques such as~\cite{Marjolein2016}, additional knowledge regarding regions of most likely change between the test and object prior is assumed, and lower weights are assigned to the prior in those regions.
@@
 These approaches variously use 4D sparsifying transforms for exploiting spatio-temporal redundancy~\cite{daniil2015}, robust principal components analysis assuming that the object consists of a large static part (background) and a sparse moving part (foreground)~\cite{HaoGao}, optical flow computations between projections (at different time instances) of the dynamic nonrigid object~\cite{koen2020} with additional key-frame and residual modelling in~\cite{Guangming2019}, spline-based models for tracking the regions of change in an SIRT framework~\cite{Van2014}, or knowledge of fluid models (piecewise constant shapes of attenuation curves in the dynamic region) in an SIRT framework~\cite{HaoGao}.
-However all these techniques ~\cite{daniil2015,koen2020,Van2015,HaoGao,Van2014} essentially reconstruct all the different stages of the object simultaneously, and use the extra redundancy across time simultaneously.
-However, in the scenario of a longitudinal study (where projection measurements are acquired at instants that are several weeks apart) which we consider in this paper, such approaches are not feasible.
+However, all these techniques~\cite{daniil2015,koen2020,Van2015,HaoGao,Van2014} essentially reconstruct all the different stages of the object simultaneously, and use the extra redundancy across time simultaneously.
+In the scenario of a longitudinal study (where projection measurements are acquired at instants that are several weeks apart) which we consider in this paper, such approaches are not feasible.
 A longitudinal study will necessarily require reconstruction results after acquisition of each set of measurements.
@@
 Very importantly, our technique clearly differentiates between genuine structural changes and ``changes'' that appear due to undersampling artefacts.
-Since we use a statistical model with multiple object priors, we avoid the problem of selecting an appropriate single object prior unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and also make use of the additional information available in the multiple priors.
+Besides this, since we use a statistical model with multiple object priors, we avoid the problem of selecting an appropriate single object prior unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and also make use of the additional information available in the multiple priors.
 
@@
 \centering
-	\includegraphics[width=0.5\textwidth]{../images/prior_cmb.png}
+	\includegraphics[width=0.5\textwidth]{../images/prior_cmb_edited.png}
         \caption{Overview of our work. The choice of the number of
@@
     sufficient for the application at hand, and the scenarios for
-    which it will fail . This leads to the idea of a weights map
+    which it will fail. This leads to the idea of a weights map
     designed to depict the location and strength of new changes at
@@
  \textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
-scans (Figure~\ref{fig:object-prior_test_okra}). The measurements
+scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
 consisted of real circular cone-beam projections from 450 views, each of size
@@
     \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
+        \includegraphics[width=\textwidth]{../images/okra/template1_marked.png}
 \captionsetup{labelformat=empty}       
@@
     \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
+        \includegraphics[width=\textwidth]{../images/okra/template2_marked.png}
 \captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
+        \includegraphics[width=\textwidth]{../images/okra/template3_marked.png}
 \captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
+        \includegraphics[width=\textwidth]{../images/okra/template4_marked.png}
 \captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.176\linewidth}
-        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/testCropped.png}}
+        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/okra/test_marked.png}}
 \captionsetup{labelformat=empty}
@@
 
-\textbf{Potato:} This dataset consisted of four scans of the humble potato (Figure~\ref{fig:object-prior_test_potato_A}).
+\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
 Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150.
@@
     \begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_green.png}}
+        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
 \captionsetup{labelformat=empty}
@@
      \end{subfigure}
-      \caption{Potato 3D dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
+      \caption{Potato 3D dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
         volume (extreme right). Notice the appearance of the fourth
@@
 imaged at its various stages of growth
-(Figure~\ref{fig:object-prior_test_sprouts}). Projections were generated
+(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated
 from the given volume of size 130$\times$130$\times$130. The ground
@@
     \begin{subfigure}[b]{0.29\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
 \captionsetup{labelformat=empty}
@@
       \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
-        right).}
+        right). Notice the structure within the red box in the test that is different from all of the other images.}
 \label{fig:object-prior_test_sprouts}
@@
 
-\textbf{Radio-frequency ablation:} We have used this dataset (Figure~\ref{fig:RFA2_test_object-prior} to
+\textbf{Radio-frequency ablation:} We have used this dataset (Fig.~\ref{fig:RFA2_test_object-prior} to
 illustrate an application where \textit{both} uniform and spatially-varying priors are
@@
 One of the slices from the reconstructed volumes 
-is shown in Figure.~\ref{fig:okra_3D_results}. The red and green 3D
+is shown in Fig.~\ref{fig:okra_3D_results}. The red and green 3D
 RoI in the video and images show the regions where new changes are
 present. The zoomed-in images around the major region of change (red
-RoI) is shown in Figure~\ref{fig:okra_zoomed_3D_results}. As in the
+RoI) is shown in Fig.~\ref{fig:okra_zoomed_3D_results}. As in the
 test, the reconstruction by spatially-varying method shows the absence
@@
 \label{sec:discussion}
-The presented uniform prior-based algorithm is suited to applications
-where we wish to detect the location of new changes in an object over
-time, and the presented spatially-varying prior-based algorithm is
-suited to applications where we wish to observe the intricate details
-of those new changes. This distinction in the techniques used has not
-been studied earlier in
-literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our
-knowledge.
+In this section, we discuss the following: a) tuning of the parameters used, b) a realistic imaging and reconstruction protocol for longitudinal studies, and c) results on homogenous dataset.
+%The presented uniform prior-based algorithm is suited to applications
+%where we wish to detect the location of new changes in an object over
+%time, and the presented spatially-varying prior-based algorithm is
+%suited to applications where we wish to observe the intricate details
+%of those new changes. %This distinction in the techniques used has not
+%been studied earlier in
+%literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our
+%knowledge.
 Even though methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
@@
 
-\subsection{\textbf{Realistic imaging protocol}}
+\subsection{\textbf{Realistic imaging and reconstruction protocol}}
+%In all our previous results, we had assumed that in a longitudinal study of $n$ scans, the first $n-1$ scans are images with sufficient views and their high-quality reconstructions are used as templates.
+The $n^{th}$ scan alone is imaged with few-views and reconstructed using our method.
+Earlier in Sec.~\ref{sec:tmh}, we discussed that the imaging protocols fell under two categories depending on the final goal (tracking or observing details): very few-view imaging and moderate view imaging.
+In both cases, the templates used were of high-quality.
+However, in a realistic scenario,  we may prefer to gradually increase from few-view to moderate views as the probe gradually approaches the tumor site.
+For the reconstruction of $n^{\textrm{th}}$ slice i.e., slice imaged at time $t=n$, the few-view reconstructions of the previously acquired slices can be used as templates.
+However, the first scan must always be taken with large number of views because it acts as a reference template to start with.
+Table.~\ref{tab:realistic_imaging_protocol} summarizes this protocol for the dataset of Fig~\ref{fig:RFA2_test_object-prior}, and Fig.~\ref{fig:RFA2_new_protocol} shows the reconstructions when this realistic protocol is used.
 
@@
 \end{figure}
-
-Earlier in Sec.~\ref{sec:tmh}, we discussed that the imaging protocols fell under two categories depending on the final goal (tracking or observing details): very few-view imaging and moderate view imaging.
-\textbf{Ideally, we may prefer to gradually increase from few-view to moderate views as the probe gradually approaches the tumor site.} For the reconstruction of $n^{\textrm{th}}$ slice i.e., slice imaged at time $t=n$, the few-view reconstructions of the previously acquired slices can be used as object-prior.
-However, the first scan must always be taken with large number of views because it acts as a reference template to start with.
-Table.~\ref{tab:realistic_imaging_protocol} summarizes this protocol for the dataset of Fig~\ref{fig:RFA2_test_object-prior}, and Fig.~\ref{fig:RFA2_new_protocol} shows the reconstructions when this realistic protocol is used.
 

### 2020-07-21 paper/tci.tex
Changes in the dataset text

@@
 \label{sec:datasets}
-In this sections, we lay the details of all the datasets used in this work.
-\subsection{Real measurements of scanned volumes}
-These datasets in the form of raw cone-beam projection measurements were acquired from a lab
- at the Australian National University (ANU). Data from commercially
+In this section, we lay the details of all the real and simulated
+datasets created and used for this work. We will make these available to the community.
+The first 3 datasets: Okra, Potato and Sprouts were acquired from the Australian National University (ANU). We wish to emphasize that data from commercially
  available CT machines is not suitable because most CT scanners do
@@
  projections to the full volumes is proprietary. Departing from this, we
- demonstrate reconstruction results (in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior} from the following raw projection data.\\
+ demonstrate reconstruction results (in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior} from the following datasets.\\
 
  \textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
-scans (Fig.~\ref{fig:object-prior_test_okra}). The measurements
-consisted of real circular cone-beam projections from 450 views, each of size
-336$\times$156. The corresponding size of the reconstructed volume is
-338$\times$338$\times$123. Prior to the first scan, two holes were
+scans (Fig.~\ref{fig:object-prior_test_okra}). Prior to the first scan, two cuts were
 drilled on the surface of the specimen. This was followed by four
 scans, each after introducing one new cut. The specimen was kept in
-the same position throughout the acquisitions. In cases where such an
-alignment is not present, all the template volumes must be pre-aligned
-before computing the eigenspace. The test must be registered to the
-object-prior after its preliminary pilot reconstruction. The ground
-truth consists of volumes reconstructed using the Feldkamp-Davis-Kress
-(FDK) algorithm~\cite{FDK} from the full set of 450 view
-projections. The test volume was reconstructed from a partial set of
-45 projections, i.e., $10\%$ of the projection views from which ground
-truth was reconstructed.\\
+the same position throughout the acquisitions.The measurements
+consisted of real circular cone-beam projections from 450 views, each of size
+336$\times$156. 
+%In cases where such an
+%alignment is not present, all the template volumes must be pre-aligned
+%before computing the eigenspace. The test must be registered to the
+%object-prior after its preliminary pilot reconstruction.
+
+In our experiments, the first volume was assumed to be the test while
+the rest were used to build the object-prior. The ground truth
+consists of volumes of size 338$\times$338$\times$123 reconstructed
+using the Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} from the
+full set of 450 view projections.
+\\
  %--------------------------------okra data-------------------------------
 \begin{figure}[!h]  
+    \begin{subfigure}[b]{0.176\linewidth}
+        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/okra/test_marked.png}}
+\captionsetup{labelformat=empty}
+        \caption{}
+    \end{subfigure}
+    \quad
     \begin{subfigure}[b]{0.18\linewidth}
@@
      \end{subfigure}
-    \begin{subfigure}[b]{0.176\linewidth}
-        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/okra/test_marked.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
-       first four from the left), and one from the test volume
-       (extreme right). In the regions marked in red and green, while
-       all slices have deformities, the test
-       has none.}
+     \caption{Okra 3D dataset: One slice each from the each of the scanned volumes.
+The first one is used as the test while the rest are used to build the object-prior.
+Notice that in the regions marked in red and green boxes, while all slices have deformities, the test has none.}
 \label{fig:object-prior_test_okra}
@@
 \textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
+While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
 Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150.
-The corresponding size of the reconstructed volume is 150$\times$150$\times$100.
-While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
-Projections were obtained using circular cone beam geometry.
 %Further, this alignment can be refined following every update of the reconstructed test volume.
-The ground truth consists of FDK reconstructions from the full set of acquired measurements from 900 projection views.
-The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed.
+
+In our experiments, the first 3 volumes were used to build the object-prior and the
+last volume was used as the test. The ground truth consists of volumes of size 150$\times$150$\times$100 reconstructed using FDK from the full set of 900 projection views. 
 %---------------------------------------
@@
 
-\subsection{Simulated measurements from real-life reconstructed volumes}
-\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU, consists of six reconstructed
-volumes corresponding to six scans of an in-vivo sprout specimen
-imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated
-from the given volume of size 130$\times$130$\times$130. The ground
-truth consists of FDK reconstructed volumes from a set of 1800 view
-projections. The test volume was reconstructed from partial set of 45
-projections, i.e., $2.5\%$ of the projection views from which ground
-truth was reconstructed.\\
+%\subsection{Simulated measurements from real-life reconstructed volumes}
+\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU,
+consists of six reconstructed volumes corresponding to six scans of an
+in-vivo sprout specimen imaged at its various stages of growth
+(Fig.~\ref{fig:object-prior_test_sprouts}).  In contrast to the
+scientific experiment performed for the case of the okra and potato
+where we introduced man-made defects, the changes here are purely the
+work of nature.
+
+In our experiments, the first 5 volumes were used to build the object-prior and the
+last volume was used as the test. The ground truth consists of FDK reconstructed
+volumes of size 130$\times$130$\times$130 from a set of 1800 view
+projections. For the test, cone-beam projections were generated from
+the test volume. \\
 %-------------------------sprouts data
@@
 
-\textbf{Radio-frequency ablation:} We have used this dataset (Fig.~\ref{fig:RFA2_test_object-prior} to
-illustrate an application where \textit{both} uniform and spatially-varying priors are
-useful. The data~\footnote{Source: Tata Memorial
-  Centre~\cite{tmh}, Parel, Mumbai.  This is the national
-  comprehensive centre for the prevention, treatment, education and
-  research in cancer, and is recognized as one of the leading cancer
-  centres in India.} consists of simulated parallel beam measurements of 2D slices
-of the organ (liver) at different stages of the scan. The details of this study are presented in the next section.
+\textbf{Liver:} %We have used this dataset
+ %to illustrate an application
+%where \textit{both} uniform and spatially-varying priors are
+%useful.
+This data was sourced from Tata Memorial Centre~\cite{tmh} in 
+  Parel, Mumbai.  This is the national comprehensive centre for the
+  prevention, treatment, education and research in cancer, and is
+  recognized as one of the leading cancer centres in India. The dataset (Fig.~\ref{fig:RFA2_test_object-prior}) consists
+of parallel beam measurements that are generated from 2D slices of the
+organ (liver) acquired at different stages of a radio-frequency
+ablation study. In such a procedure~\cite{Dong2015}, the physician
+inserts a thin needle-like probe into the organ. Repeated CT scans of
+the patient are acquired in order to track the movement of the
+needle and to ensure that it is reaching the appropriate target
+tumor. Once the needle hits the tumor, a high-frequency electric
+current is passed through the tip of the probe and this burns the
+malignant tumor (ablation). The aim of the scan at this ablation stage is to
+reveal accurate details of the changes within.
+
+In our experiments using this dataset, we demonstrate the usefulness of \textit{both}
+uniform prior and spatially varying prior. For the first case, we choose the first 6 slices to build the object prior and use slice 7 as the test. For the latter case, we choose the first
+7 slices to build the object prior and use slice 8 as the test.
 %--------------------------Results on TMH data--------------------------
@@
 Before diving into the details of the uniform and the
-spatially-varying prior methods, we first show how both the
+spatially-varying prior methods, we first show how \textit{both} the
 techniques can be applied to our advantage in a real-life medical
 longitudinal study. Here, our data consists of successive scans of the liver taken
-during a radio-frequency ablation procedure. In such a
-procedure~\cite{Dong2015}, the physician inserts a thin needle-like
-probe into the organ. Repeated CT scans of the patient need to be
-acquired in order to track the movement of the needle and to ensure
-that it is reaching the appropriate target tumor. Once the needle hits
-the tumor, a high-frequency electric current is passed through the tip
-of the probe and this burns the malignant tumor (ablation). The scan
-at this ablation stage must also reveal accurate details of the
-changes within. In this context, we classify the goal of any of our
+during a radio-frequency ablation procedure described in Sec.~\ref{sec:datasets}. In this context, we classify the goal of any of our
 reconstruction techniques into two categories: 
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
-\subcaptionbox{Proposed\\ method: uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
+\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
 \caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) FBP and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures, SSIM $=0.35$ and (d) uniform prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
-The region enclosed in red rectangle is our RoI as it contains both the new position of the needle and some background.
+The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
 All SSIM values are computed for this RoI.}}
@@
 \subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
-\subcaptionbox{Proposed\\ method: uniform\\ prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
-\subcaptionbox{Proposed\\ method: spatially-varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
+\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
+\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
 \subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
 \caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) l1-ls with SSIM $=0.46$ and (d) uniform prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) spatially-varying prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
-The region enclosed in green rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
+The region enclosed in green rectangle is our RoI as it contains both the new position of the needle and some background.
 The SSIM is computed in this RoI.
@@
 as our dataset. Note that all these 8 slices are located at the
-\emph{same} index~\footnote{The notion of~\textit{same index} (slice
-  number corresponding to the same depth) makes sense in the context,
-  because in such problems, the different scans are aligned with each
-  other.} within each of the respective
+\emph{same} index (slice number corresponding to the same
+depth) %~\footnote{The notion of~\textit{same index} (slice  number
+%corresponding to the same depth) makes sense in the context, because
+%in such problems, the different scans are aligned with each
+%other.}
+within each of the respective
 volumes. Fig.~\ref{fig:RFA2_test_object-prior} shows the chosen set of
@@
 %-------------------------------------------------
-\subsubsection{\textbf{Okra dataset}}
+\subsubsection{\textbf{Okra}}
 \label{Sec:okra_uniform}
+The test volume was reconstructed from a partial set of
+45 projections, i.e., $10\%$ of the projection views from which ground
+truth was reconstructed.
  One of the slices of the reconstructed volumes is shown in
@@
 %----------------------------------------------------
-\subsubsection{\textbf{Sprouts dataset}}
+\subsubsection{\textbf{Sprouts}}
 \label{Sec:sprouts}
- In contrast to the scientific experiment performed for the case of
- the okra where we introduced man-made defects, the changes here are
- purely the work of nature. One of the slices of the reconstructed
+The test volume was reconstructed from partial set of 45
+projections, i.e., $2.5\%$ of the projection views from which ground
+truth was reconstructed.
+One of the slices of the reconstructed
  volumes is shown in
@@
 \textbf{Computation of weights matrix $\boldsymbol{W}$:}
-Since the test volume (referred to as $\boldsymbol{x}$) is unknown to
+Since the test is unknown to
 begin with, it is not possible to decipher the precise regions in
@@
 weights. To illustrate the benefit of this method, we first performed
-2D reconstruction of a test slice from the potato dataset (please
-refer Sec.~\ref{Sec:potato} for details of the dataset)
+2D reconstruction of a test slice from the potato dataset.
 Fig.~\ref{fig:object-prior_test_potato_A1} shows the test and template
@@
 
-\subsubsection{\textbf{Okra dataset}}
+\subsubsection{\textbf{Okra}}
 \label{Sec:okra_spatially_varying}
@@
 
-\subsubsection{\textbf{Sprouts dataset}}
+\subsubsection{\textbf{Sprouts}}
 \label{Sec:sprouts_spatially_varying}
@@
 One such dataset is the Potato dataset.\\
- The selected 3D
+The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed. The selected 3D
 ground truth of template volumes, test volume, as well as the 3D reconstructions are shown in the supplementary material~\cite{supp_paper}.

### 2020-07-22 paper/response.tex
updated supplementary and response.pdf

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Author Response to Reviewers for the paper `Eliminating prior-bias from sparse-projection tomographic reconstructions'}
\begin{document}
\maketitle

\textbf{Organization of this response:} We would like to thank the editor and all three reviewers for their insightful comments. Here, we are including our response to each reviewer, and pointers to modifications (suggested by the reviewers and the AE) in our revised manuscript.  Where necessary, we tie up related comments from the multiple reviewers for ease of understanding.  We have organized this document in three parts (a) Response to comments from AE (Section A), and (b) Response to significant points made by all the other reviewers (c) Detailed  responses to the comments of each of the reviewers.

To the best of our knowledge, we have painstakingly addressed each and every point of all the reviewers, and responded adequately.  We request the reader's time to go through our responses.

In some cases, we provide results in this document to justify our stand, but these same results are not in the updated manuscript, primarily because these results do not enhance the claims in our paper . In most other cases, we have shifted such results to supplementary material and have referred to them in this document.

For ease of understanding, since the current version of the manuscript is considerably reorganized, in this document, we have used the (longer) term ``Figure x'' to refer to a figure in the old version and ``Fig. x'' to refer to the related figure in the current version. Similarly, we have used the term ``Equation y'' to refer to an equation in the old version, and ``Eq. y'' to refer to an equation in the new version, and ``Table y'' to refer to a table in the old version and ``Tab. y'' to refer to a table in the new version.

\section{Associate Editor comments}
(We have numbered the original review comments as AE-Cx, and italicized for clarity)

Two of the reviewers have raised some serious concerns about the paper, including one reviewer who opines that this work is not suited for publication in the transactions in its current form. While these concerns are sufficiently serious to merit a negative decision, I have decided to give the authors an opportunity to revise the manuscript so that they may address the constructive comments of the reviewers carefully and thoroughly followed by another round of review to assess the manuscript. In addition to the reviewer specific comments, please pay specific attention to the following:\\

\textcolor{blue}{\textbf{AE-C1.}\textit{ Overall organization of the paper to improve the exposition.}}

\textbf{Response:} 
We have now made the following significant changes in the organization of the paper:
The introduction has been modified and the stage set for outlining our contributions have been made.  We have replaced the earlier Figure 1 (which did not have longitudinal data) with a more appropriate figure (Fig.1). The unfamiliar terms ``unselective'' and ``selective'' prior have now been replaced by ``uniform'' prior and ``spatially varying'' prior to better communicate the property of the respective priors.
A new section  (Section 2) named ``Related Work'' has been included separately to contrast this work with the prevailing work in the literature. 
Details of the datasets have been moved to a separate section (Section 4) so the ground is properly set.
The two earlier sections: methods and results sections have now been split into the following 4 sections. This ensures better readability and emphasizes the cases where both uniform prior and spatially-varying prior are useful.
\begin{itemize}
 \item Section 6: Uniform prior-based reconstruction
 \item Section 7: Results: Reconstruction by uniform prior
 \item Section 8: Spatially varying prior-based reconstruction
 \item Section 9: Results: Reconstruction by spatially varying prior
   \end{itemize}
For greater clarity, we have now removed Schematic 1 (as suggested by R1) from the paper. We have  ensured that the rest of the paper can be followed without it. We have also moved the discussion on the earlier patch-based methods to supplementary material. However, results not reported earlier prior to this submission using the uniform prior on 3D volumetric data continues to be present (as mentioned above) in Section 6 since it forms an important part of our story for this paper.\\

\textcolor{blue}{\textbf{AE-C2.}\textit{ Highlight clearly the novelty of the presented work and provide accurate comparisons to relevant algorithms in the case when one has access to prior scans.}}

\textbf{Response:} We have now re-written the contributions section (Sec.3 of the main paper), that highlights the novelty of our work.  
As a response to the comparisons required,  in many cases, our methods are incomparable to previous algorithms because of the nature of the longitudinal study  We discuss this in the related work section. Further we reiterate that in our earlier manuscript version, we had compared our method with l1-regularized least squares (l1-ls) and FDK for 3D reconstructions. We had also compared (Fig.8) our method with many other iterative methods such as (ART, SART and SIRT) -- this set of comparisons was buried in a footnote, and perhaps not easily visible.
In addition to these, we now have included Table 3 to show a quantitative comparison of SSIM values of the reconstruction by various methods shown in Fig.8.  We also discuss compressed sensing (see AE-C3) results.
In addition, 
R3 has referred to ``Region-based iterative reconstruction of Structurally Changing Objects in CT''. This reference is now mentioned in our related work; although this paper is not directly applicable in longitudinal studies where object-priors `are' available, there is a reference in this paper to another paper which does make use of object-prior. We show how our work is superior in our response to R3 below (we include this in the supplementary material). \\

\textcolor{blue}{\textbf{AE-C3.}\textit{Discuss the compressed sensing methods used since there are several works on model-based iterative reconstruction/regularized inversion/CS type methods for CT.}}

\textbf{Response:} We believe we now have clearly brought out the compressed sensing based works both in the introduction and in the related work section.  Related points w.r.t. CS-type reconstruction made by R1/R3 appears below in B1 (and elsewhere in even greater detail).

In summary, we believe that the extensive work we have done based on the reviewer comments, while still maintaining the intellectual contributions of the original submitted version lends itself to the paper being accepted.

\section{Broad response to all reviewers}

We believe it is useful to single out the most serious criticism to this paper, and we wish to defend our stand. At this time, we request the reviewers  to kindly look at the first few sections, with slightly modified terminology (compared to the submitted version)  before continuing on to the responses.

\begin{itemize}
  \item R1 and R3 are concerned about the blurring and over-regularized nature of the compressed sensing-based images.  In particular R3 is seriously concerned about the quality of Compressed Sensing reconstruction. Our response is that this is a function of the number of views. In short, if the number of views is sub-Nyquist, yes, indeed CS can provide good quality reconstruction, especially with the tuning method suggested by R1. (Our updated figures demonstrate this). 
However,  coming to the main contribution of the paper, if the number of views becomes significantly small (when compared even to sub-Nyquist), reconstructions using CS is less than satisfactory, despite the removal of sub-sampling artefacts. This has also been pointed out earlier in a different (not ours) published work [11], Page 4, line 22.  We have now described the use-case for CS reconstructions in Fig. 1 and have elaborated on the blurred artefacts in our  response in R3-C7.
\item All reviewers are concerned about the seemingly low SSIM value (relatively poor reconstruction) for one of the experiments.  (Figure 10-c in the original document) while results in all the other experiments are acceptable to prove the point.  For instance R2 says ``I have one main question concerning Table 1, where I notice FDK gives for the ROI much better SSIM value than the variants of the proposed method.''  
Of course, we never intended to *not* mention this, which is why it was picked up very easily by all the reviewers, and in real life situations, it is unreasonable to expect that the ROI of detailed changes is known in advance.

In response, we first note that our updated results of comparison for this dataset (after the tuning suggested by R1) *now* results in a favourable result (Table 3).  That said, we agree that the FDK reconstructions can be superior, as evidenced for this particular dataset alone -- presumably when the region of interest is known a-priori (which is not always the case). We have devoted a separate section in the `Discussion' for this particular concern: Tab.8 better explains why our method is suitable, and Fig. 19(e) the more pleasing visual result.  
\item R1 and R3 also raise another significant point:  What happens if we have only the object prior term and ignore the sparsity prior?.  This indeed is relevant. Our response is that the answer to the question revolves around the quality of the prior. In our experiments, the object priors are of high quality, the number of views very few (the title of our paper), and hence the object-prior has a dominant effect when compared to sparsity prior;  adding the sparsity prior improves the reconstruction marginally.  That said, ignoring the sparsity prior would be akin to ignoring the established work revolving around compressed sensing.  If the object-priors were of poor quality, or if the number of views (still sub-Nyquist) were to be increased from our very few views, then the sparsity term will start playing a part.  
\item R3 remarks that `it's simply not true' about some of the overarching broad statements which we had claimed in our earlier submission (for example, ``in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections simulated from 3D volumes''). In our current version, we have now either given better context to such statements or have retracted our misunderstandings with the wisdom in R3's remarks.
\end{itemize}

\section{ Detailed response to individual review comments}

\subsection{Response to Reviewer 1}
There are some concerns associated with the compressive sensing (CS) method, the explanation for weight selection, and the clarity of results. Some of the major issues are described below.

\textcolor{blue}{\textbf{R1-C1:}\textit{In Fig. 4, the caption says CS and no prior. This is not true. CS does have a prior in the sense that it forces the reconstruction to lie in a sparse basis. You did explain this aspect of CS in section III (A).}}

\textbf{Response:} Agreed.  CS does use the sparsity prior. We have now moved this point much earlier in the introduction, and point out some of the advantages of using object-prior. Sec.1, Page1. We have corrected the captions. Specifically, (for example) the earlier caption of Fig.4-c: ``CS and no prior resulting in blurred bone structures'' has now been replaced by ``l1-ls resulting in blurred bone structures''. In the latter, ``l1-ls'' refers to L1-regularized least squares optimization \\

\textcolor{blue}{\textbf{R1-C2:}\textit{$\lambda_1$ seems to decide the strength of the CS prior. However, in section V (B), you mention that $\lambda_1$ is always chosen to be one. But, it is clear that the potato image in Fig. 10 (c) is over-regularized. It is extremely blurred.}}

\textbf{Response:} Agreed. See response is \textcolor{blue}{\textbf{R1-C3}}.\\

\textcolor{blue}{\textbf{R1-C3:}\textit{ In CS, since you use cross-validation on a test image to select $\lambda_1$, it is necessary to tune this parameter until you reach a desired SSIM or root-mean-squared-error (RMSE). With CS priors, I would expect increasing $\lambda_1$ to also lead to smoother results.}}

\textbf{Response:} With respect to Figure. 10(c) of the submitted paper which corresponds to Fig.17(c) of the new version, we have now updated the reconstruction after tuning $\lambda_1$ to get the optimal result for l1-ls, as suggested by Reviewer 1. The optimal $\lambda_1$ was found to be 1.7.

In Sec.5 of our supplementary material, we describe why the image in Fig.17(c) (Fig.10(c) of the old version) appears over-regularized by presenting reconstructions on 2D potato dataset for different number of views and optimally tuned $\lambda_1$ values.   \\

\textcolor{blue}{\textbf{R1-C4:}\textit{ What is the sparsity basis for CS prior in equation (1)? }}

\textbf{Response:} We have chosen DCT as the sparsity basis, and have now clarified this in the paper. We had observed that there is no significant improvement if, say, the wavelet transform were instead used as the basis.\\

\textcolor{blue}{\textbf{R1-C5:} \textit{Why is a CS prior necessary when you have the selective/unselective prior? What happens if there is no CS prior and if we use only the selective/unselective priors?}}

\textbf{Response:} Although the data-agnostic CS/sparsity  prior and the data-dependent object-prior  (either uniform or spatially varying) affect independent terms in the overall cost function (Eq.6), best results are obtained when both the priors are used together. Whether to use the CS prior or not is a function of the quality of the object-prior. In our case, the object priors are of high quality, and hence the object-prior has a dominant effect. Adding sparsity prior improves the reconstruction marginally.\\

\textcolor{blue}{\textbf{R1-C6:}\textit{Schematic 1 in section III (B) does not make sense. But, the explanation in section III (B) (2) is clear.}}

\textbf{Response:}  For greater clarity, we have now removed Schematic 1 from the paper; We have  ensured that the rest of the paper can be followed without it.\\

\textcolor{blue}{\textbf{R1-C6(b):}\textit{found section III (B) (2) algorithm to compute weights map W very interesting. However, it is hard to understand what artifacts can be attributed to the system geometry and an algorithm. For instance, in the third step, you mention that the difference between $P^{fdk}$ and $X^{fdk}$ will not contain false positives due to imaging geometry but will contain false positives specific to the reconstruction method. Can you show these artifacts for the potato dataset? While Fig. 7 showing weights is interesting, from a clarity standpoint, I would like to see images of artifacts that get removed at each stage of your algorithm (2) Algorithm to compute weights maps W.}}

\textbf{Response:} To illustrate how different reconstruction methods lead to different artefacts and how combining them carefully can cancel those artefacts, we present a few intermediate weights maps for a 2D reconstruction from 12 views (of the test image in Fig.10 of the paper), with and without noise. Due to the lack of space, we have not included the below images in the main paper.
%-----------------------------potato data
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
\captionsetup{labelformat=empty}
        \caption{}
\label{fig:potato_test}
     \end{subfigure}
      \caption{Potato dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A1}
\end{figure}

In the Figs.~\ref{fig:weights_no_noise} and~\ref{fig:weights_with_noise}, notice how the weights map is different for each of the methods and how it is improved when it is computed using two or more methods. We observe similar benefits even in the presence of small quantities of noise as shown below.

In the actual reconstruction of the images, the prior term is well represented and these effects are not immediately visible.  However, with low quality priors the effects may be visible.

\newpage
\textbf{Case 1: No noise in projections:}
\begin{figure}[!h]
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/no_noise/weightsIm_fbp30.png}
\captionsetup{labelformat=empty}       
 \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/no_noise/weightsIm_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{SIRT}
     \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/no_noise/weightsIm_sart30.png}
\captionsetup{labelformat=empty}
        \caption{SART}
     \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/no_noise/weightsIm_fbp_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{FBP + SIRT}
    \end{subfigure}
    \quad
        \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/no_noise/weightsIm_fbp_sart_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{FBP + SART + SIRT}
     \end{subfigure}
      \caption{Weights images by various methods while reconstructing the test in Fig.~\ref{fig:object-prior_test_potato_A1} from 12 views and no noise}
\label{fig:weights_no_noise}
\end{figure}

\textbf{Case 2: Noise with 0 mean and SD = 1$\%$ of the mean of the measurements}
\begin{figure}[!h]
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_fbp30.png}
\captionsetup{labelformat=empty}       
 \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{SIRT}
     \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_sart30.png}
\captionsetup{labelformat=empty}
        \caption{SART}
     \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_fbp_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{FBP + SIRT}
    \end{subfigure}
    \quad
        \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_fbp_sart_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{FBP + SART + SIRT}
     \end{subfigure}
      \caption{Weights images by various methods while reconstructing the test in Fig.~\ref{fig:object-prior_test_potato_A1} from 12 views in the presence of noise.}
\label{fig:weights_with_noise}
\end{figure}

\textcolor{blue}{\textbf{R1-C6:}\textit{ In results, the images are simply too big relative to the ROIs, which are tiny. It is very difficult to see the changes within the ROI. If the paper is printed, then there is no way to zoom into the images. It will be better if you could also present zoomed images of the ROI. Otherwise, you could present one full sized image and rest of the images could be only the ROI. }}

\textbf{Response:} While the zoomed-in RoI of Okra is in Figure 13 of the old manuscript (Fig.14 of the new manuscript), the zoomed-in RoI of the sprouts dataset has now been added in Fig. 16.  For other cases, larged sized images are in the supplementary material.\\

\textcolor{blue}{\textbf{R1-C7:}\textit{ Table I, II, and III present SSIM comparison. It will also be interesting to present a root mean squared error (RMSE) comparison. RMSE measure will help in evaluating the quantitative accuracy of your reconstruction.}}

\textbf{Response:} The optimal values of parameters obtained by tuning RMSE were found to be different from those obtained by tuning SSIM. Hence, for consistency, we choose only one metric (SSIM) to report accuracy of all reconstructions.
Moreover, SSIM gives us the flexibility to measure the fidelity of the structural content of our reconstruction with respect to that of test volume.\\

\textcolor{blue}{\textbf{R1-C8:}\textit{ For instance, in Fig. 10 (e), the region within the ROI seems to be brighter than the surrounding holes. This may also happen if an incorrect choice of the CS prior regularization parameter $\lambda_1$ results in excessive blurring.}}

\textbf{Response:} Despite tuning $\lambda_1$, In Fig. 19(e) (previously Fig.10(e) of the old version), the information about the new region (within RoI)  is present only in the measurements of the test, and is absent in all of the templates. This is unlike the case for the surrounding holes, the information about which is present both in the measurements of the test and the templates. Hence, the reconstruction of the hole in the RoI is not as sharp as the other holes.\\

\textcolor{blue}{\textbf{R1-C9:}\textit{Some relatively minor issues are below- Page 3, line 7, section II: Consider defining longitudinal study.}}

\textbf{Response:} We have now defined longitudinal study in the paper (Sec. 1). Longitudinal studies here refers to the acquisition of sequential CT scans of the same subject to track time-evolving changes within the subject's interior.  \\

\textcolor{blue}{\textbf{R1-C10:} \textit{Images in Fig. 3 seem to be clipped in the lower left along a circular arc! Are all reconstructions within a circular outer region of interest?}}

\textbf{Response:} All the reconstructions are within the circular region for this dataset. The ground-truth for this dataset consists of reconstructions from a proprietary software used in the CT machine at the Tata Memorial Hospital, Mumbai. The  RoI was chosen by the proprietary software and hence the exact reason for its choice is known only to the vendors. Based on inputs from physicians at the Centre, we have ensured that the RoI indeed encompasses the regions of interest, i.e. the organ in which ablation is being performed.\\

\textcolor{blue}{\textbf{R1-C11:}\textit{In Fig. 8, what is (g) combined? Also, there is no (h) but is mentioned in caption.}}

\textbf{Response:} The caption has now been correctly renamed to (g). 
By `combined', we denote the weight map computed as per Eq.7.  This equation incorporates the use of the eigen-space of the templates reconstructed from various methods (such as ART, SART, SIRT, etc.), and pilot reconstructions of the test,  again reconstructed from various methods. In Eq.7, the min(.) operator ensures that we select the new regions that are unanimously detected by all the methods of reconstruction. Hence, the word `combined' denotes that all the reconstruction methods are combined to give information about the new regions of the test.\\

\textcolor{blue}{\textbf{R1-C12:}\textit{ Try to mention the actual number of views/projections instead as a percentage. The percentage only makes sense when you are comparing against Nyquist limit for views. For instance, the total number of views for Potato dataset is 900, which is simply too many for a reconstruction size of 150x150. For such a small reconstruction, 900 is not a ``typical'' number views. It may be more ``typical'' to use 150 views in standard practice. So, expressing views as a percentage of 900 is confusing.}}

  \textbf{Response:} Just to clarify, as mentioned in the paper, the 900 views for the potato dataset was used to reconstruct the ground-truth 3D volume of size 150 x 150 x 100, and not a 2D slice of size 150 x 150.  Each of the projection images was of size 150 x 150.

Since our imaging method is circular cone beam projection, let us first assume a 2D example. Consider a circle of radius R=1 that envelops an unknown 2D region X. Then, the circumference of the circle in pixel units will be $2\pi R_p$, where$ R_p$ represents the radius in pixel units, i.e., the number of image-pixels that fit within the radius of the circle. Now, let us assume that we want to pass rays around a half of a circle (due to symmetry). We can reasonably assume that a set of $(2*\pi*R_p)/2$ angles will be ``sufficient'' to faithfully reconstruct X.
\begin{itemize}
\item Given size of the 2D object $= 200 x 200$, the length (in pixel units) of the diagonal of this image $= 200*\sqrt(2)$, and this is twice the radius of the enclosing circle.
\item Since our imaging method is circular cone beam projection, we assume a circle to tightly bound the object.
\item $R_p = 282.84/2 = 141.4$
\item No. of views $= 2*\pi*R_p = 888$ views
\end{itemize}

Similarly, in the case of 3D, assume the object is enclosed within a sphere of unit radius R. Let $R_v$ denote the radius in voxel units, i.e., number of object-voxels that fit within the radius of the sphere. Hence, in 3D, one way to compute sufficient number of views would be the following:
\begin{itemize}
\item Given size of the object scanned $= 150 x 150 x 100$, the length of the space diagonal of this cuboid = $\sqrt{(100^2 + 100^2 + 150^2)}$
\item Since our imaging method is circular cone beam projection, we assume a sphere tightly bounding the object.
\item The radius of this sphere in voxel units ($R_v$) will be $\sqrt{(100^2 + 100^2 + 150^2)}/2 = 103$
and, surface area of the sphere $= 4*\pi*(R_v)^2 = 133320$.
\item If we want to pass at least one ray for every surface voxel of this sphere, we will need 133320/2 (since sphere is symmetrical, and ray at 30 deg will pass through same voxels as ray at 30 +180 deg) = 66658 views. 
\end{itemize}
Hence our choice of 900 views for reconstruction of the ground-truth is not exceedingly large. It just happens to be sufficient due to the homogenous structure of the interior of the object (potato).

Since our gold-standard for measuring accuracy of our technique's reconstruction is the ground-truth reconstruction obtained from 900 views (for the potato dataset), we have measured our achieved reduction in views as a fraction of the views used for reconstructing ground-truth. \\

\textcolor{blue}{\textbf{R1-C13:}\textit{ Hard to notice the features within the ROI in Fig. 15. It may help to present images that zoom into the ROI.}}

\textbf{Response:} The zoomed-in RoI is now shown in Fig. 16. \\

\textcolor{blue}{\textbf{R1-C14:}\textit{ In section V (B), how was the cross-validation or empirical selection of $\lambda_1$ and $\lambda_2$ done? Did you use SSIM as a comparison metric? Did you use any particular object prior image for cross-validation? If so, which image did you use? }}

\textbf{Response:} In our earlier submission, $\lambda_1$ and $\lambda_2$ values were chosen by reconstructing the test volume by sweeping through a range of values and selecting the set of values that gave a reasonable visual quality. In the current version of the paper, we had first chosen $\lambda_1$ as that value which maximizes the SSIM of the l1-ls reconstruction. This value was retained for uniform and spatially-varying prior based reconstruction as well. $\lambda_2$ was chosen clairvoyantly,  i.e., based on the value that gave the best visual results on the test.\\

\textcolor{blue}{\textbf{R1-C15:}\textit{ You are allowed to submit documents or media as supplementary material. Instead of posting them on a dropbox, you could submit them as supplementary material to the journal. You could also use supplementary material to add additional text or figures to reduce number of pages in main paper.}}

\textbf{Response:} Thank you for the suggestion. We have now submitted the supplementary material  on the publication portal. \\

\textcolor{blue}{\textbf{R1-C16:}\textit{ To save space and if you feel comfortable, you could move the section III (A) (1) on patch based techniques to supplementary since it is not a contribution of your paper.}}

\textbf{Response:} In order to save space and for greater clarity, we have now moved the discussion on patch-based techniques to supplementary material.

\section{Response to Reviewer 2}
(We have numbered these comments as \textbf{R2-Cx}, and italicized for clarity)\\

\textcolor{blue}{\textbf{R2-C1.}\textit{ I have one main question concerning Table 1, where I notice FDK gives for the ROI much better SSIM value than the variants of the proposed method. What is the reason of this? Why can then the authors state that their method is better than FDK? A bit more detailed explanation would be satisfactory.}}

\textbf{Response:} We hypothesize that because the volume of this dataset (potato) is very homogenous (without intricate  structures), the test measurements capture sufficient information about the new regions even with $5\%$ views and hence FDK performs very well in the exact region of interest (shown as red RoI in Fig. 19(a)). However, as we expand the region of interest (green and cyan RoI in Fig. 19a), the prior-based methods perform better than FDK (please refer Table 8) in that they minimize the sub-sampling artefacts.  We have now discussed this in Section 8. B - ``Reconstruction of homogenous data''.
Had the new region been embedded within an intricate background (like the sprouts and okra), its reconstruction does give rise to artefacts as seen in Figs.13-b and 15-b.

Beside this, I only have minor comments:\\

\textcolor{blue}{\textbf{R2-C2}\textit{. P1, L49, right panel: "a" should not be typeset in italic.}}

\textbf{Response:} The italicized `a' here is used to emphasize the selection of `any one' particular template amongst the many available ones. So, we retain the typeset on ``a'' and for greater clarity, italicize the word `particular' as well . The statement now reads:
``there is the key issue of choice of a particular previously scanned object among the many previously acquired scans.''\\

\textcolor{blue}{\textbf{R2-C3.}\textit{P2, L31, left panel: The subtitle should be typeset in bold.}}

 \textbf{Response:} Accepted. The typeset has been changed.\\

\textcolor{blue}{\textbf{R2-C4. }\textit{P2, L50, left panel: ``reconstruction-'' should be corrected to ``reconstruction -''}}

 \textbf{Response:} Accepted. This has been corrected.\\

\textcolor{blue}{\textbf{R2-C5.}\textit{P5, L10, left panel: ``Eq 6'' should be corrected to ``Eq. 6'' (same in P6, L54, right panel}}

 \textbf{Response:} Accepted. This has been corrected, and the equation has now been moved to  supplementary material (Eq.2). \\

\textcolor{blue}{\textbf{R2-C6.}\textit{ P6, L17, left panel: ``i.e'' should be replaced with ``i.e.'' (correct each further occurrence}}

 \textbf{Response:} As per the conventional use, ``i.e'' has now been replaced by ``i.e.,'' in all occurrences in the paper.\\

\textcolor{blue}{\textbf{R2-C7. }\textit{P6, L42, left panel: ``Eqn. 8'' should be corrected ``Eq. 8'' (same in P7, L19, left panel}}

  \textbf{Response:} Accepted. These have been corrected.\\

 \textcolor{blue}{\textbf{R2-C8.}\textit{ Caption of Fig. 8: The correct form is (a)-(f) and (g)}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C9.}\textit{ P6, L40, right panel: Subtitle should be typeset in bold}}

  \textbf{Response:} Accepted. The typeset has been changed.\\

 \textcolor{blue}{\textbf{R2-C10.}\textit{ P7, L3, and L7: ``proposed methods'' <--> "proposed method". Choose one.}}

 \textbf{Response:} In Sec.6, we use ``Proposed method'' to refer to uniform prior-based method, and in Sec.8 we use ``Proposed method'' to refer to spatially varying prior-based method.\\

\textcolor{blue}{\textbf{R2-C11.}\textit{ Caption of Figs 10, 12, and 13: ``Unselective prior'' should be typeset in two lines instead of three.}}

  \textbf{Response:} Accepted. This has been typeset.\\

 \textcolor{blue}{\textbf{R2-C12.}\textit{ P7, L50, left panel: Replace ``Figs. 9'' with ``Fig. 9''}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C13.}\textit{ P7, L28, right panel: do not use bold typesetting here}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C14.}\textit{ Caption of Fig. 15: ``Letters missing''}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C15.}\textit{ P8, L49, right panel: Correct ``shows'' to ``show''}}

 \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C16.}\textit{ Caption of Fig. 16: ``slice-8'' should be replaced with ``image-8''}}

 \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C17.}\textit{ P9, L20, right panel: Move [16] to the second place.   }}

 \textbf{Response:} Accepted. This had been corrected.\\

\textcolor{blue}{\textbf{R2-C18.}\textit{P9, L34, right panel: ``[38](FDK'' space is missing}}

 \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C19.}\textit{P9, L36, right panel: ``in-dept'' should be corrected to ``in-depth'', ``in'' should be corrected to ``is''}}

 \textbf{Response:} Accepted. These have been corrected.\\

 \textcolor{blue}{\textbf{R2-C20.}\textit{ Caption of Fig. 17: ``weight maps'' should be corrected to ``weights maps''}}

\textbf{ Response:} Accepted. This has been corrected to `weights-maps' in all occurrences in the paper.\\

 \textcolor{blue}{\textbf{R2-C21.}\textit{ Acknowledgement: ``Dr.Andrew Kingston'' space is missing}}

\textbf{ Response:} Accepted. This has been corrected.

\bibliography{tci_ref}
\end{document}

### 2020-07-22 paper/supplementary.tex
updated supplementary and response.pdf

@@
 \newpage
-\section{\textbf{Patch-based techniques}}
-\label{sec:patch_based}
-Here we present a comparison~\cite{my_dicta_paper} of the performance of the aforementioned PCA-based global prior with a prior that is based on construction of patch-wise dictionaries.
-In both cases, the reconstruction routine is based on typical CS techniques.
-The well-known K-SVD algorithm \cite{Aharon2006} was chosen for construction of patch-based dictionaries.
-For this, patches were extracted from each of the template volumes, from which an overcomplete dictionary was obtained.
-The basic aim of the K-SVD algorithm (or any overcomplete dictionary learning technique) is the compact linear representation of all these patches using the dictionary columns.
-Let $\boldsymbol{D}$ denote the dictionary learned, $N_p$ the total number of patches, and $\boldsymbol{H_i}$ the operator to extract the $i^{\textrm{th}}$ patch from the intermediate reconstructed slice/volume.
-Then, once $\boldsymbol{D}$ is computed in an earlier `training phase', each new test slice (or test volume) can be reconstructed by optimizing a cost function such as the one below:
-\begin{multline}
-J_2(\boldsymbol{\theta},\{\boldsymbol{\alpha_i}\}_{i=1}^{N_p}) = \lVert\boldsymbol{\mathcal{R}\Upsilon\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \\ \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\lVert \boldsymbol{H_i\Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2 +\frac{\lambda_3}{ N_p}\sum_{i=1}^{N_p}\lVert\boldsymbol{\alpha_i}\rVert_1.
-\label{Eq:main_patchBased}
-\end{multline}
-The reconstruction proceeds in an alternating manner, first by minimization of Eq.~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}.
-For both these, the solver in~\cite{l1ls} is used.
-For the former case, the cost function reduces to:
-\begin{equation}
-J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = \lVert \boldsymbol{\mathcal{R} \Upsilon \theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\rVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2.
-\label{Eq:primaryObj_patchBased}
-\end{equation}
-For each $i \in \{1,...,N_p\}$, the cost function reduces to:
-\begin{equation}
-J_{\boldsymbol{\theta}}(\boldsymbol{\alpha}_i) =  \lVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D\alpha_i}\rVert_2^2  + \frac{\lambda_3}{\lambda_2}\lVert\boldsymbol{\alpha_i}\rVert_1.
-\label{Eq:alpha_patchBased}
-\end{equation}
-This summarizes the comparison with patch-based methods.
 %--------------------------------------------------------------------------
@@
 \newpage
-\section{2D reconstruction results on colon CT dataset}
 
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/template1.png}
-        \caption{template 1}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/template2.png}
-        \caption{template 2}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/template3.png}
-        \caption{template 3}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/template4.png}
-        \caption{template 4}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/template5.png}
-        \caption{template 5}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/testIm.png}
-        \caption{test image}
-     \end{subfigure}
-      \caption{2D object-prior (referred to as `templates' here)  and test slice of colon CT dataset. The region in red shows the synthetic new region added to the test slice.}
-\label{fig:joint}
-\end{figure}
-
-%--------------------------------2D Colon results----------------------------
-
-\newpage
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/testIm.png}
-        \caption{Test image}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/fbp.png}
-        \caption{FBP}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/cs_dct.png}
-        \caption{CS-DCT}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/plain_pca.png}
-        \caption{unselective prior+cs}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/colon/60_angles/weighted_pca5.png}
-       \caption{our method}
-     \end{subfigure}
-      \caption{Reconstruction of colon CT: (b) has many streak artefacts (c) slightly blurred (d) Inaccurate reconstruction of new region (corresponding to the red RoI) (d) new region accurately detected while simultaneously removing streak artefacts.}
-\label{fig:joint}
-\end{figure}
-
-%-----------------------------Sprouts : data--------------------------
-\newpage
-\section{2D reconstruction for different projection views}
-
-\textbf{2D Sprouts dataset}
-
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template1.png}
-        \caption{template 1}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template2.png}
-        \caption{template 2}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template3.png}
-        \caption{template 3}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template4.png}
-        \caption{template 4}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/template5.png}
-        \caption{template 5}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
-        \caption{test image}
-     \end{subfigure}
-      \caption{Sprouts data: CT of different stages of sprouts growing in a jar. The templates refer to previously scanned volumes that form the `object-prior'.}
-\label{fig:joint}
-\end{figure}
-
-%-----------------------------Sprouts (19 angles)--------------------------
-\newpage
-\subsection{Reconstruction from 19 projection views}
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
-        \caption{Test image}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/fbp.png}
-        \caption{FBP}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/cs_dct.png}
-        \caption{CS-DCT}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/cs_wavelet.png}
-        \caption{CS-wavelet}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/plain_pca.png}
-        \caption{unselective prior+cs}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/19_angles/1/weighted_pca5.png}
-       \caption{our method}
-     \end{subfigure}
-      \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $10\%$ sampling (19 projection views).}
-\label{fig:joint}
-\end{figure}
-
-%-----------------------------Sprouts (66 angles)--------------------------
-\newpage
-\subsection{Reconstruction from 66 projection views}
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
-        \caption{Test image}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/fbp.png}
-        \caption{FBP}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/cs_dct.png}
-        \caption{CS-DCT}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/cs_wavelet.png}
-        \caption{CS-wavelet}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/plain_pca.png}
-        \caption{unselective prior+cs}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/55_angles/1/weighted_pca5.png}
-        \caption{our method}
-     \end{subfigure}
-     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $30\%$ sampling (55 projection views).} 
-\label{fig:joint}
-\end{figure}
-
-%-----------------------------Sprouts (110 angles)--------------------------
-\newpage
-\subsection{Reconstruction from 110 projection views}
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
-        \caption{Test image}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/fbp.png}
-        \caption{FBP}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/cs_dct.png}
-        \caption{CS-DCT}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/cs_wavelet.png}
-        \caption{CS-wavelet}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/plain_pca.png}
-        \caption{unselective prior}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/92_angles/1/weighted_pca5.png}
-        \caption{our method}
-     \end{subfigure}
-     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $50\%$ sampling (92 projection views).} 
-\label{fig:joint}
-\end{figure}
-
-%-----------------------------Sprouts (154 angles)--------------------------
-\newpage
-\subsection{Reconstruction from 154 projection views}
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
-        \caption{Test image}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/fbp.png}
-        \caption{FBP}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_dct.png}
-        \caption{CS-DCT}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_wavelet.png}
-        \caption{CS-wavelet}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/plain_pca.png}
-        \caption{prior unselective+cs}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/weighted_pca5.png}
-        \caption{our method}
-     \end{subfigure}
-     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $83\%$ sampling (154 projection views).} 
-\label{fig:joint}
-\end{figure}
-\newpage
 %--------------------------BIG images: TMH results
@@
 %------------------------------------Bigger images for Sprouts------------------
-\textbf{Sprouts:}
-
+\subsection{Sprouts}
 \begin{figure}[!h]
-    \begin{subfigure}[b]{0.4\linewidth}
+    \begin{subfigure}[b]{0.38\linewidth}
         \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
@@
 \quad
-    \begin{subfigure}[b]{0.4\linewidth}
+    \begin{subfigure}[b]{0.38\linewidth}
         \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
@@
 \quad
-    \begin{subfigure}[b]{0.4\linewidth}
+    \begin{subfigure}[b]{0.38\linewidth}
         \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
@@
         \caption{l1-ls}
-     \end{subfigure}\\
+     \end{subfigure}
 \quad
-    \begin{subfigure}[b]{0.4\linewidth}
+    \begin{subfigure}[b]{0.38\linewidth}
         \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
@@
 \quad
-    \begin{subfigure}[b]{0.4\linewidth}
+    \begin{subfigure}[b]{0.38\linewidth}
         \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
@@
 %--------------------------------Bigger results for Okra------------------------
-\textbf{Okra:}
+\subsection{Okra}
 
@@
 %----------------------------------Comparison with Literature------------------------
-\section{Detecting new changes directly in the measurements}
+\section{Comparison with literature: detecting new changes directly in the measurements}
 Sec.2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature.
@@
 \end{table}
+\newpage
+%-----------------------------------Blurred results (CS)
+\section{Blurred reconstruction under limited views}
 
+When the number of views is large, the reconstruction using CS (l1-ls) is indeed good, as shown below in Fig~\ref{fig:cs_blurred_48_views}.
+For the CS reconstructions shown below, we have tuned the lambda1 values (Figs.~\ref{fig:ssim_rmse_48_views},~\ref{fig:ssim_rmse_24_views},~\ref{fig:ssim_rmse_12_views}) and selected the one with maximum SSIM.
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/48_views/testIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/48_views/result_FBP.png}
+%\captionsetup{labelformat=empty}
+        \caption{FDK}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/48_views/result_CS_lambda0_0.40.png}
+%\captionsetup{labelformat=empty}
+        \caption{l1-ls}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Reconstruction of potato test slice (150$\times$150) from 48 views. The lambda1 for l1-ls reconstruction was chosen to be the optimal value of 0.4 here.} 
+\label{fig:cs_blurred_48_views}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=0.9\columnwidth]{../images/potato/2D/cs_blurred_results/SSIM_RMSE_48_angles.png}
+%\captionsetup{labelformat=empty}
+\caption{SSIM and RMSE for reconstructionn from 48 views for varying levels of $\lambda1$. The optimal value of 0.4 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_48_views}}
+\label{fig:ssim_rmse_48_views}
+\end{figure}
+\newpage
+
+However, when the number of views decreases, the reconstruction using CS (LASSO) is blurred, but with the benefit of suppressed artefacts that are otherwise present in FBP reconstruction.
+This is illustrated in Figs.~\ref{fig:cs_blurred_24_views} and~\ref{fig:cs_blurred_12_views}.
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/24_views/testIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/24_views/result_FBP.png}
+%\captionsetup{labelformat=empty}
+        \caption{FDK}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/24_views/result_CS_lambda0_2.00.png}
+%\captionsetup{labelformat=empty}
+        \caption{l1-ls}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Reconstruction of potato test slice (150$\times$150) from 24 views. The lambda1 for l1-ls reconstruction was chosen to be the optimal value of 2 here.} 
+\label{fig:cs_blurred_24_views}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=\columnwidth]{../images/potato/2D/cs_blurred_results/SSIM_RMSE_24_angles.png}
+%\captionsetup{labelformat=empty}
+\caption{SSIM and RMSE for reconstructionn from 24 views for varying levels of $\lambda1$. The optimal value of 2 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_24_views}}
+\label{fig:ssim_rmse_24_views}
+\end{figure}
+\newpage
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/12_views/testIm.png}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/12_views/result_FBP.png}
+%\captionsetup{labelformat=empty}
+        \caption{FDK}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/12_views/result_CS_lambda0_3.00.png}
+%\captionsetup{labelformat=empty}
+        \caption{l1-ls}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Reconstruction of potato test slice (150$\times$150) from 12 views. The lambda1 for l1-ls reconstruction was chosen to be the optimal value of 3 here.} 
+\label{fig:cs_blurred_12_views}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+As seen here, the reconstruction by CS (LASSO) is indeed blurred when the number of views is very less. The iterative reconstruction was run until convergence (epsilon = 0.001).
+The plots below show the SSIM and RMSE values for varying values of lambda1 for the CS (LASSO) reconstructions of the above test image.
+
+\begin{figure}[!h]
+\centering
+       \includegraphics[width=\columnwidth]{../images/potato/2D/cs_blurred_results/SSIM_RMSE_12_angles.png}
+%\captionsetup{labelformat=empty}
+\caption{SSIM and RMSE for reconstructionn from 12 views for varying levels of $\lambda1$. The optimal value of 3 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_12_views}}
+\label{fig:ssim_rmse_12_views}
+\end{figure}
+\newpage
+%----------------------------Patch-based methods
+\section{\textbf{Patch-based techniques}}
+\label{sec:patch_based}
+Here we present a comparison~\cite{my_dicta_paper} of the performance of the aforementioned PCA-based global prior with a prior that is based on construction of patch-wise dictionaries.
+In both cases, the reconstruction routine is based on typical CS techniques.
+The well-known K-SVD algorithm \cite{Aharon2006} was chosen for construction of patch-based dictionaries.
+For this, patches were extracted from each of the template volumes, from which an overcomplete dictionary was obtained.
+The basic aim of the K-SVD algorithm (or any overcomplete dictionary learning technique) is the compact linear representation of all these patches using the dictionary columns.
+Let $\boldsymbol{D}$ denote the dictionary learned, $N_p$ the total number of patches, and $\boldsymbol{H_i}$ the operator to extract the $i^{\textrm{th}}$ patch from the intermediate reconstructed slice/volume.
+Then, once $\boldsymbol{D}$ is computed in an earlier `training phase', each new test slice (or test volume) can be reconstructed by optimizing a cost function such as the one below:
+\begin{multline}
+J_2(\boldsymbol{\theta},\{\boldsymbol{\alpha_i}\}_{i=1}^{N_p}) = \lVert\boldsymbol{\mathcal{R}\Upsilon\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \\ \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\lVert \boldsymbol{H_i\Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2 +\frac{\lambda_3}{ N_p}\sum_{i=1}^{N_p}\lVert\boldsymbol{\alpha_i}\rVert_1.
+\label{Eq:main_patchBased}
+\end{multline}
+The reconstruction proceeds in an alternating manner, first by minimization of Eq.~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}.
+For both these, the solver in~\cite{l1ls} is used.
+For the former case, the cost function reduces to:
+\begin{equation}
+J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = \lVert \boldsymbol{\mathcal{R} \Upsilon \theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\rVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2.
+\label{Eq:primaryObj_patchBased}
+\end{equation}
+For each $i \in \{1,...,N_p\}$, the cost function reduces to:
+\begin{equation}
+J_{\boldsymbol{\theta}}(\boldsymbol{\alpha}_i) =  \lVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D\alpha_i}\rVert_2^2  + \frac{\lambda_3}{\lambda_2}\lVert\boldsymbol{\alpha_i}\rVert_1.
+\label{Eq:alpha_patchBased}
+\end{equation}
+This summarizes the comparison with patch-based methods.
+\newpage
 \bibliography{tci_ref}

### 2020-07-23 paper/response.tex
Added R3-response to response.pdf

@@
 
+\section{Response to Reviewer 3}
+(We have numbered these comments as R3-Cx, and italicized for clarity)
+
+\textcolor{blue}{\textit{This paper extends an existing algorithm for reconstructing longitudinal tomographic data with a reduced number of projections, by adding a weight map that determines how much to weigh a specific term in the cost function for each voxel of the reconstructed image.
+The authors give an explanation of the approach, and show results for both simulated and experimental data.
+Although the proposed approach seems mathematically sound, the paper itself has several significant issues that make it difficult to assess whether the approach actually improves on existing work.
+}}\\
+
+\textcolor{blue}{\textbf{R3-C1:}\textit{ Most importantly, results are compared with only a single existing method that is specifically designed for low-angle tomography (compressed sensing), and the results of that method seem sub-optimal (at least, it does not match my experience with both applying such methods myself and published results of such methods).
+}}
+
+\textbf{ Response:} The results of the (compared, CS) method are sub-optimal because of a significantly fewer number of views.
+We show  (see R3-C7) that if we increase the number of views, CS actually does very well, as expected, and as mentioned by the reviewer.
+
+We have compared our 2D reconstructions with many other iterative techniques such as SIRT, SART and ART, as seen in Fig.
+12 (Figure.8).
+Earlier we had not included the SSIM values,  and these now appear in Tab.
+3.
+In addition, we have now performed a 2D reconstruction to compare our method with [3] (please see Sec.
+7 of our supplementary material.)\\
+
+\textcolor{blue}{\textbf{R3-C2:}\textit{ Since no details are given about the method that is compared with (what function does in optimize?}}
+
+\textbf{ Response:} In our submitted paper, we had compared our method to the the standard filtered back projection (written as FBP in Figure 1), and CS sensing using l1-ls (e.g.
+Line 33, Column 2, Page 4).
+The function optimized was given in Equation 8.
+We agree that we should have mentioned this earlier in the description, and this has been taken care of in the revised document.
+
+Of the many other prior-based techniques, we have now discussed  below how we contrast with them in Sec.2 (`Related work').
+In addition, we have now performed a 2D reconstruction to compare our method with [3].
+In [3], the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
+This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
+However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image.
+This can be seen in the visual results (and quantitative comparison) in Sec.
+7 of our supplementary material.\\
+
+\textcolor{blue}{\textbf{R3-C3:}\textit{ what were the parameters? how were these chosen?), the experimental results in the paper give very little information to the reader.}}
+
+\textbf{ Response:} Details of the parameters and their tuning were earlier discussed in Section 5B.
+$\lambda_1$ was set equal to 1 in all datasets (as observed by R1, and line 53, page 9, column 2).
+THis was done by visual inspection for one of the dataset and used elsewhere as is.
+We had earlier mentioned that we are using DCT in Page 6 (right column, line 58).
+
+For greater clarity, we have now explicitly mentioned the DCT bases right at the beginning on page 1 Section 1 (Introduction, below Eq.1).
+Further, we have now tuned $\lambda_1$ (as per R1's suggestions) to maximize SSIM of the whole reconstructed test-volume for l1-ls reconstruction of each dataset.
+Once the value was chosen, we retained the same $\lambda_1$ value for uniform prior and spatially-varying prior as well.
+However, this has only marginally improved the reconstructions over our previous ones in the earlier manuscript.
+Here below, we present the changes in the accuracies due to tuning of $\lambda_1$ in Tables~\ref{tab:sprouts_revised_ssim}, and~\ref{tab:okra_revised_ssim}.
+
+The new visual results and SSIM values are in Figs. 13, 15 and 19, and in Tables 4, 5 and 8.
+
+\begin{table}[!h]
+  \caption{Old and revised SSIM (within red RoI) for 3D sprouts dataset}
+  \label{tab:sprouts_revised_ssim}
+\begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{Earlier reported SSIM} & \textbf{Revised SSIM} \\ \hline
+\textbf{l1-ls} & 0.84 & 0.86 \\ \hline
+\textbf{Uniform prior} & 0.83 & 0.83 \\ \hline
+\textbf{Spatially varying prior} & 0.88 & 0.88 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+  \caption{Old and revised SSIM (within red RoI) for 3D okra dataset}
+  \label{tab:okra_revised_ssim}
+\begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{Earlier reported SSIM} & \textbf{Revised SSIM} \\ \hline
+\textbf{l1-ls} & 0.83 & 0.84 \\ \hline
+\textbf{Uniform prior} & 0.85 & 0.85 \\ \hline
+\textbf{Spatially varying prior} & 0.88 & 0.88 \\ \hline
+\end{tabular}
+\end{table}
+
+\textcolor{blue}{\textbf{R3-C4:}\textit{ To address these issues, a large amount of changes would be required in the paper (not only in the experiments, but also throughout the paper, since the performance of compressed sensing methods is one of the main motivations of introducing a new approach).
+Other issues are present in the paper as well (see below for more detailed comments).
+Therefore, I unfortunately have to recommend rejection of the current manuscript.}}
+
+\textbf{Response:} We have now made changes as per this comment and those of the Associate Editor; the details of these are given in our individual responses to the comments.
+In addition, here we wish to state that the performance of compressed sensing is not one of the main motivations of the paper.
+The use of uniform and spatially-varying object-priors in a longitudinal setting is the main contribution of this paper and these techniques are independent of the sparsity-prior (CS) being used, i.e., object-specific prior can be imposed even when $\lambda1$, the weight of sparsity prior, is set to $0$.
+The success of our method on a real-life dataset in a clinical setting is a testament to our methods.\\
+
+%\textbf{Detailed Comments}
+
+\textcolor{blue}{\textbf{R3-C5:}\textit{ The comparisons with existing methods in the current manuscript are insufficient to support the conclusions made in the paper.
+My main concerns are: - The authors only compare with a single method specific to reconstructing tomographic images from a low number of projections (which they call compressed sensing).
+However, this topic is highly studied, and there are many methods available for this.
+The paper would be improved by including results from more methods, for example dictionary learning, total variation minimization, algebraic techniques (DART etcetera), or even simply SIRT with a nonnegativity constraint.}}
+
+\textbf{Response:} This comment is similar to R3-C4.
+The main aim of our paper is the usage of an object-prior along with a weights map for reconstruction from highly undersampled projections in a longitudinal study.
+When the number of views is extremely small, then undersampling artifacts will affect any baseline method, be it SIRT, CS, ART or any other.
+However incorporation of object priors will significantly help to mitigate those artifacts.
+In Fig.12 (Figure 8), we had earlier shown a visual comparison of 2D reconstructions of one of the datasets (potato) by all of the following methods: FBP, CS with DCT as sparsity prior, CS with Haar as sparsity prior, ART, SART, SIRT and our weighted prior method.
+We have now also included a quantitative comparison of the accuracy of these results in Tab. 3 of the new manuscript.\\
+
+\textcolor{blue}{\textbf{R3-C6:}\textit{ No details are given about the CS method that was compared with.
+What type of sparsity did the method assume?
+What objective function did it minimize?
+What parameters did the authors choose?
+How were those parameters chosen?
+How many iterations were used to minimize the objective function?
+Without this information, the comparison does not have much information, and therefore can't be used to support the conclusions made in the paper.}}
+
+\textbf{Response:} This is similar to R3-C3.
+We had earlier mentioned that we are using DCT in Page 6 (right column, line 58).
+For greater clarity, we have now mentioned this in Section 1 (Introduction, below Eq.1).
+The objective function minimized while using l1-ls (CS) optimization is now introduced in Eq.1. This is the same as Eq. 6,  with $\lambda_2 = 0$.
+Details of parameter selection is now in Section 9-B.
+In our earlier submission, $\lambda_1$ and $\lambda_2$ values were chosen by reconstructing the test volume by sweeping through a range of values and selecting the set of values that gave a reasonable visual quality.
+The same value (=1) was retained for all datasets.
+In the current version of the paper, we have now tuned $lambda_1$ (as per R1's suggestions) to maximize SSIM of the whole reconstructed test volume for l1-ls reconstruction of each dataset.
+This value was retained for uniform and spatially-varying prior based reconstruction as well.
+$\lambda_2$ was chosen clairvoyantly,  i.e., based on the value that gave the best visual results on the test.\\
+
+\textcolor{blue}{\textbf{R3-C7:}\textit{ Based on my experience with reconstructing tomographic data from few projections, I would expect the CS results to look \_much\_ better than what is presented in the paper.
+As an example, in Fig 10, based on the results of the FDK algorithm, I would expect any reasonable iterative method with regularization (CS or otherwise) to produce fairly accurate results.
+I'm not sure what the cause of this is, because no details about the used CS method are given (see point above).
+Looking at the images (and other images from iterative methods given by the authors), it seems like the methods have not converged yet, but there could be other causes.}}
+
+\textbf{Response:} The methods have indeed converged.
+Also mention that the perceived quality of reconstruction results using any technique can be quite subjective, and also dependent on the structure of the image as well as the number of projection views.
+In order to demonstrate this, we show the quality of reconstructions by CS for a varying number of views in Sec.
+8 of our supplementary material.
+In this paper, we are considering a very small number of views.
+What is the cause: When the number of views is large, the reconstruction using CS (l1-ls) is indeed good.
+However, when the number of views decreases, the reconstruction using CS (LASSO) is blurred, but with the benefit of suppressed artefacts that are otherwise present in FBP reconstruction.
+This is illustrated in Sec.
+8 of our supplementary material.
+For the 3D reconstructions shown in the updated paper, the $\lambda_1$ value is now chosen by performing l1-ls reconstructions for a wide range of values and then selecting the one that maximizes SSIM.
+We also observe that the optimal $\lambda_1$ value is different for each set of views.
+Hence, an accurate selection of $\lambda_1$ for every dataset and for every set of views may be impractical depending on the application constraints.\\
+
+\textcolor{blue}{\textbf{R3-C8:}\textit{ Related to the previous point, in several results it seems that FDK actually gives the most `accurate' reconstruction for the object.
+For example, in Fig 10 the shape of the leftmost void is changed by the proposed method, and in Fig 12 the shape of the seeds (?) is not well reconstructed by the proposed method.
+This should be discussed in the manuscript.}}
+
+\textbf{Response:}  Although the shape of the left-most void (now in the green RoI of Fig.19 of the updated paper) is slightly bigger than it should be, the results of our method is better than that of FDK and this is reflected in the SSIM values of the new Table 8.
+In practice, the reconstruction of the new regions is dependent on the noise (false-positives) present in the weights-map.
+We have optimally selected the hyperparameter `k' to minimize the noise in the weights-map.
+In order to evaluate the accuracy of our reconstruction of the seeds in Figure 12 of old manuscript (Fig.13 of current manuscript), we have enlarged the green RoI to include the seeds as well (See Fig.
+13-a), and have presented the SSIM on this RoI in Table 4.
+The SSIM value in the green RoI (which includes the seeds) is the highest for our method.
+We note that the results of Fig.13 have been updated after tuning for $\lambda_1$.
+Having said that, even for the results presented in our earlier manuscript, the accuracy for our reconstruction in the area of seeds is the highest.
+The SSIM values for the old 3D okra results over the RoI covering seeds are:\\
+FDK: 0.81\\
+L1-ls:0.82\\
+Uniform prior: 0.76\\
+Spatially-varying prior: 0.84 \\
+In all our results, we wanted to quantitatively measure the structural accuracy of the reconstructions.
+Hence, we have chosen SSIM (with the following factors: 0.1 for accuracy in intensity, 0.2 for accuracy in contrast, and 0.7 for accuracy in shape).
+Hence, the SSIM values give a close interpretation of the results in addition to the visual inspection.
+\\
+
+\textcolor{blue}{\textbf{R3-C9:}\textit{There exist methods that are relevant to the current work, since they use a similar approach.
+For example, ``Region-based iterative reconstruction of structurally changing objects in CT'' uses a similar approach in which image regions that change between scans are detected and reconstructed with a weaker `similarity' prior than other regions.
+A discussion of such methods should be included in the manuscript, and, ideally, direct comparisons should be included to show how the proposed method compares with them.}}
+
+\textbf{Response:} Among the methods in literature that detect new changes, many assume specific object-properties suitable for the application at hand.
+For example, in~\cite{Van2015}, the knowledge of the attenuation coefficient of the fluid is used as a prior for reconstructing its flow through gravel.
+In~\cite{koen2020}, the changes across the successive scan volumes are assumed to be continuous, thus enabling the use of optical flow to model the motion between corresponding voxels of different scan volumes.
+In another study~\cite{vincent2017}, changes between successive scans were modelled by affine deformation whose parameters were computed for motion-correction.
+Such a correction enables acquisition from fewer views than would have otherwise not been possible for reconstruction with adequate fidelity.
+In~\cite{daniil2015}, all the scan volumes are reconstructed together using spatio-temporal regularization.
+In~\cite{Van2014} (``Region-based iterative reconstruction of structurally changing objects in CT''), spline-based models are applied for tracking the regions of change in a SIRT framework.
+However, their method essentially reconstructs from all the different scans of the object simultaneously, and uses the extra redundancy across time simultaneously.
+In contrast to this, we propose a technique to utilize pre-reconstructed object-priors that are available in longitudinal studies.
+(In longitudinal studies, each scan must be reconstructed as soon as it is imaged, with the possible use of reconstructed volumes from previous scans.)
+We have now discussed this in Sec.2 (`Related Work') of our paper.
+In addition, we have now performed a 2D reconstruction to compare our method with [3]. This has been discussed in our response to \textbf{R3-C2}.\\
+
+\textcolor{blue}{\textbf{R3-C10:}\textit{ Related to the previous point, this type of data seems well suited for data-driven techniques (e.g.
+deep learning) that have become very popular in recent years.
+Many papers exist that use deep learning for improving tomographic reconstruction from a low number of projections.
+It would be useful to include a comparison with a deep learning method, and, at the very least, discuss the possibility of using deep learning in this context.}}
+
+\textbf{Response:} Deep learning techniques typically require large amounts of data.
+However, any given longitudinal study will allow for a very limited amount of data..
+Moreover, there will be major generalization errors in deep learning based techniques for direct tomographic reconstruction, and in a clinical setting, we believe, current deep learning methods need to evolve further.\\
+
+\textcolor{blue}{\textbf{R3-C11:}\textit{The discussion of hyperparameter sensitivity is not very detailed.
+It is important to show how reconstruction change when adjusting these paremeters (for example, what happens if $\lambda_1$ is set to 0?).
+In the current manuscript, the authors simply give a range of values that worked for them, but this is not very informative since it depends critically on the scaling of the data, which we don't know.}}
+
+\textbf{Response:} The effect of the hyperparameter k on the weights-map and final reconstruction was earlier shown Figures.
+17 and 18 (Fig.
+20 and 21).
+These figures show that the selection of k decides the sensitivity to noise (false positives) in the weights-map.
+The range of k values deal with the extreme cases of very less amount of noise (Figure 17-a ,Fig.
+20-a) upto high levels of false positives at the expense of not missing any true positive.
+(Figure.
+17-l, Fig.
+20-l).\\
+
+\textcolor{blue}{\textbf{R3-C12:}\textit{ A discussion about computational costs (time, memory) should be included in the paper.
+Since most of the shown results are for quite small images, I'm worried that the approach might not scale well to the large image sizes that are common in high-resolution tomography.
+}}
+
+\textbf{Response:} While the reconstruction accuracy was measured in the (small) regions of new changes, all reconstructions were performed for the full object volume.
+
+We have now presented the computation time of the 3D reconstructions in Table 7 of the paper. 
+For spatially-varying prior, most of the computation time is used in the generation of low-quality eigen-space by reconstructing  each of the templates using CS and FDK.
+This process cannot be performed offline as it involves applying the same imaging geometry used for scanning the test.
+We had performed these reconstructions sequentially.
+Ideally, these reconstructions must be performed parallely on different machines to significantly reduce the computation time.\\
+
+\textcolor{blue}{\textbf{R3-C13:}\textit{ How does measurement noise influence results?
+Typically, in low-dose settings, significant noise is present in tomographic data.
+Does the method work well with such noisy images?
+This should be discussed and ideally results should be shown.}}
+
+\textbf{Response:} In this work, we do not consider low-dose settings.
+Here, we have used standard-dose radiation and hence the Poisson noise (that is present in low-dose measurements) is minimal here.
+We observed this consistently in all the real datasets which we experimented with.
+The only significant reconstruction artefacts are the ones due to insufficient views, and we have focussed on removing these alone, whilst preserving the new changes.
+For the case of low-dose imaging, we have presented a few reconstruction techniques in~\cite{gopal2019low}.\\
+
+\textcolor{blue}{\textbf{R3-C14:}\textit{The paper includes several statements that are either false or not well supported.
+Examples include:    - `Fig.
+1 shows that although CS removes the artefacts created due to subsampling, its reconstruction is blurred.' This is a very broad statement about the performance of an entire group of methods (CS), for which giving only a single image without any details is not enough support by far.}}
+
+\textbf{Response:} We wish to point out that our inference about CS reconstructions being blurred on undersampled data has been earlier pointed out in the published work~\cite{PICCS} in Page 4, line 22.
+We again reiterate this here that the reconstruction using CS is of good quality (as proven in literature) when the number of views is large.
+However, when the number of views is limited, the optimizer (with optimal lambda) indeed blurs the overall reconstruction in an attempt to remove the sub-sampling artefacts.
+We have now demonstrated this in our response to \textbf{R3-C7}.
+
+However, for greater clarity about our comments on CS, we have retracted the generic statement from our earlier Introduction section.
+(``Fig.
+1 shows that although CS removes the artefacts created due to subsampling, its reconstruction is blurred.'').
+Insead, since we have used a particular optimizer of the CS family, namely the l1-regularized least squares (l1-ls), we have now rephrased the term `CS'  with `l1-ls' wherever appropriate in the paper.\\
+
+\textcolor{blue}{\textbf{R3-C15:}\textit{ `which is an important issue that has so far been overlooked in the literature on tomography' -- this is again very broad, and there are actually papers that do address this issue (see above).}}
+
+\textbf{Response:} Agreed.
+We have now retracted this statement from the paper.
+However, we have now explained (in Section 2- `Related work') how our work contrasts with the other existing methods that detect new regions.
+More details are in our response to R3-C21.\\
+
+\textcolor{blue}{\textbf{R3-C16:}\textit{ `which was shown [23] to be better when compared to dictionary-based priors.' -- better in which respect?
+Currently, this strong statement is only supported by a paper that is written by the same authors -- more papers should probably be included to support this.}}
+
+\textbf{Response:} Since the main aim of our paper is to modulate the influence of priors, and not the comparison of global-priors with dictionary-priors, we have retracted this statement without any major impact in the readability of the paper.
+\\
+
+\textcolor{blue}{\textbf{R3-C17:}\textit{ `convergence of this optimization is guaranteed by the monotone convergence theorem' -- I think a reference is useful here.}}
+
+\textbf{Response:} The relevant reference is ~\cite{monotone} and is now included in the paper.\\
+
+\textcolor{blue}{\textbf{R3-C18:}\textit{ `we emphasize that in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections simulated from 3D volumes'.
+This is simply not true: there are \_many\_ papers on tomographic reconstruction that include comparisons using real (raw) data, especially outside the medical context.
+In fact, many of such datasets are publicly available, and are regularly used to compare methods.}}
+
+\textbf{Response:} Our statement was based on papers which had used either phantoms or dynamic CT data.
+For example, In papers such as~\cite{pirple}, the dataset consisted of measurements corresponding to a lung-phantom; validation was not performed on a dataset of a real lung CT.
+In~\cite{Hakka2019}, the dynamic dataset consisted of face emoji phantoms and simulations from an already available reconstructed lung volume.
+After surveying literature again, we have now found papers that have used real data.
+Hence,  we have now retracted our earlier statement about literature and have mentioned instead the general scenario: ``Data from commercially available CT machines is not suitable because most CT scanners do not reveal the raw measurements, and instead output only the full reconstructed volumes.
+Moreover, the process of conversion from the  projections to the full volumes is proprietary.'' \\
+
+\textcolor{blue}{\textbf{R3-C19:}\textit{ It is not really clear from the paper what the main contributions are compared with existing work.
+I think this is mainly caused by the structure of the paper, which is not really clear for me.
+For example, the `Contributions' section includes, for a large part, a description of one of the experimental applications of the method -- I don't understand this inclusion.
+It would be better to clearly state here the contribution of this paper compared with existing methods.
+Also, for me the fact that some results are given before the explanation of the method is confusing -- for me it would be clearer to have all experiments in a single section.
+Furthermore, Schematic 1 was not clear to me while reading the paper, since at that point terms like `old regions' and `pilot reconstruction' are not introduced.
+All these unclarities made it difficult to assess what is novel in the paper.}}
+
+\textbf{Response:} We have now re-organized the structure of the paper into the following well-differentiated sections:
+\begin{itemize}
+
+\item Introduction, 
+\item related work (to compare this work with similar papers in literature), 
+\item contributions, 
+\item application (on a longitudinal medical data), 
+\item uniform prior, 
+\item results: uniform prior (including comparison with results from FDK and l1-ls), 
+spatially-varying prior, 
+\item results: spatially varying prior (including comparison with results from FDK, l1-ls and uniform prior), 
+\item discussions (to discuss parameter tuning and limitations of our work), and 
+  conclusions.
+  \end{itemize}
+For greater clarity, we have now removed Schematic 1 from the paper; We have  ensured that the rest of the paper can be followed without it.
+
+\textcolor{blue}{\textbf{R3-C20:}\textit{ The mathematical notation is not always clear: for example, the authors define `y = Rx' while later minimizing `||Rx-y||', which, given the mathematical definition, should always be zero.
+Of course, I understand what the authors mean here, but I think it is important to be clear with the mathematical description to avoid any confusion.}}
+
+\textbf{Response:} In order to be clear with the description, we have now rewritten Sec.1 (Introduction). All the variables are now introduced in paragraph 2 and 3 of Page 1 of the paper.\\
+
+\textcolor{blue}{\textbf{R3-C21:}\textit{ It seems that the weight map approach proposed by the authors is novel in this context.
+However, related methods exist that also try to predict the image regions where change is happening and improve reconstructions using this information.
+These methods are not discussed in the paper (or compared with), making it difficult to assess the novelty properly.}}
+
+\textbf{Response:} Among the methods in literature that detect new changes, many assume specific object-properties suitable for the application at hand.
+For example, in~\cite{Van2015}, the knowledge of the attenuation coefficient of the fluid is used as a prior for reconstructing its flow through gravel.
+In~\cite{koen2020}, the changes across the successive scan volumes are assumed to be continuous, thus enabling the use of optical flow to model the motion between corresponding voxels of different scan volumes.
+In another study~\cite{vincent2017}, changes between successive scans were modelled by affine deformation whose parameters were computed for motion-correction.
+Such a correction enables acquisition from fewer views than would have otherwise not been possible for reconstruction with adequate fidelity.
+In~\cite{daniil2015}, all the scan volumes are reconstructed together using spatio-temporal regularization.
+We have now discussed this in Sec.2 (`Related Work') of our paper.
+In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. This has been discussed in our response to \textbf{R3-C2}.\\
+
 \bibliography{tci_ref}

### 2020-07-23 paper/tci.tex
Merged Lit survey

@@
  \label{sec:related}
-In this section, we survey the existing literature on tomographic reconstruction from undersampled measurements using object priors.
-In most cases, the object prior consists of an object reconstructed to high quality from a large number of projection angles.
-One of the earliest pieces of work in this area is the well-cited PICCS method~\cite{PICCS}, which enforces a robust-norm based similarity between the test and the object prior, in addition to a sparsity prior on the test.
-However in such a technique, there is no inherent mechanism to prevent the prior from overwhelming the current reconstruction, and choice of relative weights between the object and sparsity priors is difficult.
-A closely related method called PIRPLE was proposed in~\cite{pirple}, with additional steps to register the object prior and the test and a somewhat more flexible combination of data fidelity terms, sparsity prior and object prior.
-However, this method too has similar limitations as PICCS.
-In some pieces of work, the object prior is projected in the same angles as the current set of test measurements, and a set of projection differences is computed.
-These projection differences are essentially tomographic projections of the difference between the unknown test and the known object prior.
-Hence, a variety of reconstruction algorithms can be used to estimate such a difference image which can then be added to the object prior to yield the final estimate of the test.
-Such methods have been proposed in~\cite{Pourmorteza2015,Lee2012}.
-However, the reconstruction of the difference image will inherently contain artifacts due to a sparse set of projections, and these artifacts will appear in the final reconstruction as there is no mechanism to mitigate them (unlike the method that we propose).
-This can be seen in Sec.7 of our supplementary material~\cite{supp_paper}, where we have compared our method with~\cite{Lee2012}.
-In some recent techniques such as~\cite{Marjolein2016}, additional knowledge regarding regions of most likely change between the test and object prior is assumed, and lower weights are assigned to the prior in those regions.
-However, this is not done in a data driven manner and relies on additional expert domain knowledge which may not be available or which may be infeasible to acquire.
-There exists a fairly large-sized body of literature for reconstruction of structurally changing objects.
-In such cases, it may be infeasible to gather a large number of projections at every time instant.
-Moreover, there is additional temporal redundancy available which can reduce the required sample complexity for good reconstruction, and at the same time, tracking structural changes across time is of paramount importance.
-Many interesting approaches for this have been proposed in~\cite{daniil2015,koen2020, Van2015,HaoGao,Van2014}.
-These approaches variously use 4D sparsifying transforms for exploiting spatio-temporal redundancy~\cite{daniil2015}, robust principal components analysis assuming that the object consists of a large static part (background) and a sparse moving part (foreground)~\cite{HaoGao}, optical flow computations between projections (at different time instances) of the dynamic nonrigid object~\cite{koen2020} with additional key-frame and residual modelling in~\cite{Guangming2019}, spline-based models for tracking the regions of change in an SIRT framework~\cite{Van2014}, or knowledge of fluid models (piecewise constant shapes of attenuation curves in the dynamic region) in an SIRT framework~\cite{HaoGao}.
-However, all these techniques~\cite{daniil2015,koen2020,Van2015,HaoGao,Van2014} essentially reconstruct all the different stages of the object simultaneously, and use the extra redundancy across time simultaneously.
-In the scenario of a longitudinal study (where projection measurements are acquired at instants that are several weeks apart) which we consider in this paper, such approaches are not feasible.
-A longitudinal study will necessarily require reconstruction results after acquisition of each set of measurements.
-In this paper, we present a technique that makes use of multiple object priors, corresponding to high quality reconstructions of similar objects across time.
-We use these priors to improve the reconstruction of the test from largely undersampled measurements.
-In particular, we define the regions of change between the test and the eigenspace spanned by the previous high quality object priors in a purely data driven manner.
-Very importantly, our technique clearly differentiates between genuine structural changes and ``changes'' that appear due to undersampling artefacts.
-Besides this, since we use a statistical model with multiple object priors, we avoid the problem of selecting an appropriate single object prior unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and also make use of the additional information available in the multiple priors.
+ The idea of using a reduced number of views is most pronounced in
+specialized applications. For example, in~\cite{Essam2015},
+sparsity-constrained optimization is presented for angiography. Here,
+the regions of interest are the vessels alone and they are highlighted
+by physically inserting a contrast agent, and therefore there is an
+inherent sharper contrast between the vessels and the background.  In
+other applications where the spatial-gradient of the underlying volume
+is known to be sparse, the `total variation' method, as used
+in~\cite{Li2015,Polak2017}, can be applied.  In a more generalized
+application scenario, like the ones addressed in this paper, any
+information about the regions of interest is not known, and such
+techniques have limited applicability.
+
+%  As can be seen
+% in the situatiowe will
+% later see in Figs.\ref{fig:object-prior_test_okra}
+% and~\ref{fig:object-prior_test_sprouts}, the spatial-gradient of many
+% datasets is not sparse.
+
+Most object-prior based reconstruction have been in the areas of
+dynamic CT and 4D-CT. %In dynamic CT, the object being scanned
+%undergoes changes between successive projection views and hence is not
+%stationary even within a single complete scan. In contrast, in 4D-CT,
+%a set of 3D CT scans are taken over short intervals of time, and the
+%object undergoes changes between successive scans.  The reconstruction
+%is then performed over the entire set generating several 3D
+%volumes.
+%In most scenarios, the object-prior
+The object-prior usually consists of an object
+reconstructed to high quality from a large number of projection
+angles. One of the earliest pieces of work in this area is the
+well-cited PICCS method~\cite{PICCS} for dynamic CT, which enforces a robust-norm
+based similarity between the test and the object prior,
+in addition to a sparsity prior on the test. The limitation is the
+unchecked over-emphasis of the prior on the reconstruction of the test
+at hand. A closely related method called PIRPLE was proposed
+in~\cite{pirple}, with additional steps to register the object prior
+and the test and a somewhat more flexible combination of data fidelity
+terms, sparsity prior and object prior. However, this method too has
+similar limitations as PICCS.
+
+In order to prevent the object-prior from overwhelming the
+reconstruction of test, few other approaches have either estimated the
+motion between the object-prior and the test or have applied very
+specific object-properties for identifying the new changes in the
+test.  Examples for the former include~\cite{koen2020}, where the
+changes across the sucessive scan volumes are assumed to be
+continuous, thus enabling the use of optical flow to model the motion
+between corresponding voxels of different scan volumes. In another
+study~\cite{vincent2017}, changes between successive scans were
+modelled by affine deformation whose parameters were computed for
+motion-correction, which inturn enables acquisition from fewer
+views. In~\cite{daniil2015}, all the scan volumes are reconstructed
+together using spatio-temporal regularization. Here again, the
+inherent assumption is the continuity across volumes in space or
+time. The methods that use object-specific knowledge
+are~\cite{Van2015} and~\cite{Marjolein2016}.  In~\cite{Van2015}, the
+knowledge of the attenuation coefficient of the fluid is used as a
+prior for reconstructing its flow through gravel. However, this relies
+on additional expert domain knowledge which may not be available or
+which may be infeasible to acquire.
+
+Other approaches variously use robust principal components
+analysis assuming that the object consists of a large static part
+(background) and a sparse moving part (foreground)~\cite{HaoGao},
+spline-based models for tracking the regions of change in an SIRT
+framework~\cite{Van2014}. However, all these
+techniques~\cite{daniil2015,koen2020,Van2015,HaoGao,Van2014}
+essentially reconstruct all the different stages of the object
+simultaneously, and use the extra redundancy across time
+simultaneously. In the scenario of a longitudinal study (where
+projection measurements are acquired at instants that are several
+weeks apart) which we consider in this paper, such approaches are not
+feasible. A longitudinal study will necessarily require reconstruction
+results after acquisition of each set of measurements
+
+There exists methods for estimating the new changes (in the test)
+directly in the projection space. In such techniques, the object prior
+is projected in the same set of views as the current set of test
+measurements, and a set of projection differences is computed. These
+projection differences are essentially tomographic projections of the
+difference between the unknown test and the known object prior. Hence,
+a variety of reconstruction algorithms can be used to estimate such a
+difference image which can then be added to the object prior to yield
+the final estimate of the test. Such methods have been proposed
+in~\cite{Pourmorteza2015,Lee2012}. However, the reconstruction of the
+difference image will inherently contain sub-sampling artefacts, and
+these artefacts will appear in the final reconstruction as there is no
+mechanism to mitigate them (unlike the method that we propose). This
+can be seen in Sec.~4 of our supplementary material~\cite{supp_paper},
+where we have compared our method with~\cite{Lee2012}.
+
+In this paper, we present a technique that makes use of multiple
+object priors, corresponding to high quality reconstructions of
+similar objects across time. We use these priors to improve the
+reconstruction of the test from largely undersampled measurements. In
+particular, we define the regions of change between the test and the
+eigenspace spanned by the previous high quality object priors in a
+purely data driven manner. Very importantly, our technique clearly
+differentiates between genuine structural changes and ``changes'' that
+appear due to undersampling artefacts.  Besides this, since we use a
+statistical model with multiple object priors, we avoid the problem of
+selecting an appropriate single object prior
+unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and
+also make use of the additional information available in the multiple
+priors.
+
+%-------------------------------------------------------------------
 
@@
      \end{subfigure}
-      \caption{Potato dataset: One slice (slice-A) each from the previously scanned objects (the first three from left) and a slice from the test 
+      \caption{Potato dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
         volume (extreme right). Notice the appearance of the fourth

### 2020-07-23 paper/response.tex
pre-final, added results with cs_lambda=0

@@
 We have  ensured that the rest of the paper can be followed without it.
-We have also moved the discussion on the earlier patch-based methods to supplementary material.
+We have also moved the discussion on the earlier patch-based methods to supplementary material~\cite{supp_paper}.
 However, results not reported earlier prior to this submission using the uniform prior on 3D volumetric data continues to be present (as mentioned above) in Section 6 since it forms an important part of our story for this paper.\\
@@
 This reference is now mentioned in our related work; although this paper is not directly applicable in longitudinal studies where object-priors `are' available, there is a reference in this paper to another paper which does make use of object-prior.
-We show how our work is superior in our response to R3 below (we include this in the supplementary material).
+We show how our work is superior in our response to R3 below (we include this in the supplementary material~\cite{supp_paper}).
 \\
@@
 
-In Sec.5 of our supplementary material, we describe why the image in Fig.17(c) (Fig.10(c) of the old version) appears over-regularized by presenting reconstructions on 2D potato dataset for different number of views and optimally tuned $\lambda_1$ values.
+In Sec.5 of our supplementary material~\cite{supp_paper}, we describe why the image in Fig.17(c) (Fig.10(c) of the old version) appears over-regularized by presenting reconstructions on 2D potato dataset for different number of views and optimally tuned $\lambda_1$ values.
 \\
@@
 16.
-For other cases, larged sized images are in the supplementary material.\\
+For other cases, large sized images are in the supplementary material~\cite{supp_paper}.\\
 
@@
 
-\textbf{Response:} In order to save space and for greater clarity, we have now moved the discussion on patch-based techniques to supplementary material.
+\textbf{Response:} In order to save space and for greater clarity, we have now moved the discussion on patch-based techniques to supplementary material~\cite{supp_paper}.
 
@@
 
- \textbf{Response:} Accepted. This has been corrected, and the equation has now been moved to  supplementary material (Eq.2). \\
+ \textbf{Response:} Accepted. This has been corrected, and the equation has now been moved to  supplementary material~\cite{supp_paper} (Eq.2). \\
 
@@
 3.
-In addition, we have now performed a 2D reconstruction to compare our method with [3] (please see Sec.
-7 of our supplementary material.)\\
+In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012} (please see Sec.~4 of our supplementary material~\cite{supp_paper}.)\\
 
@@
 Of the many other prior-based techniques, we have now discussed  below how we contrast with them in Sec.2 (`Related work').
-In addition, we have now performed a 2D reconstruction to compare our method with [3].
-In [3], the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
+In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}.
+In~\cite{Lee2012}, the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
 This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
 However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image.
-This can be seen in the visual results (and quantitative comparison) in Sec.
-7 of our supplementary material.\\
+This can be seen in the visual results (and quantitative comparison) in Sec.~4 of our supplementary material~\cite{supp_paper}.\\
 
@@
 The same value (=1) was retained for all datasets.
-In the current version of the paper, we have now tuned $lambda_1$ (as per R1's suggestions) to maximize SSIM of the whole reconstructed test volume for l1-ls reconstruction of each dataset.
+In the current version of the paper, we have now tuned $\lambda_1$ (as per R1's suggestions) to maximize SSIM of the whole reconstructed test volume for l1-ls reconstruction of each dataset.
 This value was retained for uniform and spatially-varying prior based reconstruction as well.
@@
 In order to demonstrate this, we show the quality of reconstructions by CS for a varying number of views in Sec.
-8 of our supplementary material.
+5 of our supplementary material~\cite{supp_paper}.
 In this paper, we are considering a very small number of views.
@@
 This is illustrated in Sec.
-8 of our supplementary material.
+5 of our supplementary material~\cite{supp_paper}.
 For the 3D reconstructions shown in the updated paper, the $\lambda_1$ value is now chosen by performing l1-ls reconstructions for a wide range of values and then selecting the one that maximizes SSIM.
@@
 17-l, Fig.
-20-l).\\
+20-l).In our experiments, the object prior had a stronger impact on reconstructions than the sparsity prior.
+This is because the object prior was built using high quality previous scans.
+
+\textbf{Reconstruction with $\lambda_1 =0$:} Here, below is a slice from the reconstructed potato volume when $\lambda_1$ is set to $0$, i.e., with no sparsity prior and with object prior alone.
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/cs_lambda_0/testIm_green}
+%\captionsetup{labelformat=empty}
+        \caption{FDK}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/cs_lambda_0/fdkIm_green.png}
+%\captionsetup{labelformat=empty}
+        \caption{l1-ls}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.3\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/cs_lambda_0/weightedPriorIm_green.png}
+%\captionsetup{labelformat=empty}
+        \caption{Uniform Prior}
+     \end{subfigure}
+     \caption{Example of a reconstruction with zero sparsity prior.}
+     \label{fig:potato_cs_lambda_0}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+\begin{table}[!h]
+  \centering
+  \caption{SSIM of reconstructions shown in Fig.~\ref{fig:potato_cs_lambda_0}}
+\begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{FDK} & \textbf{Spatially varying prior} \\ \hline
+\textbf{Red RoI} & 0.94 & 0.85 \\ \hline
+\textbf{Green RoI} & 0.92 & 0.90 \\ \hline
+\textbf{Cyan RoI} & 0.88 & 0.94 \\ \hline
+\end{tabular}
+\end{table}\\
 
@@
 
-\textbf{Response:} While the reconstruction accuracy was measured in the (small) regions of new changes, all reconstructions were performed for the full object volume.
+\textbf{Response:}While the reconstruction accuracy was measured in the (small) regions of new changes, all reconstructions were performed for the full object volume.
 
-We have now presented the computation time of the 3D reconstructions in Table 7 of the paper. 
+\begin{table}[!h]
+  \centering
+\caption{Computation time for reconstruction of volumes using various methods.
+The configuration of the system used was x86\_64 architecture, 62GB RAM, 12-core AMD 3.8GHz processor, with Nvidia GeForce RTX 2080 Ti GPU.}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\hline
+   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}c@{}}Spatially-\\Varying\\ prior \\+ l1-ls\end{tabular}} \\\hline
+%\textbf{\begin{tabular}[c]{@{}c@{}}Potato\\size:(150,150,100)\\45 views\end{tabular}}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338$\times$338$\times$123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130$\times$130$\times$130)\\xx views\end{tabular}}  & 6 sec. & 3 hrs. & 60 min. &  17 hrs.\\ \hline
+\end{tabular}
+\label{table:Computation_time_3D}
+\end{table}
+
+The computation time for each of the methods is presented in Table~\ref{table:Computation_time_3D}.
 For spatially-varying prior, most of the computation time is used in the generation of low-quality eigen-space by reconstructing  each of the templates using CS and FDK.
@@
 We had performed these reconstructions sequentially.
-Ideally, these reconstructions must be performed parallely on different machines to significantly reduce the computation time.\\
+Ideally, these reconstructions must be performed in parallel on different machines to significantly reduce the computation time.\\
 
@@
 1 shows that although CS removes the artefacts created due to subsampling, its reconstruction is blurred.'').
-Insead, since we have used a particular optimizer of the CS family, namely the l1-regularized least squares (l1-ls), we have now rephrased the term `CS'  with `l1-ls' wherever appropriate in the paper.\\
+Instead, since we have used a particular optimizer of the CS family, namely the l1-regularized least squares (l1-ls), we have now rephrased the term `CS'  with `l1-ls' wherever appropriate in the paper.\\
 
@@
 \item contributions,
+\item datasets
 \item application (on a longitudinal medical data), 

### 2020-07-23 paper/tci.tex
pre-final, added results with cs_lambda=0

@@
 eigenspace spanned by the previous high quality object priors in a
-purely data driven manner. Very importantly, our technique clearly
-differentiates between genuine structural changes and ``changes'' that
-appear due to undersampling artefacts.  Besides this, since we use a
-statistical model with multiple object priors, we avoid the problem of
-selecting an appropriate single object prior
+purely data driven manner. Additionally, our technique differentiates
+between genuine structural changes and ``changes'' that appear due to
+undersampling artefacts (as seen in Sec.4 of our supplementary
+material~\cite{supp_paper}).  Besides this, since we use a statistical
+model with multiple object priors, we avoid the problem of selecting
+an appropriate single object prior
 unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and
 also make use of the additional information available in the multiple
-priors.
+priors. Our technique also has the advantage of not requiring any
+expert-domain knowledge about the object being scanned.
 
@@
 %object-prior after its preliminary pilot reconstruction.
-
 In our experiments, the first volume was assumed to be the test while
@@
 %Further, this alignment can be refined following every update of the reconstructed test volume.
-
 In our experiments, the first 3 volumes were used to build the object-prior and the
@@
 where we introduced man-made defects, the changes here are purely the
-work of nature.
-
-In our experiments, the first 5 volumes were used to build the object-prior and the
+work of nature. In our experiments, the first 5 volumes were used to build the object-prior and the
 last volume was used as the test. The ground truth consists of FDK reconstructed
@@
 %useful.
-This data was sourced from Tata Memorial Centre~\cite{tmh} in 
-  Parel, Mumbai.  This is the national comprehensive centre for the
-  prevention, treatment, education and research in cancer, and is
-  recognized as one of the leading cancer centres in India. The dataset (Fig.~\ref{fig:RFA2_test_object-prior}) consists
-of parallel beam measurements that are generated from 2D slices of the
-organ (liver) acquired at different stages of a radio-frequency
-ablation study. In such a procedure~\cite{Dong2015}, the physician
-inserts a thin needle-like probe into the organ. Repeated CT scans of
-the patient are acquired in order to track the movement of the
-needle and to ensure that it is reaching the appropriate target
+This data was sourced from Tata Memorial Centre~\cite{tmh} in Parel,
+Mumbai.  This is the national comprehensive centre for the prevention,
+treatment, education and research in cancer, and is recognized as one
+of the leading cancer centres in India. The dataset
+(Fig.~\ref{fig:RFA2_test_object-prior}) from this longitudinal medical
+study consists of 8 scans taken at different stages of radio-frequency
+ablation study of a liver. In such a procedure~\cite{Dong2015}, the
+physician inserts a thin needle-like probe into the organ. Repeated CT
+scans of the patient are acquired in order to track the movement of
+the needle and to ensure that it is reaching the appropriate target
 tumor. Once the needle hits the tumor, a high-frequency electric
 current is passed through the tip of the probe and this burns the
-malignant tumor (ablation). The aim of the scan at this ablation stage is to
-reveal accurate details of the changes within.
-
-In our experiments using this dataset, we demonstrate the usefulness of \textit{both}
-uniform prior and spatially varying prior. For the first case, we choose the first 6 slices to build the object prior and use slice 7 as the test. For the latter case, we choose the first
-7 slices to build the object prior and use slice 8 as the test.
+malignant tumor (ablation). The aim of the scan at this ablation stage
+is to reveal accurate details of the changes within.
+
+In our experiments, we generate parallel beam measurements from 2D
+slices from each of the 8 volumes. Note that all these 8 slices are
+located at the \emph{same} index (slice number corresponding to the
+same depth) within each of the respective volumes.  Observe (in
+Fig.~\ref{fig:RFA2_test_object-prior}) that the needle is seen in all
+of the first 7 slices and the effect of ablation is seen in the 8th
+slice.
+%In our experiments using this dataset, we demonstrate the usefulness of \textit{both} uniform prior and spatially varying prior.
+For the first case, we choose the first 6 slices to build the object prior and use slice 7 as the test.
+For the latter case, we choose the first 7 slices to build the object prior and use slice 8 as the test.
 %--------------------------Results on TMH data--------------------------
@@
 longitudinal study. Here, our data consists of successive scans of the liver taken
-during a radio-frequency ablation procedure described in Sec.~\ref{sec:datasets}. In this context, we classify the goal of any of our
+during a radio-frequency ablation procedure as described in Sec.~\ref{sec:datasets}. In this context, we classify the goal of any of our
 reconstruction techniques into two categories: 
@@
 \subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
-\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) FBP and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures, SSIM $=0.35$ and (d) uniform prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
+\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) FBP and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures (reasons discussed in Sec.
+5 of our supplementary material~\cite{supp_paper}), SSIM $=0.35$ and (d) uniform prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
 The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
@@
 (atleast one-fifth) than the conventional number of views used in a
-standard hospital setting.
-
-The dataset from this longitudinal medical study consists of 8 scans
-taken during the ablation procedure. We demonstrate our method for 2D
-reconstruction by choosing a single slice from each of the 8 volumes
-as our dataset. Note that all these 8 slices are located at the
-\emph{same} index (slice number corresponding to the same
-depth) %~\footnote{The notion of~\textit{same index} (slice  number
-%corresponding to the same depth) makes sense in the context, because
-%in such problems, the different scans are aligned with each
-%other.}
-within each of the respective
-volumes. Fig.~\ref{fig:RFA2_test_object-prior} shows the chosen set of
-2D slices (each of size 512$\times$512) from the different
-volumes. Observe that the needle is seen in all of the first 7 slices
-and the effect of ablation is seen in the 8th slice. \\
-
-\textbf{Tracking the needle:} We first choose slices 1-6 as our
+standard hospital setting. To summarize, when our aim is\\
+
+\begin{itemize}
+\item \textbf{Tracking the needle},  we first choose slices 1-6 as our
 object-prior, and reconstruct slice 7 with the specific goal of
@@
 
-\textbf{Observing details of the ablation:} Next, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e., a somewhat higher number of views this time.
+\item \textbf{Observing details of the ablation}, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e., a somewhat higher number of views this time.
 Fig.~\ref{fig:RFA2_few_views} shows the reconstructions of slice 8 by different methods.
 We see that the spatially-varying prior reconstruction brings in the advantage of the prior without adversely affecting the reconstruction of new regions.
+  \end{itemize}
 
@@
 \label{sec:method_uniform_prior}
-Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform  prior-based reconstruction.
-Principal Component Analysis (PCA) has been traditionally used to find the significant modes of (Gaussian corrupted) data.
+Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform  prior-based reconstruction since we are extending this algorithm to 3D reconstructions as part of this work.
+
+%Principal Component Analysis (PCA) has been traditionally used to find the significant modes of (Gaussian corrupted) data.
 In this regard, it has been widely applied in the context of data compression.
@@
 %A preliminary version of this particular method was earlier presented in \cite{my_dicta_paper}.
-
 We first present the eigenspace-cum-CS prior-based reconstruction.
@@
 The eigenspace $E_{\text{high}}$ of the $L$ previously scanned objects $Q_1,Q_2,...,Q_L$ is pre-computed.
-Here, it is assumed that the test volume, barring the new changes, can be expressed as a sparse linear combination of the principal components (eigenvectors of the covariance matrix) obtained from a group of structurally similar volumes.
+Here, it is assumed that most of the test volume, barring the new changes, can be expressed as a sparse linear combination of the principal components (eigenvectors of the covariance matrix) obtained from a group of structurally similar volumes.
 Hence, the object-prior is represented by means of PCA.
@@
 \end{align}
-Note that $\boldsymbol{\theta}$ is solved for using the basis pursuit CS solver~\cite{l1ls}. Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
+Note that $\boldsymbol{\theta}$ is solved for using the basis pursuit CS solver, (l1-ls)~\cite{l1ls}. Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
 \begin{equation}
@@
 \end{equation}
- Optimal values of $\lambda_1, \lambda_2$ must be empirically chosen \textit{a priori}, based on the reconstructions of one of the template volumes (see also Sec.~\ref{sec:discussion}).
+%Optimal values of $\lambda_1, \lambda_2$ must be empirically chosen \textit{a priori}, based on the reconstructions of one of the template volumes (see also Sec.~\ref{sec:discussion}).
 The cost function described in Eq.~\ref{Eq:main_prior} is biconvex and the convergence of this optimization is guaranteed by the monotone convergence theorem~\cite{monotone}.
@@
 \caption{3D reconstruction of the okra from $10\%$ projection
-  views (b) has strong streak artefacts, (c) blurred, (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
+  views (b) has strong streak artefacts, (c) blurred (more details in Sec.
+5 of our supplementary material~\cite{supp_paper}), (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
 \label{fig:okra_3D_results_uniform}
@@
   \centering
-  \caption{SSIM of the full reconstructed okra volume by various methods.}
-\begin{tabular}{|l|c|c|c|c|}
+  \caption{SSIM of the full reconstructed okra volume by various methods. The SSIM of ground-truth (ideal reconstruction) is 1.}
+\begin{tabular}{|l|c|c|c|}
 \hline
-                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{full Volume} & 1 (ideal)                     & 0.83        &  0.87       & \textcolor{red}{0.89}                                                                                   \\ \hline
+                   &  \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
+\textbf{full Volume} &  0.83        &  0.87       & \textcolor{red}{0.89}                                                                                   \\ \hline
 \end{tabular}
@@
   \centering
-  \caption{SSIM of the full reconstructed sprouts volume by various methods.}
+  \caption{SSIM of the full reconstructed sprouts volume by various methods. The SSIM of ground-truth (ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|}
 \hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{Full volume}   & 1 (ideal)                    & 0.91        & 0.82       & \textcolor{red}{0.95}                                                                                                                       \\ \hline
+                   &  \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
+\textbf{Full volume}  & 0.91        & 0.82       & \textcolor{red}{0.95}                                                                                                                       \\ \hline
 \end{tabular}
@@
 Although the uniform prior can be very useful in some
-circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a major
-limitation when we want accurate details of the new changes. While the
+circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a 
+limitation when we want accurate details of a portion, for example, of the new changes. While the
 uniform prior compensates very well for the possible artefacts due to
 sparse measurements, it dominates the regions with new changes masking
-the signal, as was seen earlier in Fig.~\ref{fig:RFA2_few_views}-d. Ideally, we
+the signal, as was seen earlier in Fig.~\ref{fig:RFA2_few_views}(d). Ideally, we
 will want to impose the prior only in the regions that are common
@@
  matrix $\boldsymbol{W}$, where $W_{ii}$ contains the (non-negative) weight assigned to the $i^{\textrm{th}}$ voxel of the prior.
-$\boldsymbol{W}$ is first constructed using some preliminary reconstruction methods (to be described in the following section), following which Eq.~\ref{eq:spatially-varying_prior} is used to obtain the final reconstruction.
+$\boldsymbol{W}$ is first constructed using some preliminary reconstruction methods, following which Eq.~\ref{eq:spatially-varying_prior} is used to obtain the final reconstruction.
 In regions of change in test data, we want lower weights for the prior when compared to regions that are similar to the prior.
@@
   \item Perform pilot reconstructions of the test using $M$ different
-    reconstruction algorithms\footnote{CS~\cite{lasso}, Algebraic Reconstruction Technique (ART)~\cite{art},
-     Simultaneous Algebraic Reconstruction Technique (SART)~\cite{sart} and  Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt}}. Let this set be denoted
+    reconstruction algorithms like the CS~\cite{lasso}, Algebraic Reconstruction Technique (ART)~\cite{art},
+     Simultaneous Algebraic Reconstruction Technique (SART)~\cite{sart} and  Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt}. Let this set of pilot reconstructions be denoted
     as $X \triangleq \{X^j\}_{j=1}^M$ where $j$ is an index for the
@@
 \caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g).
-The SSIM of the ground-truth (ideal reconstruction) is 1, and these are computed within the red RoI of the test image shown in Fig.~\ref{fig:potato_test}.}
+The SSIM of ground-truth (ideal reconstruction) is 1, and these are computed within the red RoI of the test image shown in Fig.~\ref{fig:potato_test}.}
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|}
@@
 \label{Sec:okra_spatially_varying}
-One of the slices from the reconstructed volumes 
+The test volume was reconstructed from a partial set of
+45 projections, i.e., $10\%$ of the projection views from which ground
+truth was reconstructed. One of the slices from the reconstructed volumes 
 is shown in Fig.~\ref{fig:okra_3D_results}. The red and green 3D
@@
 \begin{table}[!h]
+  \centering
   \caption{SSIM of 3D RoI of reconstructed okra volumes from various
     methods. Each RoI spans 7 consecutive slices where the test is
-    different from all of the previously scanned objects.}
+    different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
 \hline &
-\textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} &
 \textbf{FDK} & \textbf{l1-ls} &
@@
 \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior +
-    l1-ls\end{tabular}} \\ \hline \textbf{red RoI} & 1 (ideal) & 0.74
-& 0.84 & 0.85 & \textcolor{red}{0.88} \\ \hline \textbf{green RoI} & 1
-(ideal) & 0.81 & 0.82 & 0.77 & \textcolor{red}{0.83}
+    l1-ls\end{tabular}} \\ \hline \textbf{red RoI} & 0.74
+& 0.84 & 0.85 & \textcolor{red}{0.88} \\ \hline \textbf{green RoI} & 0.81 & 0.82 & 0.77 & \textcolor{red}{0.83}
 \\ \hline
@@
 \begin{table}[]
+  \centering
 \caption{SSIM of 3D RoI of reconstructed sprouts volumes from various methods. The RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.}
@@
 \hline
-                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{red RoI}   & 1 (ideal)                     & 0.85        & 0.86       & 0.83                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
+                   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior + l1-ls\end{tabular}} \\ \hline
+\textbf{red RoI}   & 0.85        & 0.86       & 0.83                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
 \end{tabular}
@@
 \end{table}
- The selected 3D ground truth of
+The test volume was reconstructed from partial set of 45
+projections, i.e., $2.5\%$ of the projection views from which ground
+truth was reconstructed. The selected 3D ground truth of
 template volumes, test volume, as well as the 3D reconstructions are
@@
 \label{sec:discussion}
-In this section, we discuss the following: a) tuning of the parameters used, b) a realistic imaging and reconstruction protocol for longitudinal studies, and c) results on homogenous dataset.
+In this section, we discuss the following:  a) a realistic imaging and reconstruction protocol for longitudinal studies, b) results on homogenous dataset, and (c) tuning of the parameters used.
 %The presented uniform prior-based algorithm is suited to applications
@@
 %-----------------------------------------
-\begin{table}[!h]
-  \centering
-\caption{Computation time for reconstruction of volumes using various methods.
-The configuration of the system used was x86\_64 architecture, 62GB RAM, 12-core AMD 3.8GHz processor, with Nvidia GeForce RTX 2080 Ti GPU.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-\hline
-   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}c@{}}Spatially-\\Varying\\ prior \\+ l1-ls\end{tabular}} \\\hline
-%\textbf{\begin{tabular}[c]{@{}c@{}}Potato\\size:(150,150,100)\\45 views\end{tabular}}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338$\times$338$\times$123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130$\times$130$\times$130)\\xx views\end{tabular}}  & 6 sec. & 3 hrs. & 60 min. &  17 hrs.\\ \hline
-\end{tabular}
-\label{table:Computation_time_3D}
-\end{table}
-\subsection{Computation time}
-The computation time for each of the methods is presented in Table~\ref{table:Computation_time_3D}.
-For spatially-varying prior, most of the computation time is used in the generation of low-quality eigen-space by reconstructing  each of the templates using CS and FDK.
-This process cannot be performed offline as it involves applying the same imaging geometry used for scanning the test.
-We had performed these reconstructions sequentially.
-Ideally, these reconstructions must be performed parallely on different machines to significantly reduce the computation time.
 
@@
 \label{Sec:potato}
-While the design of the weights map in the proposed algorithm aims to combine the best of information from both the current measurements and the prior, we found FDK to be preferable when the test object has a simple, homogeneous structure without intricate details.
-One such dataset is the Potato dataset.\\
-The test volume was reconstructed using measurements from 45 projection views, i.e., $5\%$ of the projection views from which ground truth was reconstructed. The selected 3D
-ground truth of template volumes, test volume, as well as the 3D reconstructions are shown in the supplementary material~\cite{supp_paper}.
-Fig.~\ref{fig:potato_3D_results_A} shows a slice from the reconstructed 3D volume.
-We observe that our method reconstructs new structures while simultaneously reducing streak artefacts.\\ %The new regions detected by different reconstruction methods are shown in Fig.~\ref{fig:weights_map_2Dpotato}.
-The lower intensities denote new regions which were assigned lower weights.
-This ensures that the new regions are reconstructed using projection measurements alone, avoiding erroneous influence of the prior.
-Table~\ref{table:potato_ssim} shows the Structure Similarity Index (SSIM) of the reconstructed new regions using various methods.
-We observe that the FDK performs very well for smaller RoI; as the RoIs get bigger, the FDK reconstructions have poor SSIM due to strong subsampling artefacts.
-In contrast, the results from l1-ls and our method progressively improve when compared to FDK as the RoIs get bigger.
-Hence, in practice, one may choose FDK for the case of simple, homogeneous dataset with smaller RoI,  and prefer spatially-varying prior-based reconstruction when the dataset is complex and RoIs are larger.
-
 %--------potato reconstruction--------------------------------------------------
@@
 
-\subsection{Effect of hyper-parameters}
+While the design of the weights map in the proposed algorithm aims to
+combine the best of information from both the current measurements and
+the prior, we found FDK to be preferable when the test object has a
+simple, homogeneous structure without intricate details. One such
+dataset is the Potato dataset (described in
+Sec.~\ref{sec:datasets}). The test volume was reconstructed using
+measurements from 45 projection views, i.e., $5\%$ of the projection
+views from which ground truth was reconstructed. The selected 3D
+ground truth of template volumes, test volume, as well as the 3D
+reconstructions are shown in the supplementary
+material~\cite{supp_paper}. Fig.~\ref{fig:potato_3D_results_A} shows a
+slice from the reconstructed 3D volume. We observe that our method
+reconstructs new structures while simultaneously reducing streak
+artefacts.Table~\ref{table:potato_ssim} shows the Structure Similarity
+Index (SSIM) of the reconstructed new regions using various
+methods. We observe that FDK performs very well for smaller RoI;
+as the RoIs get bigger, the FDK reconstructions have poor SSIM due to
+strong subsampling artefacts. In contrast, the results from l1-ls and
+our method progressively improve when compared to FDK as the RoIs get
+bigger. In practice, the RoI is not known in advance and hence, one
+may choose FDK for the case of simple, homogeneous dataset with
+smaller RoI, and prefer spatially-varying prior-based reconstruction
+when the dataset is complex and RoIs are larger.
+
+%The new regions detected by different reconstruction methods are shown in Fig.~\ref{fig:weights_map_2Dpotato}.
+The lower intensities denote new regions which were assigned lower weights.
+This ensures that the new regions are reconstructed using projection measurements alone, avoiding erroneous influence of the prior.
+
+\subsection{Tuning of parameters}
 \label{subsec:k}
-The parameters $\lambda_1$ and $\lambda_2$ must be chosen empirically
-or by cross-validation by treating one of the previously scanned
-objects as test. In our experiments, we had fixed $\lambda_1$ to be 1
-and found that this value is nearly data-independent. The value of
+ $\lambda_1$ was tuned to maximize
+SSIM of the whole reconstructed test volume for l1-ls reconstruction
+of each dataset. This value was retained for uniform and
+spatially-varying prior-based reconstruction as well. The value of
 $\lambda_2$ largely depends on the amount of artefacts we aim to

### 2020-07-25 paper/response.tex
Almost ready for submission

@@
 \usepackage{subcaption}
+\usepackage{geometry}
 \usepackage[colorlinks=true]{hyperref}
-\title{Author Response to Reviewers for the paper `Eliminating prior-bias from sparse-projection tomographic reconstructions'}
+\title{Author Response to Reviewers for the paper `Eliminating object-prior bias from sparse-projection tomographic reconstructions'}
 \begin{document}
@@
 
-\textbf{Organization of this response:} We would like to thank the editor and all three reviewers for their insightful comments.
+\textbf{Organization of this response:} We thank the associate editor (AE) and all three reviewers for their insightful comments.
 Here, we are including our response to each reviewer, and pointers to modifications (suggested by the reviewers and the AE) in our revised manuscript.
@@
 We have organized this document in three parts (a) Response to comments from AE (Section A), and (b) Response to significant points made by all the other reviewers (c) Detailed  responses to the comments of each of the reviewers.
+To the best of our knowledge, we have painstakingly addressed each and every point of all the reviewers, and responded adequately.
+We request the reader's time to go through our responses.
 
-To the best of our knowledge, we have painstakingly addressed each and every point of all the reviewers, and responded adequately.  We request the reader's time to go through our responses.
-
-In some cases, we provide results in this document to justify our stand, but these same results are not in the updated manuscript, primarily because these results do not enhance the claims in our paper .
+In some cases, we provide results in this document to justify our stand, but these same results are not in the updated manuscript, primarily because these results do not enhance the claims in our paper.
 In most other cases, we have shifted such results to supplementary material and have referred to them in this document.
 
-For ease of understanding, since the current version of the manuscript is considerably reorganized, in this document, we have used the (longer) term ``Figure x'' to refer to a figure in the old version and ``Fig.
-x'' to refer to the related figure in the current version.
-Similarly, we have used the term ``Equation y'' to refer to an equation in the old version, and ``Eq.
-y'' to refer to an equation in the new version, and ``Table y'' to refer to a table in the old version and ``Tab.
-y'' to refer to a table in the new version.
+In order to better differentiate between object-prior and sparsity-prior, we have now changed the title of the paper from `Eliminating prior-bias from sparse-projection tomographic reconstructions' to `Eliminating \textbf{object} prior-bias from sparse-projection tomographic reconstructions'.
+This is also in accordance with comments from reviewer R1.
 
-\section{Associate Editor comments}
-(We have numbered the original review comments as AE-Cx, and italicized for clarity)
+For ease of understanding, since the current version of the (revised) manuscript is considerably reorganized, in this document, we have used the (longer) terms ``Figure x'',``Equation y'' and ``Table z''  to refer to a figure, equation and table respectively in the old version, and the (shorter) terms ``Fig.~x'', ``Eq.~y'' and ``Tab.~z'' to refer to the corresponding figure, equation and table in the current version.
 
-Two of the reviewers have raised some serious concerns about the paper, including one reviewer who opines that this work is not suited for publication in the transactions in its current form.
-While these concerns are sufficiently serious to merit a negative decision, I have decided to give the authors an opportunity to revise the manuscript so that they may address the constructive comments of the reviewers carefully and thoroughly followed by another round of review to assess the manuscript.
+\section{Comments from AE}
+
+(We have numbered the original review comments as AE-Cx, and italicized for clarity.)\\
+
 In addition to the reviewer specific comments, please pay specific attention to the following:\\
@@
 
-\textbf{Response:} We have now re-written the contributions section (Sec.3 of the main paper), that highlights the novelty of our work.  
+\textbf{Response:} We have now re-written the contributions section (Sec.~3 of the main paper), that highlights the novelty of our work.  
 As a response to the comparisons required,  in many cases, our methods are incomparable to previous algorithms because of the nature of the longitudinal study  We discuss this in the related work section.
@@
 We had also compared (Fig.8) our method with many other iterative methods such as (ART, SART and SIRT) -- this set of comparisons was buried in a footnote, and perhaps not easily visible.
-In addition to these, we now have included Table 3 to show a quantitative comparison of SSIM values of the reconstruction by various methods shown in Fig.8.
+In addition to these, we have now included (earlier absent) Table 3 to show a quantitative comparison of SSIM values of the reconstruction by various methods shown in Fig.~8.
 We also discuss compressed sensing (see AE-C3) results.
@@
 This reference is now mentioned in our related work; although this paper is not directly applicable in longitudinal studies where object-priors `are' available, there is a reference in this paper to another paper which does make use of object-prior.
-We show how our work is superior in our response to R3 below (we include this in the supplementary material~\cite{supp_paper}).
+We show how our work is superior in our response to R3 below (we include this in Sec.~4 of the supplementary material~\cite{supp_paper}).
 \\
 
-\textcolor{blue}{\textbf{AE-C3.}\textit{Discuss the compressed sensing methods used since there are several works on model-based iterative reconstruction/regularized inversion/CS type methods for CT.}}
+\textcolor{blue}{\textbf{AE-C3.}\textit{ Discuss the compressed sensing methods used since there are several works on model-based iterative reconstruction/regularized inversion/CS type methods for CT.}}
 
@@
 (Figure 10-c in the original document) while results in all the other experiments are acceptable to prove the point.
-For instance R2 says ``I have one main question concerning Table 1, where I notice FDK gives for the ROI much better SSIM value than the variants of the proposed method.''
-Of course, we never intended to *not* mention this, which is why it was picked up very easily by all the reviewers, and in real life situations, it is unreasonable to expect that the ROI of detailed changes is known in advance.
+For instance R2 says \textit{``I have one main question concerning Table 1, where I notice FDK gives for the ROI much better SSIM value than the variants of the proposed method.'' }
+Of course, we never intended to \textit{not} mention this, which is why it was picked up very easily by all the reviewers, and in real life situations, it is unreasonable to expect that the ROI of detailed changes is known in advance.
 
-In response, we first note that our updated results of comparison for this dataset (after the tuning suggested by R1) *now* results in a favourable result (Table 3).
+In response, we first note that our updated results of comparison for this dataset (after the tuning suggested by R1) \textit{now} results in a favourable result (Table 3).
 That said, we agree that the FDK reconstructions can be superior, as evidenced for this particular dataset alone -- presumably when the region of interest is known a-priori (which is not always the case).
-We have devoted a separate section in the `Discussion' for this particular concern: Tab.8 better explains why our method is suitable, and Fig.
-19(e) the more pleasing visual result.
-\item R1 and R3 also raise another significant point:  What happens if we have only the object prior term and ignore the sparsity prior?.
+We have devoted a separate section in the `Discussion' for this particular concern: Tab.~7 better explains why our method is suitable, and Fig.~19(e) the more pleasing visual result.
+\item R1 and R3 also raise another significant point:  What happens if we have only the object prior term and ignore the sparsity prior?
 This indeed is relevant.
@@
 If the object-priors were of poor quality, or if the number of views (still sub-Nyquist) were to be increased from our very few views, then the sparsity term will start playing a part.
-\item R3 remarks that `it's simply not true' about some of the overarching broad statements which we had claimed in our earlier submission (for example, ``in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections simulated from 3D volumes'').
+\item R3 remarks that \textit{`it's simply not true'} about some of the overarching broad statements which we had claimed in our earlier submission (for example, ``in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections simulated from 3D volumes'').
 In our current version, we have now either given better context to such statements or have retracted our misunderstandings with the wisdom in R3's remarks.
@@
 
-\section{ Detailed response to individual review comments}
+\section{ Detailed responses to individual reviewers}
 
 \subsection{Response to Reviewer 1}
-There are some concerns associated with the compressive sensing (CS) method, the explanation for weight selection, and the clarity of results. Some of the major issues are described below.
+There are some concerns associated with the compressive sensing (CS) method, the explanation for weight selection, and the clarity of results. Some of the major issues are described below. \\
 
-\textcolor{blue}{\textbf{R1-C1:}\textit{In Fig.
+\textcolor{blue}{\textbf{R1-C1.}\textit{ In Fig.
 4, the caption says CS and no prior.
@@
 
-\textcolor{blue}{\textbf{R1-C2:}\textit{$\lambda_1$ seems to decide the strength of the CS prior.
+\textcolor{blue}{\textbf{R1-C2.}\textit{ $\lambda_1$ seems to decide the strength of the CS prior.
 However, in section V (B), you mention that $\lambda_1$ is always chosen to be one.
@@
 
-\textcolor{blue}{\textbf{R1-C3:}\textit{ In CS, since you use cross-validation on a test image to select $\lambda_1$, it is necessary to tune this parameter until you reach a desired SSIM or root-mean-squared-error (RMSE).
+\textcolor{blue}{\textbf{R1-C3.}\textit{ In CS, since you use cross-validation on a test image to select $\lambda_1$, it is necessary to tune this parameter until you reach a desired SSIM or root-mean-squared-error (RMSE).
 With CS priors, I would expect increasing $\lambda_1$ to also lead to smoother results.}}
@@
 
-\textcolor{blue}{\textbf{R1-C4:}\textit{ What is the sparsity basis for CS prior in equation (1)? }}
+\textcolor{blue}{\textbf{R1-C4.}\textit{ What is the sparsity basis for CS prior in equation (1)? }}
 
@@
 
-\textcolor{blue}{\textbf{R1-C5:} \textit{Why is a CS prior necessary when you have the selective/unselective prior?
+\textcolor{blue}{\textbf{R1-C5.} \textit{ Why is a CS prior necessary when you have the selective/unselective prior?
 What happens if there is no CS prior and if we use only the selective/unselective priors?}}
@@
 
-\textcolor{blue}{\textbf{R1-C6:}\textit{Schematic 1 in section III (B) does not make sense. But, the explanation in section III (B) (2) is clear.}}
+\textcolor{blue}{\textbf{R1-C6.}\textit{ Schematic 1 in section III (B) does not make sense. But, the explanation in section III (B) (2) is clear.}}
 
@@
 
-\textcolor{blue}{\textbf{R1-C6(b):}\textit{found section III (B) (2) algorithm to compute weights map W very interesting.
+\textcolor{blue}{\textbf{R1-C6(b).}\textit{ found section III (B) (2) algorithm to compute weights map W very interesting.
 However, it is hard to understand what artifacts can be attributed to the system geometry and an algorithm.
@@
 \end{figure}
-
 In the Figs.~\ref{fig:weights_no_noise} and~\ref{fig:weights_with_noise}, notice how the weights map is different for each of the methods and how it is improved when it is computed using two or more methods.
 We observe similar benefits even in the presence of small quantities of noise as shown below.
+In the actual reconstruction of the images, the prior term is well represented and these effects are not immediately visible.
+However, with low quality priors the effects may be visible.
 
-In the actual reconstruction of the images, the prior term is well represented and these effects are not immediately visible.  However, with low quality priors the effects may be visible.
-
-\newpage
-\textbf{Case 1: No noise in projections:}
+%\textbf{Case 1: No noise in projections:}
 \begin{figure}[!h]
@@
      \end{subfigure}
-      \caption{Weights images by various methods while reconstructing the test in Fig.~\ref{fig:object-prior_test_potato_A1} from 12 views and no noise}
+      \caption{Weights images by various methods while reconstructing the test in Fig.~\ref{fig:object-prior_test_potato_A1} from 12 views and no noise in projections.}
 \label{fig:weights_no_noise}
@@
 
-\textbf{Case 2: Noise with 0 mean and SD = 1$\%$ of the mean of the measurements}
+%\textbf{Case 2: Noise with 0 mean and SD = 1$\%$ of the mean of the measurements}
 \begin{figure}[!h]
@@
      \end{subfigure}
-      \caption{Weights images by various methods while reconstructing the test in Fig.~\ref{fig:object-prior_test_potato_A1} from 12 views in the presence of noise.}
+      \caption{Weights images by various methods while reconstructing the test in Fig.~\ref{fig:object-prior_test_potato_A1} from 12 views in the presence of Gaussian noise (with 0 mean and SD = 1$\%$ of the mean of the measurements) in projections.}
 \label{fig:weights_with_noise}
 \end{figure}
-
-\textcolor{blue}{\textbf{R1-C6:}\textit{ In results, the images are simply too big relative to the ROIs, which are tiny.
+\textcolor{blue}{\textbf{R1-C6(c).}\textit{ In results, the images are simply too big relative to the ROIs, which are tiny.
 It is very difficult to see the changes within the ROI.
@@
 
-\textcolor{blue}{\textbf{R1-C7:}\textit{ Table I, II, and III present SSIM comparison.
+\textcolor{blue}{\textbf{R1-C7.}\textit{ Table I, II, and III present SSIM comparison.
 It will also be interesting to present a root mean squared error (RMSE) comparison.
@@
 
-\textcolor{blue}{\textbf{R1-C8:}\textit{ For instance, in Fig.
+\textcolor{blue}{\textbf{R1-C8.}\textit{ For instance, in Fig.
 10 (e), the region within the ROI seems to be brighter than the surrounding holes.
@@
 
-\textcolor{blue}{\textbf{R1-C9:}\textit{Some relatively minor issues are below- Page 3, line 7, section II: Consider defining longitudinal study.}}
+\textcolor{blue}{\textbf{R1-C9.}\textit{ Some relatively minor issues are below- Page 3, line 7, section II: Consider defining longitudinal study.}}
 
@@
 
-\textcolor{blue}{\textbf{R1-C10:} \textit{Images in Fig. 3 seem to be clipped in the lower left along a circular arc! Are all reconstructions within a circular outer region of interest?}}
+\textcolor{blue}{\textbf{R1-C10.} \textit{ Images in Fig. 3 seem to be clipped in the lower left along a circular arc! Are all reconstructions within a circular outer region of interest?}}
 
@@
 
-\textcolor{blue}{\textbf{R1-C11:}\textit{In Fig. 8, what is (g) combined? Also, there is no (h) but is mentioned in caption.}}
+\textcolor{blue}{\textbf{R1-C11.}\textit{ In Fig. 8, what is (g) combined? Also, there is no (h) but is mentioned in caption.}}
 
@@
 
-\textcolor{blue}{\textbf{R1-C12:}\textit{ Try to mention the actual number of views/projections instead as a percentage.
+\textcolor{blue}{\textbf{R1-C12.}\textit{ Try to mention the actual number of views/projections instead as a percentage.
 The percentage only makes sense when you are comparing against Nyquist limit for views.
-For instance, the total number of views for Potato dataset is 900, which is simply too many for a reconstruction size of 150x150.
+For instance, the total number of views for Potato dataset is 900, which is simply too many for a reconstruction size of 150$\times$150.
 For such a small reconstruction, 900 is not a ``typical'' number views.
@@
 
-  \textbf{Response:} Just to clarify, as mentioned in the paper, the 900 views for the potato dataset was used to reconstruct the ground-truth 3D volume of size 150 x 150 x 100, and not a 2D slice of size 150 x 150.
-Each of the projection images was of size 150 x 150.
+  \textbf{Response:} Just to clarify, as mentioned in the paper, the 900 views for the potato dataset was used to reconstruct the ground-truth 3D volume of size 150$\times$150$\times$100, and not a 2D slice of size 150$\times$150.
+Each of the projection images was of size 150$\times$150.
+Here we explain our choice of views.
 
@@
 Consider a circle of radius R=1 that envelops an unknown 2D region X.
-Then, the circumference of the circle in pixel units will be $2\pi R_p$, where$ R_p$ represents the radius in pixel units, i.e., the number of image-pixels that fit within the radius of the circle.
+Then, the circumference of the circle in pixel units will be $2\pi R_p$, where $R_p$ represents the radius in pixel units, i.e., the number of image-pixels that fit within the radius of the circle.
 Now, let us assume that we want to pass rays around a half of a circle (due to symmetry).
-We can reasonably assume that a set of $(2*\pi*R_p)/2$ angles will be ``sufficient'' to faithfully reconstruct X.
+We can reasonably assume that a set of $(2\pi R_p)/2$ angles will be ``sufficient'' to faithfully reconstruct X.
 \begin{itemize}
-\item Given size of the 2D object $= 200 x 200$, the length (in pixel units) of the diagonal of this image $= 200*\sqrt(2)$, and this is twice the radius of the enclosing circle.
+\item Given size of the 2D object, 200$\times$200, the length (in pixel units) of the diagonal of this image $= 200\sqrt 2$, and this is twice the radius of the enclosing circle.
 \item Since our imaging method is circular cone beam projection, we assume a circle to tightly bound the object.
 \item $R_p = 282.84/2 = 141.4$
-\item No. of views $= 2*\pi*R_p = 888$ views
+\item No. of views $= 2\pi R_p = 888$ views
 \end{itemize}
@@
 \begin{itemize}
-\item Given size of the object scanned $= 150 x 150 x 100$, the length of the space diagonal of this cuboid = $\sqrt{(100^2 + 100^2 + 150^2)}$
+\item Given size of the object scanned, 150$\times$150$\times$100, the length of the space diagonal of this cuboid = $\sqrt{(100^2 + 100^2 + 150^2)}$
 \item Since our imaging method is circular cone beam projection, we assume a sphere tightly bounding the object.
 \item The radius of this sphere in voxel units ($R_v$) will be $\sqrt{(100^2 + 100^2 + 150^2)}/2 = 103$
-and, surface area of the sphere $= 4*\pi*(R_v)^2 = 133320$.
+and, surface area of the sphere $= 4\pi (R_v)^2 = 133320$.
 \item If we want to pass at least one ray for every surface voxel of this sphere, we will need 133320/2 (since sphere is symmetrical, and ray at 30 deg will pass through same voxels as ray at 30 +180 deg) = 66658 views.
 \end{itemize}
-Hence our choice of 900 views for reconstruction of the ground-truth is not exceedingly large. It just happens to be sufficient due to the homogenous structure of the interior of the object (potato).
+Hence our choice of 900 views for reconstruction of the ground-truth is not exceedingly large. It just happens to be sufficient due to the homogeneous structure of the interior of the object (potato).
 
@@
 
-\textcolor{blue}{\textbf{R1-C13:}\textit{ Hard to notice the features within the ROI in Fig. 15. It may help to present images that zoom into the ROI.}}
+\textcolor{blue}{\textbf{R1-C13.}\textit{ Hard to notice the features within the ROI in Fig. 15. It may help to present images that zoom into the ROI.}}
 
-\textbf{Response:} The zoomed-in RoI is now shown in Fig. 16. \\
+\textbf{Response:} The zoomed-in RoI is now shown in Fig. 17. \\
 
-\textcolor{blue}{\textbf{R1-C14:}\textit{ In section V (B), how was the cross-validation or empirical selection of $\lambda_1$ and $\lambda_2$ done?
+\textcolor{blue}{\textbf{R1-C14.}\textit{ In section V (B), how was the cross-validation or empirical selection of $\lambda_1$ and $\lambda_2$ done?
 Did you use SSIM as a comparison metric?
@@
 
-\textcolor{blue}{\textbf{R1-C15:}\textit{ You are allowed to submit documents or media as supplementary material.
+\textcolor{blue}{\textbf{R1-C15.}\textit{ You are allowed to submit documents or media as supplementary material.
 Instead of posting them on a dropbox, you could submit them as supplementary material to the journal.
@@
 
-\textcolor{blue}{\textbf{R1-C16:}\textit{ To save space and if you feel comfortable, you could move the section III (A) (1) on patch based techniques to supplementary since it is not a contribution of your paper.}}
+\textcolor{blue}{\textbf{R1-C16.}\textit{ To save space and if you feel comfortable, you could move the section III (A) (1) on patch based techniques to supplementary since it is not a contribution of your paper.}}
 
@@
 
-\section{Response to Reviewer 2}
+\subsection{Response to Reviewer 2}
 (We have numbered these comments as \textbf{R2-Cx}, and italicized for clarity)\\
@@
 
-\textbf{Response:} We hypothesize that because the volume of this dataset (potato) is very homogenous (without intricate  structures), the test measurements capture sufficient information about the new regions even with $5\%$ views and hence FDK performs very well in the exact region of interest (shown as red RoI in Fig.
+\textbf{Response:} We hypothesize that because the volume of this dataset (potato) is very homogeneous (without intricate  structures), the test measurements capture sufficient information about the new regions even with $5\%$ views and hence FDK performs very well in the exact region of interest (shown as red RoI in Fig.
 19(a)).
@@
 19a), the prior-based methods perform better than FDK (please refer Table 8) in that they minimize the sub-sampling artefacts.
-We have now discussed this in Section 8.
-B - ``Reconstruction of homogenous data''.
-Had the new region been embedded within an intricate background (like the sprouts and okra), its reconstruction does give rise to artefacts as seen in Figs.13-b and 15-b.
+We have now discussed this in Sec.~10(B) - ``Reconstruction of homogeneous data''.
+Had the new region been embedded within an intricate background (like the sprouts and okra), its reconstruction does give rise to artefacts as seen in Figs.13-b and 15-b. \\
 
-Beside this, I only have minor comments:\\
+\textcolor{blue}{\textit{Beside this, I only have minor comments:}}
 
-\textcolor{blue}{\textbf{R2-C2}\textit{. P1, L49, right panel: "a" should not be typeset in italic.}}
+\textbf{Response:}\textbf{ Here, we wish to convey that we have incorporated all of these minor corrections.
+However, many of them may not appear as is, because we have heavily rewritten and re-organized many parts of the paper based on  suggestions from all reviewers.}\\
 
-\textbf{Response:} The italicized `a' here is used to emphasize the selection of `any one' particular template amongst the many available ones.
-So, we retain the typeset on ``a'' and for greater clarity, italicize the word `particular' as well .
+\textcolor{blue}{\textbf{R2-C2.}\textit{ P1, L49, right panel: "a" should not be typeset in italic.}}
+
+\textbf{Response:} The italicized `a' here was earlier used to emphasize the selection of `any one' particular template amongst the many available ones.
+So, we had used a typeset on ``a'' for greater clarity.
+In the current version however, this statement is not present as is because we have rewritten the entire section now.\\%, italicize the word `particular' as well .
 The statement now reads:
-``there is the key issue of choice of a particular previously scanned object among the many previously acquired scans.''\\
+%``there is the key issue of choice of a particular previously scanned object among the many previously acquired scans.''\\
 
-\textcolor{blue}{\textbf{R2-C3.}\textit{P2, L31, left panel: The subtitle should be typeset in bold.}}
+\textcolor{blue}{\textbf{R2-C3.}\textit{ P2, L31, left panel: The subtitle should be typeset in bold.}}
 
@@
 
-\textcolor{blue}{\textbf{R2-C4. }\textit{P2, L50, left panel: ``reconstruction-'' should be corrected to ``reconstruction -''}}
+\textcolor{blue}{\textbf{R2-C4.}\textit{ P2, L50, left panel: ``reconstruction-'' should be corrected to ``reconstruction -''}}
 
@@
 
-\textcolor{blue}{\textbf{R2-C5.}\textit{P5, L10, left panel: ``Eq 6'' should be corrected to ``Eq. 6'' (same in P6, L54, right panel}}
+\textcolor{blue}{\textbf{R2-C5.}\textit{ P5, L10, left panel: ``Eq 6'' should be corrected to ``Eq. 6'' (same in P6, L54, right panel}}
 
@@
 
- \textbf{Response:} As per the conventional use, ``i.e'' has now been replaced by ``i.e.,'' in all occurrences in the paper.\\
+ \textbf{Response:} As per the conventional use, ``i.e'' has now been replaced by ``i.e.'' in all occurrences in the paper.\\
 
-\textcolor{blue}{\textbf{R2-C7. }\textit{P6, L42, left panel: ``Eqn. 8'' should be corrected ``Eq. 8'' (same in P7, L19, left panel}}
+\textcolor{blue}{\textbf{R2-C7.}\textit{ P6, L42, left panel: ``Eqn. 8'' should be corrected ``Eq. 8'' (same in P7, L19, left panel}}
 
@@
 
- \textcolor{blue}{\textbf{R2-C10.}\textit{ P7, L3, and L7: ``proposed methods'' <--> "proposed method". Choose one.}}
+ \textcolor{blue}{\textbf{R2-C10.}\textit{ P7, L3, and L7: ``proposed methods'' $<-->$ "proposed method". Choose one.}}
 
@@
 
-\textcolor{blue}{\textbf{R2-C18.}\textit{P9, L34, right panel: ``[38](FDK'' space is missing}}
+\textcolor{blue}{\textbf{R2-C18.}\textit{ P9, L34, right panel: ``[38](FDK'' space is missing}}
 
@@
 
- \textcolor{blue}{\textbf{R2-C19.}\textit{P9, L36, right panel: ``in-dept'' should be corrected to ``in-depth'', ``in'' should be corrected to ``is''}}
+ \textcolor{blue}{\textbf{R2-C19.}\textit{ P9, L36, right panel: ``in-dept'' should be corrected to ``in-depth'', ``in'' should be corrected to ``is''}}
 
@@
 
-\textbf{ Response:} Accepted. This has been corrected to `weights-maps' in all occurrences in the paper.\\
+\textbf{Response:} Accepted. This has been corrected to `weights-maps' in all occurrences in the paper.\\
 
@@
 
-\textbf{ Response:} Accepted. This has been corrected.
+\textbf{Response:} Accepted. This has been corrected.
 
-\section{Response to Reviewer 3}
+\subsection{Response to Reviewer 3}
 (We have numbered these comments as R3-Cx, and italicized for clarity)
@@
 
-\textcolor{blue}{\textbf{R3-C1:}\textit{ Most importantly, results are compared with only a single existing method that is specifically designed for low-angle tomography (compressed sensing), and the results of that method seem sub-optimal (at least, it does not match my experience with both applying such methods myself and published results of such methods).
+\textcolor{blue}{\textbf{R3-C1.}\textit{ Most importantly, results are compared with only a single existing method that is specifically designed for low-angle tomography (compressed sensing), and the results of that method seem sub-optimal (at least, it does not match my experience with both applying such methods myself and published results of such methods).
 }}
@@
 
-\textcolor{blue}{\textbf{R3-C2:}\textit{ Since no details are given about the method that is compared with (what function does in optimize?}}
+\textcolor{blue}{\textbf{R3-C2.}\textit{ Since no details are given about the method that is compared with (what function does in optimize?}}
 
@@
 
-\textcolor{blue}{\textbf{R3-C3:}\textit{ what were the parameters? how were these chosen?), the experimental results in the paper give very little information to the reader.}}
+\textcolor{blue}{\textbf{R3-C3.}\textit{ what were the parameters? how were these chosen?), the experimental results in the paper give very little information to the reader.}}
 
@@
 $\lambda_1$ was set equal to 1 in all datasets (as observed by R1, and line 53, page 9, column 2).
-THis was done by visual inspection for one of the dataset and used elsewhere as is.
+This was done by visual inspection for one of the dataset and used elsewhere as is.
 We had earlier mentioned that we are using DCT in Page 6 (right column, line 58).
@@
 Here below, we present the changes in the accuracies due to tuning of $\lambda_1$ in Tables~\ref{tab:sprouts_revised_ssim}, and~\ref{tab:okra_revised_ssim}.
-
-The new visual results and SSIM values are in Figs. 13, 15 and 19, and in Tables 4, 5 and 8.
+The new visual results and SSIM values are in Figs.
+13, 15 and 19, and in Tables 4, 5 and 8.
 
 \begin{table}[!h]
+  \centering
   \caption{Old and revised SSIM (within red RoI) for 3D sprouts dataset}
@@
 \textbf{Uniform prior} & 0.83 & 0.83 \\ \hline
-\textbf{Spatially varying prior} & 0.88 & 0.88 \\ \hline
+\textbf{Spatially varying prior} & \textcolor{red}{0.88} & \textcolor{red}{0.88} \\ \hline
 \end{tabular}
@@
 \begin{table}[!h]
+  \centering
   \caption{Old and revised SSIM (within red RoI) for 3D okra dataset}
@@
 \textbf{Uniform prior} & 0.85 & 0.85 \\ \hline
-\textbf{Spatially varying prior} & 0.88 & 0.88 \\ \hline
+\textbf{Spatially varying prior} & \textcolor{red}{0.88} & \textcolor{red}{0.88} \\ \hline
 \end{tabular}
@@
 
-\textcolor{blue}{\textbf{R3-C4:}\textit{ To address these issues, a large amount of changes would be required in the paper (not only in the experiments, but also throughout the paper, since the performance of compressed sensing methods is one of the main motivations of introducing a new approach).
+\textcolor{blue}{\textbf{R3-C4.}\textit{ To address these issues, a large amount of changes would be required in the paper (not only in the experiments, but also throughout the paper, since the performance of compressed sensing methods is one of the main motivations of introducing a new approach).
 Other issues are present in the paper as well (see below for more detailed comments).
@@
 In addition, here we wish to state that the performance of compressed sensing is not one of the main motivations of the paper.
-The use of uniform and spatially-varying object-priors in a longitudinal setting is the main contribution of this paper and these techniques are independent of the sparsity-prior (CS) being used, i.e., object-specific prior can be imposed even when $\lambda1$, the weight of sparsity prior, is set to $0$.
+The use of uniform and spatially-varying object-priors in a longitudinal setting is the main contribution of this paper and these techniques are independent of the sparsity-prior (CS) being used, i.e., object-specific prior can be imposed even when $\lambda_1$, the weight of sparsity prior, is set to $0$.
 The success of our method on a real-life dataset in a clinical setting is a testament to our methods.\\
@@
 
-\textcolor{blue}{\textbf{R3-C5:}\textit{ The comparisons with existing methods in the current manuscript are insufficient to support the conclusions made in the paper.
+\textcolor{blue}{\textbf{R3-C5.}\textit{ The comparisons with existing methods in the current manuscript are insufficient to support the conclusions made in the paper.
 My main concerns are: - The authors only compare with a single method specific to reconstructing tomographic images from a low number of projections (which they call compressed sensing).
@@
 
-\textcolor{blue}{\textbf{R3-C6:}\textit{ No details are given about the CS method that was compared with.
+\textcolor{blue}{\textbf{R3-C6.}\textit{ No details are given about the CS method that was compared with.
 What type of sparsity did the method assume?
@@
 
-\textcolor{blue}{\textbf{R3-C7:}\textit{ Based on my experience with reconstructing tomographic data from few projections, I would expect the CS results to look \_much\_ better than what is presented in the paper.
+\textcolor{blue}{\textbf{R3-C7.}\textit{ Based on my experience with reconstructing tomographic data from few projections, I would expect the CS results to look \_much\_ better than what is presented in the paper.
 As an example, in Fig 10, based on the results of the FDK algorithm, I would expect any reasonable iterative method with regularization (CS or otherwise) to produce fairly accurate results.
@@
 
-\textcolor{blue}{\textbf{R3-C8:}\textit{ Related to the previous point, in several results it seems that FDK actually gives the most `accurate' reconstruction for the object.
+\textcolor{blue}{\textbf{R3-C8.}\textit{ Related to the previous point, in several results it seems that FDK actually gives the most `accurate' reconstruction for the object.
 For example, in Fig 10 the shape of the leftmost void is changed by the proposed method, and in Fig 12 the shape of the seeds (?) is not well reconstructed by the proposed method.
@@
 
-\textcolor{blue}{\textbf{R3-C9:}\textit{There exist methods that are relevant to the current work, since they use a similar approach.
+\textcolor{blue}{\textbf{R3-C9.}\textit{ There exist methods that are relevant to the current work, since they use a similar approach.
 For example, ``Region-based iterative reconstruction of structurally changing objects in CT'' uses a similar approach in which image regions that change between scans are detected and reconstructed with a weaker `similarity' prior than other regions.
@@
 We have now discussed this in Sec.2 (`Related Work') of our paper.
-In addition, we have now performed a 2D reconstruction to compare our method with [3]. This has been discussed in our response to \textbf{R3-C2}.\\
+In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. This has been discussed in our response to \textbf{R3-C2}.\\
 
-\textcolor{blue}{\textbf{R3-C10:}\textit{ Related to the previous point, this type of data seems well suited for data-driven techniques (e.g.
+\textcolor{blue}{\textbf{R3-C10.}\textit{ Related to the previous point, this type of data seems well suited for data-driven techniques (e.g.
 deep learning) that have become very popular in recent years.
@@
 
-\textcolor{blue}{\textbf{R3-C11:}\textit{The discussion of hyperparameter sensitivity is not very detailed.
+\textcolor{blue}{\textbf{R3-C11.}\textit{ The discussion of hyperparameter sensitivity is not very detailed.
 It is important to show how reconstruction change when adjusting these paremeters (for example, what happens if $\lambda_1$ is set to 0?).
@@
 
-\textcolor{blue}{\textbf{R3-C12:}\textit{ A discussion about computational costs (time, memory) should be included in the paper.
+\textcolor{blue}{\textbf{R3-C12.}\textit{ A discussion about computational costs (time, memory) should be included in the paper.
 Since most of the shown results are for quite small images, I'm worried that the approach might not scale well to the large image sizes that are common in high-resolution tomography.
@@
 
-\textbf{Response:}While the reconstruction accuracy was measured in the (small) regions of new changes, all reconstructions were performed for the full object volume.
+\textbf{Response:} While the reconstruction accuracy was measured in
+the (small) regions of new changes, all reconstructions were performed
+for the full object volume. For spatially-varying prior, most of the
+computation time is used in the generation of low-quality eigen-space
+by reconstructing each of the templates using CS and FDK. This process
+cannot be performed offline as it involves applying the same imaging
+geometry used for scanning the test. However, these reconstructions
+are completely independent and can easily be performed in parallel to
+significantly reduce the computation time. Here below, we describe the
+time complexity of spatially-varying prior technique.  If
+\begin{itemize}
+\item $N =$ number of voxels of the volume
+\item $T =$ number of templates available, and
+\item $F =$ time taken for iterative l1-ls optimization,
+\end{itemize}
+then, the computational complexity is sum of the following
+\begin{itemize}
+\item $O(NT^2+T^3)$ for creating the eigenspace,
+\item $O(NT^2)$ for deriving the weights map, and
+\item time $F$  taken for iterative minimization
+\end{itemize}
+where $O(.)$ is the notation for `Big O' used in complexity analysis.\\
 
-\begin{table}[!h]
-  \centering
-\caption{Computation time for reconstruction of volumes using various methods.
-The configuration of the system used was x86\_64 architecture, 62GB RAM, 12-core AMD 3.8GHz processor, with Nvidia GeForce RTX 2080 Ti GPU.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-\hline
-   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}c@{}}Spatially-\\Varying\\ prior \\+ l1-ls\end{tabular}} \\\hline
-%\textbf{\begin{tabular}[c]{@{}c@{}}Potato\\size:(150,150,100)\\45 views\end{tabular}}  & 5 sec. & 8 min.  & 54 min. & 53 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Okra\\size:(338$\times$338$\times$123)\\45 views\end{tabular}} & 6 sec. & 8 min.  & 25 min. & 60 min. \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Sprouts\\size:(130$\times$130$\times$130)\\xx views\end{tabular}}  & 6 sec. & 3 hrs. & 60 min. &  17 hrs.\\ \hline
-\end{tabular}
-\label{table:Computation_time_3D}
-\end{table}
-
-The computation time for each of the methods is presented in Table~\ref{table:Computation_time_3D}.
-For spatially-varying prior, most of the computation time is used in the generation of low-quality eigen-space by reconstructing  each of the templates using CS and FDK.
-This process cannot be performed offline as it involves applying the same imaging geometry used for scanning the test.
-We had performed these reconstructions sequentially.
-Ideally, these reconstructions must be performed in parallel on different machines to significantly reduce the computation time.\\
-
-\textcolor{blue}{\textbf{R3-C13:}\textit{ How does measurement noise influence results?
+\textcolor{blue}{\textbf{R3-C13.}\textit{ How does measurement noise influence results?
 Typically, in low-dose settings, significant noise is present in tomographic data.
@@
 
-\textcolor{blue}{\textbf{R3-C14:}\textit{The paper includes several statements that are either false or not well supported.
+\textcolor{blue}{\textbf{R3-C14.}\textit{ The paper includes several statements that are either false or not well supported.
 Examples include:    - `Fig.
@@
 
-\textcolor{blue}{\textbf{R3-C15:}\textit{ `which is an important issue that has so far been overlooked in the literature on tomography' -- this is again very broad, and there are actually papers that do address this issue (see above).}}
+\textcolor{blue}{\textbf{R3-C15.}\textit{ `which is an important issue that has so far been overlooked in the literature on tomography' -- this is again very broad, and there are actually papers that do address this issue (see above).}}
 
@@
 
-\textcolor{blue}{\textbf{R3-C16:}\textit{ `which was shown [23] to be better when compared to dictionary-based priors.' -- better in which respect?
+\textcolor{blue}{\textbf{R3-C16.}\textit{ `which was shown [23] to be better when compared to dictionary-based priors.' -- better in which respect?
 Currently, this strong statement is only supported by a paper that is written by the same authors -- more papers should probably be included to support this.}}
@@
 
-\textcolor{blue}{\textbf{R3-C17:}\textit{ `convergence of this optimization is guaranteed by the monotone convergence theorem' -- I think a reference is useful here.}}
+\textcolor{blue}{\textbf{R3-C17.}\textit{ `convergence of this optimization is guaranteed by the monotone convergence theorem' -- I think a reference is useful here.}}
 
@@
 
-\textcolor{blue}{\textbf{R3-C18:}\textit{ `we emphasize that in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections simulated from 3D volumes'.
+\textcolor{blue}{\textbf{R3-C18.}\textit{ `we emphasize that in most of the literature on tomographic reconstruction, the results are shown on reconstruction from projections simulated from 3D volumes'.
 This is simply not true: there are \_many\_ papers on tomographic reconstruction that include comparisons using real (raw) data, especially outside the medical context.
@@
 
-\textcolor{blue}{\textbf{R3-C19:}\textit{ It is not really clear from the paper what the main contributions are compared with existing work.
+\textcolor{blue}{\textbf{R3-C19.}\textit{ It is not really clear from the paper what the main contributions are compared with existing work.
 I think this is mainly caused by the structure of the paper, which is not really clear for me.
@@
 \item uniform prior, 
-\item results: uniform prior (including comparison with results from FDK and l1-ls), 
-spatially-varying prior, 
-\item results: spatially varying prior (including comparison with results from FDK, l1-ls and uniform prior), 
+\item results of uniform prior (including comparison with results from FDK and l1-ls), 
+\item spatially-varying prior, 
+\item results of spatially-varying prior (including comparison with results from FDK, l1-ls and uniform prior), 
 \item discussions (to discuss parameter tuning and limitations of our work), and 
-  conclusions.
+  \item conclusions.
   \end{itemize}
-For greater clarity, we have now removed Schematic 1 from the paper; We have  ensured that the rest of the paper can be followed without it.
+For greater clarity, we have now removed Schematic 1 from the paper; We have  ensured that the rest of the paper can be followed without it.\\
 
-\textcolor{blue}{\textbf{R3-C20:}\textit{ The mathematical notation is not always clear: for example, the authors define `y = Rx' while later minimizing `||Rx-y||', which, given the mathematical definition, should always be zero.
+\textcolor{blue}{\textbf{R3-C20.}\textit{ The mathematical notation is not always clear: for example, the authors define `y = Rx' while later minimizing `$||Rx-y||$', which, given the mathematical definition, should always be zero.
 Of course, I understand what the authors mean here, but I think it is important to be clear with the mathematical description to avoid any confusion.}}
@@
 
-\textcolor{blue}{\textbf{R3-C21:}\textit{ It seems that the weight map approach proposed by the authors is novel in this context.
+\textcolor{blue}{\textbf{R3-C21.}\textit{ It seems that the weight map approach proposed by the authors is novel in this context.
 However, related methods exist that also try to predict the image regions where change is happening and improve reconstructions using this information.
@@
 We have now discussed this in Sec.2 (`Related Work') of our paper.
-In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. This has been discussed in our response to \textbf{R3-C2}.\\
+In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. This has been discussed in our response to R3-C2.\\
 

### 2020-07-25 paper/supplementary.tex
Almost ready for submission

@@
 \usepackage{subcaption}
+%\usepackage{geometry}
 \usepackage[colorlinks=true]{hyperref}
-\title{Supplemental material for `Eliminating prior-bias from sparse-projection
+\title{Supplemental material for `Eliminating object prior-bias from sparse-projection
 tomographic reconstructions'}
@@
 \maketitle
-This supplementary material consists of details of the optimization routine used in our method, links to view our 3D reconstructions and results of 2D reconstructions for different projection views.
+%This supplementary material consists of details of the optimization routine used in our method, links to view our 3D reconstructions and results of 2D reconstructions for different projection views.
 
@@
 \section{An alternate method to compute weights-map}
-The problem of recovering the unknown data $\boldsymbol{x}$ from its measurements falls under the broad category of inverse problems.
-In almost all such cases, the measurement model is known.
-However, a direct analytical inverse solution does not exist in most cases because of the enormous size of the matrix modelling the measurement process.
-The complexity is further increased when insufficient number of measurements are taken leading to an ill-posed problem.
-In such circumstances, iterative schemes are used to solve for $\boldsymbol{x}$ by minimizing a cost function.
+The value of $k$ (discussed in Sec.10(C) of the main paper) is typically dependent on the number of false positives the system can allow in exchange for the detection of more true positives (regions of new changes).
+It is this choice and not the particular type of dataset that affects the selection of $k$.
+In our work, the chosen $k$ corresponds to the one that gives minimal tolerance to false positives.\\
 
-A simple cost function $E_\text{model}$ would minimise any difference between the measurements of the data and the imaging model:
+However, in case one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using an alternate method described below.
+
+\begin{enumerate}
+\item For the purposes of training, treat one of the previously scanned images as test.
+\item Annotate the region of differences between the test and all of the previously scanned images based on domain knowledge.
+\item Compute the difference between the pilot reconstruction of the test and its projection onto the eigenspace. Let this spatial map be called `error map'.
+\item Train a Support Vector Machine (SVM) model to classify patches of this error-map image into one of the two categories: new changes present, new changes absent.
+\item Once the trained SVM model is obtained, it can be applied to generate binary weights-map for new test images in the same longitudinal study.
+\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, the prior and the pilot can be stitched by $\boldsymbol{R} = \boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
+Fig.~\ref{fig:okra_svm} shows results of this method on 2D okra dataset.
+
+  Alternatively, these binary weights can also be used in the optimization loop in Eq.~\ref{Eq:main} (corresponding to Eq.~6 in the main paper), although this approach has not been pursued here.
 
 \begin{equation}
-E_\text{model} = \lVert\boldsymbol{\Phi x- y}\rVert_2^2.
+%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
+%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
+J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W_b}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
+\label{Eq:main}
 \end{equation}
-where $\boldsymbol{y}$ denotes the acquired measurements of $\boldsymbol{x}$ under an imaging model $\boldsymbol{\Phi}$.
-In our 3D reconstructions, $\boldsymbol{\Phi}$ denotes cone-beam projection model.
-In the case of sparse measurements (measurements from significantly few projection views), some known information of the underlying unknown data is imposed in order to get its better estimate.
-The Compressive Sensing is one such method that exploits the fact that most naturally occurring data are sparse under some mathematical transform.
-The cost function is now given by
 
-\begin{equation}
-E_\text{CS} = \lVert\boldsymbol{\Phi x- y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
-\end{equation}
-Here $\boldsymbol{\theta}$ are the unknown sparse coefficients of $\boldsymbol{x}$.
-In order to further improve the reconstruction, we can use information available from the scans of similar volumes in the past.
-Such methods are known as `\emph{prior}-based methods'.
+\end{enumerate}
 
-For our reconstruction, the cost function $E$ includes a third term enforcing weighted similarity between the reconstructed volume and pre-computed prior.
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
 
-\begin{equation}
-  E(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\Phi x- y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{i}\boldsymbol{V_i}\alpha_i))\rVert_2^2
-\label{eq:weighted_prior}
-\end{equation}
-\newpage
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
 
-\textbf{Building the prior:}\\
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
 
-We now describe the method used to build the prior.
-We begin with, it is assumed that the test volume can be expressed as a compact linear combination of the principal components extracted from a set of similar volumes (called here as `object-prior').
-Hence, the prior is built using Principal Component Analysis (PCA), which has been a widely used technique to represent data in terms of its significant modes or directions of variation.
-\\
+        \caption{}
+     \end{subfigure}
+     \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
 
-First, a set of representative 3D volumes is chosen as object-prior.
-These volumes must represent a wide range in anatomy, in order to contribute to an eigenspace that can encompass a range of possible test slice anatomy.
-If these volumes are not aligned, then they must be first registered before computing the prior.
-The prior is built by computing the covariance matrix $C$ from the template set $\{Q_i\}$, as shown in Eq.~\ref{eq:PCA}, The space spanned by the eigenvectors $\boldsymbol{\{V_i\}}$ (eigenspace) of the covariance matrix is the global prior and is assumed to contain any test slice that is similar, but not necessarily identical to the object-prior.
-The covariance matrix is given by:
- \begin{equation}
-\begin{split}
-  C  & = \frac{1}{N-1}\sum_{i=1}^N(Q_i - \mu)(Q_i - \mu)^{T}\\
-\end{split}
-\label{eq:PCA}
-\end{equation}
-where $\mu$ denotes the mean of all previously scanned volumes $\{Q_i\}$ and $L$ denotes the number of previously scanned volumes chosen.
-The eigenvalue decomposition of $C$ will give $L$ orthogonal eigen vectors.
-We use all of the $L$ eigenvectors as a basis to represent the unknown test volume.
-\\
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
 
-\textbf{Minimizing the Cost function}\\
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
 
-We minimize the cost specified in Eqn.~\ref{eq:weighted_prior} by alternately solving for $\boldsymbol{\alpha}$ and $\boldsymbol{\theta}$
+        \caption{}
+    \end{subfigure}    
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}
 
-\begin{equation}
-E_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = ||\Phi\Psi\boldsymbol{\theta}- y||_2^2  + \lambda_1||\boldsymbol{\theta}||_1+\lambda_2||\Psi\boldsymbol{\theta} - (\mu + \sum_{i}V_i\alpha_i)||_2^2
-\label{Eq:primaryObj}
-\end{equation}
-\begin{equation}
-E_{\boldsymbol\theta}(\boldsymbol{\alpha}) = ||\Psi\boldsymbol{\theta} - (\mu + \sum_{i}V_i\alpha_i)||_2^2
-\label{Eq:alpha1}
-\end{equation}
-Eq.~\ref{Eq:alpha1} leads to the following closed form update for $\alpha$:
-\begin{equation}
-\boldsymbol{\alpha} = \boldsymbol{V}^T(\Psi\boldsymbol{\theta} - \mu)
-\label{Eq:alpha}
-\end{equation}
-An optimal value of $\lambda_2$ is empirically chosen \textit{a priori}, based on the reconstructions of one of the template slices.
+        \caption{}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
 
+        \caption{}
+     \end{subfigure}
+   % \begin{subfigure}[b]{0.19\linewidth}
+   %     \includegraphics[width=\textwidth]{images/low_dose_prior/svm_method/prior.png}
+
+    %    \caption{}
+    % \end{subfigure}
+     \caption[Selecting $k$]{Using an alternate approach to generate (binary) weights map.
+(a)-(c) the images used as object-prior, (d) the test (310$\times$310).
+Measurements along $60$ views were taken.
+(e) error-map showing new regions, (f) detected binary weights map showing regions of new changes, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions.
+} %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates,
+\label{fig:okra_svm}
+\end{figure}
+\clearpage
 %--------------------------------Links to videos-------------------------------------------------
@@
 \section{Links to view our 3D reconstructions}
-
-Please refer to the following videos to view the 3D datasets and reconstruction results referred in our paper:
+The 3D reconstructions, corresponding to the images shown in Figs.~14,~16 and 19 in the main paper, can be better visualized in the form of a video.
+Hence, please refer to the following videos to view the 3D datasets and reconstruction results:
 
 \begin{itemize}
-\item \textbf{Okra groundtruth:} \\ \url{https://www.dropbox.com/s/gn3fk3ev7s7tup0/GroundTruth.mp4?dl=0}\\
-	The first four images correspond to the four template volumes and the last (right-most) image corresponds to the test volume.
-\item \textbf{Okra 3D reconstruction results:} \\ \url{https://www.dropbox.com/s/o7vga1kjzcayjmt/Reconstruction.mp4?dl=0}\\
-       The order of images from left to right correspond to the test volume, FDK reconstruction, CS reconstruction, unselective prior + CS reconstruction, and our reconstruction. 
-\item \textbf{Potato groundtruth:} \\ \url{https://www.dropbox.com/s/whwu3th4ozr96k1/GroundTruth.mp4?dl=0}\\
-	The first three images correspond to the three template volumes and the last (right-most) image corresponds to the test volume.
-\item \textbf{Potato 3D reconstruction results:}\\  \url{https://www.dropbox.com/s/k41qg1kwrry9rwp/Reconstruction.mp4?dl=0}\\
-       The order of images from left to right correspond to the test volume, FDK reconstruction, CS reconstruction, unselective prior + CS reconstruction, and our reconstruction.
-\item \textbf{Sprouts groundtruth:} \\ \url{https://www.dropbox.com/s/0d7jbojscbx4ciz/GroundTruth.mp4?dl=0}\\
-	The first five images correspond to the five template volumes and the last (right-most) image corresponds to the test volume.
-\item \textbf{Sprouts 3D reconstruction results:}\\  \url{https://www.dropbox.com/s/o3jmsa4dwtd8a6l/Reconstruction.mp4?dl=0}\\
-       The order of images from left to right correspond to the test volume, FDK reconstruction, CS reconstruction, unselective prior + CS reconstruction, and our reconstruction.
+\item \textbf{Okra:} \\
 
+  \url{https://www.dropbox.com/sh/x3yjfzsc5633d1t/AAAaVOXvTbc06a2DomPO1kSna?dl=0}\\
+\item \textbf{Potato:} \\
+
+  \url{https://www.dropbox.com/sh/6mja5uh8fa2h0fc/AAA2h4VsLxAiXcEIhmTlM1xha?dl=0}\\
+\item \textbf{Sprouts:}\\
+
+  \url{https://www.dropbox.com/sh/qtgeyckvbxiaz3s/AADhR2zRUUN4qXSXraErcqSea?dl=0}\\
 \end{itemize}
@@
 %--------------------------BIG images: TMH results
-\section{Bigger images for reconstruction results shown in main paper}
+\section{Larger images for reconstruction results}
+All the images shown in the main paper are displayed in small size due to space constraints.
+This restricts visualization of the structural details within them.
+Therefore, we present each of those images in large size here in order to view their internal structures with better clarity.
 \subsection{Liver}
 %-------RFA2 moderate views
-\textbf{Goal: Observe details of new changes}
+%\textbf{Goal: Observe details of new changes}
 \begin{figure}[!h]
@@
 
-\textbf{Test image Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\textbf{Test image in Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in large size for better clarity.}\\
 \begin{figure}[!h]
@@
 \newpage
-\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}   is shown in large size for better clarity.}\\
 \begin{figure}[!h]
@@
 \newpage
-\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm} is shown in larger display here  again for better clarity.}\\
+\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in large size for better clarity.}\\
 \begin{figure}[!h]
@@
 \newpage
-\textbf{Test image of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\textbf{Test image of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in large size for better clarity.}\\
 \begin{figure}[!h]
@@
 \newpage
-\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
+\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in large size for better clarity.}\\
 \begin{figure}[!h]
@@
 \newpage
-\textbf{Test image of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\textbf{Test image of Figure~\ref{fig:okra_3D_results_biggerIm}   is shown in large size for better clarity.}
 \begin{figure}[!h]
@@
 
-\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in large size for better clarity.}
 \begin{figure}[!h]
@@
 
-\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
+\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}   is shown in large size for better clarity.}
 \begin{figure}[!h]
@@
 %----------------------------------Comparison with Literature------------------------
-\section{Comparison with literature: detecting new changes directly in the measurements}
+\section{Detecting new changes directly in the measurements}
+
 Sec.2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature.
@@
 
-When the number of views is large, the reconstruction using CS (l1-ls) is indeed good, as shown below in Fig~\ref{fig:cs_blurred_48_views}.
-For the CS reconstructions shown below, we have tuned the lambda1 values (Figs.~\ref{fig:ssim_rmse_48_views},~\ref{fig:ssim_rmse_24_views},~\ref{fig:ssim_rmse_12_views}) and selected the one with maximum SSIM.
+The l1-ls reconstructions shown in the main paper (for example, in Figs.~14(c),~16(c) and 19(c)), appear to be blurred.
+Here, we discuss the reason for this observation by reconstructing an image from varying number of views using l1-ls (Eq.1 in the main paper).\\
+
+When the number of views is large, the reconstruction using l1-ls is indeed good, as shown below in Fig~\ref{fig:cs_blurred_48_views}.
+For the reconstructions shown below, we have tuned the $\lambda_1$ values (Figs.~\ref{fig:ssim_rmse_48_views},~\ref{fig:ssim_rmse_24_views},~\ref{fig:ssim_rmse_12_views}) and selected the one with maximum SSIM.
 
@@
     %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of potato test slice (150$\times$150) from 48 views. The lambda1 for l1-ls reconstruction was chosen to be the optimal value of 0.4 here.} 
+     \caption{Reconstruction of potato test slice (150$\times$150) from 48 views. The $\lambda_1$ for l1-ls reconstruction was chosen to be the optimal value of 0.4 here.} 
 \label{fig:cs_blurred_48_views}
@@
 %\captionsetup{labelformat=empty}
-\caption{SSIM and RMSE for reconstructionn from 48 views for varying levels of $\lambda1$. The optimal value of 0.4 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_48_views}}
+\caption{SSIM and RMSE for reconstruction from 48 views for varying levels of $\lambda_1$. The optimal value of 0.4 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_48_views}}
 \label{fig:ssim_rmse_48_views}
@@
 
-However, when the number of views decreases, the reconstruction using CS (LASSO) is blurred, but with the benefit of suppressed artefacts that are otherwise present in FBP reconstruction.
+However, when the number of views decreases, the reconstruction using l1-ls is blurred, but with the benefit of suppressed artefacts that are otherwise present in FBP reconstruction.
 This is illustrated in Figs.~\ref{fig:cs_blurred_24_views} and~\ref{fig:cs_blurred_12_views}.
@@
     %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of potato test slice (150$\times$150) from 24 views. The lambda1 for l1-ls reconstruction was chosen to be the optimal value of 2 here.} 
+     \caption{Reconstruction of potato test slice (150$\times$150) from 24 views. The $\lambda_1$ for l1-ls reconstruction was chosen to be the optimal value of 2 here.} 
 \label{fig:cs_blurred_24_views}
@@
 %\captionsetup{labelformat=empty}
-\caption{SSIM and RMSE for reconstructionn from 24 views for varying levels of $\lambda1$. The optimal value of 2 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_24_views}}
+\caption{SSIM and RMSE for reconstruction from 24 views for varying levels of $\lambda_1$. The optimal value of 2 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_24_views}}
 \label{fig:ssim_rmse_24_views}
@@
     %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of potato test slice (150$\times$150) from 12 views. The lambda1 for l1-ls reconstruction was chosen to be the optimal value of 3 here.} 
+     \caption{Reconstruction of potato test slice (150$\times$150) from 12 views. The $\lambda_1$ for l1-ls reconstruction was chosen to be the optimal value of 3 here.} 
 \label{fig:cs_blurred_12_views}
@@
 \end{figure}
-As seen here, the reconstruction by CS (LASSO) is indeed blurred when the number of views is very less. The iterative reconstruction was run until convergence (epsilon = 0.001).
-The plots below show the SSIM and RMSE values for varying values of lambda1 for the CS (LASSO) reconstructions of the above test image.
+As seen here, the reconstruction by l1-ls is indeed blurred when the number of views is very less. The iterative reconstruction was run until convergence (epsilon = 0.001).
+%The plots below show the SSIM and RMSE values for varying values of lambda1 for the CS (LASSO) reconstructions of the above test image.
 
@@
 %\captionsetup{labelformat=empty}
-\caption{SSIM and RMSE for reconstructionn from 12 views for varying levels of $\lambda1$. The optimal value of 3 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_12_views}}
+\caption{SSIM and RMSE for reconstruction from 12 views for varying levels of $\lambda_1$. The optimal value of 3 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_12_views}}
 \label{fig:ssim_rmse_12_views}
@@
 \newpage
-%----------------------------Patch-based methods
-\section{\textbf{Patch-based techniques}}
-\label{sec:patch_based}
-Here we present a comparison~\cite{my_dicta_paper} of the performance of the aforementioned PCA-based global prior with a prior that is based on construction of patch-wise dictionaries.
-In both cases, the reconstruction routine is based on typical CS techniques.
-The well-known K-SVD algorithm \cite{Aharon2006} was chosen for construction of patch-based dictionaries.
-For this, patches were extracted from each of the template volumes, from which an overcomplete dictionary was obtained.
-The basic aim of the K-SVD algorithm (or any overcomplete dictionary learning technique) is the compact linear representation of all these patches using the dictionary columns.
-Let $\boldsymbol{D}$ denote the dictionary learned, $N_p$ the total number of patches, and $\boldsymbol{H_i}$ the operator to extract the $i^{\textrm{th}}$ patch from the intermediate reconstructed slice/volume.
-Then, once $\boldsymbol{D}$ is computed in an earlier `training phase', each new test slice (or test volume) can be reconstructed by optimizing a cost function such as the one below:
-\begin{multline}
-J_2(\boldsymbol{\theta},\{\boldsymbol{\alpha_i}\}_{i=1}^{N_p}) = \lVert\boldsymbol{\mathcal{R}\Upsilon\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \\ \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\lVert \boldsymbol{H_i\Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2 +\frac{\lambda_3}{ N_p}\sum_{i=1}^{N_p}\lVert\boldsymbol{\alpha_i}\rVert_1.
-\label{Eq:main_patchBased}
-\end{multline}
-The reconstruction proceeds in an alternating manner, first by minimization of Eq.~\ref{Eq:primaryObj_patchBased} and then by minimization of Eq.~\ref{Eq:alpha_patchBased}.
-For both these, the solver in~\cite{l1ls} is used.
-For the former case, the cost function reduces to:
-\begin{equation}
-J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) = \lVert \boldsymbol{\mathcal{R} \Upsilon \theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 + \frac{\lambda_2}{N_p}\sum_{i=1}^{N_p}\rVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D \alpha_i}\rVert_2^2.
-\label{Eq:primaryObj_patchBased}
-\end{equation}
-For each $i \in \{1,...,N_p\}$, the cost function reduces to:
-\begin{equation}
-J_{\boldsymbol{\theta}}(\boldsymbol{\alpha}_i) =  \lVert \boldsymbol{H_i \Upsilon \theta}-\boldsymbol{D\alpha_i}\rVert_2^2  + \frac{\lambda_3}{\lambda_2}\lVert\boldsymbol{\alpha_i}\rVert_1.
-\label{Eq:alpha_patchBased}
-\end{equation}
-This summarizes the comparison with patch-based methods.
-\newpage
 \bibliography{tci_ref}

### 2020-07-25 paper/tci.tex
Almost ready for submission

@@
 % Do not put math or special symbols in the title.
-\title{Eliminating prior-bias from sparse-projection tomographic reconstructions}
+\title{Eliminating object prior-bias from sparse-projection tomographic reconstructions}
 %
@@
 object's interior
-from a limited set of projection data which are acquired by passing
+from a limited set of projection data acquired by passing
 X-rays at different orientations (`views'). It is preferable to
@@
  \begin{equation}
-J_{\text{CS}}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} \Psi\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1
+J_{\text{CS}}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} \Psi\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1.
 \label{Eq:simple_cs}
  \end{equation}
+ Fig.~\ref{fig:story}
+ (second column) demonstrates the benefit of using sparsity prior when
+ the number of projection views is limited (100 views).
  We solve this cost function using the popular l1-regularized least
  squares (l1-ls) package available in~\cite{l1ls}, and choose DCT as
- our sparsity basis $\boldsymbol{\Upsilon}$.  Fig.~\ref{fig:story}
- (second column) demonstrates the benefit of using sparsity prior when
- the number of projection views is limited (100 views).
+ our sparsity basis $\boldsymbol{\Upsilon}$. We had observed no significant improvement if, say, the wavelet transform were instead used as the basis.
 
@@
  sparsity prior alone is not sufficient.  In such cases additional
- information (called the `object-prior') specific to the current
+ information (`object-prior') specific to the current
  object being scanned (called the `test' henceforth) is useful in
  further improving the reconstruction.  While this has been done in
- the context of dynamic CT-scans (as discussed in
+ the context of dynamic CT-scans (discussed more in
  Section~\ref{sec:related}), in this paper we use a set $S$ of
@@
  interior. As seen in Fig.~\ref{fig:story} (last column, 30 views) our
- method uses the prior scans \emph{uniformly} by creating an
+ method uses the set $S$ \emph{uniformly} by creating an
  eigenspace representation (Section~\ref{sec:method_uniform_prior}).
@@
  Section~\ref{sec:related}, Section~\ref{sec:contributions} lays down
- the key contributions of this work. Section~\ref{sec:tmh}
+ the key contributions of this work. Details of the datasets created and
+ used for validation
+ are described in Section~\ref{sec:datasets}. Section~\ref{sec:tmh}
  demonstrates the utility of both the uniform and spatially-varying
@@
  drawn from our work in Section~\ref{sec:conclusions}.
-
 % We present results on real and simulated 3D
@@
 In order to prevent the object-prior from overwhelming the
-reconstruction of test, few other approaches have either estimated the
+reconstruction of test, a few other approaches have either estimated the
 motion between the object-prior and the test or have applied very
@@
 test.  Examples for the former include~\cite{koen2020}, where the
-changes across the sucessive scan volumes are assumed to be
+changes across the successive scan volumes are assumed to be
 continuous, thus enabling the use of optical flow to model the motion
@@
 inherent assumption is the continuity across volumes in space or
-time. The methods that use object-specific knowledge
+time.
+
+The methods that use object-specific knowledge
 are~\cite{Van2015} and~\cite{Marjolein2016}.  In~\cite{Van2015}, the
@@
 on additional expert domain knowledge which may not be available or
-which may be infeasible to acquire.
-
-Other approaches variously use robust principal components
+which may be infeasible to acquire. Other approaches variously use robust principal components
 analysis assuming that the object consists of a large static part
@@
 spline-based models for tracking the regions of change in an SIRT
-framework~\cite{Van2014}. However, all these
+framework~\cite{Van2014}.
+
+However, all these
 techniques~\cite{daniil2015,koen2020,Van2015,HaoGao,Van2014}
@@
 There exists methods for estimating the new changes (in the test)
-directly in the projection space. In such techniques, the object prior
+directly in the projection space. In such techniques which can
+be used in longitudinal studies, the object prior
 is projected in the same set of views as the current set of test
@@
 object priors, corresponding to high quality reconstructions of
-similar objects across time. We use these priors to improve the
+similar objects across time, typically in a longitudinal study.
+We use these priors to improve the
 reconstruction of the test from largely undersampled measurements. In
@@
 In this section, we lay the details of all the real and simulated
-datasets created and used for this work. We will make these available to the community.
-The first 3 datasets: Okra, Potato and Sprouts were acquired from the Australian National University (ANU). We wish to emphasize that data from commercially
- available CT machines is not suitable because most CT scanners do
+datasets created and used for this work. The first 3 datasets: Okra, Potato and Sprouts were acquired from the Australian National University (ANU). We wish to emphasize that data from commercially
+ available CT machines may not be suitable because most CT scanners do
  not reveal the raw measurements, and instead output only the full
@@
 scans, each after introducing one new cut. The specimen was kept in
-the same position throughout the acquisitions.The measurements
+the same position throughout the acquisitions. The measurements
 consisted of real circular cone-beam projections from 450 views, each of size
@@
 %object-prior after its preliminary pilot reconstruction.
-In our experiments, the first volume was assumed to be the test while
-the rest were used to build the object-prior. The ground truth
+In our experiments, the first 4 volumes shown in Fig.~\ref{fig:object-prior_test_okra} were used to build the object-prior and the
+last volume was used as the test. The ground truth
 consists of volumes of size 338$\times$338$\times$123 reconstructed
@@
 \begin{figure}[!h]
+  \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template4_marked.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template3_marked.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template2_marked.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template1_marked.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
      \begin{subfigure}[b]{0.176\linewidth}
@@
     \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template1_marked.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template2_marked.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template3_marked.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template4_marked.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-     \caption{Okra 3D dataset: One slice each from the each of the scanned volumes.
-The first one is used as the test while the rest are used to build the object-prior.
-Notice that in the regions marked in red and green boxes, while all slices have deformities, the test has none.}
+     \caption{Okra 3D dataset: One slice each from the scanned objects that are used as object-prior (the first four from left) and a slice from the test 
+        volume (extreme right). Notice the regions marked in red and green boxes; while all slices have deformities, the test has none.}
 \label{fig:object-prior_test_okra}
@@
 in-vivo sprout specimen imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}).  In contrast to the
+(Fig.~\ref{fig:object-prior_test_sprouts}).  \textit{In contrast to the
 scientific experiment performed for the case of the okra and potato
 where we introduced man-made defects, the changes here are purely the
-work of nature. In our experiments, the first 5 volumes were used to build the object-prior and the
-last volume was used as the test. The ground truth consists of FDK reconstructed
+work of nature.} In our experiments, the first 5 volumes were used to build the object-prior and the last volume was used as the test. The ground truth consists of FDK reconstructed
 volumes of size 130$\times$130$\times$130 from a set of 1800 view
@@
     \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
+       \begin{subfigure}[b]{0.23\linewidth}
+        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}}
 %\captionsetup{labelformat=empty}       
@@
     \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}
+       \begin{subfigure}[b]{0.23\linewidth}
+        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}}
 %\captionsetup{labelformat=empty}       
@@
 %--------------------------------THM section-------------------------
-
 \section{Application: Reconstruction for CT-guided radio-ablation study}
@@
 \end{enumerate} 
-
-%--------------------RFA 2 few views
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/very_few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
-\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
-\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) FBP and no prior resulting in streaks, SSIM $= 0.48$ (c) l1-ls resulting in blurred bone structures (reasons discussed in Sec.
-5 of our supplementary material~\cite{supp_paper}), SSIM $=0.35$ and (d) uniform prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM $=0.55$.
-The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
-All SSIM values are computed for this RoI.}}
-\label{fig:RFA2_very_few_views}
-\end{figure}
-
-%-------RFA2 moderate views
-
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
-\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
-\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
-\subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
-\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM $= 0.50$ (c) l1-ls with SSIM $=0.46$ and (d) uniform prior, with SSIM $=0.51$ (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) spatially-varying prior with SSIM $=0.56$ (\emph{notice that the dominance of the prior is significantly controlled}).
-The region enclosed in green rectangle is our RoI as it contains both the new position of the needle and some background.
-The SSIM is computed in this RoI.
-(f) shows the computed weights map (defined later in the paper) used for reconstruction.
-Darker intensities indicate lower weights to prior as these are the regions of new changes.}
-\label{fig:RFA2_few_views}
-\end{figure}
-
 %Here, we demonstrate the combined use of l1-ls (CS) with the object
@@
 standard hospital setting. To summarize, when our aim is\\
-
 \begin{itemize}
@@
 of slice 7 from its measurements from only 90 views. The
-reconstructions are quantitatively compared using SSIM.\\
-
-\item \textbf{Observing details of the ablation}, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views i.e., a somewhat higher number of views this time.
+reconstructions are quantitatively compared using SSIM.
+\end{itemize}
+%--------------------RFA 2 few views
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/very_few_views/colorTestIm.png}}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
+\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
+\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) FBP and no prior resulting in streaks, SSIM=0.48 (c) l1-ls resulting in blurred bone structures (reasons discussed in Sec.
+5 of our supplementary material~\cite{supp_paper}), SSIM=0.35 and (d) uniform prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM=0.55.
+The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
+All SSIM values are computed for this RoI.}}
+\label{fig:RFA2_very_few_views}
+\end{figure}
+\begin{itemize}
+\item \textbf{Observing details of the ablation}, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views, i.e., a somewhat higher number of views this time.
 Fig.~\ref{fig:RFA2_few_views} shows the reconstructions of slice 8 by different methods.
@@
   \end{itemize}
+%-------RFA2 moderate views
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
+\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
+\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
+\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
+\subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
+\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM=0.50 (c) l1-ls with SSIM=0.46 and (d) uniform prior, with SSIM=0.51 (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) spatially-varying prior with SSIM=0.56 (\emph{notice that the dominance of the prior is significantly controlled}).
+The region enclosed in green rectangle is our RoI as it contains both the new position of the needle and some background.
+The SSIM is computed in this RoI.
+(f) shows the computed weights map (defined later in the paper) used for reconstruction.
+Darker intensities indicate lower weights to prior as these are the regions of new changes.}
+\label{fig:RFA2_few_views}
+ \vspace{-10mm}
+\end{figure}
 
@@
 Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform  prior-based reconstruction since we are extending this algorithm to 3D reconstructions as part of this work.
-
 %Principal Component Analysis (PCA) has been traditionally used to find the significant modes of (Gaussian corrupted) data.
@@
 We use all of the $L-1$ orthogonal eigenvectors as a basis to represent the unknown test volume.
-Let $\boldsymbol{\mu}$ denote the mean of the previously scanned objects, and $\boldsymbol{\alpha}$ the vector of eigen-coefficients of the test scan, of which $\alpha_k$ is the $k^{\textrm{th}}$ element.
+Let $\boldsymbol{\mu}$ denote the mean of the previously scanned objects, and $\boldsymbol{\alpha}$ the unknown vector of eigen-coefficients of the test scan, of which $\alpha_k$ is the $k^{\textrm{th}}$ element.
 Then, once the eigenspace is pre-computed, the test is reconstructed by minimizing the following cost function:
-\vspace{4mm}
+
  \begin{equation}
@@
 \end{align}
-Note that $\boldsymbol{\theta}$ is solved for using the basis pursuit CS solver, (l1-ls)~\cite{l1ls}. Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
+$\boldsymbol{\theta}$ is solved for using the basis pursuit CS solver, (l1-ls)~\cite{l1ls}. Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
 \begin{equation}
@@
  Table~\ref{table:okra_ssim_full_volume} show that the presence of a
- unifrom object prior significantly improves the overall
+ uniform object prior significantly improves the overall
  reconstruction in comparison with the usage of sparsity prior alone.
@@
 \caption{3D reconstruction of the okra from $10\%$ projection
-  views (b) has strong streak artefacts, (c) blurred (more details in Sec.
+  views (b) has strong streak artefacts, (c) blurred (reasons discussed in Sec.
 5 of our supplementary material~\cite{supp_paper}), (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
@@
  shows the SSIM of the full reconstructed volumes.  Here again, the
- presence of a unifrom object prior significantly improves the overall
+ presence of a uniform object prior significantly improves the overall
  reconstruction in comparison with the usage of sparsity prior alone.
@@
 circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a 
-limitation when we want accurate details of a portion, for example, of the new changes. While the
+limitation when we want accurate details of a portion of the new changes. While the
 uniform prior compensates very well for the possible artefacts due to
-sparse measurements, it dominates the regions with new changes masking
+sparse measurements, it may dominate the regions with new changes masking
 the signal, as was seen earlier in Fig.~\ref{fig:RFA2_few_views}(d). Ideally, we
@@
 %--------------------------------------------------------------
-\begin{table}[]
+\begin{table}[!h]
   \centering
@@
 \label{sec:discussion}
-In this section, we discuss the following:  a) a realistic imaging and reconstruction protocol for longitudinal studies, b) results on homogenous dataset, and (c) tuning of the parameters used.
+In this section, we discuss the following:  a) an alternative imaging and reconstruction protocol for longitudinal studies, b) results on homogeneous dataset, and (c) tuning of the parameters used.
 %The presented uniform prior-based algorithm is suited to applications
@@
 
-\subsection{\textbf{Realistic imaging and reconstruction protocol}}
+\subsection{\textbf{An alternative imaging and reconstruction protocol}}
 %In all our previous results, we had assumed that in a longitudinal study of $n$ scans, the first $n-1$ scans are images with sufficient views and their high-quality reconstructions are used as templates.
@@
 reconstructs new structures while simultaneously reducing streak
-artefacts.Table~\ref{table:potato_ssim} shows the Structure Similarity
+artefacts. Table~\ref{table:potato_ssim} shows the Structure Similarity
 Index (SSIM) of the reconstructed new regions using various
@@
 Fig.~\ref{fig:prior_overview}. When we wish to approximately know the
-location of new changes, we apply an uniform prior because it is fast
-and sufficient for the task at hand. We also choose a smaller number
+location of new changes, we apply a uniform prior because it is
+sufficient for the task at hand. We also choose a smaller number
 of views in order to reduce radiation. In addition, we show that when
@@
 reconstruction of localized new information in the data is not
-affected by the priors. Based on the potato and the okra experiments,
-we see that our method is able to \emph{discover both} the presence of
-a new structure, as well as the absence of a structure. We have thus
+affected by the priors. %Based on the potato and the okra experiments,
+%we see that our method is able to \emph{discover both} the presence of
+%a new structure, as well as the absence of a structure.
+We have thus
 improved the state of the art by detecting these regions of change and

### 2020-07-28 paper/response.tex
Final submitted version

@@
 Here, we are including our response to each reviewer, and pointers to modifications (suggested by the reviewers and the AE) in our revised manuscript.
-Where necessary, we tie up related comments from the multiple reviewers for ease of understanding.
-We have organized this document in three parts (a) Response to comments from AE (Section A), and (b) Response to significant points made by all the other reviewers (c) Detailed  responses to the comments of each of the reviewers.
+Where necessary, we tie up related comments from multiple reviewers for ease of understanding.
+We have organized this document in three parts (a) Response to comments from AE (b) Response to significant points made by all the reviewers (c) Detailed  responses to the comments of each of the reviewers.
 To the best of our knowledge, we have painstakingly addressed each and every point of all the reviewers, and responded adequately.
@@
 
-For ease of understanding, since the current version of the (revised) manuscript is considerably reorganized, in this document, we have used the (longer) terms ``Figure x'',``Equation y'' and ``Table z''  to refer to a figure, equation and table respectively in the old version, and the (shorter) terms ``Fig.~x'', ``Eq.~y'' and ``Tab.~z'' to refer to the corresponding figure, equation and table in the current version.
+For ease of understanding, since the current version of the (revised) manuscript is considerably reorganized, in this document, we have used the (longer) terms ``Figure x'',``Equation y'' and ``Table z''  to refer to a figure, equation and table respectively in the old version of the manuscript, and the (shorter) terms ``Fig.~x'', ``Eq.~y'' and ``Tab.~z'' to refer to the corresponding figure, equation and table in the current version.
 
@@
 
-In addition to the reviewer specific comments, please pay specific attention to the following:\\
+\textcolor{blue}{\textit{In addition to the reviewer specific comments, please pay specific attention to the following:}}\\
 
@@
 The introduction has been modified and the stage set for outlining our contributions have been made.
-We have replaced the earlier Figure 1 (which did not have longitudinal data) with a more appropriate figure (Fig.1).
-The unfamiliar terms ``unselective'' and ``selective'' prior have now been replaced by ``uniform'' prior and ``spatially varying'' prior to better communicate the property of the respective priors.
-A new section  (Section 2) named ``Related Work'' has been included separately to contrast this work with the prevailing work in the literature. 
-Details of the datasets have been moved to a separate section (Section 4) so the ground is properly set.
+We have replaced the earlier Figure~1 (which did not have longitudinal data) with a more appropriate figure (Fig.~1).
+\textbf{The unfamiliar terms ``unselective'' and ``selective'' prior have now been replaced by ``uniform'' prior and ``spatially varying'' prior to better communicate the property of the respective priors.}
+A new section  (Sec.~2) named ``Related Work'' has been included separately to contrast this work with the prevailing work in literature. 
+Details of the datasets have been moved to a separate section (Sec.~4) so the ground is properly set.
 The two earlier sections: methods and results sections have now been split into the following 4 sections.
@@
 We have  ensured that the rest of the paper can be followed without it.
-We have also moved the discussion on the earlier patch-based methods to supplementary material~\cite{supp_paper}.
+We have also removed the discussion on the earlier patch-based methods since it is not the central theme of this paper and its details can be found in~\cite{my_dicta_paper}.
 However, results not reported earlier prior to this submission using the uniform prior on 3D volumetric data continues to be present (as mentioned above) in Section 6 since it forms an important part of our story for this paper.\\
@@
 \textbf{Response:} We have now re-written the contributions section (Sec.~3 of the main paper), that highlights the novelty of our work.  
-As a response to the comparisons required,  in many cases, our methods are incomparable to previous algorithms because of the nature of the longitudinal study  We discuss this in the related work section.
+As a response to the comparisons required,  in many cases, our methods are incomparable to previous algorithms because of the nature of the longitudinal study.
+We discuss this in the `related work' section.
 Further we reiterate that in our earlier manuscript version, we had compared our method with l1-regularized least squares (l1-ls) and FDK for 3D reconstructions.
-We had also compared (Fig.8) our method with many other iterative methods such as (ART, SART and SIRT) -- this set of comparisons was buried in a footnote, and perhaps not easily visible.
-In addition to these, we have now included (earlier absent) Table 3 to show a quantitative comparison of SSIM values of the reconstruction by various methods shown in Fig.~8.
+We had also compared (Figure~8, Fig.~13) our method with many other iterative methods such as (ART, SART and SIRT) -- this set of comparisons was buried in a footnote, and perhaps not easily visible.
+In addition to these, we have now included (earlier absent) table Tab.~3 to show a quantitative comparison of SSIM values of the reconstruction by various methods shown in Fig.~13.
 We also discuss compressed sensing (see AE-C3) results.
@@
 This reference is now mentioned in our related work; although this paper is not directly applicable in longitudinal studies where object-priors `are' available, there is a reference in this paper to another paper which does make use of object-prior.
-We show how our work is superior in our response to R3 below (we include this in Sec.~4 of the supplementary material~\cite{supp_paper}).
+We show how our work is superior in our response to R3-C2 (we also include this in Sec.~4 of the supplementary material~\cite{supp_paper}).
 \\
@@
 
-\textbf{Response:} We believe we now have clearly brought out the compressed sensing based works both in the introduction and in the related work section.
+\textbf{Response:} We believe we now have clearly brought out details of the compressed sensing based optimization (specifically l1-regularized least squares [l1-ls]) both in the introduction and in the related work section.
 Related points w.r.t.
-CS-type reconstruction made by R1/R3 appears below in B1 (and elsewhere in even greater detail).
+CS-type reconstruction made by R1/R3 appears in our individual responses (and Sec.~5 of our supplementary material~\cite{supp_paper}).\\
 
@@
 However,  coming to the main contribution of the paper, if the number of views becomes significantly small (when compared even to sub-Nyquist), reconstructions using CS is less than satisfactory, despite the removal of sub-sampling artefacts.
-This has also been pointed out earlier in a different (not ours) published work [11], Page 4, line 22.
-We have now described the use-case for CS reconstructions in Fig.
-1 and have elaborated on the blurred artefacts in our  response in R3-C7.
+This has also been pointed out earlier in a different (not ours) published work~\cite{PICCS}, Page 4, line 22.
+We have now described the use-case for CS reconstructions in Fig.~1 of our revised paper, and have elaborated on the blurred artefacts in Sec.~5 of our supplementary material~\cite{supp_paper}.
 \item All reviewers are concerned about the seemingly low SSIM value (relatively poor reconstruction) for one of the experiments.
@@
 
-In response, we first note that our updated results of comparison for this dataset (after the tuning suggested by R1) \textit{now} results in a favourable result (Table 3).
+In response, we first note that our updated results of comparison for this dataset (after the tuning suggested by R1) \textit{now} results in a favourable result (table Tab.~3).
 That said, we agree that the FDK reconstructions can be superior, as evidenced for this particular dataset alone -- presumably when the region of interest is known a-priori (which is not always the case).
-We have devoted a separate section in the `Discussion' for this particular concern: Tab.~7 better explains why our method is suitable, and Fig.~19(e) the more pleasing visual result.
+We have devoted a separate section in the `Discussion' (Sec.~10(B)) for this particular concern: Tab.~7 better explains why our method is suitable, and Fig.~19 shows the updated (improved) visual result.
 \item R1 and R3 also raise another significant point:  What happens if we have only the object prior term and ignore the sparsity prior?
@@
 \subsection{Response to Reviewer 1}
+(We have numbered these comments as \textbf{R1-Cx}, and italicized for clarity.)\\
+
 There are some concerns associated with the compressive sensing (CS) method, the explanation for weight selection, and the clarity of results. Some of the major issues are described below. \\
@@
 CS does use the sparsity prior.
-We have now moved this point much earlier in the introduction, and point out some of the advantages of using object-prior.
-Sec.1, Page1.
-We have corrected the captions.
-Specifically, (for example) the earlier caption of Fig.4-c: ``CS and no prior resulting in blurred bone structures'' has now been replaced by ``l1-ls resulting in blurred bone structures''.
-In the latter, ``l1-ls'' refers to L1-regularized least squares optimization \\
+We have now moved this point much earlier in the introduction  (Sec.~1, Page~1), and point out some of the advantages of using object-prior, in addition to sparsity-prior.
+We have corrected the figure captions.
+Specifically, (for example) the earlier caption of Figure~4(c): ``CS and no prior resulting in blurred bone structures'' has now been replaced (in Fig.~7(c)) by ``l1-ls resulting in blurred bone structures''.
+In the latter, ``l1-ls'' refers to L1-regularized least squares optimization.
+\\
 
@@
 
-\textbf{Response:} Agreed. See response is \textcolor{blue}{\textbf{R1-C3}}.\\
+\textbf{Response:} Agreed. See response in R1-C3.\\
 
@@
 
-\textbf{Response:} With respect to Figure.
-10(c) of the submitted paper which corresponds to Fig.17(c) of the new version, we have now updated the reconstruction after tuning $\lambda_1$ to get the optimal result for l1-ls, as suggested by Reviewer 1.
-The optimal $\lambda_1$ was found to be 1.7.
+\textbf{Response:} With respect to Figure~10(c) of the submitted paper which corresponds to Fig.~19(c) of the new version, we have now updated the reconstruction after tuning $\lambda_1$ (using SSIM as the metric) to get the optimal result for l1-ls.
+The optimal $\lambda_1$ was found to be 1.7 for potato dataset.
+Similarly, we have also now tuned $\lambda_1$ for okra and sprouts 3D reconstructions.
 
-In Sec.5 of our supplementary material~\cite{supp_paper}, we describe why the image in Fig.17(c) (Fig.10(c) of the old version) appears over-regularized by presenting reconstructions on 2D potato dataset for different number of views and optimally tuned $\lambda_1$ values.
+In Sec.~5 of our supplementary material~\cite{supp_paper}, we describe why the image in Fig.~19(c) (Figure~10(c) of the old version) appears over-regularized by presenting reconstructions on 2D potato dataset for different number of views and optimally tuned $\lambda_1$ values.
 \\
@@
 
-\textbf{Response:} Although the data-agnostic CS/sparsity  prior and the data-dependent object-prior  (either uniform or spatially varying) affect independent terms in the overall cost function (Eq.6), best results are obtained when both the priors are used together.
+\textbf{Response:} Although the data-agnostic CS/sparsity  prior and the data-dependent object-prior  (either uniform or spatially varying) affect independent terms in the overall cost function (Eq.~6), best results are obtained when both the priors are used together.
 Whether to use the CS prior or not is a function of the quality of the object-prior.
@@
 
-\textcolor{blue}{\textbf{R1-C6.}\textit{ Schematic 1 in section III (B) does not make sense. But, the explanation in section III (B) (2) is clear.}}
+\textcolor{blue}{\textbf{R1-C6(a).}\textit{ Schematic 1 in section III (B) does not make sense. But, the explanation in section III (B) (2) is clear.}}
 
@@
 
-\textbf{Response:} To illustrate how different reconstruction methods lead to different artefacts and how combining them carefully can cancel those artefacts, we present a few intermediate weights maps for a 2D reconstruction from 12 views (of the test image in Fig.10 of the paper), with and without noise.
+\textbf{Response:} To illustrate how different reconstruction methods lead to different artefacts and how combining them carefully can cancel those artefacts, we present a few intermediate weights maps for a 2D reconstruction from 12 views (of the test image in Fig.~11 of the paper), with and without noise.
 Due to the lack of space, we have not included the below images in the main paper.
@@
 \end{figure}
-In the Figs.~\ref{fig:weights_no_noise} and~\ref{fig:weights_with_noise}, notice how the weights map is different for each of the methods and how it is improved when it is computed using two or more methods.
+In the Figs.~\ref{fig:weights_no_noise} and~\ref{fig:weights_with_noise} here, notice how the weights map is different for each of the methods and how it is improved when it is computed using two or more methods (using Eq.~7 in the paper).
 We observe similar benefits even in the presence of small quantities of noise as shown below.
@@
 \captionsetup{labelformat=empty}
-        \caption{FBP + SART + SIRT}
+        \caption{FBP + SIRT + SART}
      \end{subfigure}
@@
 
-\textbf{Response:} While the zoomed-in RoI of Okra is in Figure 13 of the old manuscript (Fig.14 of the new manuscript), the zoomed-in RoI of the sprouts dataset has now been added in Fig.
-16.
-For other cases, large sized images are in the supplementary material~\cite{supp_paper}.\\
+\textbf{Response:} While the zoomed-in RoI of Okra is in Figure 13 of the old manuscript (Fig.~15 of the new manuscript), the zoomed-in RoI of the sprouts dataset has now been added in Fig.~17.
+We have also added large sized images in Sec.~3 of the supplementary material~\cite{supp_paper}.\\
 
@@
 \textbf{Response:} Despite tuning $\lambda_1$, In Fig.
-19(e) (previously Fig.10(e) of the old version), the information about the new region (within RoI)  is present only in the measurements of the test, and is absent in all of the templates.
+19 (previously Figure~10 of the old version), the information about the new region (within RoI)  is present only in the measurements of the test, and is absent in all of the templates.
 This is unlike the case for the surrounding holes, the information about which is present both in the measurements of the test and the templates.
@@
 
-\textbf{Response:} We have now defined longitudinal study in the paper (Sec.
-1).
+\textbf{Response:} We have now defined longitudinal study in the paper (Sec.~1, Page~2, just below Fig.~1).
 Longitudinal studies here refers to the acquisition of sequential CT scans of the same subject to track time-evolving changes within the subject's interior.
@@
 
-\textbf{Response:} The caption has now been correctly renamed to (g). 
-By `combined', we denote the weight map computed as per Eq.7.
+\textbf{Response:} The caption (now in Fig.~13) has been correctly renamed to (g). 
+By `combined', we denote the weight map computed as per Eq.~7.
 This equation incorporates the use of the eigen-space of the templates reconstructed from various methods (such as ART, SART, SIRT, etc.), and pilot reconstructions of the test,  again reconstructed from various methods.
-In Eq.7, the min(.) operator ensures that we select the new regions that are unanimously detected by all the methods of reconstruction.
+In Eq.~7, the min(.) operator ensures that we select the new regions that are unanimously detected by all the methods of reconstruction.
 Hence, the word `combined' denotes that all the reconstruction methods are combined to give information about the new regions of the test.\\
@@
 
-\textbf{Response:} The zoomed-in RoI is now shown in Fig. 17. \\
+\textbf{Response:} The zoomed-in RoI is now shown in Fig.~17. \\
 
@@
 
-\textbf{Response:} Thank you for the suggestion. We have now submitted the supplementary material  on the publication portal. \\
+\textbf{Response:} Thank you for the suggestion. We have now submitted the supplementary material  on the publication portal, besides the Dropbox link. \\
 
@@
 
-\textbf{Response:} In order to save space and for greater clarity, we have now moved the discussion on patch-based techniques to supplementary material~\cite{supp_paper}.
+\textbf{Response:} We have removed the discussion on the earlier patch-based methods since it is not the central theme of this paper and its details can be found in~\cite{my_dicta_paper}.
 
@@
 
-\textbf{Response:} We hypothesize that because the volume of this dataset (potato) is very homogeneous (without intricate  structures), the test measurements capture sufficient information about the new regions even with $5\%$ views and hence FDK performs very well in the exact region of interest (shown as red RoI in Fig.
-19(a)).
-However, as we expand the region of interest (green and cyan RoI in Fig.
-19a), the prior-based methods perform better than FDK (please refer Table 8) in that they minimize the sub-sampling artefacts.
+\textbf{Response:} We hypothesize that because the volume of this dataset (potato) is very homogeneous (without intricate  structures), the test measurements capture sufficient information about the new regions even with $5\%$ views and hence FDK performs very well in the exact region of interest (shown as red RoI in Fig.~19(a)).
+However, as we expand the region of interest (green and cyan RoI in Fig.~19(a)), the prior-based methods perform better than FDK (please refer Tab.~7) in that they minimize the sub-sampling artefacts.
 We have now discussed this in Sec.~10(B) - ``Reconstruction of homogeneous data''.
-Had the new region been embedded within an intricate background (like the sprouts and okra), its reconstruction does give rise to artefacts as seen in Figs.13-b and 15-b. \\
+Had the new region been embedded within an intricate background (like the sprouts and okra), its reconstruction does give rise to artefacts as seen in Figs.~14(b) and 16(b). \\
 
@@
 
- \textbf{Response:} Accepted. This has been corrected, and the equation has now been moved to  supplementary material~\cite{supp_paper} (Eq.2). \\
+ \textbf{Response:} Accepted.
+This has been corrected for other equations.
+However, this particular equation is not present in the current version because we have removed the discussion on the earlier patch-based methods (since it is not the central theme of this paper and its details can be found in~\cite{my_dicta_paper}).
+\\
 
@@
 
- \textbf{Response:} In Sec.6, we use ``Proposed method'' to refer to uniform prior-based method, and in Sec.8 we use ``Proposed method'' to refer to spatially varying prior-based method.\\
+ \textbf{Response:} In Sec.~6, we use ``Proposed method'' to refer to uniform prior-based method, and in Sec.~8 we use ``Proposed method'' to refer to spatially varying prior-based method.\\
 
@@
 
-  \textbf{Response:} Accepted. This has been typeset.\\
+  \textbf{Response:} Since ``unselective prior'' has now been replaced by ``uniform prior'', it has been typeset in two lines in the figure captions.\\
 
@@
 
-  \textbf{Response:} Accepted. This has been corrected.\\
+  \textbf{Response:} Accepted. This has been corrected in the new Fig.~16.\\
 
@@
 
- \textbf{Response:} Accepted. This has been corrected.\\
+ \textbf{Response:} Accepted. This has been corrected (now in Fig.~18).\\
 
@@
 \textbf{ Response:} The results of the (compared, CS) method are sub-optimal because of a significantly fewer number of views.
-We show  (see R3-C7) that if we increase the number of views, CS actually does very well, as expected, and as mentioned by the reviewer.
+We show  (see Sec.~5 in our supplementary material~\cite{supp_paper}) that if we increase the number of views, CS actually does very well, as expected, and as mentioned by the reviewer.
 
-We have compared our 2D reconstructions with many other iterative techniques such as SIRT, SART and ART, as seen in Fig.
-12 (Figure.8).
+We have compared our 2D reconstructions with many other iterative techniques such as SIRT, SART and ART, as seen in Fig.~13 (Figure.~8).
 Earlier we had not included the SSIM values,  and these now appear in Tab.
@@
 
-\textcolor{blue}{\textbf{R3-C2.}\textit{ Since no details are given about the method that is compared with (what function does in optimize?}}
+\textcolor{blue}{\textbf{R3-C2.}\textit{ Since no details are given about the method that is compared with (what function does it optimize?}}
 
@@
 
-Of the many other prior-based techniques, we have now discussed  below how we contrast with them in Sec.2 (`Related work').
+Of the many other prior-based techniques, we have now discussed  below how we contrast with them in Sec.~2 (`Related work').
 In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}.
@@
 \textbf{ Response:} Details of the parameters and their tuning were earlier discussed in Section 5B.
-$\lambda_1$ was set equal to 1 in all datasets (as observed by R1, and line 53, page 9, column 2).
+$\lambda_1$ was set equal to 1 in all datasets (line 53, page 9, column 2).
 This was done by visual inspection for one of the dataset and used elsewhere as is.
@@
 Here below, we present the changes in the accuracies due to tuning of $\lambda_1$ in Tables~\ref{tab:sprouts_revised_ssim}, and~\ref{tab:okra_revised_ssim}.
-The new visual results and SSIM values are in Figs.
-13, 15 and 19, and in Tables 4, 5 and 8.
+The new visual results and SSIM values are in Figs.~14,~16 and~19, and in Tables~4,~5 and~7.
 
@@
 However incorporation of object priors will significantly help to mitigate those artifacts.
-In Fig.12 (Figure 8), we had earlier shown a visual comparison of 2D reconstructions of one of the datasets (potato) by all of the following methods: FBP, CS with DCT as sparsity prior, CS with Haar as sparsity prior, ART, SART, SIRT and our weighted prior method.
+In Fig.~13 (Figure 8), we had earlier shown a visual comparison of 2D reconstructions of one of the datasets (potato) by all of the following methods: FBP, CS with DCT as sparsity prior, CS with Haar as sparsity prior, ART, SART, SIRT and our weighted prior method.
 We have now also included a quantitative comparison of the accuracy of these results in Tab. 3 of the new manuscript.\\
@@
 The objective function minimized while using l1-ls (CS) optimization is now introduced in Eq.1. This is the same as Eq. 6,  with $\lambda_2 = 0$.
-Details of parameter selection is now in Section 9-B.
+Details of parameter selection is now in Section 10(C).
 In our earlier submission, $\lambda_1$ and $\lambda_2$ values were chosen by reconstructing the test volume by sweeping through a range of values and selecting the set of values that gave a reasonable visual quality.
@@
 \textbf{Response:} The methods have indeed converged.
-Also mention that the perceived quality of reconstruction results using any technique can be quite subjective, and also dependent on the structure of the image as well as the number of projection views.
-In order to demonstrate this, we show the quality of reconstructions by CS for a varying number of views in Sec.
-5 of our supplementary material~\cite{supp_paper}.
+The perceived quality of reconstruction results using any technique can be quite subjective, and also dependent on the structure of the image as well as the number of projection views.
+In order to demonstrate this, we show the quality of reconstructions by CS for a varying number of views in Sec.~5 of our supplementary material~\cite{supp_paper}.
 In this paper, we are considering a very small number of views.
-What is the cause: When the number of views is large, the reconstruction using CS (l1-ls) is indeed good.
+
+When the number of views is large, the reconstruction using CS (l1-ls) is indeed good.
 However, when the number of views decreases, the reconstruction using CS (LASSO) is blurred, but with the benefit of suppressed artefacts that are otherwise present in FBP reconstruction.
-This is illustrated in Sec.
-5 of our supplementary material~\cite{supp_paper}.
+This is illustrated in Sec.~5 of our supplementary material~\cite{supp_paper}.
 For the 3D reconstructions shown in the updated paper, the $\lambda_1$ value is now chosen by performing l1-ls reconstructions for a wide range of values and then selecting the one that maximizes SSIM.
@@
 
-\textbf{Response:}  Although the shape of the left-most void (now in the green RoI of Fig.19 of the updated paper) is slightly bigger than it should be, the results of our method is better than that of FDK and this is reflected in the SSIM values of the new Table 8.
+\textbf{Response:}  Although the shape of the left-most void (now in the green and cyan RoI of Fig.~19 of the updated paper) is slightly bigger than it should be, the results of our method is better than that of FDK as the region of interest progressively increases and this is reflected in the SSIM values of the new table Tab.~7.
 In practice, the reconstruction of the new regions is dependent on the noise (false-positives) present in the weights-map.
 We have optimally selected the hyperparameter `k' to minimize the noise in the weights-map.
-In order to evaluate the accuracy of our reconstruction of the seeds in Figure 12 of old manuscript (Fig.13 of current manuscript), we have enlarged the green RoI to include the seeds as well (See Fig.
-13-a), and have presented the SSIM on this RoI in Table 4.
+
+In order to evaluate the accuracy of our reconstruction of the seeds in Figure 12 of old manuscript (Fig.~14 of current manuscript), we have enlarged the green RoI to include the seeds as well (See Fig.~14-a), and have presented the SSIM on this RoI in table Tab.~4.
 The SSIM value in the green RoI (which includes the seeds) is the highest for our method.
-We note that the results of Fig.13 have been updated after tuning for $\lambda_1$.
+We note that the results in Fig.~14 have been updated after tuning for $\lambda_1$.
 Having said that, even for the results presented in our earlier manuscript, the accuracy for our reconstruction in the area of seeds is the highest.
@@
 FDK: 0.81\\
-L1-ls:0.82\\
+L1-ls: 0.82\\
 Uniform prior: 0.76\\
@@
 Hence, we have chosen SSIM (with the following factors: 0.1 for accuracy in intensity, 0.2 for accuracy in contrast, and 0.7 for accuracy in shape).
-Hence, the SSIM values give a close interpretation of the results in addition to the visual inspection.
+The SSIM values therefore give a close interpretation of the results in addition to the visual inspection.
 \\
@@
 In another study~\cite{vincent2017}, changes between successive scans were modelled by affine deformation whose parameters were computed for motion-correction.
-Such a correction enables acquisition from fewer views than would have otherwise not been possible for reconstruction with adequate fidelity.
+Such a correction enables acquisition from fewer views than would have otherwise been possible for reconstruction with adequate fidelity.
 In~\cite{daniil2015}, all the scan volumes are reconstructed together using spatio-temporal regularization.
+
 In~\cite{Van2014} (``Region-based iterative reconstruction of structurally changing objects in CT''), spline-based models are applied for tracking the regions of change in a SIRT framework.
@@
 (In longitudinal studies, each scan must be reconstructed as soon as it is imaged, with the possible use of reconstructed volumes from previous scans.)
-We have now discussed this in Sec.2 (`Related Work') of our paper.
-In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. This has been discussed in our response to \textbf{R3-C2}.\\
+We have now discussed this in Sec.~2 (`Related Work') of our paper.
+In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. This has been discussed in our response to R3-C2.\\
 
@@
 \textbf{Response:} Deep learning techniques typically require large amounts of data.
-However, any given longitudinal study will allow for a very limited amount of data..
+However, any given longitudinal study will allow for a very limited amount of data.
 Moreover, there will be major generalization errors in deep learning based techniques for direct tomographic reconstruction, and in a clinical setting, we believe, current deep learning methods need to evolve further.\\
@@
 
-\textbf{Response:} The effect of the hyperparameter k on the weights-map and final reconstruction was earlier shown Figures.
-17 and 18 (Fig.
-20 and 21).
+\textbf{Response:} The effect of the hyperparameter k on the weights-map and final reconstruction was earlier shown in Figures.~17 and 18 (Figs.~20 and 21).
 These figures show that the selection of k decides the sensitivity to noise (false positives) in the weights-map.
-The range of k values deal with the extreme cases of very less amount of noise (Figure 17-a ,Fig.
-20-a) upto high levels of false positives at the expense of not missing any true positive.
-(Figure.
-17-l, Fig.
-20-l).In our experiments, the object prior had a stronger impact on reconstructions than the sparsity prior.
-This is because the object prior was built using high quality previous scans.
+The range of k values shown deals with the extreme cases of very less amount of noise (Figure 17(a), Fig.
+20(a)) upto high levels of noise (false positives) at the expense of not missing any true positive (Figure~17(l), Fig.~20(l)).
+\\
 
-\textbf{Reconstruction with $\lambda_1 =0$:} Here, below is a slice from the reconstructed potato volume when $\lambda_1$ is set to $0$, i.e., with no sparsity prior and with object prior alone.
+In our experiments, the object prior had a stronger impact on reconstructions than the sparsity prior. This is because the object prior was built using high quality previous scans.
+
+\textbf{Reconstruction with $\lambda_1 =0$:} Here below is a slice from the reconstructed potato volume when $\lambda_1$ is set to $0$, i.e., with no sparsity prior and with object prior alone.
 \begin{figure}[!h]
@@
 \end{tabular}
-\end{table}\\
+\label{tab:zerocslambda}
+\end{table}
+
+As discussed in Sec.~10(B), for homogeneous data, FDK performs very
+well for smaller RoI; as the RoIs get bigger, the FDK reconstructions
+have poor SSIM due to strong subsampling artefacts. In contrast, the
+results from l1-ls and our method progressively improve
+(Tab.~\ref{tab:zerocslambda} here, Tab.~7 in the main paper) when compared to FDK as the RoIs get
+bigger. In practice, the RoI is not known in advance and hence, one
+may choose FDK for the case of simple, homogeneous dataset with
+smaller RoI, and prefer spatially-varying prior-based reconstruction
+when the dataset is complex and RoIs are larger.\\
 
@@
 
-\textbf{Response:} We wish to point out that our inference about CS reconstructions being blurred on undersampled data has been earlier pointed out in the published work~\cite{PICCS} in Page 4, line 22.
-We again reiterate this here that the reconstruction using CS is of good quality (as proven in literature) when the number of views is large.
-However, when the number of views is limited, the optimizer (with optimal lambda) indeed blurs the overall reconstruction in an attempt to remove the sub-sampling artefacts.
-We have now demonstrated this in our response to \textbf{R3-C7}.
+\textbf{Response:} We wish to point out that our inference about CS reconstructions being blurred on undersampled data has been earlier pointed out in another (not ours) published work~\cite{PICCS} in Page 4, line 22.
+We again reiterate this here that reconstruction using CS is of good quality (as proven in literature) when the number of views is large.
+However, when the number of views is limited, the optimizer (with optimal $\lambda$) indeed blurs the overall reconstruction in an attempt to remove the sub-sampling artefacts.
+We have now demonstrated this in our response to R3-C7 and in Sec.~5 of the supplementary material~\cite{supp_paper}.
 
@@
 
-\textbf{Response:} The relevant reference is ~\cite{monotone} and is now included in the paper.\\
+\textbf{Response:} The relevant reference is~\cite{monotone} and is now included in the paper.\\
 
@@
 \textbf{Response:} Our statement was based on papers which had used either phantoms or dynamic CT data.
-For example, In papers such as~\cite{pirple}, the dataset consisted of measurements corresponding to a lung-phantom; validation was not performed on a dataset of a real lung CT.
+For example, in papers such as~\cite{pirple}, the dataset consisted of measurements corresponding to a lung-phantom; validation was not performed on a dataset of a real lung CT.
 In~\cite{Hakka2019}, the dynamic dataset consisted of face emoji phantoms and simulations from an already available reconstructed lung volume.
 After surveying literature again, we have now found papers that have used real data.
-Hence,  we have now retracted our earlier statement about literature and have mentioned instead the general scenario: ``Data from commercially available CT machines is not suitable because most CT scanners do not reveal the raw measurements, and instead output only the full reconstructed volumes.
+Hence,  we have now retracted our earlier statement about literature and have mentioned instead the general scenario alone: ``Data from commercially available CT machines is not suitable because most CT scanners do not reveal the raw measurements, and instead output only the full reconstructed volumes.
 Moreover, the process of conversion from the  projections to the full volumes is proprietary.'' \\
@@
 
-\item Introduction, 
+\item introduction, 
 \item related work (to compare this work with similar papers in literature), 
@@
 \item application (on a longitudinal medical data), 
-\item uniform prior, 
+\item uniform prior method, 
 \item results of uniform prior (including comparison with results from FDK and l1-ls), 
-\item spatially-varying prior, 
+\item spatially-varying prior method, 
 \item results of spatially-varying prior (including comparison with results from FDK, l1-ls and uniform prior), 
@@
   \end{itemize}
-For greater clarity, we have now removed Schematic 1 from the paper; We have  ensured that the rest of the paper can be followed without it.\\
+For greater clarity, we have now removed Schematic~1 from the paper; We have  ensured that the rest of the paper can be followed without it.\\
 
@@
 
-\textbf{Response:} In order to be clear with the description, we have now rewritten Sec.1 (Introduction). All the variables are now introduced in paragraph 2 and 3 of Page 1 of the paper.\\
+\textbf{Response:} In order to be clear with the description, we have now rewritten Sec.~1 (Introduction). All the variables are now introduced in paragraph~2 and~3 of Page~1 of the paper.\\
 
@@
 In~\cite{daniil2015}, all the scan volumes are reconstructed together using spatio-temporal regularization.
-We have now discussed this in Sec.2 (`Related Work') of our paper.
-In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. This has been discussed in our response to R3-C2.\\
+We have now discussed this in Sec.~2 (`Related Work') of our paper.
+In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}.
+This has been discussed in our response to R3-C2, and in Sec.~4 of our supplementary material~\cite{supp_paper}.\\
 

### 2020-07-28 paper/tci.tex
Final submitted version

@@
 \begin{enumerate}
-\item To track the position of the needle in a relatively well-reconstructed background.%Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
-\item To accurately observe the new changes amidst a relatively well reconstructed background after the needle touches the tumor.%Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
+\item to track the position of the needle, and% in a relatively well-reconstructed background.%Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
+\item to accurately observe the new changes when the needle touches the tumor,%Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
 In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a spatially-varying prior-based reconstruction.
@@
 \end{enumerate}
+while simultaneously reducing the sub-sampling artefacts.
 %Here, we demonstrate the combined use of l1-ls (CS) with the object
@@
 \label{fig:RFA2_few_views}
- \vspace{-10mm}
+ \vspace{-9mm}
 \end{figure}
@@
 \label{sec:discussion}
-In this section, we discuss the following:  a) an alternative imaging and reconstruction protocol for longitudinal studies, b) results on homogeneous dataset, and (c) tuning of the parameters used.
+In this section, we discuss the following:  a) an alternate imaging and reconstruction protocol for longitudinal studies, b) results on homogeneous dataset, and (c) tuning of the parameters used.
 %The presented uniform prior-based algorithm is suited to applications
@@
 
-\subsection{\textbf{An alternative imaging and reconstruction protocol}}
+\subsection{\textbf{An alternate imaging and reconstruction protocol}}
 %In all our previous results, we had assumed that in a longitudinal study of $n$ scans, the first $n-1$ scans are images with sufficient views and their high-quality reconstructions are used as templates.

### 2021-08-12 paper/post_tci.tex
post_tci.pdf

--- 2020-07-28 paper/tci.tex
@@
 LASSO solution is described by one that minimizes
+
  \begin{equation}
-J_{\text{CS}}(\boldsymbol{\theta}) = \lVert\boldsymbol{\mathcal{R} \Psi\theta}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1.
-\label{Eq:simple_cs}
+   TV(\boldsymbol{x}) = \sum_{i,j}\nabla_{ij}(\boldsymbol{x})
+   \label{Eq:definition_TV}
+\end{equation}
+
+ \begin{equation}
+   J_{TV}(\boldsymbol{x}) = \lVert\boldsymbol{\mathcal{R}x}- \boldsymbol{y}\rVert_2^2 + \lambda_{TV}TV(\boldsymbol{x})
+   \label{Eq:simple_TV}
    \end{equation}
@@
 	\includegraphics[width=0.45\textwidth]{../images/story/story.png}
-        \caption{Illustration of the use of various priors in the
+        \caption{Illustration of the use of various priors in 
           reconstruction as the number of views reduces. In all cases,
           the ground truth (260$\times$260) appears in the top left.
-          For extremely large number of views (600 views), the FBP
+          For extremely large number of views (800 views), the FBP
           reconstruction (first column) is of very good quality
@@
           number of views become limited (100 views), the
-          reconstruction using sparsity prior (middle column) is
+          reconstruction using a general data-independent prior such as Total Variation (TV, middle column) is
           better both visually and quantitatively than FBP (SSIM of
-          0.90 vs 0.83). If the number of views is drastically reduced
-          (30 views), the presence of both sparsity prior and object
-          prior improves the reconstruction (SSIM=0.85) when compared
-          to presence of only sparsity prior (SSIM=0.82) or no prior
-          (SSIM=0.69).}
+          0.96 vs 0.82). If the number of views is drastically reduced
+          (20 views), the presence of both TV prior and object
+          prior together improves the reconstruction (SSIM=0.91) when compared
+          to presence of only TV prior (SSIM=0.87) or no prior
+          (SSIM=0.64).}
  \label{fig:story}
@@
 \centering
-	\includegraphics[width=0.5\textwidth]{../images/prior_cmb_edited.png}
-        \caption{Overview of our work. The choice of the number of
-          measurement views and the type of reconstruction is driven
-          by the goal in the application under consideration.  (a) When
-          our goal is relatively simple, such as tracking the location
-          of new changes while simultaneously reducing sub-sampling
-          artefacts, we propose acquiring measurements from an
-          extremely small number of views (`few-view' imaging) and
-          using uniform prior based reconstruction. (b) When our goal
-          becomes more ambitious, such as observing details of the new
-          changes while simultaneously reducing sub-sampling
-          artefacts, we propose acquiring measurements from a
-          slightly higher number of views (`moderate-view' imaging)
-          and using spatially-varying prior-based reconstruction. In
-          either case, the number of views is lower than what is
-          conventionally used.}
+	\includegraphics[width=0.5\textwidth]{../images/prior_cmb.png}
+        \caption{Overview of our work.
+When only few measurements are available, the choice of the reconstruction algorithm is driven by availability of object-prior.
+(a) In the absence of object-prior, any method that utilizes object-independent prior (such as total variation, sparsity) may be used.
+(b) In the presence of object-prior, we propose using spatially-varying prior-based reconstruction which utilizes both object-dependent and object-independent priors.
+In either case, the number of views is lower than what is conventionally used.}
  \label{fig:prior_overview}
@@
     \end{subfigure}     
-       \begin{subfigure}[b]{0.23\linewidth}
-        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}}
-%\captionsetup{labelformat=empty}       
- \caption{slice 8}
-    \end{subfigure}     
      \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver.
-Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.
-(h) the organ after the ablation: this slice is displayed on a separate intensity scale to enable proper viewing of the region marked in green that shows the after-effects of ablating the tumor.}
+Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.}
 \label{fig:RFA2_test_object-prior}
@@
 \subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/cs.png}}\hfill
-\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/plain_pca.png}}
-\caption[Representative results-1]{\textbf{Goal: Track new changes.}\small{ Reconstruction of slice 7 (`test') of Fig.~\ref{fig:RFA2_test_object-prior} from only 90 views, using (b) FBP and no prior resulting in streaks, SSIM=0.48 (c) l1-ls resulting in blurred bone structures (reasons discussed in Sec.
-5 of our supplementary material~\cite{supp_paper}), SSIM=0.35 and (d) uniform prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM=0.55.
+\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/tv_lambdaTV_0.036.png}}\hfill
+\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
+\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
+\caption{\small{ Reconstruction of `test' (slice 7) from Fig.~\ref{fig:RFA2_test_object-prior} from only 30 views, using (b) FBP and no prior resulting in streaks, SSIM=0.73 (c) TV resulting in blurred bone structures, SSIM=0.91 and (d) spatially varying object-prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM=0.95.
 The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
-All SSIM values are computed for this RoI.}}
+All SSIM values are computed for this RoI.
+(e) shows the computed weights map (defined later in the paper) used for reconstruction.
+Darker intensities indicate lower weights to prior as these are the regions of new changes.}}
 \label{fig:RFA2_very_few_views}
-\end{figure}
-\begin{itemize}
-\item \textbf{Observing details of the ablation}, we choose slices 1-7 as our object-prior and reconstruct slice 8 from 120 views, i.e., a somewhat higher number of views this time.
-Fig.~\ref{fig:RFA2_few_views} shows the reconstructions of slice 8 by different methods.
-We see that the spatially-varying prior reconstruction brings in the advantage of the prior without adversely affecting the reconstruction of new regions.
-  \end{itemize}
-%-------RFA2 moderate views
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
-\subcaptionbox{Uniform prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/plain_pca.png}}
-\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
-\subcaptionbox{Weights map}{\includegraphics[width=0.275\columnwidth]{../images/tmh/RFA2/few_views/weights_colormap.png}}
-\caption[Representative results-2]{\textbf{Goal: Observe details of new changes.} Reconstruction of slice 8 of Fig.~\ref{fig:RFA2_test_object-prior} from 120 views, using (b) FBP with SSIM=0.50 (c) l1-ls with SSIM=0.46 and (d) uniform prior, with SSIM=0.51 (\emph{notice dominance of the prior: a prominent residual shadow of the needle which was present in the object-prior, but not present in the test image}), and (e) spatially-varying prior with SSIM=0.56 (\emph{notice that the dominance of the prior is significantly controlled}).
-The region enclosed in green rectangle is our RoI as it contains both the new position of the needle and some background.
-The SSIM is computed in this RoI.
-(f) shows the computed weights map (defined later in the paper) used for reconstruction.
-Darker intensities indicate lower weights to prior as these are the regions of new changes.}
-\label{fig:RFA2_few_views}
- \vspace{-9mm}
 \end{figure}
@@
 
- \begin{equation}
-   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
-\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
-J_1(\boldsymbol{\theta,\alpha}) = \lVert\boldsymbol{\mathcal{R} x}- \boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1+\lambda_2\lVert\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k)\rVert_2^2.
-\label{Eq:main_prior}
-\end{equation}
 Here, $\lambda_1$, $\lambda_2$ are tunable weights given to the sparsity and prior terms respectively. The unknowns $\boldsymbol{\theta}$ and $\boldsymbol{\alpha}$
 are solved by alternately minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{\theta})$ using a fixed $\boldsymbol{\alpha}$, and $J_{\boldsymbol\theta}(\boldsymbol{\alpha})$ using the resultant $\boldsymbol{\theta}$, where
-\begin{align}
-J_{\boldsymbol{\alpha}}(\boldsymbol{\theta}) &\triangleq \lVert\boldsymbol{\mathcal{R} x- y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1+\lambda_2\lVert\boldsymbol{x} - (\boldsymbol{\mu + V\alpha})\rVert_2^2, \\
-J_{\boldsymbol\theta}(\boldsymbol{\alpha}) &\triangleq \lVert\boldsymbol{\Upsilon\theta} - (\boldsymbol{\mu + V\alpha})\rVert_2^2.
-\end{align}
+
 $\boldsymbol{\theta}$ is solved for using the basis pursuit CS solver, (l1-ls)~\cite{l1ls}. Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
-\begin{equation}
-\boldsymbol{\boldsymbol{\alpha}} = \boldsymbol{V}^T(\boldsymbol{\Upsilon \theta} -\boldsymbol{\mu}).
-\end{equation}
+
 %Optimal values of $\lambda_1, \lambda_2$ must be empirically chosen \textit{a priori}, based on the reconstructions of one of the template volumes (see also Sec.~\ref{sec:discussion}).
@@
 
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.185\columnwidth]{../images/okra/test.png}}}\hfill
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
-\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\caption{3D reconstruction of the okra from $10\%$ projection
-  views (b) has strong streak artefacts, (c) blurred (reasons discussed in Sec.
-5 of our supplementary material~\cite{supp_paper}), (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
-\label{fig:okra_3D_results_uniform}
-\end{figure}
-
-%---------------------------------------
-\begin{table}[!h]
-  \centering
-  \caption{SSIM of the full reconstructed okra volume by various methods. The SSIM of ground-truth (ideal reconstruction) is 1.}
-\begin{tabular}{|l|c|c|c|}
-\hline
-                   &  \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{full Volume} &  0.83        &  0.87       & \textcolor{red}{0.89}                                                                                   \\ \hline
-\end{tabular}
-\label{table:okra_ssim_full_volume}
-\end{table}
 %----------------------------------------------------
@@
 
- %-----------------------------sprouts 3D results
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.29\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{FDK}
-    \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{l1-ls}
-     \end{subfigure}\\
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{Uniform Prior}
-     \end{subfigure}
-     \caption{3D reconstruction of sprouts from $2.5\%$ projection
-       views (b, c) have poor details (d) no new information detected
-       (the prior dominates as can be seen in the blue and red
-       regions) and (e) new information detected in the regions of
-       interest. The reconstructed volumes can be viewed in the supplementary material
-       ~\cite{supp_paper}.} 
-\label{fig:sprouts_3D_results_uniform}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-
-\begin{table}
-  \centering
-  \caption{SSIM of the full reconstructed sprouts volume by various methods. The SSIM of ground-truth (ideal reconstruction) is 1.}
-\begin{tabular}{|l|c|c|c|c|}
-\hline
-                   &  \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{Full volume}  & 0.91        & 0.82       & \textcolor{red}{0.95}                                                                                                                       \\ \hline
-\end{tabular}
-\label{table:sprouts_ssim_full_volume}
-\end{table}
 %----------------------------------------------------------------------
@@
 %\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
-J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
+J_3(\boldsymbol{x},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\\ \lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
 \label{eq:spatially-varying_prior}
 \end{equation}
+\begin{align}
+J_{\boldsymbol{\alpha}}(\boldsymbol{\x}) &\triangleq \lVert\boldsymbol{\mathcal{R} x- y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\lambda_2\lVert(\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2, \\
+J_{\boldsymbol{x}}(\boldsymbol{\alpha}) &\triangleq \lVert\boldsymbol{\boldsymbol{W}(\boldsymbol{x}} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2.
+\end{align}
+
 The key to our method is the discovery of a diagonal weights
@@
     \begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
+        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/potato/post_tci/testIm_paper.png}}
 \captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_fbp30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_fbp30.png}
         \caption{FBP}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_dct30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_cs_dct30.png}
         \caption{(l1-ls)-DCT}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_cs_wavelet30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_cs_wavelet30.png}
         \caption{(l1-ls)-Haar}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_art30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_art30.png}
         \caption{ART}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sart30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_sart30.png}
         \caption{SART}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_sirt30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_sirt30.png}
         \caption{SIRT}
@@
         \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weightsIm_all_methods30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_tv30.png}
+        \caption{TV}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_all_methods30.png}
         \caption{combined}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/fbp.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/fbp.png}
         \caption{FBP}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_dct.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/cs_dct.png}
         \caption{(l1-ls)-DCT}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_wavelet.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/cs_wavelet.png}
         \caption{(l1-ls)-Haar}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/art.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/art.png}
         \caption{ART}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/sart.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/sart.png}
         \caption{SART}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/sirt.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/sirt.png}
         \caption{SIRT}
@@
         \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/weighted_pca_all_methods30.png}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/tv.png}
+        \caption{TV}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weighted_pca_all_methods30.png}
         \caption{combined}
@@
 The SSIM of ground-truth (ideal reconstruction) is 1, and these are computed within the red RoI of the test image shown in Fig.~\ref{fig:potato_test}.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
 \hline
- Fig.~\ref{fig:reconstructions_diff_methods}  & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} \\\hline
-\textbf{red RoI}  & 0.50 & 0.60  & 0.45 & 0.47 & 0.56 & 0.52 & \textcolor{red}{0.76} \\ \hline
+ Fig.~\ref{fig:reconstructions_diff_methods}  & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
+\textbf{red RoI}  & 0.51 & 0.59  & 0.53 & 0.52 & 0.60 & 0.52 & 0.81 &\textcolor{red}{0.74} \\ \hline
 \end{tabular}
@@
 
-%----------------------------------------------------
-
 \begin{figure}[!h]
 \centering
-\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.185\columnwidth]{../images/okra/testCropped.png}}}\hfill
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
-\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/prior_weighted_cropped.png}}
-\caption{3D reconstruction of the okra from $10\%$ projection
-  views (b) has strong streak artefacts, (c) blurred, (d) no new
-  information detected (prior dominates -- the deformity from the prior
-  shows up as a false positive) and (e) new information detected (no deformities
-  corresponding to red and green regions) while simultaneously
-  reducing streak artefacts. The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/input_roi.png}}}
+\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/FBP_cropped.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/TV_cropped.png}}
+%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/weighted_prior_cropped.png}}
+\caption{Reconstruction of 2D okra from 48 projection views
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
+The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
 \label{fig:okra_3D_results}
@@
 
-%--------------------------------------zoomed okra
+%----------------------------------------------------
 
@@
 \centering
-\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/input_cropped.png}}\hfill
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/FDK_cropped.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/CS_cropped.png}}\hfill
-\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/zoomed/weighted_prior_cropped.png}}
-\caption{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
-  shows up as a false positive) and (e) new information detected (no deformities
- ).}
-\label{fig:okra_zoomed_3D_results}
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.29\columnwidth]{../images/sprouts/post_TCI/20_views/testIm.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/fbp.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/tv_lambdaTV_0.100.png}}
+%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
+\caption{Reconstruction of 2D sprouts from 20 projection views
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
+The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
+\label{fig:sprouts3D_results}
 \end{figure}
@@
   \centering
-  \caption{SSIM of 3D RoI of reconstructed okra volumes from various
-    methods. Each RoI spans 7 consecutive slices where the test is
+  \caption{SSIM of reconstructed okra from various
+    methods. For 3D, the RoI spans 7 consecutive slices where the test is
     different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
@@
 \hline &
-\textbf{FDK} & \textbf{l1-ls} &
-\textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior +
-    l1-ls\end{tabular}} &
-\textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior +
-    l1-ls\end{tabular}} \\ \hline \textbf{red RoI} & 0.74
-& 0.84 & 0.85 & \textcolor{red}{0.88} \\ \hline \textbf{green RoI} & 0.81 & 0.82 & 0.77 & \textcolor{red}{0.83}
+\textbf{Backprojection} & \textbf{TV} &
+\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
+    TV\end{tabular}} \\ \hline \textbf{2D} & 0.46
+& 0.50 & \textcolor{red}{0.74} \\ \hline \textbf{3D} & 0.69 & 0.74 & \textcolor{red}{0.78}
 \\ \hline
@@
     \begin{subfigure}[b]{0.29\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/testIm.png}}
 %\captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
+        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/fbp.png}
 %\captionsetup{labelformat=empty}
-        \caption{FDK}
+        \caption{FDK, no prior}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
+        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/tv_lambdaTV_0.100.png}
 %\captionsetup{labelformat=empty}
-        \caption{l1-ls}
+        \caption{TV, no prior}
      \end{subfigure}\\
+%\quad
+%    \begin{subfigure}[b]{0.3\linewidth}
+%        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
+%\captionsetup{labelformat=empty}
+%        \caption{Uniform\\ Prior}
+%     \end{subfigure}
 \quad
     \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{Uniform\\ Prior}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
+        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}
 %\captionsetup{labelformat=empty}
@@
     %\quad
-     \caption{3D reconstruction of sprouts from $2.5\%$ projection views
-   (b, c) have poor details (d) no new information detected (the
-   prior dominates as can be seen in the blue and red regions) and
-   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.} 
+     \caption{Reconstruction of 2D sprouts from 20 projection views
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
+The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
 \label{fig:sprouts_3D_results}
@@
 
-%--------------------------------------zoomed sprouts
-
-\begin{figure}[!h]
-  \centering
-  \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_croppedBig.png}}\hfill
-    \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_croppedBig.png}}\hfill
-      \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_croppedBig.png}}\hfill
-        \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_croppedBig.png}}\hfill
-        \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_croppedBig.png}}\hfill
-          \subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_marked.png}}\hfill
-            \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_marked.png}}\hfill
-              \subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_marked.png}}\hfill
-                \subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_marked.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_marked.png}}
-\caption{Zoomed-in portion $(41 \times 36)$ containing the RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods.
-The images of the bottom row are the same as respective images of the top row, with regions marked additionally.
-(a) the test showing 3 distinct structures (in red here) (b) 3 structures recovered with poor contrast, (c) structures indistinguishable, (d) only two strong structures seen and (e) there is a hint of a third structure too with better contrast.}
-\label{fig:sprouts_zoomed_3D_results}
-\end{figure}
-
 %--------------------------------------------------------------
@@
   \centering
-\caption{SSIM of 3D RoI of reconstructed sprouts volumes from various methods. The RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects.}
+  \caption{SSIM of reconstructed sprouts from various
+    methods. For 3D, the RoI spans 7 consecutive slices where the test is
+    different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
-\hline
-                   & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior + l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}c@{}}Spatially\\Varying\\prior + l1-ls\end{tabular}} \\ \hline
-\textbf{red RoI}   & 0.85        & 0.86       & 0.83                                                               & \textcolor{red}{0.88}                                                                  \\ \hline
+\hline &
+\textbf{Backprojection} & \textbf{TV} &
+\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
+    TV\end{tabular}} \\ \hline \textbf{2D} & 0
+& 0 & \textcolor{red}{0} \\ \hline \textbf{3D} & 0.67 & 0.73 & \textcolor{red}{0.82}
+\\ \hline
 \end{tabular}
@@
 \end{table}
+
 The test volume was reconstructed from partial set of 45
@@
 
-\subsection{\textbf{An alternate imaging and reconstruction protocol}}
-%In all our previous results, we had assumed that in a longitudinal study of $n$ scans, the first $n-1$ scans are images with sufficient views and their high-quality reconstructions are used as templates.
-The $n^{th}$ scan alone is imaged with few-views and reconstructed using our method.
-Earlier in Sec.~\ref{sec:tmh}, we discussed that the imaging protocols fell under two categories depending on the final goal (tracking or observing details): very few-view imaging and moderate view imaging.
-In both cases, the templates used were of high-quality.
-However, in a realistic scenario,  we may prefer to gradually increase from few-view to moderate views as the probe gradually approaches the tumor site.
-For the reconstruction of $n^{\textrm{th}}$ slice i.e., slice imaged at time $t=n$, the few-view reconstructions of the previously acquired slices can be used as templates.
-However, the first scan must always be taken with large number of views because it acts as a reference template to start with.
-Table.~\ref{tab:realistic_imaging_protocol} summarizes this protocol for the dataset of Fig~\ref{fig:RFA2_test_object-prior}, and Fig.~\ref{fig:RFA2_new_protocol} shows the reconstructions when this realistic protocol is used.
-
-%-------------------- RFA 2 new protocol
-\begin{figure}[!h]
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
-\captionsetup{labelformat=empty}       
- \caption{image-1}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_1.png}
-\captionsetup{labelformat=empty}       
- \caption{image-1 recon}
-    \end{subfigure}
- \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
-\captionsetup{labelformat=empty}       
- \caption{image-2}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_2.png}
-\captionsetup{labelformat=empty}       
- \caption{image-2 recon}
-    \end{subfigure}
- \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
-\captionsetup{labelformat=empty}       
- \caption{image-3}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_3.png}
-\captionsetup{labelformat=empty}       
- \caption{image-3 recon}
-    \end{subfigure}
- \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
-\captionsetup{labelformat=empty}       
- \caption{image-4}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_4.png}
-\captionsetup{labelformat=empty}       
- \caption{image-4 recon}
-    \end{subfigure}
- \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
-\captionsetup{labelformat=empty}       
- \caption{image-5}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_5.png}
-\captionsetup{labelformat=empty}       
- \caption{image-5 recon}
-    \end{subfigure}
- \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6.png}
-\captionsetup{labelformat=empty}       
- \caption{image-6}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_6.png}
-\captionsetup{labelformat=empty}       
- \caption{image-6 recon}
-    \end{subfigure}
- \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
-\captionsetup{labelformat=empty}       
- \caption{image-7}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/result_image_7.png}
-\captionsetup{labelformat=empty}       
- \caption{image-7 recon}
-    \end{subfigure}
- \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/testIm.png}
-\captionsetup{labelformat=empty}       
- \caption{image-8}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/weighted_pca_all_methods_kk_0_01.png}
-\captionsetup{labelformat=empty}       
- \caption{image-8 recon}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/new_protocol/weightsIm_all_methods_kk_0_01.png}
-\captionsetup{labelformat=empty}       
- \caption{weights map}
-    \end{subfigure}
-       \caption{Reconstructions (referred as `recon') of all slices of  of Fig.~\ref{fig:RFA2_test_object-prior} using the suggested protocol in Table.~\ref{tab:realistic_imaging_protocol}.
-The last image is the weights map corresponding to the reconstruction of image-8.
-The new changes in the tumor site is picked up by the weights map.
-}
-\label{fig:RFA2_new_protocol}
-\end{figure}
-
-\begin{table}[!h]
-  \caption{Suggested multi-step imaging protocol for the CT-guided radio-frequency ablation dataset of Fig~\ref{fig:RFA2_test_object-prior}.
-The number of views is gradually increased as the probe approaches the tumor site.
-Only the first scan is taken with large number of views to act as a reference template.
-The few-view reconstructions of a slice acts as the object-prior for the reconstruction of slice being imaged at next time instant.}
-  \vspace{2mm}
-\centering\small\setlength\tabcolsep{2pt}
-\hspace*{-1cm}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Slice being\\ imaged at\\ time t\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Probe distance from\\ tumor or \\ ablation stage\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ imaging\\ views\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Reconstruction\\ protocol: type \\ of prior\end{tabular}} \\ \hline
-Slice t=1 & Very far from tumor & 360 & l1-ls \\ \hline
-Slice t=2 & Sufficiently far from tumor & 40 & Uniform \\ \hline
-Slice t=3 & Far from tumor & 50 & Uniform \\ \hline
-Slice t=4 & Near tumor & 60 & Uniform \\ \hline
-Slice t=5 & Sufficiently near tumor & 70 & Uniform \\ \hline
-Slice t=6 & Very near tumor & 80 & Uniform \\ \hline
-Slice t=7 & Very near tumor & 90 & Uniform \\ \hline
-Slice t=8 & During, after ablation & 120 & Spatially-Varying \\ \hline
-\end{tabular}\hspace*{-1cm}
-\label{tab:realistic_imaging_protocol}
-\end{table}
 %-----------------------------------------
@@
 \centering
-\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.185\columnwidth]{../images/potato/testIm_green.png}}}\hfill
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm_new.png}}\hfill
-\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
-\caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts.
-The reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
+\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/testIm_paper.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_lambdaTV_0.05.png}}
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
+\caption{Reconstruction of the 2D-potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.
+The 3D reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
 \label{fig:potato_3D_results_A}
 \end{figure}
-%------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \begin{table}[!h]
-\caption{SSIM of 3D reconstructed potato volumes from various
-  methods. Each RoI spans 7 consecutive slices where the test is
-  different from all of the previously scanned objects. In this
-  dataset alone, the new changes are in a homogeneous
-  background. Hence, the FDK performs the best when the RoI alone is
-  considered. However, it fails when the entire volume is considered
-  due to the prominent streaky artefacts.}
+  \centering
+  \caption{SSIM of reconstructed potato from various
+    methods. For 3D, the RoI spans 7 consecutive slices where the test is
+    different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
 \hline &
-\textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} &
-\textbf{FDK} & \textbf{l1-ls} &
-\textbf{\begin{tabular}[c]{@{}c@{}}Uniform\\prior\\+
-    l1-ls\end{tabular}} &
-\textbf{\begin{tabular}[c]{@{}c@{}}Spatially-Varying\\prior\\+
-    l1-ls\end{tabular}} \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}} & 1
-(ideal) & \textcolor{red}{0.94} & 0.88 & 0.71 & 0.85 \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1
-(ideal) & \textcolor{red}{0.92} & 0.91 & 0.87 & 0.88 \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}cyan RoI\\volume\end{tabular}} & 1
-(ideal) & 0.88 & \textcolor{red}{0.94} & 0.92 & 0.89 \\ \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1
-(ideal) & 0.74 & 0.81 & \textcolor{red}{0.86} & \textcolor{red}{0.86}
+\textbf{Backprojection} & \textbf{TV} &
+\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
+    TV\end{tabular}} \\ \hline \textbf{2D} & 0.52
+& 0.92 & \textcolor{red}{0.97} \\ \hline \textbf{3D} & 0.58 & 0.75 & \textcolor{red}{0.84}
 \\ \hline
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_10normalized.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}
+        \caption{k=5}
+     \end{subfigure}     
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}
         \caption{k=10}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_50normalized.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}
+        \caption{k=20}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}
+        \caption{k=30}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}
+        \caption{k=40}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}
         \caption{k=50}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_90normalized.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}
+        \caption{k=60}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}
+        \caption{k=70}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}
+        \caption{k=80}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}
         \caption{k=90}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_130normalized.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}
+        \caption{k=100}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}
         \caption{k=130}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_170normalized.png}
-        \caption{k=170}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_210normalized.png}
-        \caption{k=210}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_250normalized.png}
-        \caption{k=250}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_290normalized.png}
-        \caption{k=290}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_330normalized.png}
-        \caption{k=330}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_370normalized.png}
-        \caption{k=370}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weightsIm_410normalized.png}
-        \caption{k=410}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=1.15\textwidth]{../images/okra/2D_okra/weightsIm_450normalized_colorbar.png}
-        \caption{k=450}
      \end{subfigure}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca10_colorIm.png}
-        \caption{k=10,\\ SSIM = 0.944}
-     \end{subfigure}     
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca50.png}
-        \caption{k=50,\\ SSIM = 0.959}
-     \end{subfigure} 
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca90.png}
-        \caption{k=90,\\ SSIM = 0.955}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca130.png}
-        \caption{k=130,\\ SSIM = 0.948}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca170.png}
-        \caption{k=170,\\ SSIM = 0.942}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca210.png}
-        \caption{k=210,\\ SSIM = 0.936}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca250.png}
-        \caption{k=250,\\ SSIM = 0.931}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca290.png}
-        \caption{k=290,\\ SSIM = 0.926}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca330.png}
-        \caption{k=330,\\ SSIM = 0.922}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca370.png}
-        \caption{k=370,\\ SSIM = 0.918}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca410.png}
-        \caption{k=410,\\ SSIM = 0.915}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/2D_okra/weighted_pca450.png}
-        \caption{k=450,\\ SSIM = 0.911}
-     \end{subfigure}
-    \caption{2D reconstructions showing stable reconstructions for large variations in $k$.
-The SSIM values for all images are computed within the red RoI (shown in (a)), the region where the test is different from all of the previously scanned objects.}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}
+        \caption{k=5,\\ SSIM = 0.79}
+     \end{subfigure}     
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}
+        \caption{k=10,\\ SSIM = 0.78}
+     \end{subfigure} 
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}
+        \caption{k=20,\\ SSIM = 0.76}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}
+        \caption{k=30,\\ SSIM = 0.74}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}
+        \caption{k=40,\\ SSIM = 0.72}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}
+        \caption{k=50,\\ SSIM = 0.63}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}
+        \caption{k=60,\\ SSIM = 0.61}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}
+        \caption{k=70,\\ SSIM = 0.59}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}
+        \caption{k=80,\\ SSIM = 0.58}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}
+        \caption{k=90,\\ SSIM = 0.56}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}
+        \caption{k=100,\\ SSIM = 0.55}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
+        \caption{k=130,\\ SSIM = 0.53}
+     \end{subfigure}
+    \caption{2D reconstructions for varying values of $k$.
+The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_3D_results}(a)), the region where the test is different from all of the previously scanned objects.}
 \label{fig:reconstructions_as_k_varies}

### 2021-08-13 paper/post_tci.tex
Added all new post-TCI images; updated sprouts results in paper

@@
 \centering
-	\includegraphics[width=0.45\textwidth]{../images/story/story.png}
+	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
         \caption{Illustration of the use of various priors in 
@@
 \centering
-\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/very_few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/fbp.png}}\hfill
-\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/tv_lambdaTV_0.036.png}}\hfill
-\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
-\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
+\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
+\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
+\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
+\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
 \caption{\small{ Reconstruction of `test' (slice 7) from Fig.~\ref{fig:RFA2_test_object-prior} from only 30 views, using (b) FBP and no prior resulting in streaks, SSIM=0.73 (c) TV resulting in blurred bone structures, SSIM=0.91 and (d) spatially varying object-prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM=0.95.
@@
 \centering
-\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/input_roi.png}}}
-\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/FBP_cropped.png}}
-\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/TV_cropped.png}}
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
+\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/FBP_cropped.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/TV_cropped.png}}
 %\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/48_views/weighted_prior_cropped.png}}
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
 \caption{Reconstruction of 2D okra from 48 projection views
@@
 \centering
-\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.29\columnwidth]{../images/sprouts/post_TCI/20_views/testIm.png}}}
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/fbp.png}}
-\subcaptionbox{TV, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/tv_lambdaTV_0.100.png}}
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.29\columnwidth]{../images/sprouts/post_TCI/2D/20_views/testIm_roi.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
 %\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
+\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
 \caption{Reconstruction of 2D sprouts from 20 projection views
@@
  %-----------------------------sprouts 3D results
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.29\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/testIm.png}}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/fbp.png}
-%\captionsetup{labelformat=empty}
-        \caption{FDK, no prior}
-    \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/tv_lambdaTV_0.100.png}
-%\captionsetup{labelformat=empty}
-        \caption{TV, no prior}
-     \end{subfigure}\\
-%\quad
-%    \begin{subfigure}[b]{0.3\linewidth}
-%        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
-%\captionsetup{labelformat=empty}
-%        \caption{Uniform\\ Prior}
-%     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/post_TCI/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}
-%\captionsetup{labelformat=empty}
-        \caption{Spatially-Varying\\ prior}
-    \end{subfigure}
-    %\quad
-     \caption{Reconstruction of 2D sprouts from 20 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
-The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
-\label{fig:sprouts_3D_results}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
 
@@
 \textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
-    TV\end{tabular}} \\ \hline \textbf{2D} & 0
-& 0 & \textcolor{red}{0} \\ \hline \textbf{3D} & 0.67 & 0.73 & \textcolor{red}{0.82}
+    TV\end{tabular}} \\ \hline \textbf{2D} & 0.67
+& 0.82 & \textcolor{red}{0.86} \\ \hline \textbf{3D} & 0.67 & 0.73 & \textcolor{red}{0.82}
 \\ \hline
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}
         \caption{k=5}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}
         \caption{k=10}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}
         \caption{k=20}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}
         \caption{k=30}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}
         \caption{k=40}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}
         \caption{k=50}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}
         \caption{k=60}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}
         \caption{k=70}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}
         \caption{k=80}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}
         \caption{k=90}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}
         \caption{k=100}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}
         \caption{k=130}
@@
     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}
         \caption{k=5,\\ SSIM = 0.79}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}
         \caption{k=10,\\ SSIM = 0.78}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}
         \caption{k=20,\\ SSIM = 0.76}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}
         \caption{k=30,\\ SSIM = 0.74}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}
         \caption{k=40,\\ SSIM = 0.72}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}
         \caption{k=50,\\ SSIM = 0.63}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}
         \caption{k=60,\\ SSIM = 0.61}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}
         \caption{k=70,\\ SSIM = 0.59}
@@
   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}
         \caption{k=80,\\ SSIM = 0.58}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}
         \caption{k=90,\\ SSIM = 0.56}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}
         \caption{k=100,\\ SSIM = 0.55}
@@
    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
         \caption{k=130,\\ SSIM = 0.53}

### 2021-08-20 paper/post_tci.tex
changes in text in abstract, intro, related-work, Fig.1, Fig.2, and marked text changes in old TCI

@@
   from previously existing longitudinal scans of the same object
-  (`object-prior'), helps in the reconstruction from the current
-  measurements of that object (`test'), while requiring significantly
-  fewer updating measurements. In this work, we improve the state of
-  the art by proposing the context under which priors can be
-  effectively used based on the final goal of the application at hand.
+  (`object-prior') helps in the reconstruction of the current object (`test')  from its
+  significantly fewer measurements. A common problem with these techniques is
+  the strong influence of object-priors in the reconstruction of new regions in the test.
+  In this work, we mitigate this problem by first estimating the location of new regions and
+  then imposing object-prior in \textit{only} the other old regions which are similar to the prior.
 
@@
   angles (`views'), it is challenging when the number of views is
-  limited.
-
-  If the goal is to track the changes while simultaneously reducing
-  sub-sampling artefacts, we propose (1) acquiring measurements from
-  an \emph{extremely small} number of views and using a
-  \emph{`uniform'} prior-based reconstruction. If the goal is to
-  observe \textbf{details} of new changes, we propose (2) acquiring
-  measurements from a \emph{moderate} number of views (albeit, still
-  sub-Nyquist), and using a more involved reconstruction routine. We
+  limited (sub-Nyquist). We
   show that in the latter case, a `spatially-varying' technique is
@@
   tested the efficacy of our method on synthetic as well as real
-  projection data. The results demonstrate the use of both uniform and
-  spatially-varying priors in different scenarios. Our methods
-  significantly improve the overall quality of the reconstructed data
+  projection data, in both 2D and 3D. Our method
+  significantly improves the overall quality of reconstructed data
   while minimizing the number of measurements needed for imaging in
@@
 \begin{IEEEkeywords}
-Limited-view tomographic reconstruction, compressed sensing, priors, longitudinal studies.
+Limited-view tomographic reconstruction, regularization priors, object priors, longitudinal studies.
 \end{IEEEkeywords}
@@
 
-In conventional data acquisition techniques, the tomographic
+In conventional data acquisition techniques, tomographic
 measurements $\boldsymbol{y}$ are acquired by sampling the physical
@@
 ideally above the Nyquist rate. In such a case when there are
-sufficient measurements, reconstruction using the conventional
+sufficient measurements, reconstruction using conventional
 filtered backprojection (FBP) suffices, as seen in
@@
 left (the details of this dataset is postponed to
-Section~\ref{sec:results_uniform_prior}).
-
-However, in the last decade, reconstruction from reduced views has
-been made possible by assuming the data to exhibit sparsity under
-certain mathematical transforms $\boldsymbol{\Upsilon}$ such as the
-wavelet transforms, or the Discrete Cosine Transform (DCT). This is
-known as sparsity prior and is the fundamental principle in the widely
-used Compressed Sensing (CS) technique~\cite{Donoho,introCS}.  There
-are multiple ways to incorporate the sparsity prior using CS. We use
-the LASSO (least absolute shrinkage and selection operator) which
-iteratively solves for the solution by penalizing a combination of
-least squares error and $L_1$-norm of the sparse coefficients
-$\boldsymbol{\theta}$ of the object $\boldsymbol{x}$. If $\boldsymbol{\Psi}$
-represents the sparsity basis, i.e., if $\boldsymbol{x} = \boldsymbol{\Psi\theta}$, and 
-$\boldsymbol{\mathcal{R}}$ represents the acquisition model, then the
-LASSO solution is described by one that minimizes
-
- \begin{equation}
-   TV(\boldsymbol{x}) = \sum_{i,j}\nabla_{ij}(\boldsymbol{x})
-   \label{Eq:definition_TV}
-\end{equation}
+Section~\ref{sec:datasets}).
+
+However, reconstruction from reduced views has
+been made possible by assuming the data to exhibit certain properties such as
+smoothness in image space, sparsity in gradient space~\cite{TV} or sparsity under
+certain mathematical transforms~\cite{Donoho,introCS} such as the Discrete Cosine Transform (DCT).  There are multiple such regularization priors and our work aims at significantly improving
+the reconstructions obtained from any of these methods.
+Hence, although our technique is agnostic to the type of regularization prior used, here we have used the total Variation (TV) method as part of our presented solution.
+If $\boldsymbol{\mathcal{R}}$ represents the acquisition model, then TV-regularized solution is described by one that minimizes a combination of
+least squares error and $TV$-norm  of the object $\boldsymbol{x}$. This is described by
 
@@
  \end{equation}
+
+ where the $TV$ norm is given by
+
+  \begin{equation}
+   TV(\boldsymbol{x}) = \sum_{i,j}\nabla_{ij}(\boldsymbol{x}).
+   \label{Eq:definition_TV}
+\end{equation}
+
  Fig.~\ref{fig:story}
- (second column) demonstrates the benefit of using sparsity prior when
+ (second column) demonstrates the benefit of using a regularization prior when
  the number of projection views is limited (100 views).
- We solve this cost function using the popular l1-regularized least
- squares (l1-ls) package available in~\cite{l1ls}, and choose DCT as
- our sparsity basis $\boldsymbol{\Upsilon}$. We had observed no significant improvement if, say, the wavelet transform were instead used as the basis.
+ We solve this cost function using an optimal first-order method for large scale TV regularization
+ presented in~\cite{TVReg}  and available in~\cite{TVReg-lib}.
 
@@
  When the number of views is significantly reduced (this paper), the
- sparsity prior alone is not sufficient.  In such cases additional
+ regularization prior alone is not sufficient.  In such cases additional
  information (`object-prior') specific to the current
@@
  interior. As seen in Fig.~\ref{fig:story} (last column, 30 views) our
- method uses the set $S$ \emph{uniformly} by creating an
- eigenspace representation (Section~\ref{sec:method_uniform_prior}).
+ method uses the set $S$ by creating an
+ eigenspace representation (Section~\ref{sec:method_spatially_varying_prior}).
 
@@
  still uses \textit{all} the previous scans in the set $S$, without
- using simply the prior scan, or endeavoring to find the ``right''
+ using the prior scan \textit{as is}, or endeavoring to find the ``right''
  prior.
@@
  are described in Section~\ref{sec:datasets}. Section~\ref{sec:tmh}
- demonstrates the utility of both the uniform and spatially-varying
- methods on a longitudinal medical dataset. We now move to the
- details. Section~\ref{sec:method_uniform_prior} describes the
- construction of the uniform eigenspace prior, followed by the
- corresponding results in real and synthetic 3D biological datasets in
- Section~\ref{sec:results_uniform_prior}. Section~\ref{sec:method_spatially_varying_prior}
- describes how the uniform prior needs to be modified when accurate
- details of new changes are to be observed. A spatially-varying
- technique offers a solution, the results of which are presented in
+ demonstrates the utility of our
+ method on a longitudinal medical dataset. We now move to the
+ details. Section~\ref{sec:method_spatially_varying_prior}
+ describes the
+ construction of a uniform eigenspace prior and computation of a spatially-varying map in order to preserve new changes in the test. 
+ The results of are presented in
  Section~\ref{sec:results_spatially_varying_prior}. Section~\ref{sec:discussion}
@@
 is known to be sparse, the `total variation' method, as used
-in~\cite{Li2015,Polak2017}, can be applied.  In a more generalized
-application scenario, like the ones addressed in this paper, any
-information about the regions of interest is not known, and such
-techniques have limited applicability.
+in~\cite{Li2015,Polak2017}, can be applied.  However, as shown earlier
+in Fig.~\ref{fig:story}, these regularization priors are not sufficient when very few
+views are acquired, thus needing information from stronger priors such as those obtained from previous scans of the same or similar object.
 
@@
 feasible. A longitudinal study will necessarily require reconstruction
-results after acquisition of each set of measurements
+results after acquisition of each set of measurements.
 
@@
 the final estimate of the test. Such methods have been proposed
-in~\cite{Pourmorteza2015,Lee2012}. However, the reconstruction of the
+in~\cite{Pourmorteza2015,Lee2012}. Here the reconstruction of the
 difference image will inherently contain sub-sampling artefacts, and
@@
 unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and
-also make use of the additional information available in the multiple
+also make use of the additional information available in multiple
 priors. Our technique also has the advantage of not requiring any
@@
     \end{subfigure}     
-     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver.
+     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 7 scan volumes of a longitudinal study dataset of the liver.
 Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.}
@@
 %---------------------------------Uniform section---------------------
-\section{Uniform prior-based reconstruction}
-\label{sec:method_uniform_prior}
+\section{Spatially-Varying prior-based reconstruction}
+\label{sec:method_spatially_varying_prior}
 Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform  prior-based reconstruction since we are extending this algorithm to 3D reconstructions as part of this work.
@@
 
- \section{Results: Reconstruction by uniform prior}
- \label{sec:results_uniform_prior}
-
- The proposed method has been validated on new scans of biological
- specimens in a longitudinal setting. 
- %We emphasize that in
-% most of the literature on tomographic reconstruction, the results are
- %shown on reconstruction from projections \emph{simulated} from 3D
- %volumes. This is because most CT scanners do not reveal the raw
- %projections, and instead output only the full reconstructed
- %volumes. Moreover, the process of conversion from the projections to
- %the full volumes is proprietary.
-
-%In all figures in this section, `uniform prior' refers to optimizing Eq.~\ref{eq:spatially-varying_prior} with $\boldsymbol{W}(x,y,z)=1$.
-%----------------------------------------------------------
-%-------------------------------------------------
-\subsubsection{\textbf{Okra}}
-\label{Sec:okra_uniform}
-The test volume was reconstructed from a partial set of
-45 projections, i.e., $10\%$ of the projection views from which ground
-truth was reconstructed.
- One of the slices of the reconstructed volumes is shown in
- Fig.~\ref{fig:okra_3D_results_uniform}. The SSIM values presented in
- Table~\ref{table:okra_ssim_full_volume} show that the presence of a
- uniform object prior significantly improves the overall
- reconstruction in comparison with the usage of sparsity prior alone.
- The selected 3D ground truth of template volumes, the test volume as
- well as the 3D reconstructions can be seen in the supplementary
- material~\cite{supp_paper}.
-
-%----------------------------------------------------
-\subsubsection{\textbf{Sprouts}}
-\label{Sec:sprouts}
-The test volume was reconstructed from partial set of 45
-projections, i.e., $2.5\%$ of the projection views from which ground
-truth was reconstructed.
-One of the slices of the reconstructed
- volumes is shown in
- Fig.~\ref{fig:sprouts_3D_results_uniform}. Table~\ref{table:sprouts_ssim_full_volume}
- shows the SSIM of the full reconstructed volumes.  Here again, the
- presence of a uniform object prior significantly improves the overall
- reconstruction in comparison with the usage of sparsity prior alone.
- The selected 3D ground truth of template volumes, the test volume as
- well as the 3D reconstructions can be seen in the supplementary
- material~\cite{supp_paper}.
-
 %----------------------------------------------------------------------
-\section{Spatially-Varying prior-based reconstruction}
-\label{sec:method_spatially_varying_prior}
 

### 2021-08-27 paper/post_tci.tex
draft-1

@@
   from previously existing longitudinal scans of the same object
-  (`object-prior') helps in the reconstruction of the current object (`test')  from its
-  significantly fewer measurements. A common problem with these techniques is
-  the strong influence of object-priors in the reconstruction of new regions in the test.
-  In this work, we mitigate this problem by first estimating the location of new regions and
-  then imposing object-prior in \textit{only} the other old regions which are similar to the prior.
+  (`object-prior') helps in the reconstruction of the current object
+  (`test') from its significantly fewer measurements. A common problem
+  with these techniques is the strong influence of object-priors in
+  the reconstruction of new regions in the test.  In this work, we
+  mitigate this problem by first estimating the location of new
+  regions and then imposing object-prior in \textit{only} the other
+  old regions which are similar to the prior.
 
@@
   angles (`views'), it is challenging when the number of views is
-  limited (sub-Nyquist). We
-  show that in the latter case, a `spatially-varying' technique is
-  appropriate in order to prevent the prior from adversely affecting the
-  reconstruction of new structures that are absent in any of the
-  earlier scans. The reconstruction of new regions is safeguarded from
-  the bias of the prior by computing regional weights that moderate
-  the local influence of the priors. We are thus able to effectively
-  reconstruct both the old and the new structures in the test. We have
-  tested the efficacy of our method on synthetic as well as real
-  projection data, in both 2D and 3D. Our method
-  significantly improves the overall quality of reconstructed data
+  limited (sub-Nyquist). We show that in the latter case, a
+  `spatially-varying' technique is appropriate in order to prevent the
+  prior from adversely affecting the reconstruction of new structures
+  that are absent in any of the earlier scans. The reconstruction of
+  new regions is safeguarded from the bias of the prior by computing
+  regional weights that moderate the local influence of the priors. We
+  are thus able to effectively reconstruct both the old and the new
+  structures in the test. We have tested the efficacy of our method on
+  synthetic as well as real projection data, in both 2D and 3D. Our
+  method significantly improves the overall quality of reconstructions
   while minimizing the number of measurements needed for imaging in
@@
 Computed Tomography (CT) deals with the recovery of details of an
-object's interior
-from a limited set of projection data acquired by passing
-X-rays at different orientations (`views'). It is preferable to
-minimize the radiation exposed in order to prevent any potential
+object's interior from a limited set of projection data acquired by
+passing X-rays at different orientations (`views'). It is preferable
+to minimize the radiation exposed in order to prevent any potential
 damage to it and in order to reduce the acquisition time. Therefore,
@@
 
-In conventional data acquisition techniques, tomographic
-measurements $\boldsymbol{y}$ are acquired by sampling the physical
-object $\boldsymbol{x}$ uniformly with a substantial number of views,
-ideally above the Nyquist rate. In such a case when there are
-sufficient measurements, reconstruction using conventional
-filtered backprojection (FBP) suffices, as seen in
-Fig.~\ref{fig:story} (first column, 600 views). The figure shows the
-ground truth image (260$\times$260) of naturally growing sprouts at the top
-left (the details of this dataset is postponed to
-Section~\ref{sec:datasets}).
-
-However, reconstruction from reduced views has
-been made possible by assuming the data to exhibit certain properties such as
-smoothness in image space, sparsity in gradient space~\cite{TV} or sparsity under
-certain mathematical transforms~\cite{Donoho,introCS} such as the Discrete Cosine Transform (DCT).  There are multiple such regularization priors and our work aims at significantly improving
-the reconstructions obtained from any of these methods.
-Hence, although our technique is agnostic to the type of regularization prior used, here we have used the total Variation (TV) method as part of our presented solution.
-If $\boldsymbol{\mathcal{R}}$ represents the acquisition model, then TV-regularized solution is described by one that minimizes a combination of
-least squares error and $TV$-norm  of the object $\boldsymbol{x}$. This is described by
+In conventional data acquisition techniques, tomographic measurements
+$\boldsymbol{y}$ are acquired by sampling the physical object
+$\boldsymbol{x}$ uniformly with a substantial number of views, ideally
+above the Nyquist rate. In such a case when there are sufficient
+measurements, reconstruction using conventional filtered
+backprojection (FBP) suffices, as seen in Fig.~\ref{fig:story} (first
+column, 800 views). The figure shows the ground truth image
+(260$\times$260) of naturally growing sprouts at the top left (the
+details of this dataset is postponed to Section~\ref{sec:datasets}).
+
+However, reconstruction from reduced views has been made possible by
+assuming the data to exhibit certain properties such as smoothness in
+image space, sparsity in gradient space~\cite{TV} or sparsity under
+certain mathematical transforms~\cite{Donoho,introCS} such as the
+Discrete Cosine Transform (DCT).  There are multiple such
+regularization priors, of which we choose the total Variation (TV)
+method as a baseline for this work. If $\boldsymbol{\mathcal{R}}$
+represents the acquisition model, then TV-regularized solution is
+described by one that minimizes a combination of least squares error
+and $TV$-norm of the object $\boldsymbol{x}$. This is described by
 
@@
 
- where the $TV$ norm is given by
+ where the $TV$-norm is given by
 
   \begin{equation}
-   TV(\boldsymbol{x}) = \sum_{i,j}\nabla_{ij}(\boldsymbol{x}).
+   TV(\boldsymbol{x}) = \sum_{i,j}\nabla_{ij}(\boldsymbol{x}),
    \label{Eq:definition_TV}
@@
 
- Fig.~\ref{fig:story}
- (second column) demonstrates the benefit of using a regularization prior when
- the number of projection views is limited (100 views).
- We solve this cost function using an optimal first-order method for large scale TV regularization
- presented in~\cite{TVReg}  and available in~\cite{TVReg-lib}.
+  and $\nabla$ represents the gradient operator.
+
+ Fig.~\ref{fig:story} (second column) demonstrates the benefit of
+ using a regularization prior when the number of projection views is
+ limited (100 views).  We solve this cost function using an optimal
+ first-order method for large-scale TV regularization presented
+ in~\cite{TVReg} and available in~\cite{TVReg-lib}.
 
@@
         \caption{Illustration of the use of various priors in 
-          reconstruction as the number of views reduces. In all cases,
+          reconstruction as the number of views reduces. For all cases,
           the ground truth (260$\times$260) appears in the top left.
-          For extremely large number of views (800 views), the FBP
+          For extremely large number of views (800 views), FBP
           reconstruction (first column) is of very good quality
           (Structural Similarity Index Metric, SSIM=0.92). As the
-          number of views become limited (100 views), the
-          reconstruction using a general data-independent prior such as Total Variation (TV, middle column) is
+          number of views become limited (100 views), 
+          reconstruction using Total Variation (TV, middle column) is
           better both visually and quantitatively than FBP (SSIM of
           0.96 vs 0.82). If the number of views is drastically reduced
-          (20 views), the presence of both TV prior and object
+          (20 views), the presence of both TV prior and object-
           prior together improves the reconstruction (SSIM=0.91) when compared
@@
 
- When the number of views is significantly reduced (this paper), the
- regularization prior alone is not sufficient.  In such cases additional
- information (`object-prior') specific to the current
+ When the number of views is significantly reduced (this paper), a
+ regularization prior alone is not sufficient.  In such cases
+ additional information (`object-prior') specific to the current
  object being scanned (called the `test' henceforth) is useful in
@@
  in order to track time-evolving changes within the subject's
- interior. As seen in Fig.~\ref{fig:story} (last column, 30 views) our
- method uses the set $S$ by creating an
- eigenspace representation (Section~\ref{sec:method_spatially_varying_prior}).
-
- However, with the use of such an object prior, a new challenge
- emerges. The prior set $S$ may potentially overwhelm the necessary
- details, and when several prior scans are available, finding the
- right prior is an issue. We therefore seek an algorithm that
- estimates the location and magnitude of new changes in the
- (unknown) test. As we show in
+ interior. As seen in Fig.~\ref{fig:story} (last column, 20 views) our
+ method uses the set $S$ by creating an eigenspace representation
+ (Section~\ref{sec:method_spatially_varying_prior}).
+
+ With the use of an object-prior, a new challenge emerges. The prior
+ set $S$ may potentially overwhelm the necessary details, and when
+ several prior scans are available, finding the right one is an
+ issue. We therefore devise an algorithm that estimates the location
+ and magnitude of new changes in the (unknown) test. As we show in
  Section~\ref{sec:method_spatially_varying_prior}, this eventually
@@
  still uses \textit{all} the previous scans in the set $S$, without
- using the prior scan \textit{as is}, or endeavoring to find the ``right''
- prior.
+ using any of the prior scans \textit{as is}, or endeavoring to choose
+ one ``right'' prior.
 
@@
  Section~\ref{sec:related}, Section~\ref{sec:contributions} lays down
- the key contributions of this work. Details of the datasets created and
- used for validation
- are described in Section~\ref{sec:datasets}. Section~\ref{sec:tmh}
- demonstrates the utility of our
- method on a longitudinal medical dataset. We now move to the
- details. Section~\ref{sec:method_spatially_varying_prior}
- describes the
- construction of a uniform eigenspace prior and computation of a spatially-varying map in order to preserve new changes in the test. 
- The results of are presented in
+ the key contributions of this work. Details of the datasets created
+ and used for validation are described in
+ Section~\ref{sec:datasets}. Section~\ref{sec:tmh} demonstrates the
+ utility of our method on a longitudinal medical dataset. We now move
+ to the details. Section~\ref{sec:method_spatially_varying_prior}
+ describes computation of a spatially-varying weights map in order to
+ preserve new changes in the test.  Results are presented in
  Section~\ref{sec:results_spatially_varying_prior}. Section~\ref{sec:discussion}
@@
 
-  %although this optimizer removes most of the artefacts created due to sub-sampling, its reconstruction is blurred when the number of views is very limited, as shown in Fig.~\ref{fig:story2}. 
+  %although this optimizer removes most of the artefacts created due
+  %to sub-sampling, its reconstruction is blurred when the number of
+  %views is very limited, as shown in Fig.~\ref{fig:story2}.
 %(2) there is the key issue of the choice of \textit{a particular} previously scanned object as template among the many previously acquired scans
@@
  sparsity-constrained optimization is presented for angiography. Here,
-the regions of interest are the vessels alone and they are highlighted
-by physically inserting a contrast agent, and therefore there is an
-inherent sharper contrast between the vessels and the background.  In
-other applications where the spatial-gradient of the underlying volume
-is known to be sparse, the `total variation' method, as used
-in~\cite{Li2015,Polak2017}, can be applied.  However, as shown earlier
-in Fig.~\ref{fig:story}, these regularization priors are not sufficient when very few
-views are acquired, thus needing information from stronger priors such as those obtained from previous scans of the same or similar object.
+ the regions of interest are the vessels alone and they are
+ highlighted by physically inserting a contrast agent, and therefore
+ there is an inherent sharper contrast between the vessels and the
+ background.  In other applications where the spatial-gradient of the
+ underlying volume is known to be sparse, the `total variation'
+ method, as used in~\cite{Li2015,Polak2017}, can be applied.  However,
+ as shown earlier in Fig.~\ref{fig:story}, these regularization priors
+ are not sufficient when very few views are acquired, thus needing
+ information from stronger priors such as those obtained from previous
+ scans of the same or similar object.
 
@@
 %In most scenarios, the object-prior
-The object-prior usually consists of an object
-reconstructed to high quality from a large number of projection
-angles. One of the earliest pieces of work in this area is the
-well-cited PICCS method~\cite{PICCS} for dynamic CT, which enforces a robust-norm
-based similarity between the test and the object prior,
-in addition to a sparsity prior on the test. The limitation is the
-unchecked over-emphasis of the prior on the reconstruction of the test
-at hand. A closely related method called PIRPLE was proposed
+The object-prior usually consists of an object reconstructed to high
+quality from a large number of projection angles. One of the earliest
+pieces of work in this area is the well-cited PICCS
+method~\cite{PICCS} for dynamic CT, which enforces a robust-norm based
+similarity between the test and the object prior, in addition to a
+sparsity prior on the test. Its limitation is the unchecked
+over-emphasis of the prior on the reconstruction of the test at
+hand. A closely related method called PIRPLE was proposed
 in~\cite{pirple}, with additional steps to register the object prior
@@
 In order to prevent the object-prior from overwhelming the
-reconstruction of test, a few other approaches have either estimated the
-motion between the object-prior and the test or have applied very
-specific object-properties for identifying the new changes in the
-test.  Examples for the former include~\cite{koen2020}, where the
-changes across the successive scan volumes are assumed to be
-continuous, thus enabling the use of optical flow to model the motion
-between corresponding voxels of different scan volumes. In another
+reconstruction of test, a few other approaches have either estimated
+the motion between the object-prior and the test or have applied very
+specific object-properties for identifying new changes in test.
+Examples for the former include~\cite{koen2020}, where changes across
+the successive scan volumes are assumed to be continuous, thus
+enabling the use of optical flow to model the motion between
+corresponding voxels of different scan volumes. In another
 study~\cite{vincent2017}, changes between successive scans were
@@
 together using spatio-temporal regularization. Here again, the
-inherent assumption is the continuity across volumes in space or
-time.
-
-The methods that use object-specific knowledge
-are~\cite{Van2015} and~\cite{Marjolein2016}.  In~\cite{Van2015}, the
-knowledge of the attenuation coefficient of the fluid is used as a
-prior for reconstructing its flow through gravel. However, this relies
-on additional expert domain knowledge which may not be available or
-which may be infeasible to acquire. Other approaches variously use robust principal components
+inherent assumption is the continuity across volumes in space or time.
+
+The methods that use object-specific knowledge are~\cite{Van2015}
+and~\cite{Marjolein2016}.  In~\cite{Van2015}, knowledge of attenuation
+coefficient of the fluid is used as a prior for reconstructing its
+flow through gravel. However, this relies on additional expert domain
+knowledge which may not be available or which may be infeasible to
+acquire. Other approaches variously use robust principal components
 analysis assuming that the object consists of a large static part
@@
 
-However, all these
+All of these
 techniques~\cite{daniil2015,koen2020,Van2015,HaoGao,Van2014}
 essentially reconstruct all the different stages of the object
-simultaneously, and use the extra redundancy across time
+\textit{simultaneously}, and use the extra redundancy across time
 simultaneously. In the scenario of a longitudinal study (where
@@
 weeks apart) which we consider in this paper, such approaches are not
-feasible. A longitudinal study will necessarily require reconstruction
-results after acquisition of each set of measurements.
-
-There exists methods for estimating the new changes (in the test)
-directly in the projection space. In such techniques which can
-be used in longitudinal studies, the object prior
-is projected in the same set of views as the current set of test
-measurements, and a set of projection differences is computed. These
-projection differences are essentially tomographic projections of the
-difference between the unknown test and the known object prior. Hence,
-a variety of reconstruction algorithms can be used to estimate such a
-difference image which can then be added to the object prior to yield
-the final estimate of the test. Such methods have been proposed
-in~\cite{Pourmorteza2015,Lee2012}. Here the reconstruction of the
+feasible. A longitudinal study will necessarily require
+reconstructions soon after acquisition of each set of measurements.
+
+There also exist methods for estimating new changes (in the test)
+directly in projection space. In such techniques which can be used in
+longitudinal studies, the object-prior is projected in the same set of
+views as the current set of test measurements, and a set of projection
+differences is computed. These projection differences are essentially
+tomographic projections of differences between the unknown test and
+the known object-prior. Hence, a variety of reconstruction algorithms
+can be used to estimate such a difference image which can then be
+added to the object-prior to yield the final estimate of the
+test. Such methods have been proposed
+in~\cite{Pourmorteza2015,Lee2012}. However, reconstruction of the
 difference image will inherently contain sub-sampling artefacts, and
@@
 object priors, corresponding to high quality reconstructions of
-similar objects across time, typically in a longitudinal study.
-We use these priors to improve the
-reconstruction of the test from largely undersampled measurements. In
-particular, we define the regions of change between the test and the
-eigenspace spanned by the previous high quality object priors in a
-purely data driven manner. Additionally, our technique differentiates
-between genuine structural changes and ``changes'' that appear due to
-undersampling artefacts (as seen in Sec.4 of our supplementary
-material~\cite{supp_paper}).  Besides this, since we use a statistical
-model with multiple object priors, we avoid the problem of selecting
-an appropriate single object prior
+similar objects across time, typically in a longitudinal study.  We
+use these priors to improve the reconstruction of the test from
+largely undersampled measurements. In particular, we define regions of
+change between the test and the eigenspace spanned by previous high
+quality object-priors in a purely data driven manner. Additionally,
+our technique differentiates between genuine structural changes and
+``changes'' that appear due to undersampling artefacts (as seen in
+Sec.4 of our supplementary material~\cite{supp_paper}).  Besides this,
+since we use a statistical model with multiple object-priors, we avoid
+the problem of selecting an appropriate single object-prior
 unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and
@@
 This paper focusses on few-views reconstruction with an emphasis on
-longitudinal studies. In contrast to
-the object prior-based studies mentioned above, we
-reconstruct the current test object without any assumption of
-continuity of changes or some knowledge of the attenuation
-coefficients of the structures. We do not make any temporal assumption
-in terms of time intervals -- prior scans could be months apart. We
-use the current measurements from few-views and previous scans of the
-same object. A key idea in our work is the starting point -- the new
-test volume is close to the space spanned by the eigenvectors of the
-multiple representative previously scanned objects.
+longitudinal studies. In contrast to the object-prior based studies
+mentioned above, we reconstruct the current test object without any
+assumption of continuity of changes or knowledge of the attenuation
+coefficients of the structures. We also do not make any temporal
+assumption in terms of time intervals -- prior scans could be months
+apart. We use the current measurements from few-views and previous
+scans of the same object. A key idea in our work is this starting
+point -- the new test volume is close to the space spanned by the
+eigenvectors of multiple representative previously scanned objects.
 
@@
 
-We also demonstrate how the uniform prior can impose an inflexible
+We discuss the danger in imposing an inflexible
 constant weight (and hence an unnecessary bias) when reconstructing
@@
         \caption{Overview of our work.
-When only few measurements are available, the choice of the reconstruction algorithm is driven by availability of object-prior.
-(a) In the absence of object-prior, any method that utilizes object-independent prior (such as total variation, sparsity) may be used.
-(b) In the presence of object-prior, we propose using spatially-varying prior-based reconstruction which utilizes both object-dependent and object-independent priors.
-In either case, the number of views is lower than what is conventionally used.}
+When the number of measurements is lower than what is conventionally used, (a) a regularization prior (such as Total Variation) alone is not sufficient to mitigate the sub-sampling artefacts.
+(b) An object-prior must be used to provide additional information.
+Here, in order to prevent a prior induced bias in the reconstruction, we propose using a spatially-varying weights-map to modulate the effect of object-prior on the final reconstruction.}
  \label{fig:prior_overview}
@@
   will be made available to the community.
-  \item As seen in Fig.~\ref{fig:story}, we demonstrate the use of
-    uniform priors when very few views are used. More results appear
-    in Section~\ref{sec:results_uniform_prior} and in the
-    supplementary material.
-  \item We discuss the scenarios where a uniform object prior is
-    sufficient for the application at hand, and the scenarios for
-    which it will fail. This leads to the idea of a weights map
-    designed to depict the location and strength of new changes at
+  \item We design a weights-map
+    to depict the location and strength of new changes in the test at
     every voxel. A novel algorithm is presented to build this map from
     sub-sampled measurements of the test and a set of high quality
-    templates. Once the weights map is built, it is used for accurate
+    templates. Once the weights-map is built, it is used for accurate
     reconstruction of those changes in the test that are absent in all
@@
   \item We show the efficacy of our results in a real-life medical
-    longitudinal studies with data obtained in a clinical setting from
+    longitudinal study with data obtained in a clinical setting from
     a live teaching and
-    research hospital 
+    research hospital.
 \end{itemize}
@@
 In this section, we lay the details of all the real and simulated
-datasets created and used for this work. The first 3 datasets: Okra, Potato and Sprouts were acquired from the Australian National University (ANU). We wish to emphasize that data from commercially
+datasets created and used for this work. The first 3 datasets: Okra,
+Potato and Sprouts were acquired from the Australian National
+University (ANU). We wish to emphasize that data from commercially
 available CT machines may not be suitable because most CT scanners do
@@
 reconstructed volumes. Moreover, the process of conversion from the
- projections to the full volumes is proprietary. Departing from this, we
- demonstrate reconstruction results (in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior} from the following datasets.\\
-
- \textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
-scans (Fig.~\ref{fig:object-prior_test_okra}). Prior to the first scan, two cuts were
-drilled on the surface of the specimen. This was followed by four
-scans, each after introducing one new cut. The specimen was kept in
-the same position throughout the acquisitions. The measurements
-consisted of real circular cone-beam projections from 450 views, each of size
-336$\times$156. 
+projections to the full volumes is proprietary. Departing from this,
+we demonstrate reconstruction results (in
+Section~\ref{sec:results_spatially_varying_prior} from the following
+datasets.
+
+ \textbf{Liver:} %We have used this dataset
+ %to illustrate an application
+%where \textit{both} uniform and spatially-varying priors are
+%useful.
+This data was sourced from Tata Memorial Centre~\cite{tmh} in Parel,
+Mumbai.  This is the national comprehensive centre for the prevention,
+treatment, education and research in cancer, and is recognized as one
+of the leading cancer centres in India. The dataset
+(Fig.~\ref{fig:RFA2_test_object-prior}) from this longitudinal medical
+study consists of 7 scans taken at different stages of radio-frequency
+ablation study of a liver. In such a procedure~\cite{Dong2015}, the
+physician inserts a thin needle-like probe into the organ. Repeated CT
+scans of the patient are acquired in order to track the movement of
+the needle and to ensure that it is reaching the appropriate target
+tumor. Once the needle hits the tumor, a high-frequency electric
+current is passed through the tip of the probe and this burns the
+malignant tumor (ablation).
+
+In our experiments, we generate parallel beam measurements from 2D
+slices from each of the 7 volumes. Note that all these 7 slices are
+located at the \emph{same} index (slice number corresponding to the
+same depth) within each of the respective volumes.  Observe (in
+Fig.~\ref{fig:RFA2_test_object-prior}) that the needle is seen in all
+of the 7 slices.
+%In our experiments using this dataset, we demonstrate the usefulness of \textit{both} uniform prior and spatially varying prior.
+For the first case, we choose the first 6 slices to build the object prior and use slice 7 as the test.
+For the latter case, we choose the first 7 slices to build the object prior and use slice 8 as the test.
+%--------------------------Results on TMH data--------------------------
+%------------------RFA 2 data
+\begin{figure}[h!]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 2}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 3}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 4}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 5}
+    \end{subfigure}
+              \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 6}
+    \end{subfigure}
+       \begin{subfigure}[b]{0.23\linewidth}
+        \fcolorbox{white}{green}{\includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}}
+%\captionsetup{labelformat=empty}       
+ \caption{slice 7}
+    \end{subfigure}     
+     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 7 scan volumes of a longitudinal study dataset of the liver.
+Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.}
+\label{fig:RFA2_test_object-prior}
+\end{figure}
+
+ \textbf{Okra:} This dataset is that of an Okra specimen consisting of
+ its five scans (Fig.~\ref{fig:object-prior_test_okra}). Prior to the
+ first scan, two cuts were drilled on the surface of the
+ specimen. This was followed by four scans, each after introducing one
+ new cut. The specimen was kept in the same position throughout the
+ acquisitions. The measurements consisted of real circular cone-beam
+ projections from 450 views, each of size 336$\times$156.
 %In cases where such an
@@
 %object-prior after its preliminary pilot reconstruction.
-In our experiments, the first 4 volumes shown in Fig.~\ref{fig:object-prior_test_okra} were used to build the object-prior and the
-last volume was used as the test. The ground truth
-consists of volumes of size 338$\times$338$\times$123 reconstructed
-using the Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} from the
-full set of 450 view projections.
+In our experiments, the first 4 volumes shown in
+Fig.~\ref{fig:object-prior_test_okra} were used to build the
+object-prior and the last volume was used as the test. The ground
+truth consists of volumes of size 338$\times$338$\times$123
+reconstructed using the Feldkamp-Davis-Kress (FDK)
+algorithm~\cite{FDK} from the full set of 450 view projections.
 \\
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.176\linewidth}
-        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/okra/test_marked.png}}
+     \begin{subfigure}[b]{0.148\linewidth}
+        \fcolorbox{white}{cyan}{\includegraphics[width=\textwidth]{../images/okra/post_TCI/test_marked.png}}
 \captionsetup{labelformat=empty}
@@
      \caption{Okra 3D dataset: One slice each from the scanned objects that are used as object-prior (the first four from left) and a slice from the test 
-        volume (extreme right). Notice the regions marked in red and green boxes; while all slices have deformities, the test has none.}
+        volume (extreme right). Notice the region marked in red box; while all slices have deformities here, the test has none.}
 \label{fig:object-prior_test_okra}
@@
 %----------------------------------------------------
-
-\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}).
-While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato.
-Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150.
-%Further, this alignment can be refined following every update of the reconstructed test volume.
-In our experiments, the first 3 volumes were used to build the object-prior and the
-last volume was used as the test. The ground truth consists of volumes of size 150$\times$150$\times$100 reconstructed using FDK from the full set of 900 projection views. 
-%---------------------------------------
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
-\captionsetup{labelformat=empty}
-\caption{}
-\label{fig:potato3D_test}
-     \end{subfigure}
-      \caption{Potato 3D dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
-        volume (extreme right). Notice the appearance of the fourth
-        hole in the test slice. }
-\label{fig:object-prior_test_potato_A}
-\end{figure}
 
@@
 in-vivo sprout specimen imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}).  \textit{In contrast to the
-scientific experiment performed for the case of the okra and potato
-where we introduced man-made defects, the changes here are purely the
-work of nature.} In our experiments, the first 5 volumes were used to build the object-prior and the last volume was used as the test. The ground truth consists of FDK reconstructed
-volumes of size 130$\times$130$\times$130 from a set of 1800 view
+(Fig.~\ref{fig:object-prior_test_sprouts}).  \textit{In contrast to
+  the scientific experiment performed for the case of the okra and
+  potato where we introduced man-made defects, the changes here are
+  purely the work of nature.} In our experiments, the first 5 volumes
+were used to build the object-prior and the last volume was used as
+the test. The ground truth consists of FDK reconstructed volumes of
+size 130$\times$130$\times$130 from a set of 1800 view
 projections. For the test, cone-beam projections were generated from
@@
     \begin{subfigure}[b]{0.29\linewidth}
-        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
+        \fcolorbox{white}{yellow}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
 \captionsetup{labelformat=empty}
@@
 
-\textbf{Liver:} %We have used this dataset
- %to illustrate an application
-%where \textit{both} uniform and spatially-varying priors are
-%useful.
-This data was sourced from Tata Memorial Centre~\cite{tmh} in Parel,
-Mumbai.  This is the national comprehensive centre for the prevention,
-treatment, education and research in cancer, and is recognized as one
-of the leading cancer centres in India. The dataset
-(Fig.~\ref{fig:RFA2_test_object-prior}) from this longitudinal medical
-study consists of 8 scans taken at different stages of radio-frequency
-ablation study of a liver. In such a procedure~\cite{Dong2015}, the
-physician inserts a thin needle-like probe into the organ. Repeated CT
-scans of the patient are acquired in order to track the movement of
-the needle and to ensure that it is reaching the appropriate target
-tumor. Once the needle hits the tumor, a high-frequency electric
-current is passed through the tip of the probe and this burns the
-malignant tumor (ablation). The aim of the scan at this ablation stage
-is to reveal accurate details of the changes within.
-
-In our experiments, we generate parallel beam measurements from 2D
-slices from each of the 8 volumes. Note that all these 8 slices are
-located at the \emph{same} index (slice number corresponding to the
-same depth) within each of the respective volumes.  Observe (in
-Fig.~\ref{fig:RFA2_test_object-prior}) that the needle is seen in all
-of the first 7 slices and the effect of ablation is seen in the 8th
-slice.
-%In our experiments using this dataset, we demonstrate the usefulness of \textit{both} uniform prior and spatially varying prior.
-For the first case, we choose the first 6 slices to build the object prior and use slice 7 as the test.
-For the latter case, we choose the first 7 slices to build the object prior and use slice 8 as the test.
-%--------------------------Results on TMH data--------------------------
-%------------------RFA 2 data
-\begin{figure}[h!]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 1}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 2}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 3}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 4}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 5}
-    \end{subfigure}
-              \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
-%\captionsetup{labelformat=empty}       
- \caption{slice 6}
-    \end{subfigure}
-       \begin{subfigure}[b]{0.23\linewidth}
-        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}}
-%\captionsetup{labelformat=empty}       
- \caption{slice 7}
-    \end{subfigure}     
-     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 7 scan volumes of a longitudinal study dataset of the liver.
-Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.}
-\label{fig:RFA2_test_object-prior}
-\end{figure}
-
-%--------------------------------THM section-------------------------
-\section{Application: Reconstruction for CT-guided radio-ablation study}
-\label{sec:tmh}
-Before diving into the details of the uniform and the
-spatially-varying prior methods, we first show how \textit{both} the
-techniques can be applied to our advantage in a real-life medical
-longitudinal study. Here, our data consists of successive scans of the liver taken
-during a radio-frequency ablation procedure as described in Sec.~\ref{sec:datasets}. In this context, we classify the goal of any of our
-reconstruction techniques into two categories: 
-\begin{enumerate}
-\item to track the position of the needle, and% in a relatively well-reconstructed background.%Initially, when our goal is to only track the location of the probe while simultaneously reducing sub-sampling artefacts, we advocate capturing measurements from a small number of views (`few-view' imaging) and using uniform prior based reconstruction.
-\item to accurately observe the new changes when the needle touches the tumor,%Later, when the probe is proximal to or touches the tumor, our goal is to observe details of tumor ablation while simultaneously reducing sub-sampling artefacts.
-In this case, we propose to capture measurements from a slightly higher number of views (`moderate-view' imaging) to acquire more information, and use a spatially-varying prior-based reconstruction.
-The spatially-varying technique moderates the effect of the prior in the reconstruction of new changes in the object being scanned.
-\end{enumerate}
-while simultaneously reducing the sub-sampling artefacts.
-%Here, we demonstrate the combined use of l1-ls (CS) with the object
-%prior, in two flavors: the vanilla (uniform) and spatially-varying
-%prior-based reconstruction.
-The choice of the number of
-measurement views and the type of reconstruction -- uniform or
-spatially-varying, is driven by the goal of the procedure. First, in
-order to track the needle, a very small number of views is sufficient
-because the needle has a very high attenuation coefficient when
-compared to that of the organs. We use the uniform prior
-reconstruction here to reduce the artefacts due to sub-sampling. The
-uniform method is fast and sufficient to track the position of the
-needle.  Once the needle reaches the site of the tumor, we propose
-changing the imaging protocol to acquire measurements from a moderate
-number of views. This will enable us to get more information about the
-new changes. In addition, we then deploy the spatially-varying prior
-method in order to locate the regions of new changes and penalize any
-dominance of the prior in these regions.  Regardless of the imaging
-protocol we use (`few' or `moderate'), the number of views is smaller
-(atleast one-fifth) than the conventional number of views used in a
-standard hospital setting. To summarize, when our aim is\\
-\begin{itemize}
-\item \textbf{Tracking the needle},  we first choose slices 1-6 as our
-object-prior, and reconstruct slice 7 with the specific goal of
-tracking the needle and simultaneously reduce
-artefacts. Fig.~\ref{fig:RFA2_very_few_views} shows the reconstruction
-of slice 7 from its measurements from only 90 views. The
-reconstructions are quantitatively compared using SSIM.
-\end{itemize}
-%--------------------RFA 2 few views
+\textbf{Potato:} This dataset consisted of four scans of the humble
+potato (Fig.~\ref{fig:potato_dataset}). While the first
+scan was taken of the undistorted potato, subsequent scans were taken
+of the same specimen, each time after drilling a new hole halfway into
+the potato. Measurements from each scan consisted of real circular
+cone-beam projections from 900 views, each of size
+150$\times$150. %Further, this alignment can be refined following
+every update of the reconstructed test volume.  In our experiments,
+the first 3 volumes were used to build the object-prior and the last
+volume was used as the test. The ground truth consists of volumes of
+size 150$\times$150$\times$100 reconstructed using FDK from the full
+set of 900 projection views.
+%---------------------------------------
 \begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
-\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
-\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
-\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
-\caption{\small{ Reconstruction of `test' (slice 7) from Fig.~\ref{fig:RFA2_test_object-prior} from only 30 views, using (b) FBP and no prior resulting in streaks, SSIM=0.73 (c) TV resulting in blurred bone structures, SSIM=0.91 and (d) spatially varying object-prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks, SSIM=0.95.
-The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
-All SSIM values are computed for this RoI.
-(e) shows the computed weights map (defined later in the paper) used for reconstruction.
-Darker intensities indicate lower weights to prior as these are the regions of new changes.}}
-\label{fig:RFA2_very_few_views}
-\end{figure}
-
-%---------------------------------Uniform section---------------------
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.235\linewidth}
+        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
+\captionsetup{labelformat=empty}
+\caption{}
+\label{fig:potato3D_test}
+     \end{subfigure}
+      \caption{Potato 3D dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
+        volume (extreme right). Notice the appearance of the fourth
+        hole in the test slice. }
+\label{fig:potato_dataset}
+\end{figure}
+%----------------------------------------Method-------------------------
 \section{Spatially-Varying prior-based reconstruction}
 \label{sec:method_spatially_varying_prior}
-Having presented the application, we first review the algorithm~\cite{my_dicta_paper} for a uniform  prior-based reconstruction since we are extending this algorithm to 3D reconstructions as part of this work.
-%Principal Component Analysis (PCA) has been traditionally used to find the significant modes of (Gaussian corrupted) data.
-In this regard, it has been widely applied in the context of data compression.
-However, PCA can also be seen as a tool to provide an orthogonal basis to represent the space in which most of the test data could lie (except the new changes).
-This space is constructed from the available set of previously scanned objects which must cover a realistically representative range of structures.
-%, which was shown~\cite{my_dicta_paper} to be better when compared to dictionary-based priors.
-%A preliminary version of this particular method was earlier presented in \cite{my_dicta_paper}.
-We first present the eigenspace-cum-CS prior-based reconstruction.
-To begin with, when an object is scanned multiple times, a set of high quality reconstructions (i.e., reconstructions from a dense set of projection views) may be chosen as object-prior for the reconstruction of future scan volumes, which in turn, may be scanned using far fewer measurements.
-The eigenspace $E_{\text{high}}$ of the $L$ previously scanned objects $Q_1,Q_2,...,Q_L$ is pre-computed.
-Here, it is assumed that most of the test volume, barring the new changes, can be expressed as a sparse linear combination of the principal components (eigenvectors of the covariance matrix) obtained from a group of structurally similar volumes.
-Hence, the object-prior is represented by means of PCA.
-For the eigenspace to encompass a range of possible structures in the test slice, the object-prior must represent a wide structural range.
-Moreover, if these volumes are not aligned, then they must be first registered before computing the prior.
-The prior is built by computing the covariance matrix from the template set $\{Q_i\}_{i=1}^L$.
-The space spanned by the eigenvectors $\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance matrix is the object prior and is assumed to contain most of the test slice that is similar, but not necessarily identical to the object-prior.
-We use all of the $L-1$ orthogonal eigenvectors as a basis to represent the unknown test volume.
-Let $\boldsymbol{\mu}$ denote the mean of the previously scanned objects, and $\boldsymbol{\alpha}$ the unknown vector of eigen-coefficients of the test scan, of which $\alpha_k$ is the $k^{\textrm{th}}$ element.
-Then, once the eigenspace is pre-computed, the test is reconstructed by minimizing the following cost function:
-
-Here, $\lambda_1$, $\lambda_2$ are tunable weights given to the sparsity and prior terms respectively. The unknowns $\boldsymbol{\theta}$ and $\boldsymbol{\alpha}$
-are solved by alternately minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{\theta})$ using a fixed $\boldsymbol{\alpha}$, and $J_{\boldsymbol\theta}(\boldsymbol{\alpha})$ using the resultant $\boldsymbol{\theta}$, where
-
-$\boldsymbol{\theta}$ is solved for using the basis pursuit CS solver, (l1-ls)~\cite{l1ls}. Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
-
-%Optimal values of $\lambda_1, \lambda_2$ must be empirically chosen \textit{a priori}, based on the reconstructions of one of the template volumes (see also Sec.~\ref{sec:discussion}).
-The cost function described in Eq.~\ref{Eq:main_prior} is biconvex and the convergence of this optimization is guaranteed by the monotone convergence theorem~\cite{monotone}.
- %---------------------------------------------------------
- \vspace{2mm}
-
-%----------------------------------------------------------------------
-
-Although the uniform prior can be very useful in some
-circumstances, as was shown in Sec.~\ref{sec:tmh}, it poses a 
-limitation when we want accurate details of a portion of the new changes. While the
-uniform prior compensates very well for the possible artefacts due to
-sparse measurements, it may dominate the regions with new changes masking
-the signal, as was seen earlier in Fig.~\ref{fig:RFA2_few_views}(d). Ideally, we
-will want to impose the prior only in the regions that are common
-between the test and object-prior.  Our spatially-varying prior based
-reconstruction overcomes this limitation by minimizing the following
-cost function:
+Our method modifies the algorithm presented in~\cite{my_dicta_paper}
+and addtionally overcomes one of its major limitations by introducing
+an extra computational step. We first review the eigenspace-cum-CS
+prior-based reconstruction algorithm for a
+2D uniform prior-based reconstruction, which was
+shown~\cite{my_dicta_paper} to be better when compared to
+dictionary-based priors. PCA has been traditionally used
+to find the significant modes of (Gaussian corrupted) data. In this
+regard, it has been widely applied in the context of data
+compression. However, PCA can also be seen as a tool to provide an
+orthogonal basis to represent the space in which most of the test data
+could lie (except the new changes). This space is constructed from the
+available set of previously scanned objects which must cover a
+realistically representative range of structures. %A preliminary version of this particular
+
+To begin with,
+when an object is scanned multiple times, a set of high quality
+reconstructions (i.e., reconstructions from a dense set of
+projection views) may be chosen as object-prior for the reconstruction
+of future scan volumes, which in turn, may be scanned using far fewer
+measurements. The eigenspace $E_{\text{high}}$ of the $L$ previously
+scanned objects $Q_1,Q_2,...,Q_L$ is pre-computed. Here, it is assumed
+that most of the test volume, barring the new changes, can be
+expressed as a sparse linear combination of the principal components
+(eigenvectors of the covariance matrix) obtained from a group of
+structurally similar volumes. Hence, the object-prior is represented
+by means of PCA. For the eigenspace to encompass a range of possible
+structures in the test slice, the object-prior must represent a wide
+structural range. Moreover, if these volumes are not aligned, then
+they must be first registered before computing the prior.
+
+The prior is built by computing the covariance matrix from the
+template set $\{Q_i\}_{i=1}^L$. The space spanned by the eigenvectors
+$\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance
+matrix is the object prior and is assumed to contain most of the test
+slice (or volume in the case of 3D) that is similar, but not
+necessarily identical to the object-prior. We use all of the $L-1$
+orthogonal eigenvectors as a basis to represent the unknown test
+volume. Let $\boldsymbol{\mu}$ denote the mean of the previously
+scanned objects, and $\boldsymbol{\alpha}$ the unknown vector of
+eigen-coefficients of the test scan, of which $\alpha_k$ is the
+$k^{\textrm{th}}$ element. Then, once the eigenspace is pre-computed,
+the test was reconstructed in~\cite{my_dicta_paper} by imposing a
+penalty if the estimated slice does not lie within the eigen-space of
+the object prior.
+
+Although the uniform prior can be very useful in some circumstances,
+it poses a limitation when we want accurate details of a portion of
+the new changes. While the uniform prior compensates very well for the
+possible artefacts due to sparse measurements, it may dominate the
+regions with new changes masking the signal. Ideally, we will want to
+impose the prior only in the regions that are common between the test
+and object-prior.  Our spatially-varying prior based reconstruction
+overcomes this limitation by minimizing the following cost function:
 \begin{equation}
+  \begin{split}
 %   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
 %\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
-J_3(\boldsymbol{x},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\\ \lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
-\label{eq:spatially-varying_prior}
+  J_3(\boldsymbol{x},\boldsymbol{\alpha}) = &\lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\\
+  &\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
+  \label{eq:spatially_varying_prior}
+  \end{split}
 \end{equation}
-\begin{align}
-J_{\boldsymbol{\alpha}}(\boldsymbol{\x}) &\triangleq \lVert\boldsymbol{\mathcal{R} x- y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\lambda_2\lVert(\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2, \\
-J_{\boldsymbol{x}}(\boldsymbol{\alpha}) &\triangleq \lVert\boldsymbol{\boldsymbol{W}(\boldsymbol{x}} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2.
-\end{align}
-
-The key to our method is the discovery of a diagonal weights
- matrix $\boldsymbol{W}$, where $W_{ii}$ contains the (non-negative) weight assigned to the $i^{\textrm{th}}$ voxel of the prior.
-$\boldsymbol{W}$ is first constructed using some preliminary reconstruction methods, following which Eq.~\ref{eq:spatially-varying_prior} is used to obtain the final reconstruction.
-In regions of change in test data, we want lower weights for the prior when compared to regions that are similar to the prior.
- \\
+\begin{equation}
+  \begin{split}
+    J_{\boldsymbol{\alpha}}(\boldsymbol{\x}) \triangleq &\lVert\boldsymbol{\mathcal{R} x- y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) \\
+    &+\lambda_2\lVert(\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2
+  \end{split}
+  \end{equation}
+
+\begin{equation}
+J_{\boldsymbol{x}}(\boldsymbol{\alpha}) \triangleq \lVert\boldsymbol{\boldsymbol{W}(\boldsymbol{x}} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2.
+\end{equation}
+
+The key to our method is the discovery of a diagonal weights matrix
+$\boldsymbol{W}$, where $W_{ii}$ contains the (non-negative) weight
+assigned to the $i^{\textrm{th}}$ voxel of the prior. $\boldsymbol{W}$
+is first constructed using some preliminary reconstruction methods,
+following which Eq.~\ref{eq:spatially_varying_prior} is used to obtain
+the final reconstruction. In regions of change in test data, we want
+lower weights for the prior when compared to regions that are similar
+to the prior.
+
+$\lambda_1$, $\lambda_2$ are tunable weights given to the
+TV-prior and object-prior terms respectively. The unknowns
+$\boldsymbol{\x}$ and $\boldsymbol{\alpha}$ are solved by alternately
+minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{\x})$ using a fixed
+$\boldsymbol{\alpha}$, and $J_{\boldsymbol{x}}(\boldsymbol{\alpha})$
+using the resultant $\boldsymbol{\x}$.
+$J_{\boldsymbol{\alpha}}(\boldsymbol{\x})$ is solved for using an
+optimal first-order method for large-scale TV regularization presented
+in~\cite{TVReg} and available in~\cite{TVReg-lib}.
+Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
+
+\begin{equation}
+\boldsymbol{\alpha} = [(\boldsymbol{WV})^T\boldsymbol{WV}]^{-1}.\boldsymbol{V}^T(\boldsymbol{W}^T\boldsymbol{W}(\boldsymbol{x} - \boldsymbol{\mu}))
+\end{equation}
+
+%Optimal values of $\lambda_1, \lambda_2$ must be empirically chosen \textit{a priori}, based on the reconstructions of one of the template volumes (see also Sec.~\ref{sec:discussion}).
+The cost function described in Eq.~\ref{eq:spatially_varying_prior} is biconvex and the convergence of this optimization is guaranteed by the monotone convergence theorem~\cite{monotone}.
 
@@
 described below.
-\\
 
@@
   \item Perform pilot reconstructions of the test using $M$ different
-    reconstruction algorithms like the CS~\cite{lasso}, Algebraic Reconstruction Technique (ART)~\cite{art},
-     Simultaneous Algebraic Reconstruction Technique (SART)~\cite{sart} and  Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt}. Let this set of pilot reconstructions be denoted
-    as $X \triangleq \{X^j\}_{j=1}^M$ where $j$ is an index for the
-    reconstruction method, and $X^1 = X^{\text{fdk}}$.
-
-  \item From $\boldsymbol{y_{Q_i}}$, perform reconstructions of the template $Q_i$ using the $M$ different algorithms, for each of the $L$ previously scanned objects.
-Let this set be denoted by $Y \triangleq \{\{Y_{i}^j\}_{j=1}^M\}_{i=1}^L$ where $Y^{1}_i = Y^{\text{fdk}}_i$, $\forall i \in \{1,..,,L\}$.
-
-  \item For each of the $M$ algorithms (indexed by $j$), build an eigenspace $\boldsymbol{V_\text{low}^j}$ from $\{Y_1^j,Y_2^j, \ldots, Y_{L}^j\}$. %($j=1..M$).
-
-  \item Next, for each $j$,  project $X^j$  onto $\boldsymbol{V_\text{low}^j}$.
-Let this projection be denoted by $P^j$.
-To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e., are similar to the template reconstructions).
-The rest, i.e., new changes and their reconstruction method-dependent-artefacts, are not captured by this projection and need to be eliminated.
+    reconstruction algorithms like the CS~\cite{lasso}, Total
+    Vairiation~\cite{TV},Algebraic Reconstruction Technique
+    (ART)~\cite{art}, Simultaneous Algebraic Reconstruction Technique
+    (SART)~\cite{sart} and Simultaneous Iterative Reconstruction
+    Technique (SIRT)~\cite{sirt}. Let this set of pilot
+    reconstructions be denoted as $X \triangleq \{X^j\}_{j=1}^M$ where
+    $j$ is an index for the reconstruction method, and $X^1 =
+    X^{\text{fdk}}$.
+
+  \item From $\boldsymbol{y_{Q_i}}$, perform reconstructions of the
+    template $Q_i$ using the $M$ different algorithms, for each of the
+    $L$ previously scanned objects. Let this set be denoted by $Y
+    \triangleq \{\{Y_{i}^j\}_{j=1}^M\}_{i=1}^L$ where $Y^{1}_i =
+    Y^{\text{fdk}}_i$, $\forall i \in \{1,..,,L\}$.
+
+  \item For each of the $M$ algorithms (indexed by $j$), build an
+    eigenspace $\boldsymbol{V_\text{low}^j}$ from $\{Y_1^j,Y_2^j,
+    \ldots, Y_{L}^j\}$. %($j=1..M$).
+
+  \item Next, for each $j$, project $X^j$ onto
+    $\boldsymbol{V_\text{low}^j}$. Let this projection be denoted by
+    $P^j$. To reiterate, this captures those parts of the test volume
+    that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e., are
+    similar to the template reconstructions). The rest, i.e., new
+    changes and their reconstruction method-dependent-artefacts, are
+    not captured by this projection and need to be eliminated.
   \end{enumerate}
 %\vspace{-0.1cm}
-\item To remove all reconstruction method dependent false positives, we compute $\min_{j}(|X^j(x,y,z) - P^j(x,y,z)|)$.
-(The intuition for using the `min' is provided in the paragraph immediately following step 6 of this procedure.)
-\item Finally, the weight to prior for each voxel coordinate $(x,y,z)$ is given by
+\item To remove all reconstruction method dependent false positives,
+  we compute $\min_{j}(|X^j(x,y,z) - P^j(x,y,z)|)$. (The intuition for
+  using the `min' is provided in the paragraph immediately following
+  step 6 of this procedure.)
+\item Finally, the weight to prior for each voxel coordinate $(x,y,z)$
+  is given by
   \begin{equation} 
@@
 because it is unlikely that \emph{every} algorithm would produce a significant artefact at a voxel, and hence we hypothesize that the large difference has arisen due to genuine structural changes.
-The parameter $k$ decides the sensitivity of the weights to the difference $|X^j(x,y,z) - P^j(x,y,z)|$ and hence it depends on the size of the new regions we want to detect.
+The parameter $k$ decides the sensitivity of the weights to the difference $|X^j(x,y,z) - P^j(x,y,z)|$.
 %It must be chosen empirically based on the reconstruction of one of the template
 %volumes. 
-We found that our final reconstruction results obtained by
-solving Eq.~\ref{eq:spatially-varying_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.\\
+Selection of $k$ is discussed in detail in Sec.~\ref{sec:discussion}.\\
 %-------------------------------------------
@@
 \textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights:}
-
-%-----------------------------potato data
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/potato/post_tci/testIm_paper.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-\label{fig:potato_test}
-     \end{subfigure}
-      \caption{Potato dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
-        volume (extreme right). Notice the appearance of the fourth
-        hole in the test slice. }
-\label{fig:object-prior_test_potato_A1}
-\end{figure}
 %-----------------------------potato 2D weights
@@
      \end{subfigure}
-      \caption{Weights-maps (corresponding to the difference between pilot reconstruction of the image in the last sub-figure of Fig.~\ref{fig:object-prior_test_potato_A1} and its projection onto the eigenspace $\boldsymbol{V_\text{low}}$) constructed using different reconstruction methods individually (a-f) and collectively (g) by fusing information from all reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}.
+      \caption{For reconstruction of the test image in Fig.~\ref{fig:potato_dataset}(d) from $6$ views, these are the weights-maps (corresponding to the difference between pilot reconstruction of the test and its projection onto the eigenspace $\boldsymbol{V_\text{low}}$) constructed using different reconstruction methods individually (a-f) and collectively (g) by fusing information from all reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}.
 The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
@@
      \end{subfigure}
-      \caption{(a)-(f):Different reconstructions of~\ref{fig:object-prior_test_potato_A1}(d).
+      \caption{(a)-(f):Different reconstructions of~\ref{fig:potato_dataset}(d) from $6$ views.
 The magnitude and sharpness of the artefacts is different for each method.
@@
 2D reconstruction of a test slice from the potato dataset.
-Fig.~\ref{fig:object-prior_test_potato_A1} shows the test and template
+Fig.~\ref{fig:potato_dataset} shows the test and template
 slices. Fig.~\ref{fig:weights_map_2Dpotato} shows the weights-maps
@@
 new change in test data. Because all the iterative methods are
-computationally expensive, we chose only FBP and (l1-ls)-DCT for
+computationally expensive, we chose only FBP and TV for
 computing weights-maps for all 3D reconstructions.
@@
   \centering
-\caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g).
-The SSIM of ground-truth (ideal reconstruction) is 1, and these are computed within the red RoI of the test image shown in Fig.~\ref{fig:potato_test}.}
+\caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ground-truth (ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
@@
  Fig.~\ref{fig:reconstructions_diff_methods}  & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
-\textbf{red RoI}  & 0.51 & 0.59  & 0.53 & 0.52 & 0.60 & 0.52 & 0.81 &\textcolor{red}{0.74} \\ \hline
+  & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
 \end{tabular}
@@
 \end{table}
-%-------------------------------------------------
 
 %----------------------------------------Results-----------------------
-\section{Results: Reconstruction by spatially-varying prior}
+\section{Results}
 \label{sec:results_spatially_varying_prior}
-
-%The proposed method has been validated on 2D and 3D synthetic and real
-%tomographic data of biological and medical specimens.
-The results below show the advantage of spatially-varying prior over uniform prior while reconstructing details of the new changes within the object.
+We present results on 2D and 3D synthetic as well as real
+tomographic data of biological and medical specimens.
+
+\subsection{\textbf{CT-guided radio-ablation study}}
+\label{sec:tmh}
+
+We first show how our technique is useful in a
+real-life medical longitudinal study. Here, our data consists of
+successive scans of the liver taken during a radio-frequency ablation
+procedure as described in Sec.~\ref{sec:datasets}. Our goal is to to
+track the position of the needle in a relatively stationary
+background, while simultaneously reducing sub-sampling artefacts.
+Specifically, we choose slices 1-6 as our object-prior, and
+reconstruct slice 7 from few-views with the specific goal of tracking
+the needle and simultaneously reducing
+artefacts. Fig.~\ref{fig:tmh_2D_results} and
+Fig.~\ref{fig:tmh_2D_zoomed_results} show reconstruction of the test
+slice from its measurements from only 30 views and a zoomed-in version
+around the RoI. The reconstructions are quantitatively compared using
+SSIM.
+
+%--------------------RFA 2 few views
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
+\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
+\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
+\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
+\caption{\small{ Reconstruction of `test' (slice 7) from Fig.~\ref{fig:RFA2_test_object-prior} from only 30 views, using (b) FBP and no prior resulting in streaks (c) TV resulting in blurred bone structures and (d) spatially varying object-prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks.
+The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
+(e) shows the computed weights map used for reconstruction.
+Darker intensities indicate lower weights to prior as these are the regions of new changes.}}
+\label{fig:tmh_2D_results}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/test_zoomed.png}}}\hfill
+\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp_zoomed.png}}\hfill
+\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_zoomed.png}}\hfill
+\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_pca_zoomed.png}}
+\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:tmh_2D_results}.}
+\label{fig:tmh_2D_zoomed_results}
+\end{figure}
+
+\begin{table}[!h]
+  \centering
+  \caption{SSIM of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ground-truth (ideal reconstruction), SSIM equals 1.}
+\begin{tabular}{|l|c|c|c|c|c|}
+\hline &
+\textbf{Backprojection} & \textbf{TV} &
+\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
+    TV\end{tabular}} \\ \hline \textbf{2D} & 0.73
+& 0.91 & \textcolor{red}{0.95} \\ \hline 
+\end{tabular}
+\label{table:sprouts_ssim}
+\end{table}
+%-----------------------------------------------------------------
 
@@
 \label{Sec:okra_spatially_varying}
-The test volume was reconstructed from a partial set of
-45 projections, i.e., $10\%$ of the projection views from which ground
-truth was reconstructed. One of the slices from the reconstructed volumes 
-is shown in Fig.~\ref{fig:okra_3D_results}. The red and green 3D
-RoI in the video and images show the regions where new changes are
-present. The zoomed-in images around the major region of change (red
-RoI) is shown in Fig.~\ref{fig:okra_zoomed_3D_results}. As in the
-test, the reconstruction by spatially-varying method shows the absence
-of the deformity and better removal of sub-sampling artefacts when
-compared to FDK and l1-ls. This is also seen in the SSIM values in
+The test volume was reconstructed from a partial set of 45 real
+cone-beam projections, i.e., $10\%$ of the projection views from which
+ground truth was reconstructed. 2D reconstructions of one of the
+slices is shown in Fig.~\ref{fig:okra_2D_results}. A complete 3D
+reconstruction can be found in in the supplementary material
+~\cite{supp_paper}. The red RoI in the video and images show the
+regions where new changes are present. A zoomed-in region around the
+major region of change (red RoI) is shown in
+Fig.~\ref{fig:okra_zoomed_2D_results}. As in the test, the
+reconstruction by spatially-varying method shows the absence of the
+deformity and better removal of sub-sampling artefacts when compared
+to FDK and TV. This is also seen in the SSIM values in
 Table~\ref{table:okra_ssim}.
@@
 \centering
-\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
+\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
 \subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/FBP_cropped.png}}
@@
 %\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
+\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
 \caption{Reconstruction of 2D okra from 48 projection views
    (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
-The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
-\label{fig:okra_3D_results}
-\end{figure}
-
-%----------------------------------------------------
+3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
+\label{fig:okra_2D_results}
+\end{figure}
 
@@
 \centering
-\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.29\columnwidth]{../images/sprouts/post_TCI/2D/20_views/testIm_roi.png}}}
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
-\subcaptionbox{TV, no prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
+\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.22\columnwidth]{../images/okra/post_TCI/2D/48_views/test_zoomed.png}}}
+\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/fbp_zoomed.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/tv_zoomed.png}}
 %\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.3\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
-\caption{Reconstruction of 2D sprouts from 20 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
-The 3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
-\label{fig:sprouts3D_results}
+\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_pca_zoomed.png}}
+\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:okra_2D_results}. }
+\label{fig:okra_zoomed_2D_results}
 \end{figure}
@@
     methods. For 3D, the RoI spans 7 consecutive slices where the test is
-    different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
+    different from all of the previously scanned objects. SSIM of ground-truth (ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
@@
 
+The test volume was reconstructed from partial set of 45 real
+cone-beam projections, i.e., $2.5\%$ of the projection views from
+which ground truth was reconstructed. The selected 3D ground truth of
+template volumes, test volume, as well as the 3D reconstructions are
+shown in the supplementary material~\cite{supp_paper}.  2D
+reconstruction of one of the slices and a zoomed-in region around the
+RoI are shown in Figs.~\ref{fig:sprouts_2D_results} and
+~\ref{fig:sprouts_zoomed_2D_results} respectively. For the sake of
+exposition, the red region of interest (RoI) has been culled out from
+7 consecutive slices in the 3D volume to indicate new structures;
+other changes can be viewed in the
+video. Table~\ref{table:sprouts_ssim} shows the improvement in SSIM of
+the reconstructed new regions as compared to other methods.
+%----------------------------------------------------
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/testIm_roi.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
+\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
+\caption{Reconstruction of 2D sprouts from 20 projection views
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
+3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
+\label{fig:sprouts_2D_results}
+\end{figure}
+
+%----------------------------------------------------
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/test_zoomed.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp_zoomed.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_zoomed.png}}
+%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
+\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
+\label{fig:sprouts_zoomed_2D_results}
+\end{figure}
 %--------------------------------------------------------------
@@
 
-The test volume was reconstructed from partial set of 45
-projections, i.e., $2.5\%$ of the projection views from which ground
-truth was reconstructed. The selected 3D ground truth of
-template volumes, test volume, as well as the 3D reconstructions are
-shown in the supplementary material~\cite{supp_paper}. One of the slices of the reconstructed
-volumes and its zoomed-in RoI are shown in
-Figs.~\ref{fig:sprouts_3D_results} and
-~\ref{fig:sprouts_zoomed_3D_results} respectively. For the sake of
-exposition, the red region of interest (RoI) has been culled out from
-7 consecutive slices in the 3D volume to indicate new structures;
-other changes can be viewed in the video. Tables~\ref{table:okra_ssim}
-and \ref{table:sprouts_ssim} show the improvement in SSIM of the reconstructed new regions as compared
-to other methods.
-
 %--------------------------------------------------------------------------
-
-\section{Discussion}
-\label{sec:discussion}
-In this section, we discuss the following:  a) an alternate imaging and reconstruction protocol for longitudinal studies, b) results on homogeneous dataset, and (c) tuning of the parameters used.
-%The presented uniform prior-based algorithm is suited to applications
-%where we wish to detect the location of new changes in an object over
-%time, and the presented spatially-varying prior-based algorithm is
-%suited to applications where we wish to observe the intricate details
-%of those new changes. %This distinction in the techniques used has not
-%been studied earlier in
-%literature~\cite{geyer2015,PICCS,Ali2018,Tan2017} to the best of our
-%knowledge.
-Even though methods such as~\cite{Hakka2019} offer the flexibility of using multiple templates, the very important issue of these templates overwhelming the current reconstruction has been largely ignored.
-We have presented a principled method of tackling this particular issue via our weights map.
-We not only estimate the location of new changes, but also compute their intensities.
-This information is then used to modulate the strength of the prior during the reconstruction of the test.
-Our results consist of 3D reconstructions from real cone-beam projections of two datasets, and both 3D and 2D reconstructions from cone-beam and parallel beam projections respectively.
-In each case, we have compared our results with those from standard back-projection algorithms~\cite{Pan2009} (FDK in case of 3D and FBP incase of 2D), and Compressed Sensing~\cite{Donoho,introCS} based reconstructions.
-An in-depth analysis of each of the results is presented in Sections~\ref{sec:results_uniform_prior} and~\ref{sec:results_spatially_varying_prior}.
-We now discuss computation times, the method that suits best when the data is homogeneous, and the effect of hyper-parameters on our reconstructions.
-
-%-----------------------------------------
-
-\subsection{Reconstruction of homogeneous data}
-\label{Sec:potato}
-%--------potato reconstruction--------------------------------------------------
+\subsection{Potato}
+\label{sec:potato}
+
+The test volume was reconstructed from a partial set of 45 real
+cone-beam projections, i.e., $5\%$ of the projection views from which
+ground truth was reconstructed. 2D reconstructions of one of the
+slices is shown in Fig.~\ref{fig:potato_2D_results}. A complete 3D
+reconstruction can be found in the supplementary material
+~\cite{supp_paper}. The red RoI in the video and images show 
+regions where both new changes and some old regions are present. The
+zoomed-in images around the major region of change (red RoI) is shown
+in Fig.~\ref{fig:potato_zoomed_2D_results}.We observe that our method
+reconstructs new structures while simultaneously reducing streak
+artefacts. Table~\ref{table:potato_ssim} shows SSIM
+of the reconstructed new regions using various
+methods.
+
 \begin{figure}[!h]
@@
 \subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_lambdaTV_0.05.png}}
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
+\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
 \caption{Reconstruction of the 2D-potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.
 The 3D reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
-\label{fig:potato_3D_results_A}
+\label{fig:potato_2D_results}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
+\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
+\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
+\label{fig:potato_zoomed_2D_results}
 \end{figure}
@@
 \end{table}
-
-While the design of the weights map in the proposed algorithm aims to
-combine the best of information from both the current measurements and
-the prior, we found FDK to be preferable when the test object has a
-simple, homogeneous structure without intricate details. One such
-dataset is the Potato dataset (described in
-Sec.~\ref{sec:datasets}). The test volume was reconstructed using
-measurements from 45 projection views, i.e., $5\%$ of the projection
-views from which ground truth was reconstructed. The selected 3D
-ground truth of template volumes, test volume, as well as the 3D
-reconstructions are shown in the supplementary
-material~\cite{supp_paper}. Fig.~\ref{fig:potato_3D_results_A} shows a
-slice from the reconstructed 3D volume. We observe that our method
-reconstructs new structures while simultaneously reducing streak
-artefacts. Table~\ref{table:potato_ssim} shows the Structure Similarity
-Index (SSIM) of the reconstructed new regions using various
-methods. We observe that FDK performs very well for smaller RoI;
-as the RoIs get bigger, the FDK reconstructions have poor SSIM due to
-strong subsampling artefacts. In contrast, the results from l1-ls and
-our method progressively improve when compared to FDK as the RoIs get
-bigger. In practice, the RoI is not known in advance and hence, one
-may choose FDK for the case of simple, homogeneous dataset with
-smaller RoI, and prefer spatially-varying prior-based reconstruction
-when the dataset is complex and RoIs are larger.
-
-%The new regions detected by different reconstruction methods are shown in Fig.~\ref{fig:weights_map_2Dpotato}.
-The lower intensities denote new regions which were assigned lower weights.
-This ensures that the new regions are reconstructed using projection measurements alone, avoiding erroneous influence of the prior.
-
-\subsection{Tuning of parameters}
-\label{subsec:k}
- $\lambda_1$ was tuned to maximize
-SSIM of the whole reconstructed test volume for l1-ls reconstruction
-of each dataset. This value was retained for uniform and
-spatially-varying prior-based reconstruction as well. The value of
-$\lambda_2$ largely depends on the amount of artefacts we aim to
-remove by using prior at the cost of their dominance in the new
-regions. This value was chosen to lie between $0-1$ for our
-datasets. Finally, the hyper-parameter $k$ defines the sensitivity of
-the weights map to the difference between the test image and the prior
-(projection of test onto the space of object-prior). When $k=0$, our
-method converges to the uniform prior method. As $k$ increases, the
-weights map starts capturing the new changes in the test, at the cost
-of detecting a few false positives i.e., false new changes. In other
-words, as the weights map becomes more sensitive to the difference
-between the test and object-prior, it becomes more noisy. In order to
-visualize the effect of the hyper-parameter $k$, we performed 2D
-reconstructions of okra dataset for different values of
+%---------------------------------------------------------
+
+\section{Discussion}
+\label{sec:discussion}
+In this section, we discuss tuning of the parameters
+used in our method. $\lambda_1$, $\lambda_2$ and $k$ are the three
+hyper-parameters that need to be chosen carefully for optimal
+reconstruction. In our experiments, $\lambda_1$ was tuned to maximize
+SSIM of the whole reconstructed test volume for TV reconstruction of
+each dataset. This value was retained for spatially-varying
+prior-based reconstruction as well. The value of $\lambda_2$ largely
+depends on the amount of artefacts we aim to remove by using
+object-prior at the cost of their dominance in the new regions. This
+value was chosen to lie between $0-3$ for our datasets. Finally, the
+hyper-parameter $k$ defines the sensitivity of the weights map to the
+difference between test image and object-prior (projection of
+test onto the space of object-prior). When $k=0$, our method 
+behaves similar to the uniform prior method discussed
+in~\cite{my_dicta_paper}. As $k$ increases, the weights map starts
+capturing new changes in the test, at the cost of detecting a few
+false positives i.e., false new changes. In other words, as the
+weights-map becomes more sensitive to the difference between the test
+and object-prior, it becomes more noisy. In order to visualize the
+effect of the hyper-parameter $k$, we performed 2D reconstructions on
+okra dataset for different values of
 $k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
-obtained for each of the $k$ values. We estimate an approximate choice
-for the optimal value of $k$ by treating one of the object-prior as
-test and reconstructing it. We also note that although the weights map
-is heavily influenced by $k$, the final reconstructions are stable for
-large variations in $k$, as seen in
-Fig.~\ref{fig:reconstructions_as_k_varies}. Alternatively, in cases
-where one wishes to completely avoid the use of this hyper-parameter,
-one can construct a binary weights-map using a learning based method
-described in the supplementary material~\cite{supp_paper}.
+obtained for each of the $k$ values and
+Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
+final reconstructions. We run our experiments for a few values of $k$
+and choose the best reconstruction based on our tolerance for noise
+in the weights-map.
+When a large number of templates are available, this parameter can be
+chosen by assuming one of the templates as test and choosing the $k$
+that gave the best reconstruction. Alternatively, in cases where one
+wishes to completely avoid the use of this hyper-parameter, one can
+construct a binary weights-map using a learning based method described
+in the supplementary material~\cite{supp_paper}.
 
@@
     \caption{2D reconstructions for varying values of $k$.
-The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_3D_results}(a)), the region where the test is different from all of the previously scanned objects.}
+The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}
 \label{fig:reconstructions_as_k_varies}
@@
 This work deals with the effective use of priors for tomographic
-reconstruction in longitudinal studies. We show that we can either use
-the uniform prior method or the spatially-varying prior method to our
-advantage, depending on our goal. We establish the context under which
-these methods can be used, as outlined in
-Fig.~\ref{fig:prior_overview}. When we wish to approximately know the
-location of new changes, we apply a uniform prior because it is
-sufficient for the task at hand. We also choose a smaller number
-of views in order to reduce radiation. In addition, we show that when
-our goal shifts to observing the details of the new changes
-accurately, we acquire projections from a moderate number of views in
-order to capture more information. We further combine this with the
-somewhat slower but more accurate technique of reconstruction-- the
+reconstruction in longitudinal studies. When the number of measurements is
+substantially low, we discuss the utility of
+using information from previous scans of the same object, as outlined in
+Fig.~\ref{fig:prior_overview}. In order to observe details of new changes
+accurately, we use a novel
 spatially-varying prior-based method. This method ensures that the
 reconstruction of localized new information in the data is not
-affected by the priors. %Based on the potato and the okra experiments,
+affected by the priors, while the other relatively stationary regions benefit from the extra prior information. %Based on the potato and the okra experiments,
 %we see that our method is able to \emph{discover both} the presence of
@@
 We have thus
-improved the state of the art by detecting these regions of change and
+improved state of the art by detecting the strength and location
+of these regions of change and
 assigning low prior weights wherever necessary. The probability of
@@
 \end{document}
+
+%---------------------------------Uniform section---------------------
+%-------------------------------------------------

### 2021-08-27 paper/post_tci_supplementary.tex
draft-1

--- 2020-07-25 paper/supplementary.tex
@@
 \newpage
-%--------------------------------------------------------------------------
-\section{An alternate method to compute weights-map}
-The value of $k$ (discussed in Sec.10(C) of the main paper) is typically dependent on the number of false positives the system can allow in exchange for the detection of more true positives (regions of new changes).
-It is this choice and not the particular type of dataset that affects the selection of $k$.
-In our work, the chosen $k$ corresponds to the one that gives minimal tolerance to false positives.\\
 
-However, in case one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using an alternate method described below.
-
-\begin{enumerate}
-\item For the purposes of training, treat one of the previously scanned images as test.
-\item Annotate the region of differences between the test and all of the previously scanned images based on domain knowledge.
-\item Compute the difference between the pilot reconstruction of the test and its projection onto the eigenspace. Let this spatial map be called `error map'.
-\item Train a Support Vector Machine (SVM) model to classify patches of this error-map image into one of the two categories: new changes present, new changes absent.
-\item Once the trained SVM model is obtained, it can be applied to generate binary weights-map for new test images in the same longitudinal study.
-\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, the prior and the pilot can be stitched by $\boldsymbol{R} = \boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
-Fig.~\ref{fig:okra_svm} shows results of this method on 2D okra dataset.
-
-  Alternatively, these binary weights can also be used in the optimization loop in Eq.~\ref{Eq:main} (corresponding to Eq.~6 in the main paper), although this approach has not been pursued here.
-
-\begin{equation}
-%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
-%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
-J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W_b}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
-\label{Eq:main}
-\end{equation}
-
-\end{enumerate}
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
-
-        \caption{}
-     \end{subfigure}
-     \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
-
-        \caption{}
-    \end{subfigure}    
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}
-
-        \caption{}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
-
-        \caption{}
-     \end{subfigure}
-   % \begin{subfigure}[b]{0.19\linewidth}
-   %     \includegraphics[width=\textwidth]{images/low_dose_prior/svm_method/prior.png}
-
-    %    \caption{}
-    % \end{subfigure}
-     \caption[Selecting $k$]{Using an alternate approach to generate (binary) weights map.
-(a)-(c) the images used as object-prior, (d) the test (310$\times$310).
-Measurements along $60$ views were taken.
-(e) error-map showing new regions, (f) detected binary weights map showing regions of new changes, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions.
-} %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates,
-\label{fig:okra_svm}
-\end{figure}
-\clearpage
 %--------------------------------Links to videos-------------------------------------------------
@@
 
-%--------------------------BIG images: TMH results
-\section{Larger images for reconstruction results}
-All the images shown in the main paper are displayed in small size due to space constraints.
-This restricts visualization of the structural details within them.
-Therefore, we present each of those images in large size here in order to view their internal structures with better clarity.
-\subsection{Liver}
-%-------RFA2 moderate views
-%\textbf{Goal: Observe details of new changes}
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
-\subcaptionbox{Spatially-varying prior}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
-\caption[Representative results-2]{Reconstruction of Liver corresponding to Figure 8 of the main paper.}
-\label{fig:RFA2_few_views_biggerIm}
-\end{figure}
-\newpage
-
-\textbf{Test image in Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-\centering
-\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}
-\captionsetup{labelformat=empty}
-\caption[Representative results-2]{\large{Test slice}}
-\label{fig:RFA2_few_views_bigger}
-\end{figure}
-\newpage
-\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}   is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-\centering
-\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}
-\captionsetup{labelformat=empty}
-\caption[Representative results-2]{\large{FBP}}
-\label{fig:RFA2_few_views_bigger}
-\end{figure}
-\newpage
-\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}   is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-\centering
-\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}
-\captionsetup{labelformat=empty}
-\caption[Representative results-2]{\large{l1-ls}}
-\label{fig:RFA2_few_views_bigger}
-\end{figure}
-\newpage
-\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-\centering
-\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}
-\captionsetup{labelformat=empty}
-\caption[Representative results-2]{\large{Spatially-varying prior method}}
-\label{fig:RFA2_few_views_bigger}
-\end{figure}
-\newpage
-
-%------------------------------------Bigger images for Sprouts------------------
-\subsection{Sprouts}
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.38\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.38\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{FDK}
-    \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.38\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{l1-ls}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.38\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{Uniform\\ Prior}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.38\linewidth}
-        \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{Spatially-Varying\\ prior}
-    \end{subfigure}
-    %\quad
-    %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of sprouts corresponding to Figure 16 of the main paper.} 
-\label{fig:sprouts_3D_results_biggerIm}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-
-\newpage
-\textbf{Test image of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-    \begin{subfigure}[b]{\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
-\captionsetup{labelformat=empty}
-        \caption{\large{Test}}
-     \end{subfigure}
-\end{figure}
-\newpage
-\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-    \begin{subfigure}[b]{\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}}
-\captionsetup{labelformat=empty}
-        \caption{\large{FDK}}
-     \end{subfigure}
-\end{figure}
-\newpage
-\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-    \begin{subfigure}[b]{\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/csIm.png}}
-\captionsetup{labelformat=empty}
-        \caption{\large{l1-ls}}
-     \end{subfigure}
-\end{figure}
-\newpage
-\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-    \begin{subfigure}[b]{\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}}
-\captionsetup{labelformat=empty}
-        \caption{\large{Uniform Prior}}
-     \end{subfigure}
-\end{figure}
-\newpage
-\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in large size for better clarity.}\\
-\begin{figure}[!h]
-    \begin{subfigure}[b]{\linewidth}
-        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}}
-\captionsetup{labelformat=empty}
-        \caption{\large{Spatially-Varying Prior}}
-     \end{subfigure}
-\end{figure}
-\newpage
-
-%--------------------------------Bigger results for Okra------------------------
-\subsection{Okra}
-
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.2\columnwidth]{../images/okra/testCropped.png}}}\hfill
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
-\subcaptionbox{l1-ls}{\includegraphics[width=0.2\columnwidth]{../images/okra/cs_cropped.png}}\hfill
-\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/prior_weighted_cropped.png}}
-\caption{Reconstruction of okra corresponding to Figure 14 of the main paper.}
-\label{fig:okra_3D_results_biggerIm}
-\end{figure}
-\newpage
-\textbf{Test image of Figure~\ref{fig:okra_3D_results_biggerIm}   is shown in large size for better clarity.}
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=0.5\columnwidth]{../images/okra/testCropped.png}
-\captionsetup{labelformat=empty}
-        \caption{\large{Test}}
-\end{figure}
-\newpage
-
-\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in large size for better clarity.}
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=0.5\columnwidth]{../images/okra/fdk_cropped.png}
-\captionsetup{labelformat=empty}
-        \caption{\large{FDK}}
-\end{figure}
-\newpage
-
-\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}   is shown in large size for better clarity.}
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=0.5\columnwidth]{../images/okra/cs_cropped.png}
-\captionsetup{labelformat=empty}
-        \caption{\large{l1-ls}}
-\end{figure}
-\newpage
-
-\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in large size for better clarity.}
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=0.5\columnwidth]{../images/okra/pca_cropped.png}
-\captionsetup{labelformat=empty}
-        \caption{\large{Uniform Prior}}
-\end{figure}
-\newpage
-
-\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}   is shown in large size for better clarity.}
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=0.5\columnwidth]{../images/okra/prior_weighted_cropped.png}
-\captionsetup{labelformat=empty}
-        \caption{\large{Spatially-Varying prior}}
-\end{figure}
-\newpage
-
-%----------------------------------Comparison with Literature------------------------
-\section{Detecting new changes directly in the measurements}
-
-Sec.2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature.
-Here we present a 2D reconstruction  result (of the test shown in Figure.~\ref{fig:comparisonLit_dataset}) to compare our method with~\cite{Lee2012}, in which the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
-This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
-However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image.
-This is shown in Figure~\ref{fig:comparisonLit_results}.
-A quantitative comparison over the region of interest is shown in Table~\ref{tab:comparisonLit}.
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-%\captionsetup{labelformat=empty}
-        \caption{Template}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/testIm_color.png}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-    \end{subfigure}
-    %\captionsetup{labelformat=empty}
-     \caption{Template and test from the Potato dataset for the reconstructions shown in Figure.~\ref{fig:comparisonLit_results}} 
-\label{fig:comparisonLit_dataset}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-\newpage
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/result_new_changes.png}
-%\captionsetup{labelformat=empty}
-        \caption{~\cite{Lee2012}:new-changes}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/result_literature_test.png}
-%\captionsetup{labelformat=empty}
-        \caption{~\cite{Lee2012}:Reconstruction}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/weightsIm_all_methods30.png}
-%\captionsetup{labelformat=empty}
-        \caption{Our weights-map}
-    \end{subfigure}
-   \quad
-        \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/weighted_pca_all_methods30.png}
-%\captionsetup{labelformat=empty}
-        \caption{Our Reconstruction}
-    \end{subfigure}
-    %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of the test in Figure~\ref{fig:comparisonLit_dataset}.
-Reconstructions were performed from 12 views.
-Gaussian noise of 0 mean and SD = $1\%$ of mean of measurements, was added to the measurements.}
-\label{fig:comparisonLit_results}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-
-\begin{table}[!h]
-  \centering
-      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}}
-  \begin{tabular}{|l|l|l|}
-\hline
- & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
-\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
-\textbf{\begin{tabular}[c]{@{}l@{}}Spatially-varying \\prior\end{tabular}} & 0.89 & 0.92 \\ \hline
-  \end{tabular}
-  \label{tab:comparisonLit}
-\end{table}
-\newpage
-%-----------------------------------Blurred results (CS)
-\section{Blurred reconstruction under limited views}
-
-The l1-ls reconstructions shown in the main paper (for example, in Figs.~14(c),~16(c) and 19(c)), appear to be blurred.
-Here, we discuss the reason for this observation by reconstructing an image from varying number of views using l1-ls (Eq.1 in the main paper).\\
-
-When the number of views is large, the reconstruction using l1-ls is indeed good, as shown below in Fig~\ref{fig:cs_blurred_48_views}.
-For the reconstructions shown below, we have tuned the $\lambda_1$ values (Figs.~\ref{fig:ssim_rmse_48_views},~\ref{fig:ssim_rmse_24_views},~\ref{fig:ssim_rmse_12_views}) and selected the one with maximum SSIM.
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/48_views/testIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/48_views/result_FBP.png}
-%\captionsetup{labelformat=empty}
-        \caption{FDK}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/48_views/result_CS_lambda0_0.40.png}
-%\captionsetup{labelformat=empty}
-        \caption{l1-ls}
-    \end{subfigure}
-    %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of potato test slice (150$\times$150) from 48 views. The $\lambda_1$ for l1-ls reconstruction was chosen to be the optimal value of 0.4 here.} 
-\label{fig:cs_blurred_48_views}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=0.9\columnwidth]{../images/potato/2D/cs_blurred_results/SSIM_RMSE_48_angles.png}
-%\captionsetup{labelformat=empty}
-\caption{SSIM and RMSE for reconstruction from 48 views for varying levels of $\lambda_1$. The optimal value of 0.4 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_48_views}}
-\label{fig:ssim_rmse_48_views}
-\end{figure}
-\newpage
-
-However, when the number of views decreases, the reconstruction using l1-ls is blurred, but with the benefit of suppressed artefacts that are otherwise present in FBP reconstruction.
-This is illustrated in Figs.~\ref{fig:cs_blurred_24_views} and~\ref{fig:cs_blurred_12_views}.
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/24_views/testIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/24_views/result_FBP.png}
-%\captionsetup{labelformat=empty}
-        \caption{FDK}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/24_views/result_CS_lambda0_2.00.png}
-%\captionsetup{labelformat=empty}
-        \caption{l1-ls}
-    \end{subfigure}
-    %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of potato test slice (150$\times$150) from 24 views. The $\lambda_1$ for l1-ls reconstruction was chosen to be the optimal value of 2 here.} 
-\label{fig:cs_blurred_24_views}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=\columnwidth]{../images/potato/2D/cs_blurred_results/SSIM_RMSE_24_angles.png}
-%\captionsetup{labelformat=empty}
-\caption{SSIM and RMSE for reconstruction from 24 views for varying levels of $\lambda_1$. The optimal value of 2 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_24_views}}
-\label{fig:ssim_rmse_24_views}
-\end{figure}
-\newpage
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/12_views/testIm.png}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/12_views/result_FBP.png}
-%\captionsetup{labelformat=empty}
-        \caption{FDK}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/2D/cs_blurred_results/12_views/result_CS_lambda0_3.00.png}
-%\captionsetup{labelformat=empty}
-        \caption{l1-ls}
-    \end{subfigure}
-    %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of potato test slice (150$\times$150) from 12 views. The $\lambda_1$ for l1-ls reconstruction was chosen to be the optimal value of 3 here.} 
-\label{fig:cs_blurred_12_views}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-As seen here, the reconstruction by l1-ls is indeed blurred when the number of views is very less. The iterative reconstruction was run until convergence (epsilon = 0.001).
-%The plots below show the SSIM and RMSE values for varying values of lambda1 for the CS (LASSO) reconstructions of the above test image.
-
-\begin{figure}[!h]
-\centering
-       \includegraphics[width=\columnwidth]{../images/potato/2D/cs_blurred_results/SSIM_RMSE_12_angles.png}
-%\captionsetup{labelformat=empty}
-\caption{SSIM and RMSE for reconstruction from 12 views for varying levels of $\lambda_1$. The optimal value of 3 was chosen to obtain the reconstruction shown in Fig.~\ref{fig:cs_blurred_12_views}}
-\label{fig:ssim_rmse_12_views}
-\end{figure}
-\newpage
-\bibliography{tci_ref}
 \end{document}

### 2021-08-29 paper/post_tci.tex
Minor syntactic edits. Changed a couple of captions

@@
   mitigate this problem by first estimating the location of new
-  regions and then imposing object-prior in \textit{only} the other
-  old regions which are similar to the prior.
+  regions and then imposing object-prior in \textit{only} old regions which are similar to the prior.
 
@@
   such as in repeated scanning for disease monitoring, or in
-  tomography-guided surgical procedures. While this is easily feasible
+  tomography-guided surgical procedures. While reconstruction is easily feasible
   when measurements are acquired from a large number of projection
@@
 fidelity~\cite{yang2018,Lin2016,Xie2017,gopal2019low} or significantly
-reduce the number of measurements required to reconstruct with
+reduce measurements required to reconstruct with
 adequate fidelity. For the latter case, there are two lines of
@@
 method as a baseline for this work. If $\boldsymbol{\mathcal{R}}$
-represents the acquisition model, then TV-regularized solution is
+represents the acquisition model, then the TV-regularized solution is
 described by one that minimizes a combination of least squares error
-and $TV$-norm of the object $\boldsymbol{x}$. This is described by
+and the $TV$-norm of the object $\boldsymbol{x}$. This is described by
 
@@
 	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
-        \caption{Illustration of the use of various priors in 
+        \caption{Illustration of the use of  priors in 
           reconstruction as the number of views reduces. For all cases,
@@
 ``changes'' that appear due to undersampling artefacts (as seen in
-Sec.4 of our supplementary material~\cite{supp_paper}).  Besides this,
+Sec.~\4 of our supplementary material~\cite{supp_paper}).  Besides this,
 since we use a statistical model with multiple object-priors, we avoid
@@
         \caption{Overview of our work.
-When the number of measurements is lower than what is conventionally used, (a) a regularization prior (such as Total Variation) alone is not sufficient to mitigate the sub-sampling artefacts.
-(b) An object-prior must be used to provide additional information.
-Here, in order to prevent a prior induced bias in the reconstruction, we propose using a spatially-varying weights-map to modulate the effect of object-prior on the final reconstruction.}
+When the number of measurements is lower than what is conventionally used, (upper part of the diagram) a regularization prior (such as Total Variation) alone is not sufficient to mitigate the sub-sampling artefacts.
+(Lower) An object-prior must be used to provide additional information, but this may induce bias from the prior.
+In this paper, in order to prevent this bias, we propose using a spatially-varying weights-map to modulate the effect of object-prior on the final reconstruction.}
  \label{fig:prior_overview}
@@
 %useful.
-This data was sourced from Tata Memorial Centre~\cite{tmh} in Parel,
-Mumbai.  This is the national comprehensive centre for the prevention,
+This data was sourced from Tata Memorial Centre (TMC) ~\cite{tmh} in Parel,
+Mumbai.  TMC is the national comprehensive centre for the prevention,
 treatment, education and research in cancer, and is recognized as one
@@
     reconstruction algorithms like the CS~\cite{lasso}, Total
-    Vairiation~\cite{TV},Algebraic Reconstruction Technique
+    Variation~\cite{TV}, Algebraic Reconstruction Technique
     (ART)~\cite{art}, Simultaneous Algebraic Reconstruction Technique
@@
      \end{subfigure}
-      \caption{For reconstruction of the test image in Fig.~\ref{fig:potato_dataset}(d) from $6$ views, these are the weights-maps (corresponding to the difference between pilot reconstruction of the test and its projection onto the eigenspace $\boldsymbol{V_\text{low}}$) constructed using different reconstruction methods individually (a-f) and collectively (g) by fusing information from all reconstruction methods, as specified in Eq.~\ref{eq:weightsEq}.
-The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
+      \caption{The motivation for multiple methods is demonstrated with a slice of the data in Fig.~\ref{fig:potato_datasett}.
+The test image in Fig.~\ref{fig:potato_dataset}(d) is reconstructed using only  $6$ paltry views.
+The weights-maps
+        %(corresponding to the difference between pilot reconstruction
+        of the test and its projection onto the eigenspace
+        $\boldsymbol{V_\text{low}}$) constructed using different
+        reconstruction methods individually (a-g) are inadequate and
+        represent different false positives. By fusing information
+        from all reconstruction methods, as specified in
+        Eq.~\ref{eq:weightsEq} we get the final weights map (h). The corresponding reconstructions appear in Fig.~\ref{fig:reconstruction_diff_methods}. 
+%The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
 }
@@
      \end{subfigure}
-      \caption{(a)-(f):Different reconstructions of~\ref{fig:potato_dataset}(d) from $6$ views.
-The magnitude and sharpness of the artefacts is different for each method.
-(g) Spatially-Varying-prior method that combines weights-map information from all other methods.
-The SSIM of these reconstructions is shown in Table.~\ref{table:potato_2D_ssim}.}
+      \caption{(a)-(f): Reconstructions of~\ref{fig:potato_dataset}(d)
+        from $6$ views. The magnitude and sharpness of the artefacts
+        are different for distinct methods. (h)
+        Spatially-Varying-prior method (from this paper) combines
+        weights-map information from all other methods. The SSIM of
+        these reconstructions is shown in
+        Table.~\ref{table:potato_2D_ssim}.}
 \label{fig:reconstructions_diff_methods}

### 2021-08-29 paper/post_tci.tex
minor typos

@@
 \usepackage[font=small,skip=2pt]{caption}
-\usepackage{boxedminipage}
+%\usepackage{boxedminipage}
 %\usepackage{algpseudocode}
@@
 ``changes'' that appear due to undersampling artefacts (as seen in
-Sec.~\4 of our supplementary material~\cite{supp_paper}).  Besides this,
+Sec.\ 4 of our supplementary material~\cite{supp_paper}).  Besides this,
 since we use a statistical model with multiple object-priors, we avoid
@@
      \end{subfigure}
-      \caption{The motivation for multiple methods is demonstrated with a slice of the data in Fig.~\ref{fig:potato_datasett}.
-The test image in Fig.~\ref{fig:potato_dataset}(d) is reconstructed using only  $6$ paltry views.
-The weights-maps
+      \caption{The motivation for multiple methods is demonstrated
+        with a slice of the data in Fig.~\ref{fig:potato_datasett}.
+        The test image in Fig.~\ref{fig:potato_dataset}(d) is
+        reconstructed using only $6$ paltry views.  The weights-maps
         %(corresponding to the difference between pilot reconstruction
-        of the test and its projection onto the eigenspace
-        $\boldsymbol{V_\text{low}}$) constructed using different
+        %of the test and its projection onto the eigenspace
+        %$\boldsymbol{V_\text{low}}$) 
+        constructed using different
         reconstruction methods individually (a-g) are inadequate and
@@
         from all reconstruction methods, as specified in
-        Eq.~\ref{eq:weightsEq} we get the final weights map (h). The corresponding reconstructions appear in Fig.~\ref{fig:reconstruction_diff_methods}. 
+        Eq.~\ref{eq:weightsEq} we get the final weights map (h). The corresponding reconstructions appear in Fig.~\ref{fig:reconstruction_diff_methods}}.
 %The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.

### 2021-09-05 paper/changes.tex
Draft-2, Made changes suggested by Prof.Sharat

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{boxedminipage}
%\usepackage{geometry}
\usepackage[colorlinks=true]{hyperref}
\title{Changes after the last submission}
\begin{document}
\maketitle
In this document, we explain the steps we have taken to address the reviews received in our previous submission to TCI. In particular, there were two major concerns:

\begin{itemize}
\item \textbf{Total-Variation being better than CS + spatially-varying prior-based reconstruction:}\\

  The goal of our previous and curent work is to provide a technique that can improve upon any chosen baseline reconstruction when measurements are few. After noting reviewer's comments, we conducted further analysis and observed that TV is indeed better suited as a baseline reconstruction method for our datasets and our subsampling choices. Hence, our current paper presents all results using TV regularization coupled with spatially-varying technique, and demonstrates its benefits over TV-only and backprojection-only methods.

\item \textbf{Comparison with Deep Learning Techniques:}\\

  In a machine learning based setting, our goal of detecting new changes is a `prediction' problem in a continuous solution space i.e., \textit{``given intensities of a voxel at various time instants in a longitudinal setting, what will be the intensity of the same voxel at the next time instant?''} This estimation can be learnt by a deep neural network only if there are hundreds if not, thousands of time instants at which the previous voxel intensities are known for each voxel. This amount of data is not available to us, and may be hard to acquire because each specimen is usually scanned only a couple of times in any longitudinal study. Further, a specific `event-of-interest' may occur just once in a longitudinal study and hence training on data of all previous time instants may be misleading. If however, we use measurements from identical and full-cycle longitudinal studies (including events-of-interest) of similar specimen (instead of the `same' specimen as we used), a deep-learning technique may be applied. We see this as an extension of using object-prior generated from the same object, and hence we have not explored this direction.

  Another avenue for using deep-networks \textit{within} our current work is to replace the currently used fixed eigenspace provided by PCA by a learnt feature basis provided by a network such as an autoencoder. For each dataset, an autoencoder may be trained to learn a specific set of latent features (this might again require atleast a few tens of volumes). We see this as a future direction of work.

\end{itemize}

\end{document}

### 2021-09-05 paper/post_tci.tex
Draft-2, Made changes suggested by Prof.Sharat

@@
 \makesavenoteenv{tabular}
+
+%\setlength{\textfloatsep}{10pt plus 1cm}
 
@@
         and~Ajit Rajwade
-\thanks{Preeti Gopal is with IITB-Monash Research Academy}
+\thanks{Preeti Gopal is currently with the Applied Artificial Intelligence Institute, Deakin University}
 \thanks{Sharat Chandran and Ajit Rajwade are with the Department of Computer Science and Engineering, IIT Bombay}
@@
   mitigate this problem by first estimating the location of new
-  regions and then imposing object-prior in \textit{only} old regions which are similar to the prior.
+  regions and then imposing object-prior in \textit{only} old regions
+  which are similar to the prior.
 
@@
 Discrete Cosine Transform (DCT).  There are multiple such
-regularization priors, of which we choose the total Variation (TV)
-method as a baseline for this work. If $\boldsymbol{\mathcal{R}}$
-represents the acquisition model, then the TV-regularized solution is
-described by one that minimizes a combination of least squares error
-and the $TV$-norm of the object $\boldsymbol{x}$. This is described by
+regularization priors, of which we had initally worked with Compressed
+Sensing based l1-ls prior~\cite{my_dicta_paper}. For the purposes of
+this paper, we use a simpler method, the total Variation (TV) as a
+baseline. If $\boldsymbol{\mathcal{R}}$ represents the acquisition
+model, then the TV-regularized solution is described by one that
+minimizes a combination of least squares error and the $TV$-norm of
+the object $\boldsymbol{x}$. This is described by
 
@@
           prior together improves the reconstruction (SSIM=0.91) when compared
-          to presence of only TV prior (SSIM=0.87) or no prior
+          to presence of TV-only prior (SSIM=0.87) or no prior
           (SSIM=0.64).}
@@
  in order to track time-evolving changes within the subject's
- interior. As seen in Fig.~\ref{fig:story} (last column, 20 views) our
- method uses the set $S$ by creating an eigenspace representation
- (Section~\ref{sec:method_spatially_varying_prior}).
+ interior.
 
@@
  using any of the prior scans \textit{as is}, or endeavoring to choose
- one ``right'' prior.
+ one ``right'' prior. In this way, this work is novel and contrasted
+ with earlier work. As seen in Fig.~\ref{fig:story} (last column, 20
+ views) our method uses the set $S$ to yield a better reconstruction
+ than regularization-only or backprojection-only methods.
 
  This paper is organized as follows. After discussing related work in
- Section~\ref{sec:related}, Section~\ref{sec:contributions} lays down
- the key contributions of this work. Details of the datasets created
- and used for validation are described in
+ Section~\ref{sec:related}, Section~\ref{sec:contributions} \textit{lays down
+ the key contributions} of this work.  In order to validate our method, we created
+ new cone-beam longitudinal CT datasets, details of which are described in
  Section~\ref{sec:datasets}. Section~\ref{sec:tmh} demonstrates the
@@
  Section~\ref{sec:results_spatially_varying_prior}. Section~\ref{sec:discussion}
- discusses tuning of the hyperparameters involved, and limitations of
- our method. Finally, we conclude with key inferences that can be
+ discusses tuning of the hyperparameters involved. %and limitations of
+ %our method.
+ Finally, we conclude with key inferences that can be
  drawn from our work in Section~\ref{sec:conclusions}.
@@
 mechanism to mitigate them (unlike the method that we propose). This
-can be seen in Sec.~4 of our supplementary material~\cite{supp_paper},
+can be seen in our supplementary material~\cite{supp_paper},
 where we have compared our method with~\cite{Lee2012}.
@@
 our technique differentiates between genuine structural changes and
-``changes'' that appear due to undersampling artefacts (as seen in
-Sec.\ 4 of our supplementary material~\cite{supp_paper}).  Besides this,
+``changes'' that appear due to undersampling artefacts.  Besides this,
 since we use a statistical model with multiple object-priors, we avoid
@@
 apart. We use the current measurements from few-views and previous
-scans of the same object. A key idea in our work is this starting
+scans of the same object.
+
+A key idea in our work is this starting
 point -- the new test volume is close to the space spanned by the
 eigenvectors of multiple representative previously scanned objects.
-
-% We utilize the uniform global eigenspace prior presented
-% in~\cite{my_dicta_paper} which assume
-
-We discuss the danger in imposing an inflexible
-constant weight (and hence an unnecessary bias) when reconstructing
-the data. As a solution, we present a method to moderate the control
-of the prior by estimating and imposing spatially-varying weights to
-the prior in order to reconstruct new structures accurately. This
-spatially-varying prior tunes the effect of the templates in different
-regions of the reconstruction.
+We then present a method to accomodate new changes in the test that
+may lie outside of this eigenspace. This will prevent an unnecessary
+bias when reconstructing the data. As a solution, our method moderates
+the control of the prior by estimating and imposing spatially-varying
+weights to the prior in order to reconstruct new structures
+accurately. This spatially-varying prior tunes the effect of the
+templates in different regions of reconstruction.
 
@@
         \caption{Overview of our work.
-When the number of measurements is lower than what is conventionally used, (upper part of the diagram) a regularization prior (such as Total Variation) alone is not sufficient to mitigate the sub-sampling artefacts.
-(Lower) An object-prior must be used to provide additional information, but this may induce bias from the prior.
-In this paper, in order to prevent this bias, we propose using a spatially-varying weights-map to modulate the effect of object-prior on the final reconstruction.}
+When the number of measurements is lower than what is conventionally used, (upper part of the diagram) a regularization prior such as Total Variation alone is not sufficient to mitigate the sub-sampling artefacts.
+(Lower) An object-prior must be used to provide additional information without introducing any bias.
+To this end, here we propose using a spatially-varying weights-map to modulate the effect of object-prior on the final reconstruction.}
  \label{fig:prior_overview}
@@
 \label{sec:datasets}
-In this section, we lay the details of all the real and simulated
-datasets created and used for this work. The first 3 datasets: Okra,
-Potato and Sprouts were acquired from the Australian National
-University (ANU). We wish to emphasize that data from commercially
-available CT machines may not be suitable because most CT scanners do
-not reveal the raw measurements, and instead output only the full
-reconstructed volumes. Moreover, the process of conversion from the
-projections to the full volumes is proprietary. Departing from this,
-we demonstrate reconstruction results (in
-Section~\ref{sec:results_spatially_varying_prior} from the following
-datasets.
+In this section, we present details of the biological and medical datasets created and used for this work. For the first two datasets namely,
+Potato and Okra, the forward imaging model was available to us and hence all reconstructions were performed from raw measurements.
+For the other two datasets namely, Sprouts and Liver, the forward imaging model was not available to us (due to commercial reasons) and hence we generated measurements from these datasets assuming a circular cone-beam imaging model for 3D and a parallel-beam imaging model for 2D.
+
+\subsection{Datasets with the forward model available}
+
+These consist of longitudinal scans of a Potato and an Okra, both acquired at the Australian National University (ANU), Canberra. \\
+
+\textbf{Potato:} This dataset consisted of four scans of the humble
+potato (Fig.~\ref{fig:potato_dataset}). While the first
+scan was taken of the undistorted potato, subsequent scans were taken
+of the same specimen, each time after drilling a new hole halfway into
+the potato. Measurements from each scan consisted of real circular
+cone-beam projections from 900 views, each of size
+150$\times$150. %Further, this alignment can be refined following
+%every update of the reconstructed test volume.
+In our experiments,
+the first 3 volumes were used to build the object-prior and the last
+volume was used as the test. The ground truth consists of volumes of
+size 150$\times$150$\times$100 reconstructed using FDK from the full
+set of 900 projection views.
+%---------------------------------------
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.235\linewidth}
+        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
+\captionsetup{labelformat=empty}
+\caption{}
+\label{fig:potato3D_test}
+     \end{subfigure}
+      \caption{Potato 3D dataset: One slice each from the scanned
+        objects that are used as templates (the first three from
+        left) and a slice from the test volume (extreme right). Notice
+        the appearance of the fourth hole in the test slice. }
+\label{fig:potato_dataset}
+\end{figure}
+
+ \textbf{Okra:} This dataset is that of an Okra specimen consisting of
+ its five scans (Fig.~\ref{fig:object-prior_test_okra}).
+Each of the scanned volumes consists of a varying number of cuts (or deformations) on the surface of the specimen.
+The specimen was kept in the same position throughout the
+ acquisitions. Measurements consisted of real circular cone-beam
+ projections from 450 views, each of size 336$\times$156.
+%In cases where such an
+%alignment is not present, all the template volumes must be pre-aligned
+%before computing the eigenspace. The test must be registered to the
+%object-prior after its preliminary pilot reconstruction.
+In our experiments, the first 4 volumes shown in
+Fig.~\ref{fig:object-prior_test_okra} were used to build the
+object-prior and the last volume was used as the test. Note that in
+the region marked red, all the templates have a deformation, and hence
+an unchecked reliance of object-prior for the reconstruction of test in this region will result in a deformation. The ground truth consists of
+volumes of size 338$\times$338$\times$123 reconstructed using the
+Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} from the full set of
+450 view projections.  \\
+ %--------------------------------okra data-------------------------------
+\begin{figure}[!h]
+  \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template4_marked.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template3_marked.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template2_marked.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.18\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/template1_marked.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.148\linewidth}
+        \fcolorbox{white}{cyan}{\includegraphics[width=\textwidth]{../images/okra/post_TCI/test_marked.png}}
+\captionsetup{labelformat=empty}
+        \caption{}
+    \end{subfigure}
+     \caption{Okra 3D dataset: One slice each from the scanned objects that are used as templates (the first four from left) and a slice from the test 
+        volume (extreme right). Notice the region marked in red box; while all slices have deformities here, the test has none.}
+\label{fig:object-prior_test_okra}
+\end{figure}
+
+\subsection{Datasets without the forward model}
+These consist of longitudinal scans of a Liver obtained from Tata
+Memorial Centre (TMC) ~\cite{tmh} in Parel, Mumbai, and longitudinal
+scans of Sprouts obtained from Australian National University.
 
@@
 %useful.
-This data was sourced from Tata Memorial Centre (TMC) ~\cite{tmh} in Parel,
-Mumbai.  TMC is the national comprehensive centre for the prevention,
+TMC is the national comprehensive centre for the prevention,
 treatment, education and research in cancer, and is recognized as one
@@
 \end{figure}
-
- \textbf{Okra:} This dataset is that of an Okra specimen consisting of
- its five scans (Fig.~\ref{fig:object-prior_test_okra}). Prior to the
- first scan, two cuts were drilled on the surface of the
- specimen. This was followed by four scans, each after introducing one
- new cut. The specimen was kept in the same position throughout the
- acquisitions. The measurements consisted of real circular cone-beam
- projections from 450 views, each of size 336$\times$156.
-%In cases where such an
-%alignment is not present, all the template volumes must be pre-aligned
-%before computing the eigenspace. The test must be registered to the
-%object-prior after its preliminary pilot reconstruction.
-In our experiments, the first 4 volumes shown in
-Fig.~\ref{fig:object-prior_test_okra} were used to build the
-object-prior and the last volume was used as the test. The ground
-truth consists of volumes of size 338$\times$338$\times$123
-reconstructed using the Feldkamp-Davis-Kress (FDK)
-algorithm~\cite{FDK} from the full set of 450 view projections.
-\\
- %--------------------------------okra data-------------------------------
-\begin{figure}[!h]
-  \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template4_marked.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template3_marked.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template2_marked.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.18\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/template1_marked.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.148\linewidth}
-        \fcolorbox{white}{cyan}{\includegraphics[width=\textwidth]{../images/okra/post_TCI/test_marked.png}}
-\captionsetup{labelformat=empty}
-        \caption{}
-    \end{subfigure}
-     \caption{Okra 3D dataset: One slice each from the scanned objects that are used as object-prior (the first four from left) and a slice from the test 
-        volume (extreme right). Notice the region marked in red box; while all slices have deformities here, the test has none.}
-\label{fig:object-prior_test_okra}
-\end{figure}
 %----------------------------------------------------
@@
 %\subsection{Simulated measurements from real-life reconstructed volumes}
-\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU,
-consists of six reconstructed volumes corresponding to six scans of an
-in-vivo sprout specimen imaged at its various stages of growth
-(Fig.~\ref{fig:object-prior_test_sprouts}).  \textit{In contrast to
-  the scientific experiment performed for the case of the okra and
-  potato where we introduced man-made defects, the changes here are
-  purely the work of nature.} In our experiments, the first 5 volumes
-were used to build the object-prior and the last volume was used as
-the test. The ground truth consists of FDK reconstructed volumes of
-size 130$\times$130$\times$130 from a set of 1800 view
-projections. For the test, cone-beam projections were generated from
-the test volume. \\
+\textbf{Sprouts:} This dataset consists of six volumes
+corresponding to six scans of an in-vivo sprout specimen imaged at its
+various stages of growth (Fig.~\ref{fig:object-prior_test_sprouts}).
+\textit{In contrast to the scientific experiment performed for the
+  case of the okra and potato where we introduced man-made defects,
+  the changes here are purely the work of nature.} In our experiments,
+the first 5 volumes were used to build the object-prior and the last
+volume was used as the test. The ground truth consists of FDK
+reconstructed volumes of size 130$\times$130$\times$130 from a set of
+1800 view projections. Test measurements were generated assuming a circular cone-beam imaging model.\\
 %-------------------------sprouts data
@@
      \end{subfigure}
-      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
-        right). Notice the structure within the red box in the test that is different from all of the other images.}
+      \caption{Sprouts 3D dataset: One slice each from the scanned
+        objects that are used as templates (the first five from
+        left) and a slice from the test (extreme right). One of the
+        many regions in the test that is different from all other
+        templates is the structure within the red box.}
 \label{fig:object-prior_test_sprouts}
@@
 
-\textbf{Potato:} This dataset consisted of four scans of the humble
-potato (Fig.~\ref{fig:potato_dataset}). While the first
-scan was taken of the undistorted potato, subsequent scans were taken
-of the same specimen, each time after drilling a new hole halfway into
-the potato. Measurements from each scan consisted of real circular
-cone-beam projections from 900 views, each of size
-150$\times$150. %Further, this alignment can be refined following
-every update of the reconstructed test volume.  In our experiments,
-the first 3 volumes were used to build the object-prior and the last
-volume was used as the test. The ground truth consists of volumes of
-size 150$\times$150$\times$100 reconstructed using FDK from the full
-set of 900 projection views.
-%---------------------------------------
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
-\captionsetup{labelformat=empty}       
- \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-\captionsetup{labelformat=empty}
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.235\linewidth}
-        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
-\captionsetup{labelformat=empty}
-\caption{}
-\label{fig:potato3D_test}
-     \end{subfigure}
-      \caption{Potato 3D dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
-        volume (extreme right). Notice the appearance of the fourth
-        hole in the test slice. }
-\label{fig:potato_dataset}
-\end{figure}
 %----------------------------------------Method-------------------------
@@
 an extra computational step. We first review the eigenspace-cum-CS
-prior-based reconstruction algorithm for a
-2D uniform prior-based reconstruction, which was
+prior-based reconstruction algorithm which was
 shown~\cite{my_dicta_paper} to be better when compared to
@@
 penalty if the estimated slice does not lie within the eigen-space of
-the object prior.
-
-Although the uniform prior can be very useful in some circumstances,
-it poses a limitation when we want accurate details of a portion of
-the new changes. While the uniform prior compensates very well for the
+the object prior. Although such a prior can be very useful in some circumstances, it poses a limitation when we want accurate details of a portion of
+the new changes. While the object prior compensates very well for the
 possible artefacts due to sparse measurements, it may dominate the
-regions with new changes masking the signal. Ideally, we will want to
+regions with new changes masking the signal. \\
+
+Ideally, we will want to
 impose the prior only in the regions that are common between the test
@@
 \end{equation}
-\begin{equation}
-  \begin{split}
-    J_{\boldsymbol{\alpha}}(\boldsymbol{\x}) \triangleq &\lVert\boldsymbol{\mathcal{R} x- y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) \\
-    &+\lambda_2\lVert(\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2
-  \end{split}
-  \end{equation}
-
-\begin{equation}
-J_{\boldsymbol{x}}(\boldsymbol{\alpha}) \triangleq \lVert\boldsymbol{\boldsymbol{W}(\boldsymbol{x}} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2.
-\end{equation}
 
@@
 in~\cite{TVReg} and available in~\cite{TVReg-lib}.
+
+\begin{equation}
+  \begin{split}
+    J_{\boldsymbol{\alpha}}(\boldsymbol{\x}) \triangleq &\lVert\boldsymbol{\mathcal{R} x- y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) \\
+    &+\lambda_2\lVert(\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2
+  \end{split}
+  \end{equation}
+
+\begin{equation}
+J_{\boldsymbol{x}}(\boldsymbol{\alpha}) \triangleq \lVert\boldsymbol{\boldsymbol{W}(\boldsymbol{x}} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2.
+\end{equation}
+
 Solving for $\boldsymbol{\alpha}$ leads to the closed form update:
@@
 \begin{equation}
-\boldsymbol{\alpha} = [(\boldsymbol{WV})^T\boldsymbol{WV}]^{-1}.\boldsymbol{V}^T(\boldsymbol{W}^T\boldsymbol{W}(\boldsymbol{x} - \boldsymbol{\mu}))
+\boldsymbol{\alpha} = [(\boldsymbol{WV})^T\boldsymbol{WV}]^{-1}\boldsymbol{V}^T(\boldsymbol{W}^T\boldsymbol{W}(\boldsymbol{x} - \boldsymbol{\mu}))
 \end{equation}
@@
   \item Perform pilot reconstructions of the test using $M$ different
-    reconstruction algorithms like the CS~\cite{lasso}, Total
+    reconstruction algorithms like the CS~\cite{lasso} with any
+    suitable sparsity domain such as wavelets (Haar) or  DCT, Total
     Variation~\cite{TV}, Algebraic Reconstruction Technique
@@
 
-\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights:}
-%-----------------------------potato 2D weights
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_fbp30.png}
-        \caption{FBP}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_cs_dct30.png}
-        \caption{(l1-ls)-DCT}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_cs_wavelet30.png}
-        \caption{(l1-ls)-Haar}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_art30.png}
-        \caption{ART}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_sart30.png}
-        \caption{SART}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_sirt30.png}
-        \caption{SIRT}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_tv30.png}
-        \caption{TV}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_all_methods30.png}
-        \caption{combined}
-     \end{subfigure}
-      \caption{The motivation for multiple methods is demonstrated
-        with a slice of the data in Fig.~\ref{fig:potato_datasett}.
-        The test image in Fig.~\ref{fig:potato_dataset}(d) is
-        reconstructed using only $6$ paltry views.  The weights-maps
-        %(corresponding to the difference between pilot reconstruction
-        %of the test and its projection onto the eigenspace
-        %$\boldsymbol{V_\text{low}}$) 
-        constructed using different
-        reconstruction methods individually (a-g) are inadequate and
-        represent different false positives. By fusing information
-        from all reconstruction methods, as specified in
-        Eq.~\ref{eq:weightsEq} we get the final weights map (h). The corresponding reconstructions appear in Fig.~\ref{fig:reconstruction_diff_methods}}.
-%The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
-}
-\label{fig:weights_map_2Dpotato}
-\end{figure}
-%-----------------------------potato 2D weights
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/fbp.png}
-        \caption{FBP}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/cs_dct.png}
-        \caption{(l1-ls)-DCT}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/cs_wavelet.png}
-        \caption{(l1-ls)-Haar}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/art.png}
-        \caption{ART}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/sart.png}
-        \caption{SART}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/sirt.png}
-        \caption{SIRT}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/tv.png}
-        \caption{TV}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weighted_pca_all_methods30.png}
-        \caption{combined}
-     \end{subfigure}
-      \caption{(a)-(f): Reconstructions of~\ref{fig:potato_dataset}(d)
-        from $6$ views. The magnitude and sharpness of the artefacts
-        are different for distinct methods. (h)
-        Spatially-Varying-prior method (from this paper) combines
-        weights-map information from all other methods. The SSIM of
-        these reconstructions is shown in
-        Table.~\ref{table:potato_2D_ssim}.}
-\label{fig:reconstructions_diff_methods}
-\end{figure}
+%----------------------------------------Results-----------------------
+\section{Results}
+\label{sec:results_spatially_varying_prior}
+
+In this section, we first illustrate the advantage of using multiple types of eigenspaces for the computation of weights map, and then present reconstruction results on all datasets.
+For quatitative evaluation, we compute the Structural Similarity Index Metric\footnote{Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to (structure, contrast, intensity): $(0.7,0.2,0.1)$.} (SSIM)~\cite{ssim}.
+
+\subsection{Motivation for the use of multiple types of eigenspaces for the computation of weights}
 
@@
 2D reconstruction of a test slice from the potato dataset.
-Fig.~\ref{fig:potato_dataset} shows the test and template
+Fig.~\ref{fig:potato_data_2D} shows the test and template
 slices. Fig.~\ref{fig:weights_map_2Dpotato} shows the weights-maps
@@
 %---------------------------------------
+
+%-----------------------------potato data
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
+\captionsetup{labelformat=empty}       
+ \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+\captionsetup{labelformat=empty}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.235\linewidth}
+        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
+\captionsetup{labelformat=empty}
+        \caption{}
+\label{fig:potato_test}
+     \end{subfigure}
+      \caption{Dataset for illustrating the use of multiple eigenspaces: One slice each from the scanned objects (the first three from left) and a slice from the test volume (extreme right).
+Notice the appearance of the fourth hole in the test slice.
+}
+\label{fig:potato_data_2D}
+\end{figure}
+
+%-----------------------------potato 2D weights
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_fbp30.png}
+        \caption{FBP}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_cs_dct30.png}
+        \caption{CS-DCT}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_cs_wavelet30.png}
+        \caption{CS-Haar}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_art30.png}
+        \caption{ART}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_sart30.png}
+        \caption{SART}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_sirt30.png}
+        \caption{SIRT}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_tv30.png}
+        \caption{TV}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weightsIm_all_methods30.png}
+        \caption{This paper}
+     \end{subfigure}
+      \caption{The motivation for multiple methods is demonstrated
+        with a slice of the data in Fig.~\ref{fig:potato_data_2D}.
+        The test image in Fig.~\ref{fig:potato_data_2D}(d) is
+        reconstructed using only $6$ paltry views.  The weights-maps
+        %(corresponding to the difference between pilot reconstruction
+        %of the test and its projection onto the eigenspace
+        %$\boldsymbol{V_\text{low}}$) 
+        constructed using different
+        reconstruction methods individually (a-g) are inadequate and
+        represent different false positives. By fusing information
+        from all reconstruction methods, as specified in
+        Eq.~\ref{eq:weightsEq} we get the final weights map (h). The corresponding reconstructions appear in Fig.~\ref{fig:reconstructions_diff_methods}}.
+%The weights-maps are different because the reconstruction artefacts of the new structures in test image will be different for every reconstruction method used, as seen in Fig.~\ref{fig:reconstructions_diff_methods}.
+}
+\label{fig:weights_map_2Dpotato}
+\end{figure}
+%-----------------------------potato 2D weights
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/fbp.png}
+        \caption{FBP}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/cs_dct.png}
+        \caption{CS-DCT}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/cs_wavelet.png}
+        \caption{CS-Haar}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/art.png}
+        \caption{ART}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/sart.png}
+        \caption{SART}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/sirt.png}
+        \caption{SIRT}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/tv.png}
+        \caption{TV}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/post_tci/comparison/weighted_pca_all_methods30.png}
+        \caption{This paper}
+     \end{subfigure}
+      \caption{(a)-(f): Reconstructions of~\ref{fig:potato_data_2D}(d)
+        from $6$ views. The magnitude and sharpness of the artefacts
+        are different for distinct methods. (h)
+        Spatially-Varying-prior method (from this paper) combines
+        weights-map information from all other methods. The SSIM of
+        these reconstructions is shown in
+        Table.~\ref{table:potato_2D_ssim}.}
+\label{fig:reconstructions_diff_methods}
+\end{figure}
+%----------------------------------------------
 \begin{table}[!h]
@@
 \caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ground-truth (ideal reconstruction) is 1.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
 \hline
- Fig.~\ref{fig:reconstructions_diff_methods}  & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
-  & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
+  \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
+ 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
 \end{tabular}
@@
 
-%----------------------------------------Results-----------------------
-\section{Results}
-\label{sec:results_spatially_varying_prior}
-We present results on 2D and 3D synthetic as well as real
-tomographic data of biological and medical specimens.
-
-\subsection{\textbf{CT-guided radio-ablation study}}
+\subsection{Reconstruction of datasets with forward model available}
+\subsubsection{\textbf{Potato}}
+\label{Sec:potato_spatially_varying}
+
+The test volume was reconstructed from a partial set of 45 real
+cone-beam projections, i.e., $5\%$ of the $900$ projection views from which
+ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
+slices is shown in Fig.~\ref{fig:potato_2D_results}. A complete 3D
+reconstruction can be found in the supplementary material
+~\cite{supp_paper}. The red RoI spans
+7 consecutive slices where the test is different from all of the
+previously scanned objects. The zoomed-in images around the major
+region of change (red RoI) is shown in
+Fig.~\ref{fig:potato_zoomed_2D_results}.We observe that our method
+reconstructs new structures while simultaneously reducing streak
+artefacts. Table~\ref{table:potato_ssim} shows SSIM of the
+reconstructed new regions using various methods.
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/testIm_paper.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_lambdaTV_0.05.png}}
+\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
+\caption{Reconstruction of potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.}
+\label{fig:potato_2D_results}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
+\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
+\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
+\label{fig:potato_zoomed_2D_results}
+\end{figure}
+%-------------------------------------------------------------------------
+\begin{table}[!h]
+  \centering
+  \caption{SSIM of reconstructed potato from various
+    methods. SSIM of ground-truth (ideal reconstruction) is 1.}
+\begin{tabular}{|l|c|c|c|c|c|}
+\hline &
+\textbf{Backprojection} & \textbf{TV} &
+\textbf{This paper} \\ \hline \textbf{2D} & 0.52
+& 0.92 & \textcolor{red}{0.97} \\ \hline \textbf{3D} & 0.58 & 0.75 & \textcolor{red}{0.84}
+\\ \hline
+\end{tabular}
+\label{table:potato_ssim}
+\end{table}
+
+%--------------------------Okra-- results
+\subsubsection{\textbf{Okra}}
+\label{Sec:okra_spatially_varying}
+The test volume was reconstructed from a partial set of 45 real
+cone-beam projections, i.e., $10\%$ of the $450$ projection views from which
+ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
+slices is shown in Fig.~\ref{fig:okra_2D_results}. A complete 3D
+reconstruction can be found in in the supplementary material
+~\cite{supp_paper}. The red RoI spans 7 consecutive slices where the
+test is different from all of the previously scanned objects. A
+zoomed-in region around the major region of change (red RoI) is shown
+in Fig.~\ref{fig:okra_zoomed_2D_results}. As in the test, the
+reconstruction by spatially-varying method shows the absence of the
+deformity and better removal of sub-sampling artefacts when compared
+to FDK and TV. This is also seen in the SSIM values in
+Table~\ref{table:okra_ssim}.
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
+\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/FBP_cropped.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/TV_cropped.png}}
+%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
+\caption{Reconstruction of okra from 48 projection views
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
+\label{fig:okra_2D_results}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.22\columnwidth]{../images/okra/post_TCI/2D/48_views/test_zoomed.png}}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/fbp_zoomed.png}}
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/tv_zoomed.png}}
+%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
+\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_pca_zoomed.png}}
+\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:okra_2D_results}. }
+\label{fig:okra_zoomed_2D_results}
+\end{figure}
+
+%---------------------------------------
+\begin{table}[!h]
+  \centering
+  \caption{SSIM of reconstructed okra from various
+    methods. SSIM of ground-truth (ideal reconstruction) is 1.}
+\begin{tabular}{|l|c|c|c|c|c|}
+\hline &
+\textbf{Backprojection} & \textbf{TV} &
+\textbf{This paper} \\ \hline \textbf{2D} & 0.46
+& 0.50 & \textcolor{red}{0.74} \\ \hline \textbf{3D} & 0.69 & 0.74 & \textcolor{red}{0.78}
+\\ \hline
+\end{tabular}
+\label{table:okra_ssim}
+\end{table}
+
+\subsection{Reconstruction of datasets without forward model}
+\subsubsection{\textbf{Liver:}}
 \label{sec:tmh}
 
-We first show how our technique is useful in a
-real-life medical longitudinal study. Here, our data consists of
+Here we show how our technique is useful in a
+real-life medical longitudinal study. Our data consists of
 successive scans of the liver taken during a radio-frequency ablation
@@
 \subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
-\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
-\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
-\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
+\subcaptionbox{Backprojection\\no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
+\subcaptionbox{This paper}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
 \caption{\small{ Reconstruction of `test' (slice 7) from Fig.~\ref{fig:RFA2_test_object-prior} from only 30 views, using (b) FBP and no prior resulting in streaks (c) TV resulting in blurred bone structures and (d) spatially varying object-prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks.
-The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.
-(e) shows the computed weights map used for reconstruction.
-Darker intensities indicate lower weights to prior as these are the regions of new changes.}}
+The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.}}
 \label{fig:tmh_2D_results}
 \end{figure}
+
+%\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
 
@@
 \subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/test_zoomed.png}}}\hfill
-\subcaptionbox{FBP}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp_zoomed.png}}\hfill
-\subcaptionbox{TV}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_zoomed.png}}\hfill
-\subcaptionbox{Spatially\\varying prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_pca_zoomed.png}}
+\subcaptionbox{Backprojection\\no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp_zoomed.png}}\hfill
+\subcaptionbox{TV, no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_zoomed.png}}\hfill
+\subcaptionbox{This paper}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_pca_zoomed.png}}
 \caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:tmh_2D_results}.}
@@
   \caption{SSIM of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ground-truth (ideal reconstruction), SSIM equals 1.}
-\begin{tabular}{|l|c|c|c|c|c|}
-\hline &
-\textbf{Backprojection} & \textbf{TV} &
-\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
-    TV\end{tabular}} \\ \hline \textbf{2D} & 0.73
+\begin{tabular}{|l|c|c|c|c|}
+\hline \textbf{Backprojection} & \textbf{TV} &
+\textbf{This paper} \\ \hline  0.73
 & 0.91 & \textcolor{red}{0.95} \\ \hline 
@@
 
-\subsubsection{\textbf{Okra}}
-\label{Sec:okra_spatially_varying}
-The test volume was reconstructed from a partial set of 45 real
-cone-beam projections, i.e., $10\%$ of the projection views from which
-ground truth was reconstructed. 2D reconstructions of one of the
-slices is shown in Fig.~\ref{fig:okra_2D_results}. A complete 3D
-reconstruction can be found in in the supplementary material
-~\cite{supp_paper}. The red RoI in the video and images show the
-regions where new changes are present. A zoomed-in region around the
-major region of change (red RoI) is shown in
-Fig.~\ref{fig:okra_zoomed_2D_results}. As in the test, the
-reconstruction by spatially-varying method shows the absence of the
-deformity and better removal of sub-sampling artefacts when compared
-to FDK and TV. This is also seen in the SSIM values in
-Table~\ref{table:okra_ssim}.
-
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
-\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/FBP_cropped.png}}
-\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/TV_cropped.png}}
-%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
-\caption{Reconstruction of 2D okra from 48 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
-3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
-\label{fig:okra_2D_results}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.22\columnwidth]{../images/okra/post_TCI/2D/48_views/test_zoomed.png}}}
-\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/fbp_zoomed.png}}
-\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/tv_zoomed.png}}
-%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_pca_zoomed.png}}
-\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:okra_2D_results}. }
-\label{fig:okra_zoomed_2D_results}
-\end{figure}
-
-%---------------------------------------
-\begin{table}[!h]
-  \centering
-  \caption{SSIM of reconstructed okra from various
-    methods. For 3D, the RoI spans 7 consecutive slices where the test is
-    different from all of the previously scanned objects. SSIM of ground-truth (ideal reconstruction) is 1.}
-\begin{tabular}{|l|c|c|c|c|c|}
-\hline &
-\textbf{Backprojection} & \textbf{TV} &
-\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
-    TV\end{tabular}} \\ \hline \textbf{2D} & 0.46
-& 0.50 & \textcolor{red}{0.74} \\ \hline \textbf{3D} & 0.69 & 0.74 & \textcolor{red}{0.78}
-\\ \hline
-\end{tabular}
-\label{table:okra_ssim}
-\end{table}
-
 \subsubsection{\textbf{Sprouts}}
@@
 The test volume was reconstructed from partial set of 45 real
-cone-beam projections, i.e., $2.5\%$ of the projection views from
-which ground truth was reconstructed. The selected 3D ground truth of
+cone-beam projections, i.e., $2.5\%$ of the $1800$ projection views from
+which ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). The selected 3D ground truth of
 template volumes, test volume, as well as the 3D reconstructions are
@@
 \subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
-\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
-\caption{Reconstruction of 2D sprouts from 20 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
-3D reconstructed volumes can be viewed  in the supplementary material ~\cite{supp_paper}.}
+\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
+\caption{Reconstruction of sprouts from 20 projection views
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
 \label{fig:sprouts_2D_results}
@@
 %\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
+\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
 \caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
@@
   \caption{SSIM of reconstructed sprouts from various
-    methods. For 3D, the RoI spans 7 consecutive slices where the test is
-    different from all of the previously scanned objects. The SSIM of ground-truth (ideal reconstruction) is 1.}
+    methods. The SSIM of ground-truth (ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
 \hline &
-\textbf{Backprojection} & \textbf{TV} &
-\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
-    TV\end{tabular}} \\ \hline \textbf{2D} & 0.67
+\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
+ \\ \hline \textbf{2D} & 0.67
 & 0.82 & \textcolor{red}{0.86} \\ \hline \textbf{3D} & 0.67 & 0.73 & \textcolor{red}{0.82}
@@
 %--------------------------------------------------------------------------
-\subsection{Potato}
-\label{sec:potato}
-
-The test volume was reconstructed from a partial set of 45 real
-cone-beam projections, i.e., $5\%$ of the projection views from which
-ground truth was reconstructed. 2D reconstructions of one of the
-slices is shown in Fig.~\ref{fig:potato_2D_results}. A complete 3D
-reconstruction can be found in the supplementary material
-~\cite{supp_paper}. The red RoI in the video and images show 
-regions where both new changes and some old regions are present. The
-zoomed-in images around the major region of change (red RoI) is shown
-in Fig.~\ref{fig:potato_zoomed_2D_results}.We observe that our method
-reconstructs new structures while simultaneously reducing streak
-artefacts. Table~\ref{table:potato_ssim} shows SSIM
-of the reconstructed new regions using various
-methods.
-
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/testIm_paper.png}}}
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp.png}}
-\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_lambdaTV_0.05.png}}
-\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
-\caption{Reconstruction of the 2D-potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.
-The 3D reconstructed volumes can be viewed in the supplementary material~\cite{supp_paper}.}
-\label{fig:potato_2D_results}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
-\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
-\subcaptionbox{Spatially-\\Varying prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
-\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
-\label{fig:potato_zoomed_2D_results}
-\end{figure}
-%-------------------------------------------------------------------------
-\begin{table}[!h]
-  \centering
-  \caption{SSIM of reconstructed potato from various
-    methods. For 3D, the RoI spans 7 consecutive slices where the test is
-    different from all of the previously scanned objects. SSIM of ground-truth (ideal reconstruction) is 1.}
-\begin{tabular}{|l|c|c|c|c|c|}
-\hline &
-\textbf{Backprojection} & \textbf{TV} &
-\textbf{\begin{tabular}[c]{@{}c@{}}Spatially Varying\\prior +
-    TV\end{tabular}} \\ \hline \textbf{2D} & 0.52
-& 0.92 & \textcolor{red}{0.97} \\ \hline \textbf{3D} & 0.58 & 0.75 & \textcolor{red}{0.84}
-\\ \hline
-\end{tabular}
-\label{table:potato_ssim}
-\end{table}
+
 %---------------------------------------------------------
@@
 test onto the space of object-prior). When $k=0$, our method 
-behaves similar to the uniform prior method discussed
-in~\cite{my_dicta_paper}. As $k$ increases, the weights map starts
+behaves similar to the reconstruction using TV-only regularization. As $k$ increases, the weights map starts
 capturing new changes in the test, at the cost of detecting a few

### 2021-09-05 paper/post_tci_supplementary.tex
Draft-2, Made changes suggested by Prof.Sharat

@@
 \usepackage{subcaption}
+
+\usepackage{boxedminipage}
 %\usepackage{geometry}
@@
 \newpage
+%------------------------------------------------------------------------------
+\section{An alternate method to compute weights-map}
+The value of $k$ (discussed in Sec.7 of the main paper) is typically dependent on the number of false positives the system can allow in exchange for the detection of more true positives (regions of new changes).
+It is this choice and not the particular type of dataset that affects the selection of $k$.
+In our work, the chosen $k$ corresponds to the one that gives minimal tolerance to false positives.\\
+
+However, in case one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using an alternate method described below.
+
+\begin{enumerate}
+\item For the purposes of training, treat one of the previously scanned images as test.
+\item Annotate the region of differences between the test and all of the previously scanned images based on domain knowledge.
+\item Compute the difference between the pilot reconstruction of the test and its projection onto the eigenspace. Let this spatial map be called `error map'.
+\item Train a Support Vector Machine (SVM) model to classify patches of this error-map image into one of the two categories: new changes present, new changes absent.
+\item Once the trained SVM model is obtained, it can be applied to generate binary weights-map for new test images in the same longitudinal study.
+\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, the prior and the pilot can be stitched by $\boldsymbol{R} = \boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
+Fig.~\ref{fig:okra_svm} shows results of this method on 2D okra dataset.
+
+  Alternatively, these binary weights can also be used in the below optimization, although this approach has not been pursued here.
+
+\begin{equation}
+%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
+%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
+J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W_b}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
+\label{Eq:main}
+\end{equation}
+
+\end{enumerate}
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
+
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
+
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
+
+        \caption{}
+     \end{subfigure}
+     \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
+
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
+
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
+
+        \caption{}
+    \end{subfigure}    
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}
+
+        \caption{}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.31\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
+
+        \caption{}
+     \end{subfigure}
+   % \begin{subfigure}[b]{0.19\linewidth}
+   %     \includegraphics[width=\textwidth]{images/low_dose_prior/svm_method/prior.png}
+
+    %    \caption{}
+    % \end{subfigure}
+     \caption[Selecting $k$]{Using an alternate approach to generate (binary) weights map.
+(a)-(c) the images used as object-prior, (d) the test (310$\times$310).
+Measurements along $60$ views were taken.
+(e) error-map showing new regions, (f) detected binary weights map showing regions of new changes, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions.
+} %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates,
+\label{fig:okra_svm}
+\end{figure}
+\clearpage
 
@@
 \section{Links to view our 3D reconstructions}
-The 3D reconstructions, corresponding to the images shown in Figs.~14,~16 and 19 in the main paper, can be better visualized in the form of a video.
-Hence, please refer to the following videos to view the 3D datasets and reconstruction results:
+Reconstructions for the 3D datasets shown in Figs.~3,~4 and 6 in the main paper can be better visualized in the form of a video. Please refer to the following links to view the reconstruction results:
 
@@
 
-  \url{https://www.dropbox.com/sh/x3yjfzsc5633d1t/AAAaVOXvTbc06a2DomPO1kSna?dl=0}\\
+  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}\\
 \item \textbf{Potato:} \\
 
-  \url{https://www.dropbox.com/sh/6mja5uh8fa2h0fc/AAA2h4VsLxAiXcEIhmTlM1xha?dl=0}\\
+  \url{https://www.dropbox.com/sh/w16j7pvud2lbrpx/AACCJLxgoAurT2vVKIdu-MwFa?dl=0}\\
 \item \textbf{Sprouts:}\\
 
-  \url{https://www.dropbox.com/sh/qtgeyckvbxiaz3s/AADhR2zRUUN4qXSXraErcqSea?dl=0}\\
+  \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}\\
 \end{itemize}
 
+\clearpage
 \newpage
 
+%----------------------------------Comparison with Literature------------------------
+\section{Detecting new changes directly in the measurements}
+
+Sec.2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature.
+Here we present a 2D reconstruction  result (of the test shown in Figure.~\ref{fig:comparisonLit_dataset}) to compare our method with~\cite{Lee2012}, in which the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
+This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
+However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image.
+This is shown in Figure~\ref{fig:comparisonLit_results}.
+A quantitative comparison over the region of interest is shown in Table~\ref{tab:comparisonLit}.
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+%\captionsetup{labelformat=empty}
+        \caption{Template}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/testIm_color.png}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Template and test from the Potato dataset for the reconstructions shown in Figure.~\ref{fig:comparisonLit_results}} 
+\label{fig:comparisonLit_dataset}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+\newpage
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/result_new_changes.png}
+%\captionsetup{labelformat=empty}
+        \caption{~\cite{Lee2012}:new-changes}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/result_literature_test.png}
+%\captionsetup{labelformat=empty}
+        \caption{~\cite{Lee2012}:Reconstruction}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/weightsIm_all_methods30.png}
+%\captionsetup{labelformat=empty}
+        \caption{Our weights-map}
+    \end{subfigure}
+   \quad
+        \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/weighted_pca_all_methods30.png}
+%\captionsetup{labelformat=empty}
+        \caption{Our Reconstruction}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Reconstruction of the test in Figure~\ref{fig:comparisonLit_dataset}.
+Reconstructions were performed from 12 views.
+Gaussian noise of 0 mean and SD = $1\%$ of mean of measurements, was added to the measurements.}
+\label{fig:comparisonLit_results}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\begin{table}[!h]
+  \centering
+      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}}
+  \begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
+\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
+\textbf{\begin{tabular}[c]{@{}l@{}}Spatially-varying \\prior\end{tabular}} & 0.89 & 0.92 \\ \hline
+  \end{tabular}
+  \label{tab:comparisonLit}
+\end{table}
+\clearpage
+\newpage
+
+\section{Motivation for using multiple eigenspaces}
+
+Here we present a schematic explaining the advantage of using multiple eigenspaces within the
+proposed spatially-varying reconstruction technique.\\
+
+\noindent \begin{boxedminipage}{\textwidth} 
+{\bf Schematic 1}: Motivation behind our algorithm. (The plus $\oplus$ and the
+minus $\ominus$ operators are placeholders; precise details available
+in Section~5 of the main paper). 
+%\vspace{0.2cm}
+
+{\small
+ Let \textcolor{blue}{prior $Q:=$ old regions ($O$)}\\
+ Let \textcolor{blue}{test volume $\boldsymbol{x}:=$ old regions ($O$) $\oplus$ new regions ($N$)}\\
+% \textbf{Steps:}     
+    \begin{enumerate}
+\item  Compute pilot reconstruction of $\boldsymbol{x}$.
+Let this be called $X$.\\ \textcolor{blue}{$X = O \oplus N \oplus Ar(O) \oplus Ar(N)$}, where \\ \textcolor{blue}{$Ar(O)$} denote the reconstruction artefacts that depend on the old regions, the imaging geometry and the reconstruction method, and\\
+ \textcolor{blue}{$Ar(N)$} denote the reconstruction artefacts that depend on the new regions, imaging geometry and the reconstruction method.
+\item  Note that \textcolor{blue}{$Q \ominus X = N \oplus Ar(O) \oplus Ar(N)$} gives the new regions, but along with lots of artefacts due to the imaging geometry (sparse views).
+To eliminate these unwanted artefacts, compute \textcolor{blue}{$Y = Q \oplus Ar(O)$} by simulating projections from $Q$ using the same imaging geometry used to scan $\boldsymbol{x}$, and then reconstructing a lower quality prior volume $Y$.
+    \item Note that \textcolor{blue}{$Y \ominus X = N \oplus Ar(N)$} contains the artefacts due to the new regions only.
+These are different for different reconstruction methods.
+To eliminate these method dependent artefacts, compute $Y$ and $X$ using different reconstruction methods.
+Let these be denoted by $Y^j$ and $X^j$ respectively.
+    \item Compute
+\vspace{-0.2cm}
+           \textcolor{blue}{\begin{equation*}
+            Y^1 \ominus X^1 = N \oplus Ar^1(N)
+           \end{equation*}
+\vspace{-0.5cm}
+           \begin{equation*}
+            Y^2 \ominus X^2 = N \oplus Ar^2(N)
+           \end{equation*}}
+\vspace{-0.4cm}
+   \item  New regions are obtained by computing
+\vspace{-0.2cm}
+          \textcolor{blue}{\begin{equation*}
+          (Y^1 \ominus X^1)\cap(Y^2 \ominus X^2)= N
+          \end{equation*}}   
+\vspace{-0.5cm}
+    \item Finally, assign space-varying weights $\boldsymbol{W}$ based on step $5$.
+    \end{enumerate}
+\label{algo:newRegionDetection}
+}
+\end{boxedminipage}
+\newpage
+
+\bibliography{tci_ref}
 \end{document}

### 2021-09-05 paper/changes.tex
Small changes

@@
 
-  In a machine learning based setting, our goal of detecting new changes is a `prediction' problem in a continuous solution space i.e., \textit{``given intensities of a voxel at various time instants in a longitudinal setting, what will be the intensity of the same voxel at the next time instant?''} This estimation can be learnt by a deep neural network only if there are hundreds if not, thousands of time instants at which the previous voxel intensities are known for each voxel.
+  In a machine learning based setting, our goal of detecting new changes is a `prediction' problem in a continuous solution space i.e., \textit{``given intensities of a voxel at various time instants in a longitudinal setting and partial measurements of the voxel at the current time, what will be the intensity of the same voxel at the current time instant?''} This estimation can be learnt by a deep neural network only if there are hundreds if not, thousands of time instants at which the previous voxel intensities are known for each voxel.
 This amount of data is not available to us, and may be hard to acquire because each specimen is usually scanned only a couple of times in any longitudinal study.
+
   Further, a specific `event-of-interest' may occur just once in a longitudinal study and hence training on data of all previous time instants may be misleading.

### 2021-09-10 paper/notes.tex
added notes

\documentclass{article}
\usepackage{amsmath,mathtools}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{boxedminipage}
%\usepackage{geometry}
\usepackage[colorlinks=true]{hyperref}
\title{Notes}
\begin{document}
\maketitle
\section{Computation of Weights map}

\begin{enumerate}
\item The method currently used in paper (Method-1) is:

\begin{equation}
  \boldsymbol{W_v}(x,y,z) = \frac{1}{1+k(\min_{j}|X^j(x,y,z) - P^j(x,y,z)|)}.
  \label{eq:weightsEq}
\end{equation}

\item 
  Let $X_i$ be pilot reconstruction by $i^{th}$ method.\\
  Let $P_i$ be projection of $X_i$ on eigen-space of templates reconstructed using $i^{th}$ method.\\
  If $|X_i-P_i|$ is high, it denotes a new region (region of interest).\\
  If $|X_i-P_i|$ is low, it denotes an old region (where test=templates).
\item \textbf{Illustration of the problem in current method:}\\
  Let there be $6$ different pilot techniques.\\
  Let image intensities be in the range $(0,255)$.\\
  \textbf{Case 1:} Let $|X_i-P_i|$ for each of these methods be $180, 149, 230, 144, 160, 150$. Here, all methods indicate the presence of a new region.
  As per, Eq.~\ref{eq:weightsEq}, $min(.)$ gives $144$. Ideally, we want to select $230$ since this denotes the presence of new region with highest confidence.\\
  \textbf{Case 2: }Now let $|X_i-P_i|$ for each of the methods be $150, 20, 5, 101, 56, 17$. Here most methods (those giving $20, 5, 17, 56$ indicate no presence of new region. However, there are (two false positives) two methods (those giving $101, 150$) that denote the presence of new region.\\
  As per Eq.~\ref{eq:weightsEq}, $min(.)$ gives $5$ which is correct.\\

\item \textbf{Method to correct inaccuracy in Case 1:}\\
  Cluster the $|X_i-P_i|$ into two clusters $C_1$ and $C_2$, with $C_1$ indicating the cluster with lower mean-intensity.\\
  If $C_1$ has more elements than $C_2$, then most methods are indicating that there are no new structures. Here, pick the $min(.)$ of $C_1$ to select the value that indicates no new structures with maximum confidence (i.e., least difference between $X$ and $P$) .\\
  If $C_1$ has fewer elements than $C_2$, then most methods indicate presence of new structure. Here, choose $max(.)$  of $C_2$ to select the value that indicates new structure with maximum confidence (i.e., largest difference between $X$ and $P$).\\

\item However, inorder to create two clusters, we need a threshold.   
\item \textbf{Results using the new method}:\\
  Let threshold be 100.\\
  \textbf{Case 1:} Two clusters are $\{\emptyset\}$ and $\{180, 149, 230, 144, 160, 150\}$. Here, $max(.)$ on $C_2$ will give 230, as expected.\\
  \textbf{Case 2:} Two clusters are $\{20, 5, 56, 17\}$ and $\{150, 101\}$. Here, $C_1$ has more elements. There, we take a $min(.)$ and get $5$ ( same as our current method).

\item {\textbf{Method-2:}}\\

\[
     \boldsymbol{W_v}(x,y,z)= 
\begin{dcases}
    \frac{1}{(1+k(\min_{j\in C_1}|X^j(x,y,z) - P^j(x,y,z)|))},& \text{if } |C_1|>|C_2|\\
    \frac{1}{(1+k(\max_{j\in C_2}|X^j(x,y,z) - P^j(x,y,z)|))},              & \text{otherwise}
\end{dcases}
\]

\item \textbf{Method-3:}\\
  \begin{equation}
    \boldsymbol{W_v}(x,y,z) = \frac{1}{1+k(\textrm{median}_{j}|X^j(x,y,z) - P^j(x,y,z)|)}.
    \label{eq:weightsEqMethod3}
  \end{equation}

  No threshold is needed here. Accuracy of this method may be better than method-1 and worse than method-2.\\

  \textbf{Case 1:} Ordered set = $\{144, 149, 150, 160, 180, 230\}$. Median $= 155$. (Method-1 gives 144. Method-2 gives 230;  Ideal value is 230.)\\
  \textbf{Case 2:} Ordered set = $\{5, 20, 17, 56, 101, 150\}$. Median $= 36.5$ (Method-1 gives 5, Method-2 gives 5. Ideal value is 5.)

\end{enumerate}

%-------------------------------------------------------------------------------
\section{Computing sufficient level of subsampling}

\subsection{2D}

\begin{enumerate}
\item Let $N$ be the total number of views. 
\begin{figure}[!h]
\centering
	\includegraphics[width=0.5\textwidth]{../images/notes_1.png}
        \caption{2D image of size [D,D]. Ray at $45^\circ$}
 \label{fig:prior_overview}
\end{figure}

\begin{figure}[!h]
\centering
	\includegraphics[width=0.5\textwidth]{../images/notes_2.png}
        \caption{In order to find $N$, consider the image to be fit within a circle of radius $r = \frac{D\sqrt2}{2}$. }
 \label{fig:prior_overview}
\end{figure}

\begin{figure}[!h]
\centering
	\includegraphics[width=0.5\textwidth]{../images/notes_3.png}
        \caption{Consider the same circle, now with ray from all views. The innermost pixels will have maximum number of rays passing through them. The outermost pixels will have minimum number of rays passing through them.}
 \label{fig:prior_overview}
\end{figure}

\begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{../images/notes_4.png}
        \caption{We must ensure that there is atleast one ray passing through each outermost pixel.}
 \label{fig:prior_overview}
\end{figure}
\clearpage
\item
  \begin{align}
    N &= \frac{2\pi r}{2}\\
    &= \frac{\pi D}{\sqrt2}
  \end{align}

\item For okra, [310,310] image, N = 688.\\
 For sprouts, [260,260] image, N = 577\\
 For potato, [150, 150] image, N = 333\\
\end{enumerate}

\subsection{3D}
\begin{enumerate}
\item Here, The volume of size $[D, D, D]$ is fit within sphere of radius $\frac{\sqrt3D}{2}$.

  \begin{align}
    N &= \frac{4\pi r^2}{2}\\
    &= \frac{3\pi D^2}{2}
  \end{align}
\end{enumerate}

\end{document}

  \item At any degree, we assume atleast one ray must pass through each pixel in the longest perpendicular path to the ray within the image. For example,  At $45^\circ$ view, atleast one ray must pass through each pixel on the leading diagonal.

   \item (One ray per corner pixel helps us to find the value of the corner pixel directly.)

\item Therefore, let total number of rays be $\sqrt2DN$, where $\sqrt2$ is the number rays per view and $N$ is the total number of view.

### 2021-09-10 paper/post_tci.tex
Added a new package since otherwise compilation fails (see https://tex.stackexchange.com/questions/110513/unknown-graphics-extension-1-png)
Changed the intro section about TV and introduced subsections

Modified the contributions section caption a bit.

Changed the datasets sections

Few other misc. changes

Ran through ispell to remove spelling errors

@@
 \usepackage{amsmath,graphicx, amssymb,tabularx,booktabs}
+\usepackage{grffile}
 \usepackage{subcaption}
@@
 Discrete Cosine Transform (DCT).  There are multiple such
-regularization priors, of which we had initally worked with Compressed
+regularization priors such as the Compressed
 Sensing based l1-ls prior~\cite{my_dicta_paper}. For the purposes of
-this paper, we use a simpler method, the total Variation (TV) as a
-baseline. If $\boldsymbol{\mathcal{R}}$ represents the acquisition
+demonstrating the efficacy of our method, we use the well known total Variation (TV)
+regularization prior.
+If $\boldsymbol{\mathcal{R}}$ represents the acquisition
 model, then the TV-regularized solution is described by one that
 minimizes a combination of least squares error and the $TV$-norm of
-the object $\boldsymbol{x}$. This is described by
+the object $\boldsymbol{x}$. Mathematically, we choose to minimize
+$J_{TV}(\boldsymbol{x})$ where
 
@@
 
- where the $TV$-norm is given by
+ % where the $TV$-norm is given by
+ and
 
@@
 
-  and $\nabla$ represents the gradient operator.
+  $\nabla$ representing the gradient operator.
 
@@
 	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
-        \caption{Illustration of the use of  priors in 
-          reconstruction as the number of views reduces. For all cases,
-          the ground truth (260$\times$260) appears in the top left.
-          For extremely large number of views (800 views), FBP
-          reconstruction (first column) is of very good quality
+        \caption{Illustration of the use of priors in reconstruction
+          as the number of views reduces. For all cases, the ground
+          truth (260$\times$260) appears in the top left.  For
+          extremely large number of views (800 views), the standard
+          FBP reconstruction (first column) is of very good quality
           (Structural Similarity Index Metric, SSIM=0.92). As the
-          number of views become limited (100 views), 
-          reconstruction using Total Variation (TV, middle column) is
-          better both visually and quantitatively than FBP (SSIM of
-          0.96 vs 0.82). If the number of views is drastically reduced
-          (20 views), the presence of both TV prior and object-
-          prior together improves the reconstruction (SSIM=0.91) when compared
-          to presence of TV-only prior (SSIM=0.87) or no prior
-          (SSIM=0.64).}
+          number of views become limited (100 views), reconstruction
+          using the Total Variation regularization prior (TV, middle
+          column) is better both visually and quantitatively than FBP
+          (SSIM of 0.96 vs 0.82). If the number of views is
+          drastically reduced (20 views), the presence of both TV
+          prior and object- prior together with the spatially-varying
+          technique of this paper improves the reconstruction
+          (SSIM=0.91) when compared to presence of TV-only prior
+          (SSIM=0.87) or no prior (SSIM=0.64).}
  \label{fig:story}
@@
 
+ \subsection{Difficulties}
  When the number of views is significantly reduced (this paper), a
@@
 
- With the use of an object-prior, a new challenge emerges. The prior
+ With the use of an object-prior, a \emph{new} challenge emerges. The prior
  set $S$ may potentially overwhelm the necessary details, and when
@@
  views) our method uses the set $S$ to yield a better reconstruction
- than regularization-only or backprojection-only methods.
-
+ than the regularization-only, or the backprojection-only methods.
+
+ \subsection{Paper organization}
  This paper is organized as follows. After discussing related work in
- Section~\ref{sec:related}, Section~\ref{sec:contributions} \textit{lays down
- the key contributions} of this work.  In order to validate our method, we created
- new cone-beam longitudinal CT datasets, details of which are described in
- Section~\ref{sec:datasets}. Section~\ref{sec:tmh} demonstrates the
- utility of our method on a longitudinal medical dataset. We now move
- to the details. Section~\ref{sec:method_spatially_varying_prior}
- describes computation of a spatially-varying weights map in order to
- preserve new changes in the test.  Results are presented in
+ Section~\ref{sec:related}, Section~\ref{sec:contributions} lays down
+ the \emph{key contributions} of this work.
+
+Most datasets from commercial scanners do not provide raw
+measurements. In order to validate our method quantitatively, we
+created new cone-beam longitudinal CT datasets, details of which are
+described in Section~\ref{sec:datasets} -- these will be offered to
+the community in the public domain.  (In addition,
+Section~\ref{sec:tmh} demonstrates the utility of our method on a
+longitudinal medical dataset involving the liver in a radio-ablation
+study.)
+
+We now move to the
+details. Section~\ref{sec:method_spatially_varying_prior} describes
+the computation of a spatially-varying weights map in order to preserve
+new changes in the test.  Results are presented in
 Section~\ref{sec:results_spatially_varying_prior}. Section~\ref{sec:discussion}
@@
 study~\cite{vincent2017}, changes between successive scans were
-modelled by affine deformation whose parameters were computed for
-motion-correction, which inturn enables acquisition from fewer
+modeled by affine deformation whose parameters were computed for
+motion-correction, which in turn enables acquisition from fewer
 views. In~\cite{daniil2015}, all the scan volumes are reconstructed
@@
 \label{sec:contributions}
-This paper focusses on few-views reconstruction with an emphasis on
+This paper focuses on few-views reconstruction with an emphasis on
 longitudinal studies. In contrast to the object-prior based studies
@@
 eigenvectors of multiple representative previously scanned objects.
-We then present a method to accomodate new changes in the test that
+We then present a method to accommodate new changes in the test that
 may lie outside of this eigenspace. This will prevent an unnecessary
@@
 	\includegraphics[width=0.5\textwidth]{../images/prior_cmb.png}
-        \caption{Overview of our work.
-When the number of measurements is lower than what is conventionally used, (upper part of the diagram) a regularization prior such as Total Variation alone is not sufficient to mitigate the sub-sampling artefacts.
-(Lower) An object-prior must be used to provide additional information without introducing any bias.
-To this end, here we propose using a spatially-varying weights-map to modulate the effect of object-prior on the final reconstruction.}
+        \caption{Overview of our work. (Upper) When the number of
+          measurements is vastly lower than what is conventionally
+          used (last column of Fig.~\ref{story}) a regularization
+          prior such as Total Variation alone is not sufficient to
+          mitigate the sub-sampling artefacts. (Lower) An object-prior
+          must be used to provide additional information, but in
+          addition, new bias should not be introduced. To this end,
+          here we propose using a spatially-varying weights-map to
+          modulate the effect of object-prior on the final
+          reconstruction.}
  \label{fig:prior_overview}
@@
 \label{sec:datasets}
-In this section, we present details of the biological and medical datasets created and used for this work. For the first two datasets namely,
-Potato and Okra, the forward imaging model was available to us and hence all reconstructions were performed from raw measurements.
-For the other two datasets namely, Sprouts and Liver, the forward imaging model was not available to us (due to commercial reasons) and hence we generated measurements from these datasets assuming a circular cone-beam imaging model for 3D and a parallel-beam imaging model for 2D.
+In this section, we present details of the biological and medical
+datasets created and used for this work. For the first two datasets
+namely, Potato and Okra, the forward imaging model is available, and
+hence all reconstructions were performed from raw measurements. For
+the other two datasets namely, Sprouts and Liver, the forward imaging
+model was not available to us (due to propriety concerns) and hence
+only reconstructed volumes of real data were at hand; we therefore
+generated measurements from these datasets assuming a circular
+cone-beam imaging model for 3D and a parallel-beam imaging model for
+2D.
+
+In each case, we remark on the design of the choice of the test chosen
+in the dataset.
 
 \subsection{Datasets with the forward model available}
-
-These consist of longitudinal scans of a Potato and an Okra, both acquired at the Australian National University (ANU), Canberra. \\
+\label{sec:potatoAndOkra}
+
+These consist of longitudinal scans of a Potato and an Okra, both
+acquired by the first author at the Australian National University
+(ANU).
 
@@
 volume was used as the test. The ground truth consists of volumes of
-size 150$\times$150$\times$100 reconstructed using FDK from the full
+size 150$\times$150$\times$100 reconstructed using the 
+Feldkamp-Davis-Kress (FDK) from the full
 set of 900 projection views.
@@
         left) and a slice from the test volume (extreme right). Notice
-        the appearance of the fourth hole in the test slice. }
+        the appearance of the fourth hole in the test slice. 3D visualization is available
+      in the supplementary material~\cite{supp_paper}.}
 \label{fig:potato_dataset}
@@
 
+\textit{Remark:} The test slice (unlike the Okra below) was designed
+to show the presence of a new feature (last picture in
+Fig.~\ref{fig:potato_dataset}. Although the potato is visually bland,
+paradoxically, this becomes the reason that the Potato is challenging
+if a new method has to be shown to be effective.  Simpler methods may
+suffice.  Nevertheless, we show super performance with our method by
+vastly reducing the number of measurements corresponding to the ground truth.
+
  \textbf{Okra:} This dataset is that of an Okra specimen consisting of
- its five scans (Fig.~\ref{fig:object-prior_test_okra}).
-Each of the scanned volumes consists of a varying number of cuts (or deformations) on the surface of the specimen.
-The specimen was kept in the same position throughout the
- acquisitions. Measurements consisted of real circular cone-beam
- projections from 450 views, each of size 336$\times$156.
+ its five scans (Fig.~\ref{fig:object-prior_test_okra}). Each of the
+ scanned volumes consists of a varying number of cuts (or
+ deformations) on the surface of the specimen. The specimen was kept
+ in the same position throughout the acquisitions. Measurements
+ consisted of real circular cone-beam projections from 450 views, each
+ of size 336$\times$156.
 %In cases where such an
@@
 the region marked red, all the templates have a deformation, and hence
-an unchecked reliance of object-prior for the reconstruction of test in this region will result in a deformation. The ground truth consists of
-volumes of size 338$\times$338$\times$123 reconstructed using the
-Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} from the full set of
-450 view projections.  \\
+an unchecked reliance of object-prior for the reconstruction of test
+in this region will result in a deformation. The ground truth consists
+of volumes of size 338$\times$338$\times$123 reconstructed using the
+FDK algorithm~\cite{FDK} from the full set of
+450 view projections.
+
  %--------------------------------okra data-------------------------------
@@
     \end{subfigure}
-     \caption{Okra 3D dataset: One slice each from the scanned objects that are used as templates (the first four from left) and a slice from the test 
-        volume (extreme right). Notice the region marked in red box; while all slices have deformities here, the test has none.}
+     \caption{Okra 3D dataset: One slice each from the scanned objects
+       that are used as templates (the first four from left) and a
+       slice from the test volume (extreme right). Notice the region
+       marked in red box; while all slices have deformities here, the
+       test has none.}
 \label{fig:object-prior_test_okra}
@@
 
+\textit{Remark:} Unlike the potato, the test was designed as one with
+the absence of a feature.  Although mathematically one is the
+conjugate of the other, in practice, experimental methods may have
+difficulties which explains the choice of our test. Notice also that
+the structure of the Okra is intricate as compared to Potato, and this
+brings with it a different challenge.
+
 \subsection{Datasets without the forward model}
-These consist of longitudinal scans of a Liver obtained from Tata
-Memorial Centre (TMC) ~\cite{tmh} in Parel, Mumbai, and longitudinal
-scans of Sprouts obtained from Australian National University.
+These consist of longitudinal scans of a portion of a liver obtained
+from Tata Memorial Centre (TMC) ~\cite{tmh} in Parel, Mumbai, and
+longitudinal scans of Sprouts obtained from Australian National
+University.
 
@@
 %\captionsetup{labelformat=empty}       
- \caption{slice 7}
-    \end{subfigure}     
-     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 7 scan volumes of a longitudinal study dataset of the liver.
-Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor.}
+ \caption{slice 7 (test)}
+    \end{subfigure}     
+     \caption{Radio-frequency ablation dataset: One of the slices
+       (512$\times$512) from each of the 7 scan volumes of a
+       longitudinal study dataset of the liver. Note that in volumes
+       (a) through (g), the needle (shown in red in (f)) approaches
+       the target tumor.}
 \label{fig:RFA2_test_object-prior}
 \end{figure}
+
+\textit{Remark:} Liver is interesting because the data comes from live
+data from a clinical setting.  The oncologist has to be aware of the
+precise position of the needle contrasted with the site of the tumor,
+yet we do not want to create new mutant DNA by further bombarding the
+patient with X-rays.
+
 %----------------------------------------------------
@@
 %\subsection{Simulated measurements from real-life reconstructed volumes}
-\textbf{Sprouts:} This dataset consists of six volumes
-corresponding to six scans of an in-vivo sprout specimen imaged at its
-various stages of growth (Fig.~\ref{fig:object-prior_test_sprouts}).
-\textit{In contrast to the scientific experiment performed for the
-  case of the okra and potato where we introduced man-made defects,
-  the changes here are purely the work of nature.} In our experiments,
-the first 5 volumes were used to build the object-prior and the last
-volume was used as the test. The ground truth consists of FDK
-reconstructed volumes of size 130$\times$130$\times$130 from a set of
-1800 view projections. Test measurements were generated assuming a circular cone-beam imaging model.\\
+\textbf{Sprouts:} This dataset consists of six volumes corresponding
+to six scans of an in-vivo sprout specimen imaged at its various
+stages of growth (Fig.~\ref{fig:object-prior_test_sprouts}).  In our
+experiments, the first 5 volumes were used to build the object-prior
+and the last volume was used as the test. The ground truth consists of
+FDK reconstructed volumes of size 130$\times$130$\times$130 from a set
+of 1800 view projections. Test measurements were generated assuming a
+circular cone-beam imaging model.
+
 %-------------------------sprouts data
@@
 
+\textit{Remark:} In contrast to the scientific experiment performed
+for the case of the okra and potato where we introduced man-made
+defects, the changes in the sprouts here are purely the work of
+nature. This dataset therefore has a different set of challenges.
+
 %----------------------------------------Method-------------------------
@@
 Our method modifies the algorithm presented in~\cite{my_dicta_paper}
-and addtionally overcomes one of its major limitations by introducing
+and additionally overcomes one of its major limitations by introducing
 an extra computational step. We first review the eigenspace-cum-CS
@@
 generate \emph{low quality} reconstruction of the object-prior as
-described below.
+described below.  The algorithm is discussed next (a simplified version
+appears as a schematic in the supplementary material and may be used
+to understand the intuition.)
 
@@
 \end{enumerate}
-\vspace{0.01mm}
-Note that here $\boldsymbol{W_v}(x,y,z)$ represents the weight to the prior in the $(x,y,z)^{th}$ voxel. $\boldsymbol{W_v}(x,y,z)$ must be
-low whenever the preliminary test reconstruction $X^j(x,y,z)$ is different from its projection $P^j(x,y,z)$ onto the prior eigenspace, for \emph{every} method $j \in \{1,...,M\}$. This is
-because it is unlikely that \emph{every} algorithm would produce a significant artefact at a voxel, and hence we hypothesize that the large difference has arisen due to genuine structural changes.
-The parameter $k$ decides the sensitivity of the weights to the difference $|X^j(x,y,z) - P^j(x,y,z)|$.
+\vspace{0.01mm} Note that here $\boldsymbol{W_v}(x,y,z)$ represents
+the weight to the prior in the $(x,y,z)^{th}$
+voxel. $\boldsymbol{W_v}(x,y,z)$ must be low whenever the preliminary
+test reconstruction $X^j(x,y,z)$ is different from its projection
+$P^j(x,y,z)$ onto the prior eigenspace, for \emph{every} method $j \in
+\{1,...,M\}$. This is because it is unlikely that \emph{every}
+algorithm would produce a significant artefact at a voxel, and hence
+we hypothesize that the large difference has arisen due to genuine
+structural changes. This hypothesis is empirically and quantitatively
+proven in the next section.  The parameter $k$ decides the sensitivity
+of the weights to the difference $|X^j(x,y,z) - P^j(x,y,z)|$.
 %It must be chosen empirically based on the reconstruction of one of the template
@@
 In this section, we first illustrate the advantage of using multiple types of eigenspaces for the computation of weights map, and then present reconstruction results on all datasets.
-For quatitative evaluation, we compute the Structural Similarity Index Metric\footnote{Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to (structure, contrast, intensity): $(0.7,0.2,0.1)$.} (SSIM)~\cite{ssim}.
+For quantitative evaluation, we compute the Structural Similarity Index Metric\footnote{Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to (structure, contrast, intensity): $(0.7,0.2,0.1)$.} (SSIM)~\cite{ssim}.
 
@@
 The test volume was reconstructed from a partial set of 45 real
-cone-beam projections, i.e., $5\%$ of the $900$ projection views from which
-ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
-slices is shown in Fig.~\ref{fig:potato_2D_results}. A complete 3D
-reconstruction can be found in the supplementary material
-~\cite{supp_paper}. The red RoI spans
-7 consecutive slices where the test is different from all of the
-previously scanned objects. The zoomed-in images around the major
-region of change (red RoI) is shown in
-Fig.~\ref{fig:potato_zoomed_2D_results}.We observe that our method
-reconstructs new structures while simultaneously reducing streak
-artefacts. Table~\ref{table:potato_ssim} shows SSIM of the
-reconstructed new regions using various methods.
-
+cone-beam projections, i.e., $5\%$ of the $900$ projection views from
+which ground truth was reconstructed (see remarks in
+Sec.~\ref{sec:potatoAndOkra}). 2D reconstructions of one of the slices
+is shown in Fig.~\ref{fig:potato_2D_results}. A complete 3D
+reconstruction can be found in the supplementary
+material~\cite{supp_paper}. The red RoI spans 7 consecutive slices
+where the test is different from all of the previously scanned
+objects. The zoomed-in images around the major region of change (red
+RoI) is shown in Fig.~\ref{fig:potato_zoomed_2D_results}. 
 \begin{figure}[!h]
@@
 
+We observe
+that our method reconstructs new structures while simultaneously
+reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM of
+the reconstructed new regions using various methods.
 \begin{figure}[!h]
@@
 
-\section{Acknowledgement}
+\section{Acknowledgment}
 We are grateful to Dr. Andrew Kingston for facilitating data
@@
 %-------------------------------------------------
+
+%%  LocalWords:  Preeti Gopal Sharat Chandran Imants Svalbe Ajit IIT
+%%  LocalWords:  Rajwade Deakin Monash undersampled Nyquist FBP DCT
+%%  LocalWords:  backprojection dataset ij SSIM datasets angiography
+%%  LocalWords:  hyperparameters PICCS PIRPLE voxels affine spatio th
+%%  LocalWords:  infeasible SIRT artefacts eigenspace undersampling
+%%  LocalWords:  eigenvectors voxel ANU undistorted Feldkamp Kress Eq
+%%  LocalWords:  FDK labelformat Tata Centre TMC Parel centre centres
+%%  LocalWords:  vivo PCA pre covariance eigen tunable fdk Haar SART
+%%  LocalWords:  artefact eigenspaces RoI IITB IRCCSG NVIDIA GPU tci
+%%  LocalWords:  Akshay Baheti

### 2021-09-10 paper/post_tci.tex
typo in caption of Fig 2 fixed.

@@
           drastically reduced (20 views), the presence of both TV
-          prior and object- prior together with the spatially-varying
+          prior and object-prior together with the spatially-varying
           technique of this paper improves the reconstruction
@@
           measurements is vastly lower than what is conventionally
-          used (last column of Fig.~\ref{story}) a regularization
+          used (last column of Fig.~\ref{fig:story}) a regularization
           prior such as Total Variation alone is not sufficient to

### 2021-09-12 paper/changes.tex
Updated based on instructions on TCI pages

--- 2021-09-05 paper/changes.tex
@@
 \usepackage{boxedminipage}
-%\usepackage{geometry}
+\usepackage{a4wide}
 \usepackage[colorlinks=true]{hyperref}
-\title{Changes after the last submission}
+\title{Handling of Rejected Papers
+Changes after the last submission}
 \begin{document}
+\date{}
 \maketitle
-In this document, we explain the steps we have taken to address the reviews received in our previous submission to TCI. In particular, there were two major concerns:
+
+This paper was submitted earlier, and out of the three reviewers, two of them had pronounced this as ``publish unaltered'' and one reviewer (R1) did not recommend resubmission.
+
+The handling Editor has encouraged a resubmission of this paper taking into account the comments of R1.  In particular, R1 has these concerns and we quote these
+\begin{quote}
+  The authors have spent considerable effort in revising the
+  manuscript and addressing the concerns of the reviewers. I would
+  like to thank the authors for their effort. I believe the manuscript
+  has improved because of these revisions, especially in the structure
+  of the paper and the discussion of related work. Unfortunately, some
+  of my main concerns with regards to the experiments, the accuracy of
+  the proposed method, and the presentation of the findings remain
+  present in the revised manuscript. In some cases the revisions have
+  even increased my concerns about certain aspects. Mainly, the
+  included experiments still do not clearly show that the proposed
+  method improves upon existing ‘simple’ prior-based methods, and the
+  new results even show that there is evidence that FDK is more
+  accurate than the proposed method exactly in the region that changed
+  \end{quote}
+
+In this document, we explain the steps we have taken to address the
+reviews received in our previous submission to TCI. In particular,
+we address the main concern of the reviewer below.
 
 \begin{itemize}
-\item \textbf{Total-Variation being better than CS + spatially-varying prior-based reconstruction:}\\
+\item \textbf{Simple methods are better, why yours?}
 
-  The goal of our previous and curent work is to provide a technique that can improve upon any chosen baseline reconstruction when measurements are few.
-After noting reviewer's comments, we conducted further analysis and observed that TV is indeed better suited as a baseline reconstruction method for our datasets and our subsampling choices.
-Hence, our current paper presents all results using TV regularization coupled with spatially-varying technique, and demonstrates its benefits over TV-only and backprojection-only methods.
+The Reviewer has taken pains in showing how the Total-Variation method
+is better than our earlier Compressed Sensing plus spatially-varying
+prior-based reconstruction. In some cases FDK is more accurate.
 
-\item \textbf{Comparison with Deep Learning Techniques:}\\
+This is correct for the dataset show, and we accept this to be true.
 
-  In a machine learning based setting, our goal of detecting new changes is a `prediction' problem in a continuous solution space i.e., \textit{``given intensities of a voxel at various time instants in a longitudinal setting, what will be the intensity of the same voxel at the next time instant?''} This estimation can be learnt by a deep neural network only if there are hundreds if not, thousands of time instants at which the previous voxel intensities are known for each voxel.
-This amount of data is not available to us, and may be hard to acquire because each specimen is usually scanned only a couple of times in any longitudinal study.
-Further, a specific `event-of-interest' may occur just once in a longitudinal study and hence training on data of all previous time instants may be misleading.
-If however, we use measurements from identical and full-cycle longitudinal studies (including events-of-interest) of similar specimen (instead of the `same' specimen as we used), a deep-learning technique may be applied.
-We see this as an extension of using object-prior generated from the same object, and hence we have not explored this direction.
+  That said, the goal of our previous and curent work is to provide a
+  technique that can improve upon a chosen baseline reconstruction
+  when measurements are extremely sparse. One may choose any baseline
+  reconstruction for pedagogical, historical, or ocmmercial reasons,
+  and is there a way to improve?
 
-  Another avenue for using deep-networks \textit{within} our current work is to replace the currently used fixed eigenspace provided by PCA by a learnt feature basis provided by a network such as an autoencoder.
-For each dataset, an autoencoder may be trained to learn a specific set of latent features (this might again require atleast a few tens of volumes).
-We see this as a future direction of work.
+  Nevertheless, after noting reviewer's comments, we conducted further
+  analysis and observed that TV is indeed better suited as a baseline
+  reconstruction method for our datasets and our subsampling
+  choices. Hence, our current paper presents all results using TV
+  regularization coupled with spatially-varying technique, and
+  demonstrates its benefits over TV-only and backprojection-only
+  methods.  We have eliminated our previous implicit claim that the CS
+  based scheme is optimal for the dataset provided.
+
+  As far as FDK is concerned, the current results indeed show the
+  superiority of the TV-based scheme (as also noted by the reviewer).
+
+\item \textbf{Other comments given by Reviewer R1 and the handling editor}
+
+ \begin{itemize}
+  \item {Machine Learning}
+
+  In a machine learning based setting, our goal of detecting new
+  changes is a `prediction' problem in a continuous solution space
+  i.e., \textit{``given intensities of a voxel at various time
+    instants in a longitudinal setting and partial measurements of the
+    voxel at the current time, what will be the intensity of the same
+    voxel at the current time instant?''} This estimation can be
+  learnt by a deep neural network if there are hundreds of labeled
+  data.  However, generalization of this across multiple datasets
+  poses a question mark.
+
+  %% thousands of time instants at which the previous voxel intensities
+  %% are known for each voxel. This amount of data is not available to
+  %% us, and may be hard to acquire because each specimen is usually
+  %% scanned only a couple of times in any longitudinal study.
+
+  Further, a specific `event-of-interest' may occur just once in a
+  longitudinal study and hence training on data of all previous time
+  instants may be misleading. If however, we use measurements from
+  identical and full-cycle longitudinal studies (including
+  events-of-interest) of similar specimen (instead of the `same'
+  specimen as we used), a deep-learning technique may be applied. We
+  see this as an extension of using object-prior generated from the
+  same object, and hence we have not explored this direction.
+
+  Another avenue for using deep-networks \textit{within} our current
+  work is to replace the currently used fixed eigenspace provided by
+  PCA by a learnt feature basis provided by a network such as an
+  autoencoder. For each dataset, an autoencoder may be trained to
+  learn a specific set of latent features (this might again require
+  atleast a few tens of volumes). We see this as a future direction of
+  work.
+\end{itemize}
 

### 2021-09-12 paper/changes.tex
changes in Fig.1, 2, dataset-intro, mnior changes

@@
 
-This is correct for the dataset show, and we accept this to be true.
+This is correct for the dataset shown, and we accept this to be true.
 
@@
   when measurements are extremely sparse. One may choose any baseline
-  reconstruction for pedagogical, historical, or ocmmercial reasons,
+  reconstruction for pedagogical, historical, or commercial reasons,
   and is there a way to improve?

### 2021-09-12 paper/post_tci.tex
changed super to superior
changes in Fig.1, 2, dataset-intro, mnior changes

@@
 
- \subsection{Difficulties}
   When the number of views is significantly reduced (this paper), a
@@
  interior. 
+ \subsection{Difficulties}
 
@@
 datasets created and used for this work. For the first two datasets
-namely, Potato and Okra, the forward imaging model is available, and
-hence all reconstructions were performed from raw measurements. For
-the other two datasets namely, Sprouts and Liver, the forward imaging
-model was not available to us (due to propriety concerns) and hence
+namely, Potato and Okra, the raw measurements and  corresponding
+paramteres for cone-beam imaging model are available to us.
+Hence all reconstructions on these datasets were performed directly
+from real projection measurements. For the other two datasets namely, Sprouts and
+Liver, the raw measurements and the parameters of imaging
+model were not available to us (due to propriety concerns) and hence
 only reconstructed volumes of real data were at hand; we therefore
@@
 
-\subsection{Datasets with the forward model available}
+\subsection{Datasets with the imaging model available}
 \label{sec:potatoAndOkra}
@@
 if a new method has to be shown to be effective.  Simpler methods may
-suffice.  Nevertheless, we show super performance with our method by
+suffice.  Nevertheless, we show superior performance with our method by
 vastly reducing the number of measurements corresponding to the ground truth.
@@
 
-\subsection{Datasets without the forward model}
+\subsection{Datasets without the imaging model}
 These consist of longitudinal scans of a portion of a liver obtained
@@
 
-\subsection{Reconstruction of datasets with forward model available}
+\subsection{Reconstruction of datasets with imaging model available}
 \subsubsection{\textbf{Potato}}
@@
 
-\subsection{Reconstruction of datasets without forward model}
+\subsection{Reconstruction of datasets without imaging model}
 \subsubsection{\textbf{Liver:}}

### 2021-09-12 paper/post_tci.tex
Removed zoomed images

@@
 \usepackage{xcolor}
+\usepackage{comment}
 %\usepackage[sort&compress]{natbib}
@@
 where the test is different from all of the previously scanned
-objects. The zoomed-in images around the major region of change (red
-RoI) is shown in Fig.~\ref{fig:potato_zoomed_2D_results}. 
+objects. %The zoomed-in images around the major region of change (red
+%RoI) is shown in Fig.~\ref{fig:potato_zoomed_2D_results}. 
 \begin{figure}[!h]
@@
 the reconstructed new regions using various methods.
+\begin{comment}
 \begin{figure}[!h]
@@
 \end{figure}
+\end{comment}
 %-------------------------------------------------------------------------
@@
 ~\cite{supp_paper}. The red RoI spans 7 consecutive slices where the
-test is different from all of the previously scanned objects. A
-zoomed-in region around the major region of change (red RoI) is shown
-in Fig.~\ref{fig:okra_zoomed_2D_results}. As in the test, the
+test is different from all of the previously scanned objects. %A
+%zoomed-in region around the major region of change (red RoI) is shown
+%in Fig.~\ref{fig:okra_zoomed_2D_results}.
+As in the test, the
 reconstruction by spatially-varying method shows the absence of the
@@
 
+\begin{comment}
 \begin{figure}[!h]
@@
 \end{figure}
+\end{comment}
 
@@
 the needle and simultaneously reducing
-artefacts. Fig.~\ref{fig:tmh_2D_results} and
-Fig.~\ref{fig:tmh_2D_zoomed_results} show reconstruction of the test
-slice from its measurements from only 30 views and a zoomed-in version
-around the RoI. The reconstructions are quantitatively compared using
-SSIM.
+artefacts. Fig.~\ref{fig:tmh_2D_results} 
+shows reconstruction of the test
+slice from its measurements from only 30 views. The reconstructions are quantitatively compared using
+SSIM in Table~\ref{table:tmh_ssim}.
 
@@
 %\subcaptionbox{Weights map}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weightsIm_kk_30_lambda_prior_1.100000.png}}
-
+\begin{comment}
 \begin{figure}[!h]
@@
 \end{tabular}
-\label{table:sprouts_ssim}
+\label{table:tmh_ssim}
 \end{table}
@@
 The test volume was reconstructed from partial set of 45 real
-cone-beam projections, i.e., $2.5\%$ of the $1800$ projection views from
-which ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). The selected 3D ground truth of
-template volumes, test volume, as well as the 3D reconstructions are
-shown in the supplementary material~\cite{supp_paper}.  2D
-reconstruction of one of the slices and a zoomed-in region around the
-RoI are shown in Figs.~\ref{fig:sprouts_2D_results} and
-~\ref{fig:sprouts_zoomed_2D_results} respectively. For the sake of
+cone-beam projections, i.e., $2.5\%$ of the $1800$ projection views
+from which ground truth was reconstructed (refer
+Sec.~\ref{sec:datasets}). The selected 3D ground truth of template
+volumes, test volume, as well as the 3D reconstructions are shown in
+the supplementary material~\cite{supp_paper}. For the sake of
 exposition, the red region of interest (RoI) has been culled out from
 7 consecutive slices in the 3D volume to indicate new structures;
-other changes can be viewed in the
-video. Table~\ref{table:sprouts_ssim} shows the improvement in SSIM of
-the reconstructed new regions as compared to other methods.
+other changes can be viewed in the video.  2D reconstruction of one of
+the slices is shown in Fig.~\ref{fig:sprouts_2D_results}.
+Table~\ref{table:sprouts_ssim} shows the improvement in SSIM of the
+reconstructed new regions as compared to other methods.
 %----------------------------------------------------
@@
 %----------------------------------------------------
-
+\begin{comment}
 \begin{figure}[!h]
@@
 \end{figure}
+\end{comment}
 %--------------------------------------------------------------

### 2021-09-15 paper/post_tci.tex
Changes made based on comments from Prof.Ajit

@@
         and~Ajit Rajwade
-\thanks{Preeti Gopal is currently with the Applied Artificial Intelligence Institute, Deakin University}
-\thanks{Sharat Chandran and Ajit Rajwade are with the Department of Computer Science and Engineering, IIT Bombay}
-\thanks{Imants Svalbe is with the School of Physics and Astronomy, Monash University}}
+\thanks{Preeti Gopal is currently with the Applied Artificial Intelligence Institute, Deakin University; p.gopal@deakin.edu.au}
+\thanks{Sharat Chandran and Ajit Rajwade are with the Department of Computer Science and Engineering, IIT Bombay; \{sharat, ajitvr\}@cse.iitb.ac.in}
+\thanks{Imants Svalbe is with the School of Physics and Astronomy, Monash University; imants.svalbe@monash.edu}}
 
@@
 (260$\times$260) of naturally growing sprouts at the top left (the
-details of this dataset is postponed to Section~\ref{sec:datasets}).
+details of this dataset are postponed to Section~\ref{sec:datasets}).
 
@@
 assuming the data to exhibit certain properties such as smoothness in
-image space, sparsity in gradient space~\cite{TV} or sparsity under
+image space~\cite{Essam2015}, sparsity in gradient space~\cite{TV} or sparsity under
 certain mathematical transforms~\cite{Donoho,introCS} such as the
@@
 
-  $\nabla$ representing the gradient operator.
+  where $\nabla$ represents the gradient operator.
 
@@
 analysis assuming that the object consists of a large static part
-(background) and a sparse moving part (foreground)~\cite{HaoGao},
+(background) and a sparse moving part (foreground)~\cite{HaoGao} or
 spline-based models for tracking the regions of change in an SIRT
@@
 assumption in terms of time intervals -- prior scans could be months
-apart. We use the current measurements from few-views and previous
-scans of the same object.
+apart which is typical in cancer scanning, or could be a few
+minutes/seconds apart which is typical in CT-guided surgeries. We use
+the current measurements from few-views and previous scans of the same
+object.
 
@@
 namely, Potato and Okra, the raw measurements and  corresponding
-paramteres for cone-beam imaging model are available to us.
+parameters for cone-beam imaging model are available to us.
 Hence all reconstructions on these datasets were performed directly
@@
 study consists of 7 scans taken at different stages of radio-frequency
-ablation study of a liver. In such a procedure~\cite{Dong2015}, the
+ablation (RFA) study of a liver. In such a procedure~\cite{Dong2015}, the
 physician inserts a thin needle-like probe into the organ. Repeated CT
@@
 malignant tumor (ablation).
+A fairly high amount of radiation is administered to a patient in this RFA procedure~\cite{radiation_dose_RFA}, and hence reducing radiation per scan is highly beneficial here.
 
@@
 
-\textit{Remark:} Liver is interesting because the data comes from live
-data from a clinical setting.  The oncologist has to be aware of the
+\textit{Remark:} This dataset is interesting because it comes from a live
+clinical setting.  The oncologist has to be aware of the
 precise position of the needle contrasted with the site of the tumor,
 yet we do not want to create new mutant DNA by further bombarding the
-patient with X-rays.
+patient with X-rays~\cite{damage_repeated_CT}.
 
@@
 TV-prior and object-prior terms respectively. The unknowns
-$\boldsymbol{\x}$ and $\boldsymbol{\alpha}$ are solved by alternately
-minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{\x})$ using a fixed
+$\boldsymbol{x}$ and $\boldsymbol{\alpha}$ are solved by alternately
+minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{x})$ using a fixed
 $\boldsymbol{\alpha}$, and $J_{\boldsymbol{x}}(\boldsymbol{\alpha})$
-using the resultant $\boldsymbol{\x}$.
-$J_{\boldsymbol{\alpha}}(\boldsymbol{\x})$ is solved for using an
+using the resultant $\boldsymbol{x}$.
+$J_{\boldsymbol{\alpha}}(\boldsymbol{x})$ is solved for using an
 optimal first-order method for large-scale TV regularization presented
@@
 \begin{equation}
-J_{\boldsymbol{x}}(\boldsymbol{\alpha}) \triangleq \lVert\boldsymbol{\boldsymbol{W}(\boldsymbol{x}} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2.
+J_{\boldsymbol{x}}(\boldsymbol{\alpha}) \triangleq \lVert{\boldsymbol{W}(\boldsymbol{x}} - (\boldsymbol{\mu + V\alpha}))\rVert_2^2.
 \end{equation}
@@
     Y^{\text{fdk}}_i$, $\forall i \in \{1,..,,L\}$.
+If the set of projection views for every test is fixed a priori, this set of low quality reconstructions can be produced offline and stored, in order to save computational costs.
+If new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization.
 
@@
 
-The test volume was reconstructed from a partial set of 45 real
-cone-beam projections, i.e., $5\%$ of the $900$ projection views from
+The test volume was reconstructed from a partial set of 18 real
+cone-beam projections, i.e., $2\%$ of the $900$ projection views from
 which ground truth was reconstructed (see remarks in
@@
 \subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
-\caption{Reconstruction of potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.}
+\caption{Reconstruction of potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.
+3D reconstructions from 18 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.
+}
 \label{fig:potato_2D_results}
@@
 \label{Sec:okra_spatially_varying}
-The test volume was reconstructed from a partial set of 45 real
-cone-beam projections, i.e., $10\%$ of the $450$ projection views from which
+The test volume was reconstructed from a partial set of 30 real
+cone-beam projections, i.e., $6.7\%$ of the $450$ projection views from which
 ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
@@
 \caption{Reconstruction of okra from 48 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
+3D reconstructions from 30 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.}
 \label{fig:okra_2D_results}
@@
 
-The test volume was reconstructed from partial set of 45 real
-cone-beam projections, i.e., $2.5\%$ of the $1800$ projection views
+The test volume was reconstructed from partial set of 30 
+cone-beam projections, i.e., $1.7\%$ of the $1800$ projection views
 from which ground truth was reconstructed (refer
@@
 \caption{Reconstruction of sprouts from 20 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
+3D reconstructions from 30 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.}
 \label{fig:sprouts_2D_results}

### 2021-09-16 paper/changes.tex
Addressed reviewer's comments

@@
 \usepackage{a4wide}
+\usepackage{subcaption}
 \usepackage[colorlinks=true]{hyperref}
-\title{Handling of Rejected Papers
-Changes after the last submission}
+\title{Response to Reviewers and Associate Editor}
 \begin{document}
@@
  \begin{itemize}
-  \item {Machine Learning}
+  \item \textbf{Machine Learning}
 
@@
   work.
+
+\item \textbf{Details of other methods used for comparison}
+ We have compared our method with Algebraic Reconstruction Technique
+ (ART), Simultaneous Algebraic Reconstruction Technique (SART),
+ Simultaneous Iterative Reconstruction Technique (SIRT), Total
+ Variation (TV) and Compressed Sensing (CS) with Haar wavelet and DCT
+ as sparsity basis. The details of solvers used for these
+ algorithms are now mentioned in Page.~7 (Section-6A). For CS
+ reconstruction, we observed that Haar wavelet and DCT were best
+ suited for our dataset among various other possible sparsity basis.
+
+\item \textbf{Discussion about Metrics used}
+  In our experiments, we observed that for a given dataset and a set of projection measurements, the intensity span of histograms of reconstructed volumes differ across various methods and solvers.
+Hence, we choose to focus on preserving the structures on our reconstructions, and not rely on the absolute intensity values alone.
+Hence, we choose SSIM with a higher weightage to structure-preservation.
+For our record, we have computed RMSE values as well and they are presented here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.
+
+\begin{table}[!h]
+  \centering
+ \caption{RMSE within the RoI of 3D reconstructed Potato volume from various
+    methods.}
+\begin{tabular}{|l|c|c|c|c|}
+\hline 
+\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
+\\ \hline  0.29 & 0.24 & \textcolor{red}{0.18}
+\\ \hline
+\end{tabular}
+\label{table:potato_rmse}
+\end{table}
+
+\begin{table}[!h]
+  \centering
+ \caption{RMSE within the RoI of 3D reconstructed Sprouts volume from various
+    methods.}
+\begin{tabular}{|l|c|c|c|c|}
+\hline 
+\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
+\\ \hline  0.53 & 0.48 & \textcolor{red}{0.30}
+\\ \hline
+\end{tabular}
+\label{table:sprouts_rmse}
+\end{table}
+
+\item \textbf{Dicsussion about Computational Cost}\\
+  We now present details of both time and space complexities of our technique in Section.7B of our paper.
 \end{itemize}

### 2021-09-16 paper/post_tci.tex
Addressed reviewer's comments

@@
 different reconstruction techniques to generate different types of
-eigenspaces and combine information from all of them to compute
-weights. To illustrate the benefit of this method, we first performed
-2D reconstruction of a test slice from the potato dataset.
-Fig.~\ref{fig:potato_data_2D} shows the test and template
-slices. Fig.~\ref{fig:weights_map_2Dpotato} shows the weights-maps
+eigenspaces and combine information from all of them to compute the
+weights map. To illustrate the benefit of this method, we first performed
+2D reconstruction of a test slice from the potato dataset using
+various reconstruction methods. We used implementations of algebraic
+methods such as ART, SIRT and SART from~\cite{AIR_tools} and
+implementations of CS solver from~\cite{l1ls}. Among various possible
+sparsity basis for CS reconstruction, we observed that Haar wavelets
+and DCT were best suited for this
+dataset. Fig.~\ref{fig:potato_data_2D} shows the test and template
+slices and Fig.~\ref{fig:weights_map_2Dpotato} shows the weights maps
 generated using Eq.~\ref{eq:weightsEq} by various reconstruction
@@
 new change in test data. Because all the iterative methods are
-computationally expensive, we chose only FBP and TV for
-computing weights-maps for all 3D reconstructions.
+computationally expensive, we chose only FBP and TV for computing
+weights-maps for all 3D reconstructions.
 %---------------------------------------
@@
 \label{sec:discussion}
-In this section, we discuss tuning of the parameters
-used in our method. $\lambda_1$, $\lambda_2$ and $k$ are the three
+In this section, we discuss tuning of parameters and the computational complexity of our method.
+\subsection{Tuning of parameters:}
+$\lambda_1$, $\lambda_2$ and $k$ are the three
 hyper-parameters that need to be chosen carefully for optimal
@@
 \end{figure}
+\subsection{Computational Complexity:}
+The use of object-priors does introduce additional time and space complexities when compared to the use of a simpler prior such as TV-only prior.  For spatially-varying prior, most of the
+computation time is used in the generation of low quality eigen-space
+by reconstructing each of the templates using TV and FDK.
+If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored, in order to save computational costs.
+If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent.
+Here below, we describe the
+time complexity of spatially-varying prior technique.  If
+\begin{itemize}
+\item $N =$ number of voxels of the volume
+\item $T =$ number of templates available, and
+\item $F =$ time taken for iterative TV optimization,
+\end{itemize}
+then, the computational complexity is sum of the following
+\begin{itemize}
+\item $O(NT^2+T^3)$ for creating the eigenspace,
+\item $O(NT^2)$ for deriving the weights map, and
+\item time $F$  taken for iterative minimization
+\end{itemize}
+where $O(.)$ is the notation for `Big O' used in complexity analysis.
+In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions.
+We need to store a single weights map volume regardless of the number of templates available.
 

### 2021-09-19 paper/changes.tex
Finetuned our response to reviewers

@@
 \usepackage{caption}
-\usepackage{subcaption}
-
+\usepackage{subcaption, tabularx}
+\usepackage{xcolor}
 \usepackage{boxedminipage}
@@
 This paper was submitted earlier, and out of the three reviewers, two of them had pronounced this as ``publish unaltered'' and one reviewer (R1) did not recommend resubmission.
-
-The handling Editor has encouraged a resubmission of this paper taking into account the comments of R1.  In particular, R1 has these concerns and we quote these
+The handling Editor has encouraged a resubmission of this paper taking into account the comments of R1.
+We thank all reviewers for their remarks and in this document, we explain the steps we have taken to address the reviews received in our previous submission to TCI.
+R1 has these concerns and we quote these
 \begin{quote}
-  The authors have spent considerable effort in revising the
+  \textcolor{blue}{The authors have spent considerable effort in revising the
   manuscript and addressing the concerns of the reviewers. I would
@@
   new results even show that there is evidence that FDK is more
-  accurate than the proposed method exactly in the region that changed
+  accurate than the proposed method exactly in the region that changed}
   \end{quote}
 
-In this document, we explain the steps we have taken to address the
-reviews received in our previous submission to TCI. In particular,
-we address the main concern of the reviewer below.
+\begin{itemize}
+\item \textbf{In particular, we address the following main concern of the reviewer below.}\\
 
-\begin{itemize}
-\item \textbf{Simple methods are better, why yours?}
+    \textcolor{blue}{Note that the total
+variation minimization results are much better than the l1-ls results that the authors show in the
+paper.}\\
 
@@
   reconstruction for pedagogical, historical, or commercial reasons,
-  and is there a way to improve?
+  and given that, our key question is-- is there a way to improve?
 
@@
   superiority of the TV-based scheme (as also noted by the reviewer).
-
+  \clearpage
 \item \textbf{Other comments given by Reviewer R1 and the handling editor}
@@
  \begin{itemize}
-  \item \textbf{Machine Learning}
+ \item    \textcolor{blue}{...the paper should at least include a (short) discussion about the
+     possibility of using deep learning for this, and its disadvantages.}
+
+   We have now discussed the difficulties in using deep-learning
+   techniques for the current problem in Sec.~7C of our paper. We also
+   describe them here below.
 
@@
 
-  %% thousands of time instants at which the previous voxel intensities
-  %% are known for each voxel. This amount of data is not available to
-  %% us, and may be hard to acquire because each specimen is usually
-  %% scanned only a couple of times in any longitudinal study.
+  %% thousands of time instants at which the previous voxel
+  %% intensities are known for each voxel. This amount of data is not
+  %% available to us, and may be hard to acquire because each specimen
+  %% is usually scanned only a couple of times in any longitudinal
+  %% study.
 
@@
   instants may be misleading. If however, we use measurements from
-  identical and full-cycle longitudinal studies (including
-  events-of-interest) of similar specimen (instead of the `same'
+  identical and full-cycle longitudinal studies, including
+  events-of-interest, of similar specimen (instead of the `same'
   specimen as we used), a deep-learning technique may be applied. We
@@
 
-\item \textbf{Details of other methods used for comparison}
- We have compared our method with Algebraic Reconstruction Technique
- (ART), Simultaneous Algebraic Reconstruction Technique (SART),
- Simultaneous Iterative Reconstruction Technique (SIRT), Total
- Variation (TV) and Compressed Sensing (CS) with Haar wavelet and DCT
- as sparsity basis. The details of solvers used for these
- algorithms are now mentioned in Page.~7 (Section-6A). For CS
- reconstruction, we observed that Haar wavelet and DCT were best
- suited for our dataset among various other possible sparsity basis.
+\item \textcolor{blue}{There are no added comparisons with popular existing methods for
+  reconstruction with a small number of projections (TV, algebraic techniques, etcetera)}\\
 
-\item \textbf{Discussion about Metrics used}
+ Among the family of algebraic techniques, we have compared our method
+ with Algebraic Reconstruction Technique (ART) and Simultaneous
+ Algebraic Reconstruction Technique (SART). We do not reconstruct
+ using Discrete Algebraic Reconstruction Technique (DART) since there
+ is no prior information about the number of possible attentuation
+ coefficients in the test object. Among other iterative techniques, we
+ have used Simultaneous Iterative Reconstruction Technique (SIRT),
+ Total Variation (TV) and Compressed Sensing (CS) with Haar wavelet
+ and DCT as sparsity basis. The details of solvers used for these
+ algorithms and their reconstructions are in Page.~7 (Section-6A) of
+ the paper. For CS reconstruction, we observed that Haar wavelet and
+ DCT were best suited for our dataset among various other possible
+ sparsity basis.
+
+\item \textcolor{blue}{Why did the authors not choose the standard
+  settings for SSIM?...I don’t understand the reason given for not
+  including RMSE: the values don’t have to be optimized again -- you
+  could just optimize for SSIM but at least still report RMSE
+  comparisons.}\\
+
   In our experiments, we observed that for a given dataset and a set of projection measurements, the intensity span of histograms of reconstructed volumes differ across various methods and solvers.
@@
 
-\item \textbf{Dicsussion about Computational Cost}\\
+\item  \textcolor{blue}{A discussion about computational costs (time, memory) should be included in the paper.}
+
   We now present details of both time and space complexities of our technique in Section.7B of our paper.
+
+Most of the
+computation time in our technique is used for the generation of low quality eigen-space
+by reconstructing each of the templates using TV and FDK.
+If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs.
+With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
+If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent.
+Here below, we describe the
+time complexity of spatially-varying prior technique.  If
+\begin{itemize}
+\item $N =$ number of voxels of the volume
+\item $T =$ number of templates available, and
+\item $F =$ time taken for iterative TV optimization,
+\end{itemize}
+then, the computational complexity is sum of the following
+\begin{itemize}
+\item $O(NT^2+T^3)$ for creating the eigenspace,
+\item $O(NT^2)$ for deriving the weights map, and
+\item time $F$  taken for iterative minimization
+\end{itemize}
+where $O(.)$ is the notation for `Big O' used in complexity analysis. 
+In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions.
+We only need to store a single weights map volume regardless of the number of templates available.
+
+\begin{table}[]
+  \centering
+  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
+Here we assume that low quality eigen-spaces of the templates are computed offline.}
+\begin{tabular}{|l|l|l|l|}
+\hline
+Backprojection             & TV                        & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map\end{tabular} & \begin{tabular}[c]{@{}l@{}}Final reconstruction\\ with spatially-varying \\ prior\end{tabular} \\ \hline
+\multicolumn{1}{|c|}{0.40} & \multicolumn{1}{c|}{8.44} & \multicolumn{1}{c|}{0.04}                                             & \multicolumn{1}{c|}{46.73}                                                                     \\ \hline
+\end{tabular}
+\label{table:compute_time}
+\end{table}
 \end{itemize}

### 2021-09-19 paper/post_tci.tex
Finetuned our response to reviewers

@@
 In this section, we first illustrate the advantage of using multiple types of eigenspaces for the computation of weights map, and then present reconstruction results on all datasets.
-For quantitative evaluation, we compute the Structural Similarity Index Metric\footnote{Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to (structure, contrast, intensity): $(0.7,0.2,0.1)$.} (SSIM)~\cite{ssim}.
+For quantitative evaluation, we compute the Structural Similarity Index Metric (SSIM)~\cite{ssim}.
+Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to structure, contrast and intensity respectively: $0.7,0.2,0.1$.
 
@@
 
-The test volume was reconstructed from a partial set of 18 real
-cone-beam projections, i.e., $2\%$ of the $900$ projection views from
+The test volume was reconstructed from a partial set of $2\%$ of projection views from
 which ground truth was reconstructed (see remarks in
@@
 \subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/testIm_paper.png}}}
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp.png}}
+\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp.png}}
 \subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_lambdaTV_0.05.png}}
 \subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
-\caption{Reconstruction of potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.
-3D reconstructions from 18 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.
-}
+\caption{Reconstruction of potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.}
 \label{fig:potato_2D_results}
@@
 \label{Sec:okra_spatially_varying}
-The test volume was reconstructed from a partial set of 30 real
-cone-beam projections, i.e., $6.7\%$ of the $450$ projection views from which
+The test volume was reconstructed from a partial set of $6.7\%$ of projection views from which
 ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
@@
 \caption{Reconstruction of okra from 48 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
-3D reconstructions from 30 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.}
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
 \label{fig:okra_2D_results}
@@
 \subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
-\subcaptionbox{Backprojection\\no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
+\subcaptionbox{FBP, no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
 \subcaptionbox{TV, no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
@@
 
-The test volume was reconstructed from partial set of 30 
-cone-beam projections, i.e., $1.7\%$ of the $1800$ projection views
+The test volume was reconstructed from a partial set of  
+ $1.7\%$ of projection views
 from which ground truth was reconstructed (refer
@@
 \subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/testIm_roi.png}}}
-\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
+\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
 \subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
@@
 \caption{Reconstruction of sprouts from 20 projection views
-   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.
-3D reconstructions from 30 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.}
+   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
 \label{fig:sprouts_2D_results}
@@
 \label{sec:discussion}
-In this section, we discuss tuning of parameters and the computational complexity of our method.
+In this section, we discuss tuning of parameters, computational complexity of our method, and requirements for applying deep learning techniques in longitudinal few-view reconstruction.
 \subsection{Tuning of parameters:}
@@
 \subsection{Computational Complexity:}
-The use of object-priors does introduce additional time and space complexities when compared to the use of a simpler prior such as TV-only prior.  For spatially-varying prior, most of the
-computation time is used in the generation of low quality eigen-space
+Most of the
+computation time in our technique is used for the generation of low quality eigen-space
 by reconstructing each of the templates using TV and FDK.
-If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored, in order to save computational costs.
+If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs.
+With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
 If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent.
@@
 In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions.
-We need to store a single weights map volume regardless of the number of templates available.
+We only need to store a single weights map volume regardless of the number of templates available.
+
+\begin{table}[]
+ \centering
+  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
+Here we assume that low quality eigen-spaces of the templates are computed offline.}
+\begin{tabular}{|l|l|l|l|}
+\hline
+Backprojection             & TV                        & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map\end{tabular} & \begin{tabular}[c]{@{}l@{}}Final reconstruction\\ with spatially-varying \\ prior\end{tabular} \\ \hline
+\multicolumn{1}{|c|}{0.40} & \multicolumn{1}{c|}{8.44} & \multicolumn{1}{c|}{0.04}                                             & \multicolumn{1}{c|}{46.73}                                                                     \\ \hline
+\end{tabular}
+\label{table:compute_time}
+\end{table}
+\subsection{Requirements for applying deep learning techniques}
+Deep learning techniques are powerful tools to learn an unknown
+parameteric function relating an input space and an output space. In such
+settings, our current goal of detecting new changes is a `prediction'
+problem in a continuous solution space i.e., \textit{``given
+  intensities of a voxel at various time instants in a longitudinal
+  setting and partial measurements of the voxel at the current time,
+  what will be the intensity of the same voxel at the current time
+  instant?''}. This estimation can be learnt by a deep neural network
+if there are hundreds of labeled data.  However, generalization of
+this across multiple datasets poses a question mark.
+
+  Further, a specific `event-of-interest' may occur just once in a
+  longitudinal study and hence training on data of all previous time
+  instants may be misleading. If however, we use measurements from
+  identical and full-cycle longitudinal studies, including
+  events-of-interest, of similar specimen (instead of the `same'
+  specimen as we used), a deep-learning technique may be applied. We
+  see this as an extension of using object-prior generated from the
+  same object.
+
+  Another avenue for using deep networks \textit{within} our current
+  work is to replace the currently used fixed eigenspace provided by
+  PCA by a learnt feature basis provided by a network such as an
+  autoencoder. For each dataset, an autoencoder may be trained to
+  learn a specific set of latent features. This will again require
+  atleast a few tens of volumes. We see this as a future direction of
+  work.
 

### 2021-09-20 paper/changes.tex
updated changes with some reformatting and updated post_tci in two places

@@
 
-This paper was submitted earlier, and out of the three reviewers, two of them had pronounced this as ``publish unaltered'' and one reviewer (R1) did not recommend resubmission.
-The handling Editor has encouraged a resubmission of this paper taking into account the comments of R1.
-We thank all reviewers for their remarks and in this document, we explain the steps we have taken to address the reviews received in our previous submission to TCI.
-R1 has these concerns and we quote these
+This paper was submitted earlier, and out of the three reviewers, two
+of them had pronounced this as ``publish unaltered'' and one reviewer
+(R1) did not recommend resubmission. The handling Editor has
+encouraged a resubmission of this paper taking into account the
+comments of R1.  We thank all reviewers for their remarks and in this
+document, we explain the steps we have taken to address the reviews
+received in our previous submission to TCI. R1 makes the following
+comments, and we quote excerpts in blue here:
 \begin{quote}
@@
   included experiments still do not clearly show that the proposed
-  method improves upon existing ‘simple’ prior-based methods, and the
-  new results even show that there is evidence that FDK is more
-  accurate than the proposed method exactly in the region that changed}
+  method improves upon existing ‘simple’ prior-based methods
+%% , and the
+%%   new results even show that there is evidence that FDK is more
+%%   accurate than the proposed method exactly in the region that changed
+  }
   \end{quote}
 
-\begin{itemize}
-\item \textbf{In particular, we address the following main concern of the reviewer below.}\\
-
+The simpler method is based on the well-known ``Total Variation''. 
+In particular, we address the following main concern of the reviewer 
+\begin{quote}  
     \textcolor{blue}{Note that the total
 variation minimization results are much better than the l1-ls results that the authors show in the
-paper.}\\
+paper}
+\end{quote}
 
-The Reviewer has taken pains in showing how the Total-Variation method
-is better than our earlier Compressed Sensing plus spatially-varying
-prior-based reconstruction. In some cases FDK is more accurate.
+    by rewriting the paper considerably.  We believe the paper
+    addresses this (correct) stinging criticism of R1.  In fact R1 has taken
+    pains in showing how the Total-Variation method (and sometimes
+    FDK) is better than our earlier Compressed Sensing plus
+    spatially-varying prior-based reconstruction, and we gratefully
+    acknowledge the same.
 
-This is correct for the dataset shown, and we accept this to be true.
+Again, this is correct for the dataset shown, and we accept this to be
+true.
 
-  That said, the goal of our previous and curent work is to provide a
-  technique that can improve upon a chosen baseline reconstruction
-  when measurements are extremely sparse.  One may choose any baseline
-  reconstruction for pedagogical, historical, or commercial reasons,
-  and given that, our key question is-- is there a way to improve?
-
-  Nevertheless, after noting reviewer's comments, we conducted further
-  analysis and observed that TV is indeed better suited as a baseline
-  reconstruction method for our datasets and our subsampling
-  choices. Hence, our current paper presents all results using TV
-  regularization coupled with spatially-varying technique, and
-  demonstrates its benefits over TV-only and backprojection-only
-  methods.  We have eliminated our previous implicit claim that the CS
-  based scheme is optimal for the dataset provided.
+  We re-wrote our code and upon further analysis observed that TV is
+  indeed better suited as a baseline reconstruction method for our
+  datasets and our subsampling choices. Hence, our current paper
+  presents all results using TV regularization coupled with
+  spatially-varying technique, and demonstrates  benefits over
+  TV-only and backprojection-only methods.  \emph{We have eliminated our
+  previous implicit claim that the CS based scheme is optimal for the
+  dataset provided. }
 
@@
   superiority of the TV-based scheme (as also noted by the reviewer).
-  \clearpage
-\item \textbf{Other comments given by Reviewer R1 and the handling editor}
+
+    That said, the goal of our previous and curent work is to provide
+    a technique that can improve upon a chosen baseline reconstruction
+    when measurements are extremely sparse.  One may choose any
+    baseline reconstruction (including an inferior -- for this dataset
+    -- Compressed sensing prior) for pedagogical, historical, or
+    commercial reasons, and given that, our key question is -- is
+    there a way to improve?  The spatially-varying method of
+    moderating the prior settles this question.
+
+We also take this opportunity to address other comments given by R1
+and the handling editor.
 
@@
 
-   We have now discussed the difficulties in using deep-learning
-   techniques for the current problem in Sec.~7C of our paper. We also
-   describe them here below.
+   We accept this point, and have now discussed the difficulties in
+   using deep-learning techniques for the current problem in Sec.~7C
+   of our paper. We also describe them here below.
+
+\textcolor{red}{Comment from Sharat:  Since the material is in the text, there is no need to mention it here.}
 
@@
   could just optimize for SSIM but at least still report RMSE
-  comparisons.}\\
+  comparisons.}
 
-  In our experiments, we observed that for a given dataset and a set of projection measurements, the intensity span of histograms of reconstructed volumes differ across various methods and solvers.
-Hence, we choose to focus on preserving the structures on our reconstructions, and not rely on the absolute intensity values alone.
-Hence, we choose SSIM with a higher weightage to structure-preservation.
-For our record, we have computed RMSE values as well and they are presented here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.
+  The reason for not reporting RMSE stems from the optimization
+  process. The optimization routine we use transforms the
+  reconstruction to a different space.  That is, in our experiments,
+  we observed that for a given dataset and a set of projection
+  measurements, the intensity span of histograms of reconstructed
+  volumes differ across various methods and solvers. As a result, the
+  RMSE values are not particularly useful.  We provide the numbers
+  here to show the improvement trend but we believe it does not serve
+  the interest of the community to report these.
+
+  For the same reason, the standard setting of SSIM in matlab (for
+  instance) emphasizes the intensity. We found that even when the
+  quality of reconstruction is acceptable visually, the SSIM values
+  were not acceptable.  We choose
+  to focus on preserving the structures on our reconstructions, and
+  not rely on the absolute intensity values alone. Hence, we choose
+  SSIM with a higher weightage to structure-preservation. For our
+  record, we have computed RMSE values as well and they are presented
+  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.
 
@@
 
-\item  \textcolor{blue}{A discussion about computational costs (time, memory) should be included in the paper.}
+\item \textcolor{blue}{A discussion about computational costs (time,
+  memory) should be included in the paper.}
 
@@
 
-Most of the
-computation time in our technique is used for the generation of low quality eigen-space
-by reconstructing each of the templates using TV and FDK.
-If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs.
-With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
-If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent.
-Here below, we describe the
-time complexity of spatially-varying prior technique.  If
+Most of the computation time in our technique is used for the
+generation of low quality eigen-space by reconstructing each of the
+templates using TV and FDK. If the set of projection views for every
+test is fixed a priori, the set of low quality reconstructions can be
+produced offline and stored in order to save computational costs. With
+this assumption, Table~\ref{table:compute_time} shows the computation
+times for various stages of reconstruction of a 2D slice of Liver on
+MATLAB 2019a on an AMD 2920X 12-Core Processor machine with 64GB
+RAM. If however, new sets of projection views for every test are to be
+allowed, the low quality reconstructions can still be performed
+efficiently using parallelization since these reconstructions are
+completely independent. Here below, we describe the time complexity of
+spatially-varying prior technique.  If
 \begin{itemize}
@@
 
-\end{itemize}
-
 \end{document}

### 2021-09-20 paper/post_tci.tex
updated changes with some reformatting and updated post_tci in two places

@@
 \end{itemize}
+While we demonstrate our results with a Total Variation regularization
+prior, this work provides a technique that can improve upon any chosen
+baseline reconstruction when measurements are extremely sparse.
 
@@
 namely, Potato and Okra, the raw measurements and corresponding
-parameters for cone-beam imaging model are available to us.
-Hence all reconstructions on these datasets were performed directly
-from real projection measurements. For the other two datasets namely, Sprouts and
-Liver, the raw measurements and the parameters of imaging
+parameters for cone-beam imaging model are available to us.  Hence all
+reconstructions on these datasets were performed directly from real
+projection measurements. These datasets are ``Type A'' datasets in the
+description below.  For the other two datasets (Type B), namely,
+Sprouts and Liver, the raw measurements and the parameters of imaging
 model were not available to us (due to propriety concerns) and hence
@@
 
-In this section, we first illustrate the advantage of using multiple types of eigenspaces for the computation of weights map, and then present reconstruction results on all datasets.
-For quantitative evaluation, we compute the Structural Similarity Index Metric (SSIM)~\cite{ssim}.
-Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to structure, contrast and intensity respectively: $0.7,0.2,0.1$.
+In this section, we first illustrate the advantage of using multiple
+types of eigenspaces for the computation of weights map, and then
+present reconstruction results on all datasets. For quantitative
+evaluation, we compute the Structural Similarity Index Metric
+(SSIM)~\cite{ssim}. Here, we assign higher importance to the
+preservation of structure in a reconstruction by assigning the
+following weights to structure, contrast and intensity respectively:
+$0.7,0.2,0.1$. The reason for emphasizing the structure with an
+exponent of 0.7 steps from the optimization process since the
+intensity span and, in general, the histogram of reconstructed volumes
+differ across various methods and solvers.
 

### 2021-10-01 ARadon_wavelet.m
Add files via upload

@@ -1,0 +1,24 @@
+
+function b = ARadon_wavelet(X_data,idx,dim,numAngles,wname,size_CA)
+
+startPt = 1;
+endPt = dim(1)*dim(2);
+X = X_data(startPt:endPt);
+X = reshape(X,[dim(1) dim(2)]);
+CA_recovered = X(1:size_CA(1),1:size_CA(2));
+CH_recovered = X(1:size_CA(1),size_CA(2)+1:end);
+CV_recovered = X(size_CA(1)+1:end,1:size_CA(2));
+CD_recovered = X(size_CA(1)+1:end,size_CA(2)+1:end);
+X = idwt2(CA_recovered,CH_recovered,CV_recovered,CD_recovered,wname);
+
+X = imresize(X,[dim(1) dim(2)]);
+startPt = 1;
+endPt = numAngles;
+angles = idx(startPt:endPt);
+
+radProj = radon(X,angles);  
+
+b1 = reshape(radProj,[size(radProj,1)*size(radProj,2) 1]);
+
+b = b1;
+

### 2021-10-01 AtRadon_wavelet.m

@@ -1,0 +1,33 @@
+function X_final = AtRadon_wavelet(b_data,idx,dim,numAngles,wname)
+    
+s = size(b_data,1);
+
+startPt = 1;
+endPt = s;
+b = b_data(startPt:endPt);
+b = reshape(b,[(size(b,1))/numAngles numAngles]);
+
+startPt = 1;
+endPt = numAngles;
+angles = idx(startPt:endPt);    
+
+backProjImg  =  iradon(b,angles,'linear','Cosine');
+
+backProjImg = backProjImg(2:2+dim(1)-1,2:2+dim(2)-1);
+[CA,CH,CV,CD] = dwt2(backProjImg,wname);
+CA = imresize(CA,[dim(1)/2 dim(2)/2]);
+CH = imresize(CH,[dim(1)/2 dim(2)/2]);
+CV = imresize(CV,[dim(1)/2 dim(2)/2]);
+CD = imresize(CD,[dim(1)/2 dim(2)/2]);
+X = [CA CH;CV CD];
+
+X = reshape(X,[size(backProjImg,1)*size(backProjImg,2) 1]);       
+
+
+X_final = X;
+
+
+
+
+
+

### 2021-10-01 computeSSIM_relMSE.m

@@ -1,0 +1,568 @@
+clc;
+clear all; close all;
+dataset = 'sprouts'
+
+if strcmp(dataset,'tmh_7')
+    
+    outDirectory = 'results/tmh_7/30_views/';
+    fileName = sprintf('%s/testIm.mat',outDirectory);
+    data = load(fileName);
+    testIm = data.testIm;
+    
+    roi_row = 135:135+140;
+    roi_col = 275:275+155;
+    testIm_roi = testIm(roi_col,roi_row);
+    testIm_roi =  testIm_roi - min(testIm_roi(:));
+    testIm_roi =  testIm_roi./max(testIm_roi(:));
+    
+    
+    testIm_zoomed = testIm(275:275+155,135:135+140);    
+    testIm_zoomed  = testIm_zoomed  - min(testIm_zoomed (:));
+    testIm_zoomed = testIm_zoomed ./max(testIm_zoomed (:));
+    name = sprintf('%s/test_zoomed.png',outDirectory);
+    imwrite(testIm_zoomed,name);
+%     figure;imshow(testIm_roi,[]);
+%     fh = figure;imshow(testIm,[]);
+%     impixelinfo;
+%     hold on;
+%     rectangle('Position',[135, 275, 140, 155],'EdgeColor','g','LineWidth',3);
+%     name = sprintf('%s/testIm_roi.png',outDirectory);
+%     f=getframe; imwrite(f.cdata,name);
+
+    fileName = sprintf('%s/fbp.mat',outDirectory);
+    data = load(fileName);
+    fbp = data.result_fbp;
+    fbp_roi = fbp(roi_col,roi_row);
+    fbp_roi =  fbp_roi - min(fbp_roi(:));
+    fbp_roi =  fbp_roi./max(fbp_roi(:));
+    
+    fbp_zoomed = fbp(275:275+155,135:135+140);       
+    fbp_zoomed  = fbp_zoomed  - min(fbp_zoomed (:));
+    fbp_zoomed = fbp_zoomed ./max(fbp_zoomed (:));
+    name = sprintf('%s/fbp_zoomed.png',outDirectory);
+    imwrite(fbp_zoomed,name);
+    
+    relMSE_FBP =  mean2((fbp_roi - testIm_roi).^2)/mean2(testIm_roi.^2);
+    ssimVal_FBP = ssim(fbp_roi,testIm_roi,'Exponents',[0.1,0.2,0.7]);
+    
[…]

### 2021-10-01 driver.m

@@ -1,0 +1,125 @@
+function driver(dataset)
+%%
+if strcmp(dataset,'potato')
+    
+    angleSet =  [12]    ;
+    name = sprintf('../../../3D/potato/inputs/potato%d_cropped_900views_fdk.mat',6) ;
+    fileData = load(name);
+    volume = fileData.FDK;
+    testIm= double(volume(:,:,30));    
+    lambdaTV_list = 0.05;%:0.05:1.1;
+    lambda_prior_list = [0.1 1.1 2.1 3.1 4.1 5.1]; % The actual lambda_prior value is squared of this value.
+    kk_values = 30;
+    lambda_TV = 0.05;  
+    
+elseif strcmp(dataset,'okra')
+    
+    sliceNum = 30;
+    angleSet = [48];    
+    name = sprintf('../../data/templates/okra/okra6_okra%d_reg_450views_fdk.mat',3) ;
+    fileData = load(name);
+    volume = fileData.FDK;
+    testIm= double(volume(15:end-14,15:end-14,sliceNum));    
+    lambdaTV_list = 0.01;%:0.005:0.1;
+    lambda_prior_list = 0.7;%[0.01, 0.03, 0.05, 0.5, 0.7, 0.9, 1.1, 5, 10]; % The actual lambda_prior value is squared of this value.
+    kk_values = [5,10,20,40,50,60,70,80,90,100];%,370,410,450];%30;
+    lambda_TV = 0.01;
+    
+elseif strcmp(dataset,'sprouts')
+    
+    sliceNum = 38;
+    angleSet = 20;%[20, 30];    
+    name = sprintf('../../3D/Sprouts/inputs/sprouts%d_givenVolume.mat',11) ;
+    fileData = load(name);
+    volume = fileData.volume;
+    testIm= double(volume(10:end-4,2:end-2,38));
+%     testIm= double(volume(:,:,sliceNum)); 
+    lambdaTV_list = 0.1;%:0.05:0.30
+    lambda_prior_list = 2.1;%[0.1 1.1 2.1 3.1 4.1]; % The actual lambda_prior value is squared of this value.
+    kk_values = 30;
+    lambda_TV = 0.1;
+    
+elseif strcmp(dataset,'tmh_7')
+    
+    angleSet = 130;% [30];
+    testNo = 16  ;
+    dataFileName = 'RFA2 - Anon/Rfa/RFA 1.5 B30s -'
+    sliceNum = 27;
+ 
+    projFolderName =  sprintf('%s %d/',dataFileName,testNo);
[…]

### 2021-10-01 filteredBackProjection2D.m

@@ -1,0 +1,5 @@
+function fbp = filteredBackProjection2D(y,numAngles,idx1,dim)
+
+proj = reshape(y,[size(y,1)/numAngles numAngles]);
+fbp = iradon(proj,idx1,'linear','Cosine');
+fbp = fbp(2:2+dim(1)-1,2:2+dim(2)-1);

### 2021-10-01 genEigenSpace2Dtmh.m

@@ -1,0 +1,123 @@
+% close all;
+% clear all;
+% clc;
+
+function [eigenVecs,meanTemplate] = genEigenSpace2Dtmh(templateNos,sliceNum,dataFileName,numSlices,sizeOfSlice,outDirectory)
+
+numTemplates = length(templateNos);
+volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+% Read the templates in 3D format-------------------
+
+for i = 1:numTemplates  
+   %name = sprintf('../../data/templates/potato/potato4_potato%d_reg_900views_fdk.mat',templateNos(i)) ;
+   
+   %projFolderName =  sprintf('%s %d/',dataFileName,templateNos(i));
+   projFolderName =  sprintf('%s %d/',dataFileName,templateNos(i));
+   dirInfo = dir(projFolderName);
+   
+    for j = 1:size(dirInfo,1)-2
+        fileName = dirInfo(j+2).name;
+        filePath = sprintf('%s/%s',projFolderName,fileName);
+        image = dicomread(filePath);
+        if j==1
+            testVol = zeros([size(image,1) size(image,2) (size(dirInfo,1)-2)]);
+        end
+        testVol(:,:,j) = image;
+    end   
+      volumes(:,:,:,i) = testVol;
+end
+
+% Get the templates and compute their mean----------------------------------------------------------
+templateIm = cell(1,numTemplates);
+for i = 1:numTemplates
+    
+    in = volumes(:,:,sliceNum,i); 
+    in = in - min(in(:));
+    in  = in./max(in(:));
+    temp = in; % double(in);
+
+    
+
+    %imshow(temp,[]); title(i); pause(0.5);    
+    if i==1
+        templates = zeros((size(temp,1)*size(temp,2)), numTemplates);
+        templates(:,1) = temp(:);
+        sumI = zeros(size(templates(:,i)));
+        
+        tt = temp;
+        minimum = min(tt(:));
+        tt = tt - minimum;
+        maximum = max(tt(:));
+    end
+    templates(:,i) = temp(:);
+    sumI = sumI + templates(:,i);
+    
+    fname = sprintf('%s/template%d.mat',outDirectory,i);
+    save(fname,'temp');
+    
+    temp = temp - minimum;
+    temp = temp./maximum;
+    templateIm{i} = temp;
+    
+    name = sprintf('%s/template%d.png',outDirectory,i);
[…]

### 2021-10-01 generateMeasurements.m

@@ -1,0 +1,29 @@
+function [y,idx1,dim] = generateMeasurements(testIm,numAngles,outDirectory)
+
+%figure;imshow(testIm,[]);
+
+fname = sprintf('%s/testIm.mat',outDirectory);
+save(fname,'testIm');
+name = sprintf('%s/testIm.png',outDirectory);
+temp = testIm;
+temp = temp - min(temp(:));
+temp = temp/max(temp(:));
+imwrite(temp,name);
+% ------------------------------
+
+dim = size(testIm);
+
+% load('../../../../dir_vectors_3668.mat');
+load('dir_vectors_3668.mat');
+%%---------------selecting same set of angles everytime
+id = 1:numAngles;        
+idx = id(1:numAngles);
+CompleteAngleSet  = mtt(idx,:);
+idx1 = (atan(CompleteAngleSet(:,2)./CompleteAngleSet(:,1)))*180/pi;
+%%---------------selecting random set of angles everytime
+% idx1 = randi(200,[1 numAngles]);
+
+radProj = radon(testIm,idx1); 
+y = reshape(radProj,[size(radProj,1)*size(radProj,2) 1]);
+y = y(:);
+

### 2021-10-01 normc_fcn.m

@@ -1,0 +1,3 @@
+function nm = normc_fcn(m)
+nm = sqrt(m.^2 ./ sum(m.^2)) .* sign(m);
+end

### 2021-10-01 performPilotReconstruction.m

@@ -1,0 +1,50 @@
+function performPilotReconstruction(y,idx1,dim,pilotReconMethods,lambda_for_pilot_recon,outDirectory)
+
+numAngles = length(idx1)
+m = size(y,1);
+A_both_functions =@(z,mode) systemFunction(z,mode,idx1,dim,numAngles,m);
+
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    lambda_for_the_method = lambda_for_pilot_recon{iter};
+    
+    switch(method)
+        case(0)
+            fname = sprintf('%s/fbp.mat',outDirectory);
+            if(isfile(fname))
+                continue;
+            else
+                %tic;
+                result_fbp = filteredBackProjection2D(y,numAngles,idx1,dim);
+                %toc;
+                save(fname,'result_fbp');
+                name = sprintf('%s/fbp.png',outDirectory);
+                temp = result_fbp;
+                temp = temp - min(temp(:));
+                temp = temp/max(temp(:));
+                imwrite(temp,name);
+            end
+        
+        case(1)            
+            lambdaTV_list =lambda_for_the_method;
+            for i = 1:length(lambdaTV_list)
+                lambdaTV = lambdaTV_list(i)
+                %fname = sprintf('%s/tv_lambdaTV_%.2f.mat',outDirectory,lambdaTV);
+                fname = sprintf('%s/tv_lambdaTV_%.3f.mat',outDirectory,lambdaTV); 
+                if(isfile(fname))
+                    continue;
+                else
+                    %tic;
+                    result_tv = plain_TV(y,dim,lambdaTV,A_both_functions);
+                    %toc;
+                    save(fname,'result_tv');
+                    name = sprintf('%s/tv_lambdaTV_%.3f.png',outDirectory,lambdaTV);
+                    temp = result_tv;
+                    temp = temp - min(temp(:));
+                    temp = temp/max(temp(:));
+                    imwrite(temp,name);
+                end
+            end
+    end
+end
+

### 2021-10-01 performWeightedPriorReconstruction.m

@@ -1,0 +1,44 @@
+function performWeightedPriorReconstruction(dataset,y,idx1,dim,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior_list,kk,sliceNum,outDirectory)
+
+pilotRecons = cell([2,dim]);
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)        
+               fname = sprintf('%s/fbp.mat',outDirectory);
+               data = load(fname);
+               result_fbp = data.result_fbp;
+               pilotRecons{1} = result_fbp;
+        case(1) 
+               lambdaTV = lambda_for_base_method;
+               fname = sprintf('%s/tv_lambdaTV_%.3f.mat',outDirectory,lambdaTV);
+               data = load(fname);
+               result_tv = data.result_tv;
+               pilotRecons{2} = result_tv;
+    end
+end
+
+dim = size(result_fbp);
+
+for iter = 1:length(lambda_prior_list)
+    lambda_prior = lambda_prior_list(iter);
+    numCycles = 5;
+    [result_weighted_pca,weightsIm] =  weighted_prior(dataset,y,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,idx1,numCycles,...
+                                 pilotRecons,sliceNum,outDirectory,kk);
+
+    fname = sprintf('%s/weighted_prior_kk_%d_lambda_prior_%f.mat',outDirectory,kk,lambda_prior);
+    save(fname,'result_weighted_pca');
+    name = sprintf('%s/weighted_prior_kk_%d_lambda_prior_%f.png',outDirectory,kk,lambda_prior);
+    temp = result_weighted_pca;
+    temp = temp - min(temp(:));
+    temp = temp/max(temp(:));
+    imwrite(temp,name);    
+
+    fname = sprintf('%s/weightsIm_kk_%d_lambda_prior_%f.mat',outDirectory,kk,lambda_prior);
+    save(fname,'weightsIm');
+    name = sprintf('%s/weightsIm_kk_%d_lambda_prior_%f.png',outDirectory,kk,lambda_prior);
+    temp = weightsIm;
+    temp = temp - min(temp(:));
+    temp = temp/max(temp(:));
+    imwrite(temp,name);  
+end

### 2021-10-01 plain_TV.m

@@ -1,0 +1,25 @@
+function result_plain_TV = plain_TV(y,dim,lambdaTV,A_both_functions)
+
+    
+addpath('TVReg-master/');
+
+dims=[dim(1) dim(2)];
+opt_ref.epsb_rel = 1e-4;
+opt_ref.k_max    = 20000;
+opt_ref.verbose  = 1;
+tau = 0.0001;
+% Specify nonnegativity constraints
+constraint.type = 2;
+constraint.c    = 0*ones(prod(dims),1);
+constraint.d    = 1*ones(prod(dims),1);
+
+[x_ref fxk_ref hxk_ref gxk_ref fxkl_ref info_ref] = ...
+tvreg_upn(A_both_functions,y,lambdaTV,tau,dims,constraint,opt_ref);
+
+result_plain_TV = reshape(x_ref,[dim(1) dim(2)]);
+  
+ 
+    
+end
+
+

### 2021-10-01 projectPilot_on_EigenSpace_2D.m

@@ -1,0 +1,216 @@
+function P_pilot = projectPilot_on_EigenSpace_2D(dataset,idx1,pilotOfTestIm,lambda,A_both_functions,method,sliceNo,outDirectory)
+
+dim = size(pilotOfTestIm);
+
+if strcmp(dataset,'potato')
+    templateNos = [1,3,4];
+    numTemplates = length(templateNos);
+    numSlices = 100;
+    sizeOfSlice = [150 150];
+    volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+    for i = 1:numTemplates  
+       name = sprintf('../../3D/potato/inputs/potato%d_cropped_900views_fdk.mat',templateNos(i)) ;
+       fileData = load(name);
+       fdkVol = fileData.FDK;
+       resizedVol = fdkVol;%imresize(fdkVol(10:end-13,10:end-13,:),0.5);
+       volumes(:,:,:,i) = resizedVol;
+    end
+%     sliceNo = 30;
+end
+if strcmp(dataset,'okra')
+    templateNos = [4,5,6,7];
+    numTemplates = length(templateNos);
+    numSlices = 123; % number of slices in a volume;
+    sizeOfSlice = [310 310];
+    volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+    for i = 1:numTemplates  
+       name = sprintf('../../data/templates/okra/okra6_okra%d_reg_450views_fdk.mat',templateNos(i)) ;
+       fileData = load(name);
+       fdkVol = fileData.FDK;
+       volumes(:,:,:,i) = fdkVol(15:end-14,15:end-14,:);
+    end
+%     sliceNo = 30;
+
+end
+
+if strcmp(dataset,'sprouts')
+    templateNos = [5,6,7,9,10];
+    numTemplates = length(templateNos);
+    numSlices = 130;%161;
+    sizeOfSlice = [260 260];
+    volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+    for i = 1:numTemplates  
+       name = sprintf('../../3D/Sprouts/inputs/sprouts%d_givenVolume.mat',templateNos(i)) ;
+       fileData = load(name);
+       fdkVol = fileData.volume;
+       volumes(:,:,:,i) = fdkVol(10:end-4,2:end-2,:);
[…]

### 2021-10-01 paper/changes.tex
Changes in Complexity Analysis, minor changes in changes.pdf

@@
    We accept this point, and have now discussed the difficulties in
-   using deep-learning techniques for the current problem in Sec.~7C
-   of our paper. We also describe them here below.
-
-\textcolor{red}{Comment from Sharat:  Since the material is in the text, there is no need to mention it here.}
-
-  In a machine learning based setting, our goal of detecting new
-  changes is a `prediction' problem in a continuous solution space
-  i.e., \textit{``given intensities of a voxel at various time
-    instants in a longitudinal setting and partial measurements of the
-    voxel at the current time, what will be the intensity of the same
-    voxel at the current time instant?''} This estimation can be
-  learnt by a deep neural network if there are hundreds of labeled
-  data.  However, generalization of this across multiple datasets
-  poses a question mark.
-
-  %% thousands of time instants at which the previous voxel
-  %% intensities are known for each voxel. This amount of data is not
-  %% available to us, and may be hard to acquire because each specimen
-  %% is usually scanned only a couple of times in any longitudinal
-  %% study.
-
-  Further, a specific `event-of-interest' may occur just once in a
-  longitudinal study and hence training on data of all previous time
-  instants may be misleading. If however, we use measurements from
-  identical and full-cycle longitudinal studies, including
-  events-of-interest, of similar specimen (instead of the `same'
-  specimen as we used), a deep-learning technique may be applied. We
-  see this as an extension of using object-prior generated from the
-  same object, and hence we have not explored this direction.
-
-  Another avenue for using deep-networks \textit{within} our current
-  work is to replace the currently used fixed eigenspace provided by
-  PCA by a learnt feature basis provided by a network such as an
-  autoencoder. For each dataset, an autoencoder may be trained to
-  learn a specific set of latent features (this might again require
-  atleast a few tens of volumes). We see this as a future direction of
-  work.
+   using deep-learning techniques for the current problem in Section.~7C
+   of our paper.
 
@@
 
-  We now present details of both time and space complexities of our technique in Section.7B of our paper.
+  We now present details of both time and space complexities of our technique in Section.~7B of our paper.
 
-Most of the computation time in our technique is used for the
-generation of low quality eigen-space by reconstructing each of the
-templates using TV and FDK. If the set of projection views for every
-test is fixed a priori, the set of low quality reconstructions can be
-produced offline and stored in order to save computational costs. With
-this assumption, Table~\ref{table:compute_time} shows the computation
-times for various stages of reconstruction of a 2D slice of Liver on
-MATLAB 2019a on an AMD 2920X 12-Core Processor machine with 64GB
-RAM. If however, new sets of projection views for every test are to be
-allowed, the low quality reconstructions can still be performed
-efficiently using parallelization since these reconstructions are
-completely independent. Here below, we describe the time complexity of
-spatially-varying prior technique.  If
-\begin{itemize}
-\item $N =$ number of voxels of the volume
-\item $T =$ number of templates available, and
-\item $F =$ time taken for iterative TV optimization,
-\end{itemize}
-then, the computational complexity is sum of the following
-\begin{itemize}
-\item $O(NT^2+T^3)$ for creating the eigenspace,
-\item $O(NT^2)$ for deriving the weights map, and
-\item time $F$  taken for iterative minimization
-\end{itemize}
-where $O(.)$ is the notation for `Big O' used in complexity analysis. 
-In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions.
-We only need to store a single weights map volume regardless of the number of templates available.
-
-\begin{table}[]
-  \centering
-  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
-Here we assume that low quality eigen-spaces of the templates are computed offline.}
-\begin{tabular}{|l|l|l|l|}
-\hline
-Backprojection             & TV                        & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map\end{tabular} & \begin{tabular}[c]{@{}l@{}}Final reconstruction\\ with spatially-varying \\ prior\end{tabular} \\ \hline
-\multicolumn{1}{|c|}{0.40} & \multicolumn{1}{c|}{8.44} & \multicolumn{1}{c|}{0.04}                                             & \multicolumn{1}{c|}{46.73}                                                                     \\ \hline
-\end{tabular}
-\label{table:compute_time}
-\end{table}
   \end{itemize}

### 2021-10-01 paper/post_tci.tex
Changes in Complexity Analysis, minor changes in changes.pdf

@@
   \end{split}
+    \label{eq:compute_x}
   \end{equation}
@@
   \boldsymbol{\alpha} = [(\boldsymbol{WV})^T\boldsymbol{WV}]^{-1}\boldsymbol{V}^T(\boldsymbol{W}^T\boldsymbol{W}(\boldsymbol{x} - \boldsymbol{\mu}))
+  \label{eq:compute_alpha}
 \end{equation}
@@
 In this section, we discuss tuning of parameters, computational complexity of our method, and requirements for applying deep learning techniques in longitudinal few-view reconstruction.
-\subsection{Tuning of parameters:}
+\subsection{Tuning of parameters}
 $\lambda_1$, $\lambda_2$ and $k$ are the three
@@
 \end{figure}
-\subsection{Computational Complexity:}
+\subsection{Computational Complexity}
 Most of the
@@
 If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs.
-With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
+With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver (refer code in~\cite{codeRepo}) on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
 If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent.
 Here below, we describe the
-time complexity of spatially-varying prior technique.  If
+time complexity of spatially-varying prior technique.  Let
 \begin{itemize}
-\item $N =$ number of voxels of the volume
-\item $T =$ number of templates available, and
-\item $F =$ time taken for iterative TV optimization,
+\item $N$ denote the number of voxels of test volume,
+\item $L$ denote the number of templates available,
+\item $M$ denote the number of pilot reconstruction algorithms used for the computation of weights map, and
+\item $F$ denote the time taken for optimization.
 \end{itemize}
-then, the computational complexity is sum of the following
+$F$ consists of time taken for alternate minimization of Eq.~\ref{eq:spatially_varying_prior}, which in turn consists of time taken for repeated cycles of a closed-form update of $\boldsymbol{\alpha}$ (Eq.~\ref{eq:compute_alpha}) and an iterative optimization of  $\boldsymbol{x}$ (Eq.~\ref{eq:compute_x}).
+Speed of iterative optimization is dependent on the number of imaging views as well.
+Therefore, the time computational complexity of our method is sum of the following
 \begin{itemize}
-\item $O(NT^2+T^3)$ for creating the eigenspace,
-\item $O(NT^2)$ for deriving the weights map, and
+\item $O(NL^2+L^3)$ for creating eigenspace,
+\item $O(NL)*M$ for deriving weights map, and
 \item time $F$  taken for iterative minimization
@@
 where $O(.)$ is the notation for `Big O' used in complexity analysis. 
-In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions.
+In terms of space, the complexity is $O(NL +N)$ to store each of the $L$ templates and their low quality reconstructions, and to store one weights map.
 We only need to store a single weights map volume regardless of the number of templates available.
@@
  \centering
-  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
+  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver (refer code in~\cite{codeRepo}) on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
 Here we assume that low quality eigen-spaces of the templates are computed offline.}

### 2021-10-01 paper/changes.tex
edits to comutatinal complexity in main paper and changes regarding ssim in the changes.pdf part

@@
  is no prior information about the number of possible attentuation
- coefficients in the test object. Among other iterative techniques, we
+ coefficients in the test object.
+%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
+ Among other iterative techniques, we
  have used Simultaneous Iterative Reconstruction Technique (SIRT),
@@
   The reason for not reporting RMSE stems from the optimization
-  process. The optimization routine we use transforms the
-  reconstruction to a different space.  That is, in our experiments,
-  we observed that for a given dataset and a set of projection
-  measurements, the intensity span of histograms of reconstructed
-  volumes differ across various methods and solvers. As a result, the
-  RMSE values are not particularly useful.  We provide the numbers
-  here to show the improvement trend but we believe it does not serve
-  the interest of the community to report these.
+  process in Equation~\ref{asfdaf}. The optimization routine we use
+  transforms the reconstruction values to a different range of
+  numerical values.  That is, in our experiments, we observed that for
+  a given dataset and a set of projection measurements, the intensity
+  span of histograms of reconstructed volumes differ considerably across various
+  methods and solvers.  As a result, the RMSE values are not
+  particularly useful, and may even be misleading.  We provide the RMSE numbers below to show the
+  improvement trend but we believe it does not serve the interest of
+  the community to report these in the main paper.
 
@@
   quality of reconstruction is acceptable visually, the SSIM values
-  were not acceptable.  We choose
+  with the standard values were not acceptable.  We choose
   to focus on preserving the structures on our reconstructions, and
   not rely on the absolute intensity values alone. Hence, we choose
-  SSIM with a higher weightage to structure-preservation. For our
-  record, we have computed RMSE values as well and they are presented
-  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.
+  SSIM with a higher weightage to structure-preservation.
+
+  For the record, sample RMSE values are presented
+  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse} that shows
+  the superiority of method at the risk of misleading absolute numbers.
+
+  %% Why not combine all of the values in one table?
 

### 2021-10-01 paper/post_tci.tex
edits to comutatinal complexity in main paper and changes regarding ssim in the changes.pdf part

@@
 \subsection{Computational Complexity}
-Most of the
-computation time in our technique is used for the generation of low quality eigen-space
-by reconstructing each of the templates using TV and FDK.
-If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs.
-With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver (refer code in~\cite{codeRepo}) on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
-If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent.
-Here below, we describe the
-time complexity of spatially-varying prior technique.  Let
+
+Most of the computation time in our technique is used for the
+generation of low quality eigen-space by reconstructing each of the
+templates using TV and FDK. If the set of projection views for every
+test is fixed a priori, a reasonable assumption,
+the set of low quality reconstructions can be
+produced offline and stored in order to save computational costs. With
+this assumption, Table~\ref{table:compute_time} shows the computation
+times for various stages of reconstruction of a 2D slice of Liver
+(refer code in~\cite{codeRepo}) on MATLAB 2019a on an AMD 2920X
+12-Core Processor machine with 64GB RAM. If however, new sets of
+projection views for every test are to be allowed, the low quality
+reconstructions can still be performed efficiently using
+parallelization since these reconstructions are completely
+independent. Here below, we describe the time complexity of
+spatially-varying prior technique.  Let
 \begin{itemize}
@@
 \item $F$ denote the time taken for optimization.
+  $F$ consists of time taken for alternate minimization of Eq.~\ref{eq:spatially_varying_prior}, which in turn consists of time taken for repeated cycles of a closed-form update of $\boldsymbol{\alpha}$ (Eq.~\ref{eq:compute_alpha}) and an iterative optimization of  $\boldsymbol{x}$ (Eq.~\ref{eq:compute_x}).
 \end{itemize}
-$F$ consists of time taken for alternate minimization of Eq.~\ref{eq:spatially_varying_prior}, which in turn consists of time taken for repeated cycles of a closed-form update of $\boldsymbol{\alpha}$ (Eq.~\ref{eq:compute_alpha}) and an iterative optimization of  $\boldsymbol{x}$ (Eq.~\ref{eq:compute_x}).
-Speed of iterative optimization is dependent on the number of imaging views as well.
-Therefore, the time computational complexity of our method is sum of the following
-\begin{itemize}
-\item $O(NL^2+L^3)$ for creating eigenspace,
-\item $O(NL)*M$ for deriving weights map, and
-\item time $F$  taken for iterative minimization
-\end{itemize}
-where $O(.)$ is the notation for `Big O' used in complexity analysis. 
+We ntoe that in practice $L$ is independent of $N$ and is likely to be $O(1)$  (e.g.
+about 12 scans in a year for disease prognosis).
+Likewise $M$ is also $O(1)$.
+The speed of iterative optimization is dependent on the number of imaging views, and is profoundly impacted by the actual method used.
+Therefore, the time computational complexity of our method is sum of
+the following
+\begin{enumerate}
+\item $O(NL^2+L^3)$ for creating eigenspace, which is, in practice linear, i.e., $O(N)$
+\item $O(NL)*M$ for deriving weights map, which is, in practice linear, i.e., $O(N)$
+\item and the time $F$  taken for iterative minimization, which as mentioned above is not the key contribution of this paper. 
+\end{enumerate}
+In short, the additional burden of the key idea of this paper viz.
+generating weights map is linear in the number of voxels, although admittedly the burden $F$ of repated optimization drives up the cost.
+
 In terms of space, the complexity is $O(NL +N)$ to store each of the $L$ templates and their low quality reconstructions, and to store one weights map.

### 2021-10-02 post_tci.tex
Add files via upload
Added RMSE values in main paper, references in changes.pdf

--- 2021-10-01 paper/post_tci.tex
@@
   \centering
-\caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ground-truth (ideal reconstruction) is 1.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\caption{SSIM and Relative MSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ground-truth (ideal reconstruction) is 1.}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
 \hline
-  \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
- 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
+ & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
+SSIM & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
+Rel.MSE & 0.33 & 0.07 & 0.14 & 0.41 & 0.24 & 0.1 & 0.03 & \textcolor{red}{0.00}\\ \hline
 \end{tabular}
@@
   \centering
-  \caption{SSIM of reconstructed potato from various
+  \caption{\{SSIM/Relative MSE\} of reconstructed potato from various
     methods. SSIM of ground-truth (ideal reconstruction) is 1.}
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.52
-& 0.92 & \textcolor{red}{0.97} \\ \hline \textbf{3D} & 0.58 & 0.75 & \textcolor{red}{0.84}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.52 / 0.16
+& 0.92 / 0.00 & \textcolor{red}{0.97 / 0.00} \\ \hline \textbf{3D} & 0.58 / 0.29 & 0.75 / 0.24 & \textcolor{red}{0.84 / 0.18}
 \\ \hline
@@
 \label{Sec:okra_spatially_varying}
-The test volume was reconstructed from a partial set of $6.7\%$ of projection views from which
+The test volume was reconstructed from a partial set of $10\%$ of projection views from which
 ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
@@
   \centering
-  \caption{SSIM of reconstructed okra from various
+  \caption{\{SSIM/Relative MSE\} of reconstructed okra from various
     methods. SSIM of ground-truth (ideal reconstruction) is 1.}
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.46
-& 0.50 & \textcolor{red}{0.74} \\ \hline \textbf{3D} & 0.69 & 0.74 & \textcolor{red}{0.78}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.46 / 0.22
+& 0.50 / 0.16 & \textcolor{red}{0.74 / 0.06} \\ \hline \textbf{3D} & 0.65 / 0.35 & 0.70 / 0.32 & \textcolor{red}{0.71 / 0.29}
 \\ \hline
@@
   \centering
-  \caption{SSIM of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ground-truth (ideal reconstruction), SSIM equals 1.}
+  \caption{\{SSIM/Rel.MSE\} of 2D reconstruction of radio-frequency ablation data from various methods.
+Values have been computed within the RoI.
+For ground-truth (ideal reconstruction), SSIM equals 1.}
 \begin{tabular}{|l|c|c|c|c|}
 \hline \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline  0.73
-& 0.91 & \textcolor{red}{0.95} \\ \hline 
+\textbf{This paper} \\ \hline  0.73 / 0.05
+& 0.91 / 0.17 & \textcolor{red}{0.95 / 0.03} \\ \hline 
 \end{tabular}
@@
   \centering
-  \caption{SSIM of reconstructed sprouts from various
+  \caption{\{SSIM/Relative MSE\} of reconstructed sprouts from various
     methods. The SSIM of ground-truth (ideal reconstruction) is 1.}
@@
 \textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
- \\ \hline \textbf{2D} & 0.67
-& 0.82 & \textcolor{red}{0.86} \\ \hline \textbf{3D} & 0.67 & 0.73 & \textcolor{red}{0.82}
+ \\ \hline \textbf{2D} & 0.67 / 0.23
+& 0.82 / 0.12 & \textcolor{red}{0.86 / 0.07} \\ \hline \textbf{3D} & 0.67 / 0.53 & 0.73 / 0.48 & \textcolor{red}{0.82 / 0.30}
 \\ \hline
@@
 \end{itemize}
-We ntoe that in practice $L$ is independent of $N$ and is likely to be $O(1)$  (e.g.
+We note that in practice $L$ is independent of $N$ and is likely to be $O(1)$  (e.g.
 about 12 scans in a year for disease prognosis).
 Likewise $M$ is also $O(1)$.
-The speed of iterative optimization is dependent on the number of imaging views, and is profoundly impacted by the actual method used.
+The speed of iterative optimization is dependent on the number of imaging views, and is profoundly impacted by the actual numerical optimization technique used.
 Therefore, the time computational complexity of our method is sum of
@@
 \item $O(NL^2+L^3)$ for creating eigenspace, which is, in practice linear, i.e., $O(N)$
-\item $O(NL)*M$ for deriving weights map, which is, in practice linear, i.e., $O(N)$
+\item $O(NLM)$ for deriving weights map, which is, in practice linear, i.e., $O(N)$
 \item and the time $F$  taken for iterative minimization, which as mentioned above is not the key contribution of this paper. 
@@
 In short, the additional burden of the key idea of this paper viz.
-generating weights map is linear in the number of voxels, although admittedly the burden $F$ of repated optimization drives up the cost.
+generating weights map is linear in the number of voxels, although admittedly the burden $F$ of alternate minimization drives up the cost.
 
@@
 \hline
-Backprojection             & TV                        & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map\end{tabular} & \begin{tabular}[c]{@{}l@{}}Final reconstruction\\ with spatially-varying \\ prior\end{tabular} \\ \hline
-\multicolumn{1}{|c|}{0.40} & \multicolumn{1}{c|}{8.44} & \multicolumn{1}{c|}{0.04}                                             & \multicolumn{1}{c|}{46.73}                                                                     \\ \hline
+ \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
+\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{6} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34}                                                                     \\ \hline
 \end{tabular}

### 2021-10-02 paper/changes.tex
Add files via upload
Added RMSE values in main paper, references in changes.pdf

@@
 \documentclass{article}
+\bibliographystyle{IEEEtran}
+
 \usepackage{amsmath}
@@
  Among the family of algebraic techniques, we have compared our method
- with Algebraic Reconstruction Technique (ART) and Simultaneous
- Algebraic Reconstruction Technique (SART). We do not reconstruct
- using Discrete Algebraic Reconstruction Technique (DART) since there
+ with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
+ Algebraic Reconstruction Technique (SART)~\cite{sart}. We do not reconstruct
+ using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
  is no prior information about the number of possible attentuation
@@
  Among other iterative techniques, we
- have used Simultaneous Iterative Reconstruction Technique (SIRT),
- Total Variation (TV) and Compressed Sensing (CS) with Haar wavelet
+ have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
+ Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
  and DCT as sparsity basis. The details of solvers used for these
@@
   The reason for not reporting RMSE stems from the optimization
-  process in Equation~\ref{asfdaf}. The optimization routine we use
+  process in Equation~\ref{Eq:simple_TV}.
+
+ \begin{equation}
+   J_{TV}(\boldsymbol{x}) = \lVert\boldsymbol{\mathcal{R}x}- \boldsymbol{y}\rVert_2^2 + \lambda_{TV}TV(\boldsymbol{x})
+   \label{Eq:simple_TV}
+ \end{equation}
+
+  This optimization routine 
   transforms the reconstruction values to a different range of
@@
   For the record, sample RMSE values are presented
-  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse} that shows
-  the superiority of method at the risk of misleading absolute numbers.
+  here in Table~\ref{table:rmse} that shows
+  the superiority of our method at the risk of misleading absolute numbers.
 
@@
   \centering
- \caption{RMSE within the RoI of 3D reconstructed Potato volume from various
-    methods.}
-\begin{tabular}{|l|c|c|c|c|}
+ \caption{RMSE of reconstructions from various
+    methods within the RoI.}
+\begin{tabular}{|l|c|c|c|c|c|}
 \hline 
-\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
-\\ \hline  0.29 & 0.24 & \textcolor{red}{0.18}
+&\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
+\\ \hline \textbf{Potato}& 0.29 & 0.24 & \textcolor{red}{0.18}
+\\ \hline \textbf{Sprouts}& 0.53 & 0.48 & \textcolor{red}{0.30}
+\\ \hline \textbf{Liver}& 0.05 & 0.17 & \textcolor{red}{0.03}
 \\ \hline
 \end{tabular}
-\label{table:potato_rmse}
-\end{table}
-
-\begin{table}[!h]
-  \centering
- \caption{RMSE within the RoI of 3D reconstructed Sprouts volume from various
-    methods.}
-\begin{tabular}{|l|c|c|c|c|}
-\hline 
-\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
-\\ \hline  0.53 & 0.48 & \textcolor{red}{0.30}
-\\ \hline
-\end{tabular}
-\label{table:sprouts_rmse}
+\label{table:rmse}
 \end{table}
@@
 
+\bibliography{tci_ref}  
 \end{document}

### 2021-10-02 paper/post_tci.tex
Changes in text of RMSE

@@
 $0.7,0.2,0.1$. The reason for emphasizing the structure with an
-exponent of 0.7 steps from the optimization process since the
-intensity span and, in general, the histogram of reconstructed volumes
+exponent of 0.7 stems from the optimization process since the
+intensity span (and, in general, the histogram) of reconstructed volumes
 differ across various methods and solvers.
@@
   \centering
-\caption{SSIM of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ground-truth (ideal reconstruction) is 1.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\caption{SSIM and Relative MSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ideal reconstruction is 1.}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
 \hline
-  \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
- 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
+ & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
+SSIM & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
+Rel.MSE & 0.33 & 0.07 & 0.14 & 0.41 & 0.24 & 0.1 & 0.03 & \textcolor{red}{0.00}\\ \hline
 \end{tabular}
@@
   \centering
-  \caption{SSIM of reconstructed potato from various
-    methods. SSIM of ground-truth (ideal reconstruction) is 1.}
+  \caption{The SSIM (Relative MSE) of reconstructed potato from various
+    methods. The SSIM of ideal reconstruction is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
@@
   \centering
-  \caption{SSIM of reconstructed okra from various
-    methods. SSIM of ground-truth (ideal reconstruction) is 1.}
+  \caption{The SSIM (Relative MSE) of reconstructed okra from various
+    methods. SSIM of the ideal reconstruction is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
@@
   \centering
-  \caption{SSIM of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ground-truth (ideal reconstruction), SSIM equals 1.}
+  \caption{The SSIM (Relative MSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ideal reconstruction, SSIM equals 1.}
 \begin{tabular}{|l|c|c|c|c|}
 \hline \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline  0.73
-& 0.91 & \textcolor{red}{0.95} \\ \hline 
+\textbf{This paper} \\ \hline  0.73 / 0.05
+& 0.91 / 0.17 & \textcolor{red}{0.95 / 0.03} \\ \hline 
 \end{tabular}
@@
   \centering
-  \caption{SSIM of reconstructed sprouts from various
-    methods. The SSIM of ground-truth (ideal reconstruction) is 1.}
+  \caption{The SSIM (Relative MSE) of reconstructed sprouts from various
+    methods. The SSIM of ideal reconstruction) is 1.}
 \begin{tabular}{|l|c|c|c|c|c|}
@@
 \end{itemize}
-We ntoe that in practice $L$ is independent of $N$ and is likely to be $O(1)$  (e.g.
-about 12 scans in a year for disease prognosis).
-Likewise $M$ is also $O(1)$.
-The speed of iterative optimization is dependent on the number of imaging views, and is profoundly impacted by the actual method used.
+We note that in practice $L$ is independent of $N$ and is likely to be
+$O(1)$  (e.g. about 12 scans in a year for disease prognosis).
+Likewise $M$ is also $O(1)$. The speed of the iterative optimization is dependent on the number of imaging views, and is profoundly impacted by the actual numerical optimization technique used.  
 Therefore, the time computational complexity of our method is sum of
@@
 \item $O(NL^2+L^3)$ for creating eigenspace, which is, in practice linear, i.e., $O(N)$
-\item $O(NL)*M$ for deriving weights map, which is, in practice linear, i.e., $O(N)$
+\item $O(NLM)$ for deriving weights map, which is, in practice linear, i.e., $O(N)$
 \item and the time $F$  taken for iterative minimization, which as mentioned above is not the key contribution of this paper. 
 \end{enumerate}
-In short, the additional burden of the key idea of this paper viz.
-generating weights map is linear in the number of voxels, although admittedly the burden $F$ of repated optimization drives up the cost.
+In short, the additional burden of the key idea of this paper
+viz. generating weights map is linear in the number of voxels,
+although admittedly the burden $F$ of the alternate minimization procedure drives up
+the cost.
 
@@
 \hline
-Backprojection             & TV                        & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map\end{tabular} & \begin{tabular}[c]{@{}l@{}}Final reconstruction\\ with spatially-varying \\ prior\end{tabular} \\ \hline
-\multicolumn{1}{|c|}{0.40} & \multicolumn{1}{c|}{8.44} & \multicolumn{1}{c|}{0.04}                                             & \multicolumn{1}{c|}{46.73}                                                                     \\ \hline
+ \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
+\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{6.00} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
 \end{tabular}

### 2021-10-03 paper/changes.tex
Replaced Relative MSE values by RMSE, including reviewer's comment on DART in changes.pdf

@@
  with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
- Algebraic Reconstruction Technique (SART)~\cite{sart}. We do not reconstruct
- using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
- is no prior information about the number of possible attentuation
- coefficients in the test object.
+ Algebraic Reconstruction Technique (SART)~\cite{sart}. 
 %% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
@@
  sparsity basis.
+
+ \item \textcolor{blue}{The paper would be improved by including results from more methods, for example ...DART}\\
+   We do not reconstruct
+ using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
+ is no prior information about the number of possible attentuation
+ coefficients in the test object.
 
@@
 &\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
-\\ \hline \textbf{Potato}& 0.29 & 0.24 & \textcolor{red}{0.18}
-\\ \hline \textbf{Sprouts}& 0.53 & 0.48 & \textcolor{red}{0.30}
-\\ \hline \textbf{Liver}& 0.05 & 0.17 & \textcolor{red}{0.03}
+\\ \hline \textbf{Potato}& (from paper)  &  & \textcolor{red}{}
+\\ \hline \textbf{Sprouts}&  &  & \textcolor{red}{}
+\\ \hline \textbf{Liver}&  &  & \textcolor{red}{}
 \\ \hline

### 2021-10-03 paper/post_tci.tex
Replaced Relative MSE values by RMSE, including reviewer's comment on DART in changes.pdf

@@
   \centering
-\caption{SSIM and Relative MSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ideal reconstruction is 1.}
+\caption{SSIM and RMSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ideal reconstruction is 1.}
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
@@
 SSIM & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
-Rel.MSE & 0.33 & 0.07 & 0.14 & 0.41 & 0.24 & 0.1 & 0.03 & \textcolor{red}{0.00}\\ \hline
+RMSE & 0.38 & 0.18 & 0.25 & 0.43 & 0.33 & 0.21 & 0.11 & \textcolor{red}{0.04}\\ \hline
 \end{tabular}
@@
   \centering
-  \caption{The SSIM (Relative MSE) of reconstructed potato from various
+  \caption{The SSIM (RMSE) of reconstructed potato from various
     methods. The SSIM of ideal reconstruction is 1.}
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.52 / 0.16
-& 0.92 / 0.00 & \textcolor{red}{0.97 / 0.00} \\ \hline \textbf{3D} & 0.58 / 0.29 & 0.75 / 0.24 & \textcolor{red}{0.84 / 0.18}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.52 (0.36)
+& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
 \\ \hline
@@
   \centering
-  \caption{The SSIM (Relative MSE) of reconstructed okra from various
+  \caption{The SSIM (RMSE) of reconstructed okra from various
     methods. SSIM of the ideal reconstruction is 1.}
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.46 / 0.22
-& 0.50 / 0.16 & \textcolor{red}{0.74 / 0.06} \\ \hline \textbf{3D} & 0.65 / 0.35 & 0.70 / 0.32 & \textcolor{red}{0.71 / 0.29}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
+& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ \hline \textbf{3D, 30 views} & 0.69 (0.21) & 0.74 (0.30) & \textcolor{red}{0.78 (0.26)}\\
+\hline \textbf{3D, 45 views} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
 \\ \hline
@@
   \centering
-  \caption{The SSIM (Relative MSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ideal reconstruction, SSIM equals 1.}
+  \caption{The SSIM (RMSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ideal reconstruction, SSIM equals 1.}
 \begin{tabular}{|l|c|c|c|c|}
 \hline \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline  0.73 / 0.05
-& 0.91 / 0.17 & \textcolor{red}{0.95 / 0.03} \\ \hline 
+\textbf{This paper} \\ \hline  0.73 (0.04)
+& 0.91 (0.09) & \textcolor{red}{0.95 (0.03)} \\ \hline 
 \end{tabular}
@@
   \centering
-  \caption{The SSIM (Relative MSE) of reconstructed sprouts from various
+  \caption{The SSIM (RMSE) of reconstructed sprouts from various
     methods. The SSIM of ideal reconstruction) is 1.}
@@
 \textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
- \\ \hline \textbf{2D} & 0.67 / 0.23
-& 0.82 / 0.12 & \textcolor{red}{0.86 / 0.07} \\ \hline \textbf{3D} & 0.67 / 0.53 & 0.73 / 0.48 & \textcolor{red}{0.82 / 0.30}
+ \\ \hline \textbf{2D} & 0.67 (0.24)
+& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
 \\ \hline
@@
 
-\begin{table}[]
+\begin{table}[!h]
  \centering
@@
  \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
-\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{6.00} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
+\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{5.63} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
 \end{tabular}

### 2021-10-06 paper/post_tci.tex
Reorganized the section on computational complexity.  Also removed (latex commented) the irrelevant part of pre-computation and parallelization since the comment has already been made earlier (now appears as a footnote).
Added the note about the code base in changes.pdf also

@@
 Sensing based l1-ls prior~\cite{my_dicta_paper}. For the purposes of
-demonstrating the efficacy of our method, we use the well known total Variation (TV)
+demonstrating the efficacy of our method, we use the well known Total Variation (TV)
 regularization prior.
@@
     template $Q_i$ using the $M$ different algorithms, for each of the
-    $L$ previously scanned objects. Let this set be denoted by $Y
+    $L$ previously scanned objects.
+Let this set\footnote{If the set of projection views for every test is fixed a priori, this set of low quality reconstructions can be produced offline and stored, in order to save computational costs.
+If new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization.} be denoted by $Y
     \triangleq \{\{Y_{i}^j\}_{j=1}^M\}_{i=1}^L$ where $Y^{1}_i =
     Y^{\text{fdk}}_i$, $\forall i \in \{1,..,,L\}$.
-If the set of projection views for every test is fixed a priori, this set of low quality reconstructions can be produced offline and stored, in order to save computational costs.
-If new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization.
 
@@
 
-Most of the computation time in our technique is used for the
-generation of low quality eigen-space by reconstructing each of the
-templates using TV and FDK. If the set of projection views for every
-test is fixed a priori, a reasonable assumption,
-the set of low quality reconstructions can be
-produced offline and stored in order to save computational costs. With
-this assumption, Table~\ref{table:compute_time} shows the computation
-times for various stages of reconstruction of a 2D slice of Liver
-(refer code in~\cite{codeRepo}) on MATLAB 2019a on an AMD 2920X
-12-Core Processor machine with 64GB RAM. If however, new sets of
-projection views for every test are to be allowed, the low quality
-reconstructions can still be performed efficiently using
-parallelization since these reconstructions are completely
-independent. Here below, we describe the time complexity of
-spatially-varying prior technique.  Let
+We discuss the computing burden of our method in two parts: the big-Oh
+(symbolic) complexity, and the actual time taken on a specific dataset
+on a specific computer. In the latter case, we provide the actual
+code~\cite{codeRepo} for the purposes of reproduction.
+
+\subsubsection{Symbolic}
+Let
 \begin{itemize}
@@
 We note that in practice $L$ is independent of $N$ and is likely to be
-$O(1)$  (e.g. about 12 scans in a year for disease prognosis).
-Likewise $M$ is also $O(1)$. The speed of the iterative optimization is dependent on the number of imaging views, and is profoundly impacted by the actual numerical optimization technique used.  
+$O(1)$ (e.g., about 12 scans in a year for disease prognosis).
+Likewise $M$ is also $O(1)$. The speed of the iterative optimization
+is dependent on the number of imaging views, and is profoundly
+impacted by the actual numerical optimization technique used.
 Therefore, the time computational complexity of our method is sum of
@@
 \begin{enumerate}
-\item $O(NL^2+L^3)$ for creating eigenspace, which is, in practice linear, i.e., $O(N)$
-\item $O(NLM)$ for deriving weights map, which is, in practice linear, i.e., $O(N)$
+\item $O(NL^2+L^3)$ for creating eigenspaces, which is, in practice linear, i.e., $O(N)$.
+\item $O(NLM)$ for deriving weights map, which is, in practice linear, i.e., $O(N)$.
 \item and the time $F$  taken for iterative minimization, which as mentioned above is not the key contribution of this paper. 
 \end{enumerate}
-In short, the additional burden of the key idea of this paper
-viz. generating weights map is linear in the number of voxels,
-although admittedly the burden $F$ of the alternate minimization procedure drives up
-the cost.
-
-In terms of space, the complexity is $O(NL +N)$ to store each of the $L$ templates and their low quality reconstructions, and to store one weights map.
-We only need to store a single weights map volume regardless of the number of templates available.
-
+In short, the additional burden of the key idea of this paper viz.,
+generating weights map is linear in the number of voxels, although
+admittedly the burden $F$ of the alternate minimization procedure
+drives up the cost (as can be seen in Table~\ref{table:compute_time}).
+
+In terms of space, the complexity is $O(NL +N)$ to store each of the
+$L$ templates and their low quality reconstructions, and to store one
+weights map. We only need to store a single weights map volume
+regardless of the number of templates available.
+
+\subsubsection{Example Case}
+If the set of projection views for every test is fixed a priori, a
+reasonable assumption, the set of low quality reconstructions can be
+produced offline and stored in order to save computational costs. 
+% Most of the computation time in our technique is used for the
+% generation of low quality eigen-space by reconstructing each of the
+% templates using TV and FDK. 
+With this as the basis, Table~\ref{table:compute_time} shows the
+computation times for various stages of reconstruction of a 2D slice
+of Liver on MATLAB 2019a on an AMD
+2920X 12-Core Processor machine with 64GB RAM. 
+% If however, new sets of
+% projection views for every test are to be allowed, the low quality
+% reconstructions can still be performed efficiently using
+% parallelization since these reconstructions are completely
+% independent. 
 \begin{table}[!h]
  \centering
-  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver (refer code in~\cite{codeRepo}) on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM.
-Here we assume that low quality eigen-spaces of the templates are computed offline.}
+  \caption{Computation times (in seconds) for various stages of
+    reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD
+    2920X 12-Core Processor machine with 64GB RAM. Our code is
+    available for inspection~\cite{codeRepo}.}
 \begin{tabular}{|l|l|l|l|}

### 2021-10-07 paper/changes.tex
Reorganized the section on computational complexity.  Also removed (latex commented) the irrelevant part of pre-computation and parallelization since the comment has already been made earlier (now appears as a footnote).
Added the note about the code base in changes.pdf also
Added RMSE eq.
Also edited discussion on deep learning.
Edited DART related response, and RMSE-SSIM related response in changes.pdf.

--- 2021-10-02 paper/changes.tex
@@
 \usepackage{graphicx}
-\bibliographystyle{IEEEtran}
 \usepackage{caption}
@@
 \usepackage{a4wide}
-\usepackage{subcaption}
+\usepackage{subcaption,comment}
 \usepackage[colorlinks=true]{hyperref}
@@
  with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
- Algebraic Reconstruction Technique (SART)~\cite{sart}. We do not reconstruct
- using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
- is no prior information about the number of possible attentuation
- coefficients in the test object.
-%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
+ Algebraic Reconstruction Technique (SART)~\cite{sart}.
+In order to use the Discrete Algebraic Reconstruction Technique (DART)~\cite{dart}, one must assume the imaged object to be made of only a few fixed number of known attenuation coefficients.
+Since we do not make any such assumption about  our datasets, we have not used DART.
+%% IS THERE A NEED TO HIGHGLIHT what we have not done?
+Also give references?
  Among other iterative techniques, we
@@
 
+  We have now presented RMSE values for all reconstructions in Tables 1-5 of the main paper.
+Since RMSE corresponds to error in intensity values, we have used SSIM with a higher weightage to structure for the purpose of measuring error in preservation of structures in our reconstructions.
+  \begin{comment}
   The reason for not reporting RMSE stems from the optimization
@@
   %% Why not combine all of the values in one table?
-
-\begin{table}[!h]
-  \centering
- \caption{RMSE of reconstructions from various
-    methods within the RoI.}
-\begin{tabular}{|l|c|c|c|c|c|}
-\hline 
-&\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
-\\ \hline \textbf{Potato}& 0.29 & 0.24 & \textcolor{red}{0.18}
-\\ \hline \textbf{Sprouts}& 0.53 & 0.48 & \textcolor{red}{0.30}
-\\ \hline \textbf{Liver}& 0.05 & 0.17 & \textcolor{red}{0.03}
-\\ \hline
-\end{tabular}
-\label{table:rmse}
-\end{table}
+\end{comment}
 
@@
 
-  We now present details of both time and space complexities of our technique in Section.~7B of our paper.
+We accept this point, and present details in Section.~7B of our paper.
+We also provide the code to reproduce the compute time claimed.
 

### 2021-10-07 paper/post_tci.tex
Added RMSE eq.
Also edited discussion on deep learning.
Edited DART related response, and RMSE-SSIM related response in changes.pdf.

@@
 present reconstruction results on all datasets. For quantitative
-evaluation, we compute the Structural Similarity Index Metric
-(SSIM)~\cite{ssim}. Here, we assign higher importance to the
-preservation of structure in a reconstruction by assigning the
-following weights to structure, contrast and intensity respectively:
-$0.7,0.2,0.1$. The reason for emphasizing the structure with an
-exponent of 0.7 stems from the optimization process since the
-intensity span (and, in general, the histogram) of reconstructed volumes
-differ across various methods and solvers.
+evaluation, we use two metrics: the Root Mean Squared Error (RMSE) and the
+Structural Similarity Index Metric (SSIM)~\cite{ssim}. If
+$\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
+$\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
+computed as follows
+
+\begin{equation}
+  \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
+    \hat{\boldsymbol{x}}(i))^2}.
+ \end{equation}
+
+Since RMSE corresponds to error in intensity values, we have used SSIM
+with a higher weightage to structure for the purpose of measuring
+error in preservation of structures in our reconstructions. Hence, while
+computing SSIM, we assign the following weights to structure, contrast
+and intensity respectively: $0.7,0.2,0.1$.
+%The reason for emphasizing the structure with an
+%exponent of 0.7 stems from the optimization process since the
+%intensity span (and, in general, the histogram) of reconstructed volumes
+%differ across various methods and solvers.
 
@@
   \centering
-  \caption{The SSIM (RMSE) of reconstructed okra from various
+  \caption{The SSIM (RMSE) within the RoI of reconstructed okra from various
     methods. SSIM of the ideal reconstruction is 1.}
@@
 \textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
-& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ \hline \textbf{3D, 30 views} & 0.69 (0.21) & 0.74 (0.30) & \textcolor{red}{0.78 (0.26)}\\
-\hline \textbf{3D, 45 views} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
+& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ 
+\hline \textbf{3D} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
 \\ \hline
@@
   Further, a specific `event-of-interest' may occur just once in a
-  longitudinal study and hence training on data of all previous time
-  instants may be misleading. If however, we use measurements from
+  longitudinal study and hence training on data from all previous time
+  instants of the same specimen may be misleading. As a future work, measurements from
   identical and full-cycle longitudinal studies, including
-  events-of-interest, of similar specimen (instead of the `same'
-  specimen as we used), a deep-learning technique may be applied. We
-  see this as an extension of using object-prior generated from the
-  same object.
+  events-of-interest, from an \textit{atlas of similar specimen} can be used to train
+  a deep learning model.  We  see this as an extension of using object-prior generated from the
+  \textit{same specimen}.
 
@@
 using information from previous scans of the same object, as outlined in
-Fig.~\ref{fig:prior_overview}. In order to observe details of new changes
+Figs.~\ref{fig:story} and~\ref{fig:prior_overview}. In order to observe details of new changes
 accurately, we use a novel

### 2021-10-07 paper/post_tci.tex
Minor edits

@@
 that our method reconstructs new structures while simultaneously
-reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM of
+reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM and RMSE of
 the reconstructed new regions using various methods.
@@
 deformity and better removal of sub-sampling artefacts when compared
-to FDK and TV. This is also seen in the SSIM values in
+to FDK and TV. This is also seen in the SSIM and RMSE values in
 Table~\ref{table:okra_ssim}.
@@
 slice from its measurements from only 30 views. The reconstructions are quantitatively compared using
-SSIM in Table~\ref{table:tmh_ssim}.
+SSIM and RMSE in Table~\ref{table:tmh_ssim}.
 
@@
 the slices is shown in Fig.~\ref{fig:sprouts_2D_results}.
-Table~\ref{table:sprouts_ssim} shows the improvement in SSIM of the
+Table~\ref{table:sprouts_ssim} shows the improvement in SSIM and RMSE of the
 reconstructed new regions as compared to other methods.

### 2021-10-07 paper/post_tci.tex
commented out the equation for RMSE, and changed the language a tad in the results section.

@@
 types of eigenspaces for the computation of weights map, and then
-present reconstruction results on all datasets. For quantitative
-evaluation, we use two metrics: the Root Mean Squared Error (RMSE) and the
-Structural Similarity Index Metric (SSIM)~\cite{ssim}. If
-$\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
-$\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
-computed as follows
-
-\begin{equation}
-  \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
-    \hat{\boldsymbol{x}}(i))^2}.
- \end{equation}
-
-Since RMSE corresponds to error in intensity values, we have used SSIM
-with a higher weightage to structure for the purpose of measuring
-error in preservation of structures in our reconstructions. Hence, while
-computing SSIM, we assign the following weights to structure, contrast
-and intensity respectively: $0.7,0.2,0.1$.
+present reconstruction results on all datasets. We show both
+qualitative and quantitative results. For the latter,
+we use two metrics: the Root Mean Squared Error (RMSE) and the
+Structural Similarity Index Metric (SSIM)~\cite{ssim}. 
+% If
+% $\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
+% $\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
+% computed as follows
+
+% \begin{equation}
+%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
+%     \hat{\boldsymbol{x}}(i))^2}.
+%  \end{equation}
+While RMSE corresponds to error in intensity values and is a measure
+of absolute error, SSIM seeks to consider perceptual changes, as well
+as correlation between adjacent pixels. This can be useful in a
+clinical context.  We therefore assign a higher weightage to structure
+preservation, that is we assign the
+following weights to structure, contrast, and intensity respectively:
+$0.7,0.2,0.1$.
+
+It can be verified that in all cases, our results are favourable for the
+various datasets considered.
 %The reason for emphasizing the structure with an

### 2021-10-07 paper/post_tci.tex
fixed typo in computational complexity section

@@
 
-\subsubsection{Example Case}
+\subsubsection{Example Computation}
 If the set of projection views for every test is fixed a priori, a

### 2021-10-07 paper/changes.tex
minor change in the language regarding SSIM.

@@
 
- \begin{itemize}
+ \begin{enumerate}
  \item    \textcolor{blue}{...the paper should at least include a (short) discussion about the
@@
 
-  We have now presented RMSE values for all reconstructions in Tables 1-5 of the main paper.
-Since RMSE corresponds to error in intensity values, we have used SSIM with a higher weightage to structure for the purpose of measuring error in preservation of structures in our reconstructions.
+We accept the criticism, and have now presented both RMSE and SSIM
+values for all reconstructions in Tables 1-5 of the main paper. 
   \begin{comment}
+Since
+RMSE corresponds to error in intensity values, we have used SSIM with
+a higher weightage to structure for the purpose of measuring error in
+preservation of structures in our reconstructions.
+
   The reason for not reporting RMSE stems from the optimization
@@
 
-  \end{itemize}
+\end{enumerate}
 

### 2021-10-09 ARadon.m
Included copyright notice

@@ -1,6 +1,11 @@
 
 function b = ARadon(X_data,idx,dim,numAngles)
 
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
 startPt = 1;
 endPt = dim(1)*dim(2);
 X = X_data(startPt:endPt);

### 2021-10-09 ARadon_wavelet.m

@@ -1,24 +1,0 @@
-
-function b = ARadon_wavelet(X_data,idx,dim,numAngles,wname,size_CA)
-
-startPt = 1;
-endPt = dim(1)*dim(2);
-X = X_data(startPt:endPt);
-X = reshape(X,[dim(1) dim(2)]);
-CA_recovered = X(1:size_CA(1),1:size_CA(2));
-CH_recovered = X(1:size_CA(1),size_CA(2)+1:end);
-CV_recovered = X(size_CA(1)+1:end,1:size_CA(2));
-CD_recovered = X(size_CA(1)+1:end,size_CA(2)+1:end);
-X = idwt2(CA_recovered,CH_recovered,CV_recovered,CD_recovered,wname);
-
-X = imresize(X,[dim(1) dim(2)]);
-startPt = 1;
-endPt = numAngles;
-angles = idx(startPt:endPt);
-
-radProj = radon(X,angles);  
-
-b1 = reshape(radProj,[size(radProj,1)*size(radProj,2) 1]);
-
-b = b1;
-

### 2021-10-09 AtRadon.m

@@ -1,5 +1,11 @@
 function X_final = AtRadon(b_data,idx,dim,numAngles)
     
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
 s = size(b_data,1);
 
 startPt = 1;

### 2021-10-09 AtRadon_wavelet.m

@@ -1,33 +1,0 @@
-function X_final = AtRadon_wavelet(b_data,idx,dim,numAngles,wname)
-    
-s = size(b_data,1);
-
-startPt = 1;
-endPt = s;
-b = b_data(startPt:endPt);
-b = reshape(b,[(size(b,1))/numAngles numAngles]);
-
-startPt = 1;
-endPt = numAngles;
-angles = idx(startPt:endPt);    
-
-backProjImg  =  iradon(b,angles,'linear','Cosine');
-
-backProjImg = backProjImg(2:2+dim(1)-1,2:2+dim(2)-1);
-[CA,CH,CV,CD] = dwt2(backProjImg,wname);
-CA = imresize(CA,[dim(1)/2 dim(2)/2]);
-CH = imresize(CH,[dim(1)/2 dim(2)/2]);
-CV = imresize(CV,[dim(1)/2 dim(2)/2]);
-CD = imresize(CD,[dim(1)/2 dim(2)/2]);
-X = [CA CH;CV CD];
-
-X = reshape(X,[size(backProjImg,1)*size(backProjImg,2) 1]);       
-
-
-X_final = X;
-
-
-
-
-
-

### 2021-10-09 computeSSIM_relMSE.m

@@ -1,568 +1,0 @@
-clc;
-clear all; close all;
-dataset = 'sprouts'
-
-if strcmp(dataset,'tmh_7')
-    
-    outDirectory = 'results/tmh_7/30_views/';
-    fileName = sprintf('%s/testIm.mat',outDirectory);
-    data = load(fileName);
-    testIm = data.testIm;
-    
-    roi_row = 135:135+140;
-    roi_col = 275:275+155;
-    testIm_roi = testIm(roi_col,roi_row);
-    testIm_roi =  testIm_roi - min(testIm_roi(:));
-    testIm_roi =  testIm_roi./max(testIm_roi(:));
-    
-    
-    testIm_zoomed = testIm(275:275+155,135:135+140);    
-    testIm_zoomed  = testIm_zoomed  - min(testIm_zoomed (:));
-    testIm_zoomed = testIm_zoomed ./max(testIm_zoomed (:));
-    name = sprintf('%s/test_zoomed.png',outDirectory);
-    imwrite(testIm_zoomed,name);
-%     figure;imshow(testIm_roi,[]);
-%     fh = figure;imshow(testIm,[]);
-%     impixelinfo;
-%     hold on;
-%     rectangle('Position',[135, 275, 140, 155],'EdgeColor','g','LineWidth',3);
-%     name = sprintf('%s/testIm_roi.png',outDirectory);
-%     f=getframe; imwrite(f.cdata,name);
-
-    fileName = sprintf('%s/fbp.mat',outDirectory);
-    data = load(fileName);
-    fbp = data.result_fbp;
-    fbp_roi = fbp(roi_col,roi_row);
-    fbp_roi =  fbp_roi - min(fbp_roi(:));
-    fbp_roi =  fbp_roi./max(fbp_roi(:));
-    
-    fbp_zoomed = fbp(275:275+155,135:135+140);       
-    fbp_zoomed  = fbp_zoomed  - min(fbp_zoomed (:));
-    fbp_zoomed = fbp_zoomed ./max(fbp_zoomed (:));
-    name = sprintf('%s/fbp_zoomed.png',outDirectory);
-    imwrite(fbp_zoomed,name);
-    
-    relMSE_FBP =  mean2((fbp_roi - testIm_roi).^2)/mean2(testIm_roi.^2);
-    ssimVal_FBP = ssim(fbp_roi,testIm_roi,'Exponents',[0.1,0.2,0.7]);
-    
[…]

### 2021-10-09 driver.m

@@ -1,5 +1,14 @@
 function driver(dataset)
 %%
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+%  This is the main file. Run this with the arguement 'tmh_7' for
+%  reconstructing 2D Liver.
+
+
 if strcmp(dataset,'potato')
     
     angleSet =  [12]    ;

### 2021-10-09 filteredBackProjection2D.m

@@ -1,5 +1,10 @@
 function fbp = filteredBackProjection2D(y,numAngles,idx1,dim)
 
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
 proj = reshape(y,[size(y,1)/numAngles numAngles]);
 fbp = iradon(proj,idx1,'linear','Cosine');
 fbp = fbp(2:2+dim(1)-1,2:2+dim(2)-1);

### 2021-10-09 genEigenSpace2Dtmh.m

@@ -1,8 +1,15 @@
-% close all;
-% clear all;
-% clc;
+
 
 function [eigenVecs,meanTemplate] = genEigenSpace2Dtmh(templateNos,sliceNum,dataFileName,numSlices,sizeOfSlice,outDirectory)
+
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+% This function computes high quality eigen-space from the prior-images
+% of the liver.
 
 numTemplates = length(templateNos);
 volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
@@ -70,7 +77,6 @@ meanTemplate = sumI./numTemplates;
 
 
 % Compute the Covariance Matrix--------------------------------------------------------------------
-% Refer to Prof. Ajit's notes on face recognition using PCA
 
 templates = templates -repmat(meanTemplate,1,numTemplates);
 L = templates'*templates;

### 2021-10-09 generateMeasurements.m

@@ -1,6 +1,13 @@
 function [y,idx1,dim] = generateMeasurements(testIm,numAngles,outDirectory)
 
-%figure;imshow(testIm,[]);
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+
+% This function generates Radon measurements of the 2D test object for
+% a fixed set of views.
 
 fname = sprintf('%s/testIm.mat',outDirectory);
 save(fname,'testIm');

### 2021-10-09 normc_fcn.m

@@ -1,3 +1,9 @@
 function nm = normc_fcn(m)
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
 nm = sqrt(m.^2 ./ sum(m.^2)) .* sign(m);
 end

### 2021-10-09 performPilotReconstruction.m

@@ -1,5 +1,13 @@
 function performPilotReconstruction(y,idx1,dim,pilotReconMethods,lambda_for_pilot_recon,outDirectory)
 
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+
+% This function computes FBP and TV reconstructions of the 2D data.
+
 numAngles = length(idx1)
 m = size(y,1);
 A_both_functions =@(z,mode) systemFunction(z,mode,idx1,dim,numAngles,m);

### 2021-10-09 performWeightedPriorReconstruction.m

@@ -1,5 +1,12 @@
 function performWeightedPriorReconstruction(dataset,y,idx1,dim,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior_list,kk,sliceNum,outDirectory)
 
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+
 pilotRecons = cell([2,dim]);
 for iter = 1:length(pilotReconMethods)
     method = pilotReconMethods(iter);

### 2021-10-09 plain_TV.m

@@ -1,5 +1,9 @@
 function result_plain_TV = plain_TV(y,dim,lambdaTV,A_both_functions)
 
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
     
 addpath('TVReg-master/');
 

### 2021-10-09 projectPilot_on_EigenSpace_2D.m

@@ -1,5 +1,11 @@
 function P_pilot = projectPilot_on_EigenSpace_2D(dataset,idx1,pilotOfTestIm,lambda,A_both_functions,method,sliceNo,outDirectory)
 
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
 dim = size(pilotOfTestIm);
 
 if strcmp(dataset,'potato')
@@ -16,7 +22,6 @@ if strcmp(dataset,'potato')
        resizedVol = fdkVol;%imresize(fdkVol(10:end-13,10:end-13,:),0.5);
        volumes(:,:,:,i) = resizedVol;
     end
-%     sliceNo = 30;
 end
 if strcmp(dataset,'okra')
     templateNos = [4,5,6,7];
@@ -31,8 +36,6 @@ if strcmp(dataset,'okra')
        fdkVol = fileData.FDK;
        volumes(:,:,:,i) = fdkVol(15:end-14,15:end-14,:);
     end
-%     sliceNo = 30;
-
 end
 
 if strcmp(dataset,'sprouts')
@@ -48,8 +51,6 @@ if strcmp(dataset,'sprouts')
        fdkVol = fileData.volume;
        volumes(:,:,:,i) = fdkVol(10:end-4,2:end-2,:);
     end
-%     sliceNo = 30;
-
 end
 
 if strcmp(dataset,'tmh_7')
@@ -59,8 +60,7 @@ if strcmp(dataset,'tmh_7')
     numSlices = 43;%161;
     sizeOfSlice = [512 512];
     volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
-%     sliceNum = 27;
-%     sliceNo = sliceNum;
+
     
     for k= 1:numTemplates
         testNo = templateNos(k);
@@ -83,8 +83,7 @@ if strcmp(dataset,'tmh_8')
     numSlices = 43;%161;
     sizeOfSlice = [512 512];
     volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
-%     sliceNum = 27;
-%     sliceNo = sliceNum;
+
     
     for k= 1:numTemplates
         testNo = templateNos(k);
[…]

### 2021-10-09 systemFunction.m

@@ -1,0 +1,53 @@
+function output = systemFunction(z,mode,idx,dim,numAngles,m)
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+if mode==0
+    n = dim(1)*dim(2);
+    output = [m n];
+    
+elseif mode==1
+    
+    X_data = z;
+    startPt = 1;
+    endPt = dim(1)*dim(2);
+    X = X_data(startPt:endPt);
+    X = reshape(X,[dim(1) dim(2)]);
+
+    startPt = 1;
+    endPt = numAngles;
+    angles = idx(startPt:endPt);
+
+    radProj = radon(X,angles);  
+
+    b1 = reshape(radProj,[size(radProj,1)*size(radProj,2) 1]);
+
+    b = b1;
+    output = b;
+    
+elseif mode==2
+    
+    b_data = z;
+    s = size(b_data,1);
+
+    startPt = 1;
+    endPt = s;
+    b = b_data(startPt:endPt);
+    b = reshape(b,[(size(b,1))/numAngles numAngles]);
+
+    startPt = 1;
+    endPt = numAngles;
+    angles = idx(startPt:endPt);    
+
+    backProjImg  =  iradon(b,angles,'linear','Cosine');
+
+    backProjImg = backProjImg(2:2+dim(1)-1,2:2+dim(2)-1);
+    X = reshape(backProjImg,[size(backProjImg,1)*size(backProjImg,2) 1]);       
+
+
+    X_final = X;
+    output = X_final;
+end

### 2021-10-09 systemFunction_prior.m

@@ -1,0 +1,63 @@
+function output = systemFunction_prior(z,mode,idx,dim,numAngles,m,lambda_prior,W)
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+if mode==0
+    n = dim(1)*dim(2);
+    output = [m n];
+    
+elseif mode==1  %forward system matrix operator
+    
+    X_data = z;
+    startPt = 1;
+    endPt = dim(1)*dim(2);
+    X = X_data(startPt:endPt);
+    X = reshape(X,[dim(1) dim(2)]);
+
+    startPt = 1;
+    endPt = numAngles;
+    angles = idx(startPt:endPt);
+
+    radProj = radon(X,angles);  
+
+    b1 = reshape(radProj,[size(radProj,1)*size(radProj,2) 1]);
+    vectX =  lambda_prior.*reshape(X,[dim(1)*dim(2) 1]).*W(:); 
+    b = cat(1,b1,vectX);
+
+    output = b;
+    
+elseif mode==2
+    
+    b_data = z;
+    s1 = size(b_data,1)-(dim(1)*dim(2)); %m
+    s2 = size(b_data,1);  %(m+n)
+
+    startPt = 1;
+    endPt =  s1;
+    b = b_data(startPt:endPt);
+    b = reshape(b,[(size(b,1))/numAngles numAngles]);
+
+    startPt = endPt + 1;
+    endPt = s2;
+    Y2 = b_data(startPt:endPt);
+
+    startPt = 1;
+    endPt = numAngles;
+    angles = idx(startPt:endPt);    
+
+    backProjImg  =  iradon(b,angles,'linear','Cosine');
+
+    backProjImg = backProjImg(2:2+dim(1)-1,2:2+dim(2)-1);
+    X = reshape(backProjImg,[size(backProjImg,1)*size(backProjImg,2) 1]);       
+
+    %-------------- Modification for the PICCS part -starts------------------
+    X = X + (lambda_prior).*Y2.*W(:);
+
+    %-------------- Modification for the PICCS part -ends------------------
+
+    X_final = X;
+    output = X_final;
+end

### 2021-10-09 weighted_prior.m

@@ -1,0 +1,147 @@
+function [result_weighted_prior,W] =  weighted_prior(dataset,y_given,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,idx1,numCycles,...
+                                 pilotRecons,sliceNum,outDirectory,kk)
+                             
+
+% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+
+% Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
+% This function computes the weighted prior reconstruction by first
+% estimating the weights-map W and then computing the reconstruction by
+% alternate minimization (of Eq.4 in the paper).
+
+
+if strcmp(dataset,'tmh_7')
+    templateNos = [10,11,12,13,14,15];
+    dataFileName = 'RFA2 - Anon/Rfa/RFA 1.5 B30s -';
+    numSlices = 43;%161;
+    sizeOfSlice = [512 512];
+%     sliceNum = 27;
+    
+    [eigenVecs,meanTemplateOriginal] = genEigenSpace2Dtmh(templateNos,sliceNum,dataFileName,numSlices,sizeOfSlice,outDirectory);
+
+    
+elseif strcmp(dataset,'tmh_8')
+    templateNos = [10,11,12,13,14,15,16]
+    dataFileName = 'RFA2 - Anon/Rfa/RFA 1.5 B30s -';
+    numSlices = 43;%161;
+    sizeOfSlice = [512 512];
+%     sliceNum = 27;
+
+    [eigenVecs,meanTemplateOriginal] = genEigenSpace2Dtmh(templateNos,sliceNum,dataFileName,numSlices,sizeOfSlice,outDirectory);
+else
+    fname = sprintf('EigenSpace_2D_%s.mat',dataset); 
+    es = load(fname);
+    eigenVecs = es.eigenVecs;
+    meanTemplateOriginal = es.meanTemplate;
+end
+numAngles = length(idx1);
+m = size(y_given,1);
+A_both_functions =@(z,mode) systemFunction(z,mode,idx1,dim,numAngles,m);    
+
+%%  --------------------------construct the weight map---------------------------------------
+
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)
[…]

### 2021-10-09 ARadon.m
minor edits in header information

@@ -1,7 +1,7 @@
 
 function b = ARadon(X_data,idx,dim,numAngles)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 AtRadon.m

@@ -1,7 +1,7 @@
 function X_final = AtRadon(b_data,idx,dim,numAngles)
     
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 driver.m

@@ -1,6 +1,6 @@
 function driver(dataset)
 %%
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 filteredBackProjection2D.m

@@ -1,9 +1,10 @@
 function fbp = filteredBackProjection2D(y,numAngles,idx1,dim)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+
 
 proj = reshape(y,[size(y,1)/numAngles numAngles]);
 fbp = iradon(proj,idx1,'linear','Cosine');

### 2021-10-09 genEigenSpace2Dtmh.m

@@ -3,7 +3,7 @@
 function [eigenVecs,meanTemplate] = genEigenSpace2Dtmh(templateNos,sliceNum,dataFileName,numSlices,sizeOfSlice,outDirectory)
 
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 generateMeasurements.m

@@ -1,6 +1,6 @@
 function [y,idx1,dim] = generateMeasurements(testIm,numAngles,outDirectory)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 normc_fcn.m

@@ -1,9 +1,9 @@
 function nm = normc_fcn(m)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
-% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade  
 
 nm = sqrt(m.^2 ./ sum(m.^2)) .* sign(m);
 end

### 2021-10-09 performPilotReconstruction.m

@@ -1,6 +1,6 @@
 function performPilotReconstruction(y,idx1,dim,pilotReconMethods,lambda_for_pilot_recon,outDirectory)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 performWeightedPriorReconstruction.m

@@ -1,7 +1,7 @@
 function performWeightedPriorReconstruction(dataset,y,idx1,dim,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior_list,kk,sliceNum,outDirectory)
 
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 plain_TV.m

@@ -1,9 +1,9 @@
 function result_plain_TV = plain_TV(y,dim,lambdaTV,A_both_functions)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
-% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade  
     
 addpath('TVReg-master/');
 

### 2021-10-09 projectPilot_on_EigenSpace_2D.m

@@ -1,7 +1,7 @@
 function P_pilot = projectPilot_on_EigenSpace_2D(dataset,idx1,pilotOfTestIm,lambda,A_both_functions,method,sliceNo,outDirectory)
 
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 systemFunction.m

@@ -1,9 +1,9 @@
 function output = systemFunction(z,mode,idx,dim,numAngles,m)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
-% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 
+% Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade  
 
 if mode==0
     n = dim(1)*dim(2);

### 2021-10-09 systemFunction_prior.m

@@ -1,6 +1,6 @@
 function output = systemFunction_prior(z,mode,idx,dim,numAngles,m,lambda_prior,W)
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-09 weighted_prior.m

@@ -2,7 +2,7 @@ function [result_weighted_prior,W] =  weighted_prior(dataset,y_given,pilotReconM
                                  pilotRecons,sliceNum,outDirectory,kk)
                              
 
-% This code is part of the following work which has been submitted to Transactions of Computational Imaging for peer review.
+% This code is part of the following work which has been submitted to IEEE Transactions on Computational Imaging for peer review.
 
 % Title: "Eliminating object prior-bias from sparse-projection tomographic reconstructions"
 % Authors: Preeti Gopal, Sharat Chandran, Imants Svalbe and Ajit Rajwade 

### 2021-10-11 paper/post_tci.tex
Changes suggested by Prof. Ajit in main paper

@@
         \includegraphics[width=\textwidth]{../images/potato/template_1.png}
-\captionsetup{labelformat=empty}       
+%\captionsetup{labelformat=empty}       
  \caption{}
@@
         \includegraphics[width=\textwidth]{../images/potato/template_2.png}
-\captionsetup{labelformat=empty}
+%\captionsetup{labelformat=empty}
         \caption{}
@@
         \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-\captionsetup{labelformat=empty}
+%\captionsetup{labelformat=empty}
         \caption{}
@@
         \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
-\captionsetup{labelformat=empty}
+%\captionsetup{labelformat=empty}
         \caption{}
@@
      \end{subfigure}
-      \caption{Dataset for illustrating the use of multiple eigenspaces: One slice each from the scanned objects (the first three from left) and a slice from the test volume (extreme right).
+      \caption{Dataset for illustrating the use of multiple eigenspaces.
+(a)-(c): One slice each from the scanned objects, and (d): a slice from the test volume.
 Notice the appearance of the fourth hole in the test slice.
@@
         constructed using different
-        reconstruction methods individually (a-g) are inadequate and
+        reconstruction methods individually (a)-(g) are inadequate and
         represent different false positives. By fusing information
@@
      \end{subfigure}
-      \caption{(a)-(f): Reconstructions of~\ref{fig:potato_data_2D}(d)
+      \caption{(a)-(g): Reconstructions of~\ref{fig:potato_data_2D}(d)
         from $6$ views. The magnitude and sharpness of the artefacts
@@
   \centering
-\caption{SSIM and RMSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ideal reconstruction is 1.}
+\caption{SSIM and RMSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(h).
+The SSIM of ideal reconstruction is 1.
+The ideal RMSE is 0, and the worst RMSE possible is 1 here.}
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
@@
 reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM and RMSE of
-the reconstructed new regions using various methods.
+the reconstructed new regions using various methods. The ground truth and reconstructions are normalized to lie in [0-1].
 \begin{comment}
@@
   \caption{The SSIM (RMSE) of reconstructed potato from various
-    methods. The SSIM of ideal reconstruction is 1.}
+    methods.
+The SSIM of ideal reconstruction is 1.
+The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+The 2D reconstructed images are shown in Fig.~\ref{fig:potato_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
 \begin{tabular}{|l|c|c|c|c|c|}
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.52 (0.36)
-& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
+\textbf{This paper} \\ \hline \textbf{2D, 6 views} & 0.52 (0.36)
+& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D, 18 views} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
 \\ \hline
@@
 to FDK and TV. This is also seen in the SSIM and RMSE values in
-Table~\ref{table:okra_ssim}.
+Table~\ref{table:okra_ssim}. The ground truth and reconstructions are normalized to lie in [0-1].
 
@@
   \caption{The SSIM (RMSE) within the RoI of reconstructed okra from various
-    methods. SSIM of the ideal reconstruction is 1.}
+    methods.
+SSIM of the ideal reconstruction is 1.
+The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+The 2D reconstructed images are shown in Fig.~\ref{fig:okra_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
 \begin{tabular}{|l|c|c|c|c|c|}
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
+\textbf{This paper} \\ \hline \textbf{2D, 48 views} & 0.46 (0.28)
 & 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ 
-\hline \textbf{3D} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
+\hline \textbf{3D, 45 views} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
 \\ \hline
@@
 shows reconstruction of the test
-slice from its measurements from only 30 views. The reconstructions are quantitatively compared using
+slice from its measurements from only 30 views. The ground truth and reconstructions are normalized to lie in [0-1] and are quantitatively compared using
 SSIM and RMSE in Table~\ref{table:tmh_ssim}.
@@
   \centering
-  \caption{The SSIM (RMSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ideal reconstruction, SSIM equals 1.}
+  \caption{The SSIM (RMSE) of 2D reconstruction of radio-frequency ablation data from various methods.
+Values have been computed within the RoI.
+For ideal reconstruction, SSIM equals 1.
+The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+The  reconstructed images are shown in Fig.~\ref{fig:tmh_2D_results},}
 \begin{tabular}{|l|c|c|c|c|}
@@
 Table~\ref{table:sprouts_ssim} shows the improvement in SSIM and RMSE of the
-reconstructed new regions as compared to other methods.
+reconstructed new regions as compared to other methods. The ground truth and reconstructions are normalized to lie in [0-1].
 %----------------------------------------------------
@@
   \caption{The SSIM (RMSE) of reconstructed sprouts from various
-    methods. The SSIM of ideal reconstruction) is 1.}
+    methods.
+The SSIM of ideal reconstruction) is 1.
+The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+The 2D reconstructed images are shown in Fig.~\ref{fig:sprouts_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
 \begin{tabular}{|l|c|c|c|c|c|}
@@
 \textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
- \\ \hline \textbf{2D} & 0.67 (0.24)
-& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
+ \\ \hline \textbf{2D, 20 views} & 0.67 (0.24)
+& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D, 30 views} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
 \\ \hline
@@
   what will be the intensity of the same voxel at the current time
-  instant?''}. This estimation can be learnt by a deep neural network
+  instant?''}. This estimation can be learned by a deep neural network
 if there are hundreds of labeled data.  However, generalization of
@@
   work is to replace the currently used fixed eigenspace provided by
-  PCA by a learnt feature basis provided by a network such as an
+  PCA by a learned feature basis provided by a network such as an
   autoencoder. For each dataset, an autoencoder may be trained to

### 2021-10-11 paper/post_tci.tex
Changes to the para immediately following Results where we talk about RMSE  (best and worst)

@@
 %  \end{equation}
-While RMSE corresponds to error in intensity values and is a measure
-of absolute error, SSIM seeks to consider perceptual changes, as well
-as correlation between adjacent pixels. This can be useful in a
-clinical context.  We therefore assign a higher weightage to structure
-preservation, that is we assign the
-following weights to structure, contrast, and intensity respectively:
-$0.7,0.2,0.1$.
-
-It can be verified that in all cases, our results are favourable for the
-various datasets considered.
+RMSE corresponds to error in intensity values and is a measure of
+absolute error. For purposes of normalization, while reporting numbers
+we rescale intensity values of both the ground truth and the
+reconstructed results to lie between 0 to 1, so that the best possible
+RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks
+to consider perceptual changes, as well as correlation between
+adjacent pixels. This can be useful in a clinical context.  Here, we
+therefore assign a higher weightage to structure preservation, that is
+we assign the following weights to structure, contrast, and intensity
+respectively: $0.7,0.2,0.1$.
+
+Our results are optimized for SSIM, but it can be verified that in all
+cases for the various datasets considered, our results are favourable
+with either metric.
 %The reason for emphasizing the structure with an
@@
         Spatially-Varying-prior method (from this paper) combines
-        weights-map information from all other methods. The SSIM of
+        weights-map information from all other methods. Quantitative
+        metrics for evaluation  of
         these reconstructions is shown in
@@
   \centering
-\caption{SSIM and RMSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(h).
-The SSIM of ideal reconstruction is 1.
-The ideal RMSE is 0, and the worst RMSE possible is 1 here.}
+\caption{SSIM and RMSE of the reconstructions shown in
+  Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(h). %The SSIM of
+                                %ideal reconstruction is 1. The ideal
+                                %RMSE is 0, and the worst RMSE
+                                %possible is 1 here.
+}
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
@@
   \centering
-  \caption{The SSIM (RMSE) of reconstructed potato from various
+  \caption{SSIM (RMSE) of reconstructed potato from various
     methods. 
-The SSIM of ideal reconstruction is 1.
-The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+%The SSIM of ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
 The 2D reconstructed images are shown in Fig.~\ref{fig:potato_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
@@
   \centering
-  \caption{The SSIM (RMSE) within the RoI of reconstructed okra from various
+  \caption{SSIM (RMSE) within the RoI of reconstructed okra from various
     methods. 
-SSIM of the ideal reconstruction is 1.
-The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+%SSIM of the ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
 The 2D reconstructed images are shown in Fig.~\ref{fig:okra_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
@@
   \centering
-  \caption{The SSIM (RMSE) of 2D reconstruction of radio-frequency ablation data from various methods.
-Values have been computed within the RoI.
-For ideal reconstruction, SSIM equals 1.
-The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+  \caption{SSIM (RMSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. 
+%For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
 The  reconstructed images are shown in Fig.~\ref{fig:tmh_2D_results},}
@@
   \centering
-  \caption{The SSIM (RMSE) of reconstructed sprouts from various
+  \caption{SSIM (RMSE) of reconstructed sprouts from various
     methods. 
-The SSIM of ideal reconstruction) is 1.
-The ideal RMSE is 0, and the worst RMSE possible is 1 here.
+%The SSIM of ideal reconstruction) is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
 The 2D reconstructed images are shown in Fig.~\ref{fig:sprouts_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}

### 2021-10-11 paper/post_tci.tex
Removed the part about RMSE bet 0 to 1 in each case.
Changes in Suppl. material and # views in the main paper

@@
 mechanism to mitigate them (unlike the method that we propose). This
-can be seen in our supplementary material~\cite{supp_paper},
+can be seen in Sec.~3 our supplementary material~\cite{supp_paper},
 where we have compared our method with~\cite{Lee2012}.
@@
 reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM and RMSE of
-the reconstructed new regions using various methods. The ground truth and reconstructions are normalized to lie in [0-1].
+the reconstructed new regions using various methods. 
+%The ground truth and reconstructions are normalized to lie in [0-1].
 \begin{comment}
@@
   \centering
-  \caption{SSIM (RMSE) of reconstructed potato from various
+  \caption{SSIM (RMSE) within the RoI of reconstructed potato from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D, 6 views} & 0.52 (0.36)
-& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D, 18 views} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.52 (0.36)
+& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
 \\ \hline
@@
 to FDK and TV. This is also seen in the SSIM and RMSE values in
-Table~\ref{table:okra_ssim}. The ground truth and reconstructions are normalized to lie in [0-1].
+Table~\ref{table:okra_ssim}. 
+%The ground truth and reconstructions are normalized to lie in [0-1].
 
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D, 48 views} & 0.46 (0.28)
+\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
 & 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ 
-\hline \textbf{3D, 45 views} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
+\hline \textbf{3D} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
 \\ \hline
@@
 \subsection{Reconstruction of datasets without imaging model}
-\subsubsection{\textbf{Liver:}}
+\subsubsection{\textbf{Liver}}
 \label{sec:tmh}
@@
 shows reconstruction of the test
-slice from its measurements from only 30 views. The ground truth and reconstructions are normalized to lie in [0-1] and are quantitatively compared using
+slice from its measurements from only 30 views. 
+The ground truth and reconstructions 
+%are normalized to lie in [0-1] and 
+are quantitatively compared using
 SSIM and RMSE in Table~\ref{table:tmh_ssim}.
@@
   \centering
-  \caption{SSIM (RMSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. 
+  \caption{SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
 %For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
@@
 Table~\ref{table:sprouts_ssim} shows the improvement in SSIM and RMSE of the
-reconstructed new regions as compared to other methods. The ground truth and reconstructions are normalized to lie in [0-1].
+reconstructed new regions as compared to other methods. 
+%The ground truth and reconstructions are normalized to lie in [0-1].
 %----------------------------------------------------
@@
   \centering
-  \caption{SSIM (RMSE) of reconstructed sprouts from various
+  \caption{SSIM (RMSE) within the RoI of reconstructed sprouts from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
- \\ \hline \textbf{2D, 20 views} & 0.67 (0.24)
-& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D, 30 views} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
+ \\ \hline \textbf{2D} & 0.67 (0.24)
+& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
 \\ \hline

### 2021-10-11 paper/post_tci_supplementary.tex
Changes in Suppl. material and # views in the main paper

@@
 \documentclass{article}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 \usepackage{amsmath}
@@
 \usepackage{subcaption}
+\usepackage{comment}
 
@@
 \maketitle
-%This supplementary material consists of details of the optimization routine used in our method, links to view our 3D reconstructions and results of 2D reconstructions for different projection views.
+This supplementary material consists of details which we did not include in the main paper for purposes of brevity.
+This document consists of links to view our complete 3D reconstructions, more details on why we use many eigenspaces, an alternate method to compute weights map and comparison with a method in literature.
+\tableofcontents
 
-\tableofcontents
-\newpage
-%------------------------------------------------------------------------------
-\section{An alternate method to compute weights-map}
-The value of $k$ (discussed in Sec.7 of the main paper) is typically dependent on the number of false positives the system can allow in exchange for the detection of more true positives (regions of new changes).
-It is this choice and not the particular type of dataset that affects the selection of $k$.
-In our work, the chosen $k$ corresponds to the one that gives minimal tolerance to false positives.\\
+%--------------------
+%--------------------------------Links to videos-------------------------------------------------
 
-However, in case one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using an alternate method described below.
-
-\begin{enumerate}
-\item For the purposes of training, treat one of the previously scanned images as test.
-\item Annotate the region of differences between the test and all of the previously scanned images based on domain knowledge.
-\item Compute the difference between the pilot reconstruction of the test and its projection onto the eigenspace. Let this spatial map be called `error map'.
-\item Train a Support Vector Machine (SVM) model to classify patches of this error-map image into one of the two categories: new changes present, new changes absent.
-\item Once the trained SVM model is obtained, it can be applied to generate binary weights-map for new test images in the same longitudinal study.
-\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, the prior and the pilot can be stitched by $\boldsymbol{R} = \boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
-Fig.~\ref{fig:okra_svm} shows results of this method on 2D okra dataset.
-
-  Alternatively, these binary weights can also be used in the below optimization, although this approach has not been pursued here.
-
-\begin{equation}
-%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
-%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
-J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W_b}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
-\label{Eq:main}
-\end{equation}
-
-\end{enumerate}
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
-
-        \caption{}
-     \end{subfigure}
-     \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
-
-        \caption{}
-     \end{subfigure}
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
-
-        \caption{}
-    \end{subfigure}    
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}
-
-        \caption{}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.31\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
-
-        \caption{}
-     \end{subfigure}
-   % \begin{subfigure}[b]{0.19\linewidth}
-   %     \includegraphics[width=\textwidth]{images/low_dose_prior/svm_method/prior.png}
-
-    %    \caption{}
-    % \end{subfigure}
-     \caption[Selecting $k$]{Using an alternate approach to generate (binary) weights map.
-(a)-(c) the images used as object-prior, (d) the test (310$\times$310).
-Measurements along $60$ views were taken.
-(e) error-map showing new regions, (f) detected binary weights map showing regions of new changes, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions.
-} %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates,
-\label{fig:okra_svm}
-\end{figure}
-\clearpage
-
-%--------------------------------Links to videos-------------------------------------------------
-\newpage
 \section{Links to view our 3D reconstructions}
-Reconstructions for the 3D datasets shown in Figs.~3,~4 and 6 in the main paper can be better visualized in the form of a video. Please refer to the following links to view the reconstruction results:
+Here we present the 3D reconstruction results discussed in Sec.~6 of the main paper.
+For each dataset, the links contain 2 videos: one showing all the templates and test volumes, and the other showing the reconstructed volumes by various methods.
+The videos are in .avi format and display reconstructions in a slice-by-slice manner.
 
 \begin{itemize}
-\item \textbf{Okra:} \\
+\item \textbf{Okra:}
 
-  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}\\
-\item \textbf{Potato:} \\
+  3D Okra of size $338\times 338\times 123$ was reconstructed from 45 cone-beam view measurements.
 
-  \url{https://www.dropbox.com/sh/w16j7pvud2lbrpx/AACCJLxgoAurT2vVKIdu-MwFa?dl=0}\\
-\item \textbf{Sprouts:}\\
+  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}
+\item \textbf{Potato:}
 
-  \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}\\
+    3D Potato of size $150\times 150\times 100$ was reconstructed from 18 cone-beam view measurements.
+
+  \url{https://www.dropbox.com/sh/w16j7pvud2lbrpx/AACCJLxgoAurT2vVKIdu-MwFa?dl=0}
+\item \textbf{Sprouts:}
+
+    3D Sprouts of size $130\times 130\times 130$ was reconstructed from 30 cone-beam view measurements.
+
+  \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}
 \end{itemize}
 
-\clearpage
-\newpage
-
-%----------------------------------Comparison with Literature------------------------
-\section{Detecting new changes directly in the measurements}
-
-Sec.2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature.
-Here we present a 2D reconstruction  result (of the test shown in Figure.~\ref{fig:comparisonLit_dataset}) to compare our method with~\cite{Lee2012}, in which the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
-This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
-However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image.
-This is shown in Figure~\ref{fig:comparisonLit_results}.
-A quantitative comparison over the region of interest is shown in Table~\ref{tab:comparisonLit}.
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
-%\captionsetup{labelformat=empty}
-        \caption{Template}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/potato/testIm_color.png}
-%\captionsetup{labelformat=empty}
-        \caption{Test}
-    \end{subfigure}
-    %\captionsetup{labelformat=empty}
-     \caption{Template and test from the Potato dataset for the reconstructions shown in Figure.~\ref{fig:comparisonLit_results}} 
-\label{fig:comparisonLit_dataset}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-\newpage
-
-\begin{figure}[!h]
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/result_new_changes.png}
-%\captionsetup{labelformat=empty}
-        \caption{~\cite{Lee2012}:new-changes}
-     \end{subfigure}
-\quad
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/result_literature_test.png}
-%\captionsetup{labelformat=empty}
-        \caption{~\cite{Lee2012}:Reconstruction}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/weightsIm_all_methods30.png}
-%\captionsetup{labelformat=empty}
-        \caption{Our weights-map}
-    \end{subfigure}
-   \quad
-        \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\textwidth]{../images/comparison_lit/weighted_pca_all_methods30.png}
-%\captionsetup{labelformat=empty}
-        \caption{Our Reconstruction}
-    \end{subfigure}
-    %\captionsetup{labelformat=empty}
-     \caption{Reconstruction of the test in Figure~\ref{fig:comparisonLit_dataset}.
-Reconstructions were performed from 12 views.
-Gaussian noise of 0 mean and SD = $1\%$ of mean of measurements, was added to the measurements.}
-\label{fig:comparisonLit_results}
-%\addtolength{\textfloatsep}{-0.8cm}
-\end{figure}
-
-\begin{table}[!h]
-  \centering
-      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}}
-  \begin{tabular}{|l|l|l|}
-\hline
- & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
-\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
-\textbf{\begin{tabular}[c]{@{}l@{}}Spatially-varying \\prior\end{tabular}} & 0.89 & 0.92 \\ \hline
-  \end{tabular}
-  \label{tab:comparisonLit}
-\end{table}
-\clearpage
-\newpage
-
-\section{Motivation for using multiple eigenspaces}
+%------------------------------------------------------
+\section{Motivation for using multiple eigenspaces in our method}
 
@@
 \end{boxedminipage}
+
+%\clearpage
+%----------------------------------------------------------
+\section{An alternate method to compute weights -map}
+The value of $k$ (discussed in Sec.~7 of the main paper) is typically dependent on the number of false positives the system can allow in exchange for the detection of more true positives (regions of new changes).
+It is this choice and not the particular type of dataset that affects the selection of $k$.
+In our work, the chosen $k$ corresponds to the one that gives minimal tolerance to false positives.
+However, in case one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using an alternate method described below.
+
+\begin{enumerate}
+\item For the purposes of training, treat one of the previously scanned images as test.
+Annotate the region of differences between the test and all of the previously scanned images based on domain knowledge.
+\item Compute the difference between the pilot reconstruction of the test and its projection onto the eigenspace. Let this spatial map be called `error map'.
+\item Train a Support Vector Machine (SVM) model to classify patches of this error-map image into one of the two categories: new changes present, new changes absent.
+\item Once the trained SVM model is obtained, it can be applied to generate binary weights-map for new test images in the same longitudinal study.
+\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, the prior and the pilot can be stitched by $\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
+Fig.~\ref{fig:okra_svm} shows results of this method on 2D okra dataset.
+
+  Alternatively, these binary weights can also be used in the alternate minimization optimization described in Eq.~4 of the main paper, although this approach has not been pursued here.
+
+  \begin{comment}
+\begin{equation}
+%   \setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
+%\setlength{\abovedisplayskip}{-2pt} \setlength{\abovedisplayshortskip}{-2pt}
+J_3(\boldsymbol{\theta},\boldsymbol{\alpha}) = \lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1\lVert\boldsymbol{\theta}\rVert_1 +\lambda_2\lVert\boldsymbol{W_b}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
+\label{Eq:main}
+\end{equation}
+\end{comment}
+\end{enumerate}
+
+\begin{figure}[]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
+        \caption{}
+     \end{subfigure}
+     \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
+        \caption{}
+     \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}
+
+        \caption{}
+    \end{subfigure}    
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
+        \caption{}
+     \end{subfigure}
+     \caption[Selecting $k$]{Using an alternate approach to generate (binary) weights map.
+(a)-(c) the images used as object-prior, (d) the test (310$\times$310).
+Measurements along $60$ views were taken.
+(e) error-map showing new regions, (f) detected binary weights map showing regions of new changes, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions.
+} %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates,
+\label{fig:okra_svm}
+\end{figure}
+\clearpage
+
+\newpage
+
+%----------------------------------Comparison with Literature------------------------
+\section{Empirical comparison with a method in literature:\\ Detecting new changes directly in the measurements}
+
+Sec.~2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature.
+Here we present a 2D reconstruction  result (of the test shown in Figure.~\ref{fig:comparisonLit_dataset}) to compare our method with~\cite{Lee2012}, in which the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template.
+This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
+However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image.
+This is shown in Figure~\ref{fig:comparisonLit_results}.
+A quantitative comparison over the region of interest is shown in Table~\ref{tab:comparisonLit}.
+\begin{figure}[!h]
+  \centering
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
+%\captionsetup{labelformat=empty}
+        \caption{Template}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/potato/testIm_color.png}
+%\captionsetup{labelformat=empty}
+        \caption{Test}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Template and test from the Potato dataset for the reconstructions shown in Figure.~\ref{fig:comparisonLit_results}} 
+\label{fig:comparisonLit_dataset}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\begin{figure}[!h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/result_new_changes.png}
+%\captionsetup{labelformat=empty}
+        \caption{~\cite{Lee2012}:new-changes}
+     \end{subfigure}
+\quad
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/result_literature_test.png}
+%\captionsetup{labelformat=empty}
+        \caption{~\cite{Lee2012}:Reconstruction}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/weightsIm_all_methods30.png}
+%\captionsetup{labelformat=empty}
+        \caption{Our weights-map}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/comparison_lit/weighted_pca_all_methods30.png}
+%\captionsetup{labelformat=empty}
+        \caption{Our reconstruction}
+    \end{subfigure}
+    %\captionsetup{labelformat=empty}
+     \caption{Reconstruction of the test in Figure~\ref{fig:comparisonLit_dataset}.
+Reconstructions were performed from 12 views.
+Gaussian noise of 0 mean and SD = $1\%$ of mean of measurements, was added to the measurements.}
+\label{fig:comparisonLit_results}
+%\addtolength{\textfloatsep}{-0.8cm}
+\end{figure}
+
+\begin{table}[!h]
+  \centering
+      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}.}
+  \begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
+\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
+\textbf{\begin{tabular}[c]{@{}l@{}}Weighted prior\\reconstruction\end{tabular}} & 0.89 & 0.92 \\ \hline
+  \end{tabular}
+  \label{tab:comparisonLit}
+\end{table}
+\clearpage
 \newpage

### 2021-10-12 paper/post_tci.tex
changed the section on tuning and corresponding changes to supplementary

@@
 mechanism to mitigate them (unlike the method that we propose). This
-can be seen in Sec.~3 our supplementary material~\cite{supp_paper},
+can be seen in Sec.~4 of our supplementary material~\cite{supp_paper},
 where we have compared our method with~\cite{Lee2012}.
@@
 
-$\lambda_1$, $\lambda_2$ are tunable weights given to the
+$\lambda_1$ and  $\lambda_2$ are tunable weights given to the
 TV-prior and object-prior terms respectively. The unknowns
@@
 \label{sec:discussion}
-In this section, we discuss tuning of parameters, computational complexity of our method, and requirements for applying deep learning techniques in longitudinal few-view reconstruction.
+In this section, we discuss tuning of parameters, computational
+complexity of our method, and requirements for applying deep learning
+techniques in longitudinal few-view reconstruction.
+
 \subsection{Tuning of parameters}
-$\lambda_1$, $\lambda_2$ and $k$ are the three
-hyper-parameters that need to be chosen carefully for optimal
-reconstruction. In our experiments, $\lambda_1$ was tuned to maximize
-SSIM of the whole reconstructed test volume for TV reconstruction of
-each dataset. This value was retained for spatially-varying
-prior-based reconstruction as well. The value of $\lambda_2$ largely
-depends on the amount of artefacts we aim to remove by using
-object-prior at the cost of their dominance in the new regions. This
-value was chosen to lie between $0-3$ for our datasets. Finally, the
-hyper-parameter $k$ defines the sensitivity of the weights map to the
-difference between test image and object-prior (projection of
-test onto the space of object-prior). When $k=0$, our method 
-behaves similar to the reconstruction using TV-only regularization. As $k$ increases, the weights map starts
-capturing new changes in the test, at the cost of detecting a few
-false positives i.e., false new changes. In other words, as the
-weights-map becomes more sensitive to the difference between the test
-and object-prior, it becomes more noisy. In order to visualize the
-effect of the hyper-parameter $k$, we performed 2D reconstructions on
-okra dataset for different values of
+$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
+need to be chosen carefully for optimal reconstruction. In our
+experiments, $\lambda_1$ was tuned in such a way as to maximize the
+SSIM of the complete reconstructed test volume using the TV-only
+regularizer.  In particular, the RoI was not considered.  Now, this
+value was retained for our spatially-varying prior-based
+reconstruction as well.  In principle, one could have jointly
+optimized both $\lambda_1$ and $\lambda_2$ to get even better results
+compared to the one we have in Section~\ref{results}.  The value of
+$\lambda_2$ largely depends on the amount of artefacts one aims to
+remove by using object-prior at the cost of their dominance in the new
+regions. This value was chosen to lie between $0-3$ for our datasets
+(having the fixed $\lambda_1$).
+
+The hyper-parameter $k$ defines the sensitivity of the weights map to
+the difference between test image and object-prior (projection of test
+onto the space of object-prior). When $k=0$, our method behaves
+similar to the reconstruction using TV-only regularization. As $k$
+increases, the weights map starts capturing new changes in the test,
+at the cost of detecting a few false positives i.e., false new
+changes. In other words, as the weights-map becomes more sensitive to
+the difference between the test and object-prior, it becomes more
+noisy. In order to visualize the effect of the hyper-parameter $k$, we
+performed 2D reconstructions on okra dataset for different values of
 $k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
@@
 final reconstructions. We run our experiments for a few values of $k$
-and choose the best reconstruction based on our tolerance for noise
-in the weights-map.
-When a large number of templates are available, this parameter can be
-chosen by assuming one of the templates as test and choosing the $k$
-that gave the best reconstruction. Alternatively, in cases where one
-wishes to completely avoid the use of this hyper-parameter, one can
-construct a binary weights-map using a learning based method described
-in the supplementary material~\cite{supp_paper}.
+and empirically choose the best reconstruction based on our tolerance
+for noise in the weights-map.  However, when a large number of
+templates are available, instead of this empirical method, this
+parameter can be chosen by assuming one of the templates as a
+pseudo-test and validating the $k$ that results in the best
+reconstruction (also see Sec~3 of \cite{supp_paper}.
+
+Alternatively, in cases where one wishes to completely avoid the use
+of this hyper-parameter, one can construct a binary weights-map using
+a learning based method described in the supplementary
+material~\cite{supp_paper}.
 

### 2021-10-12 paper/post_tci_supplementary.tex
changed the section on tuning and corresponding changes to supplementary

@@
 \begin{document}
+\date{}
 \maketitle
-This supplementary material consists of details which we did not include in the main paper for purposes of brevity.
-This document consists of links to view our complete 3D reconstructions, more details on why we use many eigenspaces, an alternate method to compute weights map and comparison with a method in literature.
+This supplementary material consists of details which we did not
+include in the main paper for purposes of brevity. This document
+consists of links to view our complete 3D reconstructions, an
+alternate simpler motivation for the use of multiple eigenspaces, and an
+alternate method to compute the parameters for the weights map. We
+also include a comparison with a method in literature based on
+comments from a reviewer.
+
 \tableofcontents
@@
 \section{Links to view our 3D reconstructions}
-Here we present the 3D reconstruction results discussed in Sec.~6 of the main paper.
-For each dataset, the links contain 2 videos: one showing all the templates and test volumes, and the other showing the reconstructed volumes by various methods.
-The videos are in .avi format and display reconstructions in a slice-by-slice manner.
+Here we present the 3D reconstruction results discussed in Sec.~6 of
+the main paper. For each dataset, the links contain 2 videos: one
+showing all the templates and test volumes, and the other showing the
+reconstructed volumes by various methods. The videos are in
+\verb+.avi+ format and display reconstructions in a slice-by-slice
+manner.
 
@@
 %------------------------------------------------------
-\section{Motivation for using multiple eigenspaces in our method}
+\section{Using multiple eigenspaces}
 
-Here we present a schematic explaining the advantage of using multiple eigenspaces within the
-proposed spatially-varying reconstruction technique.\\
+Here we present a schematic explaining the advantage of using multiple
+eigenspaces within the proposed spatially-varying reconstruction
+technique. This may be viewed as a simpler version of the somewhat
+long algorithm described in the main paper.
 
@@
 %----------------------------------------------------------
-\section{An alternate method to compute weights -map}
-The value of $k$ (discussed in Sec.~7 of the main paper) is typically dependent on the number of false positives the system can allow in exchange for the detection of more true positives (regions of new changes).
-It is this choice and not the particular type of dataset that affects the selection of $k$.
-In our work, the chosen $k$ corresponds to the one that gives minimal tolerance to false positives.
-However, in case one wishes to completely avoid the use of this hyper-parameter, one can construct a binary weights-map using an alternate method described below.
+\section{Learning-based computation of weights map}
+
+The value of $k$ (discussed in Sec.~7 of the main paper) is typically
+dependent on the number of false positives the system can allow in
+exchange for the detection of more true positives (regions of new
+changes). It is this choice and not the particular type of dataset
+that affects the selection of $k$. In our work, the chosen $k$
+corresponds to the one that gives minimal tolerance to false
+positives. However, in case one wishes to completely avoid the use of
+this hyper-parameter, one can construct a binary weights-map using a
+method described below.
 
 \begin{enumerate}
-\item For the purposes of training, treat one of the previously scanned images as test.
-Annotate the region of differences between the test and all of the previously scanned images based on domain knowledge.
-\item Compute the difference between the pilot reconstruction of the test and its projection onto the eigenspace. Let this spatial map be called `error map'.
-\item Train a Support Vector Machine (SVM) model to classify patches of this error-map image into one of the two categories: new changes present, new changes absent.
-\item Once the trained SVM model is obtained, it can be applied to generate binary weights-map for new test images in the same longitudinal study.
-\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, the prior and the pilot can be stitched by $\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
-Fig.~\ref{fig:okra_svm} shows results of this method on 2D okra dataset.
+\item For the purposes of training, treat one of the previously
+  scanned images as test. Annotate the region of differences between
+  the test and all of the previously scanned images based on domain
+  knowledge.
 
-  Alternatively, these binary weights can also be used in the alternate minimization optimization described in Eq.~4 of the main paper, although this approach has not been pursued here.
+\item Compute the difference between the pilot reconstruction of the
+  test and its projection onto the eigenspace. Let this spatial map be
+  called `error map'.
+
+\item Train a Support Vector Machine (SVM) model (or any other
+  classifier model) to classify patches of this error-map image into
+  one of the two categories: new changes present, new changes absent.
+
+\item Once the trained SVM model is obtained, apply the model and
+  generate binary weights-map for new test images in the same
+  longitudinal study.
+
+\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, use
+  these in the alternate minimization optimization described in Eq.~7
+  of the main paper.
+\end{enumerate}
+
+We mention in passing that if we are to entirely avoid the other
+parameters (viz. $\lambda_1$ and $\lambda_2$, the prior and the pilot
+can be stitched in a simplistic way using the equation 
+$\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
+The advantage of this method is that the computational time is
+signficantly reduced since the alternate minimization procedure is not
+used.
+
+%Fig.~\ref{fig:okra_svm} shows results of this method on 2D okra dataset.
 
@@
 \end{comment}
-\end{enumerate}
+%\end{enumerate}
 
@@
 \end{figure}
-\clearpage
-
-\newpage
+%\clearpage
+%\newpage
 
@@
 \textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
-\textbf{\begin{tabular}[c]{@{}l@{}}Weighted prior\\reconstruction\end{tabular}} & 0.89 & 0.92 \\ \hline
+\textbf{\begin{tabular}[c]{@{}l@{}}This paper\end{tabular}} & 0.89 & 0.92 \\ \hline
   \end{tabular}
@@
 \end{table}
-\clearpage
-\newpage
+%\clearpage
+%\newpage
 

### 2021-10-14 paper/post_tci.tex
Included text changes suggested by Prof.Svalbe

@@
  using a regularization prior when the number of projection views is
- limited (100 views).  We solve this cost function using an optimal
+ limited (for example reducing sampling to 100 views for the same resolution reconstructed image).  We solve this cost function using an optimal
  first-order method for large-scale TV regularization presented
@@
 
-  When the number of views is significantly reduced (this paper), a
+  When the number of views is reduced significantly further (as is discussed in this work), a
  regularization prior alone is not sufficient.  In such cases
@@
  set $S$ may potentially overwhelm the necessary details, and when
- several prior scans are available, finding the right one is an
+ several prior scans are available, finding the best one is an
  issue. We therefore devise an algorithm that estimates the location
  and magnitude of new changes in the (unknown) test. As we show in
- Section~\ref{sec:method_spatially_varying_prior}, this eventually
- prevents the prior from adversely affecting the reconstruction of new
+ Section~\ref{sec:method_spatially_varying_prior}, this prevents the prior from adversely affecting the reconstruction of new
  regions in the test. We refer to this method as a
@@
  using any of the prior scans \textit{as is}, or endeavoring to choose
- one ``right'' prior. In this way, this work is novel and contrasted
- with earlier work. As seen in Fig.~\ref{fig:story} (last column, 20
+ one ``right'' prior. In this way, this work is novel and compared to
+ earlier work. As seen in Fig.~\ref{fig:story} (last column, 20
  views) our method uses the set $S$ to yield a better reconstruction
@@
 the structure of the Okra is intricate as compared to Potato, and this
-brings with it a different challenge.
+brings with it a stronger challenge.
 
@@
 This work deals with the effective use of priors for tomographic
-reconstruction in longitudinal studies. When the number of measurements is
-substantially low, we discuss the utility of
+reconstruction in longitudinal studies. When the number of measurements 
+impedes the benefit of applying classic regularization methods, we discuss the utility of
 using information from previous scans of the same object, as outlined in
@@
 of these regions of change and
-assigning low prior weights wherever necessary. The probability of
+assigning low prior weights wherever necessary.
+This innovation becomes evident through the weights maps shown here in Figures~\ref{fig:weights_map_2Dpotato} and~\ref{fig:few_view_okra_2D_weights}.
+The probability of
 presence of a `new region' is enhanced considerably by a novel

### 2021-10-15 paper/changes.tex
Tuning of parameters is now placed in results section; comparision with literature is removed in supplementary material, cross-ref included while introducing lambda 1 and 2

@@
 
-    That said, the goal of our previous and curent work is to provide
+    \textit{That said, the goal of our previous and curent work is to provide
     a technique that can improve upon a chosen baseline reconstruction
@@
     there a way to improve?  The spatially-varying method of
-    moderating the prior settles this question.
+    moderating the prior settles this question.}
 

### 2021-10-15 paper/post_tci.tex
Tuning of parameters is now placed in results section; comparision with literature is removed in supplementary material, cross-ref included while introducing lambda 1 and 2

@@
 these artefacts will appear in the final reconstruction as there is no
-mechanism to mitigate them (unlike the method that we propose). This
-can be seen in Sec.~4 of our supplementary material~\cite{supp_paper},
-where we have compared our method with~\cite{Lee2012}.
+mechanism to mitigate them (unlike the method that we propose). %This
+%can be seen in Sec.~4 of our supplementary material~\cite{supp_paper},
+%where we have compared our method with~\cite{Lee2012}.
 
@@
 $\lambda_1$ and  $\lambda_2$ are tunable weights given to the
-TV-prior and object-prior terms respectively. The unknowns
+TV-prior and object-prior terms respectively. Their selection is discussed in
+Section.~\ref{sec:tuning_parameters}. The unknowns
 $\boldsymbol{x}$ and $\boldsymbol{\alpha}$ are solved by alternately
@@
 reconstructed results to lie between 0 to 1, so that the best possible
-RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks
-to consider perceptual changes, as well as correlation between
-adjacent pixels. This can be useful in a clinical context.  Here, we
-therefore assign a higher weightage to structure preservation, that is
-we assign the following weights to structure, contrast, and intensity
-respectively: $0.7,0.2,0.1$.
-
-Our results are optimized for SSIM, but it can be verified that in all
-cases for the various datasets considered, our results are favourable
-with either metric.
+RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks to
+consider perceptual changes, as well as correlation between adjacent
+pixels. This can be useful in a clinical context.  Here, we therefore
+assign a higher weightage to structure preservation, that is we assign
+the following weights to structure, contrast, and intensity
+respectively: $0.7,0.2,0.1$. Our results are optimized for SSIM, but
+it can be verified that in all cases for the various datasets
+considered, our results are favourable with either metric.
+
+Here below, we first discuss tuning of parameters followed by the
+rationale for using multiple eigenspaces to compute weightsmap. We
+then present reconstruction results for each of the datasets.
 %The reason for emphasizing the structure with an
@@
 %differ across various methods and solvers.
+
+\subsection{Tuning of parameters}
+\label{sec:tuning_parameters}
+$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
+need to be chosen carefully for optimal reconstruction. In our
+experiments, $\lambda_1$ was tuned in such a way as to maximize the
+SSIM of the complete reconstructed test volume using the TV-only
+regularizer.  In particular, the RoI was not considered.  Now, this
+value was retained for our spatially-varying prior-based
+reconstruction as well.  In principle, one could have jointly
+optimized both $\lambda_1$ and $\lambda_2$ to get even better results
+compared to the one we have in Sections~\ref{sec:results_with_imaging_model}, and~\ref{sec:results_without_imaging_model}.  The value of
+$\lambda_2$ largely depends on the amount of artefacts one aims to
+remove by using object-prior at the cost of their dominance in the new
+regions. This value was chosen to lie between $0-3$ for our datasets
+(having the fixed $\lambda_1$).
+
+The hyper-parameter $k$ defines the sensitivity of the weights map to
+the difference between test image and object-prior (projection of test
+onto the space of object-prior). When $k=0$, our method behaves
+similar to the reconstruction using TV-only regularization. As $k$
+increases, the weights map starts capturing new changes in the test,
+at the cost of detecting a few false positives i.e., false new
+changes. In other words, as the weights-map becomes more sensitive to
+the difference between the test and object-prior, it becomes more
+noisy. In order to visualize the effect of the hyper-parameter $k$, we
+performed 2D reconstructions on okra dataset for different values of
+$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
+obtained for each of the $k$ values and
+Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
+final reconstructions. We run our experiments for a few values of $k$
+and empirically choose the best reconstruction based on our tolerance
+for noise in the weights-map.  However, when a large number of
+templates are available, instead of this empirical method, this
+parameter can be chosen by assuming one of the templates as a
+pseudo-test and validating the $k$ that results in the best
+reconstruction (also see Sec~3 of \cite{supp_paper}.
+
+Alternatively, in cases where one wishes to completely avoid the use
+of this hyper-parameter, one can construct a binary weights-map using
+a learning based method described in the supplementary
+material~\cite{supp_paper}.
+
+%--------------effect of the value of $k$ on Okra dataset
+
+\begin{figure}[h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}
+        \caption{k=5}
+     \end{subfigure}     
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}
+        \caption{k=10}
+     \end{subfigure} 
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}
+        \caption{k=20}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}
+        \caption{k=30}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}
+        \caption{k=40}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}
+        \caption{k=50}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}
+        \caption{k=60}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}
+        \caption{k=70}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}
+        \caption{k=80}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}
+        \caption{k=90}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}
+        \caption{k=100}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}
+        \caption{k=130}
+     \end{subfigure}
+    \caption{Different weights-maps for okra reconstruction. Low intensity denotes regions of new changes in test.}
+\label{fig:few_view_okra_2D_weights}
+\end{figure}
+\begin{figure}[h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}
+        \caption{k=5,\\ SSIM = 0.79}
+     \end{subfigure}     
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}
+        \caption{k=10,\\ SSIM = 0.78}
+     \end{subfigure} 
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}
+        \caption{k=20,\\ SSIM = 0.76}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}
+        \caption{k=30,\\ SSIM = 0.74}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}
+        \caption{k=40,\\ SSIM = 0.72}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}
+        \caption{k=50,\\ SSIM = 0.63}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}
+        \caption{k=60,\\ SSIM = 0.61}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}
+        \caption{k=70,\\ SSIM = 0.59}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}
+        \caption{k=80,\\ SSIM = 0.58}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}
+        \caption{k=90,\\ SSIM = 0.56}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}
+        \caption{k=100,\\ SSIM = 0.55}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
+        \caption{k=130,\\ SSIM = 0.53}
+     \end{subfigure}
+    \caption{2D reconstructions for varying values of $k$.
+The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}
+\label{fig:reconstructions_as_k_varies}
+\end{figure}
 
@@
 \subsection{Reconstruction of datasets with imaging model available}
+\label{sec:results_with_imaging_model}
 \subsubsection{\textbf{Potato}}
@@
 \subsection{Reconstruction of datasets without imaging model}
+\label{sec:results_without_imaging_model}
 \subsubsection{\textbf{Liver}}
@@
 \label{sec:discussion}
-In this section, we discuss tuning of parameters, computational
-complexity of our method, and requirements for applying deep learning
+In this section, we discuss computational
+complexity of our method and requirements for applying deep learning
 techniques in longitudinal few-view reconstruction.
-
-\subsection{Tuning of parameters}
-$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
-need to be chosen carefully for optimal reconstruction. In our
-experiments, $\lambda_1$ was tuned in such a way as to maximize the
-SSIM of the complete reconstructed test volume using the TV-only
-regularizer.  In particular, the RoI was not considered.  Now, this
-value was retained for our spatially-varying prior-based
-reconstruction as well.  In principle, one could have jointly
-optimized both $\lambda_1$ and $\lambda_2$ to get even better results
-compared to the one we have in Section~\ref{results}.  The value of
-$\lambda_2$ largely depends on the amount of artefacts one aims to
-remove by using object-prior at the cost of their dominance in the new
-regions. This value was chosen to lie between $0-3$ for our datasets
-(having the fixed $\lambda_1$).
-
-The hyper-parameter $k$ defines the sensitivity of the weights map to
-the difference between test image and object-prior (projection of test
-onto the space of object-prior). When $k=0$, our method behaves
-similar to the reconstruction using TV-only regularization. As $k$
-increases, the weights map starts capturing new changes in the test,
-at the cost of detecting a few false positives i.e., false new
-changes. In other words, as the weights-map becomes more sensitive to
-the difference between the test and object-prior, it becomes more
-noisy. In order to visualize the effect of the hyper-parameter $k$, we
-performed 2D reconstructions on okra dataset for different values of
-$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
-obtained for each of the $k$ values and
-Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
-final reconstructions. We run our experiments for a few values of $k$
-and empirically choose the best reconstruction based on our tolerance
-for noise in the weights-map.  However, when a large number of
-templates are available, instead of this empirical method, this
-parameter can be chosen by assuming one of the templates as a
-pseudo-test and validating the $k$ that results in the best
-reconstruction (also see Sec~3 of \cite{supp_paper}.
-
-Alternatively, in cases where one wishes to completely avoid the use
-of this hyper-parameter, one can construct a binary weights-map using
-a learning based method described in the supplementary
-material~\cite{supp_paper}.
-
-%--------------effect of the value of $k$ on Okra dataset
-
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}
-        \caption{k=5}
-     \end{subfigure}     
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}
-        \caption{k=10}
-     \end{subfigure} 
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}
-        \caption{k=20}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}
-        \caption{k=30}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}
-        \caption{k=40}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}
-        \caption{k=50}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}
-        \caption{k=60}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}
-        \caption{k=70}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}
-        \caption{k=80}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}
-        \caption{k=90}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}
-        \caption{k=100}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}
-        \caption{k=130}
-     \end{subfigure}
-    \caption{Different weights-maps for okra reconstruction. Low intensity denotes regions of new changes in test.}
-\label{fig:few_view_okra_2D_weights}
-\end{figure}
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}
-        \caption{k=5,\\ SSIM = 0.79}
-     \end{subfigure}     
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}
-        \caption{k=10,\\ SSIM = 0.78}
-     \end{subfigure} 
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}
-        \caption{k=20,\\ SSIM = 0.76}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}
-        \caption{k=30,\\ SSIM = 0.74}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}
-        \caption{k=40,\\ SSIM = 0.72}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}
-        \caption{k=50,\\ SSIM = 0.63}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}
-        \caption{k=60,\\ SSIM = 0.61}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}
-        \caption{k=70,\\ SSIM = 0.59}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}
-        \caption{k=80,\\ SSIM = 0.58}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}
-        \caption{k=90,\\ SSIM = 0.56}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}
-        \caption{k=100,\\ SSIM = 0.55}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
-        \caption{k=130,\\ SSIM = 0.53}
-     \end{subfigure}
-    \caption{2D reconstructions for varying values of $k$.
-The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}
-\label{fig:reconstructions_as_k_varies}
-\end{figure}
 \subsection{Computational Complexity}

### 2021-10-15 paper/post_tci_supplementary.tex
Tuning of parameters is now placed in results section; comparision with literature is removed in supplementary material, cross-ref included while introducing lambda 1 and 2

@@
 \item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, use
-  these in the alternate minimization optimization described in Eq.~7
+  these in the alternate minimization optimization described in Eq.~3
   of the main paper.
@@
 We mention in passing that if we are to entirely avoid the other
-parameters (viz. $\lambda_1$ and $\lambda_2$, the prior and the pilot
+parameters (viz. $\lambda_1$ and $\lambda_2$), the prior and the pilot
 can be stitched in a simplistic way using the equation 
@@
 %\newpage
+
+\end{document}
 
@@
 %\newpage
-
 \bibliography{tci_ref}
-\end{document}

### 2021-10-15 paper/post_tci_supplementary.tex
Minor edits in suppl material intro

@@
 alternate simpler motivation for the use of multiple eigenspaces, and an
-alternate method to compute the parameters for the weights map. We
-also include a comparison with a method in literature based on
-comments from a reviewer.
+alternate learning-based method to compute weights map. %We
+%also include a comparison with a method in literature based on
+%comments from a reviewer.
 

### 2021-10-15 paper/post_tci.tex
Commented on the souble precision of SSIM in Fig. 1 caption

@@
           (SSIM=0.91) when compared to presence of TV-only prior
-          (SSIM=0.87) or no prior (SSIM=0.64).}
+          (SSIM=0.87) or no prior (SSIM=0.64), an improvement by $4\%$ and $27\%$ respectively (since the ideal SSIM=1).}
  \label{fig:story}

### 2021-10-15 paper/post_tci.tex
some textual changes.

--- 2021-10-15 paper/post_tci.tex
@@
           FBP reconstruction (first column) is of very good quality
-          (Structural Similarity Index Metric, SSIM=0.92). As the
+          (Structural Similarity Index Metric, SSIM=0.92, ideal SSIM=1.00). As the
           number of views become limited (100 views), reconstruction
@@
           (SSIM=0.91) when compared to presence of TV-only prior
-          (SSIM=0.87) or no prior (SSIM=0.64).}
+          (SSIM=0.87) or no prior (SSIM=0.64).
+          % , an improvement by $4\%$ and $27\%$ respectively (since the ideal SSIM=1)
+}
  \label{fig:story}
@@
 
-  When the number of views is reduced significantly further (as is discussed in this work), a
- regularization prior alone is not sufficient.  In such cases
- additional information (`object-prior') specific to the current
- object being scanned (called the `test' henceforth) is useful in
- further improving the reconstruction.  While this has been done in
- the context of dynamic CT-scans (discussed more in
- Section~\ref{sec:related}), in this paper we use a set $S$ of
+ When the number of views is reduced significantly further (as
+ discussed in this work), a regularization prior alone is not
+ sufficient.  In such cases additional information (`object-prior')
+ specific to the current object being scanned (called the `test'
+ henceforth) is useful in further improving the reconstruction.  While
+ this has been done in the context of dynamic CT-scans (discussed more
+ in Section~\ref{sec:related}), in this paper we use a set $S$ of
  previous scans of the same object. This is relevant in a longitudinal
@@
  using any of the prior scans \textit{as is}, or endeavoring to choose
- one ``right'' prior. In this way, this work is novel and compared to
+ one ``right'' prior. In this way, this work is novel and to be
+ contrasted with 
  earlier work. As seen in Fig.~\ref{fig:story} (last column, 20
@@
 the structure of the Okra is intricate as compared to Potato, and this
-brings with it a stronger challenge.
+brings with it a different challenge.
 
@@
 
-$\lambda_1$ and  $\lambda_2$ are tunable weights given to the
-TV-prior and object-prior terms respectively. Their selection is discussed in
-Section.~\ref{sec:tuning_parameters}. The unknowns
+$\lambda_1$ and $\lambda_2$ are tunable weights given to the TV-prior
+and object-prior terms respectively and the specification of these are
+discussed in Section.~\ref{sec:tuning_parameters}. The unknowns
 $\boldsymbol{x}$ and $\boldsymbol{\alpha}$ are solved by alternately
@@
 SSIM of the complete reconstructed test volume using the TV-only
-regularizer.  In particular, the RoI was not considered.  Now, this
-value was retained for our spatially-varying prior-based
-reconstruction as well.  In principle, one could have jointly
-optimized both $\lambda_1$ and $\lambda_2$ to get even better results
-compared to the one we have in Sections~\ref{sec:results_with_imaging_model}, and~\ref{sec:results_without_imaging_model}.  The value of
-$\lambda_2$ largely depends on the amount of artefacts one aims to
-remove by using object-prior at the cost of their dominance in the new
-regions. This value was chosen to lie between $0-3$ for our datasets
+regularizer.  In particular, regions of interest (RoI) are obviously
+not known in advance, and thus not considered for the purpose of
+tuning.  Further, this value was retained for our spatially-varying
+prior-based reconstruction as well, that is, the value optimized for
+the TV-only regularize is maintained for the method proposed in this
+paper.  In principle, one could have jointly optimized both
+$\lambda_1$ and $\lambda_2$ to get even better results compared to the
+one we have in Sections~\ref{sec:results_with_imaging_model},
+and~\ref{sec:results_without_imaging_model}.  The value of $\lambda_2$
+largely depends on the amount of artefacts one aims to remove by using
+object-prior at the cost of their dominance in the new regions. This
+value was empirically chosen to lie between $0--3$ for our datasets
 (having the fixed $\lambda_1$).
@@
 admittedly the burden $F$ of the alternate minimization procedure
-drives up the cost (as can be seen in Table~\ref{table:compute_time}).
+drives up the cost (as can be seen in
+Table~\ref{table:compute_time}). The supplementary material describes
+a method to avoid this cost if absolutely necessary.
 

### 2021-10-15 paper/post_tci.tex
minor changes

@@
 prior-based reconstruction as well, that is, the value optimized for
-the TV-only regularize is maintained for the method proposed in this
+the TV-only regularizer is maintained for the method proposed in this
 paper.  In principle, one could have jointly optimized both
@@
 and~\ref{sec:results_without_imaging_model}.  The value of $\lambda_2$
-largely depends on the amount of artefacts one aims to remove by using
-object-prior at the cost of their dominance in the new regions. This
-value was empirically chosen to lie between $0--3$ for our datasets
-(having the fixed $\lambda_1$).
+largely depends on the amount of artefacts one aims to remove by the
+use of object-prior at the cost of their dominance in the new
+regions. This value was empirically chosen to lie between $(0,3)$ for
+our datasets (having the fixed $\lambda_1$).
 
@@
 reconstruction (also see Sec~3 of \cite{supp_paper}.
+%--------------effect of the value of $k$ on Okra dataset
+\begin{figure}[h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}
+        \caption{k=5}
+     \end{subfigure}     
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}
+        \caption{k=10}
+     \end{subfigure} 
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}
+        \caption{k=20}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}
+        \caption{k=30}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}
+        \caption{k=40}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}
+        \caption{k=50}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}
+        \caption{k=60}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}
+        \caption{k=70}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}
+        \caption{k=80}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}
+        \caption{k=90}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}
+        \caption{k=100}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}
+        \caption{k=130}
+     \end{subfigure}
+    \caption{Different weights-maps for okra reconstruction. Low intensity denotes regions of new changes in test.}
+\label{fig:few_view_okra_2D_weights}
+\end{figure}
+\begin{figure}[h]
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}
+        \caption{k=5,\\ SSIM = 0.79}
+     \end{subfigure}     
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}
+        \caption{k=10,\\ SSIM = 0.78}
+     \end{subfigure} 
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}
+        \caption{k=20,\\ SSIM = 0.76}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}
+        \caption{k=30,\\ SSIM = 0.74}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}
+        \caption{k=40,\\ SSIM = 0.72}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}
+        \caption{k=50,\\ SSIM = 0.63}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}
+        \caption{k=60,\\ SSIM = 0.61}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}
+        \caption{k=70,\\ SSIM = 0.59}
+     \end{subfigure}
+  \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}
+        \caption{k=80,\\ SSIM = 0.58}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}
+        \caption{k=90,\\ SSIM = 0.56}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}
+        \caption{k=100,\\ SSIM = 0.55}
+     \end{subfigure}
+   \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
+        \caption{k=130,\\ SSIM = 0.53}
+     \end{subfigure}
+    \caption{2D reconstructions for varying values of $k$.
+The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}
+\label{fig:reconstructions_as_k_varies}
+\end{figure}
 
@@
 material~\cite{supp_paper}.
-
-%--------------effect of the value of $k$ on Okra dataset
-
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_5_lambda_prior_0.700000.png}
-        \caption{k=5}
-     \end{subfigure}     
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_10_lambda_prior_0.700000.png}
-        \caption{k=10}
-     \end{subfigure} 
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_20_lambda_prior_0.700000.png}
-        \caption{k=20}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_30_lambda_prior_0.700000.png}
-        \caption{k=30}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_40_lambda_prior_0.700000.png}
-        \caption{k=40}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_50_lambda_prior_0.700000.png}
-        \caption{k=50}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_60_lambda_prior_0.700000.png}
-        \caption{k=60}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_70_lambda_prior_0.700000.png}
-        \caption{k=70}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_80_lambda_prior_0.700000.png}
-        \caption{k=80}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_90_lambda_prior_0.700000.png}
-        \caption{k=90}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_100_lambda_prior_0.700000.png}
-        \caption{k=100}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weightsIm_kk_130_lambda_prior_0.700000.png}
-        \caption{k=130}
-     \end{subfigure}
-    \caption{Different weights-maps for okra reconstruction. Low intensity denotes regions of new changes in test.}
-\label{fig:few_view_okra_2D_weights}
-\end{figure}
-\begin{figure}[h]
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_5_lambda_prior_0.700000.png}
-        \caption{k=5,\\ SSIM = 0.79}
-     \end{subfigure}     
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_10_lambda_prior_0.700000.png}
-        \caption{k=10,\\ SSIM = 0.78}
-     \end{subfigure} 
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_20_lambda_prior_0.700000.png}
-        \caption{k=20,\\ SSIM = 0.76}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_30_lambda_prior_0.700000.png}
-        \caption{k=30,\\ SSIM = 0.74}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_40_lambda_prior_0.700000.png}
-        \caption{k=40,\\ SSIM = 0.72}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_50_lambda_prior_0.700000.png}
-        \caption{k=50,\\ SSIM = 0.63}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_60_lambda_prior_0.700000.png}
-        \caption{k=60,\\ SSIM = 0.61}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_70_lambda_prior_0.700000.png}
-        \caption{k=70,\\ SSIM = 0.59}
-     \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_80_lambda_prior_0.700000.png}
-        \caption{k=80,\\ SSIM = 0.58}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_90_lambda_prior_0.700000.png}
-        \caption{k=90,\\ SSIM = 0.56}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_100_lambda_prior_0.700000.png}
-        \caption{k=100,\\ SSIM = 0.55}
-     \end{subfigure}
-   \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/okra/post_TCI/2D/48_views/tuning_k/weighted_prior_kk_130_lambda_prior_0.700000.png}
-        \caption{k=130,\\ SSIM = 0.53}
-     \end{subfigure}
-    \caption{2D reconstructions for varying values of $k$.
-The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}
-\label{fig:reconstructions_as_k_varies}
-\end{figure}
 

### 2021-10-15 paper/post_tci_supplementary.tex
Added videos
minor changes of adding *

@@
 \begin{itemize}
-\item \textbf{Okra:}
 
-  3D Okra of size $338\times 338\times 123$ was reconstructed from 45 cone-beam view measurements.
-
-  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}
 \item \textbf{Potato:}
@@
     \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}
+
+  \item \textbf{Okra:}
+
+  3D Okra of size $338\times 338\times 123$ was reconstructed from 45 cone-beam view measurements.
+
+  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}
 \end{itemize}
@@
 can be stitched in a simplistic way using the equation 
-$\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
+$\boldsymbol{W_b}*(\rm{pilot}) + (1-\boldsymbol{W_b})*(\rm{prior})$.
 The advantage of this method is that the computational time is

### 2021-10-15 paper/changes.tex
Final set of changes

@@
 
-    \textit{That said, the goal of our previous and curent work is to provide
+    \textit{That said, the goal of our previous and current work is to provide
     a technique that can improve upon a chosen baseline reconstruction
@@
    We accept this point, and have now discussed the difficulties in
-   using deep-learning techniques for the current problem in Section.~7C
+   using deep-learning techniques for the current problem in Section.~7B
    of our paper.
@@
  and DCT as sparsity basis. The details of solvers used for these
- algorithms and their reconstructions are in Page.~7 (Section-6A) of
+ algorithms and their reconstructions are in Page.~8 (Section 6B) of
  the paper. For CS reconstruction, we observed that Haar wavelet and
@@
 
-We accept this point, and present details in Section.~7B of our paper.
+We accept this point, and present details in Section.~7A of our paper.
 We also provide the code to reproduce the compute time claimed.

### 2021-10-15 paper/post_tci.tex
Final set of changes

@@
 pseudo-test and validating the $k$ that results in the best
-reconstruction (also see Sec~3 of \cite{supp_paper}.
+reconstruction (also see Sec~3 of \cite{supp_paper}).
 %--------------effect of the value of $k$ on Okra dataset
@@
         metrics for evaluation  of
-        these reconstructions is shown in
+        these reconstructions are shown in
         Table.~\ref{table:potato_2D_ssim}.}
@@
 Deep learning techniques are powerful tools to learn an unknown
-parameteric function relating an input space and an output space. In such
+parametric function relating an input space and an output space. In such
 settings, our current goal of detecting new changes is a `prediction'
@@
 assigning low prior weights wherever necessary.
-This innovation becomes evident through the weights maps shown here in Figures~\ref{fig:weights_map_2Dpotato} and~\ref{fig:few_view_okra_2D_weights}.
+This innovation becomes evident through the weights maps shown in Figure~\ref{fig:weights_map_2Dpotato} and the resulting reconstructions shown in Figure~\ref{fig:reconstructions_diff_methods}.
 The probability of

### 2021-10-15 paper/post_tci_supplementary.tex
saving suppl edits
Final set of changes

--- 2021-10-15 paper/post_tci_supplementary.tex
@@
     \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}
+ \item \textbf{Okra:}
+
+  3D Okra of size $338\times 338\times 123$ was reconstructed from 45 cone-beam view measurements.
+
+  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}
 \end{itemize}
@@
 
-The value of $k$ (discussed in Sec.~7 of the main paper) is typically
+The value of $k$ (discussed in Sec.~6A of the main paper) is typically
 dependent on the number of false positives the system can allow in
@@
 We mention in passing that if we are to entirely avoid the other
-parameters (viz. $\lambda_1$ and $\lambda_2$), the prior and the pilot
+parameters (viz. $\lambda_1$ and $\lambda_2$), the object-prior and the pilot
 can be stitched in a simplistic way using the equation
-$\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
+
+$\boldsymbol{W_b}*(\rm{pilot}) + (1-\boldsymbol{W_b})*(\rm{object\textrm{ }prior})$.
 The advantage of this method is that the computational time is
-signficantly reduced since the alternate minimization procedure is not
+significantly reduced since the alternate minimization procedure is not
 used.
@@
 \begin{figure}[]
-    \begin{subfigure}[b]{0.24\linewidth}
+    \begin{subfigure}[b]{0.32\linewidth}
         \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
@@
      \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
+    \begin{subfigure}[b]{0.32\linewidth}
         \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
@@
      \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
+    \begin{subfigure}[b]{0.32\linewidth}
         \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
@@
      \end{subfigure}
-     \begin{subfigure}[b]{0.24\linewidth}
+     \begin{subfigure}[b]{0.32\linewidth}
         \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
@@
      \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
+    \begin{subfigure}[b]{0.32\linewidth}
         \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
+    \begin{subfigure}[b]{0.32\linewidth}
         \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}
-
-        \caption{}
-    \end{subfigure}    
-    \begin{subfigure}[b]{0.24\linewidth}
-        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
         \caption{}
@@
 Measurements along $60$ views were taken.
-(e) error-map showing new regions, (f) detected binary weights map showing regions of new changes, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions.
+(e) error-map showing new regions, (f) detected binary weights map showing regions of new changes.}%, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions.
 } %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates,
@@
 \bibliography{tci_ref}
+
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}
+
+        \caption{}
+    \end{subfigure}    
+    \begin{subfigure}[b]{0.24\linewidth}
+        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
+        \caption{}
+     \end{subfigure}

### 2022-02-03 paper/post_tci.tex
First set of changes after Dec-reviews: Std,Custom SSIM, DL Literature, hyperparameter tuning

@@
   with these techniques is the strong influence of object-priors in
-  the reconstruction of new regions in the test.  In this work, we
-  mitigate this problem by first estimating the location of new
-  regions and then imposing object-prior in \textit{only} old regions
-  which are similar to the prior.
+  the reconstruction of new changes in the test.  In this work, we
+  mitigate this problem by first estimating the location of changes (`new
+  regions') and then imposing object-prior in \textit{only} those regions
+  which are similar to the prior (`old regions').
 
@@
   synthetic as well as real projection data, in both 2D and 3D. Our
-  method significantly improves the overall quality of reconstructions
-  while minimizing the number of measurements needed for imaging in
-  longitudinal studies.
+  technique significantly improves the overall quality of
+  reconstructions while minimizing the number of measurements needed
+  for imaging in longitudinal studies. We show that with
+  as little as $2\%$ of measurements, our method achieves a structural
+  fidelity of $0.84$, with $1.00$ representing ideal reconstruction.
 \end{abstract}
@@
  With the use of an object-prior, a \emph{new} challenge emerges. The prior
- set $S$ may potentially overwhelm the necessary details, and when
+ set $S$ may potentially overwhelm the necessary details~\cite{mythesis}, and when
  several prior scans are available, finding the best one is an
@@
 expert-domain knowledge about the object being scanned.
+
+ In the recent past, deep learning based techniques have also been widely used for limited view CT reconstruction without the use of any longitudinal object-prior.
+For example, in~\cite{anirudh}, a neural network is trained to predict the complete sinogram from an incomplete one obtained from few-view imaging.
+This complete sinogram is then fed to analytical reconstruction algorithms to obtain the final reconstruction.
+Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework.
+\cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram.
+\cite{special} trains an adverserial network for artifact removal and edge preservation in limited view reconstruction.
+While all of the above methods predict full-view reconstruction from the measurements of test object alone, we believe it is beneficial to use information from longitudinal data, especially if naturally available, like in the radio-frequency ablation datasets that we use.
+In this context, we present an analytical method that uses the available longitudinal data to better inform the reconstruction of the test.
+We first construct a `weights map' that gives clear insights about regions of change within the object over time.
 
@@
 consider perceptual changes, as well as correlation between adjacent
-pixels. This can be useful in a clinical context.  Here, we therefore
-assign a higher weightage to structure preservation, that is we assign
-the following weights to structure, contrast, and intensity
-respectively: $0.7,0.2,0.1$. Our results are optimized for SSIM, but
+pixels.
+This can be useful in a clinical context.
+The SSIM~\cite{multiscale_ssim} also provides a flexibility to set coefficients for the following three factors: Structure, Contrast and Intensity.
+In all our results, we report SSIM with both the standard setting, i.e., with coefficients $1.0,1.0,1.0$ and a structure-focussed setting, wherein we assign a higher weightage to structure preservation.
+In the latter case, we assign the following coefficients to the factors Structure, Contrast, and Intensity respectively: $0.7,0.2,0.1$.
+Our results are optimized for structure-focussed SSIM, but
 it can be verified that in all cases for the various datasets
@@
 \label{sec:tuning_parameters}
-$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
+The three hyper-parameters, $\lambda_1$, $\lambda_2$ and $k$
 need to be chosen carefully for optimal reconstruction. In our
-experiments, $\lambda_1$ was tuned in such a way as to maximize the
+experiments, $\lambda_1$ was tuned to maximize the
 SSIM of the complete reconstructed test volume using the TV-only
-regularizer.  In particular, regions of interest (RoI) are obviously
-not known in advance, and thus not considered for the purpose of
-tuning.  Further, this value was retained for our spatially-varying
+regularizer.  In particular, regions of interest (RoI) are 
+not known in advance, and thus not considered for the purpose of this
+tuning.
+Thus, we compare our reconstruction with the best possible baseline TV reconstruction by choosing the $\lambda_1$ that gives the best SSIM for TV reconstruction.
+Further, this value was retained for our spatially-varying
 prior-based reconstruction as well, that is, the value optimized for
@@
 one we have in Sections~\ref{sec:results_with_imaging_model},
-and~\ref{sec:results_without_imaging_model}.  The value of $\lambda_2$
+and~\ref{sec:results_without_imaging_model}.
+
+The value of $\lambda_2$
 largely depends on the amount of artefacts one aims to remove by the
 use of object-prior at the cost of their dominance in the new
-regions. This value was empirically chosen to lie between $(0,3)$ for
-our datasets (having the fixed $\lambda_1$).
+regions.
+This value is chosen omnisciently, i.e., with the chosen $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM.
+This  was found to lie between $(0,3)$ for
+our datasets.
+In practice however, one may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.
 
@@
     \caption{2D reconstructions for varying values of $k$.
-The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}
+The SSIM (structure-focussed) values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}
 \label{fig:reconstructions_as_k_varies}
@@
 
-Alternatively, in cases where one wishes to completely avoid the use
-of this hyper-parameter, one can construct a binary weights-map using
-a learning based method described in the supplementary
-material~\cite{supp_paper}.
+Our supplementary material~\cite{supp_paper} (part-3) discusses an alternate reconstruction method that does not require two of the three hyperparameters: $\lambda_1$ and $\lambda_2$.
+In this method, the computed weights-map is used to stitch parts of the pilot reconstruction and object-prior based on the weights map, and hence there is no optimization to be solved involving $\lambda_1$ and $\lambda_2$.
+The computation of weights map alone requires selection of the hyperparameter value k.
 
@@
         The test image in Fig.~\ref{fig:potato_data_2D}(d) is
-        reconstructed using only $6$ paltry views.  The weights-maps
+        reconstructed using only $6$ views.  The weights-maps
         %(corresponding to the difference between pilot reconstruction
@@
   \centering
-\caption{SSIM and RMSE of the reconstructions shown in
+\caption{Standard-SSIM (`SSIM-1'), structure-focussed SSIM (`SSIM-2') and RMSE of the reconstructions shown in
   Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(h). %The SSIM of
@@
 & \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
-SSIM & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
+SSIM-1 & 0.31 & 0.48  & 0.39  & 0.51 & 0.55  & 0.42 & 0.68 &\textcolor{red}{0.78} \\ \hline
+SSIM-2 & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
 RMSE & 0.38 & 0.18 & 0.25 & 0.43 & 0.33 & 0.21 & 0.11 & \textcolor{red}{0.04}\\ \hline
@@
   \centering
-  \caption{SSIM (RMSE) within the RoI of reconstructed potato from various
+  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed potato from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.52 (0.36)
-& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.22, 0.52 (0.36)
+& 0.86, 0.92 (0.06) & \textcolor{red}{0.95, 0.97 (0.03)} \\ \hline \textbf{3D} & 0.30, 0.58 (0.26) & 0.56, 0.75 (0.21) & \textcolor{red}{0.72, 0.84 (0.16)}
 \\ \hline
@@
   \centering
-  \caption{SSIM (RMSE) within the RoI of reconstructed okra from various
+  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed okra from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
-& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ 
-\hline \textbf{3D} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.26, 0.46 (0.28)
+& 0.27, 0.50 (0.24) & \textcolor{red}{0.56, 0.74 (0.15)} \\ 
+\hline \textbf{3D} & 0.52, 0.65 (0.22) & 0.56, 0.70 (0.21) & \textcolor{red}{0.57, 0.71 (0.19)}
 \\ \hline
@@
   \centering
-  \caption{SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
+  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
 %For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
@@
 \hline \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline  0.73 (0.04)
-& 0.91 (0.09) & \textcolor{red}{0.95 (0.03)} \\ \hline 
+\textbf{This paper} \\ \hline 0.54, 0.73 (0.04)
+& 0.80, 0.91 (0.09) & \textcolor{red}{0.90, 0.95 (0.03)} \\ \hline 
 \end{tabular}
@@
   \centering
-  \caption{SSIM (RMSE) within the RoI of reconstructed sprouts from various
+  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed sprouts from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
- \\ \hline \textbf{2D} & 0.67 (0.24)
-& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
+ \\ \hline \textbf{2D} & 0.42, 0.67 (0.24)
+& 0.61, 0.82 (0.17) & \textcolor{red}{0.72, 0.86 (0.13)} \\ \hline \textbf{3D} & 0.44, 0.67 (0.25) & 0.47, 0.73 (0.23) & \textcolor{red}{0.66, 0.82 (0.14)}
 \\ \hline
@@
 
-\section{Discussion}
+\section{Computational Complexity}
 \label{sec:discussion}
-In this section, we discuss computational
-complexity of our method and requirements for applying deep learning
-techniques in longitudinal few-view reconstruction.
-\subsection{Computational Complexity}
+%In this section, we discuss computational
+%complexity of our method and requirements for applying deep learning
+%techniques in longitudinal few-view reconstruction.
+%\subsection{Computational Complexity}
 
@@
   \caption{Computation times (in seconds) for various stages of
-    reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD
+    reconstruction of a (512$\times$512) 2D slice of Liver from 30 views, on MATLAB 2019a on an  AMD
     2920X 12-Core Processor machine with 64GB RAM. Our code is
@@
 \hline
- \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
+ \begin{tabular}[c]{@{}l@{}} FBP \end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \end{tabular} \\ \hline
 \multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{5.63} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
@@
 \end{table}
+\begin{comment}
 \subsection{Requirements for applying deep learning techniques}
@@
   work.
+\end{comment}
 

### 2022-02-03 paper/ssim_formaula.tex
First set of changes after Dec-reviews: Std,Custom SSIM, DL Literature, hyperparameter tuning

\documentclass{article}
\usepackage{amsmath,graphicx}
\usepackage{subcaption}
\usepackage{xcolor}

\begin{document}

With $\mu_x$, $\mu_y$ and $\sigma_x^2$, $\sigma_y^2$ being the averages and variances of pixel values along dimensions $x$ and $y$ respectively, $\sigma_{xy}$ being the covariance along $x$ and $y$, $L$ being the dynamic range, $c_1$ and $c_2$, and $c_3$ being defined to be $(k_1L)^2$, $(K_2L)^2$ and $c_2/2$ repectively, with $k_1=0.01$ and $k_2=0.03$, the three components of SSIM metric: luminance $l$, contrast $c$ and structure $s$ are defined as:

\begin{equation}
l(x,y) = \frac{2\mu_x\mu_y + c_1}{\mu_x^2 + \mu_y^2 + c_1}
\end{equation}

\begin{equation}
  c(x,y) = \frac{2\sigma_x\sigma_y + c_2}{\sigma_x^2 + \sigma_y^2 + c_2}
\end{equation}

\begin{equation}
  s(x,y) = \frac{\sigma_{xy} + c_3}{\sigma_x\sigma_y + c_3}
\end{equation}

Fianlly, SSIM is defined as

\begin{equation}
  SSIM = \frac{1}{n}\sum_x\sum_y [l(x,y)^\alpha. c(x,y)^\beta. s(x,y)^\gamma],
\end{equation}

where $n$ denotes the total number of pixels. The coefficients $\alpha$, $\beta$ and $\gamma$ are generally set to $1$ but are adjustable to suit the application goal.

%--------------------------------okra data-------------------------------
\begin{figure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.186\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/thesis/okra/testCropped.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption[Okra 3D dataset]{Okra 3D dataset: One slice each from the templates (the
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:templates_test_okra}
\end{figure}
%----------------------------------------------------

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/testCropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/fdk_cropped.png}}\hfill
\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/cs_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/prior_weighted_cropped.png}}
\caption[3D reconstruction of okra dataset]{3D reconstruction of the okra from $10\%$ projection
  views (b) has strong streak artefacts, (c) blurred, (d) no new
  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
  corresponding to red and green regions) while simultaneously
  reducing streak artefacts.}
\label{fig:okra_3D_results}
\end{figure}

%--------------------------------------zoomed okra

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/input_cropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
\caption[Zoomed results of Okra dataset]{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
 ).}
\label{fig:okra_zoomed_3D_results}
\end{figure}

\end{document}

### 2022-02-03 3D_Recon/okra/ParamSetting_okra_pca.m
Added 3D Recon Okra scripts

@@ -1,0 +1,85 @@
+%{ 
+Parameter setting corresponding to Imaging geometry used at the time
+of acquiring measurements.
+%}
+
+
+function ParamSetting_okra_pca(angStepSize,outDirectory)
+
+param.nx = 338; %number of voxels
+param.ny = 338;
+param.nz = 123;
+
+param.sx = 107.6;% mm (real size)
+param.sy = 107.6; % mm 
+param.sz = 39; % mm  
+
+%The real detector panel pixel density (number of pixels)
+param.nu = 336;		
+param.nv = 156;
+
+% Detector setting (real size)
+param.su = 336*0.15*8;	% mm (real size)
+param.sv = 156*0.15*8;     % mm
+
+% X-ray source and detector setting
+param.DSD = 785.5;    %  Distance source to detector 
+param.DSO = 210;	  %  X-ray source to object axis distance
+
+% angle setting
+param.dir = 1;            % gantry rotating direction (clock wise/ counter clockwise)
+param.dang = angStepSize; % angular step size (deg)
+param.deg =  0:param.dang:359.5; 
+param.deg = param.deg*param.dir;
+param.nProj = length(param.deg);
+
+param.parker = 1;
+% data with 360 deg -> param.parker = 0 , data less than 360 deg -> param.parker=1 
+
+% % % % % % Confirm your parameters % % % % % % %
+ 
+% filter='ram-lak','cosine', 'hamming', 'hann' 
+param.filter='ram-lak'; % high pass filter
+
+param.dx = param.sx/param.nx; % single voxel size
+param.dy = param.sy/param.ny;
+param.dz = param.sz/param.nz;
+param.du = param.su/param.nu;
+param.dv = param.sv/param.nv;
+
+param.off_u = 0; param.off_v = 0; % detector rotation shift (real size)
+
+%----- Geometry calculation ----
+param.xs = [-(param.nx-1)/2:1:(param.nx-1)/2]*param.dx;
+param.ys = [-(param.ny-1)/2:1:(param.ny-1)/2]*param.dy;
+param.zs = [-(param.nz-1)/2:1:(param.nz-1)/2]*param.dz;
+
+param.us = (-(param.nu-1)/2:1:(param.nu-1)/2)*param.du + param.off_u;
+param.vs = (-(param.nv-1)/2:1:(param.nv-1)/2)*param.dv + param.off_v;
+
+param.interptype = 'linear'; 
+
+% % % % % % Confirm your parameters % % % % % % %
[…]

### 2022-02-03 3D_Recon/okra/TVReg-master/tvreg_demo3.m

@@ -1,0 +1,146 @@
+%tvreg_demo3  Demo script for a TV tomography problem
+%% This script illustrates the use of the TV algorithm
+% implemented in the functions tvreg_upn and tvreg_gpbb.
+% The user can easily modify the script for
+% other noise levels, regularization etc..
+%
+% The scripts loads a a clean threedimensional version of the 
+% classical Shepp-Logan phantom image, and  
+% obtains the observed data by multiplication with 
+% a tomography matrix A and addition of noise.
+% The algorithms tvreg_upn and tvreg_gpbb are used to 
+% obtain the TV reconstructions of the phantom. An reference
+% solution is calculated to obtain an estimate of the optimal
+% objective.
+%
+% This script only differs from tvreg_demo1 that the A matrix
+% is implicit formed as a matrix function.
+
+clear
+close all
+clc
+
+addpath lebdir tomobox
+
+% Ensure we can reproduce results by fixing random numbers
+randn('state',600)
+rand('state',700)
+
+%% Set parameters
+rnl    = 0.01;       % Noise level
+alpha  = 0.1;        % Regularization parameter
+r1_max = 13;         % Halfwidth of object cube
+N      = 2*r1_max+1; % Full width of object cube
+N3     = N^3;        % Total number of variables
+dims   = [N,N,N];    % Dimensions
+u_max  = 15;         % Halfwidth of projection planes
+U      = 2*u_max+1;  % Full width of projection planes
+numProjections = 25; % Number of projections to reconstruct from
+
+%% Construct tomography system matrix A and make spy plot
+P              = getLebedevDirections(numProjections);
+A              = buildSystemMatrix(r1_max,u_max,P);
+
+figure
+spy(A)
+title('Sparsity pattern in A')
+
+%% Construct true image and right hand side
+X0     = phantom3d('Modified Shepp-Logan',N);       % Cube version
+x0     = X0(:);                                     % Vectorized version
+borig  = A*x0;                                      % Projections from true
[…]

### 2022-02-03 3D_Recon/okra/compute_quant_results.m

@@ -1,0 +1,138 @@
+clear all;
+clc;
+close all;
+% outDirectory = 'results/TV_with_weighted_prior/45_views_with_registered_templates';
+outDirectory = 'results/TV_with_weighted_prior/30_views';
+dataset ='okra3';
+
+file = load(sprintf('%s/okra3_testVol.mat',outDirectory));
+testVol = double(file.data);
+% testVol = testVol(:,110:end-100,:);
+file = load(sprintf('%s/FDK.mat',outDirectory));
+fdkVol = double(file.FDK);
+% fdkVol = fdkVol(:,110:end-100,:);
+file = load(sprintf('%s/TV_lambdaTV_0.45.mat',outDirectory));
+tvVol = file.TV;
+% tvVol = tvVol(:,110:end-100,:);
+file = load(sprintf('%s/weighted_prior_kk_1_lambda_prior_0.500000.mat',outDirectory));
+weightedPriorVol = file.result_weighted_pca;
+% weightedPriorVol = weightedPriorVol(:,110:end-100,:);
+
+
+
+
+
+% testVol = testVol - min(testVol(:));
+% testVol  = testVol./max(testVol(:));
+% fdkVol = fdkVol - min(fdkVol(:));
+% fdkVol = fdkVol./max(fdkVol(:));
+% tvVol = tvVol - min(tvVol(:));
+% tvVol = tvVol./max(tvVol(:));
+% weightedPriorVol = weightedPriorVol - min(weightedPriorVol(:));
+% weightedPriorVol = weightedPriorVol./max(weightedPriorVol(:));  
+
+
+% leaveSlices = 0;
+% ssim_fdk = ssim(fdkVol(:,:,end-leaveSlices),testVol(:,:,end-leaveSlices))
+% ssim_tv = ssim(tvVol(:,:,end-leaveSlices),testVol(:,:,end-leaveSlices))
+% ssim_wightedPrior = ssim(weightedPriorVol(:,:,end-leaveSlices),testVol(:,:,end-leaveSlices))
+% 
+% relRMSE_fdk = rmseVol(fdkVol,testVol)
+% relRMSE_tv = rmseVol(tvVol,testVol)
+% relRMSE_weightedPrior = rmseVol(weightedPriorVol,testVol)
+% 
[…]

### 2022-02-03 3D_Recon/okra/genEigenSpaceOkra_hole.m

@@ -1,0 +1,114 @@
+function genEigenSpaceOkra_hole(templateNos,outDirectory)
+
+startTemplateNum = templateNos(1);
+endTemplateNum = templateNos(end);
+numTemplates = length(startTemplateNum:endTemplateNum);
+numSlices = 123; 
+sizeOfSlice = [338 338];
+
+volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+% Read the templates in 3D format-------------------
+
+for i = 1:numTemplates  
+   name = sprintf('inputs/okra%d_okra6_reg_cropped_450views_fdk.mat',i+startTemplateNum-1) 
+   % --The templates have been registered with repect to Okra6 (6th volume of Okra)
+
+   fileData = load(name);
+   volumes(:,:,:,i) = fileData.FDK;
+   image = volumes(:,:,30,i);
+   image = image - min(image(:));
+   image = image./max(image(:));
+   name = sprintf('inputs/template_%d.png',i);
+   imwrite(image,name);
+   
+   % store cropped image
+   
+   image = volumes(:,110:end-100,30,i);
+   image = image - min(image(:));
+   image = image./max(image(:));
+   name = sprintf('inputs/templateCropped_%d.png',i);
+   imwrite(image,name);
+end
+
+
+% store templates and test together------------------
+
+name = sprintf('inputs/okra%d_cropped_450views_fdk.mat',3) ;
+fileDataTest = load(name);
+testVol = fileDataTest.FDK;
+image = testVol(:,110:end-100,30);
+image = image - min(image(:));
+image = image./max(image(:));
+name = 'inputs/test.png';
+imwrite(image,name);
+
+
+
+all_templates = [volumes(:,:,1:end-65,1) volumes(:,:,1:end-65,2) volumes(:,:,1:end-65,3) volumes(:,:,1:end-65,4) testVol(:,:,1:end-65)];
+all_templates = all_templates - min(all_templates(:));
+all_templates = all_templates./max(all_templates(:));
+name = 'templates_and_test';
+dataset ='_';
+store_video(all_templates,name,'inputs',dataset);
+tempTestImg = [volumes(:,:,10,1) volumes(:,:,10,2) volumes(:,:,10,3) volumes(:,:,10,4) testVol(:,:,10)];
+tempTestImg = tempTestImg - min(tempTestImg(:));
+tempTestImg = tempTestImg./max(tempTestImg(:));
[…]

### 2022-02-03 3D_Recon/okra/main.m

@@ -1,0 +1,160 @@
+%{
+This is the main file for reconstructing 3D volumes from measurements of
+Okra.
+%}
+
+dataset = 'okra3';
+outDirectory = ('results/TV_with_weighted_prior/30_views/')
+mkdir(outDirectory);
+sliceNumber = 30;
+lambda_prior_list = [0.1,0.3,0.5,0.7,0.9];
+
+projFileName = sprintf('inputs/Preeti_%s/projf32_LIN_AP.nc',dataset);
+ncid = netcdf.open(projFileName);
+proj = double(netcdf.getVar(ncid,1));
+netcdf.close(ncid);
+  
+startz = 1; endz = size(proj,3); % corresponds to each view
+starty = 100; endy = 255;
+startx = 11; endx = size(proj,1)-10-1; 
+
+proj = proj(startx:endx, starty: endy, startz:endz);
+
+selectedProj = 1:15:size(proj,3);
+proj = proj(:,:,selectedProj);
+angStepSize = 12;
+numAngles = length(selectedProj)
+ParamSetting_okra_pca(angStepSize,outDirectory)
+name = sprintf('%s/parameters_okra_pca.mat',outDirectory);
+load(name);
+
+dim = [param.nx param.ny param.nz]; 
+
+sizeProj = size(proj);
+save('ProjectionSize.mat','sizeProj');
+
+
+%% --------generate Ground truth------------------
+
+name = sprintf('inputs/%s_cropped_450views_fdk.mat',dataset);
+testVolFile = load(name);
+testVol = testVolFile.FDK;
+name = 'testVol';
+store_video(testVol,name,outDirectory,dataset);
+
+name = sprintf('%s/testVol.png',outDirectory);
+temp = testVol(:,:,sliceNumber);
+temp = temp - min(temp(:));
+temp = temp./max(temp(:));
+imwrite(temp,name);
+
+testVol1 = testVol - min(testVol(:));
+testVol1  = testVol1./max(testVol1(:));
+
+
+%% -----Filtered Back-projection-----------------------
+
+disp('starting FDK');
+tic;
+[FDK] = okra_FDK(proj,param,dim);
+time_FDK = toc;
+
+name = 'FDK';
+store_video(FDK,name,outDirectory,dataset);
+name = sprintf('%s/FDK.mat',outDirectory);
+save(name,'testVol','FDK');
+name = sprintf('%s/FDK.png',outDirectory);
+temp = FDK(:,:,sliceNumber);
[…]

### 2022-02-03 3D_Recon/okra/okra_CS.m

@@ -1,0 +1,13 @@
+function CS = okra_CS(proj,param,dim,lambda0,rel_tol)
+
+Afun = @(z) AConeBeam(z,dim,param);
+Atfun = @(z) AtConeBeam(z,dim,param);
+
+y = proj(:) ;
+
+m = size(y,1);
+n = param.nx*param.ny*param.nz;       
+
+[x_hat,status,historyNoPrior]=l1_ls_modified(Afun,Atfun,m,n,y,lambda0,rel_tol);
+output = reshape(x_hat,[param.nx param.ny param.nz]);
+CS = mirt_idctn(output);

### 2022-02-03 3D_Recon/okra/okra_FDK.m

@@ -1,0 +1,4 @@
+function FDK = okra_FDK(proj,param,dim)
+
+proj_filtered = filtering(proj,param);
+FDK = CTbackprojection(proj_filtered, param);

### 2022-02-03 3D_Recon/okra/okra_entire_dataset.m

@@ -1,0 +1,39 @@
+close all;
+clear all;
+
+templateNos = [1,2,3,4,5,6, 7];
+numTemplates = length(templateNos);
+numSlices = 123; % number of slices in a volume;
+sizeOfSlice = [338 338];
+
+
+volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+% Read the templates in 3D format-------------------
+
+for i = 1:numTemplates  
+   name = sprintf('inputs/okra%d_okra6_reg_cropped_450views_fdk.mat',templateNos(i)) ;
+   fileData = load(name);
+   volumes(:,:,:,i) = fileData.FDK;
+   
+    temp = volumes(:,:,30,i);
+    fname = sprintf('slice%d.mat',i);
+    save(fname,'temp');    
+    temp = temp - min(temp(:));
+    temp = temp./max(temp(:));    
+    name = sprintf('slice%d.png',i);
+    imwrite(temp,name);
+end
+ 
+allVolumes = [volumes(:,:,1:60,1) volumes(:,:,1:60,2) volumes(:,:,1:60,3) volumes(:,:,1:60,4) volumes(:,:,1:60,5) volumes(:,:,1:60,6) volumes(:,:,1:60,7)];
+allVolumes = allVolumes - min(allVolumes(:));
+allVolumes = allVolumes./max(allVolumes(:));
+name = 'entire_dataset';
+dataset ='okra';
+store_video(allVolumes,name,'inputs',dataset);
+tempTestImg = [volumes(:,:,30,1) volumes(:,:,30,2) volumes(:,:,30,3) volumes(:,:,30,4) volumes(:,:,30,5) volumes(:,:,30,6) volumes(:,:,30,7) ];
+tempTestImg = tempTestImg - min(tempTestImg(:));
+tempTestImg = tempTestImg./max(tempTestImg(:));
+imwrite(tempTestImg,'inputs/okra_entire_dataset.png');
+
+

### 2022-02-03 3D_Recon/okra/okra_fdk_presentation.m

@@ -1,0 +1,88 @@
+close all;
+clear all;
+
+dataDir = dir('../data/okra/');
+numOkras = size(dataDir,1)-2;
+outDirectory = 'inputs/presentation';
+mkdir(outDirectory);
+
+for i = 1:1;%numOkras
+    
+    dataDir(i+2).name
+    projFileName = sprintf('../data/okra/Preeti_okra%d/projf32_LIN_AP.nc',i);
+    ncid = netcdf.open(projFileName);
+    proj = double(netcdf.getVar(ncid,1));
+    netcdf.close(ncid);
+    %------------------------------------------
+
+    startz = 1; endz = size(proj,3); % corresponds to each view
+    starty = 100; endy = 255;
+    startx = 11; endx = size(proj,1)-10-1; 
+
+    %-------------------------------
+
+    proj = proj(startx:endx, starty: endy, startz:endz); 
+    angStepSize = 0.8;
+
+
+%     mask = find(proj~=-1);
+%     minimum = min(proj(mask));
+%     proj(mask) = proj(mask) - minimum;
+%     proj(proj==-1) = 0;
+%     proj = proj./max(proj(:));
+%     name = sprintf('okra%d_proj_cropped.avi',i);
+%     writevideo (name, proj, 8);
+
+%     proj1 = zeros([168 78 size(proj,3)]);
+%     for i = 1:size(proj(:,:,3))
+%         img = proj(:,:,i);
+%         img = imresize(img,[168 78]);
+%         proj1(:,:,i) = img;
+%     end
+%     proj = proj1;
+     size(proj)
+    %----------------------------Filtered Back-projection---------------------------
+
+    ParamSetting_okra_pca(angStepSize)
+    load('parameters_okra_pca.mat');
+
+    proj_filtered = filtering(proj,param);
+    FDK_original = CTbackprojection(proj_filtered, param);
+    
+    name = sprintf('%s/okra%d_cropped_450views_fdk.mat',outDirectory,i);
+    save(name,'FDK_original');
+    
+    FDK = FDK_original(:,:,1:end-80);
+    
+    FDK = FDK - min(FDK(:));
+    FDK = FDK./max(FDK(:));
+    FDKPermuted1 = permute(FDK,[3 1 2]);
+    FDKPermuted2 = permute(FDK,[3 2 1]);    
+    
+    % write to video file
+    
[…]

### 2022-02-03 3D_Recon/okra/okra_hole_pca.m

@@ -1,0 +1,281 @@
+close all;
+clear all;
+dataset = 'okra3';
+
+projFileName = sprintf('../data/okra/Preeti_%s/projf32_LIN_AP.nc',dataset);
+ncid = netcdf.open(projFileName);
+proj = double(netcdf.getVar(ncid,1));
+netcdf.close(ncid);
+%------------------------------------------
+  
+startz = 1; endz = size(proj,3); % corresponds to each view
+starty = 100; endy = 255;%size(proj,2)-1;
+startx = 11; endx = size(proj,1)-10-1; 
+
+proj = proj(startx:endx, starty: endy, startz:endz);
+selectedProj = 1:10:size(proj,3);
+proj = proj(:,:,selectedProj);
+angStepSize = 8;
+ParamSetting_okra_pca(angStepSize)
+load('parameters_okra_pca.mat');
+
+dim = [param.nx param.ny param.nz]; 
+%----------------------------Filtered Back-projection---------------------------
+
+proj_filtered = filtering(proj,param);
+FDK = CTbackprojection(proj_filtered, param);
+
+FDK = FDK - min(FDK(:));
+FDK= FDK./max(FDK(:));
+FDKPermuted1 = permute(FDK,[3 1 2]);
+FDKPermuted2 = permute(FDK,[3 2 1]);
+
+name = sprintf('%s_reg_45views_fdk.mat',dataset);
+% FDKfile = load(name);
+% FDK = FDKfile.FDK;
+save(name,'FDK');
+% % 
+% % % write to video file
+% % 
+name = sprintf('%s_reg_45views_fdk_z.avi',dataset);
+writevideo (name, FDK,8);
+name = sprintf('%s_reg_45views_fdk_y.avi',dataset);
+writevideo (name, FDKPermuted1, 8);
+name = sprintf('%s_reg_45views_fdk_x.avi',dataset);
+writevideo (name, FDKPermuted2, 8);
+% 
+% %-------------------------Simple CS (No prior)-------------------------------
+% 
+lambda0 = 1;
+Afun = @(z) AConeBeam(z,dim,param);
+Atfun = @(z) AtConeBeam(z,dim,param);
+
+y = proj(:) ;
+% 
+rel_tol = 0.1; % relative target duality gap
+m = size(y,1);
+n = param.nx*param.ny*param.nz;       
+%tic;
[…]

### 2022-02-03 3D_Recon/okra/performWeightedPriorReconstruction.m

@@ -1,0 +1,33 @@
+function [result_weighted_pca,weightsIm] =  performWeightedPriorReconstruction(dataset,y,param,...
+    dim,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,...
+    kk,sliceNumber,outDirectory)
+
+pilotRecons = cell([2,dim]);
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)        
+               fname = sprintf('%s/FDK.mat',outDirectory);
+               data = load(fname);
+               FDK = data.FDK;
+               pilotRecons{1} = FDK;
+        case(1) 
+               lambda_for_method = lambda_for_pilot_recon(2); 
+               lambdaTV = lambda_for_method{1};
+%                lambdaTV = lambda_for_base_method;
+               fname = sprintf('%s/TV_lambdaTV_%.2f.mat',outDirectory,lambdaTV);
+               data = load(fname);
+               TV = data.TV;
+               pilotRecons{2} = TV;
+    end
+end
+
+dim = size(FDK);
+
+
+numCycles = 3;
+[result_weighted_pca,weightsIm] =  weighted_prior(dataset,y,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,param,numCycles,...
+                             pilotRecons,kk,sliceNumber,outDirectory);
+                   
+
+    

### 2022-02-03 3D_Recon/okra/projectPilot_on_EigenSpace_3D.m

@@ -1,0 +1,156 @@
+function P_pilot = projectPilot_on_EigenSpace_3D(dataset,param,pilotOfTestVol,lambda,A_both_functions,method,sliceNumber,outDirectory)
+
+
+if strcmp(dataset,'okra3')
+    dim = size(pilotOfTestVol);
+    templateNos = [4,5,6,7];
+    numTemplates = length(templateNos);
+    numSlices = 123; 
+    sizeOfSlice = [338 338];
+    % resize the  templates--------------------------------------------------------
+    templates = zeros(sizeOfSlice(1)*sizeOfSlice(2)*numSlices,numTemplates);
+
+    
+    % Get the templates and compute their mean----------------------------------------------------------
+
+    for i = 1:numTemplates         
+        if strcmp(method,'FDK')       
+            fname = sprintf('%s/FDK_template_%d.mat',outDirectory,templateNos(i));
+            if(isfile(fname))
+                fprintf('Loading FDK reconstructions of template volumes from existing files\n')
+                data = load(fname);
+                FDK = data.FDK;
+            else
+                fprintf('Computing FDK reconstructions of template volumes\n');
+                name = sprintf('inputs/okra%d_okra6_reg_cropped_450views_fdk.mat',templateNos(i))
+                fileData  = load(name);
+                FDK_high_quality = fileData.FDK;
+                proj = double(CTprojection(FDK_high_quality,param));
+                
+                % START: If raw projections of templates are to be used----------
+                
+%                 projFileName = sprintf('inputs/Preeti_okra%d/projf32_LIN_AP.nc',startTemplateNum + (i-1));
+%                 ncid = netcdf.open(projFileName);
+%                 proj = double(netcdf.getVar(ncid,1));
+%                 netcdf.close(ncid);
+% 
+%                 startz = 1; endz = size(proj,3); % corresponds to each view
+%                 starty = 100; endy = 255;
+%                 startx = 11; endx = size(proj,1)-10-1; 
+% 
+%                 proj = proj(startx:endx, starty: endy, startz:endz);
+%                 selectedProj = 1:10:size(proj,3);
+%                 proj = proj(:,:,selectedProj);
+
+                % END: If raw projections of templates are to be used----------
+
+                FDK = okra_FDK(proj,param,dim);
+                save(fname,'FDK');
+            end
+            temp = FDK - min(FDK(:));
+            temp = temp./max(temp(:));
+            templates(:,i) = temp(:);
[…]

### 2022-02-03 3D_Recon/okra/rmseVol.m

@@ -1,0 +1,14 @@
+function [rel_mseVal,rmseval] = rmseVol(resultVol,testVol)
+
+% meanSqError = mean((resultVol - testVol).^2,3);
+% meanSqError = mean2(meanSqError);
+% msi = mean(testVol.^2,3);
+% msi = mean2(msi);
+% 
+% rmseVal = sqrt(meanSqError)/sqrt(msi);
+
+meanSqError = mean((resultVol(:) - testVol(:)).^2);
+msi = mean(testVol(:).^2);
+
+rel_mseVal = sqrt(meanSqError)/sqrt(msi);
+rmseval = sqrt(meanSqError);

### 2022-02-03 3D_Recon/okra/store_video.m

@@ -1,0 +1,18 @@
+function store_video(data,fileName,outDirectory,dataset)
+
+data = data - min(data(:));
+data = data./max(data(:));
+dataPermuted1 = permute(data,[3 1 2]);
+dataPermuted2 = permute(data,[3 2 1]);
+
+name = sprintf('%s/%s_%s.mat',outDirectory,dataset,fileName);
+save(name,'data');
+name = sprintf('%s/%s_%s_z.avi',outDirectory,dataset,fileName);
+writevideo (name, data,8);
+name = sprintf('%s/%s_%s_y.avi',outDirectory,dataset,fileName);
+writevideo (name, dataPermuted1, 8);
+name = sprintf('%s/%s_%s_x.avi',outDirectory,dataset,fileName);
+writevideo (name, dataPermuted2, 8);
+
+
+

### 2022-02-03 3D_Recon/okra/videos_okra.m

@@ -1,0 +1,38 @@
+close all;
+clear all;
+clc;
+
+
+outDirectory = 'results/TV_with_weighted_prior/30_views';
+dataset = 'okra3';
+
+file = load('inputs/okra3_cropped_450views_fdk.mat');
+testVol = file.FDK;
+testVol = testVol(:,:,1:60);
+testVol = testVol - min(testVol(:));
+testVol = testVol./max(testVol(:));
+name = sprintf('%s/FDK.mat',outDirectory);
+file = load(name);
+fdkVol = file.FDK;
+fdkVol = fdkVol(:,:,1:60);
+fdkVol = fdkVol - min(fdkVol(:));
+fdkVol = fdkVol./max(fdkVol(:));
+name = sprintf('%s/TV_lambdaTV_0.45.mat',outDirectory);
+file = load(name);
+tvVol = file.TV;
+tvVol = tvVol(:,:,1:60);
+tvVol = tvVol - min(tvVol(:));
+tvVol = tvVol./max(tvVol(:));
+name = sprintf('%s/weighted_prior_kk_1_lambda_prior_0.500000.mat',outDirectory);
+file = load(name);
+weightedPriorVol = file.result_weighted_pca;
+weightedPriorVol = weightedPriorVol(:,:,1:60);
+weightedPriorVol = weightedPriorVol - min(weightedPriorVol(:));
+weightedPriorVol = weightedPriorVol./max(weightedPriorVol(:));
+
+
+
+name = 'all_results';
+all_results = [testVol fdkVol tvVol weightedPriorVol];
+store_video(all_results,name,outDirectory,dataset);
+    

### 2022-02-03 3D_Recon/okra/visualizeResults_with_TV.m

@@ -1,0 +1,47 @@
+clear all;
+close all;
+
+output_dir = 'results/TV_with_weighted_prior/45_views_with_registered_templates';
+name = sprintf('%s/okra3_testVol.mat',output_dir);
+f1 = load(name);
+
+name = sprintf('%s/FDK.mat',output_dir);
+f3 = load(name);
+
+name = sprintf('%s/TV_lambdaTV_0.50.mat',output_dir);
+f4 = load(name);
+
+name = sprintf('%s/weighted_prior_kk_1_lambda_prior_0.400000.mat',output_dir);
+f6 = load(name);
+
+
+
+%-------------store the images-------------
+
+fdkIm = f1.data(:,:,30);
+ImCropped = fdkIm(:,110:end-100);
+ImCropped = ImCropped - min(ImCropped(:));
+ImCropped = ImCropped./max(ImCropped(:));
+imwrite(ImCropped,'test_cropped.png');
+
+
+fdkIm = f3.FDK(:,:,30);
+ImCropped = fdkIm(:,110:end-100);
+ImCropped = ImCropped - min(ImCropped(:));
+ImCropped = ImCropped./max(ImCropped(:));
+imwrite(ImCropped,'fdk_cropped.png');
+
+
+tvIm = f4.TV(:,:,30);
+ImCropped = tvIm(:,110:end-100);
+ImCropped = ImCropped - min(ImCropped(:));
+ImCropped = ImCropped./max(ImCropped(:));
+imwrite(ImCropped,'TV_cropped.png');
+
+
+prior_weightedIm = f6.result_weighted_pca(:,:,30);
+ImCropped = prior_weightedIm(:,110:end-100);
+ImCropped = ImCropped - min(ImCropped(:));
+ImCropped = ImCropped./max(ImCropped(:));
+imwrite(ImCropped,'prior_weighted_cropped.png');
+

### 2022-02-03 3D_Recon/okra/weighted_prior.m

@@ -1,0 +1,140 @@
+function [result_weighted_prior,W] =  weighted_prior(dataset,y_given,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,param,numCycles,...
+                                 pilotRecons,kk,sliceNumber,outDirectory)
+
+fname = sprintf('%s/EigenSpace_%s_hole.mat',outDirectory,'okra'); 
+es = load(fname);
+eigenVecs = es.eigenVecs;
+meanTemplateOriginal = es.meanTemplate;
+m = size(y_given,1);
+A_both_functions =@(z,mode) systemFunction(z,mode,dim,param,m);  
+
+%%  --------------------------construct the weight map---------------------------------------
+
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)
+            lambda = 1; % dummy value
+            FDK = pilotRecons{1};
+            FDK = FDK - min(FDK(:));
+            FDK = FDK./max(FDK(:));	
+            method_name = 'FDK';
+            P_FDK = projectPilot_on_EigenSpace_3D(dataset,param,FDK,lambda,A_both_functions,method_name,sliceNumber,outDirectory);
+            fname = sprintf('%s/ProjectedTestFDK.mat',outDirectory);
+            save(fname,'P_FDK');
+            name = sprintf('%s/FDK_P_FDK.png',outDirectory);
+            temp = [FDK(:,:,sliceNumber) P_FDK(:,:,sliceNumber)];
+            %figure;imshow(temp,[]);
+            temp = temp - min(temp(:));
+            temp = temp/max(temp(:));
+            imwrite(temp,name);
+        case(1)
+            lambda_for_method = lambda_for_pilot_recon(2); 
+            lambda_TV = lambda_for_method{1};
+            TV = pilotRecons{2};
+            TV = TV - min(TV(:));
+            TV = TV./max(TV(:));
+            method_name = 'TV';
+            P_TV = projectPilot_on_EigenSpace_3D(dataset,param,TV,lambda_TV,A_both_functions,method_name,sliceNumber,outDirectory);
+            fname = sprintf('%s/ProjectedTestTV.mat',outDirectory);
+            save(fname,'P_TV');
+            name = sprintf('%s/TV_P_TV.png',outDirectory);
[…]

### 2022-02-05 3D_Recon/okra/compute_quant_results.m
Cleaned scripts for Okra

@@ -7,48 +7,16 @@ dataset ='okra3';
 
 file = load(sprintf('%s/okra3_testVol.mat',outDirectory));
 testVol = double(file.data);
-% testVol = testVol(:,110:end-100,:);
 file = load(sprintf('%s/FDK.mat',outDirectory));
 fdkVol = double(file.FDK);
-% fdkVol = fdkVol(:,110:end-100,:);
 file = load(sprintf('%s/TV_lambdaTV_0.45.mat',outDirectory));
 tvVol = file.TV;
-% tvVol = tvVol(:,110:end-100,:);
 file = load(sprintf('%s/weighted_prior_kk_1_lambda_prior_0.500000.mat',outDirectory));
 weightedPriorVol = file.result_weighted_pca;
-% weightedPriorVol = weightedPriorVol(:,110:end-100,:);
-
-
-
-
-
-% testVol = testVol - min(testVol(:));
-% testVol  = testVol./max(testVol(:));
-% fdkVol = fdkVol - min(fdkVol(:));
-% fdkVol = fdkVol./max(fdkVol(:));
-% tvVol = tvVol - min(tvVol(:));
-% tvVol = tvVol./max(tvVol(:));
-% weightedPriorVol = weightedPriorVol - min(weightedPriorVol(:));
-% weightedPriorVol = weightedPriorVol./max(weightedPriorVol(:));  
-
-
-% leaveSlices = 0;
-% ssim_fdk = ssim(fdkVol(:,:,end-leaveSlices),testVol(:,:,end-leaveSlices))
-% ssim_tv = ssim(tvVol(:,:,end-leaveSlices),testVol(:,:,end-leaveSlices))
-% ssim_wightedPrior = ssim(weightedPriorVol(:,:,end-leaveSlices),testVol(:,:,end-leaveSlices))
-% 
-% relRMSE_fdk = rmseVol(fdkVol,testVol)
-% relRMSE_tv = rmseVol(tvVol,testVol)
-% relRMSE_weightedPrior = rmseVol(weightedPriorVol,testVol)
-% 
-% ssim_fdk_1 = ssim(fdkVol(:,:,end-leaveSlices),testVol(:,:,end-leaveSlices),'Exponent',[0.1 0.2 0.7])
[…]

### 2022-02-05 3D_Recon/okra/okra_CS.m

@@ -1,13 +1,0 @@
-function CS = okra_CS(proj,param,dim,lambda0,rel_tol)
-
-Afun = @(z) AConeBeam(z,dim,param);
-Atfun = @(z) AtConeBeam(z,dim,param);
-
-y = proj(:) ;
-
-m = size(y,1);
-n = param.nx*param.ny*param.nz;       
-
-[x_hat,status,historyNoPrior]=l1_ls_modified(Afun,Atfun,m,n,y,lambda0,rel_tol);
-output = reshape(x_hat,[param.nx param.ny param.nz]);
-CS = mirt_idctn(output);

### 2022-02-05 3D_Recon/okra/okra_entire_dataset.m

@@ -1,39 +1,0 @@
-close all;
-clear all;
-
-templateNos = [1,2,3,4,5,6, 7];
-numTemplates = length(templateNos);
-numSlices = 123; % number of slices in a volume;
-sizeOfSlice = [338 338];
-
-
-volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
-
-% Read the templates in 3D format-------------------
-
-for i = 1:numTemplates  
-   name = sprintf('inputs/okra%d_okra6_reg_cropped_450views_fdk.mat',templateNos(i)) ;
-   fileData = load(name);
-   volumes(:,:,:,i) = fileData.FDK;
-   
-    temp = volumes(:,:,30,i);
-    fname = sprintf('slice%d.mat',i);
-    save(fname,'temp');    
-    temp = temp - min(temp(:));
-    temp = temp./max(temp(:));    
-    name = sprintf('slice%d.png',i);
-    imwrite(temp,name);
-end
- 
-allVolumes = [volumes(:,:,1:60,1) volumes(:,:,1:60,2) volumes(:,:,1:60,3) volumes(:,:,1:60,4) volumes(:,:,1:60,5) volumes(:,:,1:60,6) volumes(:,:,1:60,7)];
-allVolumes = allVolumes - min(allVolumes(:));
-allVolumes = allVolumes./max(allVolumes(:));
-name = 'entire_dataset';
-dataset ='okra';
-store_video(allVolumes,name,'inputs',dataset);
-tempTestImg = [volumes(:,:,30,1) volumes(:,:,30,2) volumes(:,:,30,3) volumes(:,:,30,4) volumes(:,:,30,5) volumes(:,:,30,6) volumes(:,:,30,7) ];
-tempTestImg = tempTestImg - min(tempTestImg(:));
-tempTestImg = tempTestImg./max(tempTestImg(:));
-imwrite(tempTestImg,'inputs/okra_entire_dataset.png');
-
-

### 2022-02-05 3D_Recon/okra/okra_fdk_presentation.m

@@ -1,88 +1,0 @@
-close all;
-clear all;
-
-dataDir = dir('../data/okra/');
-numOkras = size(dataDir,1)-2;
-outDirectory = 'inputs/presentation';
-mkdir(outDirectory);
-
-for i = 1:1;%numOkras
-    
-    dataDir(i+2).name
-    projFileName = sprintf('../data/okra/Preeti_okra%d/projf32_LIN_AP.nc',i);
-    ncid = netcdf.open(projFileName);
-    proj = double(netcdf.getVar(ncid,1));
-    netcdf.close(ncid);
-    %------------------------------------------
-
-    startz = 1; endz = size(proj,3); % corresponds to each view
-    starty = 100; endy = 255;
-    startx = 11; endx = size(proj,1)-10-1; 
-
-    %-------------------------------
-
-    proj = proj(startx:endx, starty: endy, startz:endz); 
-    angStepSize = 0.8;
-
-
-%     mask = find(proj~=-1);
-%     minimum = min(proj(mask));
-%     proj(mask) = proj(mask) - minimum;
-%     proj(proj==-1) = 0;
-%     proj = proj./max(proj(:));
-%     name = sprintf('okra%d_proj_cropped.avi',i);
-%     writevideo (name, proj, 8);
-
-%     proj1 = zeros([168 78 size(proj,3)]);
-%     for i = 1:size(proj(:,:,3))
-%         img = proj(:,:,i);
-%         img = imresize(img,[168 78]);
-%         proj1(:,:,i) = img;
-%     end
-%     proj = proj1;
-     size(proj)
-    %----------------------------Filtered Back-projection---------------------------
-
-    ParamSetting_okra_pca(angStepSize)
-    load('parameters_okra_pca.mat');
-
-    proj_filtered = filtering(proj,param);
-    FDK_original = CTbackprojection(proj_filtered, param);
-    
-    name = sprintf('%s/okra%d_cropped_450views_fdk.mat',outDirectory,i);
-    save(name,'FDK_original');
-    
-    FDK = FDK_original(:,:,1:end-80);
-    
-    FDK = FDK - min(FDK(:));
-    FDK = FDK./max(FDK(:));
-    FDKPermuted1 = permute(FDK,[3 1 2]);
-    FDKPermuted2 = permute(FDK,[3 2 1]);    
-    
-    % write to video file
-    
[…]

### 2022-02-05 3D_Recon/okra/okra_hole_pca.m

@@ -1,281 +1,0 @@
-close all;
-clear all;
-dataset = 'okra3';
-
-projFileName = sprintf('../data/okra/Preeti_%s/projf32_LIN_AP.nc',dataset);
-ncid = netcdf.open(projFileName);
-proj = double(netcdf.getVar(ncid,1));
-netcdf.close(ncid);
-%------------------------------------------
-  
-startz = 1; endz = size(proj,3); % corresponds to each view
-starty = 100; endy = 255;%size(proj,2)-1;
-startx = 11; endx = size(proj,1)-10-1; 
-
-proj = proj(startx:endx, starty: endy, startz:endz);
-selectedProj = 1:10:size(proj,3);
-proj = proj(:,:,selectedProj);
-angStepSize = 8;
-ParamSetting_okra_pca(angStepSize)
-load('parameters_okra_pca.mat');
-
-dim = [param.nx param.ny param.nz]; 
-%----------------------------Filtered Back-projection---------------------------
-
-proj_filtered = filtering(proj,param);
-FDK = CTbackprojection(proj_filtered, param);
-
-FDK = FDK - min(FDK(:));
-FDK= FDK./max(FDK(:));
-FDKPermuted1 = permute(FDK,[3 1 2]);
-FDKPermuted2 = permute(FDK,[3 2 1]);
-
-name = sprintf('%s_reg_45views_fdk.mat',dataset);
-% FDKfile = load(name);
-% FDK = FDKfile.FDK;
-save(name,'FDK');
-% % 
-% % % write to video file
-% % 
-name = sprintf('%s_reg_45views_fdk_z.avi',dataset);
-writevideo (name, FDK,8);
-name = sprintf('%s_reg_45views_fdk_y.avi',dataset);
-writevideo (name, FDKPermuted1, 8);
-name = sprintf('%s_reg_45views_fdk_x.avi',dataset);
-writevideo (name, FDKPermuted2, 8);
-% 
-% %-------------------------Simple CS (No prior)-------------------------------
-% 
-lambda0 = 1;
-Afun = @(z) AConeBeam(z,dim,param);
-Atfun = @(z) AtConeBeam(z,dim,param);
-
-y = proj(:) ;
-% 
-rel_tol = 0.1; % relative target duality gap
-m = size(y,1);
-n = param.nx*param.ny*param.nz;       
-%tic;
[…]

### 2022-02-05 3D_Recon/okra/videos_okra.m

@@ -1,38 +1,0 @@
-close all;
-clear all;
-clc;
-
-
-outDirectory = 'results/TV_with_weighted_prior/30_views';
-dataset = 'okra3';
-
-file = load('inputs/okra3_cropped_450views_fdk.mat');
-testVol = file.FDK;
-testVol = testVol(:,:,1:60);
-testVol = testVol - min(testVol(:));
-testVol = testVol./max(testVol(:));
-name = sprintf('%s/FDK.mat',outDirectory);
-file = load(name);
-fdkVol = file.FDK;
-fdkVol = fdkVol(:,:,1:60);
-fdkVol = fdkVol - min(fdkVol(:));
-fdkVol = fdkVol./max(fdkVol(:));
-name = sprintf('%s/TV_lambdaTV_0.45.mat',outDirectory);
-file = load(name);
-tvVol = file.TV;
-tvVol = tvVol(:,:,1:60);
-tvVol = tvVol - min(tvVol(:));
-tvVol = tvVol./max(tvVol(:));
-name = sprintf('%s/weighted_prior_kk_1_lambda_prior_0.500000.mat',outDirectory);
-file = load(name);
-weightedPriorVol = file.result_weighted_pca;
-weightedPriorVol = weightedPriorVol(:,:,1:60);
-weightedPriorVol = weightedPriorVol - min(weightedPriorVol(:));
-weightedPriorVol = weightedPriorVol./max(weightedPriorVol(:));
-
-
-
-name = 'all_results';
-all_results = [testVol fdkVol tvVol weightedPriorVol];
-store_video(all_results,name,outDirectory,dataset);
-    

### 2022-02-05 3D_Recon/okra/visualizeResults_with_TV.m

@@ -1,47 +1,0 @@
-clear all;
-close all;
-
-output_dir = 'results/TV_with_weighted_prior/45_views_with_registered_templates';
-name = sprintf('%s/okra3_testVol.mat',output_dir);
-f1 = load(name);
-
-name = sprintf('%s/FDK.mat',output_dir);
-f3 = load(name);
-
-name = sprintf('%s/TV_lambdaTV_0.50.mat',output_dir);
-f4 = load(name);
-
-name = sprintf('%s/weighted_prior_kk_1_lambda_prior_0.400000.mat',output_dir);
-f6 = load(name);
-
-
-
-%-------------store the images-------------
-
-fdkIm = f1.data(:,:,30);
-ImCropped = fdkIm(:,110:end-100);
-ImCropped = ImCropped - min(ImCropped(:));
-ImCropped = ImCropped./max(ImCropped(:));
-imwrite(ImCropped,'test_cropped.png');
-
-
-fdkIm = f3.FDK(:,:,30);
-ImCropped = fdkIm(:,110:end-100);
-ImCropped = ImCropped - min(ImCropped(:));
-ImCropped = ImCropped./max(ImCropped(:));
-imwrite(ImCropped,'fdk_cropped.png');
-
-
-tvIm = f4.TV(:,:,30);
-ImCropped = tvIm(:,110:end-100);
-ImCropped = ImCropped - min(ImCropped(:));
-ImCropped = ImCropped./max(ImCropped(:));
-imwrite(ImCropped,'TV_cropped.png');
-
-
-prior_weightedIm = f6.result_weighted_pca(:,:,30);
-ImCropped = prior_weightedIm(:,110:end-100);
-ImCropped = ImCropped - min(ImCropped(:));
-ImCropped = ImCropped./max(ImCropped(:));
-imwrite(ImCropped,'prior_weighted_cropped.png');
-

### 2022-02-05 3D_Recon/okra/rmseVol.m
Cleaned scripts for Okra

@@ -1,12 +1,5 @@
 function [rel_mseVal,rmseval] = rmseVol(resultVol,testVol)
 
-% meanSqError = mean((resultVol - testVol).^2,3);
-% meanSqError = mean2(meanSqError);
-% msi = mean(testVol.^2,3);
-% msi = mean2(msi);
-% 
-% rmseVal = sqrt(meanSqError)/sqrt(msi);
-
 meanSqError = mean((resultVol(:) - testVol(:)).^2);
 msi = mean(testVol(:).^2);
 

### 2022-02-05 3D_Recon/potato/ParamSetting_potato_pca.m
Added potato recon script files

@@ -1,0 +1,81 @@
+%% Parameter setting %%
+
+% % % % % % Confirm your parameters % % % % % % %
+function ParamSetting_potato_pca(angStepSize,outDirectory)
+
+param.nx = 150;
+param.ny = 150;
+param.nz = 100;
+
+param.sx = 23.8;
+param.sy = 23.8;
+param.sz = 15.84; 
+
+%The real detector panel pixel density (number of pixels)
+param.nu = 150;	% number of pixels
+param.nv = 150;
+
+% Detector setting (real size)
+param.su = 150*0.15*4;	% mm (real size) % subsampling fector of 4
+param.sv = 150*0.15*4;     % mm
+
+% X-ray source and detector setting
+param.DSD = 261.8;    %  Distance source to detector 
+param.DSO = 70;	%  X-ray source to object axis distance
+
+% angle setting
+param.dir = 1;   % gantry rotating direction (clock wise/ counter clockwise)
+param.dang = angStepSize; % angular step size (deg)
+param.deg =  0:param.dang:359.9; % you can change
+param.deg = param.deg*param.dir;
+param.nProj = length(param.deg);
+
+param.parker = 1; % data with 360 deg -> param.parker = 0 , data less than 360 deg -> param.parker=1 
+
+% % % % % % Confirm your parameters % % % % % % %
+ 
+% filter='ram-lak','cosine', 'hamming', 'hann' 
+param.filter='ram-lak'; % high pass filter
+
+param.dx = param.sx/param.nx; % single voxel size
+param.dy = param.sy/param.ny;
+param.dz = param.sz/param.nz;
+param.du = param.su/param.nu;
+param.dv = param.sv/param.nv;
+
+param.off_u = 0; param.off_v = 0; % detector rotation shift (real size)
+
+% % % Geometry calculation % % %
+param.xs = [-(param.nx-1)/2:1:(param.nx-1)/2]*param.dx;
+param.ys = [-(param.ny-1)/2:1:(param.ny-1)/2]*param.dy;
+param.zs = [-(param.nz-1)/2:1:(param.nz-1)/2]*param.dz;
+
+param.us = (-(param.nu-1)/2:1:(param.nu-1)/2)*param.du + param.off_u;
+param.vs = (-(param.nv-1)/2:1:(param.nv-1)/2)*param.dv + param.off_v;
+
+param.interptype = 'linear'; % 'linear', 'nearest'
+
+% % % % % % Confirm your parameters % % % % % % %
[…]

### 2022-02-05 3D_Recon/potato/compute_quant_results.m

@@ -1,0 +1,140 @@
+clear all;
+clc;
+close all;
+outDirectory = 'results/TV_with_weighted_prior/18_views';
+
+file = load(sprintf('%s/potato6_testVol.mat',outDirectory));
+testVol = double(file.data);
+file = load(sprintf('%s/FDK.mat',outDirectory));
+fdkVol = double(file.FDK);
+file = load(sprintf('%s/TV_lambdaTV_0.10.mat',outDirectory));
+tvVol = file.TV;
+file = load(sprintf('%s/weighted_prior_kk_1_lambda_prior_0.220000.mat',outDirectory));
+weightedPriorVol = file.result_weighted_pca;
+
+
+roi1_col = 55:55+15; % red RoI
+roi1_row = 78:78+15;
+roi2_col = 30:30+50;% green RoI
+roi2_row = 60:60+35;
+roi3_col = 20:20+80;
+roi3_row = 40:40 +70;
+% roi3_col = 130:145;
+% roi3_row = 140:180;
+roi1_frames = 30:37;
+roi2_frames = 30:37;
+roi3_frames = 30:37;
+
+
+exponent_vector = [0.1 0.2 0.7];
+ %exponent_vector = [1 1 1];
+
+roi1_testVol = testVol(roi1_row,roi1_col,roi1_frames);
+roi1_fbp = fdkVol(roi1_row,roi1_col,roi1_frames);
+roi1_tv = tvVol(roi1_row,roi1_col,roi1_frames);
+roi1_weighted_pca = weightedPriorVol(roi1_row,roi1_col,roi1_frames);
+
+
+roi1_testVol = roi1_testVol - min(roi1_testVol(:));
+roi1_testVol  = roi1_testVol./max(roi1_testVol(:));
+roi1_fbp = roi1_fbp - min(roi1_fbp(:));
+roi1_fbp = roi1_fbp./max(roi1_fbp(:));
+roi1_tv = roi1_tv - min(roi1_tv(:));
+roi1_tv = roi1_tv./max(roi1_tv(:));
+roi1_weighted_pca = roi1_weighted_pca - min(roi1_weighted_pca(:));
+roi1_weighted_pca = roi1_weighted_pca./max(roi1_weighted_pca(:));  
+
+ssim1_fbp = ssim(roi1_fbp,roi1_testVol,'Exponent',exponent_vector);
[…]

### 2022-02-05 3D_Recon/potato/genEigenSpacePotato_hole.m

@@ -1,0 +1,106 @@
+function genEigenSpacePotato_hole(templateNos,outDirectory)
+
+numTemplates = length(templateNos);
+numSlices = 100;
+sizeOfSlice = [150 150];
+
+
+volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+% Read the templates in 3D format-------------------
+
+for i = 1:numTemplates  
+   name = sprintf('inputs/potato%d_cropped_900views_fdk.mat',templateNos(i)) ;
+   fileData = load(name);
+   volumes(:,:,:,i) = fileData.FDK;
+   image = volumes(:,:,30,i);
+   image = image - min(image(:));
+   image = image./max(image(:));
+   name = sprintf('inputs/template_%d.png',i);
+   imwrite(image,name);
+end
+ 
+% store templates and test together------------------
+name = sprintf('inputs/potato%d_cropped_900views_fdk.mat',6) ;
+fileDataTest = load(name);
+testVol = fileDataTest.FDK;
+image = testVol(:,:,30);
+image = image - min(image(:));
+image = image./max(image(:));
+name = 'inputs/test.png';
+imwrite(image,name);
+
+% fh = figure;imshow(image); hold on;
+% rectangle('Position',[55, 78,15 ,15],'EdgeColor','r','LineWidth',2);
+% name = sprintf('inputs/test.png');
+% f=getframe; imwrite(f.cdata,name);
+
+
+all_templates = [volumes(:,:,:,1) volumes(:,:,:,2) volumes(:,:,:,3) testVol];
+all_templates = all_templates - min(all_templates(:));
+all_templates = all_templates./max(all_templates(:));
+name = 'templates_and_test';
+dataset ='potato';
+store_video(all_templates,name,'inputs',dataset);
+tempTestImg = [volumes(:,:,30,1) volumes(:,:,30,2) volumes(:,:,30,3) testVol(:,:,30)];
+tempTestImg = tempTestImg - min(tempTestImg(:));
+tempTestImg = tempTestImg./max(tempTestImg(:));
+imwrite(tempTestImg,'inputs/template_test_image.png');
+% resize the
+% templates--------------------------------------------------------
+templates = zeros(sizeOfSlice(1)*sizeOfSlice(2)*numSlices,numTemplates);
+
+for i = 1:numTemplates   
+   temp = volumes(:,:,:,i);
+   temp = temp(:);   
+   templates(:,i) = temp;
+end
+
[…]

### 2022-02-05 3D_Recon/potato/main.m

@@ -1,0 +1,176 @@
+% potato_few_views
+
+dataset = 'potato6';
+outDirectory = ('results/TV_with_weighted_prior/18_views/');
+mkdir(outDirectory);
+projFolderName =  sprintf('Preeti_%s/projf32_LIN_AP_nc',dataset);
+dirInfo = dir(projFolderName);
+sliceNumber = 30;
+lambda_prior_list = [0.1 0.2 0.22 0.25 0.3 0.4 1];
+
+%% -------------Read Projection data---------------------------
+
+for j = 3:size(dirInfo,1)
+    fileName = dirInfo(j).name;
+    filePath = sprintf('%s/%s',projFolderName,fileName);
+    ncid = netcdf.open(filePath);
+    projections = double(netcdf.getVar(ncid,1));
+    if j==3
+        proj = projections;
+    else
+        proj = cat(3,proj,projections);                  
+    end
+    netcdf.close(ncid);
+end
+
+  
+startz = 1; endz = size(proj,3); % corresponds to each view
+starty = 121; endy = size(proj,2)-121+1;
+startx = 125; endx = size(proj,1)-125+1; 
+
+proj = proj(startx:endx, starty: endy, startz:endz); 
+%selectedProj = 1:20:size(proj,3);
+selectedProj = 1:50:size(proj,3);
+proj = proj(:,:,selectedProj);
+proj1 = zeros(150,150,size(proj,3));
+for i = 1:size(proj,3)
+    image = imresize(proj(:,:,i),[150 150]);
+    proj1(:,:,i) = image;
+end
+proj = proj1;
+angStepSize = 20;
+numAngles = length(selectedProj);
+ParamSetting_potato_pca(angStepSize,outDirectory)
+name = sprintf('%s/parameters_potato_pca.mat',outDirectory);
+load(name);
+
+dim = [param.nx param.ny param.nz]; 
+
+sizeProj = size(proj);
+save('ProjectionSize.mat','sizeProj');
+
+
+%% --------generate Ground truth for final comparison------------------
+
+name = sprintf('inputs/%s_cropped_900views_fdk',dataset);
+testVolFile = load(name);
+testVol = testVolFile.FDK;
+name = 'testVol';
+store_video(testVol,name,outDirectory,dataset);
+
+name = sprintf('%s/testVol.png',outDirectory);
+temp = testVol(:,:,sliceNumber);
[…]

### 2022-02-05 3D_Recon/potato/performWeightedPriorReconstruction.m

@@ -1,0 +1,31 @@
+function [result_weighted_pca,weightsIm] =  performWeightedPriorReconstruction(dataset,y,param,...
+    dim,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,...
+    kk,sliceNumber,outDirectory)
+
+pilotRecons = cell([2,dim]);
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)        
+               fname = sprintf('%s/FDK.mat',outDirectory);
+               data = load(fname);
+               FDK = data.FDK;
+               pilotRecons{1} = FDK;
+        case(1) 
+               lambdaTV = lambda_for_pilot_recon{2};
+               fname = sprintf('%s/TV_lambdaTV_%.2f.mat',outDirectory,lambdaTV);
+               data = load(fname);
+               TV = data.TV;
+               pilotRecons{2} = TV;
+    end
+end
+
+dim = size(FDK);
+
+
+numCycles = 5;%5;
+[result_weighted_pca,weightsIm] =  weighted_prior(dataset,y,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,param,numCycles,...
+                             pilotRecons,kk,sliceNumber,outDirectory);
+                   
+
+    

### 2022-02-05 3D_Recon/potato/plain_TV.m

@@ -1,0 +1,23 @@
+function result_plain_TV = plain_TV(y,dim,lambdaTV,A_both_functions)
+
+    
+addpath('TVReg-master/');
+
+dims=[dim(1) dim(2) dim(3)];
+opt_ref.epsb_rel = 1e-4;
+opt_ref.k_max    = 20000;
+opt_ref.verbose  = 1;
+tau = 0.0001;
+% Specify nonnegativity constraints
+constraint.type = 2;
+constraint.c    = 0*ones(prod(dims),1);
+constraint.d    = 1*ones(prod(dims),1);
+tic;
+[x_ref fxk_ref hxk_ref gxk_ref fxkl_ref info_ref] = ...
+tvreg_upn(A_both_functions,y,lambdaTV,tau,dims,constraint,opt_ref);
+toc;
+result_plain_TV = reshape(x_ref,[dim(1) dim(2) dim(3)]);
+  
+ 
+    
+end

### 2022-02-05 3D_Recon/potato/potato_FDK.m

@@ -1,0 +1,4 @@
+function FDK = potato_FDK(proj,param,dim)
+
+proj_filtered = filtering(proj,param);
+FDK = CTbackprojection(proj_filtered, param);

### 2022-02-05 3D_Recon/potato/projectPilot_on_EigenSpace_3D.m

@@ -1,0 +1,169 @@
+function P_pilot = projectPilot_on_EigenSpace_3D(dataset,param,pilotOfTestVol,lambda,A_both_functions,method,sliceNumber,outDirectory)
+
+
+
+if strcmp(dataset,'potato6')
+    dim = size(pilotOfTestVol);
+    templateNos = [1,3,4];
+    numTemplates = length(templateNos);
+    numSlices = 100;
+    sizeOfSlice = [150 150];
+    % resize the  templates--------------------------------------------------------
+    templates = zeros(sizeOfSlice(1)*sizeOfSlice(2)*numSlices,numTemplates);
+    
+    % Get the templates and compute their mean----------------------------------------------------------
+
+    for i = 1:numTemplates         
+        if strcmp(method,'FDK')       
+            fname = sprintf('%s/FDK_template_%d.mat',outDirectory,templateNos(i));
+            if(isfile(fname))
+                fprintf('Loading FDK reconstructions of template volumes from existing files\n')
+                data = load(fname);
+                FDK = data.FDK;
+            else
+                fprintf('Computing FDK reconstructions of template volumes\n');
+                projFolderName =  sprintf('Preeti_potato%d/projf32_LIN_AP_nc',templateNos(i))
+                dirInfo = dir(projFolderName);
+                for j = 3:size(dirInfo,1)
+                    fileName = dirInfo(j).name;
+                    filePath = sprintf('%s/%s',projFolderName,fileName);
+                    ncid = netcdf.open(filePath);
+                    projections = double(netcdf.getVar(ncid,1));
+                    if j==3
+                        proj = projections;
+                    else
+                        proj = cat(3,proj,projections);                  
+                    end
+                    netcdf.close(ncid);
+                end
+                %------------------------------------------
+
+                startz = 1; endz = size(proj,3); % corresponds to each view
+                starty = 121; endy = size(proj,2)-121+1;
+                startx = 125; endx = size(proj,1)-125+1; 
+
+                proj = proj(startx:endx, starty: endy, startz:endz); 
+                selectedProj = 1:50:size(proj,3);
+                proj = proj(:,:,selectedProj);
+                proj1 = zeros(150,150,size(proj,3));
+                for ii = 1:size(proj,3)
+                    image = imresize(proj(:,:,ii),[150 150]);
+                    proj1(:,:,ii) = image;
+                end
+                proj = proj1;
[…]

### 2022-02-05 3D_Recon/potato/store_video.m

@@ -1,0 +1,13 @@
+function store_video(data,fileName,outDirectory,dataset)
+
+data = data - min(data(:));
+data = data./max(data(:));
+
+name = sprintf('%s/%s_%s.mat',outDirectory,dataset,fileName);
+save(name,'data');
+name = sprintf('%s/%s_%s_z.avi',outDirectory,dataset,fileName);
+writevideo (name, data,8);
+
+
+
+

### 2022-02-05 3D_Recon/potato/weighted_prior.m

@@ -1,0 +1,159 @@
+function [result_weighted_prior,W] =  weighted_prior(dataset,y_given,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,param,numCycles,...
+                                 pilotRecons,kk,sliceNumber,outDirectory)
+
+fname = sprintf('%s/EigenSpace_%s_hole.mat',outDirectory,'potato'); 
+es = load(fname);
+eigenVecs = es.eigenVecs;
+meanTemplateOriginal = es.meanTemplate;
+m = size(y_given,1);
+A_both_functions =@(z,mode) systemFunction(z,mode,dim,param,m);  
+
+%%  --------------------------construct the weight map---------------------------------------
+
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)
+            lambda = 1; % dummy value
+            FDK = pilotRecons{1};
+            FDK = FDK - min(FDK(:));
+            FDK = FDK./max(FDK(:));	
+            method_name = 'FDK';
+            P_FDK = projectPilot_on_EigenSpace_3D(dataset,param,FDK,lambda,A_both_functions,method_name,sliceNumber,outDirectory);
+            fname = sprintf('%s/ProjectedTestFDK.mat',outDirectory);
+            save(fname,'P_FDK');
+            name = sprintf('%s/FDK_P_FDK.png',outDirectory);
+            temp = [FDK(:,:,sliceNumber) P_FDK(:,:,sliceNumber)];
+            %figure;imshow(temp,[]);
+            temp = temp - min(temp(:));
+            temp = temp/max(temp(:));
+            imwrite(temp,name);
+        case(1)
+            lambda_for_method = lambda_for_pilot_recon(2); 
+            lambda_TV = lambda_for_method{1};
+            TV = pilotRecons{2};
+            TV = TV - min(TV(:));
+            TV = TV./max(TV(:));
+            method_name = 'TV';
+            P_TV = projectPilot_on_EigenSpace_3D(dataset,param,TV,lambda_TV,A_both_functions,method_name,sliceNumber,outDirectory);
+            fname = sprintf('%s/ProjectedTestTV.mat',outDirectory);
+            save(fname,'P_TV');
+            name = sprintf('%s/TV_P_TV.png',outDirectory);
[…]

### 2022-02-05 3D_Recon/potato/main.m
Added potato projection-data

@@ -3,7 +3,7 @@
 dataset = 'potato6';
 outDirectory = ('results/TV_with_weighted_prior/18_views/');
 mkdir(outDirectory);
-projFolderName =  sprintf('Preeti_%s/projf32_LIN_AP_nc',dataset);
+projFolderName =  sprintf('inputs/%s/projf32_LIN_AP_nc',dataset);
 dirInfo = dir(projFolderName);
 sliceNumber = 30;
 lambda_prior_list = [0.1 0.2 0.22 0.25 0.3 0.4 1];

### 2022-02-05 3D_Recon/potato/projectPilot_on_EigenSpace_3D.m

@@ -22,7 +22,7 @@ if strcmp(dataset,'potato6')
                 FDK = data.FDK;
             else
                 fprintf('Computing FDK reconstructions of template volumes\n');
-                projFolderName =  sprintf('Preeti_potato%d/projf32_LIN_AP_nc',templateNos(i))
+                projFolderName =  sprintf('inputs/potato%d/projf32_LIN_AP_nc',templateNos(i))
                 dirInfo = dir(projFolderName);
                 for j = 3:size(dirInfo,1)
                     fileName = dirInfo(j).name;
@@ -67,7 +67,7 @@ if strcmp(dataset,'potato6')
                 TV = data.TV;
             else
                 fprintf('Computing TV reconstructions of template volumes\n');
-                projFolderName =  sprintf('Preeti_potato%d/projf32_LIN_AP_nc',templateNos(i));
+                projFolderName =  sprintf('inputs/potato%d/projf32_LIN_AP_nc',templateNos(i));
                 dirInfo = dir(projFolderName);
                 for j = 3:size(dirInfo,1)
                     fileName = dirInfo(j).name;

### 2022-02-06 paper/post_tci.tex
Tuning hyper-parameters rewritten

@@
 \label{sec:tuning_parameters}
-The three hyper-parameters, $\lambda_1$, $\lambda_2$ and $k$
-need to be chosen carefully for optimal reconstruction. In our
-experiments, $\lambda_1$ was tuned to maximize the
+The aim of our experiments is to demonstrate the benefit of using weighted prior reconstruction when optimal hyperparameter values for $\lambda_1$, $\lambda_2$ and $k$ are chosen.
+In this regard, we assume the ground-truth to be known.
+Specifically, $\lambda_1$ was tuned to maximize the
 SSIM of the complete reconstructed test volume using the TV-only
@@
 tuning.
-Thus, we compare our reconstruction with the best possible baseline TV reconstruction by choosing the $\lambda_1$ that gives the best SSIM for TV reconstruction.
-Further, this value was retained for our spatially-varying
-prior-based reconstruction as well, that is, the value optimized for
-the TV-only regularizer is maintained for the method proposed in this
-paper.  In principle, one could have jointly optimized both
-$\lambda_1$ and $\lambda_2$ to get even better results compared to the
-one we have in Sections~\ref{sec:results_with_imaging_model},
-and~\ref{sec:results_without_imaging_model}.
-
-The value of $\lambda_2$
-largely depends on the amount of artefacts one aims to remove by the
-use of object-prior at the cost of their dominance in the new
-regions.
-This value is chosen omnisciently, i.e., with the chosen $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM.
-This  was found to lie between $(0,3)$ for
-our datasets.
-In practice however, one may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.
-
-The hyper-parameter $k$ defines the sensitivity of the weights map to
+This optimal $\lambda_1$ was retained for spatially-varying prior-based reconstruction.
+With the already chosen optimal $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM with reference to the ground truth.
+%The value of $\lambda_2$ influences the amount of artefacts that can be removed by the use of object-prior at the expense of its dominance in new regions.
+%This value was found to lie between $(0,3)$ for our datasets.
+%In principle, one could have jointly optimized both $\lambda_1$ and $\lambda_2$ to get even better results compared to the one we have in Sections~\ref{sec:results_with_imaging_model}, and~\ref{sec:results_without_imaging_model}.
+In practice however, since ground-truth will never be available, these parameters must be tuned using only the set of templates available.
+One of the templates can be assumed to be a pseudo-test, and a grid search can be performed to get the best possible hyperparameter values.
+These values can then be used for reconstructing the `real' test volume.
+
+%in the nvone may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.
+
+$k$ defines the sensitivity of the weights map to
 the difference between test image and object-prior (projection of test

### 2022-02-07 paper/post_tci.tex
updated the results sections based on our discussion.

@@
   (`test') from its significantly fewer measurements. A common problem
-  with these techniques is the strong influence of object-priors in
+  with these techniques is the %strong 
+  influence of object-priors in
   the reconstruction of new changes in the test.  In this work, we
@@
 present reconstruction results on all datasets.  We show both
-qualitative and quantitative results. For the latter,
+qualitative and quantitative results.  Before we do this, it is import
+to first consider our method of reporting our results.
+
+\subsection{Metrics}
+In order to show the efficacy, we will clearly need to have either a
+gold-standard method, or a ground truth reference reconstruction such
+as those described in Sec~\ref{sec:datasets} (see, for example, the
+top left figure in Fig.~\ref{fig:story}).  For quantitative results,
 we use two metrics: the Root Mean Squared Error (RMSE) and the
@@
 RMSE corresponds to error in intensity values and is a measure of
-absolute error. For purposes of normalization, while reporting numbers
-we rescale intensity values of both the ground truth and the
-reconstructed results to lie between 0 to 1, so that the best possible
-RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks to
-consider perceptual changes, as well as correlation between adjacent
-pixels.
-This can be useful in a clinical context.
-The SSIM~\cite{multiscale_ssim} also provides a flexibility to set coefficients for the following three factors: Structure, Contrast and Intensity.
-In all our results, we report SSIM with both the standard setting, i.e., with coefficients $1.0,1.0,1.0$ and a structure-focussed setting, wherein we assign a higher weightage to structure preservation.
-In the latter case, we assign the following coefficients to the factors Structure, Contrast, and Intensity respectively: $0.7,0.2,0.1$.
-Our results are optimized for structure-focussed SSIM, but
-it can be verified that in all cases for the various datasets
-considered, our results are favourable with either metric.
-
-Here below, we first discuss tuning of parameters followed by the
-rationale for using multiple eigenspaces to compute weightsmap. We
-then present reconstruction results for each of the datasets.
+absolute error. Our results depend on the optimization library (as
+mentioned earlier) \cite{TVReg-lib}; however, the range of values
+returned by other libraries (such as the Matlab implementation of FDK
+used in our ground truth reconstructions) are not compatible with
+these.  This is not an issue for qualtitative results since the
+display program compensates for range differences. For RMSE, and
+for purposes of normalization and a fair comparison, while reporting
+numbers, we therefore rescale intensity values of both the ground
+truth and the reconstructed results to lie between 0 to 1, so that the
+best possible RMSE is 0, and the worst value is 1.
+
+On the other hand, SSIM seeks to consider perceptual changes, as well
+as correlation between adjacent pixels. This can be useful in a
+clinical context. The SSIM~\cite{multiscale_ssim} was designed to
+flexible set coefficients for the following three factors: Structure,
+Contrast and Intensity. We observed that in many cases, our
+qualitative results (e.g., when the standard TV regularization method
+outperforms FDK) do not correspond favourably to the default SSIM settings.  We
+therefore assigned the following coefficients to the factors
+Structure, Contrast, and Intensity respectively: $0.7,0.2,0.1$. Our
+results are optimized for structure-focussed SSIM, but it can be
+verified that in all cases for the various datasets considered, our
+results are favourable with either the default metric, i.e, with
+coefficients $1.0,1.0,1.0$ or with our structure-focused metric
+wherein we assign a relatively higher weightage to structure
+preservation.
+
 %The reason for emphasizing the structure with an
@@
 
-\subsection{Tuning of parameters}
+Finally, for a fair comparison in order to not distort metrics,
+we report these values in what we believe is a reasonable area of
+``new regions''. In particular, these regions of interest (RoI) are
+obviously not known in advance, and is thus appropriate for a ``test''.
+
+% \subsection{Tuning of parameters}
 \label{sec:tuning_parameters}
-The aim of our experiments is to demonstrate the benefit of using weighted prior reconstruction when optimal hyperparameter values for $\lambda_1$, $\lambda_2$ and $k$ are chosen.
-In this regard, we assume the ground-truth to be known.
-Specifically, $\lambda_1$ was tuned to maximize the
-SSIM of the complete reconstructed test volume using the TV-only
-regularizer.  In particular, regions of interest (RoI) are 
-not known in advance, and thus not considered for the purpose of this
-tuning.
-This optimal $\lambda_1$ was retained for spatially-varying prior-based reconstruction.
-With the already chosen optimal $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM with reference to the ground truth.
+
+Next, we turn to the parameters of the algorithm.  $\lambda_1$,
+$\lambda_2$ and $k$ are the three hyper-parameters that need to be
+chosen carefully for best results. Since the aim of our experiments is
+to demonstrate the benefit of using weighted prior reconstruction, we
+proceed to adjust these parameters by (as mentioned earlier) assuming
+the ground-truth to be known.
+
+Specifically, $\lambda_1$ was tuned to maximize the SSIM of the
+complete reconstructed test volume using the TV-only regularizer.
+It's important to note that we retain this value of $\lambda_1$ for
+the spatially-varying prior-based reconstruction, i.e., we \emph{do
+  not} adjust this value for our spatially-varying method, and,
+neither do we know the target ROI where the metric is going to be
+finally employed.  With the already chosen optimal $\lambda_1$, we
+apply our method for a range of $\lambda_2$ values and select the one
+that gives the best SSIM with reference to the ground
+truth.
 %The value of $\lambda_2$ influences the amount of artefacts that can be removed by the use of object-prior at the expense of its dominance in new regions.
 %This value was found to lie between $(0,3)$ for our datasets.
-%In principle, one could have jointly optimized both $\lambda_1$ and $\lambda_2$ to get even better results compared to the one we have in Sections~\ref{sec:results_with_imaging_model}, and~\ref{sec:results_without_imaging_model}.
-In practice however, since ground-truth will never be available, these parameters must be tuned using only the set of templates available.
-One of the templates can be assumed to be a pseudo-test, and a grid search can be performed to get the best possible hyperparameter values.
-These values can then be used for reconstructing the `real' test volume.
-
-%in the nvone may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.
+%In principle, one could have jointly optimized both $\lambda_1$ and
+%$\lambda_2$ to get even better results compared to the one we have in
+%Sections~\ref{sec:results_with_imaging_model},
+%and~\ref{sec:results_without_imaging_model}.  
+We note that in practice, however, since ground-truth will never be
+available, these parameters must be tuned using only the set of
+templates available.  One of the templates can be assumed to be a
+pseudo-test, and a grid search can be performed to get the best
+possible hyperparameter values. These values can then be used for
+reconstructing the `real' test volume.
+
+%in the nvone may select $\lambda_2$ omnisciently only while imaging a
+%particular class of object (say `sprouts') for the first time, and
+%thereafter retain the same $\lambda_2$ while imaging other objects of
+%the same class in future.
 

### 2022-02-09 paper/response_2022.tex
Added response_2022

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage[colorlinks=true]{hyperref}
\title{Author Response to Reviewers for the paper `Reducing object prior-bias in sparse projection tomographic reconstructions'}
\begin{document}
\maketitle

We thank all the reviewers for their detailed feedback on our work. Based on their comments, we have incorporated changes in our revised paper, and have discussed these in this document.

\section{Comments from AE}

\textcolor{blue}{\textit{While the reviewers have acknowledged improvements compared to the earlier manuscript, they have raised some important concerns about the manuscript in its current form. While addressing each of the reviewer specific comments, please pay specific attention to the following:}}

  \begin{itemize}
  \item \textcolor{blue}{\textit{Characterization of deep learning methods and its relation to the presented work}}

    We have now included a discussion of deep-learning methods in `Related Work', Section 2, of our paper, and have cited a few notable references pertaining to training neural networks to directly predict full-view sinogram and reconstruct the test object from its limited-view measurements.

    \item\textcolor{blue}{\textit{Presenting all relevant details so the work in the paper can be re-produced without ambiguity}}

      To ensure reproducibility, we had earlier shared the code files for 2D reconstructions. We have now added complete code 3D reconstructions as well in our github repository: \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}

  \end{itemize}

  \section{Recommendation R1: AQ - Publish With Minor, Required Changes}

  \textbf{Comments:}The authors have significantly improved their paper when compared to the earlier rejected submission. The results are now much clearer. I have a few relatively minor comments below.\\

  \textcolor{blue}{\textbf{[R1-1,2; re-wording abstract]:}\textit{In the abstract, I feel you are underselling your contributions. You may want to add a line or two that quantifies the fidelity of your reconstructions for a given percentage of the total number of views (as required by Nyquist sampling). Your method is very relevant for scenarios such as Flash X-ray CT where we only are able to measure 5-20 views. Hence, some quantifying statement that appeals to the very few view CT community may be useful. In the abstract, the sentence "In this work, we mitigate this problem by first estimating the location of new regions and then imposing object-prior in only old regions which are similar to the prior." introduces terms such as "new regions" and "old regions" that don't carry any meaning. Please rewrite.}}\\

  \textbf{Response:} The reason we didn't specify quantitative results in the abstract is its dependency on various factors such as the number of views and structural complexity of the object data itself. We have however mentioned the importance of estimating a weights-map that shows the location and intensity of new regions. Meaning of the terms `old regions' and `new regions' have also been clarified in the new abstract.\\

  \textcolor{blue}{\textbf{[R1-3]:}\textit{In page 3 and lines 50-53 right column, you mention that your code will be released. However, I recommend including a link to github or other website with the code before publication.}}\\

  \textbf{Response:} Earlier, we had shared the complete code for 2D reconstruction. We have now added code for 3D reconstructions as well in the github repository: \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}\\

  \textcolor{blue}{\textbf{[R1-4]:}\textit{In page 7 and lines 39-42 left column, what are the weights for? I don't see any equation where these can be substituted for quantifying results. Also, RMSE and SSIM have their own definitions.}}\\

  \textbf{Response:} Our earlier usage of the term `weights' with respect to SSIM might have been confusing since we also refer to `weights-map' throughout our paper. We have used the commonly used SSIM metric, for which, we have now provided reference to the original paper where the metric has been defined. SSIM comprises of three factors: Luminance, Contrast and Structure. These factors (called `coefficients' in our paper) for these three terms are adjustable to suit the application at hand. A description of computation of SSIM for a 2D image is given below. (The same formula can be extended to 3D.)

With $\mu_x$, $\mu_y$ and $\sigma_x^2$, $\sigma_y^2$ being the averages and variances of pixel values along dimensions $x$ and $y$ respectively, $\sigma_{xy}$ being the covariance along $x$ and $y$, $L$ being the dynamic range, $c_1$ and $c_2$, and $c_3$ being defined to be $(k_1L)^2$, $(K_2L)^2$ and $c_2/2$ repectively, with $k_1=0.01$ and $k_2=0.03$, the three components of SSIM metric: luminance $l$, contrast $c$ and structure $s$ are defined as:

\begin{equation}
l(x,y) = \frac{2\mu_x\mu_y + c_1}{\mu_x^2 + \mu_y^2 + c_1}
\end{equation}

\begin{equation}
  c(x,y) = \frac{2\sigma_x\sigma_y + c_2}{\sigma_x^2 + \sigma_y^2 + c_2}
\end{equation}

\begin{equation}
  s(x,y) = \frac{\sigma_{xy} + c_3}{\sigma_x\sigma_y + c_3}
\end{equation}

Fianlly, SSIM is defined as

\begin{equation}
  SSIM = \frac{1}{n}\sum_x\sum_y [l(x,y)^\alpha. c(x,y)^\beta. s(x,y)^\gamma],
\end{equation}

where $n$ denotes the total number of pixels. The coefficients $\alpha$, $\beta$ and $\gamma$ are generally set to $1$ but are adjustable to suit the application goal.\\

\textcolor{blue}{\textbf{[R1-5, 6 (on Hyper-parameters)]:}\textit{In page 7 and lines 52-56 left column, I don't understand your tuning of $\lambda_1$. How is SSIM optimized when ground-truth is unknown for the test volume?
    It appears that the weight $\lambda_2$ must be chosen carefully and sufficiently high to ensure that we achieve the very fidelity reconstruction shown in Fig. 11 (h) with just 6 views. A lower incorrect choice for $\lambda_2$ will certainly bring back the artifacts. Even the parameter k probably plays an important role in achieving Fig. 11(h). Thus, your explanation for choosing $\lambda_2$ (in page 7 and lines 8-10 right column) and k (in page 7 and lines 23-27 right column) is inadequate. If you base your choice of $\lambda_2$ and k on "tolerance for noise" and/or "artifacts", how do you even quantify the relevant noise and artifacts? If $\lambda_2$ and k are chosen incorrectly, I am sure your method won't work. Hence, this detail needs to be discussed.}}\\

\textbf{Response:} Since the aim of our experiments is to demonstrate the benefit of using weighted prior reconstruction, we adjust these parameters by assuming the ground-truth to be known. However, we do not assume the Region Of Interest (RoI) of the test to be known.

We note that in practice, however, since ground-truth will never be
available, these parameters must be tuned using only the set of
templates available.  One of the templates can be assumed to be a
pseudo-test, and a grid search can be performed to get the best
possible hyperparameter values. These values can then be used for
reconstructing the `real' test volume.

As mentioned in Sec.6-B of the paper, $\lambda_1$ was tuned to maximize the SSIM of the complete reconstructed test volume using the TV-only regularizer. With the already chosen optimal $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM with reference to the ground truth.

As far as the stability of parameter $k$ is concerned, in Fig. 8 of our paper, we show how the quality of reconstructions vary for different values of $k$. We see that the reconstructions are similar for a significant range of $k$ values. (5-40) for Okra. For the purposes of demonstrating the benefit of our method, we choose $k$ omnisciently assuming known ground truth of test (and unknown RoI). In real-world, $k$ must also be tuned by using one of the templates as pseudo-test and performing a grid search to select the best value.\\

\section{Recommendation R2: RQ - Review Again After Major Changes}

\textbf{Comments:}The paper has greatly improved with the new focus! I would like to thank the authors for the extra work. I do have a few remaining comments:\\

\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use standard metrics for comparison, instead of the custom metrics currently used. For SSIM, reporting with the standard weightings is important (if the authors want, of course they can show both the standard weightings and the custom ones!). For RSME, I don't understand why the authors rescale images before computing the metric -- this can greatly alter the metrics, making them difficult to interpret and compare across papers. For the RMSE, it is best to not use any scaling at all (or, a fixed scaling for all reconstructions only based on the ground truth).
}}\\

\textbf{Response}:
Since SSIM inherently offers a flexibility to set coefficients based on what we want to evaluate, we believe that having a set of coefficients that focus on measuring structural preservation is better suited for our goal. However, in the paper, we have now included quantitative results with both custom (structure-focussed) SSIM and default SSIM. The benefit of the proposed method is seen with either setting of the metric.\\

\textcolor{blue}{\textbf{[R2-2]:}\textit{The computation comparison is not very convincing to me. In practice, given a certain number of projections, a user might want to compare possible reconstruction algorithms to decide what is the best one to use from a computation time / reconstruction quality tradeoff point of view. Therefore, it would be good to compare times between methods for the same number of projections (it is of course possible to show results for a few different cases, e.g. many views, moderate views, and few views). It is also useful to include more detailed information about the data size (detector size, reconstruction size, number of projections, etcetera). Furthermore, please show timing results for all steps of the algorithm, including the computation of the low quality reconstructions, pilot reconstructions, and building of eigenspaces.}}\\

\textbf{Response}: Earlier, we had indeed measured all computation times for exactly the same number of views. However, field-titles of Table-6 may not have been clear in this regard. Hence, we have edited the caption and Table-field titles of Table-6 (Page 10) to accurately describe details of measurement. Here, computation times of all methods and stages of reconstructions are measured for 30 views for  Liver slice of size $(512 \times 512)$.

Additionally, the TV reconstruction is our pilot reconstruction and hence their computation times are equal.

Having specified the exact compute times in our machine, we also note that the type of machine and the degree of parallelism available in the current times make these timing measurements, especially for iterative solutions, very subjective.
\\

\textcolor{blue}{\textbf{[R2-3]:}\textit{In several parts of the paper, the authors claim that existing object-prior based methods have problems, e.g.: "A common problem with these techniques is the strong influence of object-priors in the reconstruction of new regions in the test". At the moment, this hard claim is not supported in the paper by references or (even better) comparison results. It would be good to show, on one (or more) of the datasets used, that this is indeed the case, and that the proposed methods solves this problem.}}\\

\textbf{Response:}We have now included a reference (Pg.2, Line 3 under Sec.1-A) to a PhD thesis wherein the problem of object-priors biasing the reconstruction of new test regions is discussed in detail. 
A sample result (Fig.1-3 here) from the thesis is shown below. It illustrates how an unweighted application of prior can adversely affect the reconstruction of new regions in the test.\\

\begin{figure}[!h]
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.186\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/thesis/okra/testCropped.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption[Okra 3D dataset]{Okra 3D dataset: One slice each from the templates (the
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:templates_test_okra}
\end{figure}
%----------------------------------------------------

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/testCropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/fdk_cropped.png}}\hfill
\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/cs_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/prior_weighted_cropped.png}}
\caption[3D reconstruction of okra dataset]{3D reconstruction of the okra from $10\%$ projection
  views (b) has strong streak artefacts, (c) blurred, (d) no new
  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
  corresponding to red and green regions) while simultaneously
  reducing streak artefacts.}
\label{fig:okra_3D_results}
\end{figure}

%--------------------------------------zoomed okra

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/input_cropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
\caption[Zoomed results of Okra dataset]{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (e) new information detected (no deformities
 ).}
\label{fig:okra_zoomed_3D_results}
\end{figure}

\textcolor{blue}{\textbf{[R2-4]:}\textit{The discussion of deep learning methods in Section 7B is not very strong in my opinion. There are many existing techniques that have shown quite convincing results for reconstructing CT images with a low number of projections, even without taking into account any static parts across time. These methods rely on learning image-based correlations instead of the "given intensities of a voxel at various time instants in a longitudinal setting and partial measurements of the voxel at the current time, what will be the intensity of the same voxel at the current time instant?" given by the authors. These image-based methods often don't need 'hundreds of labeled data', sometimes being able to accurately learn from just one time step. In the paper, these methods should be discussed, and proper references should be included.}}\\

\textbf{Response}: We acknowledge that there has been significant work pertaining to training neural networks to directly predict full-view sinogram and reconstruction of the test object from its limited-view measurements. We have now included a discussion of deep-learning methods in `Related Work', Section 2, of our paper, and have now cited a few notable references.

We also believe that information from longitudinal data, if available, is helpful and must be used to better inform reconstruction of the test. This is especially the case in applications where longitudinal data is naturally available as part of the process as in radio frequency ablations. It is in this context that our paper presents an analytical method to fuse the existing prior data with test measurements in order to construct a `weights map'. This map gives clear insights about regions of change within the object over time.\\

\textcolor{blue}{\textbf{[R2-5]:}\textit{What algorithm is used to minimize Eq 3? How many iterations were used for this minimization? How was convergence ensured?}}\\

\textbf{Response}: Eq. 3 consists of alternately solving for Eq.4 and Eq.5. While Eq.5 has a closed form solution, Eq.4 was solved using the solver mentioned in Reference [18]. (as mentioned in page 6, just above Eq.4). 
For solving Eq.4, maximum number of iterations was set to 200 and tolerance was set to 1e-4.

The number of alternate minimization cycles (between Eq.4 and~5) was set to 3. We observed that further cycles did not improve reconstruction significantly for the extra time consumed.
\\

\textcolor{blue}{\textbf{[R2-6]:}\textit{What were the various parameters of the reconstructions show in Fig 11? How were they chosen?
}}\\

\textbf{Response}: For 2D reconstructions using ART, SIRT and SART, we set the maximum iterations to 50 and observed that further iterations did not improve the quality of reconstructions.\\

\textcolor{blue}{\textbf{[R2-7]:}\textit{How was the $\lambda_2$ parameter empirically chosen?
}}\\

\textbf{Response}: Please refer to our response to a similar query in \textcolor{blue}{\textbf{[R1-5,6]}}.\\

\textcolor{blue}{\textbf{[R2-8]:}\textit{In some parts of the paper, the use of language could be improved. Also, I think it is better to not use words like `paltry'.}}\\

\textbf{Response}: Although we had meant to use `paltry' in a neutral way to only suggest the use of very few measuremetns, we  have noted this and made the change.\\

\section{Recommendation R3: RQ - Review Again After Major Changes}

\textbf{Comments:} The paper presents an image reconstruction method for recovering samples from limited projections provided that the high-quality CT-scans of the same sample exist. This approach could be useful to longitudinal studies in which the patient's previous CT scans are available and the purpose is to reduce the dose. So this is good!\\

The structure of the paper is good and the authors did a good job in presenting both the theory and the validation with experimental data, demonstrating the potential. of the nice things about the paper is that they use PCA to get the orthonormal basis to represent the image and this both serves as a regularizer as well as a nice way to quantify new features in data.
\\

\textcolor{blue}{\textbf{[R3-1]:}\textit{One challenge of the method that I can see is that these datasets needs to be aligned but there is not much discussion on this procedure or how this can be performed in a realistic setting. Are the variation from a past to present scans looking similar? In addition to the variations in scans taken at different times, in the low-quality scan, the features are less pronounced so the registration might pose a challenge even if the sample looks similar. So, it would be good to see the artifacts due to an intentionally less-aligned images and a discussion about the limitations would be nice.
}}\\

\textbf{Response}:Yes, registration between the unknown test and templates is important for our method. Registration is also a common problem in many other fields such as MRI/CT/PET data.  There is a lot of research on linear and non-linear methods to optimise this. The focus in our paper is not on registration but on building accurate maps that delineate regions of structural changes in already pre-registered data (registered using state-of-the-art methods).  Hence, in this work, we do not intend to predict what difficulties registration might present but rather that show that it is possible to blend prior and new views.\\

We note that in practice, a pilot reconstruction of the test must be registered with similarly imaged, pilot reconstructed templates. This registration is challenging due to the presence of sub-sampling artefacts. We consider the problem of registration as a separate one and intend the practitioners to use any state-of-the-art registration algorithm before applying the proposed method in our paper. 
\\

\textcolor{blue}{\textbf{[R3-2]:}\textit{Another challenge, as the authors acknowledge, is the high number of hyper-parameters. I believe the paper can benefit a lot from an in depth analysis to get some insights about how this parameters should be chosen. Because otherwise the applicability of the method is limited given the amount of time required to solve the reconstruction problem.
}}\\

\textbf{Response}: Please refer to our response to a similar query in \textcolor{blue}{\textbf{[R1-5,6]}}.\\

\textcolor{blue}{\textbf{[R3-3]:}\textit{The title says ``eliminating object prior-bias'', but I think this is not accurate, because you give a weight to those priors, but not fully eliminate them. A more appropriate wording might be ``Prior-informed sparse-projection...'' or ``Weighted object-priors from past CT-scans for ...'' or something like this.}}\\

\textbf{Response}: Thank you for suggesting other possible titles. We have changed it to ``Reducing object prior-bias from sparse-projection tomographic reconstructions''\\

\textcolor{blue}{\textbf{[R3-4]:}\textit{As a final remark, the authors can also use this technique for imaging dynamical samples. A discussion would be nice.}}\\

\textbf{Response}: Based on our understanding, dynamic imaging is a technique for acquiring only those measurements that have high entropy. This involves computing the next the measurement location based on the past measurements acquired for the \textit{same} object volume. This is different from our scenario in which we consider measurements from \textit{multiple volumes} of an object, each taken at a different time. The measurement-locations of the test are also not pre-computed while imaging, in our case.

Hence, our method may not be directly applicable for reconstruction from dynamic imaging wherein the acquired measurements of a single object are already non-redundant by design. However, a suitable dynamic imaging reconstruction algorithm (like the Compressed Sensing)  can definitely be used as a pilot reconstruction method within our framework.

  \end{document}

\bibliography{tci_ref}
\end{document}
\begin{table}[!h]
  \centering
\caption{Standard-SSIM (`SSIM-1'), structure-focussed SSIM (`SSIM-2') and RMSE of the reconstructions shown in Fig.11:(a)-(h) of the paper. %The SSIM of
                                %ideal reconstruction is 1. The ideal
                                %RMSE is 0, and the worst RMSE
                                %possible is 1 here.
}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
& \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} & \textbf{(e)} & \textbf{(f)} &  \textbf{(g)} &  \textbf{(h)} \\\hline
SSIM-1 & 0.31 & 0.48  & 0.39  & 0.51 & 0.55  & 0.42 & 0.68 &\textcolor{red}{0.78} \\ \hline
SSIM-2 & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline
RMSE & 0.38 & 0.18 & 0.25 & 0.43 & 0.33 & 0.21 & 0.11 & \textcolor{red}{0.04}\\ \hline
\end{tabular}
\label{table:potato_2D_ssim}
\end{table}

### 2022-02-09 paper/post_tci.tex
Added response_2022

@@
 % Do not put math or special symbols in the title.
-\title{Eliminating object prior-bias from sparse-projection tomographic reconstructions}
+\title{Reducing object prior-bias from sparse-projection tomographic reconstructions}
 %
@@
   reconstructions while minimizing the number of measurements needed
-  for imaging in longitudinal studies. We show that with
-  as little as $2\%$ of measurements, our method achieves a structural
-  fidelity of $0.84$, with $1.00$ representing ideal reconstruction.
+  for imaging in longitudinal studies.% We show that with   as little as $2\%$ of measurements, our method achieves a structural   fidelity of $0.84$, with $1.00$ representing ideal reconstruction.
 \end{abstract}
@@
 
-% \subsection{Tuning of parameters}
+\subsection{Hyper-parameters}
 \label{sec:tuning_parameters}
@@
   \centering
-\caption{Standard-SSIM (`SSIM-1'), structure-focussed SSIM (`SSIM-2') and RMSE of the reconstructions shown in
+\caption{Default-SSIM (`SSIM-1'), structure-focussed SSIM (`SSIM-2') and RMSE of the reconstructions shown in
   Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(h). %The SSIM of
@@
   \centering
-  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed potato from various
+  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed potato from various
     methods. 
@@
   \centering
-  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed okra from various
+  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed okra from various
     methods. 
@@
   \centering
-  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
+  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
 %For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
@@
   \centering
-  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed sprouts from various
+  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed sprouts from various
     methods. 

### 2022-02-09 paper/post_tci.tex
Changed k to p for specifying components of eigenvector and eigencoefficients in Eq.3

@@
 template set $\{Q_i\}_{i=1}^L$. The space spanned by the eigenvectors
-$\{\boldsymbol{V_k}\}_{k=1}^{L-1}$ (eigenspace) of the covariance
+$\{\boldsymbol{V_p}\}_{p=1}^{L-1}$ (eigenspace) of the covariance
 matrix is the object prior and is assumed to contain most of the test
@@
 scanned objects, and $\boldsymbol{\alpha}$ the unknown vector of
-eigen-coefficients of the test scan, of which $\alpha_k$ is the
-$k^{\textrm{th}}$ element. Then, once the eigenspace is pre-computed,
+eigen-coefficients of the test scan, of which $\alpha_p$ is the
+$p^{\textrm{th}}$ element. Then, once the eigenspace is pre-computed,
 the test was reconstructed in~\cite{my_dicta_paper} by imposing a
@@
   J_3(\boldsymbol{x},\boldsymbol{\alpha}) = &\lVert\boldsymbol{\mathcal{R} x}-\boldsymbol{y}\rVert_2^2  + \lambda_1TV(\boldsymbol{x}) +\\
-  &\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{k}\boldsymbol{V_k}\alpha_k))\rVert_2^2.
+  &\lambda_2\lVert\boldsymbol{W}(\boldsymbol{x} - (\boldsymbol{\mu} + \sum_{p}\boldsymbol{V_p}\alpha_p))\rVert_2^2.
   \label{eq:spatially_varying_prior}

### 2022-02-09 paper/response_2022.tex
Specified intensity ranges of reconstructed volumes in response_2022

@@
 However, in the paper, we have now included quantitative results with both custom (structure-focussed) SSIM and default SSIM.
-The benefit of the proposed method is seen with either setting of the metric.\\
+The benefit of the proposed method is seen with either setting of the metric.
+
+For computation of both SSIM and RMSE, we find that rescaling is necessary because different optimization routines generate solutions whose intensity ranges vary from that of the ground truth.
+For example, for reconstruction of the potato data from 18 views, Table~\ref{Tab:ranges} shows the min.
+and max.
+intensity values of the groundtruth and reconstructed volumes.\\
+
+\begin{table}[]
+  \centering
+  \caption{Minimum and maximum intensity values of groundtruth and reconstructed volumes of potato data, reconstructed from 18 views.}
+  \begin{tabular}{|l|l|l|l|}
+\hline
+ & \textbf{\begin{tabular}[c]{@{}l@{}}Ground\\ truth\end{tabular}} & \textbf{FDK} & \textbf{TV} \\ \hline
+\textbf{Min.} & 0.00 & -0.19 & 0.00 \\ \hline
+\textbf{Max.} & 1.00 & 0.24 & 0.24 \\ \hline
+  \end{tabular}
+  \label{Tab:ranges}
+\end{table}
 

### 2022-02-10 paper/response_2022.tex
edited responses_2022.tex tried to fit figures on one page,
otherwise it is difficult to make sense.  Also tried to introduce
enumerate for R2 since he makes multiple points, so it's important to
separate the points.  Also SSIM has moved to a unified place.

--- 2022-02-09 paper/response_2022.tex
@@
 
-We thank all the reviewers for their detailed feedback on our work. Based on their comments, we have incorporated changes in our revised paper, and have discussed these in this document.
+We thank all the reviewers for their detailed feedback on our
+work. Based on their comments, we have incorporated significant
+changes in our revised paper, and have discussed these in this
+document. We also request the reviewers to read these comments along
+with the changes in the paper, especially related the comments in
+Section~6 (Results).
 
@@
 
-\textcolor{blue}{\textit{While the reviewers have acknowledged improvements compared to the earlier manuscript, they have raised some important concerns about the manuscript in its current form.
-While addressing each of the reviewer specific comments, please pay specific attention to the following:}}
+\textcolor{blue}{\textit{While the reviewers have acknowledged
+    improvements compared to the earlier manuscript, they have raised
+    some important concerns about the manuscript in its current
+    form. While addressing each of the reviewer specific comments,
+    please pay specific attention to the following:}}
 
   \begin{itemize}
-  \item \textcolor{blue}{\textit{Characterization of deep learning methods and its relation to the presented work}}
+  \item \textcolor{blue}{\textit{Characterization of deep learning
+        methods and its relation to the presented work}}
 
-    We have now included a discussion of deep-learning methods in `Related Work', Section 2, of our paper, and have cited a few notable references pertaining to training neural networks to directly predict full-view sinogram and reconstruct the test object from its limited-view measurements.
+    We have now included a discussion of deep-learning (DL) methods in
+    `Related Work', Section 2, of our paper, and have cited a few
+    notable references pertaining to training neural networks to
+    directly predict full-view sinogram and reconstruct the test
+    object from its limited-view measurements. The ability of DL to
+    uncover new features from one or many example images or training
+    session is not being disputed. Here the focus is on a new discrete
+    algorithm that builds structural maps that can and does point to
+    new features.
 
-    \item\textcolor{blue}{\textit{Presenting all relevant details so the work in the paper can be re-produced without ambiguity}}
+    \item\textcolor{blue}{\textit{Presenting all relevant details so
+          the work in the paper can be re-produced without ambiguity}}
 
-      To ensure reproducibility, we had earlier shared the code files for 2D reconstructions.
-We have now added complete code 3D reconstructions as well in our github repository: \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}
+      To ensure reproducibility, we had earlier shared the code files
+      for 2D reconstructions. We have now added complete code for 3D
+      reconstructions as well, and as suggested, placed them in our
+      github repository:
+      \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}
+      This repository is currently not a public repository since the
+      paper is in the review process.
 
@@
 
-  \section{Recommendation R1: AQ - Publish With Minor, Required Changes}
+As a side note, based on the suggestion of R3, we have made a
+slight change to the title of the paper using the word ``Mitigating''
+instead of ``Eliminating''.
 
-  \textbf{Comments:}The authors have significantly improved their paper when compared to the earlier rejected submission.
-The results are now much clearer.
-I have a few relatively minor comments below.\\
+  \section{Recommendation R1: AQ - Publish With Minor, Required
+    Changes}
 
-  \textcolor{blue}{\textbf{[R1-1,2; re-wording abstract]:}\textit{In the abstract, I feel you are underselling your contributions.
-You may want to add a line or two that quantifies the fidelity of your reconstructions for a given percentage of the total number of views (as required by Nyquist sampling).
-Your method is very relevant for scenarios such as Flash X-ray CT where we only are able to measure 5-20 views.
-Hence, some quantifying statement that appeals to the very few view CT community may be useful.
-In the abstract, the sentence "In this work, we mitigate this problem by first estimating the location of new regions and then imposing object-prior in only old regions which are similar to the prior." introduces terms such as "new regions" and "old regions" that don't carry any meaning.
-Please rewrite.}}\\
+  \textbf{Comments:}The authors have significantly improved their
+  paper when compared to the earlier rejected submission. The results
+  are now much clearer. I have a few relatively minor comments below.
 
-  \textbf{Response:} The reason we didn't specify quantitative results in the abstract is its dependency on various factors such as the number of views and structural complexity of the object data itself.
-We have however mentioned the importance of estimating a weights-map that shows the location and intensity of new regions.
-Meaning of the terms `old regions' and `new regions' have also been clarified in the new abstract.\\
+  \textcolor{blue}{\textbf{[R1-1,2; re-wording abstract]:}\textit{In
+      the abstract, I feel you are underselling your
+      contributions. You may want to add a line or two that quantifies
+      the fidelity of your reconstructions for a given percentage of
+      the total number of views (as required by Nyquist
+      sampling). Your method is very relevant for scenarios such as
+      Flash X-ray CT where we only are able to measure 5-20
+      views. Hence, some quantifying statement that appeals to the
+      very few view CT community may be useful. In the abstract, the
+      sentence "In this work, we mitigate this problem by first
+      estimating the location of new regions and then imposing
+      object-prior in only old regions which are similar to the
+      prior." introduces terms such as "new regions" and "old regions"
+      that don't carry any meaning. Please rewrite.}}\\
 
-  \textcolor{blue}{\textbf{[R1-3]:}\textit{In page 3 and lines 50-53 right column, you mention that your code will be released.
-However, I recommend including a link to github or other website with the code before publication.}}\\
+  \textbf{Response:}
 
-  \textbf{Response:} Earlier, we had shared the complete code for 2D reconstruction.
-We have now added code for 3D reconstructions as well in the github repository: \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}\\
+  Duly noted the issue of ``old-regions'', we have defined and
+  re-written the  abstract.
 
-  \textcolor{blue}{\textbf{[R1-4]:}\textit{In page 7 and lines 39-42 left column, what are the weights for?
-I don't see any equation where these can be substituted for quantifying results.
-Also, RMSE and SSIM have their own definitions.}}\\
+  While we appreciate the suggestion on the quantification of our
+  results, we felt that (as styles go) it would be better to keep a
+  lower profile because of the dependency on various factors such as
+  the number of views and structural complexity of the object data
+  itself.
 
-  \textbf{Response:} Our earlier usage of the term `weights' with respect to SSIM might have been confusing since we also refer to `weights-map' throughout our paper.
-We have used the commonly used SSIM metric, for which, we have now provided reference to the original paper where the metric has been defined.
-SSIM comprises of three factors: Luminance, Contrast and Structure.
-These factors (called `coefficients' in our paper) for these three terms are adjustable to suit the application at hand.
-A description of computation of SSIM for a 2D image is given below.
-(The same formula can be extended to 3D.)
+  \textcolor{blue}{\textbf{[R1-3]:}\textit{In page 3 and lines 50-53
+      right column, you mention that your code will be
+      released. However, I recommend including a link to github or
+      other website with the code before publication.}}
 
-With $\mu_x$, $\mu_y$ and $\sigma_x^2$, $\sigma_y^2$ being the averages and variances of pixel values along dimensions $x$ and $y$ respectively, $\sigma_{xy}$ being the covariance along $x$ and $y$, $L$ being the dynamic range, $c_1$ and $c_2$, and $c_3$ being defined to be $(k_1L)^2$, $(K_2L)^2$ and $c_2/2$ repectively, with $k_1=0.01$ and $k_2=0.03$, the three components of SSIM metric: luminance $l$, contrast $c$ and structure $s$ are defined as:
+  \textbf{Response:} Earlier, we had shared the complete code for 2D
+  reconstruction. We have now added code for 3D reconstructions as
+  well in the github repository:
+  \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}
 
-\begin{equation}
-l(x,y) = \frac{2\mu_x\mu_y + c_1}{\mu_x^2 + \mu_y^2 + c_1}
-\end{equation}
+  \textcolor{blue}{\textbf{[R1-4]:}\textit{In page 7 and lines 39-42
+      left column, what are the weights for? I don't see any equation
+      where these can be substituted for quantifying results. Also,
+      RMSE and SSIM have their own definitions.}}
 
-\begin{equation}
-  c(x,y) = \frac{2\sigma_x\sigma_y + c_2}{\sigma_x^2 + \sigma_y^2 + c_2}
-\end{equation}
-
-\begin{equation}
-  s(x,y) = \frac{\sigma_{xy} + c_3}{\sigma_x\sigma_y + c_3}
-\end{equation}
-
-Fianlly, SSIM is defined as
-
-\begin{equation}
-  SSIM = \frac{1}{n}\sum_x\sum_y [l(x,y)^\alpha. c(x,y)^\beta. s(x,y)^\gamma],
-\end{equation}
-
-where $n$ denotes the total number of pixels. The coefficients $\alpha$, $\beta$ and $\gamma$ are generally set to $1$ but are adjustable to suit the application goal.\\
+  \textbf{Response:} This point has come up in R2 as well (in a larger
+  context), and we defer the discussion to that response.  Our earlier
+  usage of the term `weights' with respect to SSIM might have been
+  confusing since we also refer to `weights-map' throughout our paper.
 
@@
 
-\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use standard metrics for comparison, instead of the custom metrics currently used.
-For SSIM, reporting with the standard weightings is important (if the authors want, of course they can show both the standard weightings and the custom ones!).
-For RSME, I don't understand why the authors rescale images before computing the metric -- this can greatly alter the metrics, making them difficult to interpret and compare across papers.
-For the RMSE, it is best to not use any scaling at all (or, a fixed scaling for all reconstructions only based on the ground truth).
-}}\\
+\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use
+    standard metrics for comparison, instead of the custom metrics
+    currently used. For SSIM, reporting with the standard weightings
+    is important (if the authors want, of course they can show both
+    the standard weightings and the custom ones!). For RSME, I don't
+    understand why the authors rescale images before computing the
+    metric -- this can greatly alter the metrics, making them
+    difficult to interpret and compare across papers. For the RMSE, it
+    is best to not use any scaling at all (or, a fixed scaling for all
+    reconstructions only based on the ground truth).  }}
 
 \textbf{Response}:
-Since SSIM inherently offers a flexibility to set coefficients based on what we want to evaluate, we believe that having a set of coefficients that focus on measuring structural preservation is better suited for our goal.
-However, in the paper, we have now included quantitative results with both custom (structure-focussed) SSIM and default SSIM.
-The benefit of the proposed method is seen with either setting of the metric.\\
 
-\textcolor{blue}{\textbf{[R2-2]:}\textit{The computation comparison is not very convincing to me.
-In practice, given a certain number of projections, a user might want to compare possible reconstruction algorithms to decide what is the best one to use from a computation time / reconstruction quality tradeoff point of view.
-Therefore, it would be good to compare times between methods for the same number of projections (it is of course possible to show results for a few different cases, e.g.
-many views, moderate views, and few views).
-It is also useful to include more detailed information about the data size (detector size, reconstruction size, number of projections, etcetera).
-Furthermore, please show timing results for all steps of the algorithm, including the computation of the low quality reconstructions, pilot reconstructions, and building of eigenspaces.}}\\
+\begin{enumerate}
 
-\textbf{Response}: Earlier, we had indeed measured all computation times for exactly the same number of views.
-However, field-titles of Table-6 may not have been clear in this regard.
-Hence, we have edited the caption and Table-field titles of Table-6 (Page 10) to accurately describe details of measurement.
-Here, computation times of all methods and stages of reconstructions are measured for 30 views for  Liver slice of size $(512 \times 512)$.
+  \item
 
-Additionally, the TV reconstruction is our pilot reconstruction and hence their computation times are equal.
+    [Meta comment: This section is also in response to R1 (\emph{SSIM
+      have their own definitions}.]
 
-Having specified the exact compute times in our machine, we also note that the type of machine and the degree of parallelism available in the current times make these timing measurements, especially for iterative solutions, very subjective.
-\\
+    [Standard vs custom:] We have used the commonly used SSIM metric,
+    for which, we have now provided reference to the original paper
+    where the metric has been defined. As is well know, SSIM comprises
+    of three factors: Luminance, Contrast and Structure. These factors
+    (now termed `coefficients', earlier `weights' paper) for these
+    three terms are adjustable to suit the application at hand.  Since
+    SSIM inherently offers a flexibility to set coefficients based on
+    what we want to evaluate, we believe that having a set of
+    coefficients that focus on measuring structural preservation is
+    better suited for our goal.
 
-\textcolor{blue}{\textbf{[R2-3]:}\textit{In several parts of the paper, the authors claim that existing object-prior based methods have problems, e.g.: "A common problem with these techniques is the strong influence of object-priors in the reconstruction of new regions in the test".
-At the moment, this hard claim is not supported in the paper by references or (even better) comparison results.
-It would be good to show, on one (or more) of the datasets used, that this is indeed the case, and that the proposed methods solves this problem.}}\\
+    However, in the revised version, we have now included quantitative
+    results with both custom (structure-focussed) SSIM and default
+    SSIM. The benefit of the proposed method is seen with
+    \textbf{either} setting of the metric.
 
-\textbf{Response:}We have now included a reference (Pg.2, Line 3 under Sec.1-A) to a PhD thesis wherein the problem of object-priors biasing the reconstruction of new test regions is discussed in detail.
-A sample result (Fig.1-3 here) from the thesis is shown below. It illustrates how an unweighted application of prior can adversely affect the reconstruction of new regions in the test.\\
+    Since the discussion on SSIM has persisted from the previous
+    version, we take the liberty of providing a more detailed
+    response. % A description of
+    % computation of SSIM for a 2D image is given below. (The same
+    % formula can be extended to 3D.)
 
-\begin{figure}[!h]
+    With $\mu_x$, $\mu_y$ and $\sigma_x^2$, $\sigma_y^2$ being the
+    averages and variances of pixel values along dimensions $x$ and
+    $y$ respectively, $\sigma_{xy}$ being the covariance along $x$ and
+    $y$, $L$ being the dynamic range, $c_1$ and $c_2$, and $c_3$ being
+    defined to be $(k_1L)^2$, $(K_2L)^2$ and $c_2/2$ repectively, with
+    $k_1=0.01$ and $k_2=0.03$, the three components of SSIM metric:
+    luminance $l$, contrast $c$ and structure $s$ are defined as:
+
+\begin{equation}
+l(x,y) = \frac{2\mu_x\mu_y + c_1}{\mu_x^2 + \mu_y^2 + c_1}
+\end{equation}
+
+\begin{equation}
+  c(x,y) = \frac{2\sigma_x\sigma_y + c_2}{\sigma_x^2 + \sigma_y^2 + c_2}
+\end{equation}
+
+\begin{equation}
+  s(x,y) = \frac{\sigma_{xy} + c_3}{\sigma_x\sigma_y + c_3}
+\end{equation}
+
+Fianlly, SSIM is defined as
+
+\begin{equation}
+  SSIM = \frac{1}{n}\sum_x\sum_y [l(x,y)^\alpha. c(x,y)^\beta. s(x,y)^\gamma],
+\end{equation}
+
+where $n$ denotes the total number of pixels. The coefficients
+$\alpha$, $\beta$ and $\gamma$ are set to $1$ as default, but need to
+be adjusted to suit the application goal.
+
+\item Rescaling
+
+  For computation of both SSIM and RMSE, we find that rescaling is
+  necessary because the different optimization routines generate
+  solutions whose ranges vary from that of the ground truth.  For
+  example, for reconstruction of the potato data from 18 views,
+  Table~\ref{Tab:ranges} shows the minimum and maximum intensity
+  values of the groundtruth and reconstructed volumes (in the case of
+  TV regularization). The pernicious effect of this is obviously
+  invisible in the qualitative results where the display program
+  autoadjusts showing TV superior to FDK. In a quantitative setting it
+  becomes necessary to rescale, otherwise TV using a prior will appear
+  to be inferior to FDK (without a prior).  The same issue persists in
+  the reconstruction using the external optimization program
+  mentioned. %TODO give section or reference?
+
+\begin{table}[]
+  \centering
+  \caption{Minimum and maximum intensity values of groundtruth and
+    reconstructed volumes of potato data reconstructed from 18
+    views.}
+  \begin{tabular}{|l|l|l|l|}
+\hline
+ & \textbf{\begin{tabular}[c]{@{}l@{}}Ground\\ truth\end{tabular}} & \textbf{FDK} & \textbf{TV} \\ \hline
+\textbf{Minimum} & 0.00 & -0.19 & 0.00 \\ \hline
+\textbf{Maximum} & 1.00 & 0.24 & 0.24 \\ \hline
+  \end{tabular}
+  \label{Tab:ranges}
+\end{table}
+\end{enumerate}
+
+\textcolor{blue}{\textbf{[R2-2]:}\textit{The computation comparison is
+    not very convincing to me. In practice, given a certain number of
+    projections, a user might want to compare possible reconstruction
+    algorithms to decide what is the best one to use from a
+    computation time / reconstruction quality tradeoff point of
+    view. Therefore, it would be good to compare times between methods
+    for the same number of projections (it is of course possible to
+    show results for a few different cases, e.g. many views, moderate
+    views, and few views). It is also useful to include more detailed
+    information about the data size (detector size, reconstruction
+    size, number of projections, etcetera). Furthermore, please show
+    timing results for all steps of the algorithm, including the
+    computation of the low quality reconstructions, pilot
+    reconstructions, and building of eigenspaces.}}
+
+\textbf{Response}:
+
+\begin{enumerate}
+
+\item \emph{ \ldots therefore it would be good \ldots } Indeed, this
+  is precisely what we have done.  Sadly our column header of Table-6
+  conveyed a different impression. We intended to indicate that FDK is
+  good for sufficient views, and TV is sufficent for moderate
+  views. We ended up misleading the reviewer.
+
+  Hence, we have edited the caption and Table-field titles of Table-6
+  (Page 10) to accurately describe details of measurement.
+
+\item \emph{ \ldots all steps \ldots} We also provide the details
+  required.  We note that the TV reconstruction \emph{is} our pilot
+  reconstruction and hence the computation times are equal.
+
+  Having specified the exact compute times in our machine, we also
+  note that the type of machine and the degree of parallelism
+  available in the current times make these timing measurements,
+  especially for iterative solutions, subjective.
+
+\end{enumerate}
+
+\begin{figure}[!t]
     \begin{subfigure}[b]{0.19\linewidth}
-        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_1.png}
+        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_1.png}
 \captionsetup{labelformat=empty}       
@@
     \begin{subfigure}[b]{0.19\linewidth}
-        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_2.png}
+        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_2.png}
 \captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.19\linewidth}
-        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_3.png}
+        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_3.png}
 \captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.19\linewidth}
-        \includegraphics[width=\textwidth]{../images/thesis/okra/templateCropped_4.png}
+        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_4.png}
 \captionsetup{labelformat=empty}
@@
     \begin{subfigure}[b]{0.186\linewidth}
-        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/thesis/okra/testCropped.png}}
+        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}
 \captionsetup{labelformat=empty}
@@
      \end{subfigure}
-     \caption[Okra 3D dataset]{Okra 3D dataset: One slice each from the templates (the
+     \caption[Okra 3D dataset]{Okra 3D dataset: One slice each from
+       the templates (the 
        first four from the left), and one from the test volume
@@
 \centering
-\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/testCropped.png}}\hfill
-\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/fdk_cropped.png}}\hfill
-\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/cs_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/prior_weighted_cropped.png}}
+\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}\hfill
+\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/fdk_cropped.png}}\hfill
+\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
+\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
 \caption[3D reconstruction of okra dataset]{3D reconstruction of the okra from $10\%$ projection
@@
 
-\begin{figure}[!h]
+\begin{figure}[!b]
 \centering
-\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/input_cropped.png}}\hfill
-\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
-\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
+\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/input_cropped.png}}\hfill
+\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
+\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
 \caption[Zoomed results of Okra dataset]{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
-  shows up as a false positive) and (e) new information detected (no deformities
- ).}
+  shows up as a false positive) and (e) new information detected (no deformities).}
 \label{fig:okra_zoomed_3D_results}
 \end{figure}
+
+\textcolor{blue}{\textbf{[R2-3]:}\textit{In several parts of the
+    paper, the authors claim that existing object-prior based methods
+    have problems, e.g.: "A common problem with these techniques is
+    the strong influence of object-priors in the reconstruction of new
+    regions in the test". At the moment, this hard claim is not
+    supported in the paper by references or (even better) comparison
+    results. It would be good to show, on one (or more) of the
+    datasets used, that this is indeed the case, and that the proposed
+    methods solves this problem.}}
+
+\textbf{Response:} We have now included a reference (Pg.2, Line 3
+under Sec.1-A) to a PhD thesis wherein the problem of object-priors
+biasing the reconstruction of new test regions is discussed in detail.
+A sample result (Fig.1-3 here) from the thesis is shown below. It
+illustrates how an unweighted application of prior can adversely
+affect the reconstruction of new regions in the test.
 

### 2022-02-13 paper/post_tci.tex
Removed brackets for RMSE in tables

@@
   \centering
-  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed potato from various
+  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of reconstructed potato from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.22, 0.52 (0.36)
-& 0.86, 0.92 (0.06) & \textcolor{red}{0.95, 0.97 (0.03)} \\ \hline \textbf{3D} & 0.30, 0.58 (0.26) & 0.56, 0.75 (0.21) & \textcolor{red}{0.72, 0.84 (0.16)}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.22, 0.52, 0.36
+& 0.86, 0.92, 0.06 & \textcolor{red}{0.95, 0.97, 0.03} \\ \hline \textbf{3D} & 0.30, 0.58, 0.26 & 0.56, 0.75, 0.21 & \textcolor{red}{0.72, 0.84, 0.16}
 \\ \hline
@@
   \centering
-  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed okra from various
+  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of reconstructed okra from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline \textbf{2D} & 0.26, 0.46 (0.28)
-& 0.27, 0.50 (0.24) & \textcolor{red}{0.56, 0.74 (0.15)} \\ 
-\hline \textbf{3D} & 0.52, 0.65 (0.22) & 0.56, 0.70 (0.21) & \textcolor{red}{0.57, 0.71 (0.19)}
+\textbf{This paper} \\ \hline \textbf{2D} & 0.26, 0.46, 0.28
+& 0.27, 0.50, 0.24 & \textcolor{red}{0.56, 0.74, 0.15} \\ 
+\hline \textbf{3D} & 0.52, 0.65, 0.22 & 0.56, 0.70, 0.21 & \textcolor{red}{0.57, 0.71, 0.19}
 \\ \hline
@@
   \centering
-  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
+  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
 %For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
@@
 \hline \textbf{Backprojection} & \textbf{TV} &
-\textbf{This paper} \\ \hline 0.54, 0.73 (0.04)
-& 0.80, 0.91 (0.09) & \textcolor{red}{0.90, 0.95 (0.03)} \\ \hline 
+\textbf{This paper} \\ \hline 0.54, 0.73, 0.04
+& 0.80, 0.91, 0.09 & \textcolor{red}{0.90, 0.95, 0.03} \\ \hline 
 \end{tabular}
@@
   \centering
-  \caption{Default-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed sprouts from various
+  \caption{Default-SSIM, structure-focussed SSIM and RMSE within the RoI of reconstructed sprouts from various
     methods. 
@@
 \textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
- \\ \hline \textbf{2D} & 0.42, 0.67 (0.24)
-& 0.61, 0.82 (0.17) & \textcolor{red}{0.72, 0.86 (0.13)} \\ \hline \textbf{3D} & 0.44, 0.67 (0.25) & 0.47, 0.73 (0.23) & \textcolor{red}{0.66, 0.82 (0.14)}
+ \\ \hline \textbf{2D} & 0.42, 0.67, 0.24
+& 0.61, 0.82, 0.17 & \textcolor{red}{0.72, 0.86, 0.13} \\ \hline \textbf{3D} & 0.44, 0.67, 0.25 & 0.47, 0.73, 0.23 & \textcolor{red}{0.66, 0.82, 0.14}
 \\ \hline

### 2022-02-13 3D_Recon/sprouts/ParamSetting_sprouts.m
Added sprouts 3D recon scripts

@@ -1,0 +1,81 @@
+%% Parameter setting %%
+
+% % % % % % Confirm your parameters % % % % % % %
+function ParamSetting_sprouts(angStepSize)
+
+param.nx = 130;%number of voxels
+param.ny = 130;
+param.nz = 130;
+
+param.sx = 25;% mm (real size)
+param.sy = 25;% mm 114
+param.sz = 24;% mm  
+
+%The real detector panel pixel density (number of pixels)
+param.nu = 512;		% number of pixels
+param.nv = 512;
+
+% Detector setting (real size)
+param.su = 512*0.2*4;	% mm (real size)
+param.sv = 512*0.2*4;   % mm
+
+% X-ray source and detector setting
+param.DSD = 974.182;    %  Distance source to detector 
+param.DSO = 126.644;	%  X-ray source to object axis distance
+
+% angle setting
+param.dir = 1;   % gantry rotating direction (clock wise/ counter clockwise)
+param.dang = angStepSize; % angular step size (deg)
+param.deg =  0:param.dang:359.9; 
+param.deg = param.deg*param.dir;
+param.nProj = length(param.deg);
+
+param.parker = 1; % data with 360 deg -> param.parker = 0 , data less than 360 deg -> param.parker=1 
+
+% % % % % % Confirm your parameters % % % % % % %
+ 
+% filter='ram-lak','cosine', 'hamming', 'hann' 
+param.filter='ram-lak'; % high pass filter
+
+param.dx = param.sx/param.nx; % single voxel size
+param.dy = param.sy/param.ny;
+param.dz = param.sz/param.nz;
+param.du = param.su/param.nu;
+param.dv = param.sv/param.nv;
+
+param.off_u = 0; param.off_v = 0; % detector rotation shift (real size)
+
+% % % Geometry calculation % % %
+param.xs = [-(param.nx-1)/2:1:(param.nx-1)/2]*param.dx;
+param.ys = [-(param.ny-1)/2:1:(param.ny-1)/2]*param.dy;
+param.zs = [-(param.nz-1)/2:1:(param.nz-1)/2]*param.dz;
+
+param.us = (-(param.nu-1)/2:1:(param.nu-1)/2)*param.du + param.off_u;
+param.vs = (-(param.nv-1)/2:1:(param.nv-1)/2)*param.dv + param.off_v;
+
+param.interptype = 'linear'; % 'linear', 'nearest'
+
+% % % % % % Confirm your parameters % % % % % % %
[…]

### 2022-02-13 3D_Recon/sprouts/compute_quant_results.m

@@ -1,0 +1,77 @@
+clear all;
+clc;
+close all;
+outDirectory = 'results/TV_with_weighted_prior/30_views';
+
+
+file = load(sprintf('%s/sprouts11_testVol.mat',outDirectory));
+testVol = double(file.data);
+file = load(sprintf('%s/FDK.mat',outDirectory));
+fdkVol = double(file.FDK);
+file = load(sprintf('%s/TV_lambdaTV_0.15.mat',outDirectory));
+tvVol = file.TV;
+file = load(sprintf('%s/weighted_prior_kk_1_lambda_prior_0.500000.mat',outDirectory));
+weightedPriorVol = file.result_weighted_pca;
+
+roi1_col = 90:115;
+roi1_row = 75:95;
+roi1_frames = 33:39;
+
+exponent_factor = [0.1 0.2 0.7]
+%  exponent_factor = [1 1 1]
+
+roi1_testVol = testVol(roi1_row,roi1_col,roi1_frames);
+roi1_fbp = fdkVol(roi1_row,roi1_col,roi1_frames);
+roi1_tv = tvVol(roi1_row,roi1_col,roi1_frames);
+roi1_weighted_pca = weightedPriorVol(roi1_row,roi1_col,roi1_frames);
+
+roi1_testVol  = roi1_testVol  - min(roi1_testVol (:));
+roi1_testVol  = roi1_testVol ./max(roi1_testVol (:));
+roi1_fbp = roi1_fbp - min(roi1_fbp(:));
+roi1_fbp = roi1_fbp./max(roi1_fbp(:));
+roi1_tv = roi1_tv - min(roi1_tv(:));
+roi1_tv = roi1_tv./max(roi1_tv(:));
+roi1_weighted_pca = roi1_weighted_pca - min(roi1_weighted_pca(:));
+roi1_weighted_pca = roi1_weighted_pca./max(roi1_weighted_pca(:));  
+
+ssim1_fbp = ssim(roi1_fbp,roi1_testVol,'Exponent',exponent_factor);
+ssim1_tv = ssim(roi1_tv,roi1_testVol,'Exponent',exponent_factor);
+ssim1_weighted_pca = ssim(roi1_weighted_pca,roi1_testVol,'Exponent',exponent_factor); 
+[relRMSE1_fbp, rmse1_fbp] = rmseVol(roi1_fbp,roi1_testVol)
+[relRMSE1_tv, rmse1_tv] = rmseVol(roi1_tv,roi1_testVol)
[…]

### 2022-02-13 3D_Recon/sprouts/genEigenSpaceSprouts_hole.m

@@ -1,0 +1,104 @@
+function genEigenSpaceSprouts_hole(templateNos,outDirectory)
+
+startTemplateNum = templateNos(1);
+endTemplateNum = templateNos(end);
+numTemplates = length(startTemplateNum:endTemplateNum);
+numSlices = 130; % number of slices in a volume;
+sizeOfSlice = [130 130];
+
+
+volumes  = zeros(sizeOfSlice(1),sizeOfSlice(2),numSlices,numTemplates);
+
+% Read the templates in 3D format-------------------
+
+for i = 1:numTemplates  
+   name = sprintf('inputs/sprouts_%d_syntheticVolume_1800views.mat',i+startTemplateNum-1) 
+   fileData = load(name);
+   volumes(:,:,:,i) = fileData.data;
+   image = volumes(:,:,38,i);
+   image = image - min(image(:));
+   image = image./max(image(:));
+   name = sprintf('inputs/template_%d.png',i);
+   imwrite(image,name);
+   
+end
+
+
+% store templates and test together------------------
+name = sprintf('inputs/sprouts_%d_syntheticVolume_1800views.mat',11);
+fileDataTest = load(name);
+testVol = fileDataTest.data;
+image = testVol(:,:,38);
+image = image - min(image(:));
+image = image./max(image(:));
+name = 'inputs/test.png';
+imwrite(image,name);
+
+
+all_templates = [volumes(:,:,:,1) volumes(:,:,:,2) volumes(:,:,:,3) volumes(:,:,:,4) volumes(:,:,:,5) testVol(:,:,:)];
+all_templates = all_templates - min(all_templates(:));
+all_templates = all_templates./max(all_templates(:));
+name = 'templates_and_test';
+dataset ='_';
+store_video(all_templates,name,'inputs',dataset);
+tempTestImg = [volumes(:,:,30,1) volumes(:,:,30,2) volumes(:,:,30,3) volumes(:,:,30,4) volumes(:,:,30,5) testVol(:,:,30)];
+tempTestImg = tempTestImg - min(tempTestImg(:));
+tempTestImg = tempTestImg./max(tempTestImg(:));
+imwrite(tempTestImg,'inputs/template_test_image.png');
+
+
+% resize the
+% templates--------------------------------------------------------
+templates = zeros(sizeOfSlice(1)*sizeOfSlice(2)*numSlices,numTemplates);
+
+for i = 1:numTemplates  
[…]

### 2022-02-13 3D_Recon/sprouts/main.m

@@ -1,0 +1,147 @@
+clc;clear all;
+
+dataset = 'sprouts11'
+outDirectory = ('results/TV_with_weighted_prior/30_views/');
+mkdir(outDirectory);
+sliceNumber = 38;
+lambda_prior_list = 0.5;
+
+
+angStepSize = 12;
+ParamSetting_sprouts(angStepSize)
+load('parameters_sprouts.mat');
+dim = [param.nx param.ny param.nz]; 
+
+
+
+%% Generate synthetic projections------------------------
+
+name = 'inputs/sprouts_11_syntheticVolume_1800views.mat';
+file = load(name);
+volume = double(file.data);
+proj = double(CTprojection(volume,param));
+sizeProj = size(proj);
+save('ProjectionSize.mat','sizeProj');
+
+%% --------generate Ground truth------------------
+
+testVol = volume;
+name = 'testVol';
+store_video(testVol,name,outDirectory,dataset);
+
+name = sprintf('%s/testVol.png',outDirectory);
+temp = testVol(:,:,sliceNumber);
+temp = temp - min(temp(:));
+temp = temp./max(temp(:));
+imwrite(temp,name);
+
+testVol1 = testVol - min(testVol(:));
+testVol1  = testVol1./max(testVol1(:));
+
+
+
+%% -----Filtered Back-projection-----------------------------------------------------------------
+
+disp('starting FDK');
+tic;
+[FDK] = sprouts_FDK(proj,param,dim);
+time_FDK = toc;
+
+name = 'FDK';
+store_video(FDK,name,outDirectory,dataset);
+name = sprintf('%s/FDK.mat',outDirectory);
+save(name,'testVol','FDK');
+name = sprintf('%s/FDK.png',outDirectory);
+temp = FDK(:,:,sliceNumber);
+temp = temp - min(temp(:));
+temp = temp./max(temp(:));
+imwrite(temp,name);
+
+FDK1 = FDK - min(FDK(:));
+FDK1 = FDK1./max(FDK1(:));
+
+
+%% --------TV Reconstruction (No object-prior)
+m = size(proj(:),1);
+A_both_functions =@(z,mode) systemFunction(z,mode,dim,param,m);
+y = reshape(proj,[sizeProj(1)*sizeProj(2)*sizeProj(3) 1]);
+
+
+
+lambdaTV_list = 0.17;
+for i = 1:length(lambdaTV_list)
+    lambdaTV = lambdaTV_list(i)
+    pilotReconMethods = [0,1]; 
+    
[…]

### 2022-02-13 3D_Recon/sprouts/performWeightedPriorReconstruction.m

@@ -1,0 +1,31 @@
+function [result_weighted_pca,weightsIm] =  performWeightedPriorReconstruction(dataset,y,param,...
+    dim,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,...
+    kk,sliceNumber,outDirectory)
+
+pilotRecons = cell([2,dim]);
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)        
+               fname = sprintf('%s/FDK.mat',outDirectory);
+               data = load(fname);
+               FDK = data.FDK;
+               pilotRecons{1} = FDK;
+        case(1) 
+               lambdaTV = lambda_for_base_method;
+               fname = sprintf('%s/TV_lambdaTV_%.2f.mat',outDirectory,lambdaTV);
+               data = load(fname);
+               TV = data.TV;
+               pilotRecons{2} = TV;
+    end
+end
+
+dim = size(FDK);
+
+
+numCycles = 3;
+[result_weighted_pca,weightsIm] =  weighted_prior(dataset,y,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,param,numCycles,...
+                             pilotRecons,kk,sliceNumber,outDirectory);
+                   
+
+    

### 2022-02-13 3D_Recon/sprouts/projectPilot_on_EigenSpace_3D.m

@@ -1,0 +1,121 @@
+function P_pilot = projectPilot_on_EigenSpace_3D(dataset,param,pilotOfTestVol,lambda,A_both_functions,method,sliceNumber,outDirectory)
+
+
+
+if strcmp(dataset,'sprouts11')
+    dim = size(pilotOfTestVol);
+    templateNos = [6,7,8,9,10];
+    numTemplates = length(templateNos);
+    numSlices = 130; 
+    sizeOfSlice = [130 130];
+    % resize the  templates--------------------------------------------------------
+    templates = zeros(sizeOfSlice(1)*sizeOfSlice(2)*numSlices,numTemplates);
+
+    
+    % Get the templates and compute their mean----------------------------------------------------------
+
+    for i = 1:numTemplates         
+        if strcmp(method,'FDK')       
+            fname = sprintf('%s/FDK_template_%d.mat',outDirectory,templateNos(i));
+            if(isfile(fname))
+                fprintf('Loading FDK reconstructions of template volumes from existing files\n')
+                data = load(fname);
+                FDK = data.FDK;
+            else
+                fprintf('Computing FDK reconstructions of template volumes\n');
+                name = sprintf('inputs/sprouts_%d_syntheticVolume_1800views.mat',templateNos(i))
+                fileData  = load(name);
+                FDK_high_quality = fileData.data;
+                proj = double(CTprojection(FDK_high_quality,param));
+                FDK = sprouts_FDK(proj,param,dim);
+                save(fname,'FDK');
+            end
+            temp = FDK - min(FDK(:));
+            temp = temp./max(temp(:));
+            templates(:,i) = temp(:);
+
+            
+        elseif strcmp(method,'TV')   
+                fname = sprintf('%s/TV_template_%d.mat',outDirectory,templateNos(i));
+            if(isfile(fname))
+                fprintf('Loading TV reconstructions of template volumes from existing files\n')
+                data = load(fname);
+                TV = data.TV;
+            else
+                fprintf('Computing TV reconstructions of template volumes\n');
+                name = sprintf('inputs/sprouts_%d_syntheticVolume_1800views.mat',templateNos(i))
+                fileData = load(name);
+                FDK_high_quality = fileData.data;
+                proj = double(CTprojection(FDK_high_quality,param));                
+                TV = plain_TV(proj(:),dim,lambda,A_both_functions);
[…]

### 2022-02-13 3D_Recon/sprouts/rmseVol.m

@@ -1,0 +1,7 @@
+function [rel_mseVal,rmseval] = rmseVol(resultVol,testVol)
+
+meanSqError = mean((resultVol(:) - testVol(:)).^2);
+msi = mean(testVol(:).^2);
+
+rel_mseVal = sqrt(meanSqError)/sqrt(msi);
+rmseval = sqrt(meanSqError);

### 2022-02-13 3D_Recon/sprouts/sprouts_FDK.m

@@ -1,0 +1,4 @@
+function FDK = sprouts_FDK(proj,param,dim)
+
+proj_filtered = filtering(proj,param);
+FDK = CTbackprojection(proj_filtered, param);

### 2022-02-13 3D_Recon/sprouts/store_video.m

@@ -1,0 +1,17 @@
+function store_video(data,fileName,outDirectory,dataset)
+
+data = data - min(data(:));
+data = data./max(data(:));
+dataPermuted1 = permute(data,[3 1 2]);
+dataPermuted2 = permute(data,[3 2 1]);
+name = sprintf('%s/%s_%s.mat',outDirectory,dataset,fileName);
+save(name,'data');
+name = sprintf('%s/%s_%s_z.avi',outDirectory,dataset,fileName);
+writevideo (name, data,8);
+name = sprintf('%s/%s_%s_y.avi',outDirectory,dataset,fileName);
+writevideo (name, dataPermuted1, 8);
+name = sprintf('%s/%s_%s_x.avi',outDirectory,dataset,fileName);
+writevideo (name, dataPermuted2, 8);
+
+
+

### 2022-02-13 3D_Recon/sprouts/systemFunction.m

@@ -1,0 +1,25 @@
+function output = systemFunction(z,mode,dim,param,m)
+
+if mode==0
+    n = dim(1)*dim(2)*dim(3);
+    output = [m n];
+    
+elseif mode==1
+    
+    X_data = z;
+    X = reshape(X_data,[dim(1) dim(2) dim(3)]);
+    proj = CTprojection(X,param);
+    sizeProj = size(proj);
+    b = reshape(proj,[sizeProj(1)*sizeProj(2)*sizeProj(3) 1]);
+    output = double(b);
+    
+elseif mode==2
+    
+    b_data = z;
+    f = load('ProjectionSize.mat');
+    b_data = reshape(b_data,[f.sizeProj(1) f.sizeProj(2) f.sizeProj(3)]);
+    proj_filtered = filtering(b_data,param);
+    backProjImg = CTbackprojection(proj_filtered, param);
+    X_final = reshape(backProjImg,[size(backProjImg,1)*size(backProjImg,2)*size(backProjImg,3) 1]);
+    output = double(X_final);
+end

### 2022-02-13 3D_Recon/sprouts/systemFunction_prior.m

@@ -1,0 +1,49 @@
+function output = systemFunction_prior(z,mode,param,dim,m,lambda_prior,W)
+
+if mode==0
+    n = dim(1)*dim(2)*dim(3);
+    output = [m n];
+    
+elseif mode==1  %forward system matrix operator
+    
+    X = z;
+    X = reshape(X,[dim(1) dim(2) dim(3)]);
+    
+    proj = CTprojection(X,param);
+    sizeProj = size(proj);
+    b1 = reshape(proj,[sizeProj(1)*sizeProj(2)*sizeProj(3) 1]);
+    save('ProjectionSize.mat','sizeProj');
+    
+    vectX =  lambda_prior.*reshape(X,[dim(1)*dim(2)*dim(3) 1]).*W(:); 
+    output = cat(1,b1,vectX);
+    output = double(output);
+    
+elseif mode==2
+    
+    b_data = z;
+    s1 = size(b_data,1)-(dim(1)*dim(2)*dim(3)); %m
+    s2 = size(b_data,1);  %(m+n)
+
+    startPt = 1;
+    endPt =  s1;
+    b = b_data(startPt:endPt);
+    
+    startPt = endPt + 1;
+    endPt = s2;
+    Y2 = b_data(startPt:endPt);
+
+    f = load('ProjectionSize.mat');
+    b = reshape(b,[f.sizeProj(1) f.sizeProj(2) f.sizeProj(3)]);
+    proj_filtered = filtering(b,param);
+    backProjImg = CTbackprojection(proj_filtered, param);
+
+    X = reshape(backProjImg,[size(backProjImg,1)*size(backProjImg,2)*size(backProjImg,3) 1]); 
+       
+%-------------- Modification for the PICCS part -starts------------------
+    X = X + (lambda_prior).*Y2.*W(:);
+
+%-------------- Modification for the PICCS part -ends------------------
+
+    output = double(X);
+
+end

### 2022-02-13 3D_Recon/sprouts/weighted_prior.m

@@ -1,0 +1,144 @@
+function [result_weighted_prior,W] =  weighted_prior(dataset,y_given,pilotReconMethods,lambda_for_pilot_recon, baseMethod,lambda_for_base_method,lambda_prior,dim,param,numCycles,...
+                                 pilotRecons,kk,sliceNumber,outDirectory)
+
+fname = sprintf('%s/EigenSpace_%s_hole.mat',outDirectory,'sprouts'); 
+es = load(fname);
+eigenVecs = es.eigenVecs;
+meanTemplateOriginal = es.meanTemplate;
+m = size(y_given,1);
+A_both_functions =@(z,mode) systemFunction(z,mode,dim,param,m);  
+
+%%  --------------------------construct the weight map---------------------------------------
+
+for iter = 1:length(pilotReconMethods)
+    method = pilotReconMethods(iter);
+    switch(method)
+        case(0)
+            lambda = 1; % dummy value
+            FDK = pilotRecons{1};
+            FDK = FDK - min(FDK(:));
+            FDK = FDK./max(FDK(:));	
+            method_name = 'FDK';
+            P_FDK = projectPilot_on_EigenSpace_3D(dataset,param,FDK,lambda,A_both_functions,method_name,sliceNumber,outDirectory);
+            fname = sprintf('%s/ProjectedTestFDK.mat',outDirectory);
+            save(fname,'P_FDK');
+            name = sprintf('%s/FDK_P_FDK.png',outDirectory);
+            temp = [FDK(:,:,sliceNumber) P_FDK(:,:,sliceNumber)];
+            %figure;imshow(temp,[]);
+            temp = temp - min(temp(:));
+            temp = temp/max(temp(:));
+            imwrite(temp,name);
+        case(1)
+            lambda_for_method = lambda_for_pilot_recon(2); 
+            lambda_TV = lambda_for_method{1};
+            TV = pilotRecons{2};
+            TV = TV - min(TV(:));
+            TV = TV./max(TV(:));
+            method_name = 'TV';
+            P_TV = projectPilot_on_EigenSpace_3D(dataset,param,TV,lambda_TV,A_both_functions,method_name,sliceNumber,outDirectory);
+            fname = sprintf('%s/ProjectedTestTV.mat',outDirectory);
+            save(fname,'P_TV');
+            name = sprintf('%s/TV_P_TV.png',outDirectory);
[…]

### 2022-02-13 3D_Recon/sprouts/writeColorVideo.m

@@ -1,0 +1,12 @@
+function writeColorVideo (filename, vid, framerate)
+
+[H,W,C,NF] = size(vid);
+ff = VideoWriter(filename);
+ff.FrameRate = framerate;
+
+
+open (ff);
+for i=1:NF
+    writeVideo(ff,vid(:,:,:,i));
+end
+close (ff);

### 2022-02-13 paper/response_2022.tex
Corrected github link

@@
       github repository:
-      \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}
+      \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}.
       This repository is currently not a public repository since the
@@
   well in the github repository:
-  \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction.}
+  \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}.
 

### 2022-02-15 3D_Recon/okra/main.m
Removed data files; minor changes in scripts

@@ -9,7 +9,7 @@ mkdir(outDirectory);
 sliceNumber = 30;
 lambda_prior_list = [0.1,0.3,0.5,0.7,0.9];
 
-projFileName = sprintf('inputs/Preeti_%s/projf32_LIN_AP.nc',dataset);
+projFileName = sprintf('inputs/%s/projf32_LIN_AP.nc',dataset);
 ncid = netcdf.open(projFileName);
 proj = double(netcdf.getVar(ncid,1));
 netcdf.close(ncid);

### 2022-02-15 paper/response_2022.tex
Rewritten reponses pertaining sharing of code

@@
 
-      To ensure reproducibility, we had earlier shared the code files
-      for 2D reconstructions. We have now added complete code for 3D
-      reconstructions as well, and as suggested, placed them in our
-      github repository:
+      In addition to the previously shared code for 2D reconstructions, we have now added code for 3D reconstructions in our github repository:\\
       \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}.
-      This repository is currently not a public repository since the
-      paper is in the review process.
+This ensures reproducibility of our results.
+The repository is currently not a public repository since the  paper is in the review process.
 
@@
 
-  \textbf{Response:} Earlier, we had shared the complete code for 2D
-  reconstruction. We have now added code for 3D reconstructions as
-  well in the github repository:
-  \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}.
+  \textbf{Response:} We had earlier shared code for 2D
+  reconstructions in our github repository:\\
+  \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}. To this, we have now added code for 3D reconstructions for all datasets.
 

### 2022-02-15 paper/response_2022.tex
Itemized a few responses

@@
 
-  Duly noted the issue of ``old-regions'', we have defined and
+\begin{enumerate}
+
+\item \emph{ \ldots introduces terms such as "new regions" and "old regions"
+      that don't carry any meaning. \ldots }Duly noted the issue of ``old-regions'', we have defined and
   re-written the  abstract.
 
-  While we appreciate the suggestion on the quantification of our
+  \item \emph {\ldots You may want to add a line or two that quantifies
+      the fidelity of your reconstructions \ldots} While we appreciate the suggestion on the quantification of our
   results, we felt that (as styles go) it would be better to keep a
   lower profile because of the dependency on various factors such as
-  the number of views and structural complexity of the object data
+  the number of views, type of imaging geometry and structural complexity of the object data
   itself.
+
+  \end{enumerate}
 
@@
 
-\textbf{Response:} Since the aim of our experiments is to demonstrate the benefit of using weighted prior reconstruction, we adjust these parameters by assuming the ground-truth to be known.
+\textbf{Response:}
+\begin{enumerate}
+
+\item Use of ground-truth:\\ Since the aim of our experiments is to demonstrate the benefit of using weighted prior reconstruction, we adjust these parameters by assuming the ground-truth to be known.
 However, we do not assume the Region Of Interest (RoI) of the test to be known.
 
-We note that in practice, however, since ground-truth will never be
+\item Choosing paramters in real-life scenario: \\We note that in practice, however, since ground-truth will never be
 available, these parameters must be tuned using only the set of
@@
 
-As mentioned in Sec.6-B of the paper, $\lambda_1$ was tuned to maximize the SSIM of the complete reconstructed test volume using the TV-only regularizer.
+\item Our choice of $\lambda_1$ and $\lambda_2$ for demonstration: \\As mentioned in Sec.6-B of the paper, $\lambda_1$ was tuned to maximize the SSIM of the complete reconstructed test volume using the TV-only regularizer.
 With the already chosen optimal $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM with reference to the ground truth.
 
-As far as the stability of parameter $k$ is concerned, in Fig.
+\item Choosing $k$:\\ As far as the stability of parameter $k$ is concerned, in Fig.
 8 of our paper, we show how the quality of reconstructions vary for different values of $k$.
@@
 In real-world, $k$ must also be tuned by using one of the templates as pseudo-test and performing a grid search to select the best value.\\
+
+  \end{enumerate}
 

### 2022-02-15 paper/response_2022.tex
word smithing and figure layout

@@
-\documentclass{article}
+\documentclass[11pt]{article}
 \usepackage{amsmath}
@@
 \usepackage[colorlinks=true]{hyperref}
-\title{Author Response to Reviewers for the paper `Reducing object prior-bias in sparse projection tomographic reconstructions'}
+\title{Author Response to Reviewers for the paper `Reducing object
+  prior-bias in sparse projection tomographic reconstructions'} 
 \begin{document}
+\date{}
 \maketitle
@@
 We thank all the reviewers for their detailed feedback on our
-work. Based on their comments, we have incorporated significant
-changes in our revised paper, and have discussed these in this
-document. We also request the reviewers to read these comments along
-with the changes in the paper, especially related the comments in
-Section~6 (Results).
+work. Based on the comments, we have incorporated significant changes
+in our revised paper, and have discussed these in this document. We
+also request the reviewers to read these comments along with the
+changes in the paper, especially related to the comments in Section~6
+(Results), these being the most significant ones.
 
@@
 
-      In addition to the previously shared code for 2D reconstructions, we have now added code for 3D reconstructions in our github repository:\\
-      \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}.
-This ensures reproducibility of our results.
-The repository is currently not a public repository since the  paper is in the review process.
+      In addition to the previously shared code for 2D
+      reconstructions, we have now added code for 3D reconstructions
+      \href{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}{in
+        our github repository}. This ensures reproducibility of our
+      results. The repository is currently not a public repository
+      since the paper is still in the review process.
 
@@
 
-As a side note, based on the suggestion of R3, we have made a
-slight change to the title of the paper using the word ``Mitigating''
-instead of ``Eliminating''.
+  As an additional note, based on the suggestion of R3, we have made a
+  slight change to the title of the paper using the word
+  ``Mitigating'' instead of ``Eliminating''.
 
-  \section{Recommendation R1: AQ - Publish With Minor, Required
+  \section{R1: AQ - Publish With Minor, Required
     Changes}
 
-  \textbf{Comments:}The authors have significantly improved their
+  \textbf{Comments:} The authors have significantly improved their
   paper when compared to the earlier rejected submission. The results
@@
 
-  \textcolor{blue}{\textbf{[R1-1,2; re-wording abstract]:}\textit{In
+  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-1,2; re-wording abstract]:} \textit{In
       the abstract, I feel you are underselling your
@@
       prior." introduces terms such as "new regions" and "old regions"
-      that don't carry any meaning. Please rewrite.}}\\
+      that don't carry any meaning. Please rewrite.}}
 
@@
 \begin{enumerate}
-
-\item \emph{ \ldots introduces terms such as "new regions" and "old regions"
-      that don't carry any meaning. \ldots }Duly noted the issue of ``old-regions'', we have defined and
-  re-written the  abstract.
 
@@
   itself.
+\item \emph{ \ldots introduces terms such as "new regions" and "old regions"
+      that don't carry any meaning. \ldots }Duly noted the issue of ``old-regions'', we have defined and
+  re-written the  abstract.
 
@@
 
-  \textcolor{blue}{\textbf{[R1-3]:}\textit{In page 3 and lines 50-53
+  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-3]:}\textit{In page 3 and lines 50-53
       right column, you mention that your code will be
@@
 
-  \textbf{Response:} We had earlier shared code for 2D
-  reconstructions in our github repository:\\
-  \url{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}. To this, we have now added code for 3D reconstructions for all datasets.
+  \textbf{Response:} We had earlier shared code for 2D reconstructions
+  \href{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}{in
+    our github repository}. To this, we have now added code for 3D
+  reconstructions for all datasets.
 
-  \textcolor{blue}{\textbf{[R1-4]:}\textit{In page 7 and lines 39-42
+  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-4]:}\textit{In page 7 and lines 39-42
       left column, what are the weights for? I don't see any equation
@@
   \textbf{Response:} This point has come up in R2 as well (in a larger
-  context), and we defer the discussion to that response.  Our earlier
-  usage of the term `weights' with respect to SSIM might have been
-  confusing since we also refer to `weights-map' throughout our paper.
+  context), and we defer our detailed response to that section. In
+  general, we agree that our earlier usage of the term `weights' with
+  respect to SSIM might have been confusing since we also refer to
+  `weights-map' throughout our paper.
 
-\textcolor{blue}{\textbf{[R1-5, 6 (on Hyper-parameters)]:}\textit{In page 7 and lines 52-56 left column, I don't understand your tuning of $\lambda_1$.
-How is SSIM optimized when ground-truth is unknown for the test volume?
-    It appears that the weight $\lambda_2$ must be chosen carefully and sufficiently high to ensure that we achieve the very fidelity reconstruction shown in Fig.
-11 (h) with just 6 views.
-A lower incorrect choice for $\lambda_2$ will certainly bring back the artifacts.
-Even the parameter k probably plays an important role in achieving Fig.
-11(h).
-Thus, your explanation for choosing $\lambda_2$ (in page 7 and lines 8-10 right column) and k (in page 7 and lines 23-27 right column) is inadequate.
-If you base your choice of $\lambda_2$ and k on "tolerance for noise" and/or "artifacts", how do you even quantify the relevant noise and artifacts?
-If $\lambda_2$ and k are chosen incorrectly, I am sure your method won't work.
-Hence, this detail needs to be discussed.}}\\
+  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-5, 6 (on Hyper-parameters)]:} \textit{In
+      page 7 and lines 52-56 left column, I don't understand your
+      tuning of $\lambda_1$. How is SSIM optimized when ground-truth
+      is unknown for the test volume?  It appears that the weight
+      $\lambda_2$ must be chosen carefully and sufficiently high to
+      ensure that we achieve the very fidelity reconstruction shown in
+      Fig. 11 (h) with just 6 views. A lower incorrect choice for
+      $\lambda_2$ will certainly bring back the artifacts. Even the
+      parameter k probably plays an important role in achieving
+      Fig. 11(h). Thus, your explanation for choosing $\lambda_2$ (in
+      page 7 and lines 8-10 right column) and k (in page 7 and lines
+      23-27 right column) is inadequate. If you base your choice of
+      $\lambda_2$ and k on "tolerance for noise" and/or "artifacts",
+      how do you even quantify the relevant noise and artifacts? If
+      $\lambda_2$ and k are chosen incorrectly, I am sure your method
+      won't work. Hence, this detail needs to be discussed.}}
 
@@
 
-\item Choosing paramters in real-life scenario: \\We note that in practice, however, since ground-truth will never be
-available, these parameters must be tuned using only the set of
-templates available.  One of the templates can be assumed to be a
-pseudo-test, and a grid search can be performed to get the best
-possible hyperparameter values. These values can then be used for
-reconstructing the `real' test volume.
+\item Choosing paramters in real-life scenario: \\We note that in
+  practice, however, since ground-truth will never be available, these
+  parameters must be tuned using only the set of templates available.
+  One of the templates can be assumed to be a pseudo-test, and a grid
+  search can be performed to get the best possible hyperparameter
+  values. These values can then be used for reconstructing the `real'
+  test volume.  Since the available templates are of high quality,
+  this is a reasonable technique.
 
-\item Our choice of $\lambda_1$ and $\lambda_2$ for demonstration: \\As mentioned in Sec.6-B of the paper, $\lambda_1$ was tuned to maximize the SSIM of the complete reconstructed test volume using the TV-only regularizer.
-With the already chosen optimal $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM with reference to the ground truth.
+\item Our choice of $\lambda_1$ and $\lambda_2$ for demonstration:
+  \\As mentioned in Sec.6-B of the paper, $\lambda_1$ was tuned to
+  maximize the SSIM of the complete reconstructed test volume using
+  the TV-only regularizer. This of course favours the TV-only
+  regularizer method in contrast to not favouring our method.  With
+  the already chosen optimal $\lambda_1$, we apply our method for a
+  range of $\lambda_2$ values and select the one that gives the best
+  SSIM with reference to the ground truth.
 
-\item Choosing $k$:\\ As far as the stability of parameter $k$ is concerned, in Fig.
-8 of our paper, we show how the quality of reconstructions vary for different values of $k$.
-We see that the reconstructions are similar for a significant range of $k$ values.
-(5-40) for Okra.
-For the purposes of demonstrating the benefit of our method, we choose $k$ omnisciently assuming known ground truth of test (and unknown RoI).
-In real-world, $k$ must also be tuned by using one of the templates as pseudo-test and performing a grid search to select the best value.\\
+\item Choosing $k$:\\ As far as the stability of parameter $k$ is
+  concerned, in Fig.\ 8 of our paper, we show how the quality of
+  reconstructions vary for different values of $k$. We see that the
+  reconstructions are similar for a significant range of $k$
+  values (viz. (5-40) for Okra). For the purposes of demonstrating the
+  benefit of our method, we choose $k$ omnisciently assuming known
+  ground truth of test (and unknown RoI). In real-world, $k$ must also
+  be tuned by using one of the templates as pseudo-test and performing
+  a grid search to select the best value.
 
@@
 
-\section{Recommendation R2: RQ - Review Again After Major Changes}
+\section{R2: RQ - Review Again After Major Changes}
 
-\textbf{Comments:}The paper has greatly improved with the new focus! I would like to thank the authors for the extra work. I do have a few remaining comments:\\
+\textbf{Comments:}The paper has greatly improved with the new focus! I
+would like to thank the authors for the extra work. I do have a few
+remaining comments:
 
-\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use
     standard metrics for comparison, instead of the custom metrics
@@
 
+\item Rescaling
+
+For computation of both SSIM and RMSE, we find that rescaling is
+necessary because the different optimization routines generate
+solutions whose ranges vary from that of the ground truth.  For
+example, for reconstruction of the potato data from 18 views,
+Table~\ref{Tab:ranges} shows the minimum and maximum intensity values
+of the groundtruth and reconstructed volumes (in the case of TV
+regularization). The pernicious effect of this is obviously invisible
+in the qualitative results where the display program autoadjusts
+showing TV superior to FDK. In a quantitative setting it becomes
+necessary to rescale, otherwise TV (using a prior) will appear to be
+inferior to FDK (without a prior), when it's obviously not the case.
+The same issue persists in the reconstruction using the external
+optimization program mentioned. %TODO give section or reference?
+
+  \begin{table}[h!]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+      \hline
+      & \textbf{\begin{tabular}[c]{@{}l@{}}Ground\\ truth\end{tabular}} & \textbf{FDK} & \textbf{TV} \\ \hline
+      \textbf{Minimum} & 0.00 & -0.19 & 0.00 \\ \hline
+      \textbf{Maximum} & 1.00 & 0.24 & 0.24 \\ \hline
+    \end{tabular}
+    \caption{ \label{Tab:ranges} Example. Minimum and maximum
+      intensity values of groundtruth and reconstructed volumes of
+      potato data reconstructed from 18 views.}
+  \end{table}
+
   \item
 
-    [Meta comment: This section is also in response to R1 (\emph{SSIM
-      have their own definitions}.]
+    [Meta comment: This section is also in response to R1 (\ldots \emph{SSIM
+      have their own definitions}\ldots]
 
@@
 
-    However, in the revised version, we have now included quantitative
+    However, in the revised version, \emph{we have now included quantitative
     results with both custom (structure-focussed) SSIM and default
     SSIM. The benefit of the proposed method is seen with
-    \textbf{either} setting of the metric.
+    \textbf{either} setting of the metric.}
 
@@
 be adjusted to suit the application goal.
-
-\item Rescaling
-
-  For computation of both SSIM and RMSE, we find that rescaling is
-  necessary because the different optimization routines generate
-  solutions whose ranges vary from that of the ground truth.  For
-  example, for reconstruction of the potato data from 18 views,
-  Table~\ref{Tab:ranges} shows the minimum and maximum intensity
-  values of the groundtruth and reconstructed volumes (in the case of
-  TV regularization). The pernicious effect of this is obviously
-  invisible in the qualitative results where the display program
-  autoadjusts showing TV superior to FDK. In a quantitative setting it
-  becomes necessary to rescale, otherwise TV using a prior will appear
-  to be inferior to FDK (without a prior).  The same issue persists in
-  the reconstruction using the external optimization program
-  mentioned. %TODO give section or reference?
-
-\begin{table}[]
-  \centering
-  \caption{Minimum and maximum intensity values of groundtruth and
-    reconstructed volumes of potato data reconstructed from 18
-    views.}
-  \begin{tabular}{|l|l|l|l|}
-\hline
- & \textbf{\begin{tabular}[c]{@{}l@{}}Ground\\ truth\end{tabular}} & \textbf{FDK} & \textbf{TV} \\ \hline
-\textbf{Minimum} & 0.00 & -0.19 & 0.00 \\ \hline
-\textbf{Maximum} & 1.00 & 0.24 & 0.24 \\ \hline
-  \end{tabular}
-  \label{Tab:ranges}
-\end{table}
 \end{enumerate}
 
-\textcolor{blue}{\textbf{[R2-2]:}\textit{The computation comparison is
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-2]:}\textit{The computation comparison is
     not very convincing to me. In practice, given a certain number of
@@
 
-\begin{figure}[!t]
+\begin{figure}[p]
     \begin{subfigure}[b]{0.19\linewidth}
@@
 \captionsetup{labelformat=empty}       
- \caption{}
+% \caption{}
     \end{subfigure}
@@
 \captionsetup{labelformat=empty}
-        \caption{}
+%        \caption{}
      \end{subfigure}
@@
 \captionsetup{labelformat=empty}
-        \caption{}
+%        \caption{}
      \end{subfigure}
-     \caption[Okra 3D dataset]{Okra 3D dataset: One slice each from
-       the templates (the 
-       first four from the left), and one from the test volume
-       (extreme right). In the regions marked in red and green, while
-       all slices have deformities, the test
+     \caption[Okra 3D dataset]{One slice each from the templates and
+       one from the test volume (extreme right). In the regions marked
+       in red and green, while all slices have deformities, the test
        has none.}
 \label{fig:templates_test_okra}
-\end{figure}
-%----------------------------------------------------
-
-\begin{figure}[!h]
+%\end{figure}
+%\begin{figure}[p]
 \centering
@@
 \subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
-\caption[3D reconstruction of okra dataset]{3D reconstruction of the okra from $10\%$ projection
-  views (b) has strong streak artefacts, (c) blurred, (d) no new
+%\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
+\subcaptionbox{This paper}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
+\caption[3D reconstruction of okra dataset]{Reconstruction from $10\%$
+  views: (b) strong streak artefacts, (c) blurred, (d) no new
   information detected (prior dominates -- the deformity from the prior
@@
 \label{fig:okra_3D_results}
-\end{figure}
-
-%--------------------------------------zoomed okra
-
-\begin{figure}[!b]
+%\end{figure}
+%\begin{figure}[p]
 \centering
@@
 \subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
-\caption[Zoomed results of Okra dataset]{Zoomed in portion corresponding to the red RoI of Fig.~\ref{fig:okra_3D_results} for various methods (b) has strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
+\caption[Zoomed results of Okra dataset]{Zoomed RoI of Fig.~\ref{fig:okra_3D_results} (b) strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
   shows up as a false positive) and (e) new information detected (no deformities).}
@@
 
-\textcolor{blue}{\textbf{[R2-3]:}\textit{In several parts of the
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-3]:}\textit{In several parts of the
     paper, the authors claim that existing object-prior based methods
@@
 biasing the reconstruction of new test regions is discussed in detail.
-A sample result (Fig.1-3 here) from the thesis is shown below. It
+A sample result (Figures 1-3) from the thesis is shown. It
 illustrates how an unweighted application of prior can adversely
@@
 
-\textcolor{blue}{\textbf{[R2-4]:}\textit{The discussion of deep learning methods in Section 7B is not very strong in my opinion.
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-4]:}\textit{The discussion of deep learning methods in Section 7B is not very strong in my opinion.
 There are many existing techniques that have shown quite convincing results for reconstructing CT images with a low number of projections, even without taking into account any static parts across time.
@@
 
-\textcolor{blue}{\textbf{[R2-5]:}\textit{What algorithm is used to minimize Eq 3? How many iterations were used for this minimization? How was convergence ensured?}}\\
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-5]:}\textit{What algorithm is used to minimize Eq 3? How many iterations were used for this minimization? How was convergence ensured?}}\\
 
@@
 
-\textcolor{blue}{\textbf{[R2-6]:}\textit{What were the various parameters of the reconstructions show in Fig 11? How were they chosen?
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-6]:}\textit{What were the various parameters of the reconstructions show in Fig 11? How were they chosen?
 }}\\
@@
 
-\textcolor{blue}{\textbf{[R2-7]:}\textit{How was the $\lambda_2$ parameter empirically chosen?
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-7]:}\textit{How was the $\lambda_2$ parameter empirically chosen?
 }}\\
@@
 
-\textcolor{blue}{\textbf{[R2-8]:}\textit{In some parts of the paper, the use of language could be improved. Also, I think it is better to not use words like `paltry'.}}\\
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-8]:}\textit{In some parts of the paper, the use of language could be improved. Also, I think it is better to not use words like `paltry'.}}\\
 
@@
 
-\section{Recommendation R3: RQ - Review Again After Major Changes}
+\section{R3: RQ - Review Again After Major Changes}
 
@@
 
-\textcolor{blue}{\textbf{[R3-1]:}\textit{One challenge of the method that I can see is that these datasets needs to be aligned but there is not much discussion on this procedure or how this can be performed in a realistic setting.
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-1]:} \textit{One challenge of the method that I can see is that these datasets needs to be aligned but there is not much discussion on this procedure or how this can be performed in a realistic setting.
 Are the variation from a past to present scans looking similar?
@@
 
-\textbf{Response}:Yes, registration between the unknown test and templates is important for our method.
+\textbf{Response}: Yes, registration between the unknown test and templates is important for our method.
 Registration is also a common problem in many other fields such as MRI/CT/PET data.
@@
 
-\textcolor{blue}{\textbf{[R3-2]:}\textit{Another challenge, as the authors acknowledge, is the high number of hyper-parameters.
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-2]:}\textit{Another challenge, as the authors acknowledge, is the high number of hyper-parameters.
 I believe the paper can benefit a lot from an in depth analysis to get some insights about how this parameters should be chosen.
@@
 
-\textcolor{blue}{\textbf{[R3-3]:}\textit{The title says ``eliminating object prior-bias'', but I think this is not accurate, because you give a weight to those priors, but not fully eliminate them.
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-3]:}\textit{The title says ``eliminating object prior-bias'', but I think this is not accurate, because you give a weight to those priors, but not fully eliminate them.
 A more appropriate wording might be ``Prior-informed sparse-projection...'' or ``Weighted object-priors from past CT-scans for ...'' or something like this.}}\\
 
-\textbf{Response}: Thank you for suggesting other possible titles. We have changed it to ``Reducing object prior-bias from sparse-projection tomographic reconstructions''\\
+\textbf{Response}: Thank you for suggesting other possible titles. We
+agree. We have changed the title to ``Mitigating object prior-bias from sparse-projection tomographic reconstructions''\\
 
-\textcolor{blue}{\textbf{[R3-4]:}\textit{As a final remark, the authors can also use this technique for imaging dynamical samples. A discussion would be nice.}}\\
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-4]:}\textit{As a final remark, the authors can also use this technique for imaging dynamical samples. A discussion would be nice.}}\\
 

### 2022-02-15 paper/response_2022.tex
Cross-references included in responses

@@
       where these can be substituted for quantifying results. Also,
-      RMSE and SSIM have their own definitions.}}
+      RMSE and \hypertarget{ssim-R1}{SSIM have their own definitions}.}}
 
   \textbf{Response:} This point has come up in R2 as well (in a larger
-  context), and we defer our detailed response to that section. In
+  context), and we defer our detailed response to that section \textcolor{blue}{\textbf{\hyperlink{ssim}{[R2-1]}}}. In
   general, we agree that our earlier usage of the term `weights' with
@@
 
-  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-5, 6 (on Hyper-parameters)]:} \textit{In
+  \vspace{0.5cm}\textcolor{blue}{\textbf{\hypertarget{hyperparameters}{[R1-5, 6 (on Hyper-parameters)]:}} \textit{In
       page 7 and lines 52-56 left column, I don't understand your
@@
 
-    [Meta comment: This section is also in response to R1 (\ldots \emph{SSIM
+    [\hypertarget{ssim}{Meta comment:} This section is also in response to \hyperlink{ssim-R1}{R1} (\ldots \emph{SSIM
       have their own definitions}\ldots]
@@
 
-\textbf{Response}: Please refer to our response to a similar query in \textcolor{blue}{\textbf{[R1-5,6]}}.\\
+\textbf{Response}: Please refer to our response to a similar query in \textcolor{blue}{\textbf{\hyperlink{hyperparameters}{[R1-5,6]}}}.\\
 

### 2022-02-16 paper/response_2022.tex
minor updates in formatting

@@
 
-  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-1,2; re-wording abstract]:} \textit{In
+  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-1,2]:} \textit{In
       the abstract, I feel you are underselling your
@@
 
-  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-3]:}\textit{In page 3 and lines 50-53
+  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-3]:} \textit{In page 3 and lines 50-53
       right column, you mention that your code will be
@@
 
-  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-4]:}\textit{In page 7 and lines 39-42
+  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-4]:} \textit{In page 7 and lines 39-42
       left column, what are the weights for? I don't see any equation
@@
 
-\textbf{Comments:}The paper has greatly improved with the new focus! I
+\textbf{Comments:} The paper has greatly improved with the new focus! I
 would like to thank the authors for the extra work. I do have a few
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-1]:}\textit{I highly suggest to use
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-1]:} \textit{I highly suggest to use
     standard metrics for comparison, instead of the custom metrics
@@
     of three factors: Luminance, Contrast and Structure. These factors
-    (now termed `coefficients', earlier `weights' paper) for these
+    (now termed `coefficients', earlier `weights') for these
     three terms are adjustable to suit the application at hand.  Since
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-2]:}\textit{The computation comparison is
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-2]:} \textit{The computation comparison is
     not very convincing to me. In practice, given a certain number of
@@
 \item \emph{ \ldots therefore it would be good \ldots } Indeed, this
-  is precisely what we have done.  Sadly our column header of Table-6
-  conveyed a different impression. We intended to indicate that FDK is
-  good for sufficient views, and TV is sufficent for moderate
-  views. We ended up misleading the reviewer.
+  is precisely what we have done.  Sadly, our earlier column header of
+  Table-6 conveyed a different impression. We intended to indicate
+  that FDK is good for sufficient views, and TV is sufficent for
+  moderate views. We ended up misleading the reviewer.
 
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-3]:}\textit{In several parts of the
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-3]:} \textit{In several parts of the
     paper, the authors claim that existing object-prior based methods
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-4]:}\textit{The discussion of deep learning methods in Section 7B is not very strong in my opinion.
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-4]:} \textit{The discussion of deep learning methods in Section 7B is not very strong in my opinion.
 There are many existing techniques that have shown quite convincing results for reconstructing CT images with a low number of projections, even without taking into account any static parts across time.
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-5]:}\textit{What algorithm is used to minimize Eq 3? How many iterations were used for this minimization? How was convergence ensured?}}\\
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-5]:} \textit{What algorithm is used to minimize Eq 3? How many iterations were used for this minimization? How was convergence ensured?}}\\
 
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-6]:}\textit{What were the various parameters of the reconstructions show in Fig 11? How were they chosen?
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-6]:} \textit{What were the various parameters of the reconstructions show in Fig 11? How were they chosen?
 }}\\
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-7]:}\textit{How was the $\lambda_2$ parameter empirically chosen?
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-7]:} \textit{How was the $\lambda_2$ parameter empirically chosen?
 }}\\
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-8]:}\textit{In some parts of the paper, the use of language could be improved. Also, I think it is better to not use words like `paltry'.}}\\
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-8]:} \textit{In some parts of the paper, the use of language could be improved. Also, I think it is better to not use words like `paltry'.}}\\
 
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-2]:}\textit{Another challenge, as the authors acknowledge, is the high number of hyper-parameters.
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-2]:} \textit{Another challenge, as the authors acknowledge, is the high number of hyper-parameters.
 I believe the paper can benefit a lot from an in depth analysis to get some insights about how this parameters should be chosen.
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-3]:}\textit{The title says ``eliminating object prior-bias'', but I think this is not accurate, because you give a weight to those priors, but not fully eliminate them.
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-3]:} \textit{The title says ``eliminating object prior-bias'', but I think this is not accurate, because you give a weight to those priors, but not fully eliminate them.
 A more appropriate wording might be ``Prior-informed sparse-projection...'' or ``Weighted object-priors from past CT-scans for ...'' or something like this.}}\\
@@
 
-\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-4]:}\textit{As a final remark, the authors can also use this technique for imaging dynamical samples. A discussion would be nice.}}\\
+\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-4]:} \textit{As a final remark, the authors can also use this technique for imaging dynamical samples. A discussion would be nice.}}\\
 

### 2022-02-16 paper/post_tci.tex
Changes in DL Lit, other minor changes, added DL papers

@@
 % Do not put math or special symbols in the title.
-\title{Reducing object prior-bias from sparse-projection tomographic reconstructions}
+\title{Mitigating object prior-bias from sparse-projection tomographic reconstructions}
 %
@@
 Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework.
-\cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram.
+In ~\cite{kim2019extreme}, a generative adversarial network is used to predict a reconstruction from an extremely sparse sinogram.
+This is used as an initialization in  a traditional iterative reconstruction algorithm to compute the final reconstruction.
+Given this pipeline, our method can be used to further inform the iterative reconstruction of the available template information, as presented in Fig.~\ref{fig:Lit}.
+Among other techniques, \cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram.
 \cite{special} trains an adverserial network for artifact removal and edge preservation in limited view reconstruction.
@@
 We first construct a `weights map' that gives clear insights about regions of change within the object over time.
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=0.5\textwidth]{../images/Lit.png}
+        \caption{Illustration of the application of our method within the framework presented in~\cite{kim2019extreme}.}
+ \label{fig:Lit}
+ \end{figure}
 

### 2022-02-16 paper/response_2022.tex

@@
 \usepackage[colorlinks=true]{hyperref}
-\title{Author Response to Reviewers for the paper `Reducing object
+\title{Author Response to Reviewers for the paper `Mitigating object
   prior-bias in sparse projection tomographic reconstructions'} 
@@
 
-  \vspace{0.5cm}\textcolor{blue}{\textbf{\hypertarget{hyperparameters}{[R1-5, 6 (on Hyper-parameters)]:}} \textit{In
+  \vspace{0.5cm}\textcolor{blue}{\textbf{\hypertarget{hyperparameters}{[R1-5, 6]:}} \textit{In
       page 7 and lines 52-56 left column, I don't understand your
@@
 \subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}\hfill
-\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/fdk_cropped.png}}\hfill
-\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
-%\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
-\subcaptionbox{This paper}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/fdk_cropped.png}}\hfill
+%\subcaptionbox{CS,no prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
+\subcaptionbox{Unweighted \\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Weighted prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
 \caption[3D reconstruction of okra dataset]{Reconstruction from $10\%$
-  views: (b) strong streak artefacts, (c) blurred, (d) no new
+  views: (b) strong streak artefacts, %(c) blurred,
+  (c) no new
   information detected (prior dominates -- the deformity from the prior
-  shows up as a false positive) and (e) new information detected (no deformities
+  shows up as a false positive) and (d) new information detected (no deformities
   corresponding to red and green regions) while simultaneously
@@
 \subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
-\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\unweighted \\template priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Sparsity and \\weighted template\\ priors}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
-\caption[Zoomed results of Okra dataset]{Zoomed RoI of Fig.~\ref{fig:okra_3D_results} (b) strong streak artefacts, (c) blurred, (d) no new  information detected (prior dominates -- the deformity from the prior
-  shows up as a false positive) and (e) new information detected (no deformities).}
+%\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{Unweighted \\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{Weighted prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
+\caption[Zoomed results of Okra dataset]{Zoomed RoI of Fig.~\ref{fig:okra_3D_results} (b) strong streak artefacts, %(c) blurred,
+  (c) no new  information detected (prior dominates -- the deformity from the prior
+  shows up as a false positive) and (d) new information detected (no deformities).}
 \label{fig:okra_zoomed_3D_results}
@@
 A sample result (Figures 1-3) from the thesis is shown. It
-illustrates how an unweighted application of prior can adversely
+illustrates how an unweighted application of prior (equivalent to $\boldsymbol{W}$ being Identity matrix in Eq.3 of our paper) can adversely
 affect the reconstruction of new regions in the test.

### 2022-02-16 paper/post_tci.tex
minor edits
Rewritten DL-Lit in paper and reponse sheet

--- 2022-02-13 paper/post_tci.tex
@@
 
- In the recent past, deep learning based techniques have also been widely used for limited view CT reconstruction without the use of any longitudinal object-prior.
-For example, in~\cite{anirudh}, a neural network is trained to predict the complete sinogram from an incomplete one obtained from few-view imaging.
-This complete sinogram is then fed to analytical reconstruction algorithms to obtain the final reconstruction.
-Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework.
-\cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram.
+In the recent past, deep learning based techniques~\cite{anirudh},\cite{kim2019extreme},\cite{bo2021},\cite{special} have also been widely used for limited view CT reconstruction.
+For example, in~\cite{anirudh}, a neural network is trained to predict the complete sinogram from an incomplete one.% This complete sinogram is then fed to analytical reconstruction algorithms to obtain the final reconstruction.
+ ~\cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram.
 \cite{special} trains an adverserial network for artifact removal and edge preservation in limited view reconstruction.
-While all of the above methods predict full-view reconstruction from the measurements of test object alone, we believe it is beneficial to use information from longitudinal data, especially if naturally available, like in the radio-frequency ablation datasets that we use.
+In this work, the ability of these techniques to
+uncover new features from one or many example training images is not being disputed.
+Instead, we focus is on a new discrete algorithm that builds structural maps that can and does point to new features.
+Having said that, our work is complementary to learning-based teachniques and can fit alongside a deep learning framework.
+For example, in~\cite{kim2019extreme}, an adversarial network is used to predict a reconstruction from extremely sparse measurements.
+This is used as an initialization in  a traditional iterative reconstruction algorithm to compute the final reconstruction.
+Given this pipeline, our method can be used to further inform the iterative algorithm of the available template information, as presented in Fig.~\ref{fig:Lit}.
+
+    %Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework.
+      We further note that all of the above existing methods predict full-view reconstruction from the measurements of test object alone.
+We believe it is beneficial to use information from longitudinal data, especially if naturally available, like in the radio-frequency ablation datasets that we use.
 In this context, we present an analytical method that uses the available longitudinal data to better inform the reconstruction of the test.
 We first construct a `weights map' that gives clear insights about regions of change within the object over time.
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=0.5\textwidth]{../images/Lit.png}
+        \caption{Illustration of the application of our method (marked in yellow, red) within the deep learning based framework presented in~\cite{kim2019extreme}.}
+ \label{fig:Lit}
+ \end{figure}
 

### 2022-02-16 paper/response_2022.tex

@@
     directly predict full-view sinogram and reconstruct the test
-    object from its limited-view measurements. The ability of DL to
-    uncover new features from one or many example images or training
-    session is not being disputed. Here the focus is on a new discrete
-    algorithm that builds structural maps that can and does point to
-    new features.
+    object from its limited-view measurements. We also discuss how
+    our work is complementary to learning-based teachniques and can
+    fit alongside a deep learning framework, as seen in Figure.2 of the paper. Hence, the ability of DL to
+    uncover new features from one or many example training images is not being disputed.
+Here the focus is on a new discrete algorithm that builds structural maps that can and does point to new features.
 
@@
 %\subcaptionbox{CS,no prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
-\subcaptionbox{Unweighted \\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
-\subcaptionbox{Weighted prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
+\subcaptionbox{Only object-\\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially\\ varying object-\\ prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
 \caption[3D reconstruction of okra dataset]{Reconstruction from $10\%$
@@
 \subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/input_cropped.png}}\hfill
-\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
+\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
 %\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Unweighted \\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
-\subcaptionbox{Weighted prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
+\subcaptionbox{Only object-\\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
+\subcaptionbox{Spatially\\ varying object-\\ prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
 \caption[Zoomed results of Okra dataset]{Zoomed RoI of Fig.~\ref{fig:okra_3D_results} (b) strong streak artefacts, %(c) blurred,
@@
 \textbf{Response:} We have now included a reference (Pg.2, Line 3
-under Sec.1-A) to a PhD thesis wherein the problem of object-priors
-biasing the reconstruction of new test regions is discussed in detail.
-A sample result (Figures 1-3) from the thesis is shown. It
-illustrates how an unweighted application of prior (equivalent to $\boldsymbol{W}$ being Identity matrix in Eq.3 of our paper) can adversely
+under Sec.1-A) to a PhD thesis. This thesis discusses the problem of object-priors biasing the reconstruction of new test regions.
+A sample result (Figures 1-3) from the thesis is shown here. It
+illustrates how a direct application of object-prior can adversely
 affect the reconstruction of new regions in the test.
@@
 We have now included a discussion of deep-learning methods in `Related Work', Section 2, of our paper, and have now cited a few notable references.
+We also discuss how
+    our work is complementary to learning-based teachniques and can
+    fit alongside a deep learning framework, as seen in Figure.2 of the paper. Hence, the ability of DL to
+    uncover new features from one or many example training images is not being disputed.
+Here the focus is on a new discrete algorithm that builds structural maps that can and does point to new features.
 

### 2022-02-16 paper/post_tci.tex
reorgnaized literature

--- 2022-02-13 paper/post_tci.tex
@@
 
-In this paper, we present a technique that makes use of multiple
-object priors, corresponding to high quality reconstructions of
-similar objects across time, typically in a longitudinal study.  We
-use these priors to improve the reconstruction of the test from
-largely undersampled measurements. In particular, we define regions of
-change between the test and the eigenspace spanned by previous high
-quality object-priors in a purely data driven manner. Additionally,
-our technique differentiates between genuine structural changes and
-``changes'' that appear due to undersampling artefacts.  Besides this,
-since we use a statistical model with multiple object-priors, we avoid
-the problem of selecting an appropriate single object-prior
+In the recent past, deep learning based
+techniques~\cite{anirudh},\cite{kim2019extreme},\cite{bo2021},\cite{special}
+have been used for limited view CT reconstruction. For example,
+in~\cite{anirudh}, a neural network is trained to predict the complete
+sinogram (measurements) from an incomplete one.  This complete
+sinogram is then fed to analytical reconstruction algorithms to obtain
+the final reconstruction.  ~\cite{bo2021} presented a cascade of
+neural networks that predict full-view reconstruction from limited
+view FBP reconstruction while simultaneously ensuring consistency
+between the predicted sinogram and the acquired
+sinogram. \cite{special} trains an adversarial network for artifact
+removal and edge preservation in limited view reconstruction.
+However, all of the above existing methods predict full-view
+reconstruction from the measurements of the test object alone. We
+believe it is beneficial to use information from longitudinal data,
+especially if naturally available, like in the radio-frequency
+ablation datasets that we use.
+
+That said, the ability of these data-driven techniques to uncover new
+features is not being disputed in this work. In fact, our work can be
+used in tandem with these methods. For example, one of the state of
+the art works is \cite{kim2019extreme}, where an adversarial network
+is used to predict a reconstruction from extremely sparse measurements
+(similar to the ones we employ in this work, albeit for chest
+X-rays). This reconstruction is used as an initialization in a
+traditional analytical iterative reconstruction algorithm to compute
+the final reconstruction.  Given this pipeline, and our emphasis on
+longitudinal data, our method can be used to further inform the
+iterative algorithm of the available template information. The scheme
+is presented in Fig.~\ref{fig:Lit}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.5\textwidth]{../images/Lit.png}
+  \caption{Illustration of the application of our method (marked
+    in yellow, red) within the deep learning based framework of
+    \cite{kim2019extreme} (in blue).}
+  \label{fig:Lit}
+\end{figure}
+
+ %Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework.
+
+Our focus in this paper instead is an analytical method that uses the
+available longitudinal data to better inform the reconstruction of the
+test.  We present a technique that makes use of multiple object
+priors, corresponding to high quality reconstructions of similar
+objects across time, typically in a longitudinal study.  We use these
+priors to improve the reconstruction of the test from largely
+undersampled measurements. In particular, we define regions of change
+between the test and the eigenspace spanned by previous high quality
+object-priors in a purely data driven manner.  We first construct a
+`weights map' that gives clear insights about regions of change within
+the object over time.  Additionally, our technique differentiates
+between genuine structural changes and ``changes'' that appear due to
+undersampling artefacts.  Besides this, since we use a statistical
+model with multiple object-priors, we avoid the problem of selecting
+an appropriate single object-prior
 unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and
@@
 expert-domain knowledge about the object being scanned.
-
- In the recent past, deep learning based techniques have also been widely used for limited view CT reconstruction without the use of any longitudinal object-prior.
-For example, in~\cite{anirudh}, a neural network is trained to predict the complete sinogram from an incomplete one obtained from few-view imaging.
-This complete sinogram is then fed to analytical reconstruction algorithms to obtain the final reconstruction.
-Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework.
-\cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram.
-\cite{special} trains an adverserial network for artifact removal and edge preservation in limited view reconstruction.
-While all of the above methods predict full-view reconstruction from the measurements of test object alone, we believe it is beneficial to use information from longitudinal data, especially if naturally available, like in the radio-frequency ablation datasets that we use.
-In this context, we present an analytical method that uses the available longitudinal data to better inform the reconstruction of the test.
-We first construct a `weights map' that gives clear insights about regions of change within the object over time.
 
@@
 present reconstruction results on all datasets.  We show both
-qualitative and quantitative results.  Before we do this, it is import
+qualitative and quantitative results.  Before we do this, it is important
 to first consider our method of reporting our results.

### 2022-02-16 paper/response_2022.tex
some changes in the dl stuff

@@
     directly predict full-view sinogram and reconstruct the test
-    object from its limited-view measurements. We also discuss how
-    our work is complementary to learning-based teachniques and can
-    fit alongside a deep learning framework, as seen in Figure.2 of the paper. Hence, the ability of DL to
-    uncover new features from one or many example training images is not being disputed.
-Here the focus is on a new discrete algorithm that builds structural maps that can and does point to new features.
+    object from its limited-view measurements. We also discuss how our
+    work is complementary to learning-based teachniques and can fit
+    alongside a recent, state of the art, deep learning framework, as
+    seen in Fig.~2 of the paper. Hence, the ability of DL to uncover
+    new features is not being disputed. Instead, our focus is on a
+    novel discrete method.
 
@@
 
-\textbf{Response}: We acknowledge that there has been significant work pertaining to training neural networks to directly predict full-view sinogram and reconstruction of the test object from its limited-view measurements.
-We have now included a discussion of deep-learning methods in `Related Work', Section 2, of our paper, and have now cited a few notable references.
-We also discuss how
-    our work is complementary to learning-based teachniques and can
-    fit alongside a deep learning framework, as seen in Figure.2 of the paper. Hence, the ability of DL to
-    uncover new features from one or many example training images is not being disputed.
-Here the focus is on a new discrete algorithm that builds structural maps that can and does point to new features.
+\textbf{Response}: We acknowledge that there has been significant work
+pertaining to training neural networks to directly predict full-view
+sinogram and reconstruction of the test object from its limited-view
+measurements. We have now included a discussion of deep-learning
+methods in `Related Work', Section 2, of our paper, and have now cited
+a few notable references. We also discuss how our work is
+complementary to learning-based teachniques and can fit alongside a
+deep learning framework, as seen in Fig.~2 of the revised paper. That
+said, the focus of our work is on a new discrete algorithm that builds
+structural maps that can and does point to new features.
 

### 2022-02-17 paper/response_2022.tex
Edited response reg. registration

@@
     for which, we have now provided reference to the original paper
-    where the metric has been defined. As is well know, SSIM comprises
+    where the metric has been defined. As is well known, SSIM comprises
     of three factors: Luminance, Contrast and Structure. These factors
@@
 The focus in our paper is not on registration but on building accurate maps that delineate regions of structural changes in already pre-registered data (registered using state-of-the-art methods).
-Hence, in this work, we do not intend to predict what difficulties registration might present but rather that show that it is possible to blend prior and new views.\\
-
-We note that in practice, a pilot reconstruction of the test must be registered with similarly imaged, pilot reconstructed templates.
+Hence, in this work, we do not intend to predict what difficulties registration might present but rather that show that it is possible to blend prior and new views.
+%We note that in practice, a pilot reconstruction of the test must be registered with similarly imaged, pilot reconstructed templates.
 This registration is challenging due to the presence of sub-sampling artefacts.
-We consider the problem of registration as a separate one and intend the practitioners to use any state-of-the-art registration algorithm before applying the proposed method in our paper.
+We consider the problem of registration as a separate one and intend the practitioners to use any state-of-the-art registration algorithm, such as~\cite{robert2021},\cite{registrationThesis}, before applying the proposed method in our paper.
 \\
@@
 
-  \end{document}
-
  \bibliography{tci_ref}
